### 2021-08-07 hybridmodel.tex
Added AAAI initial version

\def\year{2022}\relax
%File: formatting-instructions-latex-2022.tex
%release 2022.1
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai22}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
%
% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
\usepackage{algorithm}
\usepackage{algorithmic}

%
% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
\usepackage{newfloat}
\usepackage{listings}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{booktabs}

\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}
%
%\nocopyright
%
% PDF Info Is REQUIRED.
% For /Title, write your title in Mixed Case.
% Don't use accents or commands. Retain the parentheses.
% For /Author, add all authors within the parentheses,
% separated by commas. No accents, special characters
% or commands are allowed.
% Keep the /TemplateVersion tag as is
\pdfinfo{
/Title (Hybrid recurrent model for time series with inclusion of external weak signals)
/Author (Etienne David, Jean Bellot, Sylvain Le Corff)
/TemplateVersion (2022.1)
}

% DISALLOWED PACKAGES
% \usepackage{authblk} -- This package is specifically forbidden
% \usepackage{balance} -- This package is specifically forbidden
% \usepackage{color (if used in text)
% \usepackage{CJK} -- This package is specifically forbidden
% \usepackage{float} -- This package is specifically forbidden
% \usepackage{flushend} -- This package is specifically forbidden
% \usepackage{fontenc} -- This package is specifically forbidden
% \usepackage{fullpage} -- This package is specifically forbidden
% \usepackage{geometry} -- This package is specifically forbidden
% \usepackage{grffile} -- This package is specifically forbidden
% \usepackage{hyperref} -- This package is specifically forbidden
% \usepackage{navigator} -- This package is specifically forbidden
% (or any other package that embeds links such as navigator or hyperref)
% \indentfirst} -- This package is specifically forbidden
% \layout} -- This package is specifically forbidden
% \multicol} -- This package is specifically forbidden
% \nameref} -- This package is specifically forbidden
% \usepackage{savetrees} -- This package is specifically forbidden
% \usepackage{setspace} -- This package is specifically forbidden
% \usepackage{stfloats} -- This package is specifically forbidden
% \usepackage{tabu} -- This package is specifically forbidden
% \usepackage{titlesec} -- This package is specifically forbidden
% \usepackage{tocbibind} -- This package is specifically forbidden
% \usepackage{ulem} -- This package is specifically forbidden
% \usepackage{wrapfig} -- This package is specifically forbidden
% DISALLOWED COMMANDS
% \nocopyright -- Your paper will not be published if you use this command
% \addtolength -- This command may not be used
% \balance -- This command may not be used
% \baselinestretch -- Your paper will not be published if you use this command
% \clearpage -- No page breaks of any kind may be used for the final version of your paper
% \columnsep -- This command may not be used
% \newpage -- No page breaks of any kind may be used for the final version of your paper
% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
% \pagestyle -- This command may not be used
% \tiny -- This is not an acceptable font size.
% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

% The file aaai22.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

% Title

% Your title must be in mixed case, not sentence case.
% That means all verbs (including short verbs like be, is, using,and go),
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash
\title{Hybrid Recurrent Model With External Weak Signals}
\author{
    %Authors
    % All authors must be in the same font size and format.
    Etienne David,\textsuperscript{\rm 1,\rm 2}\\
    Jean Bellot,\textsuperscript{\rm 1}\\
    Sylvain Le Corff\textsuperscript{\rm 2}\\
}
\affiliations{
    %Afiliations
    \textsuperscript{\rm 1}Heuritech, Paris\\
    \textsuperscript{\rm 2}Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC, Institut Polytechnique de Paris, Palaiseau
    % If you have multiple authors and multiple affiliations
    % use superscripts in text and roman font to identify them.
    % For example,

    % Sunil Issar, \textsuperscript{\rm 2}
    % J. Scott Penberthy, \textsuperscript{\rm 3}
    % George Ferguson,\textsuperscript{\rm 4}
    % Hans Guesgen, \textsuperscript{\rm 5}.
    % Note that the comma should be placed BEFORE the superscript for optimum readability

    %2275 East Bayshore Road, Suite 160\\
    %Palo Alto, California 94303\\
    % email address must be in roman text type, not monospace or sans serif
    etienne.david@heuritech.com, jean.bellot@heuritech.com, sylvain.le$\_$corff@telecom-sudparis.eu
%
% See more examples next
}

%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\iffalse
\title{My Publication Title --- Single Author}
\author {
    Author Name
}
\affiliations{
    Affiliation\\
    Affiliation Line 2\\
    name@example.com
}
\fi

\iffalse
%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\title{My Publication Title --- Multiple Authors}
\author {
    % Authors
    First Author Name,\textsuperscript{\rm 1}
    Second Author Name, \textsuperscript{\rm 2}
    Third Author Name \textsuperscript{\rm 1}
}
\affiliations {
    % Affiliations
    \textsuperscript{\rm 1} Affiliation 1\\
    \textsuperscript{\rm 2} Affiliation 2\\
    firstAuthor@affiliation1.com, secondAuthor@affilation2.com, thirdAuthor@affiliation1.com
}
\fi

% REMOVE THIS: bibentry
% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
\usepackage{bibentry}
% END REMOVE bibentry

\newcommand{\ts}{y}
\newcommand{\fullts}{{\bf \ts}}
\newcommand{\tspred}{\hat{\ts}}
\newcommand{\lvl}{\hat{l}}
\newcommand{\fulllvl}{{\bf \lvl}}
\newcommand{\seas}{\hat{s}}
\newcommand{\fullseas}{{\bf \seas}}
\newcommand{\lsmooth}{\alpha}
\newcommand{\ssmooth}{\beta}
\newcommand{\lag}{h}
\newcommand{\window}{w}
\newcommand{\etspred}{\hat{y}}
\newcommand{\fulletspred}{{\bf \etspred}}
\newcommand{\tswindow}{{\bf \ts}}
\newcommand{\meants}{\Bar{\ts}}
\newcommand{\rnnwindow}{{\bf \rnn}}
\newcommand{\rnn}{z}
\newcommand{\err}{err}
\newcommand{\errwindow}{{\bf \err}}
\newcommand{\rnnmodel}{\textsc{rnn}}
\newcommand{\etsmodel}{\textsc{ets(n,n,a)}}
\newcommand{\ws}{w}
\newcommand{\fullws}{{\bf \ws}}
\newcommand{\wswindow}{{\bf \ws}}
\newcommand{\concatinput}{x}
\newcommand{\fullconcatinput}{{ \bf \concatinput}}
\newcommand{\numberts}{14000}

\begin{document}

\maketitle

\begin{abstract}
Developing models and algorithms to draw causal inference for time series is a long standing statistical problem. It is crucial for many applications, in particular for fashion or retail industries, to make optimal inventory decision and avoid massive wastes. By tracking thousands of fashion trends on social media with stat-of-the-art computer vision approaches, we propose in this paper, the first study of fashion time series forecasting. Our contribution is  twofold. We first provide the first fashion dataset gathering \numberts\ weekly fashion time series. As influence dynamics are the key of emerging trend detection, we associate with each time series several external weak signals representing behaviors of influencers towards the trend. Secondly, to leverage such a complex and rich dataset, we propose a new hybrid forecasting model. Our approach combines per-time-series parametric models with seasonal components and a global recurrent neural network to include sporadic external signals. This hybrid model provides state-of-the-art results on the fashion dataset, and illustrates the benefit of the contribution of  external weak signals.
\end{abstract}

\section{Introduction}

Multivariate time series forecasting is a widespread statistical problem with  many applications, see for instance \citep{sarkka2013bayesian, douc2014nonlinear, zucchini2017hidden} and the numerous references therein.
 %Due to the diversity of applications and use cases, a multitude of models have been proposed. 
 Parametric generative models allow to provide explainable predictions with statistical guarantees based on a precise modeling of the predictive distributions of new data based on a record of past observations. %The parameters of these models are usually estimated using a sequence of observations of the target time series. 
Calibrating these models, for instance using maximum likelihood inference, often requires a fair amount of tuning to design a time series-specific model to provide  accurate forecasts and sharp confidence intervals.  Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.  The exponential smoothing model \citep{RePEc:inm:oropre:v:9:y:1961:i:5:p:673-685} or the ARIMA with the Box-Jenkins approach \citep{box2015time} are for instance very popular parametric linear generative models.  Hidden Markov models (HMM) are also widespread and presuppose that available observations are defined using missing data, possibly lying in a high dimensional state space, describing the dynamical system. This hidden state is assumed to be a Markov chain such that at each time step the received observation is a random function of the corresponding latent data.  Although hidden states are modeled as a Markov chain (or a mixing process)  the observations arising therefrom present a highly complex statistical structure. %Introducing latent hidden states, they assume that the predictive distribution is not unique and constant in time but multiple and lead by the values of the hidden states changing during time. 
 In various applications where signals exhibit non-stationarities such as trends and seasonality, classical HMM are not adapted. However, \citep{touron2017modeling}  recently proposed seasonal HMM, assuming that transition probabilities between the states, as well as the emission distributions, are not constant in time but evolve in a periodic manner. Strong consistency results were established in \citep{touron2019consistency} and Expectation Maximization based numerical experiments were proposed.
Altough thes works provide promising results, HMM are computationally expensive to train and are not yet well studied for sequences with thousands of components with a seasonal behavior.

 %However, for a large part of applications, parametric generative approaches show limitation to capture  complexity. Accurate candidates can be found with latent data models.

%During the past decades, forecasting applications have taken a totally new proportion. 
In many fields, single or few time series have become thousands of sequences with complex statistical structures. In this new context, classical time series specific statistical models show limitations when dealing with numerous heterogeneous data. Recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \citep{ hochreiter1997long,vaswani2017attention, salinas2020deepar, li2019enhancing, lim2019temporal}. %In the past decades, with the impressive results of deep neural networks (DNN) in vision or language, some time series forecasting applications have been proposed. 
Significant improvements have been achieved with Reccurent Neural Network and its Long Short-Term Memory (LSTM) or Gated Recurrent Unit (GRU)  declinations \citep{8614252}. 
A good example is the DeepAR model \citep{salinas2020deepar}. Based on a LSTM architecture, it can predict accurate probability distributions of the future of a sequence. More recently, applications using the Transformer model have been proposed  \citep{li2019enhancing}. A direct concurrent of the DeepAR model can be found with the Temporal Fusion Transformers (TFT) approach \citep{lim2019temporal}.  Unfortunately, they suffer from two main weaknesses. Firstly, many of them are "black-boxes"  as the final forecast usually does not come with a statistical guarantee  although a few recent works focused on measuring uncertainty in recurrent neural networks, see  \cite{martin2020monte}. Secondly, without a fine prepossessing and well chosen hyper-parameters, these methods could lead to poor results and are often outperformed by traditional statistical parametric models, see \cite{makridakis2018m4}.

In this paper, we consider  new time series forecasting application referred to as {\em fashion trends prediction}. Based on a cutting-edge image recognition technology, we built the first fashion dataset containing \numberts\ sequences representing the apparition of fashion trends on social media per week from 01-01-2015 to 01-01-2019. Our fashion time series has very appealing properties: they have all the same length, same seasonality, no missing value and the absence of sparse time series even for niche trends. The originality of our dataset come from the fact that additional external weak signals can be introduced. With our fashion expertise, we detected several groups of fashion users with a high influence power. Analysing their specific behaviours on social medias, we add to each time series, 4 external weak signals representing the same fashion trends but on a sub-category of users. We call them weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal. With this totally new application, we aim at showing a model able to deal with our large fashion dataset, leverage our complex external weak signals and finally provide the most accurate forecasts.

Recurrent neural network seems to be the perfect candidate to tackle our forecasting problem due to their capability of leveraging external data.  Recently, hybrid models combining DNN architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \citep{zhang2003time,jianwei2019novel,bandara2020lstm}. The approach providing the most striking results was proposed in  \citep{smyl2020hybrid} in the context of the M4 forecasting competition \citep{makridakis2020m4}.  Given a large dataset, a per-time-series multiplicative exponential smoothing model is introduced to estimate simple but fundamental components for each time series and compute a first prediction. Then a global recurrent neural network is trained on the entire dataset to correct errors of the previous exponential smoothing models. %With this process, the hybrid approach succeeds at mixing strengths of both model families: robustness of the time series specific parametric models and the power of neural network at learn complex dynamics on large dataset. 
However, the hybrid model has not been designed to deal with external signals even if it include a neural network.

Following this work, we present in this paper a new hyrbid recurrent model for time series forecasting with inclusion of external weak signals. %We design a more general hybrid framework including the original multiplicative model and a new additive one. 
Our approach enriches existing hybrd models  by incorporating an unobserved regime switching feature to account for the need neural network based correction. In order to leverage external signals, we modify the hybrid framework to allow the regime shift and the  global error-corrector neural network to deal with external data. By adding our fashion external weak signals in our proposed framework, we show the real potential of the hybrid approach: a global neural network, able to leverage large amount of data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of the parametric models.

The paper is organized as follow. Section~\ref{sec:hybrid} describes our hybrid framework which consists of an exponential smoothing model and a recurrent neural network combining the target sequences with external weak signals. Then, we present our new fashion dataset in Section~\ref{sec:dataset}. Section~\ref{sec:exp} describes our results and comparisons with several benchmarks. Finally, we conclude our paper and detail research perspectives in Section~\ref{sec:discussion}.

\section{Hybrid model with external signals}
\label{sec:hybrid}
We introduce a new hybrid approach for time series forecasting  composed of two parts: an additive exponential smoothing (ETS) per time series and a global RNN. We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network. Then, we use a recurrent neural network and weak signals to correct the predictions provided by the ETS.

Consider $N\geqslant 1$ time series. For all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$, let $\ts_t^n$ be the value of the $n$-th sequence at time $t$ and  $\fullts^n = \{\ts_t^n\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.   The objective of this paper is to propose a model to  forecast all time series in a given time frame  $\lag \in \mathbb{N}$, i.e. we aim at sampling $\{\ts^n_{t+1:t+\lag}\}_{1\leqslant n \leqslant N}$ based on $\{\ts^n_{1:t}\}_{1\leqslant n \leqslant N}$.

%It is assumed that for all $1\leqslant n \leqslant N$, $\fullts^n$ is a seasonal time series with a season equal to $m \in \mathbb{N}$, $m$ equals 4 for quarterly, 12 for monthly or 52 for weekly time series. However, no restriction in term of scale and noise distributions are assumed in the generative law of each time series.

\subsection{Per time series statistical model}
%The first step in our additive hybrid model is to consider, for each time series, an exponential smoothing  statistical model.
The time-series-specific models compute, for each sequence, two components,  level  and  seasonality. For all $1\leqslant n \leqslant N$ and $0\leqslant t \leqslant T$, let $\lvl_t^n$ be the value of the $n$-th level component at time $t$ and  $\fulllvl^n = \{\lvl_t^n\}_{0\leqslant t \leqslant T}$ be all the values of this level component. For all $1\leqslant n \leqslant N$ and $-m+1\leqslant t \leqslant T$, let $\seas_t^n$ be the value of the $n$-th seasonality component at time $t$ and  $\fullseas^n = \{\seas_t^n\}_{-m+1\leqslant t \leqslant T}$ be all the values of this season component. $m \in \mathbb{N}$ is the seasonality length (4 for quarterly, 12 for monthly or 52 for weekly time series). Given the sequence $\fullts^n$, the two components  $\fulllvl^n$ and $\fullseas^n$ are computed using exponential smoothing.
For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n,\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms. We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
\begin{align*}
    \lvl^n_{t} &= \lsmooth^n (\ts^n_t - \seas^n_{t-m}) + (1- \lsmooth^n)\lvl^n_{t-1}\,, \\
    \seas^n_t &= \ssmooth^n (\ts^n_t - \lvl^n_{t-1}) + (1 - \ssmooth^n)\seas^n_{t-1}\,. 
\end{align*}

For all $n \in \{1,\ldots,N\}$, given the level component $\fulllvl^n$, the seasonality component $\fullseas^n$ and the forecast horizon $\lag \in \mathbb{N}$, the exponential smoothing forecast $\{\etspred^{ets,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ is, for all $i \in \{1,\ldots,\lag\}$,
$$
\etspred^{ets,n}_{T+i|T} = \lvl^n_T + \seas^n_{T+i-m(k+1)}\,,
$$
where $k = \lfloor(i-1)/m\rfloor$.

%For this first stage, we decided to use an additive exponential smoothing for many reasons: firstly, it is easily understandable and it is pretty robust for any kind of sequences.

This statistical model offers a fine approach to normalize and deseasonnalize the sequences. In addition, with its two recurrent equations only, it is simple to code and incorporate in a larger framework using deep learning model and GPUs. However, other statistical methods could have been used as the basis of our hybrid approach. For example, S. Smyl created his hybrid model with a multiplicative exponential smoothing model instead of the additive form. At the end, The main complexity is in the next stage: succeed in training a global RNN to understand all the per-time-series statistical models and correct their mistakes.

\subsection{Error-corrector recurrent model}

The Second stage of our hybrid model is to train a global RNN on all our sequences. its goal is not to compute directly a forecast for each time series but to compute a correction of the first statistical prediction. We motivate this choice for two reasons. Firstly, pure machine learning methods achieve relatively poor results in time series forecasting. Turning a full forecasting task into a correcting task largely simplifies the RNN goals. Secondly, neural network needs a thorough data pre-processing and classical pre-processing methods are not really suited for time-series. With our collection of exponential smoothing models, we find a fine way to normalize and deseasonalize the RNN's inputs and outputs. We describe bellow how we design a RNN able to understand the first exponential smoothing models and estimate a correction of their forecasting errors.

Let $\window \in \mathbb{N}$ be the size of our window, usually this input window is equal to the forecast horizon $\window = \lag$. Consider the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnn^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$, 
$$
\rnn^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} - \lvl^n_T - \seas^n_{T-w+i}}{\meants^n_T}\,, \quad \mathrm{where}\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}  \ts^n_{T-w+i}\,.
$$

This new input is used to correct the exponential smoothing prediction.
Write, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,H\}$, $\err^{n,T}_{T+i|T} = \ts^n_{T+i} - \etspred^{ets,n}_{T+i|T}$. 
Consider then a recurrent neural network denoted by RNN which aims at predicting the exponential smoothing error. Given $\rnnwindow^n_T$, the output of this neural network is, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$,
$$
\rnnmodel(\rnnwindow^n_T)_{T+i} = \frac{\hat{\err}^{n,T}_{T+i|T}}{\meants^n_T}
$$
Finally, for all $1\leqslant n \leqslant N$, the  final forecast of the model is $\{\tspred^{n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$, where, for all $i \in \{1,\ldots,\lag\}$ :
\begin{align*}
\tspred^n_{T+i|T}  = \etspred^{ets,n}_{T+i|T} +  \meants^n_T\times \rnnmodel(\rnnwindow^n_T)_{T+i}  &= \lvl^n_T + \seas^n_{T+i-m(k+1)} + \hat{\err}^{n,T}_{T+i|T}\,.
\end{align*}

\subsection{Weak signal}

Using a time-series-specific statistical model, the hybrid network achieves striking accuracy on single sequences. Then, the shared recurrent neural network relies on the strength of machine learning methods at leveraging a huge quantities of heterogeneous data.
In addition to the $N$ target time series, we consider $K \times N$ external sequences indexed from $0$ to $T$. For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ linked to the sequence $\fullts^n$. We note $\fullws^n = \{\{\ws_t^{n,k}\}_{1\leqslant t \leqslant T}\}_{1\leqslant k \leqslant K}$ all the values of the family of weak signals linked to the $n$-th sequence. In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the family. Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for our RNN,   $$\fullconcatinput^n_T = \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w} = \{\rnn^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}$$
Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ our final forecast $\{\tspred^{n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ become :

$$
\tspred^n_{T+i|T} 
= \etspred^{ets,n}_{T+i|T} +  \rnnmodel(\fullconcatinput^n_T)_{T+i} \times \meants^n_T
$$

\begin{figure}
  \centering
    \includegraphics[width=0.8\linewidth]{figure/hybrid_model_archi.png}
  \caption{Hybrid model with weak signals architecture}
\end{figure}

\section{Fashion dataset with external weak signals}
\label{sec:dataset}
In image of language processing, there are available reference datasets covering varieties of applications. However, for time series forecasting, there is a lack of large, rich and public datasets where neural network approaches can express their potential. With the M4 and M5 competitions, we can find large amounts of data but they show several limitation. For example the M4 dataset does not propose external signals in addition to the time series. Conversely, the M5 one does so but like other sales datasets \citep{C.Favorita}, it includes a majority of sporadic time series that do not allow the application of some kinds of models\citep{makridakis2020m5}. With this paper, we aim at widening the set of available datasets for time series forecasting with the first fashion dataset including external weak signals.

Heuritech is the first company to adopt a data-intensive approach  for the fashion forecasting. It analyzes every day images shared on social networks thanks to a high throughput computer vision systems. Aggregating detected clothes by trends, we create thousands of time series with the same good properties: same weekly seasonality, shared behaviours and the same length: from 2015-01-05 to 2020-09-01. Each time series is normalized in order to remove social networks biases and their values lie between 0 and 1. The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones. An overview of it can be found in table 1.

\begin{table}
  \caption{Fashion time series overview. For each couple geozone/category, we give the number of female and male trends (Female/Male)}
  \label{sample-table}
  \centering
  \resizebox{\textwidth}{!}{
  \begin{tabular}{lllllllllll}
    \toprule
    &  Top  & Pants & Short & Skirt & Dress & Coat & Shoes & Color & Texture &  \\
    \midrule
     United States & 587/290 & 195/158  & 64/37 & 38/- & 38/- & 271/218 & 439/114 & 59/59 & 129/103\\
     Europe & 587/290 &  195/158& 64/37 & 38/- & 38/- & 271/218 & 439/114 & 59/59 & 135/111\\
     Japan &  587/290 & 193/158 & 64/37 & 38/- &  37/- & 271/218 &  429/114 & 59/59 &  124/98\\
     China &  586/290 & 195/158 & 64/37 & 38/- &  37/- & 271/218 &  433/114 & 59/59 &  128/113\\
     Brazil &  587/290 & 195/158 & 64/37 & 38/- &  38/- & 271/218 & 439/114 & 59/59 & 136/110\\
     \midrule
     Total & 2934/1450 & 973/790 & 320/185 & 190/- & 188/- & 1355/1090 & 2179/570 & 295/294 & 652/535 & \numberts\\
    \bottomrule
  \end{tabular}
  }
\end{table}

In addition to this large dataset we design for each sequence several weak signals :
\begin{itemize}
    \item Firstly, we create a specific fashion-oriented panel of micro-influencers. In theoretical fashion dynamics \citep{rogersdiffusion}, different categories of adopters adopt a trend in succession, resulting in several adoption waves. With this specific panel, we aim at detecting the first waves announcing emerging trends or the collapse of other ones. By analyzing images shared by this specific panel on social medias, we create a first weak signal named \textit{fashion-forwards} for each of the previous trends.
    \item for the other weak signals, we analyzed only a specific part of social media users depending of the number of followers. With three thresholds we create the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high}. The first one represents users with few followers, the second one is made of users with a moderate amount of followers and the last one gathers superstar and users of any fields with thousands of influencers. Again, the motivation here is to detect behaviour gaps between this three segments that could announce bigger changes in the main signal.
\end{itemize}

At the end, we have for each trends 4 linked weak signals representing this trends on a specific panel of social media users. These extra signals are frequently sparse for micro trends and they often lack of interest for common fashion trends. However on several examples, they are fundamental to detect the future fashion evolution.

As an example, an impressive emerging fashion trend is represented in figure 2. The graph shows the evolution of one of our shoes trends on social media and its linked \textit{fashion-forward} weak signal. During the first 3 years, common users and our panel of mode-influencers share the same behaviour. The trend start to boom in the mainstream people during the first month of 2018. However, we can detect early signals in the fashion-forward panel at the end of 2017. Early adopters started to change there behaviour and show more frequently the trend on social media. With fashion influence dynamics, the new tendency spreads to every part of social media users and more generally on the society. Finally, after a pick reached at the end of 2018 for our fashion-influencers, a regular decrease appear. They leave gradually the old trend to focus more on the latest or propose new ones.

\begin{figure}
  \centering
    \includegraphics[width=1.\linewidth]{figure/good_example.png}
  \caption{A shoes trend of our dataset. In black the main signal and in red its associated \textit{fashion-forward} weak signal. The Gap between our two signals in the end of 2017/beginning of 2018 announces the future explosion of the fashion trend.}
\end{figure}

\section{Experimental results}
\label{sec:exp}
In this section, we evaluate how our hybrid framework is able to deal with the fashion dataset and leverage our complex external weak signals. To lead our experience, we keep hide the last year of each time series as our test set. For each method and each time series, based on the first five years of data, we predict the last year and compute our accuracy on it.

\subsection{Training}

To train our hybrid models, we made the choice of don't using the original code of the hybrid method provided during the M4 competition. Indeed, the proposed implementation is difficult to use in a more general framework and it is quite slow because it doesn't enable the use of GPU. Thereby, we propose with this paper, a new version of the hybrid framework, including the original multiplicative model and the new additive one. Our proposed code is developed in Python using the Tensorflow library and it allows the use of a GPU to speed up the training process.

In addition to a more general framework, we add the possibility of doing inference with our new implementation. We design a new process to compute and provide a forecast for a totally  new collection of sequences without retraining the entire hybrid model. Given a new time series, we freeze the weights of the error-corrector recurrent model and we only train the new time-series-specific statistical model linked to the new sequence. It remains the responsibility of the users to provide new sequences sharing same behaviours than the dataset using for the training to keep the same accuracy level.

For more details about the general hybrid training, a complete description of the training process can be found in the M4 hybrid model paper or in an interesting application of the method on electric load forecasting, see \citep{dudek2020hybrid}.

\subsection{Benchmarks, hybrid models and Metrics}

As benchmarks, we chose several well-known statistical methods and a full Machine Learning (ML) model. For the statistical part, using the R package "forecast", we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}. \textit{Snaive} forecasts are only the repetition of the last same past period. \textit{stlm} approach use a multiplicative decomposition and models the seasonality adjusted time series with an exponenantial smoothing model. \textit{Thetam} model decompose the original signal in $\theta$-lines, forecast each one separately and recompose them to produce the final forecast. \textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization. The last one \textit{auto.arima} is the R implementation of ARIMA model with an automatic selection of the best parameters. For the full ML method, we train a global Long-Short Term Memory (\textit{lstm}) neural network on all our dataset (\textcolor{green}{ ici j'ai entrainé un lstm simple sans appliquer aucun preprocessing. Ses résultats sont dans la table 2/3 et ils sont  déjà très corrects. Si j'applique en plus une normalisation, le lstm simple devient aussi bon que nos méthodes hybrides. --> creuser pourquoi}. Against these models, we propose two versions of the hybrid approach without the external weak signal. The first one is the original multiplicative form of the hybrid model that we name \textit{hybrid-mul}. The second one is the additive variant described in Section~\ref{sec:hybrid} and we named it \textit{hybrid-add}. To reach a higher accuracy level we propose at the end an ensembling (\textit{ensembling} of our two hybrid approaches using the FFORMA method created during the M4 competition, see \citep{fforma} .

Finally, to evaluate the power of our external signals and the capacity of our hybrid models to leverage them, we propose for our two approaches a version with the external weak signals. We name them respectively \textit{hybrid-mul-ws} for the multiplicative version and \textit{hybrid-add-ws} for the additive one. As benchmarks we propose the same comparison with our previous full ML model \textit{lstm} with a version including weak signals \textit{lstm-ws}.

To compare the different methods, we use the same metrics as in the M4 competition: the Mean Absolute Scaled Error (MASE), the Symmetric Mean Absolute Percentage Error (SMAPE) and the final M4 competition metric, the Overall Weighted Average (OWA) of the SMAPE and the MASE.

$$
MASE = \frac{\frac{1}{h}\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\frac{1}{T-m}\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|} \quad
SMAPE = \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}
$$

$$
OWA = \frac{1}{2}(\frac{MASE}{MASE_{snaive}} + \frac{SMAPE}{SMAPE_{snaive}})
$$

\subsection{Heuritech Fashion dataset results}

In a first place, Table 2 shows the final accuracy of the statistical models, the LSTM model and our 2 hybrid models without external data. Even without the weak signals, our 2 hybrid approaches largely outperform the statistical references. The multiplicative model show the best accuracy with a OWA equal to 0.875. We can note that the additive model slightly under-performs the traditional multiplicative one on average. This doesn't show a weakness of the additive version but more that a large part of our dataset is more-suited for multiplicative modelization. At the end, the strength of training both methods, additive and multiplicative, is in the final porposed ensembling \textit{ensembling} that combines the two approaches with the FForma ensembling.

In a second place, Table 3 shows the evaluation of our 4 trained hybrid models: the 2 previous ones without weak signals, and our 2 full hybrid models with weak signals. We present also the accuracy of a simple LSTM model with and without weak signals. We can show the impressive improvement due to our external signals. Again, the multiplicative method achieves the best accuracy with OWA metric equal to 0.860. We propose like previously, an ensembling mixing our two full hybrid models with weak signals and it reach the high level of accuracy with an OWA equal to 0.849.

In a third place, table 4 presents the result of our inference process. We split our dataset in five equal parts of 2800 sequences and hide the last year for each trends. Then, like a cross validation, we train a model on 4 parts and compute its accuracy on the last one on the last year. The model never saw the last part so we use our inference process to compute predictions. With a permutation of the parts, we can repeat the process and train 5 models, each trained on a specific pool of 4 parts and tested on the remaining part of the dataset. For each hybrid model (additive/multiplicative with and without weak signals) Table 4 shows the average accuracy and the Standard Deviation of the 5 trained hybrid models. We can see that our inference process achieve really accurate results and practically the same that our hybrid models trained on the entire dataset. These results prove that, even without having seen a sequence during the training, if the time series share same behaviours that the training sample, our hybrid approaches can perfectly compute accurate predictions. Furthermore, the Standard Deviation is really low for all our metrics. This result shows that our hybrid framework is robust and reach constant accuracy level on large dataset.

Finally, with our results, we can make two interesting conclusions: 
\begin{itemize}
    \item Firstly, the hybird modeling is a really promising framework. By mixing the performance of local parametric models and a global DNN, our two versions clearly outperform traditional statistical methods. Furthermore, this framework is totally suited for dealing with external signals. With a fine pre-processing and a well-designed architecture, our two models succeed at leveraging our complex extra data and reach an impressive accuracy levels.
    \item Secondly, our results bring to light the quality of our new Fashion dataset. Even without weak signal, our DNN based model outperforms time series specific model. This show that our dataset is well suited to train complex neural network architectures able to learn information cross sequences. With the addition of our weak signals, we give a totally new dimension to our fashion dataset. Our results show that our external weak signals hide a complex but usable predictive power by DNN architecture. By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting.
\end{itemize}

\subsection{Discussion}

\begin{table}
  \caption{Results summary (Mean/Median) on our Fashion dataset. In a first time, we train our hybrid approaches without our external weak signals.}
  \label{sample-table}
  \centering
  \begin{tabular}{lllllll}
    \toprule
    &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std  \\
    \midrule
     snaive & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
     thetam & 0.924/0.869  & 0.35 & 25.82/22.54  & 14.6 & 0.952/0.915 & 0.26\\
     stlm & 0.893/0.834 & 0.35 & 25.07/21.93  & 14.3 & 0.917/0.895 & 0.21\\
     tbats & 0.886/0.822  & 0.34 &  24.81/21.60 & 14.0 &  0.910/0.882 & 0.22 \\
     lstm & 0.881/0.824 & 0.34 & 24.41/21.56 & 12.81 & 0.895/0.885 & 0.11 \\
     hybrid-add & 0.863/0.812  & 0.32 & 24.17/21.36 & 13.0 & 0.877/0.880 & 0.08 \\
     hybrid-mul & 0.858/0.817 & 0.30 & 24.06/21.30 & 13.0 & 0.876/0.873 & 0.11 \\
     Ensembling & 0.846/0.804 & 0.30 & 23.78/21.07 & 12.9 & 0.864/0.863 & 0.10  \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}
  \caption{Comparison between our hybrid models without and with our external weak signals, (Mean/Median)}
  \label{sample-table}
  \centering
  \begin{tabular}{lllllll}
    \toprule
    &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std \\
    \midrule
    lstm & 0.881/0.824 & 0.34 & 24.41/21.56 & 12.81 & 0.895/0.885 & 0.11 \\
    lstm-ws & 0.869/0.814 & 0.33 & 24.56/21.33 & 14.40 & 0.890/0.874 & 0.132 \\
     hybrid-add & 0.863/0.812  & 0.32 & 24.17/21.36 & 13.0 & 0.877/0.880 & 0.08 \\
     hybrid-mul & 0.858/0.817 & 0.30 & 24.06/21.30 & 13.0 & 0.876/0.873 & 0.11 \\
     hybrid-add-ws & 0.852/0.807 & 0.30 & 24.03/21.17 & 13.0 & 0.872/0.869 & 0.10 \\
     hybrid-mul-ws & 0.836/0.798 & 0.29 & 23.67/20.87 & 12.9 & 0.860/0.858 & 0.12 \\
     Ensembling & 0.827/0.787 & 0.29 & 23.43/20.63 & 12.8 & 0.849/0.849 & 0.11\\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}
  \caption{Cross-Validation. we split our dataset in 5 equal parts. We train for each hybrid approach, 5 models on 4 specific parts of the dataset and we test them of the remaining parts with our inference process.}
  \label{sample-table}
  \centering
  \begin{tabular}{lllllll}
    \toprule
    &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std \\
    \midrule
     hybrid-add & 0.861  & 0.004 & 24.16 & 0.18 & 0.877 & 0.002 \\
     hybrid-mul & 0.856 & 0.008 & 23.95 & 0.25 & 0.870 & 0.005 \\
     hybrid-add-ws & 0.848 & 0.004 & 24.00 & 0.18 & 0.869 & 0.002 \\
     hybrid-mul-ws & 0.844 & 0.010 & 23.74 & .20 & 0.863 & 0.006 \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Conclusion}
\label{sec:discussion}
In this paper, we propose the first hybrid model including external weak signals for time series forecasting. We show that hybrid framework is a really promising way. With its extended error-corrector DNN part, it is clearly well-suited for dealing with any kind of external signals in order to correct weaknesses of first parametric models. Furthermore, With our additive version, we show that the hybrid model is not frozen in it original form. Thereby, future research explorations would be to improve its framework with new per-time-series approaches and test new error-corrector DNN part like the recent Transformer model.

With this first contribution, we join the first fashion dataset gathering \numberts\ mode times series and a complex collection of extra signals. We believe that this dataset hide really fine dynamics and interactions where complex models would express their potential. By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting and pave the way for further explorations.

\bibliography{aaai22.bib}

\section{Appendices}

\subsection{Further training details}
\label{section:train_details}

\end{document}

### 2021-08-07 hybridmodel.tex
Added Bernoulli shift

@@
 \usepackage{booktabs}
+\usepackage{xcolor}
 
@@
 
-\subsection{Error-corrector recurrent model}
+\subsection{Regime switching error-corrector recurrent model}
 
-The Second stage of our hybrid model is to train a global RNN on all our sequences.
-its goal is not to compute directly a forecast for each time series but to compute a correction of the first statistical prediction.
+Then we train a global RNN on all sequences to compute a correction of the first statistical prediction.
 We motivate this choice for two reasons.
@@
 Secondly, neural network needs a thorough data pre-processing and classical pre-processing methods are not really suited for time-series.
-With our collection of exponential smoothing models, we find a fine way to normalize and deseasonalize the RNN's inputs and outputs.
-We describe bellow how we design a RNN able to understand the first exponential smoothing models and estimate a correction of their forecasting errors.
+With our collection of exponential smoothing models, we propose a fine way to normalize and deseasonalize the RNN inputs and outputs.
+%We describe bellow how we design a RNN able to understand the first exponential smoothing models and estimate a correction of their forecasting errors.
 
-Let $\window \in \mathbb{N}$ be the size of our window, usually this input window is equal to the forecast horizon $\window = \lag$.
+Let $\window \in \mathbb{N}$ be the window size, usually this input window is equal to the forecast horizon $\window = \lag$.
 Consider the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnn^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$,
 $$
-\rnn^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} - \lvl^n_T - \seas^n_{T-w+i}}{\meants^n_T}\,, \quad \mathrm{where}\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}  \ts^n_{T-w+i}\,.
+\rnn^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} - \lvl^n_T - \seas^n_{T-w+i}}{\meants^n_T}\,,
 $$
-
+where $ \meants^n_T = \sum_{i = 1}^{w}  \ts^n_{T-w+i}/w$.
 This new input is used to correct the exponential smoothing prediction.
-Write, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,H\}$, $\err^{n,T}_{T+i|T} = \ts^n_{T+i} - \etspred^{ets,n}_{T+i|T}$. 
+%Write, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,H\}$, $\err^{n,T}_{T+i|T} = \ts^n_{T+i} - \etspred^{ets,n}_{T+i|T}$.
 Consider then a recurrent neural network denoted by RNN which aims at predicting the exponential smoothing error.
-Given $\rnnwindow^n_T$, the output of this neural network is, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$,
+Given $\rnnwindow^n_T$, the proposed model is given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by
 $$
-\rnnmodel(\rnnwindow^n_T)_{T+i} = \frac{\hat{\err}^{n,T}_{T+i|T}}{\meants^n_T}
+\ts^n_{T+i}  = \etspred^{ets,n}_{T+i|T} +  U^n_T\times\meants^n_T\times \rnnmodel(\rnnwindow^n_T)_{T+i} + \varepsilon^n_{T+i}\,,%\\
+%  &= \lvl^n_T + \seas^n_{T+i-m(k+1)} +  U^n_T\times\meants^n_T\times \rnnmodel(\rnnwindow^n_T)_{T+i} + \varepsilon^n_{T+i}\,,
 $$
-Finally, for all $1\leqslant n \leqslant N$, the  final forecast of the model is $\{\tspred^{n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$, where, for all $i \in \{1,\ldots,\lag\}$ :
-\begin{align*}
-\tspred^n_{T+i|T}  = \etspred^{ets,n}_{T+i|T} +  \meants^n_T\times \rnnmodel(\rnnwindow^n_T)_{T+i}  &= \lvl^n_T + \seas^n_{T+i-m(k+1)} + \hat{\err}^{n,T}_{T+i|T}\,.
-\end{align*}
+where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent random variables with \textcolor{red}{specify here the right distribution} and $ U^n_T$ an unobserved regime switching Bernoulli random variable.
+%$$
+%\ts^n_{T+i} = \rnnmodel(\rnnwindow^n_T)_{T+i} = \frac{\hat{\err}^{n,T}_{T+i|T}}{\meants^n_T}
+%$$
+%Finally, for all $1\leqslant n \leqslant N$, the  final forecast of the model is $\{\tspred^{n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$, where, for all $i \in \{1,\ldots,\lag\}$ :
+%\begin{align*}
+%\tspred^n_{T+i|T}  &= \etspred^{ets,n}_{T+i|T} +  \meants^n_T\times \rnnmodel(\rnnwindow^n_T)_{T+i}\,,\\
+%  &= \lvl^n_T + \seas^n_{T+i-m(k+1)} + \hat{\err}^{n,T}_{T+i|T}\,.
+%\end{align*}
 
@@
 In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the family.
-Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for our RNN,   $$\fullconcatinput^n_T = \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w} = \{\rnn^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}$$
-Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ our final forecast $\{\tspred^{n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ become :
-
+Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for our RNN,
+\begin{align*}
+\fullconcatinput^n_T &= \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}\,, \\
+&= \{\rnn^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
+\end{align*}
+Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ our final forecast $\{\tspred^{n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ become:
 $$
@@
 
-\begin{table}
+\begin{table*}
   \caption{Fashion time series overview. For each couple geozone/category, we give the number of female and male trends (Female/Male)}
@@
   }
-\end{table}
+\end{table*}
 
@@
 The last one \textit{auto.arima} is the R implementation of ARIMA model with an automatic selection of the best parameters.
-For the full ML method, we train a global Long-Short Term Memory (\textit{lstm}) neural network on all our dataset (\textcolor{green}{ ici j'ai entrainé un lstm simple sans appliquer aucun preprocessing.
-Ses résultats sont dans la table 2/3 et ils sont  déjà très corrects.
-Si j'applique en plus une normalisation, le lstm simple devient aussi bon que nos méthodes hybrides.
---> creuser pourquoi}.
+For the full ML method, we train a global Long-Short Term Memory (\textit{lstm}) neural network on all our dataset.
 Against these models, we propose two versions of the hybrid approach without the external weak signal.
@@
 
-\begin{table}
+\begin{table*}
   \caption{Results summary (Mean/Median) on our Fashion dataset. In a first time, we train our hybrid approaches without our external weak signals.}
@@
   \end{tabular}
-\end{table}
+\end{table*}
 
-\begin{table}
+\begin{table*}
   \caption{Comparison between our hybrid models without and with our external weak signals, (Mean/Median)}
@@
   \end{tabular}
-\end{table}
+\end{table*}
 
-\begin{table}
+\begin{table*}
   \caption{Cross-Validation.
@@
   \end{tabular}
-\end{table}
+\end{table*}
 
@@
 
+\subsection{RNN architecture and baselines}
+\label{section:architectures}
+
 \subsection{Further training details}
@@
 
+\subsection{Details on the Fashion dataset}
+\label{section:dataset_details}
+
 \end{document}

### 2021-08-07 hybridmodel.tex
Added Bernoulli shift in the score function

@@
 $$
-where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent random variables with \textcolor{red}{specify here the right distribution} and $ U^n_T$ an unobserved regime switching Bernoulli random variable.
+where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent random variables with \textcolor{red}{specify here the right distribution} and $U^n_T$ an unobserved regime switching Bernoulli random variable.
+The random variable $U^n_T$ allows to provide RNN corrections only when ETS prediction is not sharp enough \textcolor{red}{Show in appendix cases where ETS alone is enough and cases where correction is required}.
+The law of $U^n_T$ is parameterized by a Feed Forward Neural Network (FFNN) with input \textcolor{red}{complete here}.
 %$$
@@
 \end{align*}
-Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ our final forecast $\{\tspred^{n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ become:
-$$
-\tspred^n_{T+i|T} 
-= \etspred^{ets,n}_{T+i|T} +  \rnnmodel(\fullconcatinput^n_T)_{T+i} \times \meants^n_T
-$$
+Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ our final model becomes:
+%$$
+%\tspred^n_{T+i|T} 
+%= \etspred^{ets,n}_{T+i|T} +  \rnnmodel(\fullconcatinput^n_T)_{T+i} \times \meants^n_T
+%$$
+\begin{equation}
+\label{eq:full:model}
+\ts^n_{T+i}  = \etspred^{ets,n}_{T+i|T} +  U^n_T\times\meants^n_T\times \rnnmodel(\fullconcatinput^n_T)_{T+i} + \varepsilon^n_{T+i}\,,
+\end{equation}
+\textcolor{red}{specify here the right distribution for $U$ (depends on the weak signal or no)}. The complete architecture is displayed in Figure~\ref{fig:architecture}.
 
@@
     \includegraphics[width=0.8\linewidth]{figure/hybrid_model_archi.png}
-  \caption{Hybrid model with weak signals architecture}
+  \caption{Hybrid model with weak signals architecture.}
+\label{fig:architecture}
 \end{figure}
+
+As $U^n_T$ is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
+Therefore we use Fisher's identity to compute the score function and write a gradient ascent algorithm to estimate simultaneously the weights of the RNN and of the FFNN denoted by $\theta$.
+The score is
+\begin{multline*}
+\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T})
+\\ = \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h}\right]\,,
+\end{multline*}
+where the joint likelihood $p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T}) = p_\theta(U_T^n|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$ is given by \eqref{eq:full:model} and the expectation is under the posterior distribution of $U_T^n$ given $\ts^n_{1:T+h}$  \textcolor{red}{details to add in appendix}.
 

### 2021-08-07 hybridmodel.tex
Discussion on the choice of model/loss function

@@
 where the joint likelihood $p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T}) = p_\theta(U_T^n|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$ is given by \eqref{eq:full:model} and the expectation is under the posterior distribution of $U_T^n$ given $\ts^n_{1:T+h}$  \textcolor{red}{details to add in appendix}.
+\textcolor{red}{Assume that $\theta_p$ is the current value for the weights of the FFNN and the RNN and write $\omega_p^n = \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T+h})$.
+Note that
+$$
+\omega_p^n \propto \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T})p_{\theta_p}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\,.
+$$
+Then,
+\begin{multline*}
+\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \omega_p^n\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})\\
++ (1-\omega_p^n)\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,.
+\end{multline*}
+The loss function is then given by
+\begin{multline*}
+\theta\mapsto - \omega_p^n \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})\\
+- (1-\omega_p^n) \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,,
+\end{multline*} 
+where no gradient is computed on $\omega_p^n$.
+In both terms, $\log p_\theta(U_T^n=0|\ts^n_{1:T})$ and $\log p_\theta(U_T^n=0|\ts^n_{1:T})$ are simply given by the output of the FFNN.
+Choices for the model.
+\begin{itemize}
+\item In the case where the  $\varepsilon^n_{T+i}$ are Gaussian and independent, up to an additive constant
+$$
+\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) = -c\sum_{i=1}^{h}(\ts^n_{T+i}  - \etspred^{ets,n}_{T+i|T})^2
+$$
+and
+\begin{multline*}
+\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\\
+ = -c\sum_{i=1}^{h}(\ts^n_{T+i}  - \etspred^{ets,n}_{T+i|T} - \meants^n_T\times \rnnmodel(\fullconcatinput^n_T)_{T+i})^2\,.
+\end{multline*}
+Choice of $c$ ?
+\item In the case where the  $\varepsilon^n_{T+i}$ are Laplace and independent, up to an additive constant
+$$
+\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) = -c\sum_{i=1}^{h}|\ts^n_{T+i}  - \etspred^{ets,n}_{T+i|T}|
+$$
+and
+\begin{multline*}
+\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\\
+ = -c\sum_{i=1}^{h}|\ts^n_{T+i}  - \etspred^{ets,n}_{T+i|T} - \meants^n_T\times \rnnmodel(\fullconcatinput^n_T)_{T+i}|\,.
+\end{multline*}
+Choice of $c$ ?
+\end{itemize}}
 

### 2021-08-08 hybridmodel.tex
Discussion on the choice of model/loss function
A few corrections

@@
 The objective of this paper is to propose a model to  forecast all time series in a given time frame  $\lag \in \mathbb{N}$, i.e.
-we aim at sampling $\{\ts^n_{t+1:t+\lag}\}_{1\leqslant n \leqslant N}$ based on $\{\ts^n_{1:t}\}_{1\leqslant n \leqslant N}$.
+we aim at sampling $\{\ts^n_{T+1:T+\lag}\}_{1\leqslant n \leqslant N}$ based on $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$.
 
@@
 For all $1\leqslant n \leqslant N$ and $-m+1\leqslant t \leqslant T$, let $\seas_t^n$ be the value of the $n$-th seasonality component at time $t$ and  $\fullseas^n = \{\seas_t^n\}_{-m+1\leqslant t \leqslant T}$ be all the values of this season component.
-$m \in \mathbb{N}$ is the seasonality length (4 for quarterly, 12 for monthly or 52 for weekly time series).
+$m \in \mathbb{N}$ is the seasonality (4 for quarterly, 12 for monthly or 52 for weekly time series).
 Given the sequence $\fullts^n$, the two components  $\fulllvl^n$ and $\fullseas^n$ are computed using exponential smoothing.
 For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n,\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms.
-We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
+We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ \textcolor{red}{issue with the time index ?} and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
 \begin{align*}
@@
 
-Then we train a global RNN on all sequences to compute a correction of the first statistical prediction.
-We motivate this choice for two reasons.
+Then, we train a global RNN on all sequences to compute a correction of the initial prediction.
+%We motivate this choice for two reasons.
 Firstly, pure machine learning methods achieve relatively poor results in time series forecasting.
 Turning a full forecasting task into a correcting task largely simplifies the RNN goals.
-Secondly, neural network needs a thorough data pre-processing and classical pre-processing methods are not really suited for time-series.
-With our collection of exponential smoothing models, we propose a fine way to normalize and deseasonalize the RNN inputs and outputs.
+This task requires a thorough data pre-processing and with our collection of exponential smoothing models  we propose a fine way to normalize and deseasonalize the RNN inputs and outputs.
 %We describe bellow how we design a RNN able to understand the first exponential smoothing models and estimate a correction of their forecasting errors.
@@
 
+\subsection{Examples from the dataset}
+\label{section:examples}
+
 \end{document}

### 2021-08-20 hybridmodel.tex
Many corrections throughout the main text

@@
 \end{multline*}
-where the joint likelihood $p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T}) = p_\theta(U_T^n|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$ is given by \eqref{eq:full:model} and the expectation is under the posterior distribution of $U_T^n$ given $\ts^n_{1:T+h}$  \textcolor{red}{details to add in appendix}.
-\textcolor{red}{Assume that $\theta_p$ is the current value for the weights of the FFNN and the RNN and write $\omega_p^n = \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T+h})$.
+where the joint likelihood $p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T}) = p_\theta(U_T^n|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$ is given by \eqref{eq:full:model} and the expectation is under the posterior distribution of $U_T^n$ given $\ts^n_{1:T+h}$.
+\textcolor{red}{details to add in appendix.} \textcolor{red}{Assume that $\theta_p$ is the current value for the weights of the FFNN and the RNN and write $\omega_p^n = \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T+h})$.
 Note that
@@
 \label{sec:dataset}
-In image of language processing, there are available reference datasets covering varieties of applications.
+%In image of language processing, there are available reference datasets covering varieties of applications.
 However, for time series forecasting, there is a lack of large, rich and public datasets where neural network approaches can express their potential.
-With the M4 and M5 competitions, we can find large amounts of data but they show several limitation.
-For example the M4 dataset does not propose external signals in addition to the time series.
-Conversely, the M5 one does so but like other sales datasets \citep{C.Favorita}, it includes a majority of sporadic time series that do not allow the application of some kinds of models\citep{makridakis2020m5}.
-With this paper, we aim at widening the set of available datasets for time series forecasting with the first fashion dataset including external weak signals.
+\textcolor{red}{Other datasets for time series (see Alice paper on the SMC Transformer): air quality, weather, energy, Covid.
+These datasets exist but no easy weak signals to derive from them i guess.
+}
+M4 and M5 competitions\textcolor{red}{Add link in footnote} provide a large amount of time series data but they show several limitations.
+For example, the M4 dataset does not propose external signals in addition to the target time series.
+Conversely, the M5 dataset does include weak signals, but like other sales datasets \citep{C.Favorita}, it includes a majority of sporadic time series that cannot be included straightforwadly in a statistical model, see \citep{makridakis2020m5}.
+With this paper, we aim at overcoming this limitation of available datasets for time series forecasting with the first fashion dataset including external weak signals.
 
-Heuritech is the first company to adopt a data-intensive approach  for the fashion forecasting.
-It analyzes every day images shared on social networks thanks to a high throughput computer vision systems.
-Aggregating detected clothes by trends, we create thousands of time series with the same good properties: same weekly seasonality, shared behaviours and the same length: from 2015-01-05 to 2020-09-01.
+%Heuritech is the first company to adopt a data-intensive approach  for the fashion forecasting. 
+Every day images shared on social networks are analyzed thanks to a high throughput computer vision systems.
+Aggregating detected clothes by trends, we create thousands of time series with the same good properties: same weekly seasonality, shared behaviours and the same length: from 2015-01-05 to 2020-09-01 \textcolor{red}{Add a few details here or in the appendix}.
 Each time series is normalized in order to remove social networks biases and their values lie between 0 and 1.
@@
 
-In addition to this large dataset we design for each sequence several weak signals :
-\begin{itemize}
-    \item Firstly, we create a specific fashion-oriented panel of micro-influencers.
-In theoretical fashion dynamics \citep{rogersdiffusion}, different categories of adopters adopt a trend in succession, resulting in several adoption waves.
+In addition to this large dataset we design for each sequence several weak signals.
+Firstly, we create a specific fashion-oriented panel of micro-influencers.
+In theoretical fashion dynamics \citep{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
 With this specific panel, we aim at detecting the first waves announcing emerging trends or the collapse of other ones.
 By analyzing images shared by this specific panel on social medias, we create a first weak signal named \textit{fashion-forwards} for each of the previous trends.
-    \item for the other weak signals, we analyzed only a specific part of social media users depending of the number of followers.
-With three thresholds we create the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high}.
+We also analyzed only a specific part of social media users depending of the number of followers.
+With three thresholds we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high}.
 The first one represents users with few followers, the second one is made of users with a moderate amount of followers and the last one gathers superstar and users of any fields with thousands of influencers.
 Again, the motivation here is to detect behaviour gaps between this three segments that could announce bigger changes in the main signal.
-\end{itemize}
 
@@
 
-As an example, an impressive emerging fashion trend is represented in figure 2.
-The graph shows the evolution of one of our shoes trends on social media and its linked \textit{fashion-forward} weak signal.
-During the first 3 years, common users and our panel of mode-influencers share the same behaviour.
+As an example, an impressive emerging fashion trend is represented in Figure 2, \textcolor{red}{see other examples in Appendix~\ref{}}.
+It shows the evolution of one shoes trends on social media and its linked \textit{fashion-forward} weak signal.
+During the first 3 years, common users and the panel of mode-influencers share the same behaviour.
 The trend start to boom in the mainstream people during the first month of 2018.
@@
 Early adopters started to change there behaviour and show more frequently the trend on social media.
-With fashion influence dynamics, the new tendency spreads to every part of social media users and more generally on the society.
-Finally, after a pick reached at the end of 2018 for our fashion-influencers, a regular decrease appear.
-They leave gradually the old trend to focus more on the latest or propose new ones.
+With fashion influence dynamics, the new tendency spreads to every part of social media users.
+Finally, after a pick reached at the end of 2018 for the fashion-influencers, a regular decrease appear.
+%They leave gradually the old trend to focus more on the latest or propose new ones.
 
@@
 In black the main signal and in red its associated \textit{fashion-forward} weak signal.
-The Gap between our two signals in the end of 2017/beginning of 2018 announces the future explosion of the fashion trend.}
+The Gap between our two signals in the end of 2017/beginning of 2018 announces the future explosion of the fashion trend.
+\textcolor{red}{Provide other examples in the appendix to hightlight the variety of the proposed data.}}
 \end{figure}
@@
 \label{sec:exp}
-In this section, we evaluate how our hybrid framework is able to deal with the fashion dataset and leverage our complex external weak signals.
+%In this section, we evaluate how our hybrid framework is able to deal with the fashion dataset and leverage our complex external weak signals.
 To lead our experience, we keep hide the last year of each time series as our test set.
@@
 
-To train our hybrid models, we made the choice of don't using the original code of the hybrid method provided during the M4 competition.
+%To train our hybrid models, we made the choice of don't using the original code of the hybrid method provided during the M4 competition.
 Indeed, the proposed implementation is difficult to use in a more general framework and it is quite slow because it doesn't enable the use of GPU.
 Thereby, we propose with this paper, a new version of the hybrid framework, including the original multiplicative model and the new additive one.
-Our proposed code is developed in Python using the Tensorflow library and it allows the use of a GPU to speed up the training process.
+Our code is developed in Python using the Tensorflow library and it allows the use of a GPU to speed up the training process contrary to other methods \textcolor{red}{\cite{} developed for the M4 competition}.
+In addition, our approach offers the possibility of providing forecasts for a totally  new collection of sequences without retraining the entire hybrid model.
+Given a new time series,  the weights of the error-corrector recurrent model are frozen and only the new time-series-specific statistical model has to be trained.% It remains the responsibility of the users to provide new sequences sharing same behaviours than the dataset using for the training to keep the same accuracy level.
 
-In addition to a more general framework, we add the possibility of doing inference with our new implementation.
-We design a new process to compute and provide a forecast for a totally  new collection of sequences without retraining the entire hybrid model.
-Given a new time series, we freeze the weights of the error-corrector recurrent model and we only train the new time-series-specific statistical model linked to the new sequence.
-It remains the responsibility of the users to provide new sequences sharing same behaviours than the dataset using for the training to keep the same accuracy level.
+%For more details about the general hybrid training, a complete description of the training process can be found in the M4 hybrid model paper or in an interesting application of the method on electric load forecasting, see \citep{dudek2020hybrid}.
 
-For more details about the general hybrid training, a complete description of the training process can be found in the M4 hybrid model paper or in an interesting application of the method on electric load forecasting, see \citep{dudek2020hybrid}.
-
+\textcolor{red}{Detail here or in the appendix the training details: number of samples, optimizers, learning rates, etc.}
 \subsection{Benchmarks, hybrid models and Metrics}
 
-As benchmarks, we chose several well-known statistical methods and a full Machine Learning (ML) model.
-For the statistical part, using the R package "forecast", we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
+As benchmarks, we chose several well-known statistical methods and deep learning approaches.
+Using the R package {\em forecast}, we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
 \textit{Snaive} forecasts are only the repetition of the last same past period.
@@
 \textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization.
-The last one \textit{auto.arima} is the R implementation of ARIMA model with an automatic selection of the best parameters.
-For the full ML method, we train a global Long-Short Term Memory (\textit{lstm}) neural network on all our dataset.
-Against these models, we propose two versions of the hybrid approach without the external weak signal.
+The last one \textit{auto.arima} is the R implementation of ARIMA model with an automatic selection of the best parameters \textcolor{red}{add a reference for these models (paper or R package help section)}.
+We also considered a Long-Short Term Memory (\textit{lstm}) neural network.
+%Against these models, we propose two versions of the hybrid approach without the external weak signal.
 The first one is the original multiplicative form of the hybrid model that we name \textit{hybrid-mul}.
 The second one is the additive variant described in Section~\ref{sec:hybrid} and we named it \textit{hybrid-add}.
-To reach a higher accuracy level we propose at the end an ensembling (\textit{ensembling} of our two hybrid approaches using the FFORMA method created during the M4 competition, see \citep{fforma} .
+To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}). 
+Finally, we evaluate the model with  inclusion of external signals referred to as \textit{hybrid-add-ws} \textcolor{red}{together with a multiplicative version described in Appendix~\ref{}}.
+In order to provide fair comparisons, we also include a \textit{lstm} with inclusion of weak signals, referred to as \textit{lstm-ws}.
 
-Finally, to evaluate the power of our external signals and the capacity of our hybrid models to leverage them, we propose for our two approaches a version with the external weak signals.
-We name them respectively \textit{hybrid-mul-ws} for the multiplicative version and \textit{hybrid-add-ws} for the additive one.
-As benchmarks we propose the same comparison with our previous full ML model \textit{lstm} with a version including weak signals \textit{lstm-ws}.
-
-To compare the different methods, we use the same metrics as in the M4 competition: the Mean Absolute Scaled Error (MASE), the Symmetric Mean Absolute Percentage Error (SMAPE) and the final M4 competition metric, the Overall Weighted Average (OWA) of the SMAPE and the MASE.
-
-$$
-MASE = \frac{\frac{1}{h}\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\frac{1}{T-m}\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|} \quad
-SMAPE = \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}
-$$
-
-$$
-OWA = \frac{1}{2}(\frac{MASE}{MASE_{snaive}} + \frac{SMAPE}{SMAPE_{snaive}})
-$$
+To compare the different methods, we use the same metrics as in the M4 competition: the Mean Absolute Scaled Error (mase), the Symmetric Mean Absolute Percentage Error (smape) and the final M4 competition metric, the Overall Weighted Average (owa) of the smape and the mase defined as follows:
+\begin{align*}
+\mathrm{mase} &= \frac{\frac{1}{h}\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\frac{1}{T-m}\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,\\
+\mathrm{smape} &= \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}\,,\\
+\mathrm{owa} &= \frac{1}{2}(\frac{mase}{mase_{snaive}} + \frac{smape}{smape_{snaive}})\,,
+\end{align*}
+\textcolor{red}{where $\mathrm{smape_{snaive}}$ and $\mathrm{mase_{snaive}}$ are}.
 

### 2021-08-20 hybridmodel.tex
Many corrections throughout the main text

@@
 \textcolor{red}{Detail here or in the appendix the training details: number of samples, optimizers, learning rates, etc.}
+
+\vspace{.2cm}
+
+\textcolor{red}{Detail Train/test split.}
+
 \subsection{Benchmarks, hybrid models and Metrics}
@@
 \begin{align*}
-\mathrm{mase} &= \frac{\frac{1}{h}\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\frac{1}{T-m}\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,\\
+\mathrm{mase} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,\\
 \mathrm{smape} &= \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}\,,\\
-\mathrm{owa} &= \frac{1}{2}(\frac{mase}{mase_{snaive}} + \frac{smape}{smape_{snaive}})\,,
+\mathrm{owa} &= \frac{1}{2}\left(\frac{mase}{mase_{snaive}} + \frac{smape}{smape_{snaive}}\right)\,,
 \end{align*}
@@
 
-\subsection{Heuritech Fashion dataset results}
+\subsection{Results for XXX Dataset}
+\textcolor{red}{If possible, a few results of the hybrid approach without weak signals on a dataset other than Heuritech.}
+
+\subsection{Result for Heuritech Fashion dataset}
+
+\textcolor{red}{Add a figure of a time series with all models (and others in Appendix).}
+
+\vspace{.2cm}
+
+\textcolor{red}{Add a table with the results on the trends classifications used in Heuritech.}
 

### 2021-08-30 hybridmodel.tex
Add precisions for the statistical model init

@@
 Given the sequence $\fullts^n$, the two components  $\fulllvl^n$ and $\fullseas^n$ are computed using exponential smoothing.
-For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n,\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms.
-We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ \textcolor{red}{issue with the time index ?} and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
+For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n, \lvl^n_0, \{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters, $\lvl^n_0$ the first level term and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms.
+We have finally for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$, \textcolor{blue}{Now, I initialize alpha, gamma, the 52 first seasons and the first level with a python package}
+%We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ \textcolor{red}{issue with the time index ?} and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
 \begin{align*}
@@
 
-For all $n \in \{1,\ldots,N\}$, given the level component $\fulllvl^n$, the seasonality component $\fullseas^n$ and the forecast horizon $\lag \in \mathbb{N}$, the exponential smoothing forecast $\{\etspred^{ets,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ is, for all $i \in \{1,\ldots,\lag\}$,
+For all $1\leqslant n \leqslant N$, given the level component $\fulllvl^n$, the seasonality component $\fullseas^n$ and the forecast horizon $\lag \in \mathbb{N}$, the exponential smoothing forecast $\{\etspred^{ets,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ is, for all $i \in \{1,\ldots,\lag\}$,
 $$

### 2021-08-30 hybridmodel.tex
Change the name of predictor/classifier

@@
 %Write, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,H\}$, $\err^{n,T}_{T+i|T} = \ts^n_{T+i} - \etspred^{ets,n}_{T+i|T}$.
-Consider then a recurrent neural network denoted by RNN which aims at predicting the exponential smoothing error.
+Consider then a recurrent neural network denoted by RNN-p which aims at predicting the exponential smoothing error.
 Given $\rnnwindow^n_T$, the proposed model is given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by
@@
 $$
-where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent random variables with \textcolor{red}{specify here the right distribution} and $U^n_T$ an unobserved regime switching Bernoulli random variable.
-The random variable $U^n_T$ allows to provide RNN corrections only when ETS prediction is not sharp enough \textcolor{red}{Show in appendix cases where ETS alone is enough and cases where correction is required}.
-The law of $U^n_T$ is parameterized by a Feed Forward Neural Network (FFNN) with input \textcolor{red}{complete here}.
+where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent random variables with a Laplace distribution and $U^n_T$ an unobserved regime switching Bernoulli random variable.
+The random variable $U^n_T$ allows to provide RNN-p corrections only when ETS prediction is not sharp enough \textcolor{red}{Show in appendix cases where ETS alone is enough and cases where correction is required}.
+The law of $U^n_T$ is parameterized by a recurrent neural network denoted by RNN-c with the same input than RNN-p \textcolor{blue}{RNN-p for the predictor and RNN-c for the classifier, maybe names are confusing.
+They have, for now, the same archi/inputs}.
 %$$
@@
 
+\subsection{Hidden regime}
+
 As $U^n_T$ is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
-Therefore we use Fisher's identity to compute the score function and write a gradient ascent algorithm to estimate simultaneously the weights of the RNN and of the FFNN denoted by $\theta$.
+Therefore we use Fisher's identity to compute the score function and write a gradient ascent algorithm to estimate simultaneously the weights of RNN-p and of RNN-c denoted by $\theta$.
 The score is
@@
 where the joint likelihood $p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T}) = p_\theta(U_T^n|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$ is given by \eqref{eq:full:model} and the expectation is under the posterior distribution of $U_T^n$ given $\ts^n_{1:T+h}$.
-\textcolor{red}{details to add in appendix.} \textcolor{red}{Assume that $\theta_p$ is the current value for the weights of the FFNN and the RNN and write $\omega_p^n = \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T+h})$.
+\textcolor{red}{details to add in appendix.} \textcolor{red}{Assume that $\theta_p$ is the current value for the weights of the RNN-p and the RNN-c and write $\omega_p^n = \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T+h})$.
 Note that

### 2021-08-30 hybridmodel.tex
WIP dataset presentation part

@@
 However, for time series forecasting, there is a lack of large, rich and public datasets where neural network approaches can express their potential.
-\textcolor{red}{Other datasets for time series (see Alice paper on the SMC Transformer): air quality, weather, energy, Covid.
+%\textcolor{red}{Other datasets for time series (see Alice paper on the SMC Transformer): air quality, weather, energy, Covid.
 These datasets exist but no easy weak signals to derive from them i guess.
 }
-M4 and M5 competitions\textcolor{red}{Add link in footnote} provide a large amount of time series data but they show several limitations.
+%M4 and M5 competitions\textcolor{red}{Add link in footnote} provide a large amount of time series data but they show several limitations.
 For example, the M4 dataset does not propose external signals in addition to the target time series.
@@
 
+\textcolor{blue}{WIP}
+With this paper, we provide the first dataset dedicated to fashion.
+Our fashion dataset is built with a high throughput computer vision systems analysing every day images shared on social networks.
+Aggregating detected clothes by trends, we create thousands of time series representing trends life from 2015-01-05 to 2020-09-01 on social media .
+Our sequences show several desirable properties: same length, same yearly seasonality, shared behaviours and no missing values.
+Finnaly, our dataset contains a selection of $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
+An overview of it can be found in table 1.
+
+%a rich dataset gathering 14000 time series of fashion trend occurance on social medias.
+we build our  Every day images shared on social networks are analyzed thanks to a high throughput computer vision systems.
+Aggregating detected clothes by trends, we create thousands of time series with the same good properties: : from 2015-01-05 to 2020-09-01.
+Each time series is normalized in order to remove social networks biases and their values lie between 0 and 1.
+The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
+An overview of it can be found in table 1.
+
 %Heuritech is the first company to adopt a data-intensive approach  for the fashion forecasting. 
-Every day images shared on social networks are analyzed thanks to a high throughput computer vision systems.
+%Every day images shared on social networks are analyzed thanks to a high throughput computer vision systems.
 Aggregating detected clothes by trends, we create thousands of time series with the same good properties: same weekly seasonality, shared behaviours and the same length: from 2015-01-05 to 2020-09-01 \textcolor{red}{Add a few details here or in the appendix}.
@@
 The first one represents users with few followers, the second one is made of users with a moderate amount of followers and the last one gathers superstar and users of any fields with thousands of influencers.
-Again, the motivation here is to detect behaviour gaps between this three segments that could announce bigger changes in the main signal.
+Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.
 

### 2021-08-30 hybridmodel.tex
Updated title

--- 2021-08-30 hybridmodel.tex
@@
 \pdfinfo{
-/Title (Hybrid recurrent model for time series with inclusion of external weak signals)
+/Title (Hybrid recurrent model for regime switching nonstationary time series)
 /Author (Etienne David, Jean Bellot, Sylvain Le Corff)
@@
 % directly follow a colon or long dash
-\title{Hybrid Recurrent Model With External Weak Signals}
+\title{Hybrid recurrent model for regime switching nonstationary time series}
 \author{
@@
 It is crucial for many applications, in particular for fashion or retail industries, to make optimal inventory decision and avoid massive wastes.
-By tracking thousands of fashion trends on social media with stat-of-the-art computer vision approaches, we propose in this paper, the first study of fashion time series forecasting.
+By tracking thousands of fashion trends on social media with stat-of-the-art computer vision approaches, we propose a new model for fashion time series forecasting.
 Our contribution is  twofold.
@@
 Given the sequence $\fullts^n$, the two components  $\fulllvl^n$ and $\fullseas^n$ are computed using exponential smoothing.
-For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n, \lvl^n_0, \{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters, $\lvl^n_0$ the first level term and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms.
-We have finally for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$, \textcolor{blue}{Now, I initialize alpha, gamma, the 52 first seasons and the first level with a python package}
-%We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ \textcolor{red}{issue with the time index ?} and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
+For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n,\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms.
+We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ \textcolor{red}{issue with the time index ?} and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
 \begin{align*}
@@
 
-For all $1\leqslant n \leqslant N$, given the level component $\fulllvl^n$, the seasonality component $\fullseas^n$ and the forecast horizon $\lag \in \mathbb{N}$, the exponential smoothing forecast $\{\etspred^{ets,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ is, for all $i \in \{1,\ldots,\lag\}$,
+For all $n \in \{1,\ldots,N\}$, given the level component $\fulllvl^n$, the seasonality component $\fullseas^n$ and the forecast horizon $\lag \in \mathbb{N}$, the exponential smoothing forecast $\{\etspred^{ets,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ is, for all $i \in \{1,\ldots,\lag\}$,
 $$

### 2021-09-26 iclr2022/hybridmodel_iclr.tex
Add iclr 2022 directory

--- 2021-08-30 hybridmodel.tex
@@
-\def\year{2022}\relax
-%File: formatting-instructions-latex-2022.tex
-%release 2022.1
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage{aaai22}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet}  % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-%
-% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
-\usepackage{algorithm}
-\usepackage{algorithmic}
+\documentclass{article} % For LaTeX2e
+\usepackage{iclr2022_conference,times}
 
-%
-% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
-\usepackage{newfloat}
-\usepackage{listings}
-\usepackage{multirow}
-\usepackage{hhline}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{dsfont}
-\usepackage{amsthm}
+% Optional math commands from https://github.com/goodfeli/dlbook_notation.
+\input{math_commands.tex}
+
+\usepackage{hyperref}
+\usepackage{url}
 \usepackage{amssymb}
-\usepackage{booktabs}
-\usepackage{xcolor}
+\usepackage{graphicx}
 
-\lstset{%
-	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
-	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
-	aboveskip=0pt,belowskip=0pt,%
-	showstringspaces=false,tabsize=2,breaklines=true}
-\floatstyle{ruled}
-\newfloat{listing}{tb}{lst}{}
-\floatname{listing}{Listing}
-%
-%\nocopyright
-%
-% PDF Info Is REQUIRED.
-% For /Title, write your title in Mixed Case.
-% Don't use accents or commands. Retain the parentheses.
-% For /Author, add all authors within the parentheses,
-% separated by commas. No accents, special characters
-% or commands are allowed.
-% Keep the /TemplateVersion tag as is
-\pdfinfo{
-/Title (Hybrid recurrent model for regime switching nonstationary time series)
-/Author (Etienne David, Jean Bellot, Sylvain Le Corff)
-/TemplateVersion (2022.1)
+\title{Hybrid recurrent model for regime switching nonstationary time series}
+
+\author{Etienne DAVID \\
+Heuritech \\
+Paris \\
+\texttt{etienne.david@heuritech.com} \\
+\And
+Sylvain Le Corff \\
+Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC \\
+Institut Polytechnique de Paris, Palaiseau \\
+\texttt{sylvain.le$\_$corff@telecom-sudparis.eu} \\
+\And 
+Jean Bellot \\
+Heuritech \\
+Paris \\
+\texttt{jean.bellot@heuritech.com} \\
 }
 
-% DISALLOWED PACKAGES
-% \usepackage{authblk} -- This package is specifically forbidden
-% \usepackage{balance} -- This package is specifically forbidden
-% \usepackage{color (if used in text)
-% \usepackage{CJK} -- This package is specifically forbidden
-% \usepackage{float} -- This package is specifically forbidden
-% \usepackage{flushend} -- This package is specifically forbidden
-% \usepackage{fontenc} -- This package is specifically forbidden
-% \usepackage{fullpage} -- This package is specifically forbidden
-% \usepackage{geometry} -- This package is specifically forbidden
-% \usepackage{grffile} -- This package is specifically forbidden
-% \usepackage{hyperref} -- This package is specifically forbidden
-% \usepackage{navigator} -- This package is specifically forbidden
-% (or any other package that embeds links such as navigator or hyperref)
-% \indentfirst} -- This package is specifically forbidden
-% \layout} -- This package is specifically forbidden
-% \multicol} -- This package is specifically forbidden
-% \nameref} -- This package is specifically forbidden
-% \usepackage{savetrees} -- This package is specifically forbidden
-% \usepackage{setspace} -- This package is specifically forbidden
-% \usepackage{stfloats} -- This package is specifically forbidden
-% \usepackage{tabu} -- This package is specifically forbidden
-% \usepackage{titlesec} -- This package is specifically forbidden
-% \usepackage{tocbibind} -- This package is specifically forbidden
-% \usepackage{ulem} -- This package is specifically forbidden
-% \usepackage{wrapfig} -- This package is specifically forbidden
-% DISALLOWED COMMANDS
-% \nocopyright -- Your paper will not be published if you use this command
-% \addtolength -- This command may not be used
-% \balance -- This command may not be used
-% \baselinestretch -- Your paper will not be published if you use this command
-% \clearpage -- No page breaks of any kind may be used for the final version of your paper
-% \columnsep -- This command may not be used
-% \newpage -- No page breaks of any kind may be used for the final version of your paper
-% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
-% \pagestyle -- This command may not be used
-% \tiny -- This is not an acceptable font size.
-% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
-% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference
+% The \author macro works with any number of authors. There are two commands
+% used to separate the names and addresses of multiple authors: \And and \AND.
+%
+% Using \And between authors leaves it to \LaTeX{} to determine where to break
+% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
+% puts 3 of 4 authors names on the first line, and the last on the second
+% line, try using \AND instead of \And before the third author name.
 
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
-
-% The file aaai22.sty is the style file for AAAI Press
-% proceedings, working notes, and technical reports.
-%
-
-% Title
-
-% Your title must be in mixed case, not sentence case.
-% That means all verbs (including short verbs like be, is, using,and go),
-% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
-% articles, conjunctions, and prepositions are lower case unless they
-% directly follow a colon or long dash
-\title{Hybrid recurrent model for regime switching nonstationary time series}
-\author{
-    %Authors
-    % All authors must be in the same font size and format.
-    Etienne David,\textsuperscript{\rm 1,\rm 2}\\
-    Jean Bellot,\textsuperscript{\rm 1}\\
-    Sylvain Le Corff\textsuperscript{\rm 2}\\
-}
-\affiliations{
-    %Afiliations
-    \textsuperscript{\rm 1}Heuritech, Paris\\
-    \textsuperscript{\rm 2}Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC, Institut Polytechnique de Paris, Palaiseau
-    % If you have multiple authors and multiple affiliations
-    % use superscripts in text and roman font to identify them.
-    % For example,
-
-    % Sunil Issar, \textsuperscript{\rm 2}
-    % J. Scott Penberthy, \textsuperscript{\rm 3}
-    % George Ferguson,\textsuperscript{\rm 4}
-    % Hans Guesgen, \textsuperscript{\rm 5}.
-    % Note that the comma should be placed BEFORE the superscript for optimum readability
-
-    %2275 East Bayshore Road, Suite 160\\
-    %Palo Alto, California 94303\\
-    % email address must be in roman text type, not monospace or sans serif
-    etienne.david@heuritech.com, jean.bellot@heuritech.com, sylvain.le$\_$corff@telecom-sudparis.eu
-%
-% See more examples next
-}
-
-%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-\iffalse
-\title{My Publication Title --- Single Author}
-\author {
-    Author Name
-}
-\affiliations{
-    Affiliation\\
-    Affiliation Line 2\\
-    name@example.com
-}
-\fi
-
-\iffalse
-%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-\title{My Publication Title --- Multiple Authors}
-\author {
-    % Authors
-    First Author Name,\textsuperscript{\rm 1}
-    Second Author Name, \textsuperscript{\rm 2}
-    Third Author Name \textsuperscript{\rm 1}
-}
-\affiliations {
-    % Affiliations
-    \textsuperscript{\rm 1} Affiliation 1\\
-    \textsuperscript{\rm 2} Affiliation 2\\
-    firstAuthor@affiliation1.com, secondAuthor@affilation2.com, thirdAuthor@affiliation1.com
-}
-\fi
-
-% REMOVE THIS: bibentry
-% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
-\usepackage{bibentry}
-% END REMOVE bibentry
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
 
@@
 
+%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
 \begin{document}
@@
 %We design a more general hybrid framework including the original multiplicative model and a new additive one.
-Our approach enriches existing hybrd models  by incorporating an unobserved regime switching feature to account for the need neural network based correction.
+Our approach enriches existing hybrid models  by incorporating an unobserved regime switching feature to account for the need neural network based correction.
 In order to leverage external signals, we modify the hybrid framework to allow the regime shift and the  global error-corrector neural network to deal with external data.
@@
 \textcolor{blue}{WIP}
+%With this paper, we provide the first dataset dedicated to fashion.
+Our fashion dataset is built with a high throughput computer vision systems analysing every day images shared on social networks.
+Aggregating detected clothes by trends, we create for the first time thousand of time series representing fashion trends life on social media.
+Moreover, our sequences show desirable properties.
+They have all the same length, weekly time step, shared behaviours, no sporadic sequence and no missing values.
+We provide publicly a selection of $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
+An overview of it can be found in table 1.
+
 With this paper, we provide the first dataset dedicated to fashion.
 Our fashion dataset is built with a high throughput computer vision systems analysing every day images shared on social networks.
-Aggregating detected clothes by trends, we create thousands of time series representing trends life from 2015-01-05 to 2020-09-01 on social media .
-Our sequences show several desirable properties: same length, same yearly seasonality, shared behaviours and no missing values.
-Finnaly, our dataset contains a selection of $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
+Aggregating detected clothes by trends, we create for the first time thousand of time series representing fashion trends life on social media.
+Our sequences show several desirable properties: same length (from 2015-01-05 to 2020-09-01), same yearly seasonality, shared behaviours and no missing values.
+We provide publicly a selection of $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
 An overview of it can be found in table 1.
@@
   \begin{tabular}{lllllllllll}
-    \toprule
+    \hline
     &  Top  & Pants & Short & Skirt & Dress & Coat & Shoes & Color & Texture &  \\
-    \midrule
+    \hline
      United States & 587/290 & 195/158  & 64/37 & 38/- & 38/- & 271/218 & 439/114 & 59/59 & 129/103\\
@@
      Brazil &  587/290 & 195/158 & 64/37 & 38/- &  38/- & 271/218 & 439/114 & 59/59 & 136/110\\
-     \midrule
+     \hline
      Total & 2934/1450 & 973/790 & 320/185 & 190/- & 188/- & 1355/1090 & 2179/570 & 295/294 & 652/535 & \numberts\\
-    \bottomrule
+    \hline
   \end{tabular}
@@
 With three thresholds we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high}.
-The first one represents users with few followers, the second one is made of users with a moderate amount of followers and the last one gathers superstar and users of any fields with thousands of influencers.
+Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.These extra signals are frequently sparse for micro trends and they often lack of interest for common fashion trends.
+However on several examples, they are fundamental to detect the future fashion evolution.
+
+%The first one represents users with few followers, the second one is made of users with a moderate amount of followers and the last one gathers superstar and users of any fields with thousands of influencers.
 Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.
 
-At the end, we have for each trends 4 linked weak signals representing this trends on a specific panel of social media users.
+%At the end, we have for each trends 4 linked weak signals representing this trends on a specific panel of social media users.
 These extra signals are frequently sparse for micro trends and they often lack of interest for common fashion trends.
@@
   \begin{tabular}{lllllll}
-    \toprule
+    \hline
     &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std  \\
-    \midrule
+    \hline
      snaive & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
@@
      Ensembling & 0.846/0.804 & 0.30 & 23.78/21.07 & 12.9 & 0.864/0.863 & 0.10  \\
-    \bottomrule
+    \hline
   \end{tabular}
@@
   \begin{tabular}{lllllll}
-    \toprule
+    \hline
     &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std \\
-    \midrule
+    \hline
     lstm & 0.881/0.824 & 0.34 & 24.41/21.56 & 12.81 & 0.895/0.885 & 0.11 \\
@@
      Ensembling & 0.827/0.787 & 0.29 & 23.43/20.63 & 12.8 & 0.849/0.849 & 0.11\\
-    \bottomrule
+    \hline
   \end{tabular}
@@
   \begin{tabular}{lllllll}
-    \toprule
+    \hline
     &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std \\
-    \midrule
+    \hline
      hybrid-add & 0.861  & 0.004 & 24.16 & 0.18 & 0.877 & 0.002 \\
@@
      hybrid-mul-ws & 0.844 & 0.010 & 23.74 & .20 & 0.863 & 0.006 \\
-    \bottomrule
+    \hline
   \end{tabular}
@@
 
-\bibliography{aaai22.bib}
+\bibliography{iclr2022_conference}
+\bibliographystyle{iclr2022_conference}
 
-\section{Appendices}
-
-\subsection{RNN architecture and baselines}
-\label{section:architectures}
-
-\subsection{Further training details}
-\label{section:train_details}
-
-\subsection{Details on the Fashion dataset}
-\label{section:dataset_details}
-
-\subsection{Examples from the dataset}
-\label{section:examples}
+\appendix
+\section{Appendix}
 

### 2021-09-26 iclr2022/hybridmodel_iclr.tex
Add infos on the classifier RNN

@@
 \newcommand{\numberts}{14000}
+\newcommand{\threshold}{\eta}
 
@@
 $m \in \mathbb{N}$ is the seasonality (4 for quarterly, 12 for monthly or 52 for weekly time series).
-Given the sequence $\fullts^n$, the two components  $\fulllvl^n$ and $\fullseas^n$ are computed using exponential smoothing.
 For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n, \lvl^n_0, \{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters, $\lvl^n_0$ the first level term and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms.
-We have finally for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$, \textcolor{blue}{Now, I initialize alpha, gamma, the 52 first seasons and the first level with a python package}
+Given the sequence $\fullts^n$ and the parameters $\Theta^n$ , the two components  $\fulllvl^n$ and $\fullseas^n$ are computed as follow :
 %We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ \textcolor{red}{issue with the time index ?} and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
@@
 $$
-\ts^n_{T+i}  = \etspred^{ets,n}_{T+i|T} +  U^n_T\times\meants^n_T\times \rnnmodel(\rnnwindow^n_T)_{T+i} + \varepsilon^n_{T+i}\,,%\\
-%  &= \lvl^n_T + \seas^n_{T+i-m(k+1)} +  U^n_T\times\meants^n_T\times \rnnmodel(\rnnwindow^n_T)_{T+i} + \varepsilon^n_{T+i}\,,
+\ts^n_{T+i}  = \etspred^{ets,n}_{T+i|T} +  U^n_T\times\meants^n_T\times \rnnmodel_p(\rnnwindow^n_T)_{T+i} + \varepsilon^n_{T+i}\,,%\\
+%  &= \lvl^n_T + \seas^n_{T+i-m(k+1)} +  U^n_T\times\meants^n_T\times \rnnmodel_p(\rnnwindow^n_T)_{T+i} + \varepsilon^n_{T+i}\,,
 $$
@@
 The random variable $U^n_T$ allows to provide RNN-p corrections only when ETS prediction is not sharp enough \textcolor{red}{Show in appendix cases where ETS alone is enough and cases where correction is required}.
-The law of $U^n_T$ is parameterized by a recurrent neural network denoted by RNN-c with the same input than RNN-p \textcolor{blue}{RNN-p for the predictor and RNN-c for the classifier, maybe names are confusing.
-They have, for now, the same archi/inputs}.
+The law of $U^n_T$ is parameterized by a recurrent neural network denoted by RNN-c with the same input than RNN-p.
+\begin{align*}
+U^n_T = \mathbf{1}_{\rnnmodel_p(\rnnwindow^n_T) > \threshold}
+\end{align*}
+
+\textcolor{blue}{RNN-p for the predictor and RNN-c for the classifier, maybe names are confusing. They have, for now, the same archi/inputs}.
 %$$
@@
 \label{eq:full:model}
-\ts^n_{T+i}  = \etspred^{ets,n}_{T+i|T} +  U^n_T\times\meants^n_T\times \rnnmodel(\fullconcatinput^n_T)_{T+i} + \varepsilon^n_{T+i}\,,
+\ts^n_{T+i}  = \etspred^{ets,n}_{T+i|T} +  U^n_T\times\meants^n_T\times \rnnmodel_p(\fullconcatinput^n_T)_{T+i} + \varepsilon^n_{T+i}\,,
 \end{equation}
-\textcolor{red}{specify here the right distribution for $U$ (depends on the weak signal or no)}. The complete architecture is displayed in Figure~\ref{fig:architecture}.
+with :
+\begin{align*}
+U^n_T = \mathbf{1}_{\rnnmodel_p(\fullconcatinput^n_T) > \threshold}
+\end{align*}
+The complete architecture is displayed in Figure~\ref{fig:architecture}.
 

### 2021-09-28 iclr2022/hybridmodel_iclr.tex
new Hybrid Model section

@@
 \newcommand{\tspred}{\hat{\ts}}
-\newcommand{\lvl}{\hat{l}}
-\newcommand{\fulllvl}{{\bf \lvl}}
-\newcommand{\seas}{\hat{s}}
-\newcommand{\fullseas}{{\bf \seas}}
-\newcommand{\lsmooth}{\alpha}
-\newcommand{\ssmooth}{\beta}
+\newcommand{\stat}{f}
+\newcommand{\statparam}{\Theta}
+\newcommand{\fullstat}{{\bf \stat}}
 \newcommand{\lag}{h}
 \newcommand{\window}{w}
-\newcommand{\etspred}{\hat{y}}
-\newcommand{\fulletspred}{{\bf \etspred}}
 \newcommand{\tswindow}{{\bf \ts}}
@@
 \newcommand{\rnnmodel}{\textsc{rnn}}
-\newcommand{\etsmodel}{\textsc{ets(n,n,a)}}
 \newcommand{\ws}{w}
@@
 \newcommand{\fullconcatinput}{{ \bf \concatinput}}
-\newcommand{\numberts}{14000}
+\newcommand{\numberts}{10000}
 \newcommand{\threshold}{\eta}
+\newcommand{\predictor}{RNN_p}
+\newcommand{\classifier}{RNN_c}
+\newcommand{\remainer}{r}
+\newcommand{\hiddenregime}{U}
 
@@
 In order to leverage external signals, we modify the hybrid framework to allow the regime shift and the  global error-corrector neural network to deal with external data.
-By adding our fashion external weak signals in our proposed framework, we show the real potential of the hybrid approach: a global neural network, able to leverage large amount of data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of the parametric models.
+By adding our fashion external weak signals in our proposed framework, we show the real potential of the hybrid approach: a global neural network, able to leverage large amount of data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of any parametric models.
 
 The paper is organized as follow.
-Section~\ref{sec:hybrid} describes our hybrid framework which consists of an exponential smoothing model and a recurrent neural network combining the target sequences with external weak signals.
+Section~\ref{sec:hybrid} describes our hybrid framework which consists of a per-time-series parametric model and a recurrent neural network combining the target sequences with external weak signals.
 Then, we present our new fashion dataset in Section~\ref{sec:dataset}.
@@
 \label{sec:hybrid}
-We introduce a new hybrid approach for time series forecasting  composed of two parts: an additive exponential smoothing (ETS) per time series and a global RNN.
+We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global RNN.
 We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
-Then, we use a recurrent neural network and weak signals to correct the predictions provided by the ETS.
+Then, we use a recurrent neural network and weak signals to correct the predictions provided by the first collection of parametric models.
 
@@
 %The first step in our additive hybrid model is to consider, for each time series, an exponential smoothing  statistical model.
-The time-series-specific models compute, for each sequence, two components,  level  and  seasonality.
+%The time-series-specific models compute, for each sequence, two components,  level  and  seasonality.
 For all $1\leqslant n \leqslant N$ and $0\leqslant t \leqslant T$, let $\lvl_t^n$ be the value of the $n$-th level component at time $t$ and  $\fulllvl^n = \{\lvl_t^n\}_{0\leqslant t \leqslant T}$ be all the values of this level component.
@@
 $m \in \mathbb{N}$ is the seasonality (4 for quarterly, 12 for monthly or 52 for weekly time series).
-For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n, \lvl^n_0, \{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters, $\lvl^n_0$ the first level term and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms.
+The time-series-specific models compute, for each sequence, a first $\lag$-ahead prediction based on the past.
+For all $1\leqslant n \leqslant N$, we note $\stat^n$ the $n$-th parametric model linked to the $n$-th sequence.
+Each model gather a collection of parameters in order to provide a forecast.
+We note $\statparam^n$ the parameters of the statistical model $\stat^n$.
+Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$, the parametric models, $\{\stat^n\}_{1\leqslant n \leqslant N}$ and the associated paramters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the first time-series-specific forecasts $\{\tspred^{stat,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+$$
+\tspred^{stat,n}_{T+i|T} = \stat^n(\ts^n_{1:T}|\statparam^n)_i\,,
+$$
+
+During the M4 competition, the hybrid model's author based his framework on a multiplicative exponential smoothing model as the time-series-specific model.
+However, on sporadic time series, this choice could lead to poor result and instability.
+In our approach, we decided to go deeper and provide a general framework able to deal with any kind of per-time-series models.
+In the Section~\ref{sec:exp}, we present two versions of our framework.
+The first one use an additive exponential smoothing as reference and the second one use a TBATS model as reference.
+At the end, The main complexity is in the next stage: succeed in training a global RNN to understand all the per-time-series statistical models and correct their mistakes if needed.
+% Indeed, depending on time series, some family of parametric models can achieve really heterogeneous level of accuracy. 
+%For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n, \lvl^n_0, \{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters, $\lvl^n_0$ the first level term and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms.
 Given the sequence $\fullts^n$ and the parameters $\Theta^n$ , the two components  $\fulllvl^n$ and $\fullseas^n$ are computed as follow :
 %We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ \textcolor{red}{issue with the time index ?} and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
-\begin{align*}
-    \lvl^n_{t} &= \lsmooth^n (\ts^n_t - \seas^n_{t-m}) + (1- \lsmooth^n)\lvl^n_{t-1}\,, \\
-    \seas^n_t &= \ssmooth^n (\ts^n_t - \lvl^n_{t-1}) + (1 - \ssmooth^n)\seas^n_{t-1}\,. 
-\end{align*}
+%\begin{align*}
+    %\lvl^n_{t} &= \lsmooth^n (\ts^n_t - \seas^n_{t-m}) + (1- \lsmooth^n)\lvl^n_{t-1}\,, \\
+    %\seas^n_t &= \ssmooth^n (\ts^n_t - \lvl^n_{t-1}) + (1 - \ssmooth^n)\seas^n_{t-1}\,. 
+%\end{align*}
 
-For all $1\leqslant n \leqslant N$, given the level component $\fulllvl^n$, the seasonality component $\fullseas^n$ and the forecast horizon $\lag \in \mathbb{N}$, the exponential smoothing forecast $\{\etspred^{ets,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ is, for all $i \in \{1,\ldots,\lag\}$,
-$$
-\etspred^{ets,n}_{T+i|T} = \lvl^n_T + \seas^n_{T+i-m(k+1)}\,,
-$$
-where $k = \lfloor(i-1)/m\rfloor$.
+%For all $1\leqslant n \leqslant N$, given the level component $\fulllvl^n$, the seasonality component $\fullseas^n$ and the forecast horizon $\lag \in \mathbb{N}$, the exponential smoothing forecast $\{\etspred^{ets,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ is, for all $i \in \{1,\ldots,\lag\}$,
+%$$
+%\etspred^{ets,n}_{T+i|T} = \lvl^n_T + \seas^n_{T+i-m(k+1)}\,,
+%$$
+%where $k = \lfloor(i-1)/m\rfloor$.
 
@@
 
-This statistical model offers a fine approach to normalize and deseasonnalize the sequences.
+%This statistical model offers a fine approach to normalize and deseasonnalize the sequences.
 In addition, with its two recurrent equations only, it is simple to code and incorporate in a larger framework using deep learning model and GPUs.
@@
 
-Then, we train a global RNN on all sequences to compute a correction of the initial prediction.
+%At this stage, we want to train a global RNN, trained on all the N sequences and able to understand and correct the weaknesses of the first per-time-series parametric models.
+%At this stage, we can write that for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+%$$
+%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \varepsilon^n_{T+i}\,,
+%$$
+At this stage, we assume that we have two different regimes.
+In the regime 0, the first parametric forecast succed at catching all the information of the $n$-th sequence.
+Conversely, in the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainer$.
+Our regime-switching system is then :
+
+$$
+\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \hiddenregime^n_T * \remainer^{n}_{T+i} + \varepsilon^n_{T+i}\,,
+$$
+where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent \textcolor{blue}{centered} random variables and $U^n_T$ an unobserved regime switching Bernoulli random variable.
+%In the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainer$.
+%For this regime, we have for all $i \in \{1,\ldots,\lag\}$ :
+%$$
+%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \remainer^{n}_{T+i} + \varepsilon^n_{T+i}\,,
+%$$
+
+To estimate this system, we introduce our new regime swithing error-corrector framework.
+We train two global RNN on all sequences, a classifier ($\classifier$) and a predictor ($\predictor$).
+We train the classifier to provide a probability of being in the regime 1 and we train the predictor to estimate the first per-time-series forecasts errors if we are in the regime 1.
+However, these tasks require a thorough data pre-processing and with our collection of parametric models, we propose a fine way to normalize and deseasonalize the RNNs inputs.
+
+%Then, we train a global RNN on all sequences to compute a correction of the initial prediction.
+%Then, we train a global RNN on all sequences to compute a correction of the initial prediction.
 %We motivate this choice for two reasons.
@@
 Turning a full forecasting task into a correcting task largely simplifies the RNN goals.
-This task requires a thorough data pre-processing and with our collection of exponential smoothing models  we propose a fine way to normalize and deseasonalize the RNN inputs and outputs.
+%This task requires a thorough data pre-processing and with our collection of parametric models, we propose a fine way to normalize and deseasonalize the RNN inputs and outputs.
 %We describe bellow how we design a RNN able to understand the first exponential smoothing models and estimate a correction of their forecasting errors.
 
-Let $\window \in \mathbb{N}$ be the window size, usually this input window is equal to the forecast horizon $\window = \lag$.
+Let $\window \in \mathbb{N}$ be the window size, usually this window is equal to the forecast horizon $\window = \lag$.
 Consider the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnn^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$,
 $$
-\rnn^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} - \lvl^n_T - \seas^n_{T-w+i}}{\meants^n_T}\,,
+\rnn^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{stat,n}_{T-w+i|T-w}}{\meants^n_T}\,,
 $$
 where $ \meants^n_T = \sum_{i = 1}^{w}  \ts^n_{T-w+i}/w$.
-This new input is used to correct the exponential smoothing prediction.
+We use this sequence as input of our two neural network, $\classifier$ and $\predictor$.
 %Write, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,H\}$, $\err^{n,T}_{T+i|T} = \ts^n_{T+i} - \etspred^{ets,n}_{T+i|T}$.
-Consider then a recurrent neural network denoted by RNN-p which aims at predicting the exponential smoothing error.
+
+Given $\rnnwindow^n_T$, the proposed regime swithing error-corrector reccurent model is given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by :
+$$
+\ts^n_{T+i}  = \tspred^{stat,n}_{T-w+i|T-w} +  \mathbf{1}_{\classifier(\rnnwindow^n_T) > \threshold} \times \predictor(\rnnwindow^n_T)_{T+i} \times \meants^n_T + \varepsilon^n_{T+i}\
+$$
+
+where $\mathbf{1}$ is the indicatrice function and $\threshold$ a threshold parameter.\\
+
+%Consider then a recurrent neural network denoted by RNN-p which aims at predicting the exponential smoothing error.
 Given $\rnnwindow^n_T$, the proposed model is given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by
-$$
-\ts^n_{T+i}  = \etspred^{ets,n}_{T+i|T} +  U^n_T\times\meants^n_T\times \rnnmodel_p(\rnnwindow^n_T)_{T+i} + \varepsilon^n_{T+i}\,,%\\
-%  &= \lvl^n_T + \seas^n_{T+i-m(k+1)} +  U^n_T\times\meants^n_T\times \rnnmodel_p(\rnnwindow^n_T)_{T+i} + \varepsilon^n_{T+i}\,,
-$$
-where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent random variables with a Laplace distribution and $U^n_T$ an unobserved regime switching Bernoulli random variable.
+%$$
+%\ts^n_{T+i}  = \tspred^{stat,n}_{T-w+i|T-w} +  U^n_T\times\meants^n_T\times \rnnmodel_p(\rnnwindow^n_T)_{T+i} + \varepsilon^n_{T+i}\,,%\\
+%  &= \stat^n(\ts^n_{1:T}|\statparam^n)_i +  U^n_T\times\meants^n_T\times \rnnmodel_p(\rnnwindow^n_T)_{T+i} + \varepsilon^n_{T+i}\,,
+%$$
+%where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent random variables with a Laplace distribution and $U^n_T$ an unobserved regime switching Bernoulli random variable.
 The random variable $U^n_T$ allows to provide RNN-p corrections only when ETS prediction is not sharp enough \textcolor{red}{Show in appendix cases where ETS alone is enough and cases where correction is required}.
 The law of $U^n_T$ is parameterized by a recurrent neural network denoted by RNN-c with the same input than RNN-p.
-\begin{align*}
-U^n_T = \mathbf{1}_{\rnnmodel_p(\rnnwindow^n_T) > \threshold}
-\end{align*}
-
-\textcolor{blue}{RNN-p for the predictor and RNN-c for the classifier, maybe names are confusing. They have, for now, the same archi/inputs}.
+%\begin{align*}
+%U^n_T = \mathbf{1}_{\rnnmodel_p(\rnnwindow^n_T) > \threshold}
+%\end{align*}
 %$$
@@
 In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the family.
-Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for our RNN,
+Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for our two RNN,
 \begin{align*}
@@
 \end{align*}
+
 Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ our final model becomes:
@@
 \label{eq:full:model}
-\ts^n_{T+i}  = \etspred^{ets,n}_{T+i|T} +  U^n_T\times\meants^n_T\times \rnnmodel_p(\fullconcatinput^n_T)_{T+i} + \varepsilon^n_{T+i}\,,
+\ts^n_{T+i}  = \tspred^{stat,n}_{T-w+i|T-w} +  \mathbf{1}_{\classifier(\fullconcatinput^n_T) > \threshold} \times \predictor(\fullconcatinput^n_T)_{T+i} \times \meants^n_T + \varepsilon^n_{T+i}\,,
 \end{equation}
-with :
-\begin{align*}
-U^n_T = \mathbf{1}_{\rnnmodel_p(\fullconcatinput^n_T) > \threshold}
-\end{align*}
 The complete architecture is displayed in Figure~\ref{fig:architecture}.
@@
 
-As $U^n_T$ is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
+As $\hiddenregime$ is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
 Therefore we use Fisher's identity to compute the score function and write a gradient ascent algorithm to estimate simultaneously the weights of RNN-p and of RNN-c denoted by $\theta$.
 The score is
-\begin{multline*}
-\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T})
-\\ = \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h}\right]\,,
-\end{multline*}
+\begin{equation}
+\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h}\right]\,,
+\end{equation}
+\\
 where the joint likelihood $p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T}) = p_\theta(U_T^n|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$ is given by \eqref{eq:full:model} and the expectation is under the posterior distribution of $U_T^n$ given $\ts^n_{1:T+h}$.
-\textcolor{red}{details to add in appendix.} \textcolor{red}{Assume that $\theta_p$ is the current value for the weights of the RNN-p and the RNN-c and write $\omega_p^n = \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T+h})$.
-Note that
-$$
-\omega_p^n \propto \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T})p_{\theta_p}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\,.
-$$
-Then,
-\begin{multline*}
-\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \omega_p^n\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})\\
-+ (1-\omega_p^n)\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,.
-\end{multline*}
-The loss function is then given by
-\begin{multline*}
-\theta\mapsto - \omega_p^n \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})\\
-- (1-\omega_p^n) \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,,
-\end{multline*} 
-where no gradient is computed on $\omega_p^n$.
-In both terms, $\log p_\theta(U_T^n=0|\ts^n_{1:T})$ and $\log p_\theta(U_T^n=0|\ts^n_{1:T})$ are simply given by the output of the FFNN.
-Choices for the model.
-\begin{itemize}
-\item In the case where the  $\varepsilon^n_{T+i}$ are Gaussian and independent, up to an additive constant
-$$
-\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) = -c\sum_{i=1}^{h}(\ts^n_{T+i}  - \etspred^{ets,n}_{T+i|T})^2
-$$
-and
-\begin{multline*}
-\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\\
- = -c\sum_{i=1}^{h}(\ts^n_{T+i}  - \etspred^{ets,n}_{T+i|T} - \meants^n_T\times \rnnmodel(\fullconcatinput^n_T)_{T+i})^2\,.
-\end{multline*}
-Choice of $c$ ?
-\item In the case where the  $\varepsilon^n_{T+i}$ are Laplace and independent, up to an additive constant
-$$
-\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) = -c\sum_{i=1}^{h}|\ts^n_{T+i}  - \etspred^{ets,n}_{T+i|T}|
-$$
-and
-\begin{multline*}
-\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\\
- = -c\sum_{i=1}^{h}|\ts^n_{T+i}  - \etspred^{ets,n}_{T+i|T} - \meants^n_T\times \rnnmodel(\fullconcatinput^n_T)_{T+i}|\,.
-\end{multline*}
-Choice of $c$ ?
-\end{itemize}}
+A complete description of the training process can be found in Appendix.
 
@@
 
+\textcolor{red}{details to add in appendix.} \textcolor{red}{Assume that $\theta_p$ is the current value for the weights of the RNN-p and the RNN-c and write $\omega_p^n = \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T+h})$.
+Note that
+$$
+\omega_p^n \propto \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T})p_{\theta_p}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\,.
+$$
+Then,
+\begin{multline*}
+\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \omega_p^n\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})\\
++ (1-\omega_p^n)\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,.
+\end{multline*}
+The loss function is then given by
+\begin{multline*}
+\theta\mapsto - \omega_p^n \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})\\
+- (1-\omega_p^n) \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,,
+\end{multline*} 
+where no gradient is computed on $\omega_p^n$.
+In both terms, $\log p_\theta(U_T^n=0|\ts^n_{1:T})$ and $\log p_\theta(U_T^n=0|\ts^n_{1:T})$ are simply given by the output of the FFNN.
+Choices for the model.
+\begin{itemize}
+\item In the case where the  $\varepsilon^n_{T+i}$ are Gaussian and independent, up to an additive constant
+$$
+\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) = -c\sum_{i=1}^{h}(\ts^n_{T+i}  - \tspred^{stat,n}_{T-w+i|T-w})^2
+$$
+and
+\begin{multline*}
+\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\\
+ = -c\sum_{i=1}^{h}(\ts^n_{T+i}  - \tspred^{stat,n}_{T-w+i|T-w} - \meants^n_T\times \rnnmodel(\fullconcatinput^n_T)_{T+i})^2\,.
+\end{multline*}
+Choice of $c$ ?
+\item In the case where the  $\varepsilon^n_{T+i}$ are Laplace and independent, up to an additive constant
+$$
+\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) = -c\sum_{i=1}^{h}|\ts^n_{T+i}  - \tspred^{stat,n}_{T-w+i|T-w}|
+$$
+and
+\begin{multline*}
+\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\\
+ = -c\sum_{i=1}^{h}|\ts^n_{T+i}  - \tspred^{stat,n}_{T-w+i|T-w} - \meants^n_T\times \rnnmodel(\fullconcatinput^n_T)_{T+i}|\,.
+\end{multline*}
+Choice of $c$ ?
+\end{itemize}}
+
 \end{document}

### 2021-09-28 iclr2022/hybridmodel_iclr.tex
add info in the Dataset section

@@
 
+\subsection{Fashion dataset}
+
 With this paper, we provide the first dataset dedicated to fashion.
@@
 Aggregating detected clothes by trends, we create for the first time thousand of time series representing fashion trends life on social media.
-Our sequences show several desirable properties: same length (from 2015-01-05 to 2020-09-01), same yearly seasonality, shared behaviours and no missing values.
+Our sequences have all 261 time steps, from 2015-01-05 to 2020-09-01 with weekly values and no missing walues.
+Each time series is normalized in order to remove social networks biases and their values lie between 0 and 1.
+The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
+An overview of it can be found in table 1.
+
+With in-house fashion experts, we selected especially a collection of $\numberts$ fashion trend in order to represent finely the issues that face the fashion industry.
+A large part of our time series are quite stable, their seasons and evolutions are regular.
+However, some sequences show interesting behaviours with huge changes.
+We call them emerging or declining trends depending of the change direction.
+One central point is to accurately detect and forecast these trends.
+
+%Our sequences show several desirable properties: same length (from 2015-01-05 to 2020-09-01), same yearly seasonality, shared behaviours and no missing values.
 We provide publicly a selection of $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.

### 2021-09-29 iclr2022/hybridmodel_iclr.tex
update the model archi figure and the dataset section

@@
 \newcommand{\classifier}{RNN_c}
-\newcommand{\remainer}{r}
+\newcommand{\remainder}{r}
 \newcommand{\hiddenregime}{U}
@@
 Developing models and algorithms to draw causal inference for time series is a long standing statistical problem.
-It is crucial for many applications, in particular for fashion or retail industries, to make optimal inventory decision and avoid massive wastes.
-By tracking thousands of fashion trends on social media with stat-of-the-art computer vision approaches, we propose a new model for fashion time series forecasting.
+It is crucial for many applications, in particular for fashion or retail industries, to make optimal inventory decisions and avoid massive wastes.
+By tracking thousands of fashion trends on social media with state-of-the-art computer vision approaches, we propose a new model for fashion time series forecasting.
 Our contribution is  twofold.
@@
 Strong consistency results were established in \citep{touron2019consistency} and Expectation Maximization based numerical experiments were proposed.
-Altough thes works provide promising results, HMM are computationally expensive to train and are not yet well studied for sequences with thousands of components with a seasonal behavior.
+Altough these works provide promising results, HMM are computationally expensive to train and are not yet well studied for sequences with thousands of components with a seasonal behavior \textcolor{blue}{with thousands of components or with a seasonal behavior ?}.
 
@@
 We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
-Then, we use a recurrent neural network and weak signals to correct the predictions provided by the first collection of parametric models.
+Then, we use 2 recurrent neural networks and weak signals to correct the predictions provided by the first collection of parametric models.
 
@@
 At this stage, we assume that we have two different regimes.
-In the regime 0, the first parametric forecast succed at catching all the information of the $n$-th sequence.
-Conversely, in the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainer$.
+In the regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence.
+Conversely, in the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainder$.
 Our regime-switching system is then :
@@
 $$
-\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \hiddenregime^n_T * \remainer^{n}_{T+i} + \varepsilon^n_{T+i}\,,
+\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \hiddenregime^n_T * \remainder^{n}_{T+i} + \varepsilon^n_{T+i}\,,
 $$
-where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent \textcolor{blue}{centered} random variables and $U^n_T$ an unobserved regime switching Bernoulli random variable.
-%In the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainer$.
+where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent \textcolor{blue}{centered} random variables, $\{\remainder^n_{T+i}\}_{i\leqslant 1}$ are non null remainders and $U^n_T$ an unobserved regime switching Bernoulli random variable.
+%In the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainder$.
 %For this regime, we have for all $i \in \{1,\ldots,\lag\}$ :
 %$$
-%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \remainer^{n}_{T+i} + \varepsilon^n_{T+i}\,,
+%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \remainder^{n}_{T+i} + \varepsilon^n_{T+i}\,,
 %$$
@@
 Given $\rnnwindow^n_T$, the proposed regime swithing error-corrector reccurent model is given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by :
-$$
-\ts^n_{T+i}  = \tspred^{stat,n}_{T-w+i|T-w} +  \mathbf{1}_{\classifier(\rnnwindow^n_T) > \threshold} \times \predictor(\rnnwindow^n_T)_{T+i} \times \meants^n_T + \varepsilon^n_{T+i}\
-$$
+\begin{align*}
+\ts^n_{T+i}  &= \tspred^{stat,n}_{T-w+i|T-w} +  \hat{\hiddenregime}^n_T * \hat{\remainder}^{n}_{T+i} + \varepsilon^n_{T+i} \\
+\hat{\hiddenregime}^n_T &= \mathbf{1}_{\classifier(\rnnwindow^n_T) > \threshold} \\
+\hat{\remainder}^{n}_{T+i} &= \predictor(\rnnwindow^n_T)_{T+i} \times \meants^n_T
+\end{align*}
 
@@
 \begin{align*}
-\fullconcatinput^n_T &= \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}\,, \\
-&= \{\rnn^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
+\fullconcatinput^n_T &= \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}\, \\
+&= \{\rnn^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,
 \end{align*}
@@
   \centering
-    \includegraphics[width=0.8\linewidth]{figure/hybrid_model_archi.png}
+    \includegraphics[width=1.2\linewidth]{figure/Regime_switching_recurrent_model}
   \caption{Hybrid model with weak signals architecture.}
@@
 
-\textcolor{blue}{WIP}
 %With this paper, we provide the first dataset dedicated to fashion.
@@
 
+\subsection{Weak signal}
+
 In addition to this large dataset we design for each sequence several weak signals.
@@
 
+%\subsection{Emerging/Declining fashion trend}
+
+%One of the main objectifs of the fashion industry is to correctly understand and anticipate the futur tendances. 
+%With in-house fashion experts, we selected a collection of $\tsnumber$ fashion trend representing finely the issues that face the fashion industry.
+Our dataset gather 3 types of trends, the common trends, the declining trends and the emerging trends.
+
+%A large part of our time series are regular, their evolutions are slow and constant in time.
+
+%A large part of these trends are commom, their evolutions are regular and well anticipated. In addition to these trends, we find two
+
+%One of the today main objectifs of the fashion industry is to drastically reduce the massive waste due to wrong inventory decisions, see for instance \citep{}.
+With our new dataset, we want to create a focus at detecting precisely
+
 %The first one represents users with few followers, the second one is made of users with a moderate amount of followers and the last one gathers superstar and users of any fields with thousands of influencers.
@@
 
-As an example, an impressive emerging fashion trend is represented in Figure 2, \textcolor{red}{see other examples in Appendix~\ref{}}.
+\subsection{Example}
+
+As an example, an impressive emerging fashion trend is represented in Figure 2, see other examples in Appendix~\ref{}.
 It shows the evolution of one shoes trends on social media and its linked \textit{fashion-forward} weak signal.
@@
 \subsection{Training}
+
+To train our hybrid model, we split our dataset in 3 parts, train,eval and test set.
+We use the 3 first years as our train set, we keep the 4th year for our eval set and we hide the last year for our test set.
+In order to increase our train set, we use a commom moving window as in Figure~\ref{fig:architecture}.
 

### 2021-09-29 iclr2022/hybridmodel_iclr.tex
write the training part

@@
 $$
-where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent \textcolor{blue}{centered} random variables, $\{\remainder^n_{T+i}\}_{i\leqslant 1}$ are non null remainders and $U^n_T$ an unobserved regime switching Bernoulli random variable.
+where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent random variables, $\{\remainder^n_{T+i}\}_{i\leqslant 1}$ are non null remainders and $U^n_T$ an unobserved regime switching Bernoulli random variable.
 %In the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainder$.
@@
 As $\hiddenregime$ is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
-Therefore we use Fisher's identity to compute the score function and write a gradient ascent algorithm to estimate simultaneously the weights of RNN-p and of RNN-c denoted by $\theta$.
+Therefore we use Fisher's identity to compute the score function and write a gradient ascent algorithm to estimate simultaneously the weights of RNN-p and of RNN-c denoted by $\theta = \{\theta_p,\theta_c\}$.
 The score is
@@
 We use the 3 first years as our train set, we keep the 4th year for our eval set and we hide the last year for our test set.
-In order to increase our train set, we use a commom moving window as in Figure~\ref{fig:architecture}.
+We train our hyrid model to compute a one-year ahead prediction with $\window$ and $\lag$ equal to 52.
+In order to increase our train set, we use a moving window as in Figure~\ref{fig:movingwindow}.
+All our code is developed in Python using the Tensorflow library.
+It allows the use of a GPU to speed up the trainig process.
+
+For the first parametric per-time-series models, we used existing Python or R librarys to set the different parameters $\statparam^n$. There are then fixed during the training of the recurrent models.
+For $\classifier$ and $\predictor$, we built an architecture summaryse in Figure~\ref{fig:rnnarchi}.
+There are both composed of 3 LSTM layer and a different final Dense layer to provide the correct output.
+After the $\classifier$ final dense layer, we add a sigmoid activation to return a probability.
+We use 2 Adam otpimizers with the same learning rate equal to 0.001 and we fix the batch size at 64.
+At the end, we use the eval set to fix the $\threshold$ parameter of the $classifier$.
+
+We propose two versions of our regime switching hybrid recurrent model.
+The first one is an hybrid model with an additive exponential smoothing model as parametric model.For the second one, we use the TBATS approach as paramteric model.
 
@@
 Thereby, we propose with this paper, a new version of the hybrid framework, including the original multiplicative model and the new additive one.
-Our code is developed in Python using the Tensorflow library and it allows the use of a GPU to speed up the training process contrary to other methods \textcolor{red}{\cite{} developed for the M4 competition}.
+%Our code is developed in Python using the Tensorflow library and it allows the use of a GPU to speed up the training process contrary to other methods \textcolor{red}{\cite{} developed for the M4 competition}.
 In addition, our approach offers the possibility of providing forecasts for a totally  new collection of sequences without retraining the entire hybrid model.
@@
 
-\textcolor{red}{Detail here or in the appendix the training details: number of samples, optimizers, learning rates, etc.}
+%\textcolor{red}{Detail here or in the appendix the training details: number of samples, optimizers, learning rates, etc.}
 
-\vspace{.2cm}
+%\vspace{.2cm}
 
-\textcolor{red}{Detail Train/test split.}
+%\textcolor{red}{Detail Train/test split.}
 
@@
 As benchmarks, we chose several well-known statistical methods and deep learning approaches.
-Using the R package {\em forecast}, we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
+Using the R package {\em forecast} and the Python packages {\em statsmodels, tbats} , we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
 \textit{Snaive} forecasts are only the repetition of the last same past period.
+\textit{ets} model is an additive exponential smoothing with a level component and a seasonal component.
 \textit{stlm} approach use a multiplicative decomposition and models the seasonality adjusted time series with an exponenantial smoothing model.
@@
 \textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization.
-The last one \textit{auto.arima} is the R implementation of ARIMA model with an automatic selection of the best parameters \textcolor{red}{add a reference for these models (paper or R package help section)}.
-We also considered a Long-Short Term Memory (\textit{lstm}) neural network.
-%Against these models, we propose two versions of the hybrid approach without the external weak signal.
-The first one is the original multiplicative form of the hybrid model that we name \textit{hybrid-mul}.
-The second one is the additive variant described in Section~\ref{sec:hybrid} and we named it \textit{hybrid-add}.
-To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}). 
-Finally, we evaluate the model with  inclusion of external signals referred to as \textit{hybrid-add-ws} \textcolor{red}{together with a multiplicative version described in Appendix~\ref{}}.
-In order to provide fair comparisons, we also include a \textit{lstm} with inclusion of weak signals, referred to as \textit{lstm-ws}.
+The last one \textit{auto.arima} is the R implementation of ARIMA model with an automatic selection of the best parameters.
+A complete description and references for these models can be found in \citep{packageforecast}.
+As a deep learning approach, we considered a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52.
 
-To compare the different methods, we use the same metrics as in the M4 competition: the Mean Absolute Scaled Error (mase), the Symmetric Mean Absolute Percentage Error (smape) and the final M4 competition metric, the Overall Weighted Average (owa) of the smape and the mase defined as follows:
+Against these models, we propose our two versions of our regime switching hybrid reccurent model (rshm) called respectively \textit{rshm-ets} and \textit{rshm-tbats} according to the per-time-series model choice.
+%Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}.
+The first one, that we name \textit{rshm-ets}, is the hybrid model with an additive exponential smoothing model as parametric model.
+For the second one, we use the TBATS approach as paramteric model and we named it \textit{rshm-tbats}.
+%To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}). 
+Finally, we evaluate our hybrid framework with the inclusion of external signals referred to as \textit{rshm-ets-ws} and \textit{rshm-tbats-ws}.
+In order to provide a fair comparison, we also train a \textit{lstm} with the weak signals, referred to as \textit{lstm-ws}.
+
+To compare the different methods, we use the same metrics as in the M4 competition: the Mean Absolute Scaled Error (MASE), the Symmetric Mean Absolute Percentage Error (sMAPE) and the final M4 competition metric, the Overall Weighted Average (OWA) of the sMAPE and the MASE defined as follows:
 \begin{align*}
-\mathrm{mase} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,\\
-\mathrm{smape} &= \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}\,,\\
-\mathrm{owa} &= \frac{1}{2}\left(\frac{mase}{mase_{snaive}} + \frac{smape}{smape_{snaive}}\right)\,,
+\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,\\
+\mathrm{sMAPE} &= \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}\,,\\
+\mathrm{OWA} &= \frac{1}{2}\left(MASE/MASE_{snaive} + sMAPE/sMAPE_{snaive}\right)\,,
 \end{align*}
-\textcolor{red}{where $\mathrm{smape_{snaive}}$ and $\mathrm{mase_{snaive}}$ are}.
 
-\subsection{Results for XXX Dataset}
-\textcolor{red}{If possible, a few results of the hybrid approach without weak signals on a dataset other than Heuritech.}
+where $\hat{Y}$ is a model prediction, $\lag$ is the horizon, $m$ the seasonality and $MASE_{snaive}$ is the $MASE$ computed with the $snaive$ model prediction, idem for the $sMAPE_{snaive}$.
+
+Detecting emerging and declining trends is a crucial issue for the fashion industry.
+A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes.
+In a given year, we define an increasing trend as a trend that do more than 10\% of growth in term of Year and Year.In the same way, we define a decreasing trend as a trend that decline of 10\% or more.
+We classify the other trend as flat trend.
+On the test set, the year 2019, we have 1871 increasing trends, 2016 decreasing trends and 6113 flat trends.
+In addition to the accuracy metrics, we compare also the different methods on this classification task.
+
+%As detecting emerging and declining trends is a fondamental issue that is facing the fashion industry, we evaluate also the different methods on this task.
+In a given year, we define an increasing trend as a trend that do more than 10\% of growth in term of Year and Year.A decreasing trend is a trend that decline of -10\% or more.
+We classify the other trend as flat trend.
+On the test set, the year 2019, we have 1871 increasing trends, 2016 decreasing trends and 6113 flat trends.
+We evaluate all the methods on this classification task.
+
+%\textcolor{red}{where $\mathrm{smape_{snaive}}$ and $\mathrm{mase_{snaive}}$ are}.
+
+%\subsection{Results for XXX Dataset}
+%\textcolor{red}{If possible, a few results of the hybrid approach without weak signals on a dataset other than Heuritech.}
 
@@
 
-\vspace{.2cm}
+%\vspace{.2cm}
 
@@
 \appendix
-\section{Appendix}
+
+\section{Fashion Dataset overview}
+\section{Hidden regime algorithm}
+
+In our framework, we assume that our sequence are generated with a regime with 2 hidden regime.
+As this regime, noted $\hiddenregime$, is never observed, we can compute explicitely the following quantity :
+%$p(\ts^n_{T+1:T+h}|\ts^n_{1:T})$
+
+%Based on the Expectation-Maximization (EM) algorithm and the Fisher's identity, we write a new algorithm to estimate jointly $\theta = \{\theta_p,\theta_c\}$, the weights of RNN-p and of RNN-c.
+
+%During our training, we note $\theta^{(t)}$ the value of $\theta$ at an epoch $t$.
+
+%\begin{equation}
+%\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h}\right]\,,
+%\end{equation}
+
+\section{}
 

### 2021-09-30 iclr2022/hybridmodel_iclr.tex
Add some figures

@@
 \newcommand{\stat}{f}
-\newcommand{\statparam}{\Theta}
+\newcommand{\statparam}{\theta_{stat}}
 \newcommand{\fullstat}{{\bf \stat}}
@@
 \newcommand{\classifier}{RNN_c}
+\newcommand{\rnnparam}{\theta}
 \newcommand{\remainder}{r}
@@
 In the regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence.
+the final forecast of our framework is the prediction of the per-time-series parametric model.
 Conversely, in the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainder$.
@@
 As $\hiddenregime$ is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
-Therefore we use Fisher's identity to compute the score function and write a gradient ascent algorithm to estimate simultaneously the weights of RNN-p and of RNN-c denoted by $\theta = \{\theta_p,\theta_c\}$.
+Therefore we use Fisher's identity to compute the score function and write a gradient ascent algorithm to estimate simultaneously the weights of RNN-p and of RNN-c denoted by $\rnnparam = \{\rnnparam_c,\rnnparam_p\}$.
 The score is
@@
 Aggregating detected clothes by trends, we create for the first time thousand of time series representing fashion trends life on social media.
-Our sequences have all 261 time steps, from 2015-01-05 to 2020-09-01 with weekly values and no missing walues.
+Our sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing walues.
 Each time series is normalized in order to remove social networks biases and their values lie between 0 and 1.
@@
     \hline
-     United States & 587/290 & 195/158  & 64/37 & 38/- & 38/- & 271/218 & 439/114 & 59/59 & 129/103\\
-     Europe & 587/290 &  195/158& 64/37 & 38/- & 38/- & 271/218 & 439/114 & 59/59 & 135/111\\
-     Japan &  587/290 & 193/158 & 64/37 & 38/- &  37/- & 271/218 &  429/114 & 59/59 &  124/98\\
-     China &  586/290 & 195/158 & 64/37 & 38/- &  37/- & 271/218 &  433/114 & 59/59 &  128/113\\
-     Brazil &  587/290 & 195/158 & 64/37 & 38/- &  38/- & 271/218 & 439/114 & 59/59 & 136/110\\
+United States & 411/208 & 149/112 & 47/22 & 29/- & 20/- & 208/151 & 293/86 & 38/44 & 85/81\\
+     Europe & 409/228 &  134/114 & 48/21 & 28/- & 20/- & 211/159 & 303/78 & 41/42 & 87/74\\
+     Japan &  403/218 & 136/107 & 49/31 & 28/- &  23/- & 185/149 &  311/78 & 46/42 &  92/65\\
+     China &  424/202 & 147/114 & 46/29 & 27/- &  27/- & 178/161 &  310/78 & 41/47 &  88/77\\
+     Brazil &  431/222 & 134/117 & 49/27 & 30/- &  28/- & 203/152 & 311/76 & 48/41 & 107/84\\
      \hline
-     Total & 2934/1450 & 973/790 & 320/185 & 190/- & 188/- & 1355/1090 & 2179/570 & 295/294 & 652/535 & \numberts\\
+     Total & 2078/1078 & 700/564 & 239/130 & 142/- & 118/- & 985/772 & 1528/396 & 214/216 & 459/381 & \numberts\\
     \hline
@@
   \centering
-    \includegraphics[width=1.\linewidth]{figure/good_example.png}
+    \includegraphics[width=1.\linewidth]{figure/emergering_trend.png}
   \caption{A shoes trend of our dataset.
@@
 We train our hyrid model to compute a one-year ahead prediction with $\window$ and $\lag$ equal to 52.
-In order to increase our train set, we use a moving window as in Figure~\ref{fig:movingwindow}.
+In order to increase our train set, we use a moving window as in Figure~\ref{fig:train_eval_test_set}.
 All our code is developed in Python using the Tensorflow library.
@@
 The first one is an hybrid model with an additive exponential smoothing model as parametric model.For the second one, we use the TBATS approach as paramteric model.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=1.\linewidth]{figure/train_eval_test_set}
+  \caption{$\classifier$ and $\predictor$ architecture.}
+\label{fig:rnn_architecture}
+\end{figure}
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.8\linewidth]{figure/rnn_archi}
+  \caption{$\classifier$ and $\predictor$ architecture.}
+\label{fig:rnn_architecture}
+\end{figure}
 
@@
 
-\textcolor{red}{Add a figure of a time series with all models (and others in Appendix).}
+%\textcolor{red}{Add a figure of a time series with all models (and others in Appendix).}
 
@@
 
-\textcolor{red}{Add a table with the results on the trends classifications used in Heuritech.}
+%\textcolor{red}{Add a table with the results on the trends classifications used in Heuritech.}
 
-In a first place, Table 2 shows the final accuracy of the statistical models, the LSTM model and our 2 hybrid models without external data.
+The Table ??? present the final result for all our methods on the three metrics presented above.
+\begin{itemize}
+	\item For the statistical models, we can see a large domination of the TBATS model with a MASE equal to ...
+It is one of the main reason why we use this model on one of our hybrid framwork as the parametric model.
+However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmarck candidates.
+This result show that, with a large dataset, deep learning model can outperform the traditional approaches on average.
+An example of prediction of all the benchmarck methods is displayed in the Figure ????.
+	\item Our two different regime switching hybrid model achieve higher level of accuracy compare to the \textit{ets} or \textit{tbats} results.
+For the \textit{rshm-ets}, we pass from ???
+for the \textit{ets} model alone to ????
+for the hybrid model.
+Its $\classifier$ threshold $\threshold$ was fix at ???.
+With this threshold, the error-corrector model correct ????
+sequences of the $\numberts$.
+On these corrected time series, compare to the \textit{ets} apporach, our appoach MASE fall from ???
+to ???.
+However \textit{rshm-ets} doesn't succed at outperform some of the benchmarck model, for example \textit{tbats} of \textit{lstm}.
+The \textit{rshm-tbats} version clearly outperform all the previous model.
+Based on a \textit{tbats} model, wich already achieve a interesting level of accuracy, \textit{rshm-tbats} reach the higher level of accuracy with a MASE equal to ????, that is -???
+compare at the top-2 model.
+With a threshold fixed at ???, this version of our hybrid framework correct ???
+sequences of the $\numberts$.
+An example of our two regime-switching hybrid recurrent model is presented in the Figure ....
+\end{itemize}
+
+\begin{table*}
+  \caption{Results summary (Mean/Median) on our Fashion dataset. In a first time, we train our hybrid approaches without our external weak signals.}
+  \label{sample-table}
+  \centering
+  \begin{tabular}{lllllll}
+    \hline
+    &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std  \\
+    \hline
+     \textit{snaive} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
+     \textit{ets} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
+     \textit{thetam} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
+     \textit{stlm} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
+     \textit{tbats} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
+     \textit{auto.arima} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
+     \textit{lstm} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
+     \textit{rshm-ets} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
+     \textit{\textbf{rshm-tbat}} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
+    \hline
+  \end{tabular}
+\end{table*}
+
+%In a first place, Table 2 shows the final accuracy of the statistical models, the LSTM model and our 2 hybrid models without external data.
 Even without the weak signals, our 2 hybrid approaches largely outperform the statistical references.
@@
 
-In a second place, Table 3 shows the evaluation of our 4 trained hybrid models: the 2 previous ones without weak signals, and our 2 full hybrid models with weak signals.
+%In a second place, Table 3 shows the evaluation of our 4 trained hybrid models: the 2 previous ones without weak signals, and our 2 full hybrid models with weak signals.
 We present also the accuracy of a simple LSTM model with and without weak signals.
@@
 
-In a third place, table 4 presents the result of our inference process.
+%In a third place, table 4 presents the result of our inference process.
 We split our dataset in five equal parts of 2800 sequences and hide the last year for each trends.
@@
 
-Finally, with our results, we can make two interesting conclusions: 
-\begin{itemize}
-    \item Firstly, the hybird modeling is a really promising framework.
+With our results, we can make two interesting conclusions.
+Firstly, the regime switching hybrid framework is a really promising framework.
 By mixing the performance of local parametric models and a global DNN, our two versions clearly outperform traditional statistical methods.
@@
 With a fine pre-processing and a well-designed architecture, our two models succeed at leveraging our complex extra data and reach an impressive accuracy levels.
-    \item Secondly, our results bring to light the quality of our new Fashion dataset.
-Even without weak signal, our DNN based model outperforms time series specific model.
+Secondly, our results bring to light the quality of our new Fashion dataset.
+We saw that the full LSTM model \textit{lstm} outperforms all time series specific models.
 This show that our dataset is well suited to train complex neural network architectures able to learn information cross sequences.
@@
 By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting.
-\end{itemize}
 
@@
 
-\begin{table*}
-  \caption{Results summary (Mean/Median) on our Fashion dataset. In a first time, we train our hybrid approaches without our external weak signals.}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{lllllll}
-    \hline
-    &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std  \\
-    \hline
-     snaive & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
-     thetam & 0.924/0.869  & 0.35 & 25.82/22.54  & 14.6 & 0.952/0.915 & 0.26\\
-     stlm & 0.893/0.834 & 0.35 & 25.07/21.93  & 14.3 & 0.917/0.895 & 0.21\\
-     tbats & 0.886/0.822  & 0.34 &  24.81/21.60 & 14.0 &  0.910/0.882 & 0.22 \\
-     lstm & 0.881/0.824 & 0.34 & 24.41/21.56 & 12.81 & 0.895/0.885 & 0.11 \\
-     hybrid-add & 0.863/0.812  & 0.32 & 24.17/21.36 & 13.0 & 0.877/0.880 & 0.08 \\
-     hybrid-mul & 0.858/0.817 & 0.30 & 24.06/21.30 & 13.0 & 0.876/0.873 & 0.11 \\
-     Ensembling & 0.846/0.804 & 0.30 & 23.78/21.07 & 12.9 & 0.864/0.863 & 0.10  \\
-    \hline
-  \end{tabular}
-\end{table*}
+%\begin{table*}
+ % \caption{Comparison between our hybrid models without and with our external weak signals, (Mean/Median)}
+  %\label{sample-table}
+  %\centering
+  %\begin{tabular}{lllllll}
+   % \hline
+    %&  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std \\
+    %\hline
+    %lstm & 0.881/0.824 & 0.34 & 24.41/21.56 & 12.81 & 0.895/0.885 & 0.11 \\
+    %lstm-ws & 0.869/0.814 & 0.33 & 24.56/21.33 & 14.40 & 0.890/0.874 & 0.132 \\
+    % hybrid-add & 0.863/0.812  & 0.32 & 24.17/21.36 & 13.0 & 0.877/0.880 & 0.08 \\
+     %hybrid-mul & 0.858/0.817 & 0.30 & 24.06/21.30 & 13.0 & 0.876/0.873 & 0.11 \\
+  %   hybrid-add-ws & 0.852/0.807 & 0.30 & 24.03/21.17 & 13.0 & 0.872/0.869 & 0.10 \\
+%     hybrid-mul-ws & 0.836/0.798 & 0.29 & 23.67/20.87 & 12.9 & 0.860/0.858 & 0.12 \\
+ %    Ensembling & 0.827/0.787 & 0.29 & 23.43/20.63 & 12.8 & 0.849/0.849 & 0.11\\
+  %  \hline
+  %\end{tabular}
+%\end{table*}
 
-\begin{table*}
-  \caption{Comparison between our hybrid models without and with our external weak signals, (Mean/Median)}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{lllllll}
-    \hline
-    &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std \\
-    \hline
-    lstm & 0.881/0.824 & 0.34 & 24.41/21.56 & 12.81 & 0.895/0.885 & 0.11 \\
-    lstm-ws & 0.869/0.814 & 0.33 & 24.56/21.33 & 14.40 & 0.890/0.874 & 0.132 \\
-     hybrid-add & 0.863/0.812  & 0.32 & 24.17/21.36 & 13.0 & 0.877/0.880 & 0.08 \\
-     hybrid-mul & 0.858/0.817 & 0.30 & 24.06/21.30 & 13.0 & 0.876/0.873 & 0.11 \\
-     hybrid-add-ws & 0.852/0.807 & 0.30 & 24.03/21.17 & 13.0 & 0.872/0.869 & 0.10 \\
-     hybrid-mul-ws & 0.836/0.798 & 0.29 & 23.67/20.87 & 12.9 & 0.860/0.858 & 0.12 \\
-     Ensembling & 0.827/0.787 & 0.29 & 23.43/20.63 & 12.8 & 0.849/0.849 & 0.11\\
-    \hline
-  \end{tabular}
-\end{table*}
-
-\begin{table*}
-  \caption{Cross-Validation.
+%\begin{table*}
+ % \caption{Cross-Validation.
 we split our dataset in 5 equal parts.
 We train for each hybrid approach, 5 models on 4 specific parts of the dataset and we test them of the remaining parts with our inference process.}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{lllllll}
-    \hline
-    &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std \\
-    \hline
-     hybrid-add & 0.861  & 0.004 & 24.16 & 0.18 & 0.877 & 0.002 \\
-     hybrid-mul & 0.856 & 0.008 & 23.95 & 0.25 & 0.870 & 0.005 \\
-     hybrid-add-ws & 0.848 & 0.004 & 24.00 & 0.18 & 0.869 & 0.002 \\
-     hybrid-mul-ws & 0.844 & 0.010 & 23.74 & .20 & 0.863 & 0.006 \\
-    \hline
-  \end{tabular}
-\end{table*}
+  %\label{sample-table}
+  %\centering
+ % \begin{tabular}{lllllll}
+  %  \hline
+   % &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std \\
+   % \hline
+   %  hybrid-add & 0.861  & 0.004 & 24.16 & 0.18 & 0.877 & 0.002 \\
+   %  hybrid-mul & 0.856 & 0.008 & 23.95 & 0.25 & 0.870 & 0.005 \\
+   %  hybrid-add-ws & 0.848 & 0.004 & 24.00 & 0.18 & 0.869 & 0.002 \\
+   %  hybrid-mul-ws & 0.844 & 0.010 & 23.74 & .20 & 0.863 & 0.006 \\
+   % \hline
+  %\end{tabular}
+%\end{table*}
 
@@
 \section{Fashion Dataset overview}
+
 \section{Hidden regime algorithm}

### 2021-10-01 iclr2022/hybridmodel_iclr.tex
a few corrections

@@
 \label{sec:hybrid}
-We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global RNN.
+%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global RNN.
 We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
-Then, we use 2 recurrent neural networks and weak signals to correct the predictions provided by the first collection of parametric models.
+We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of 2 RNN.
+We use a per time series statistical model to learn local behaviour, to normalize sequences and to compute a first forecast.
+Then, we use 2 recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
 
@@
 The time-series-specific models compute, for each sequence, a first $\lag$-ahead prediction based on the past.
-For all $1\leqslant n \leqslant N$, we note $\stat^n$ the $n$-th parametric model linked to the $n$-th sequence.
-Each model gather a collection of parameters in order to provide a forecast.
-We note $\statparam^n$ the parameters of the statistical model $\stat^n$.
-Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$, the parametric models, $\{\stat^n\}_{1\leqslant n \leqslant N}$ and the associated paramters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the first time-series-specific forecasts $\{\tspred^{stat,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+For all $1\leqslant n \leqslant N$, we note $\stat^n$ the $n$-th parametric model linked to the $n$-th sequence and $\statparam^n$ its parameters.
+Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$, the parametric models $\{\stat^n\}_{1\leqslant n \leqslant N}$ and its associated parameters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the time-series-specific forecasts $\{\tspred^{stat,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
 $$
@@
 We train the classifier to provide a probability of being in the regime 1 and we train the predictor to estimate the first per-time-series forecasts errors if we are in the regime 1.
-However, these tasks require a thorough data pre-processing and with our collection of parametric models, we propose a fine way to normalize and deseasonalize the RNNs inputs.
+However, these 2 tasks require a thorough data pre-processing and with our collection of parametric models, we propose a fine way to normalize and deseasonalize the RNNs inputs.
 
@@
 \end{equation}
-The complete architecture is displayed in Figure~\ref{fig:architecture}.
+An illustration of our proposed architecture is displayed in Figure~\ref{fig:architecture}.
 
@@
 A large part of our time series are quite stable, their seasons and evolutions are regular.
-However, some sequences show interesting behaviours with huge changes.
+However, some sequences show interesting behaviours with sudden changes.
 We call them emerging or declining trends depending of the change direction.
-One central point is to accurately detect and forecast these trends.
+A central point of our work is to accurately detect and forecast these trends.
+
+%With only the historical data, predict this breaking point is challenging and some time impossible.
+
+%a large part of this One central point is to accurately detect and forecast these trends.
 
@@
 We train our hyrid model to compute a one-year ahead prediction with $\window$ and $\lag$ equal to 52.
-In order to increase our train set, we use a moving window as in Figure~\ref{fig:train_eval_test_set}.
+In order to increase our train set, we use a moving window that provide 53 input/output couples per sequences, being 530000 couples in total.
+An example of our splitting is shown in  Figure~\ref{fig:train_eval_test_set}.
 All our code is developed in Python using the Tensorflow library.
@@
 After the $\classifier$ final dense layer, we add a sigmoid activation to return a probability.
-We use 2 Adam otpimizers with the same learning rate equal to 0.001 and we fix the batch size at 64.
-At the end, we use the eval set to fix the $\threshold$ parameter of the $classifier$.
+We use 2 Adam otpimizers with the same learning rate equal to ???
+and we fix the batch size at 64.
+At the end, we use the eval set to fix the $\threshold$ parameter that determine, depending of the output of $\predictor$, when use the $\predictor$ correction.
 
 We propose two versions of our regime switching hybrid recurrent model.
-The first one is an hybrid model with an additive exponential smoothing model as parametric model.For the second one, we use the TBATS approach as paramteric model.
+The first one is an hybrid model with an additive exponential smoothing model as the reference.
+For the second one, we use the TBATS approach as the reference.
 
@@
   \caption{$\classifier$ and $\predictor$ architecture.}
-\label{fig:rnn_architecture}
+\label{fig:train_eval_test_set}
 \end{figure}
@@
 As benchmarks, we chose several well-known statistical methods and deep learning approaches.
-Using the R package {\em forecast} and the Python packages {\em statsmodels, tbats} , we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
-\textit{Snaive} forecasts are only the repetition of the last same past period.
+Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels, tbats} , we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
+\textit{snaive} forecasts are only the repetition of the last same past period.
 \textit{ets} model is an additive exponential smoothing with a level component and a seasonal component.
@@
 
-Against these models, we propose our two versions of our regime switching hybrid reccurent model (rshm) called respectively \textit{rshm-ets} and \textit{rshm-tbats} according to the per-time-series model choice.
+Against these models, we propose our two versions of our regime switching hybrid reccurent model (rshm) called respectively rshm-ets and rshm-tbats according to the per-time-series model choice.
 %Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}.
@@
 %To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}). 
-Finally, we evaluate our hybrid framework with the inclusion of external signals referred to as \textit{rshm-ets-ws} and \textit{rshm-tbats-ws}.
-In order to provide a fair comparison, we also train a \textit{lstm} with the weak signals, referred to as \textit{lstm-ws}.
+For our two versions, in a first time, we propose a version without our weak signal called \textit{rshm-ets} and \textit{rshm-tbats}.
+Then we evaluate our hybrid framework with the inclusion of our weak signals (ws) referred to as \textit{rshm-ets-ws} and \textit{rshm-tbats-ws}.
+In order to provide a fair comparison, we also train a \textit{lstm} with the weak signals named \textit{lstm-ws}.
 
@@
 In a given year, we define an increasing trend as a trend that do more than 10\% of growth in term of Year and Year.In the same way, we define a decreasing trend as a trend that decline of 10\% or more.
-We classify the other trend as flat trend.
+We classify other trends as flat trends.
 On the test set, the year 2019, we have 1871 increasing trends, 2016 decreasing trends and 6113 flat trends.

### 2021-10-01 iclr2022/hybridmodel_iclr.tex
Updated bilbio and introduction

@@
 Strong consistency results were established in \citep{touron2019consistency} and Expectation Maximization based numerical experiments were proposed.
-Altough these works provide promising results, HMM are computationally expensive to train and are not yet well studied for sequences with thousands of components with a seasonal behavior \textcolor{blue}{with thousands of components or with a seasonal behavior ?}.
+Altough these works provide promising results, HMM are computationally expensive to train and are not yet well studied for seasonal  sequences with thousands of components.
 
@@
 We call them weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal.
-With this totally new application, we aim at showing a model able to deal with our large fashion dataset, leverage our complex external weak signals and finally provide the most accurate forecasts.
+With this totally new application, we aim at designing a model able to deal with our large fashion dataset, leverage our complex external weak signals and finally provide the most accurate forecasts.
 
-Recurrent neural network seems to be the perfect candidate to tackle our forecasting problem due to their capability of leveraging external data.
+Recurrent neural network are appealing to tackle our forecasting problem due to their capability of leveraging external data.
 Recently, hybrid models combining DNN architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \citep{zhang2003time,jianwei2019novel,bandara2020lstm}.
@@
 %With this process, the hybrid approach succeeds at mixing strengths of both model families: robustness of the time series specific parametric models and the power of neural network at learn complex dynamics on large dataset.
-However, the hybrid model has not been designed to deal with external signals even if it include a neural network.
+%However, the hybrid model has not been designed to deal with external signals even if it include a neural network.
 

### 2021-10-01 iclr2022/hybridmodel_iclr.tex
Updated Sections 2.1 to 2.3

@@
 \newcommand{\threshold}{\eta}
-\newcommand{\predictor}{RNN_p}
-\newcommand{\classifier}{RNN_c}
+\newcommand{\predictor}{\mathrm{RNN}_p}
+\newcommand{\classifier}{\mathrm{RNN}_c}
 \newcommand{\rnnparam}{\theta}
@@
 We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
-We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of 2 RNN.
-We use a per time series statistical model to learn local behaviour, to normalize sequences and to compute a first forecast.
-Then, we use 2 recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
+We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of two RNN.
+We use a per time series statistical model to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
+Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
 
@@
 The time-series-specific models compute, for each sequence, a first $\lag$-ahead prediction based on the past.
-For all $1\leqslant n \leqslant N$, we note $\stat^n$ the $n$-th parametric model linked to the $n$-th sequence and $\statparam^n$ its parameters.
-Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$, the parametric models $\{\stat^n\}_{1\leqslant n \leqslant N}$ and its associated parameters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the time-series-specific forecasts $\{\tspred^{stat,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+For all $1\leqslant n \leqslant N$, we note $\stat^n_{\statparam^n}$ the $n$-th parametric model of the the $n$-th sequence where $\statparam^n$ are  unknown parameters.
+Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$ and the estimated  parameters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the time-series-specific forecasts $\{\tspred^{stat,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
 $$
-\tspred^{stat,n}_{T+i|T} = \stat^n(\ts^n_{1:T}|\statparam^n)_i\,,
+\tspred^{stat,n}_{T+i|T} = \stat^n_{\statparam^n}(\ts^n_{1:T})_i\,.
 $$
 
-During the M4 competition, the hybrid model's author based his framework on a multiplicative exponential smoothing model as the time-series-specific model.
+During the M4 competition, the hybrid model of \cite{} is based on a multiplicative exponential smoothing model as the time-series-specific model.
 However, on sporadic time series, this choice could lead to poor result and instability.
 In our approach, we decided to go deeper and provide a general framework able to deal with any kind of per-time-series models.
-In the Section~\ref{sec:exp}, we present two versions of our framework.
-The first one use an additive exponential smoothing as reference and the second one use a TBATS model as reference.
-At the end, The main complexity is in the next stage: succeed in training a global RNN to understand all the per-time-series statistical models and correct their mistakes if needed.
+In Section~\ref{sec:exp}, we present two versions of our framework.
+The first one use an  exponential smoothing as reference  similar to \cite{} and the second one use a TBATS model \cite{} which provides better results.
+The main complexity is in the next stage: training a global RNN to correct the per-time-series statistical models when the statistical models provide poor performance.
 % Indeed, depending on time series, some family of parametric models can achieve really heterogeneous level of accuracy. 
@@
 %$$
-At this stage, we assume that we have two different regimes.
-In the regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence.
-the final forecast of our framework is the prediction of the per-time-series parametric model.
-Conversely, in the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainder$.
-Our regime-switching system is then :
+In this paper, we introduce a model based on a latent regime.
+In regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence and the final forecast of our framework is the prediction of the per-time-series parametric model.
+Conversely, in regime 1, the first parametric forecast is unaccurate and it remains a residual random error term that can be estimated.
+% quantity that we note $\remainder$.
+Conditionally on $\{\fullts^n\}_{1\leqslant n\leqslant N}$, our regime-switching model is:
 
 $$
-\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \hiddenregime^n_T * \remainder^{n}_{T+i} + \varepsilon^n_{T+i}\,,
+\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \hiddenregime^n_T \cdot \remainder^{n}_{T+i} + \varepsilon^n_{T+i} = \stat^n_{\statparam^n}(\ts^n_{1:T})_i + \hiddenregime^n_T \cdot \remainder^{n}_{T+i} + \varepsilon^n_{T+i}\,,
 $$
-where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent random variables, $\{\remainder^n_{T+i}\}_{i\leqslant 1}$ are non null remainders and $U^n_T$ an unobserved regime switching Bernoulli random variable.
+where $\{\varepsilon^n_{T+i}\}_{1\leqslant i\leqslant \lag}$ are independent random variables, $U^n_T$ is an unobserved regime switching Bernoulli random variable and $\{\remainder^n_{T+i}\}_{1\leqslant i\leqslant \lag}$ is the random error term to be estimated.
 %In the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainder$.
@@
 
-To estimate this system, we introduce our new regime swithing error-corrector framework.
+To estimate this model, we introduce our new regime swithing error-corrector framework.
 We train two global RNN on all sequences, a classifier ($\classifier$) and a predictor ($\predictor$).
-We train the classifier to provide a probability of being in the regime 1 and we train the predictor to estimate the first per-time-series forecasts errors if we are in the regime 1.
-However, these 2 tasks require a thorough data pre-processing and with our collection of parametric models, we propose a fine way to normalize and deseasonalize the RNNs inputs.
+We train the classifier to estimate the law of the Bernoulli random variable $\hiddenregime^n_T$ we train the predictor to predict $\{\remainder^{n}_{T+i}\}_{1\leqslant i\leqslant \lag}$.
+However, these two tasks require a thorough data pre-processing and with our collection of parametric models, we propose first to normalize and deseasonalize the RNNs inputs.
 
@@
 where $ \meants^n_T = \sum_{i = 1}^{w}  \ts^n_{T-w+i}/w$.
-We use this sequence as input of our two neural network, $\classifier$ and $\predictor$.
+We use this sequence as input of  $\classifier$ and $\predictor$.
 %Write, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,H\}$, $\err^{n,T}_{T+i|T} = \ts^n_{T+i} - \etspred^{ets,n}_{T+i|T}$.
-
  Given $\rnnwindow^n_T$, the proposed regime swithing error-corrector reccurent model is given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by :
 \begin{align*}
-\ts^n_{T+i}  &= \tspred^{stat,n}_{T-w+i|T-w} +  \hat{\hiddenregime}^n_T * \hat{\remainder}^{n}_{T+i} + \varepsilon^n_{T+i} \\
-\hat{\hiddenregime}^n_T &= \mathbf{1}_{\classifier(\rnnwindow^n_T) > \threshold} \\
-\hat{\remainder}^{n}_{T+i} &= \predictor(\rnnwindow^n_T)_{T+i} \times \meants^n_T
+\ts^n_{T+i}  &= \tspred^{stat,n}_{T-w+i|T-w} +  \hat{\hiddenregime}^n_T * \hat{\remainder}^{n}_{T+i} + \varepsilon^n_{T+i}\,, \\
+\hat{\hiddenregime}^n_T &= \mathbf{1}_{\classifier(\rnnwindow^n_T) > \threshold}\,, \\
+\hat{\remainder}^{n}_{T+i} &= \predictor(\rnnwindow^n_T)_{T+i} \times \meants^n_T\,.
 \end{align*}
 
-where $\mathbf{1}$ is the indicatrice function and $\threshold$ a threshold parameter.\\
+where $\mathbf{1}$ is the indicator function and $\threshold$ a threshold parameter.
 
@@
 Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for our two RNN,
-\begin{align*}
-\fullconcatinput^n_T &= \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}\, \\
-&= \{\rnn^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,
-\end{align*}
-
+$$
+\fullconcatinput^n_T = \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}= \{\rnn^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
+$$
 Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ our final model becomes:
@@
   \centering
-    \includegraphics[width=1.2\linewidth]{figure/Regime_switching_recurrent_model}
+    \includegraphics[width=1\linewidth]{figure/Regime_switching_recurrent_model}
   \caption{Hybrid model with weak signals architecture.}
@@
 
-As $\hiddenregime$ is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
+As the regime is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
 Therefore we use Fisher's identity to compute the score function and write a gradient ascent algorithm to estimate simultaneously the weights of RNN-p and of RNN-c denoted by $\rnnparam = \{\rnnparam_c,\rnnparam_p\}$.

### 2021-10-01 iclr2022/hybridmodel_iclr.tex
Updated Sections 2.4

@@
 \begin{equation}
+\label{eq:score}
 \nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h}\right]\,,
 \end{equation}
-\\
 where the joint likelihood $p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T}) = p_\theta(U_T^n|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$ is given by \eqref{eq:full:model} and the expectation is under the posterior distribution of $U_T^n$ given $\ts^n_{1:T+h}$.
+Write $\omega_p^n = \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T+h})$.
+Note that
+$$
+\omega^n \propto \mathbb{P}_{\theta}(U_T^n = 1|\ts^n_{1:T})p_{\theta}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\,,
+$$
+where $ \mathbb{P}_{\theta}(U_T^n = 1|\ts^n_{1:T})$ is parameterized by $\classifier$ and the predictive probability density $p_{\theta}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})$ is parameterized by $\predictor$ and the statistical model.
+Then, by \eqref{eq:score},
+\begin{multline*}
+\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \omega^n\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})\\
++ (1-\omega^n)\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,.
+\end{multline*}
+The loss function is then given by
+$$
+\theta\mapsto - \omega^n \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})- (1-\omega^n) \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,.
+$$
 A complete description of the training process can be found in Appendix.

### 2021-10-01 iclr2022/hybridmodel_iclr.tex
Updated Section 3

@@
 
-With this paper, we provide the first dataset dedicated to fashion.
-Our fashion dataset is built with a high throughput computer vision systems analysing every day images shared on social networks.
+We provide the first dataset dedicated to fashion trends forecasting.
+Our fashion dataset is built with a high throughput computer vision system analysing every day images shared on social networks.
 Aggregating detected clothes by trends, we create for the first time thousand of time series representing fashion trends life on social media.
@@
 The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
-An overview of it can be found in table 1.
+An overview of it can be found in Table~\ref{sample-table}.
 
-With in-house fashion experts, we selected especially a collection of $\numberts$ fashion trend in order to represent finely the issues that face the fashion industry.
+With in-house fashion experts, we selected especially a collection of $\numberts$ fashion trends in order to represent finely the issues that face the fashion industry.
 A large part of our time series are quite stable, their seasons and evolutions are regular.
@@
 With three thresholds we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high}.
-Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.These extra signals are frequently sparse for micro trends and they often lack of interest for common fashion trends.
+Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.
+These extra signals are frequently sparse for micro trends and they often lack of interest for common fashion trends.
 However on several examples, they are fundamental to detect the future fashion evolution.
@@
 
-\subsection{Example}
+%\subsection{Example}
 
-As an example, an impressive emerging fashion trend is represented in Figure 2, see other examples in Appendix~\ref{}.
+As an example, an impressive emerging fashion trend is represented in Figure~\ref{fig:oneemergingtrend}, see other examples in Appendix~\ref{}.
 It shows the evolution of one shoes trends on social media and its linked \textit{fashion-forward} weak signal.
@@
 In black the main signal and in red its associated \textit{fashion-forward} weak signal.
-The Gap between our two signals in the end of 2017/beginning of 2018 announces the future explosion of the fashion trend.
-\textcolor{red}{Provide other examples in the appendix to hightlight the variety of the proposed data.}}
+The Gap between our two signals in the end of 2017/beginning of 2018 announces the future explosion of the fashion trend.}
+\label{fig:oneemergingtrend}
 \end{figure}

### 2021-10-01 iclr2022/hybridmodel_iclr.tex
add results on 1000ts

--- 2021-10-01 iclr2022/hybridmodel_iclr.tex
@@
 \newcommand{\threshold}{\eta}
-\newcommand{\predictor}{\mathrm{RNN}_p}
-\newcommand{\classifier}{\mathrm{RNN}_c}
+\newcommand{\predictor}{RNN_p}
+\newcommand{\classifier}{RNN_c}
 \newcommand{\rnnparam}{\theta}
@@
 Strong consistency results were established in \citep{touron2019consistency} and Expectation Maximization based numerical experiments were proposed.
-Altough these works provide promising results, HMM are computationally expensive to train and are not yet well studied for seasonal  sequences with thousands of components.
+Altough these works provide promising results, HMM are computationally expensive to train and are not yet well studied for sequences with thousands of components with a seasonal behavior \textcolor{blue}{with thousands of components or with a seasonal behavior ?}.
 
@@
 We call them weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal.
-With this totally new application, we aim at designing a model able to deal with our large fashion dataset, leverage our complex external weak signals and finally provide the most accurate forecasts.
+With this totally new application, we aim at showing a model able to deal with our large fashion dataset, leverage our complex external weak signals and finally provide the most accurate forecasts.
 
-Recurrent neural network are appealing to tackle our forecasting problem due to their capability of leveraging external data.
+Recurrent neural network seems to be the perfect candidate to tackle our forecasting problem due to their capability of leveraging external data.
 Recently, hybrid models combining DNN architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \citep{zhang2003time,jianwei2019novel,bandara2020lstm}.
@@
 %With this process, the hybrid approach succeeds at mixing strengths of both model families: robustness of the time series specific parametric models and the power of neural network at learn complex dynamics on large dataset.
-%However, the hybrid model has not been designed to deal with external signals even if it include a neural network.
+However, the hybrid model has not been designed to deal with external signals even if it include a neural network.
 
@@
 We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
-We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of two RNN.
-We use a per time series statistical model to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
-Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
+We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of 2 RNN.
+We use a per time series statistical model to learn local behaviour, to normalize sequences and to compute a first forecast.
+Then, we use 2 recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
 
@@
 The time-series-specific models compute, for each sequence, a first $\lag$-ahead prediction based on the past.
-For all $1\leqslant n \leqslant N$, we note $\stat^n_{\statparam^n}$ the $n$-th parametric model of the the $n$-th sequence where $\statparam^n$ are  unknown parameters.
-Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$ and the estimated  parameters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the time-series-specific forecasts $\{\tspred^{stat,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+For all $1\leqslant n \leqslant N$, we note $\stat^n$ the $n$-th parametric model linked to the $n$-th sequence and $\statparam^n$ its parameters.
+Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$, the parametric models $\{\stat^n\}_{1\leqslant n \leqslant N}$ and its associated parameters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the time-series-specific forecasts $\{\tspred^{stat,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
 $$
-\tspred^{stat,n}_{T+i|T} = \stat^n_{\statparam^n}(\ts^n_{1:T})_i\,.
+\tspred^{stat,n}_{T+i|T} = \stat^n(\ts^n_{1:T}|\statparam^n)_i\,,
 $$
 
-During the M4 competition, the hybrid model of \cite{} is based on a multiplicative exponential smoothing model as the time-series-specific model.
+During the M4 competition, the hybrid model's author based his framework on a multiplicative exponential smoothing model as the time-series-specific model.
 However, on sporadic time series, this choice could lead to poor result and instability.
 In our approach, we decided to go deeper and provide a general framework able to deal with any kind of per-time-series models.
-In Section~\ref{sec:exp}, we present two versions of our framework.
-The first one use an  exponential smoothing as reference  similar to \cite{} and the second one use a TBATS model \cite{} which provides better results.
-The main complexity is in the next stage: training a global RNN to correct the per-time-series statistical models when the statistical models provide poor performance.
+In the Section~\ref{sec:exp}, we present two versions of our framework.
+The first one use an additive exponential smoothing as reference and the second one use a TBATS model as reference.
+At the end, The main complexity is in the next stage: succeed in training a global RNN to understand all the per-time-series statistical models and correct their mistakes if needed.
 % Indeed, depending on time series, some family of parametric models can achieve really heterogeneous level of accuracy. 
@@
 %$$
-In this paper, we introduce a model based on a latent regime.
-In regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence and the final forecast of our framework is the prediction of the per-time-series parametric model.
-Conversely, in regime 1, the first parametric forecast is unaccurate and it remains a residual random error term that can be estimated.
-% quantity that we note $\remainder$.
-Conditionally on $\{\fullts^n\}_{1\leqslant n\leqslant N}$, our regime-switching model is:
+At this stage, we assume that we have two different regimes.
+In the regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence.
+the final forecast of our framework is the prediction of the per-time-series parametric model.
+Conversely, in the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainder$.
+Our regime-switching system is then :
 
 $$
-\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \hiddenregime^n_T \cdot \remainder^{n}_{T+i} + \varepsilon^n_{T+i} = \stat^n_{\statparam^n}(\ts^n_{1:T})_i + \hiddenregime^n_T \cdot \remainder^{n}_{T+i} + \varepsilon^n_{T+i}\,,
+\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \hiddenregime^n_T * \remainder^{n}_{T+i} + \varepsilon^n_{T+i}\,,
 $$
-where $\{\varepsilon^n_{T+i}\}_{1\leqslant i\leqslant \lag}$ are independent random variables, $U^n_T$ is an unobserved regime switching Bernoulli random variable and $\{\remainder^n_{T+i}\}_{1\leqslant i\leqslant \lag}$ is the random error term to be estimated.
+where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent random variables, $\{\remainder^n_{T+i}\}_{i\leqslant 1}$ are non null remainders and $U^n_T$ an unobserved regime switching Bernoulli random variable.
 %In the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainder$.
@@
 
-To estimate this model, we introduce our new regime swithing error-corrector framework.
+To estimate this system, we introduce our new regime swithing error-corrector framework.
 We train two global RNN on all sequences, a classifier ($\classifier$) and a predictor ($\predictor$).
-We train the classifier to estimate the law of the Bernoulli random variable $\hiddenregime^n_T$ we train the predictor to predict $\{\remainder^{n}_{T+i}\}_{1\leqslant i\leqslant \lag}$.
-However, these two tasks require a thorough data pre-processing and with our collection of parametric models, we propose first to normalize and deseasonalize the RNNs inputs.
+We train the classifier to provide a probability of being in the regime 1 and we train the predictor to estimate the first per-time-series forecasts errors if we are in the regime 1.
+However, these 2 tasks require a thorough data pre-processing and with our collection of parametric models, we propose a fine way to normalize and deseasonalize the RNNs inputs.
 
@@
 where $ \meants^n_T = \sum_{i = 1}^{w}  \ts^n_{T-w+i}/w$.
-We use this sequence as input of  $\classifier$ and $\predictor$.
+We use this sequence as input of our two neural network, $\classifier$ and $\predictor$.
 %Write, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,H\}$, $\err^{n,T}_{T+i|T} = \ts^n_{T+i} - \etspred^{ets,n}_{T+i|T}$.
+
 Given $\rnnwindow^n_T$, the proposed regime swithing error-corrector reccurent model is given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by :
 \begin{align*}
-\ts^n_{T+i}  &= \tspred^{stat,n}_{T-w+i|T-w} +  \hat{\hiddenregime}^n_T * \hat{\remainder}^{n}_{T+i} + \varepsilon^n_{T+i}\,, \\
-\hat{\hiddenregime}^n_T &= \mathbf{1}_{\classifier(\rnnwindow^n_T) > \threshold}\,, \\
-\hat{\remainder}^{n}_{T+i} &= \predictor(\rnnwindow^n_T)_{T+i} \times \meants^n_T\,.
+\ts^n_{T+i}  &= \tspred^{stat,n}_{T-w+i|T-w} +  \hat{\hiddenregime}^n_T * \hat{\remainder}^{n}_{T+i} + \varepsilon^n_{T+i} \\
+\hat{\hiddenregime}^n_T &= \mathbf{1}_{\classifier(\rnnwindow^n_T) > \threshold} \\
+\hat{\remainder}^{n}_{T+i} &= \predictor(\rnnwindow^n_T)_{T+i} \times \meants^n_T
 \end{align*}
 
-where $\mathbf{1}$ is the indicator function and $\threshold$ a threshold parameter.
+where $\mathbf{1}$ is the indicatrice function and $\threshold$ a threshold parameter.\\
 
@@
 Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for our two RNN,
-$$
-\fullconcatinput^n_T = \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}= \{\rnn^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
-$$
+\begin{align*}
+\fullconcatinput^n_T &= \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}\, \\
+&= \{\rnn^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,
+\end{align*}
+
 Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ our final model becomes:
@@
   \centering
-    \includegraphics[width=1\linewidth]{figure/Regime_switching_recurrent_model}
+    \includegraphics[width=1.2\linewidth]{figure/Regime_switching_recurrent_model}
   \caption{Hybrid model with weak signals architecture.}
@@
 
-As the regime is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
+As $\hiddenregime$ is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
 Therefore we use Fisher's identity to compute the score function and write a gradient ascent algorithm to estimate simultaneously the weights of RNN-p and of RNN-c denoted by $\rnnparam = \{\rnnparam_c,\rnnparam_p\}$.
@@
 
-The Table ??? present the final result for all our methods on the three metrics presented above.
+\textcolor{blue}{Result on 1000ts}  \\
+\textcolor{blue}{hybrid model correct all time series and not only a a group of hundred. WIP}  \\
+In a first time, we present the accuracy of all our methods without using our weak signals.for our 3 metrics and for each model, we compute the average and standard deviation on all our sequences on the final year.
+Results are shown in the Table ???.
 \begin{itemize}
@@
 \begin{table*}
-  \caption{Results summary (Mean/Median) on our Fashion dataset. In a first time, we train our hybrid approaches without our external weak signals.}
+  \caption{Results summary on our Fashion dataset. For each metric, we compute the average and the standard deviation on all the test set.}
   \label{sample-table}
@@
     \hline
-    &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std  \\
+    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
     \hline
-     \textit{snaive} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
-     \textit{ets} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
-     \textit{thetam} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
-     \textit{stlm} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
-     \textit{tbats} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
-     \textit{auto.arima} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
-     \textit{lstm} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
-     \textit{rshm-ets} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
-     \textit{\textbf{rshm-tbat}} & 0.983/0.936 & 0.33 & 27.68/24.42 & 15.0 & 1./1. & 0.\\
+     \textit{snaive} & 0.871 & 0.255 & 25.29 & 14.90 & 1. & 0.\\
+     \textit{ets} & 0.801 & 0.274 & 24.18 & 17.51 & 0.944 & 0.286\\
+     \textit{thetam} & 0.849 & 0.364 & 24.58 & 17.07 & 0.980 & 0.333\\
+     \textit{stlm} & 0.765 & 0.265 & 22.22 & 13.77 & 0.885 & 0.188\\
+     \textit{tbats} & 0.734 & 0.254 & 21.19 & 13.79 & 0.847 & 0.171\\
+     \textit{auto.arima} & 0. & 0. & . & . & . & 0.\\
+     \textit{lstm} & 0.765 & 0.278 & 21.00 & 11.42 & 0.872 & 0.160\\
+     \textit{rshm-ets} & 0. & 0. & . & . & . & 0.\\
+     \textit{\textbf{rshm-tbats}} & 0.726 & 0.242 & 21.09 & 13.60 & 0.840 & 0.157\\
+     \textit{oracle} & 0.709 & 0.235 & 20.55 & 13.30 & 0.812 & 0.153\\
+    \hline
+  \end{tabular}
+\end{table*}
+
+We also compute for each method a confusion matrix in order to evaluate in what matter, each candidate is able to detect and accurately forecast increasing/decreasing trends.
+
+\begin{table*}
+  \caption{\textit{tbats} model confusion matrix}
+  \label{sample-table}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 33 & 167 & 8 \\
+    true-flat-trend & 21 & 578 & 22 \\
+    true-inc-trend & 7 & 136 & 28 \\
+    \hline
+  \end{tabular}
+\end{table*}
+
+\begin{table*}
+  \caption{\textit{ets} model confusion matrix}
+  \label{sample-table}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 43 & 145 & 20 \\
+    true-flat-trend & 43 & 544 & 34 \\
+    true-inc-trend & 16 & 122 & 33 \\
+    \hline
+  \end{tabular}
+\end{table*}
+\begin{table*}
+  \caption{\textit{lstm} model confusion matrix}
+  \label{sample-table}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 0 & 208 & 0 \\
+    true-flat-trend & 0 & 621 & 0 \\
+    true-inc-trend & 0 & 171 & 0 \\
+    \hline
+  \end{tabular}
+\end{table*}
+\begin{table*}
+  \caption{\textit{rshm-tbats} model confusion matrix}
+  \label{sample-table}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 33 & 166 & 9 \\
+    true-flat-trend & 13 & 596 & 12 \\
+    true-inc-trend & 7 & 139 & 25 \\
+    \hline
+  \end{tabular}
+\end{table*}
+
+In a seconde time, we evaluate how our framework is able to understand and leverage our weak signals.
+The Table ???
+presents the result of our three candidates that we train with our weak signals : \textit{lstm-ws}, \textit{rshm-ets-ws} and \textit{rshm-tbats-ws}.
+
+\begin{table*}
+  \caption{Results summary on our Fashion dataset. We compare methods without our weak signal and than method but train with our weak signals as an additional input}
+  \label{sample-table}
+  \centering
+  \begin{tabular}{lllllll}
+    \hline
+    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
+    \hline
+     \textit{lstm} & 0.765 & 0.278 & 21.00 & 11.42 & 0.872 & 0.160\\
+     \textit{rshm-ets} & 0. & 0. & . & . & . & 0.\\
+     \textit{\textbf{rshm-tbats}} & 0.726 & 0.242 & 21.09 & 13.60 & 0.840 & 0.157\\
+    \hline
+     \textit{lstm-ws} & 0.758 & 0.271 & 20.89 & 11.46 & 0.867 & 0.163\\
+     \textit{rshm-ets-ws} & 0. & 0. & . & . & . & 0.\\
+     \textit{\textbf{rshm-tbats-ws}} & 0. & 0. & . & . & 0. & 0.\\
+    \hline
+  \end{tabular}
+\end{table*}
+
+Again, we show the result of our model with external signal on the classifier task. The Table ???/???/??? present their results.
+
+\begin{table*}
+  \caption{\textit{lstm-ws} model confusion matrix}
+  \label{sample-table}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 1 & 205 & 2 \\
+    true-flat-trend & 2 & 619 & 0 \\
+    true-inc-trend & 0 & 168 & 3 \\
+    \hline
+  \end{tabular}
+\end{table*}
+\begin{table*}
+  \caption{\textit{rshm-ets-ws} model confusion matrix}
+  \label{sample-table}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 0 & 0 & 0 \\
+    true-flat-trend & 0 & 0 & 0 \\
+    true-inc-trend & 0 & 0 & 0 \\
+    \hline
+  \end{tabular}
+\end{table*}
+\begin{table*}
+  \caption{\textit{rshm-tbats-ws} model confusion matrix}
+  \label{sample-table}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 0 & 0 & 9 \\
+    true-flat-trend & 0 & 0 & 0 \\
+    true-inc-trend & 0 & 0 & 0 \\
     \hline

### 2021-10-03 iclr2022/hybridmodel_iclr.tex
A few updates in the experiments

@@
 
-To train our hybrid model, we split our dataset in 3 parts, train,eval and test set.
+To train our hybrid model, we split our dataset into three blocks, train,eval and test sets.
 We use the 3 first years as our train set, we keep the 4th year for our eval set and we hide the last year for our test set.
+Each set is made of weekly time series.
 We train our hyrid model to compute a one-year ahead prediction with $\window$ and $\lag$ equal to 52.
@@
 
-For the first parametric per-time-series models, we used existing Python or R librarys to set the different parameters $\statparam^n$. There are then fixed during the training of the recurrent models.
-For $\classifier$ and $\predictor$, we built an architecture summaryse in Figure~\ref{fig:rnnarchi}.
+For the first parametric per-time-series models, we used existing Python or R librarys to estimate the different parameters $\statparam^n$.
+There are then fixed during the training of the recurrent models.
+The proposed hybrid model introduced in this numerical section is the TBATS model of \cite{XXX}.
+This model is also compared to an hybrid model with an additive exponential smoothing model as a reference close to \cite{XXX}.
+For $\classifier$ and $\predictor$, we built an architecture summarized in Figure~\ref{fig:rnnarchi}.
 There are both composed of 3 LSTM layer and a different final Dense layer to provide the correct output.
@@
 We use 2 Adam otpimizers with the same learning rate equal to ???
-and we fix the batch size at 64.
-At the end, we use the eval set to fix the $\threshold$ parameter that determine, depending of the output of $\predictor$, when use the $\predictor$ correction.
-
-We propose two versions of our regime switching hybrid recurrent model.
-The first one is an hybrid model with an additive exponential smoothing model as the reference.
-For the second one, we use the TBATS approach as the reference.
+and the batch size is  64.
+The eval set is used to fix the $\threshold$ parameter that determine, depending of the output of $\predictor$, when  tuse the $\predictor$ correction.
 
@@
 Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels, tbats} , we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
-\textit{snaive} forecasts are only the repetition of the last same past period.
-\textit{ets} model is an additive exponential smoothing with a level component and a seasonal component.
-\textit{stlm} approach use a multiplicative decomposition and models the seasonality adjusted time series with an exponenantial smoothing model.
-\textit{Thetam} model decompose the original signal in $\theta$-lines, forecast each one separately and recompose them to produce the final forecast.
-\textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization.
-The last one \textit{auto.arima} is the R implementation of ARIMA model with an automatic selection of the best parameters.
+The \textit{snaive} forecasts are only the repetition of the last same past period.
+The \textit{ets} model is an additive exponential smoothing with a level component and a seasonal component.
+The \textit{stlm} approach uses a multiplicative decomposition and models the seasonality adjusted time series with an exponenantial smoothing model.
+The \textit{Thetam} model decomposes the original signal in $\theta$-lines, forecasts each one separately and recomposes them to produce the final forecast and  \textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization.
+Finally,  \textit{auto.arima} is the R implementation of ARIMA model with an automatic selection of the best parameters.
 A complete description and references for these models can be found in \citep{packageforecast}.
@@
 A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes.
-In a given year, we define an increasing trend as a trend that do more than 10\% of growth in term of Year and Year.In the same way, we define a decreasing trend as a trend that decline of 10\% or more.
+In a given year, we define an increasing trend as a trend that does more than 10\% of growth in term of Year and Year.
+In the same way, we define a decreasing trend as a trend that declines of 10\% or more.
 We classify other trends as flat trends.

### 2021-10-03 iclr2022/hybridmodel_iclr.tex
add figs and corrections

--- 2021-10-01 iclr2022/hybridmodel_iclr.tex
@@
 With this paper, we provide the first dataset dedicated to fashion.
-Our fashion dataset is built with a high throughput computer vision systems analysing every day images shared on social networks.
-Aggregating detected clothes by trends, we create for the first time thousand of time series representing fashion trends life on social media.
-Our sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing walues.
+Our fashion dataset is built with a high throughput computer vision system analysing every day images shared on social networks.
+Aggregating detected clothes by trends, we create for the first time thousands of time series representing fashion trends life on social media.
+Our sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
 Each time series is normalized in order to remove social networks biases and their values lie between 0 and 1.
-The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
+The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 different categories and 5 geozones.
 An overview of it can be found in table 1.
 
-With in-house fashion experts, we selected especially a collection of $\numberts$ fashion trend in order to represent finely the issues that face the fashion industry.
+With in-house fashion experts, we selected especially a collection of $\numberts$ fashion trends in order to represent finely the issues that face the fashion industry.
 A large part of our time series are quite stable, their seasons and evolutions are regular.
 However, some sequences show interesting behaviours with sudden changes.
-We call them emerging or declining trends depending of the change direction.
+We call them emerging or declining trends depending on the change in direction.
 A central point of our work is to accurately detect and forecast these trends.
@@
 With this specific panel, we aim at detecting the first waves announcing emerging trends or the collapse of other ones.
-By analyzing images shared by this specific panel on social medias, we create a first weak signal named \textit{fashion-forwards} for each of the previous trends.
-We also analyzed only a specific part of social media users depending of the number of followers.
+By analyzing images shared by this specific panel on social media, we create a first weak signal named \textit{fashion-forwards} for each of the previous trends.
+We also analyzed only a specific part of social media users depending on the number of followers.
 With three thresholds we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high}.
-Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.These extra signals are frequently sparse for micro trends and they often lack of interest for common fashion trends.
-However on several examples, they are fundamental to detect the future fashion evolution.
+Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.These extra signals are frequently sparse for micro trends and they often lack interest in common fashion trends.
+However, in several examples, they are fundamental to detect the future fashion evolution.
 
@@
 As an example, an impressive emerging fashion trend is represented in Figure 2, see other examples in Appendix~\ref{}.
-It shows the evolution of one shoes trends on social media and its linked \textit{fashion-forward} weak signal.
+It shows the evolution of one shoe trend on social media and its linked \textit{fashion-forward} weak signal.
 During the first 3 years, common users and the panel of mode-influencers share the same behaviour.
-The trend start to boom in the mainstream people during the first month of 2018.
+The trend started to boom in the mainstream people during the first month of 2018.
 However, we can detect early signals in the fashion-forward panel at the end of 2017.
-Early adopters started to change there behaviour and show more frequently the trend on social media.
+Early adopters started to change their behaviour and show more frequently the trend on social media.
 With fashion influence dynamics, the new tendency spreads to every part of social media users.
-Finally, after a pick reached at the end of 2018 for the fashion-influencers, a regular decrease appear.
+Finally, after a peak reached at the end of 2018 for the fashion-influencers, a regular decrease appeared.
 %They leave gradually the old trend to focus more on the latest or propose new ones.
@@
 We use the 3 first years as our train set, we keep the 4th year for our eval set and we hide the last year for our test set.
-We train our hyrid model to compute a one-year ahead prediction with $\window$ and $\lag$ equal to 52.
-In order to increase our train set, we use a moving window that provide 53 input/output couples per sequences, being 530000 couples in total.
+We train our hybrid model to compute a one-year ahead prediction with $\window$ and $\lag$ equal to 52.
+In order to increase our train set, we use a moving window that provides 53 input/output couples per sequence, being 530000 couples in total.
 An example of our splitting is shown in  Figure~\ref{fig:train_eval_test_set}.
 All our code is developed in Python using the Tensorflow library.
-It allows the use of a GPU to speed up the trainig process.
+It allows the use of a GPU to speed up the training process.
 
-For the first parametric per-time-series models, we used existing Python or R librarys to set the different parameters $\statparam^n$. There are then fixed during the training of the recurrent models.
+For the first parametric per-time-series models, we used existing Python or R libraries to set the different parameters $\statparam^n$. They are then fixed during the training of the recurrent models.
+
 For $\classifier$ and $\predictor$, we built an architecture summaryse in Figure~\ref{fig:rnnarchi}.
-There are both composed of 3 LSTM layer and a different final Dense layer to provide the correct output.
+They are both composed of 3 LSTM layers and a different final Dense layer to provide the correct output.
 After the $\classifier$ final dense layer, we add a sigmoid activation to return a probability.
-We use 2 Adam otpimizers with the same learning rate equal to ???
-and we fix the batch size at 64.
-At the end, we use the eval set to fix the $\threshold$ parameter that determine, depending of the output of $\predictor$, when use the $\predictor$ correction.
+We use 2 Adam optimizers with the same learning rate equal to $5\times10^{-6}$ and we fix the batch size at 64.
+At the end, we use the eval set to fix the $\threshold$ parameter that determines, depending on the output of $\predictor$, when using the $\predictor$ correction.
 
 We propose two versions of our regime switching hybrid recurrent model.
-The first one is an hybrid model with an additive exponential smoothing model as the reference.
+The first one is a hybrid model with an additive exponential smoothing model as the reference.
 For the second one, we use the TBATS approach as the reference.
@@
 \textit{ets} model is an additive exponential smoothing with a level component and a seasonal component.
-\textit{stlm} approach use a multiplicative decomposition and models the seasonality adjusted time series with an exponenantial smoothing model.
-\textit{Thetam} model decompose the original signal in $\theta$-lines, forecast each one separately and recompose them to produce the final forecast.
+\textit{stlm} approach uses a multiplicative decomposition and models the seasonally adjusted time series with an exponential smoothing model.
+\textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast.
 \textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization.
-The last one \textit{auto.arima} is the R implementation of ARIMA model with an automatic selection of the best parameters.
-A complete description and references for these models can be found in \citep{packageforecast}.
+The last one \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters.
+A complete description and references for these models can be found in \citep{hyndman2020package}.
 As a deep learning approach, we considered a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52.
 
-Against these models, we propose our two versions of our regime switching hybrid reccurent model (rshm) called respectively rshm-ets and rshm-tbats according to the per-time-series model choice.
+Against these models, we propose two versions of our regime switching hybrid recurrent model (rshm) called respectively rshm-ets and rshm-tbats according to the per-time-series model choice.
 %Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}.
@@
 %To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}). 
-For our two versions, in a first time, we propose a version without our weak signal called \textit{rshm-ets} and \textit{rshm-tbats}.
+For our two versions, we propose a version without our weak signal called \textit{rshm-ets} and \textit{rshm-tbats}.
 Then we evaluate our hybrid framework with the inclusion of our weak signals (ws) referred to as \textit{rshm-ets-ws} and \textit{rshm-tbats-ws}.
@@
 A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes.
-In a given year, we define an increasing trend as a trend that do more than 10\% of growth in term of Year and Year.In the same way, we define a decreasing trend as a trend that decline of 10\% or more.
+In a given year, we define an increasing trend as a trend that does more than 10\% of growth in terms of Year and Year.In the same way, we define a decreasing trend as a trend that declines by 10\% or more.
 We classify other trends as flat trends.
 On the test set, the year 2019, we have 1871 increasing trends, 2016 decreasing trends and 6113 flat trends.
-In addition to the accuracy metrics, we compare also the different methods on this classification task.
+In addition to the accuracy metrics, we also compare the different methods on this classification task.
 
@@
 \textcolor{blue}{Result on 1000ts}  \\
-\textcolor{blue}{hybrid model correct all time series and not only a a group of hundred. WIP}  \\
-In a first time, we present the accuracy of all our methods without using our weak signals.for our 3 metrics and for each model, we compute the average and standard deviation on all our sequences on the final year.
-Results are shown in the Table ???.
-\begin{itemize}
-	\item For the statistical models, we can see a large domination of the TBATS model with a MASE equal to ...
-It is one of the main reason why we use this model on one of our hybrid framwork as the parametric model.
-However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmarck candidates.
-This result show that, with a large dataset, deep learning model can outperform the traditional approaches on average.
-An example of prediction of all the benchmarck methods is displayed in the Figure ????.
-	\item Our two different regime switching hybrid model achieve higher level of accuracy compare to the \textit{ets} or \textit{tbats} results.
+%For our 3 metrics and for each model, we compute the average and standard deviation on all our sequences on the final year on the \numberts sequences. Results are shown in the Table ???.  
+Table~\ref{tab:metricresults} summarize the results of all our benchmark models and our 2 hybrid methods for the 3 metrics described above.
+Values are errors averaged over our \numberts on the test set.
+For the statistical models, we can see a large domination of the TBATS model with an OWA equal to 0.847.
+It is one of the main reasons why we use this model on one of our hybrid frameworks as the parametric model.
+However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates.
+This result shows that, with a large dataset, deep learning models can outperform the traditional approaches on average.
+An example of prediction of all the benchmark methods is displayed in the Figure~\ref{fig:forecastexample}.Our two different regime switching hybrid models achieve a higher level of accuracy compared to their references.
 For the \textit{rshm-ets}, we pass from ???
@@
 for the hybrid model.
-Its $\classifier$ threshold $\threshold$ was fix at ???.
+Its $\classifier$ threshold $\threshold$ was fixed at ???.
 With this threshold, the error-corrector model correct ????
 sequences of the $\numberts$.
-On these corrected time series, compare to the \textit{ets} apporach, our appoach MASE fall from ???
+On these corrected time series, compared to the \textit{ets} approach, our approach MASE falls from ???
 to ???.
-However \textit{rshm-ets} doesn't succed at outperform some of the benchmarck model, for example \textit{tbats} of \textit{lstm}.
-The \textit{rshm-tbats} version clearly outperform all the previous model.
-Based on a \textit{tbats} model, wich already achieve a interesting level of accuracy, \textit{rshm-tbats} reach the higher level of accuracy with a MASE equal to ????, that is -???
-compare at the top-2 model.
-With a threshold fixed at ???, this version of our hybrid framework correct ???
-sequences of the $\numberts$.
-An example of our two regime-switching hybrid recurrent model is presented in the Figure ....
-\end{itemize}
+However \textit{rshm-ets} doesn't succeed at outperforming some of the benchmark models, for example \textit{tbats} of \textit{lstm}.
+The \textit{rshm-tbats} version clearly outperforms all the previous models.
+Based on a \textit{tbats} model, which already achieves an interesting level of accuracy, \textit{rshm-tbats} reach the higher level with a MASE equal to 0.728 and and the lower OWA equal to 0.840.
+With a threshold fixed at 0.5, this version of our hybrid framework corrects 294 TBATS predictions.
+On these 294 trends, the \textit{tbats} has an OWA equal to 0.867 and with the regime switching model correction, we reach an OWA equal to 0.845.
+An example of prediction of our two regime-switching hybrid recurrent model is presented in the Figure~\ref{fig:hybridforecast}.
+Other additional examples and results can be found in Appendix.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=1.\linewidth]{figure/example_prediction}
+  \caption{Example of benchmarck models's predictions on an emerging trend}
+\label{fig:forecastexample}
+\end{figure}
+
+\begin{figure}
+  \centering
+    \includegraphics[width=1.\linewidth]{figure/rshm_tbats_prediction_example}
+  \caption{Example of the \textit{rshm-ets} model prediction.
+In blue the ets reference and in red the $\predictor$ correction.
+$\classifier$ return ???
+that is greater than its threshold ???: we use then the correction.}
+  \centering
+    \includegraphics[width=1.\linewidth]{figure/rshm_tbats_prediction_example}
+  \caption{Example of the \textit{rshm-tbats} model prediction.
+In blue the Tbats reference and in red the $\predictor$ correction.
+$\classifier$ return 0.537 that is greater than its threshold 0.5: we use the RNN correction.}
+\label{fig:hybridforecast}
+\end{figure}
 
@@
   \caption{Results summary on our Fashion dataset. For each metric, we compute the average and the standard deviation on all the test set.}
-  \label{sample-table}
   \centering
@@
      \textit{rshm-ets} & 0. & 0. & . & . & . & 0.\\
-     \textit{\textbf{rshm-tbats}} & 0.726 & 0.242 & 21.09 & 13.60 & 0.840 & 0.157\\
-     \textit{oracle} & 0.709 & 0.235 & 20.55 & 13.30 & 0.812 & 0.153\\
+     \textit{\textbf{rshm-tbats}} & 0.728 & 0.245 & 21.02 & 13.54 & 0.840 & 0.159\\
+     \textit{oracle} & 0.716 & 0.239 & 20.74 & 13.44 & 0.828 & 0.156\\
     \hline
   \end{tabular}
+\label{tab:metricresults}
 \end{table*}
 
-We also compute for each method a confusion matrix in order to evaluate in what matter, each candidate is able to detect and accurately forecast increasing/decreasing trends.
+We also compute for each method a confusion matrix on the increase/flat/decreasing classification task.
+Our two hybrid models show interesting results.
+They achieve a better accuracy by detecting new increasing/decreasing trends or reducing the number of huge errors, predicting the opposite change direction.
+For example \textit{rshm-tbats} divide by 2 the number of classification errors of its reference.
+Another interesting result is that \textit{lstm} predicts only flat trends.
+
+\begin{table*}
+  \caption{\textit{ets} model confusion matrix}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 43 & 145 & 20 \\
+    true-flat-trend & 43 & 544 & 34 \\
+    true-inc-trend & 16 & 122 & 33 \\
+    \hline
+  \end{tabular}
+  \caption{\textit{rshm-ets} model confusion matrix}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 0 & 0 & 0 \\
+    true-flat-trend & 0 & 0 & 0 \\
+    true-inc-trend & 0 & 0 & 0 \\
+    \hline
+  \end{tabular}
+  \caption{\textit{rshm-ets-ws} model confusion matrix}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 0 & 0 & 0 \\
+    true-flat-trend & 0 & 0 & 0 \\
+    true-inc-trend & 0 & 0 & 0 \\
+    \hline
+  \end{tabular}
+\label{tab:etsclass}
+\end{table*}
 
@@
   \caption{\textit{tbats} model confusion matrix}
-  \label{sample-table}
   \centering
@@
   \end{tabular}
-\end{table*}
-
-\begin{table*}
-  \caption{\textit{ets} model confusion matrix}
-  \label{sample-table}
+  \caption{\textit{rshm-tbats} model confusion matrix}
   \centering
@@
     \hline
-	true-dec-trend & 43 & 145 & 20 \\
-    true-flat-trend & 43 & 544 & 34 \\
-    true-inc-trend & 16 & 122 & 33 \\
+	true-dec-trend & 27 & 174 & 7 \\
+    true-flat-trend & 11 & 597 & 13 \\
+    true-inc-trend & 5 & 140 & 26 \\
     \hline
   \end{tabular}
+  \caption{\textit{rshm-tbats-ws} model confusion matrix}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 26 & 171 & 11 \\
+    true-flat-trend & 17 & 579 & 25 \\
+    true-inc-trend & 3 & 136 & 32 \\
+    \hline
+  \end{tabular}
+\label{tab:tbatsclass}
 \end{table*}
+
 \begin{table*}
   \caption{\textit{lstm} model confusion matrix}
-  \label{sample-table}
   \centering
@@
   \end{tabular}
-\end{table*}
-\begin{table*}
-  \caption{\textit{rshm-tbats} model confusion matrix}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 33 & 166 & 9 \\
-    true-flat-trend & 13 & 596 & 12 \\
-    true-inc-trend & 7 & 139 & 25 \\
-    \hline
-  \end{tabular}
-\end{table*}
-
-In a seconde time, we evaluate how our framework is able to understand and leverage our weak signals.
-The Table ???
-presents the result of our three candidates that we train with our weak signals : \textit{lstm-ws}, \textit{rshm-ets-ws} and \textit{rshm-tbats-ws}.
-
-\begin{table*}
-  \caption{Results summary on our Fashion dataset. We compare methods without our weak signal and than method but train with our weak signals as an additional input}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{lllllll}
-    \hline
-    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
-    \hline
-     \textit{lstm} & 0.765 & 0.278 & 21.00 & 11.42 & 0.872 & 0.160\\
-     \textit{rshm-ets} & 0. & 0. & . & . & . & 0.\\
-     \textit{\textbf{rshm-tbats}} & 0.726 & 0.242 & 21.09 & 13.60 & 0.840 & 0.157\\
-    \hline
-     \textit{lstm-ws} & 0.758 & 0.271 & 20.89 & 11.46 & 0.867 & 0.163\\
-     \textit{rshm-ets-ws} & 0. & 0. & . & . & . & 0.\\
-     \textit{\textbf{rshm-tbats-ws}} & 0. & 0. & . & . & 0. & 0.\\
-    \hline
-  \end{tabular}
-\end{table*}
-
-Again, we show the result of our model with external signal on the classifier task. The Table ???/???/??? present their results.
-
-\begin{table*}
   \caption{\textit{lstm-ws} model confusion matrix}
-  \label{sample-table}
-  \centering
+  %\centering
   \begin{tabular}{llll}
@@
   \end{tabular}
+\label{tab:lstmclass}
 \end{table*}
+
+The Table~\ref{tab:metricresultsws},Table~\ref{tab:etsclass} and Table~\ref{tab:tbatsclass} presents how our candidates are able to understand and leverage our weak signals in terms of accuracy and classification.
+The full lstm approach shows a slight increase, from 0.872 to 0.867 for the OWA metric, and correctly predicts 4 increasing/decreasing trends.
+\textcolor{blue}{No for now, WIP} A real improvement is shown by our proposed regime switching framework.
+With a threshold fixed at 0.465, this version of our hybrid framework corrects 118 TBATS predictions.
+On these 118 trends,   the \textit{tbats} has an OWA equal to 0.893 and with the regime switching model correction, we reach an OWA equal to 0.868.
+
 \begin{table*}
-  \caption{\textit{rshm-ets-ws} model confusion matrix}
-  \label{sample-table}
+  \caption{Results summary on our Fashion dataset. We compare methods without our weak signal and than method but train with our weak signals as an additional input}
   \centering
-  \begin{tabular}{llll}
+  \begin{tabular}{lllllll}
     \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
     \hline
-	true-dec-trend & 0 & 0 & 0 \\
-    true-flat-trend & 0 & 0 & 0 \\
-    true-inc-trend & 0 & 0 & 0 \\
+     \textit{lstm} & 0.765 & 0.278 & 21.00 & 11.42 & 0.872 & 0.160\\
+     \textit{rshm-ets} & 0. & 0. & . & . & . & 0.\\
+     \textit{\textbf{rshm-tbats}} & 0.728 & 0.245 & 21.02 & 13.54 & 0.840 & 0.159\\
+    \hline
+     \textit{lstm-ws} & 0.758 & 0.271 & 20.89 & 11.46 & 0.867 & 0.163\\
+     \textit{rshm-ets-ws} & 0. & 0. & . & . & . & 0.\\
+     \textit{\textbf{rshm-tbats-ws}} & 0.731 & 0.248 & 21.10 & 13.53 & 0.844 & 16.23\\
     \hline
   \end{tabular}
-\end{table*}
-\begin{table*}
-  \caption{\textit{rshm-tbats-ws} model confusion matrix}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 0 & 0 & 9 \\
-    true-flat-trend & 0 & 0 & 0 \\
-    true-inc-trend & 0 & 0 & 0 \\
-    \hline
-  \end{tabular}
+\label{tab:metricresultsws}
 \end{table*}
@@
 
-With our results, we can make two interesting conclusions.
+%With our results, we can make two interesting conclusions.
 Firstly, the regime switching hybrid framework is a really promising framework.
@@
 
+With our results, we can make two interesting conclusions.
+Firstly, the regime switching hybrid framework is a really promising framework.
+By mixing the performance of local parametric models and a global DNN, our two versions clearly outperform traditional statistical methods.
+Furthermore, this framework is totally suited for dealing with external signals.
+With a fine pre-processing and a well-designed architecture, our two models succeed at leveraging our complex extra data and reach impressive accuracy levels.
+Secondly, our results bring to light the quality of our new Fashion dataset.
+We saw that the full LSTM model \textit{lstm} outperforms all time series specific models.
+This shows that our dataset is well suited to train complex neural network architectures able to learn information cross sequences.
+With the addition of our weak signals, we give a totally new dimension to our fashion dataset.
+Our results show that our external weak signals hide a complex but usable predictive power by DNN architecture.
+By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting.
 %\begin{table*}
@@
 \label{sec:discussion}
+
 In this paper, we propose the first hybrid model including external weak signals for time series forecasting.
-We show that hybrid framework is a really promising way.
+We show that the hybrid framework is a really promising way.
 With its extended error-corrector DNN part, it is clearly well-suited for dealing with any kind of external signals in order to correct weaknesses of first parametric models.
-Furthermore, With our additive version, we show that the hybrid model is not frozen in it original form.
-Thereby, future research explorations would be to improve its framework with new per-time-series approaches and test new error-corrector DNN part like the recent Transformer model.
-
+Furthermore, With our additive version, we show that the hybrid model is not frozen in its original form.
+Thereby, future research explorations would be to improve its framework with new per-time-series approaches and test new error-corrector DNN parts like the recent Transformer model.
 With this first contribution, we join the first fashion dataset gathering \numberts\ mode times series and a complex collection of extra signals.
-We believe that this dataset hide really fine dynamics and interactions where complex models would express their potential.
+We believe that this dataset hides really fine dynamics and interactions where complex models would express their potential.
 By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting and pave the way for further explorations.
@@
 \bibliographystyle{iclr2022_conference}
+\bibliography{hybridmodel_iclr.bib}
 
@@
 
-\section{Fashion Dataset overview}
+\section{Appendix : Fashion Dataset overview}
 
-\section{Hidden regime algorithm}
+\section{Appendix : Hidden regime algorithm}
 
@@
 %\end{equation}
-
-\section{}
 
@@
 
+\section{Appendix : Additional results, explorations and examples.}
+
 \end{document}

### 2021-10-03 iclr2022/hybridmodel_iclr.tex
update results and few corrections

--- 2021-10-03 iclr2022/hybridmodel_iclr.tex
@@
 Our fashion dataset is built with a high throughput computer vision system analysing every day images shared on social networks.
-Aggregating detected clothes by trends, we create for the first time thousand of time series representing fashion trends life on social media.
-Our sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing walues.
+Aggregating detected clothes by trends, we create for the first time thousands of time series representing fashion trends life on social media.
+Our sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
 Each time series is normalized in order to remove social networks biases and their values lie between 0 and 1.
-The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
-An overview of it can be found in Table~\ref{sample-table}.
+The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 different categories and 5 geozones.
+An overview of it can be found in table 1.
 
@@
 However, some sequences show interesting behaviours with sudden changes.
-We call them emerging or declining trends depending of the change direction.
+We call them emerging or declining trends depending on the change in direction.
 A central point of our work is to accurately detect and forecast these trends.
@@
 With this specific panel, we aim at detecting the first waves announcing emerging trends or the collapse of other ones.
-By analyzing images shared by this specific panel on social medias, we create a first weak signal named \textit{fashion-forwards} for each of the previous trends.
-We also analyzed only a specific part of social media users depending of the number of followers.
+By analyzing images shared by this specific panel on social media, we create a first weak signal named \textit{fashion-forwards} for each of the previous trends.
+We also analyzed only a specific part of social media users depending on the number of followers.
 With three thresholds we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high}.
-Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.
-These extra signals are frequently sparse for micro trends and they often lack of interest for common fashion trends.
-However on several examples, they are fundamental to detect the future fashion evolution.
+Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.These extra signals are frequently sparse for micro trends and they often lack interest in common fashion trends.
+However, in several examples, they are fundamental to detect the future fashion evolution.
 
@@
 As an example, an impressive emerging fashion trend is represented in Figure~\ref{fig:oneemergingtrend}, see other examples in Appendix~\ref{}.
-It shows the evolution of one shoes trends on social media and its linked \textit{fashion-forward} weak signal.
+It shows the evolution of one shoe trend on social media and its linked \textit{fashion-forward} weak signal.
 During the first 3 years, common users and the panel of mode-influencers share the same behaviour.
-The trend start to boom in the mainstream people during the first month of 2018.
+The trend started to boom in the mainstream people during the first month of 2018.
 However, we can detect early signals in the fashion-forward panel at the end of 2017.
-Early adopters started to change there behaviour and show more frequently the trend on social media.
+Early adopters started to change their behaviour and show more frequently the trend on social media.
 With fashion influence dynamics, the new tendency spreads to every part of social media users.
-Finally, after a pick reached at the end of 2018 for the fashion-influencers, a regular decrease appear.
+Finally, after a peak reached at the end of 2018 for the fashion-influencers, a regular decrease appeared.
 %They leave gradually the old trend to focus more on the latest or propose new ones.
@@
 Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels, tbats} , we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
-The \textit{snaive} forecasts are only the repetition of the last same past period.
-The \textit{ets} model is an additive exponential smoothing with a level component and a seasonal component.
-The \textit{stlm} approach uses a multiplicative decomposition and models the seasonality adjusted time series with an exponenantial smoothing model.
-The \textit{Thetam} model decomposes the original signal in $\theta$-lines, forecasts each one separately and recomposes them to produce the final forecast and  \textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization.
-Finally,  \textit{auto.arima} is the R implementation of ARIMA model with an automatic selection of the best parameters.
-A complete description and references for these models can be found in \citep{packageforecast}.
+\textit{snaive} forecasts are only the repetition of the last same past period.
+\textit{ets} model is an additive exponential smoothing with a level component and a seasonal component.
+\textit{stlm} approach uses a multiplicative decomposition and models the seasonally adjusted time series with an exponential smoothing model.
+\textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast.
+\textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization.
+The last one \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters.
+A complete description and references for these models can be found in \citep{hyndman2020package}.
 As a deep learning approach, we considered a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52.
 
-Against these models, we propose our two versions of our regime switching hybrid reccurent model (rshm) called respectively rshm-ets and rshm-tbats according to the per-time-series model choice.
+Against these models, we propose two versions of our regime switching hybrid recurrent model (rshm) called respectively rshm-ets and rshm-tbats according to the per-time-series model choice.
 %Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}.
@@
 A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes.
-In a given year, we define an increasing trend as a trend that does more than 10\% of growth in term of Year and Year.
-In the same way, we define a decreasing trend as a trend that declines of 10\% or more.
+In a given year, we define an increasing trend as a trend that does more than 10\% of growth in terms of Year and Year.In the same way, we define a decreasing trend as a trend that declines by 10\% or more.
 We classify other trends as flat trends.
 On the test set, the year 2019, we have 1871 increasing trends, 2016 decreasing trends and 6113 flat trends.
-In addition to the accuracy metrics, we compare also the different methods on this classification task.
+In addition to the accuracy metrics, we also compare the different methods on this classification task.
 
@@
 
-\section{}
-
 \textcolor{red}{details to add in appendix.} \textcolor{red}{Assume that $\theta_p$ is the current value for the weights of the RNN-p and the RNN-c and write $\omega_p^n = \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T+h})$.
@@
 
+\section{Additional results, explorations and examples.}
+
 \end{document}

### 2021-10-04 iclr2022/hybridmodel_iclr.tex
a few corrections

@@
 
-During the M4 competition, the hybrid model of \cite{} is based on a multiplicative exponential smoothing model as the time-series-specific model.
+During the M4 competition, the hybrid model of \cite{smyl2020hybrid} is based on a multiplicative exponential smoothing model as the time-series-specific model.
 However, on sporadic time series, this choice could lead to poor result and instability.
@@
 In Section~\ref{sec:exp}, we present two versions of our framework.
-The first one use an  exponential smoothing as reference  similar to \cite{} and the second one use a TBATS model \cite{} which provides better results.
+The first one use an  exponential smoothing as reference  similar to \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results.
 The main complexity is in the next stage: training a global RNN to correct the per-time-series statistical models when the statistical models provide poor performance.
@@
 \begin{align*}
-\ts^n_{T+i}  &= \tspred^{stat,n}_{T-w+i|T-w} +  \hat{\hiddenregime}^n_T * \hat{\remainder}^{n}_{T+i} + \varepsilon^n_{T+i}\,, \\
+\ts^n_{T+i}  &= \tspred^{stat,n}_{T-w+i|T-w} +  \hat{\hiddenregime}^n_T \cdot \hat{\remainder}^{n}_{T+i} + \varepsilon^n_{T+i}\,, \\
 \hat{\hiddenregime}^n_T &= \mathbf{1}_{\classifier(\rnnwindow^n_T) > \threshold}\,, \\
-\hat{\remainder}^{n}_{T+i} &= \predictor(\rnnwindow^n_T)_{T+i} \times \meants^n_T\,.
+\hat{\remainder}^{n}_{T+i} &= \predictor(\rnnwindow^n_T)_{T+i} \cdot \meants^n_T\,.
 \end{align*}
@@
 \label{eq:full:model}
-\ts^n_{T+i}  = \tspred^{stat,n}_{T-w+i|T-w} +  \mathbf{1}_{\classifier(\fullconcatinput^n_T) > \threshold} \times \predictor(\fullconcatinput^n_T)_{T+i} \times \meants^n_T + \varepsilon^n_{T+i}\,,
+\ts^n_{T+i}  = \tspred^{stat,n}_{T-w+i|T-w} +  \mathbf{1}_{\classifier(\fullconcatinput^n_T) > \threshold} \cdot \predictor(\fullconcatinput^n_T)_{T+i} \cdot \meants^n_T + \varepsilon^n_{T+i}\,,
 \end{equation}
@@
 There are then fixed during the training of the recurrent models.
-The proposed hybrid model introduced in this numerical section is the TBATS model of \cite{XXX}.
-This model is also compared to an hybrid model with an additive exponential smoothing model as a reference close to \cite{XXX}.
+The proposed hybrid model introduced in this numerical section is the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771}.
+This model is also compared to an hybrid model with an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}.
 For $\classifier$ and $\predictor$, we built an architecture summarized in Figure~\ref{fig:rnnarchi}.
@@
 After the $\classifier$ final dense layer, we add a sigmoid activation to return a probability.
-We use 2 Adam otpimizers with the same learning rate equal to ???
-and the batch size is  64.
-The eval set is used to fix the $\threshold$ parameter that determine, depending of the output of $\predictor$, when  tuse the $\predictor$ correction.
+We use 2 Adam otpimizers with the same learning rate equal to $5\cdot 10^{-6}$ and the batch size is  64.
+The eval set is used to fix the $\threshold$ parameter that determine, depending of the output of $\predictor$, when use the $\predictor$ correction.
 
@@
 \subsection{Discussion}
+\label{sec:discussion}
+
+%With our results, we can make two interesting conclusions.
+Firstly, the regime switching hybrid framework is a really promising framework.
+By mixing the performance of local parametric models and a global DNN, our two versions clearly outperform traditional statistical methods.
+Furthermore, this framework is totally suited for dealing with external signals.
+With a fine pre-processing and a well-designed architecture, our two models succeed at leveraging our complex extra data and reach impressive accuracy levels.
+Secondly, our results bring to light the quality of our new Fashion dataset.
+We saw that the full LSTM model \textit{lstm} outperforms all time series specific models.
+This shows that our dataset is well suited to train complex neural network architectures able to learn information cross sequences.
+With the addition of our weak signals, we give a totally new dimension to our fashion dataset.
+Our results show that our external weak signals hide a complex but usable predictive power by DNN architecture.
+By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting.
 
@@
 Our results show that our external weak signals hide a complex but usable predictive power by DNN architecture.
-By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting.
+
 %\begin{table*}
@@
 \section{Conclusion}
-\label{sec:discussion}
-In this paper, we propose the first hybrid model including external weak signals for time series forecasting.
+\label{sec:conclusion}
+%In this paper, we propose the first hybrid model including external weak signals for time series forecasting.
 We show that hybrid framework is a really promising way.
@@
 Thereby, future research explorations would be to improve its framework with new per-time-series approaches and test new error-corrector DNN part like the recent Transformer model.
+
+In this paper, we propose the first hybrid model including external weak signals for time series forecasting.
+We show that hybrid framework is a really promising way.
+With its extended error-corrector DNN part, it is clearly well-suited for dealing with any kind of external signals in order to correct weaknesses of first parametric models.
+Furthermore, With our general framework, we show that the hybrid model is able to include any kind of any per-time-series models.
+Thereby, future research explorations would be to evaluate its framework with different per-time-series approaches and understand relationships between first parametric model choice and final hybrid model accuracy.
+For our regime switching recurrent error-corrector, we assumed the existence of only 2 regimes.
+A logical exploration would be to extend our framework with multiple regimes: change the binary RNN classifier to a multi-label classifier and train several regime-specialized RNN predictors.
 

### 2021-10-04 iclr2022/hybridmodel_iclr.tex
add hidden regime part in Appendix

@@
 $$
-\rnn^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{stat,n}_{T-w+i|T-w}}{\meants^n_T}\,,
+\rnn^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{stat,n}_{T-w+i|T}}{\meants^n_T}\,,
 $$
@@
 \begin{align*}
-\ts^n_{T+i}  &= \tspred^{stat,n}_{T-w+i|T-w} +  \hat{\hiddenregime}^n_T \cdot \hat{\remainder}^{n}_{T+i} + \varepsilon^n_{T+i}\,, \\
+\ts^n_{T+i}  &= \tspred^{stat,n}_{T-w+i|T} +  \hat{\hiddenregime}^n_T \cdot \hat{\remainder}^{n}_{T+i} + \varepsilon^n_{T+i}\,, \\
 \hat{\hiddenregime}^n_T &= \mathbf{1}_{\classifier(\rnnwindow^n_T) > \threshold}\,, \\
@@
 \label{eq:full:model}
-\ts^n_{T+i}  = \tspred^{stat,n}_{T-w+i|T-w} +  \mathbf{1}_{\classifier(\fullconcatinput^n_T) > \threshold} \cdot \predictor(\fullconcatinput^n_T)_{T+i} \cdot \meants^n_T + \varepsilon^n_{T+i}\,,
+\ts^n_{T+i}  = \tspred^{stat,n}_{T-w+i|T} +  \mathbf{1}_{\classifier(\fullconcatinput^n_T) > \threshold} \cdot \predictor(\fullconcatinput^n_T)_{T+i} \cdot \meants^n_T + \varepsilon^n_{T+i}\,,
 \end{equation}
@@
 
-In our framework, we assume that our sequence are generated with a regime with 2 hidden regime.
-As this regime, noted $\hiddenregime$, is never observed, we can compute explicitely the following quantity :
-%$p(\ts^n_{T+1:T+h}|\ts^n_{1:T})$
+In our framework, we assume that our sequence are generated with 2 hidden regime.
+As this regime, noted $\hiddenregime$, is never observed, we use the Expectation Maximization (EM) algorithm to write our loss function:
+We note $\rnnparam^{(t)} = \{\rnnparam_c^{(t)},\rnnparam_p^{(t)}\}$ the weights of $\classifier$ and of $\predictor$ at a fixed epoch $t$.
 
-%Based on the Expectation-Maximization (EM) algorithm and the Fisher's identity, we write a new algorithm to estimate jointly $\theta = \{\theta_p,\theta_c\}$, the weights of RNN-p and of RNN-c.
+As the EM algorithm, we want to compute the following value :
 
-%During our training, we note $\theta^{(t)}$ the value of $\theta$ at an epoch $t$.
+\begin{align}
+\mathbb{Q}^n(\rnnparam|\rnnparam^{(t)}) &= \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h},\rnnparam^{(t)}\right]\ \\
+& = \sum_{U_T^n} p(U_T^n|\ts^n_{1:T+h},\rnnparam^{(t)}) \times \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T}) \\
+& = \sum_{U_T^n} p(U_T^n|\ts^n_{1:T+h},\rnnparam^{(t)}) \times \log[p_\theta(U_T^n|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})]
+\end{align}
 
-%\begin{equation}
-%\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h}\right]\,,
-%\end{equation}
+where $ \mathbb{P}_{\theta}(U_T^n = 1|\ts^n_{1:T})$ is parameterized by $\classifier$ and the predictive probability density $p_{\theta}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})$ is parameterized by $\predictor$ and the statistical model.
 
-\textcolor{red}{details to add in appendix.} \textcolor{red}{Assume that $\theta_p$ is the current value for the weights of the RNN-p and the RNN-c and write $\omega_p^n = \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T+h})$.
-Note that
+Write $\omega_{\rnnparam^{(t)}}^n = \mathbb{P}(U_T^n = 1|\ts^n_{1:T+h},\rnnparam^{(t)})$. We have:
+
+\begin{align*}
+\omega_{\rnnparam^{(t)}}^n &= \mathbb{P}_(U_T^n = 1|\ts^n_{1:T+h},\rnnparam^{(t)}) \\
+& =  \frac{p(\ts^n_{T+1:T+h},U_T^n = 1|\ts^n_{1:T},\rnnparam^{(t)})}{p_(\ts^n_{T+1:T+h}|\ts^n_{1:T})} \\
+& =  \frac{p(\ts^n_{T+1:T+h}|U_T^n = 1,\ts^n_{1:T},\rnnparam^{(t)}) \times p(U_T^n = 1|\ts^n_{1:T},\rnnparam^{(t)})}{\sum_{U_T^n}p(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T},\rnnparam^{(t)}) \times p(U_T^n|\ts^n_{1:T},\rnnparam^{(t)})}
+\end{align*}
+
+where , $\mathbb{P}(U_T^n=1|\ts^n_{1:T},\rnnparam^{(t)})$ is the output of $\classifier$ at epoch $t$ and the predictive probability density $p(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})$ is compute with the output of $\predictor$ at epoch $t$.
+
+To compute our final loss function, we have to define the predictive probability density $p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$.
+
+In our model final equation~\ref{eq:full:model}, we assume that $\varepsilon^n_{T+i}$ are independent and follow a Laplace distribution.
+
+We have for the regime 0 :
+
+\begin{align*}
+p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) &= \prod_{i=1}^{h}\frac{1}{2b}e^{\frac{1}{b}|\ts^n_{T+i}  - \tspred^{stat,n}_{T+i|T}|} \\
+& = \frac{1}{(2b)^h}e^{\frac{1}{b}\sum_{i=1}^{h}|\ts^n_{T+i}  - \tspred^{stat,n}_{T+i|T}|}
+\end{align*}
+
+and for the regime 1 :
+\begin{align*}
+p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) &= \frac{1}{(2b)^h}e^{\frac{1}{b}\sum_{i=1}^{h}|\ts^n_{T+i}  - \tspred^{stat,n}_{T-w+i|T}-\meants^n_T \cdot \predictor(\fullconcatinput^n_T)_{T+i} |}
+\end{align*}
+
+with $b$ and constant that we fixed at $ \meants^n_T = \sum_{i = 1}^{w}  \ts^n_{T-w+i}/w$.
+
+Finally, we have all the values to compute the loss function :
+
 $$
-\omega_p^n \propto \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T})p_{\theta_p}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\,.
+\theta\mapsto - \omega_{\rnnparam^{(t)}}^n \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})
+- (1-\omega_{\rnnparam^{(t)}}^n) \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,, \\
 $$
-Then,
-\begin{multline*}
-\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \omega_p^n\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})\\
-+ (1-\omega_p^n)\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,.
-\end{multline*}
-The loss function is then given by
-\begin{multline*}
-\theta\mapsto - \omega_p^n \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})\\
-- (1-\omega_p^n) \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,,
-\end{multline*} 
-where no gradient is computed on $\omega_p^n$.
-In both terms, $\log p_\theta(U_T^n=0|\ts^n_{1:T})$ and $\log p_\theta(U_T^n=0|\ts^n_{1:T})$ are simply given by the output of the FFNN.
-Choices for the model.
-\begin{itemize}
-\item In the case where the  $\varepsilon^n_{T+i}$ are Gaussian and independent, up to an additive constant
-$$
-\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) = -c\sum_{i=1}^{h}(\ts^n_{T+i}  - \tspred^{stat,n}_{T-w+i|T-w})^2
-$$
-and
-\begin{multline*}
-\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\\
- = -c\sum_{i=1}^{h}(\ts^n_{T+i}  - \tspred^{stat,n}_{T-w+i|T-w} - \meants^n_T\times \rnnmodel(\fullconcatinput^n_T)_{T+i})^2\,.
-\end{multline*}
-Choice of $c$ ?
-\item In the case where the  $\varepsilon^n_{T+i}$ are Laplace and independent, up to an additive constant
-$$
-\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) = -c\sum_{i=1}^{h}|\ts^n_{T+i}  - \tspred^{stat,n}_{T-w+i|T-w}|
-$$
-and
-\begin{multline*}
-\log p_\theta(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\\
- = -c\sum_{i=1}^{h}|\ts^n_{T+i}  - \tspred^{stat,n}_{T-w+i|T-w} - \meants^n_T\times \rnnmodel(\fullconcatinput^n_T)_{T+i}|\,.
-\end{multline*}
-Choice of $c$ ?
-\end{itemize}}
+where no gradient is computed on $\omega_{\rnnparam^{(t)}}^n$.
 

### 2021-11-24 iclr2022/hybridmodel_iclr.tex
Corrections appendix
A few updates

@@
 Firstly, many of them are "black-boxes"  as the final forecast usually does not come with a statistical guarantee  although a few recent works focused on measuring uncertainty in recurrent neural networks, see  \cite{martin2020monte}.
-Secondly, without a fine prepossessing and well chosen hyper-parameters, these methods could lead to poor results and are often outperformed by traditional statistical parametric models, see \cite{makridakis2018m4}.
+Secondly, without a fine prepossessing and well chosen hyper-parameters, these methods could lead to poor results and are often outperformed by traditional statistical models, see \cite{makridakis2018m4}.
 
@@
 
-Recurrent neural network are appealing to tackle our forecasting problem due to their capability of leveraging external data.
+Recurrent neural networks are appealing to tackle our forecasting problem due to their capability of leveraging external data.
 Recently, hybrid models combining DNN architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \citep{zhang2003time,jianwei2019novel,bandara2020lstm}.
@@
 %We design a more general hybrid framework including the original multiplicative model and a new additive one.
-Our approach enriches existing hybrid models by incorporating an unobserved regime switching feature to account for the need neural network based correction.
+Our approach enriches existing hybrid models by incorporating an unobserved regime switching feature to account for the need of a neural network based correction.
 In order to leverage external signals, we modify the hybrid framework to allow the regime shift and the  global error-corrector neural network to deal with external data.
@@
 The main complexity is in the next stage: training a global RNN to correct the per-time-series statistical models when the statistical models provide poor performance.
+\textcolor{red}{Plutot dire ici que l'on souhaite corriger des erreurs specifiques: et introduire les types de trends mal predites que l'on souhaite corriger.}
 % Indeed, depending on time series, some family of parametric models can achieve really heterogeneous level of accuracy. 
@@
 We train two global RNN on all sequences, a classifier ($\classifier$) and a predictor ($\predictor$).
-We train the classifier to estimate the law of the Bernoulli random variable $\hiddenregime^n_T$ we train the predictor to predict $\{\remainder^{n}_{T+i}\}_{1\leqslant i\leqslant \lag}$.
+We train the classifier to estimate the law of the Bernoulli random variable $\hiddenregime^n_T$ and we train the predictor to predict $\{\remainder^{n}_{T+i}\}_{1\leqslant i\leqslant \lag}$.
 However, these two tasks require a thorough data pre-processing and with our collection of parametric models, we propose first to normalize and deseasonalize the RNNs inputs.
@@
 \mathbb{Q}^n(\rnnparam|\rnnparam^{(t)}) &= \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h},\rnnparam^{(t)}\right]\ \\
-& = \sum_{U_T^n} p(U_T^n|\ts^n_{1:T+h},\rnnparam^{(t)}) \times \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T}) \\
-& = \sum_{U_T^n} p(U_T^n|\ts^n_{1:T+h},\rnnparam^{(t)}) \times \log[p_\theta(U_T^n|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})]
+& = \sum_{j} p(U_T^n = j|\ts^n_{1:T+h},\rnnparam^{(t)}) \times \textcolor{red}{\nabla_\theta} \log p_\theta(\ts^n_{T+1:T+h},U_T^n = j|\ts^n_{1:T}) \\
+& = \sum_{j} p(U_T^n = j|\ts^n_{1:T+h},\rnnparam^{(t)}) \times \textcolor{red}{\nabla_\theta}\log[p_\theta(U_T^n = j|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n = j,\ts^n_{1:T})]
 \end{align}

### 2021-11-25 iclr2022/hybridmodel_iclr.tex
add fina result on 10k/1k/100ts dataset

@@
 
-\textcolor{blue}{Result on 1000ts}  \\
+%\textcolor{blue}{Result on 1000ts}  \\
 %For our 3 metrics and for each model, we compute the average and standard deviation on all our sequences on the final year on the \numberts sequences. Results are shown in the Table ???.  
-Table~\ref{tab:metricresults} summarize the results of all our benchmark models and our 2 hybrid methods for the 3 metrics described above.
+%Table~\ref{tab:metricresults} summarize the results of all our benchmark models and our 2 hybrid methods for the 3 metrics described above.
 Values are errors averaged over our \numberts on the test set.
@@
 
-\begin{figure}
-  \centering
-    \includegraphics[width=1.\linewidth]{figure/example_prediction}
-  \caption{Example of benchmarck models's predictions on an emerging trend}
-\label{fig:forecastexample}
-\end{figure}
+%\begin{figure}
+%  \centering
+%    \includegraphics[width=1.\linewidth]{figure/example_prediction}
+%  \caption{Example of benchmarck models's predictions on an emerging trend}
+%\label{fig:forecastexample}
+%\end{figure}
 
-\begin{figure}
-  \centering
-    \includegraphics[width=1.\linewidth]{figure/rshm_tbats_prediction_example}
-  \caption{Example of the \textit{rshm-ets} model prediction.
+%\begin{figure}
+%  \centering
+%    \includegraphics[width=1.\linewidth]{figure/rshm_tbats_prediction_example}
+%  \caption{Example of the \textit{rshm-ets} model prediction.
 In blue the ets reference and in red the $\predictor$ correction.
-$\classifier$ return ???
+$%\classifier$ return ???
 that is greater than its threshold ???: we use then the correction.}
-  \centering
-    \includegraphics[width=1.\linewidth]{figure/rshm_tbats_prediction_example}
-  \caption{Example of the \textit{rshm-tbats} model prediction.
+%  \centering
+%    \includegraphics[width=1.\linewidth]{figure/rshm_tbats_prediction_example}
+%  \caption{Example of the \textit{rshm-tbats} model prediction.
 In blue the Tbats reference and in red the $\predictor$ correction.
 $\classifier$ return 0.537 that is greater than its threshold 0.5: we use the RNN correction.}
-\label{fig:hybridforecast}
-\end{figure}
+%\label{fig:hybridforecast}
+%\end{figure}
 
 \begin{table*}
-  \caption{Results summary on our Fashion dataset. For each metric, we compute the average and the standard deviation on all the test set.}
+  \caption{Results summary on our 10000ts Fashion dataset.
+For each metric, we compute the average on all our time series.
+For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
   \centering
@@
     \hline
-     \textit{snaive} & 0.871 & 0.255 & 25.29 & 14.90 & 1. & 0.\\
-     \textit{ets} & 0.801 & 0.274 & 24.18 & 17.51 & 0.944 & 0.286\\
-     \textit{thetam} & 0.849 & 0.364 & 24.58 & 17.07 & 0.980 & 0.333\\
-     \textit{stlm} & 0.765 & 0.265 & 22.22 & 13.77 & 0.885 & 0.188\\
-     \textit{tbats} & 0.734 & 0.254 & 21.19 & 13.79 & 0.847 & 0.171\\
-     \textit{auto.arima} & 0. & 0. & . & . & . & 0.\\
-     \textit{lstm} & 0.765 & 0.278 & 21.00 & 11.42 & 0.872 & 0.160\\
-     \textit{rshm-ets} & 0. & 0. & . & . & . & 0.\\
-     \textit{\textbf{rshm-tbats}} & 0.728 & 0.245 & 21.02 & 13.54 & 0.840 & 0.159\\
-     \textit{oracle} & 0.716 & 0.239 & 20.74 & 13.44 & 0.828 & 0.156\\
+     \textit{snaive} & 0.881 & - & 25.27 & - & 1. & -\\
+     \textit{thetam}  & 0.844 & - & 24.17 & - & 0.970 & -\\
+     \textit{arima} & 0.826 & - & 23.63 & - & 0.949 & -\\
+     \textit{stlm} & 0.770 & - & 22.05 & - & 0.882 & -\\
+     \textit{tbats} & 0.745 & - & 21.13 & - & 0.850 & -\\
+     \textit{lstm-withws} & 0.728 & 0.004 & 20.18 & 0.085 & 0.837 & 0.004\\
+     \textit{lstm-nows} & 0.724 & 0.003 & 20.08 & 0.052  & 0.825 & 0.004\\
+     \textit{hybrid-withws} & 0.713 & 0.005 & 20.53 & 0.170 & 0.825 & 0.009\\
+     \textit{hybrid-nows} & 0.715 & 0.002 & 20.41 & 0.056 & 0.816 & 0.002\\
     \hline
@@
 
-We also compute for each method a confusion matrix on the increase/flat/decreasing classification task.
+\begin{table*}
+  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series.
+For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
+  \centering
+  \begin{tabular}{lllllll}
+    \hline
+    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
+    \hline
+     \textit{snaive} & 0.871 & - & 25.29 & - & 1. & -\\
+     \textit{thetam}  & 0.849 & - & 24.58 & - & 0.980 & -\\
+     \textit{arima} & 0.821 & - & 23.69 & - & 0.951 & -\\
+     \textit{stlm} & 0.765 & - & 22.22 & - & 0.885 & -\\
+     \textit{lstm-nows} & 0.740 & 0.007 & 20.56 & 0.154 & 0.856 & 0.008\\
+     \textit{tbats} & 0.734 & - & 21.19 & - & 0.847 & -\\
+     \textit{hybrid-nows} & 0.719 & 0.002 & 20.79 & 0.094 & 0.833 & 0.004\\
+    \hline
+  \end{tabular}
+\label{tab:metricresults}
+\end{table*}
+
+\begin{table*}
+  \caption{Results summary on our 100ts Fashion dataset.
+For each metric, we compute the average on all our time series.
+For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
+  \centering
+  \begin{tabular}{lllllll}
+    \hline
+    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
+    \hline
+     \textit{snaive} & 0.876 & - & 26.98 & - & 1. & -\\
+     \textit{thetam}  & 0.823 & - & 25.11 & - & 0.944 & -\\
+     \textit{arima} & 0.814 & - & 24.61 & - & 0.940 & -\\
+     \textit{lstm-nows} & 0.767 & 0.045 & 22.22 & 0.848 & 0.877 & 0.051\\
+     \textit{stlm} & 0.742 & - & 23.03 & - & 0.863 & -\\
+     \textit{tbats} & 0.745 & - & 22.16 & - & 0.856 & -\\
+     \textit{hybrid-nows} & 0.739 & 0.003 & 22.31 & 0.083 & 0.845 & 0.003\\
+    \hline
+  \end{tabular}
+\label{tab:metricresults}
+\end{table*}
+
+%We also compute for each method a confusion matrix on the increase/flat/decreasing classification task.
 Our two hybrid models show interesting results.
@@
 
-\begin{table*}
-  \caption{\textit{ets} model confusion matrix}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 43 & 145 & 20 \\
-    true-flat-trend & 43 & 544 & 34 \\
-    true-inc-trend & 16 & 122 & 33 \\
-    \hline
-  \end{tabular}
-  \caption{\textit{rshm-ets} model confusion matrix}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 0 & 0 & 0 \\
-    true-flat-trend & 0 & 0 & 0 \\
-    true-inc-trend & 0 & 0 & 0 \\
-    \hline
-  \end{tabular}
-  \caption{\textit{rshm-ets-ws} model confusion matrix}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 0 & 0 & 0 \\
-    true-flat-trend & 0 & 0 & 0 \\
-    true-inc-trend & 0 & 0 & 0 \\
-    \hline
-  \end{tabular}
-\label{tab:etsclass}
-\end{table*}
+%\begin{table*}
+%  \caption{\textit{ets} model confusion matrix}
+%  \centering
+%  \begin{tabular}{llll}
+%    \hline
+%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+%    \hline
+%	true-dec-trend & 43 & 145 & 20 \\
+%    true-flat-trend & 43 & 544 & 34 \\
+%    true-inc-trend & 16 & 122 & 33 \\
+%    \hline
+%  \end{tabular}
+%  \caption{\textit{rshm-ets} model confusion matrix}
+%  \centering
+%  \begin{tabular}{llll}
+%    \hline
+%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+%    \hline
+%	true-dec-trend & 0 & 0 & 0 \\
+%    true-flat-trend & 0 & 0 & 0 \\
+%    true-inc-trend & 0 & 0 & 0 \\
+%    \hline
+%  \end{tabular}
+%  \caption{\textit{rshm-ets-ws} model confusion matrix}
+%  \centering
+%  \begin{tabular}{llll}
+%    \hline
+%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+%    \hline
+%	true-dec-trend & 0 & 0 & 0 \\
+%    true-flat-trend & 0 & 0 & 0 \\
+%    true-inc-trend & 0 & 0 & 0 \\
+%    \hline
+%  \end{tabular}
+%\label{tab:etsclass}
+%\end{table*}
 
-\begin{table*}
-  \caption{\textit{tbats} model confusion matrix}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 33 & 167 & 8 \\
-    true-flat-trend & 21 & 578 & 22 \\
-    true-inc-trend & 7 & 136 & 28 \\
-    \hline
-  \end{tabular}
-  \caption{\textit{rshm-tbats} model confusion matrix}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 27 & 174 & 7 \\
-    true-flat-trend & 11 & 597 & 13 \\
-    true-inc-trend & 5 & 140 & 26 \\
-    \hline
-  \end{tabular}
-  \caption{\textit{rshm-tbats-ws} model confusion matrix}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 26 & 171 & 11 \\
-    true-flat-trend & 17 & 579 & 25 \\
-    true-inc-trend & 3 & 136 & 32 \\
-    \hline
-  \end{tabular}
-\label{tab:tbatsclass}
-\end{table*}
+%\begin{table*}
+%  \caption{\textit{tbats} model confusion matrix}
+%  \centering
+%  \begin{tabular}{llll}
+%    \hline
+%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+%    \hline
+%	true-dec-trend & 33 & 167 & 8 \\
+%    true-flat-trend & 21 & 578 & 22 \\
+%    true-inc-trend & 7 & 136 & 28 \\
+%    \hline
+%  \end{tabular}
+%  \caption{\textit{rshm-tbats} model confusion matrix}
+%  \centering
+%  \begin{tabular}{llll}
+%    \hline
+%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+%    \hline
+%	true-dec-trend & 27 & 174 & 7 \\
+%    true-flat-trend & 11 & 597 & 13 \\
+%    true-inc-trend & 5 & 140 & 26 \\
+%    \hline
+%  \end{tabular}
+%  \caption{\textit{rshm-tbats-ws} model confusion matrix}
+%  \centering
+%  \begin{tabular}{llll}
+%    \hline
+%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+%    \hline
+%	true-dec-trend & 26 & 171 & 11 \\
+%    true-flat-trend & 17 & 579 & 25 \\
+%    true-inc-trend & 3 & 136 & 32 \\
+%    \hline
+%  \end{tabular}
+%\label{tab:tbatsclass}
+%\end{table*}
 
-\begin{table*}
-  \caption{\textit{lstm} model confusion matrix}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 0 & 208 & 0 \\
-    true-flat-trend & 0 & 621 & 0 \\
-    true-inc-trend & 0 & 171 & 0 \\
-    \hline
-  \end{tabular}
-  \caption{\textit{lstm-ws} model confusion matrix}
-  %\centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 1 & 205 & 2 \\
-    true-flat-trend & 2 & 619 & 0 \\
-    true-inc-trend & 0 & 168 & 3 \\
-    \hline
-  \end{tabular}
-\label{tab:lstmclass}
-\end{table*}
+%\begin{table*}
+%  \caption{\textit{lstm} model confusion matrix}
+%  \centering
+%  \begin{tabular}{llll}
+%    \hline
+%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+%    \hline
+%	true-dec-trend & 0 & 208 & 0 \\
+%    true-flat-trend & 0 & 621 & 0 \\
+%    true-inc-trend & 0 & 171 & 0 \\
+%    \hline
+%  \end{tabular}
+%  \caption{\textit{lstm-ws} model confusion matrix}
+%  %\centering
+%  \begin{tabular}{llll}
+%    \hline
+%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+%    \hline
+%	true-dec-trend & 1 & 205 & 2 \\
+%    true-flat-trend & 2 & 619 & 0 \\
+%    true-inc-trend & 0 & 168 & 3 \\
+%    \hline
+%  \end{tabular}
+%\label{tab:lstmclass}
+%\end{table*}
 
-The Table~\ref{tab:metricresultsws},Table~\ref{tab:etsclass} and Table~\ref{tab:tbatsclass} presents how our candidates are able to understand and leverage our weak signals in terms of accuracy and classification.
+%The Table~\ref{tab:metricresultsws},Table~\ref{tab:etsclass} and Table~\ref{tab:tbatsclass} presents how our candidates are able to understand and leverage our weak signals in terms of accuracy and classification.
 The full lstm approach shows a slight increase, from 0.872 to 0.867 for the OWA metric, and correctly predicts 4 increasing/decreasing trends.
@@
 
-\begin{table*}
-  \caption{Results summary on our Fashion dataset. We compare methods without our weak signal and than method but train with our weak signals as an additional input}
-  \centering
-  \begin{tabular}{lllllll}
-    \hline
-    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
-    \hline
-     \textit{lstm} & 0.765 & 0.278 & 21.00 & 11.42 & 0.872 & 0.160\\
-     \textit{rshm-ets} & 0. & 0. & . & . & . & 0.\\
-     \textit{\textbf{rshm-tbats}} & 0.728 & 0.245 & 21.02 & 13.54 & 0.840 & 0.159\\
-    \hline
-     \textit{lstm-ws} & 0.758 & 0.271 & 20.89 & 11.46 & 0.867 & 0.163\\
-     \textit{rshm-ets-ws} & 0. & 0. & . & . & . & 0.\\
-     \textit{\textbf{rshm-tbats-ws}} & 0.731 & 0.248 & 21.10 & 13.53 & 0.844 & 16.23\\
-    \hline
-  \end{tabular}
-\label{tab:metricresultsws}
-\end{table*}
+%\begin{table*}
+%  \caption{Results summary on our Fashion dataset. We compare methods without our weak signal and than method but train with our weak signals as an additional input}
+%  \centering
+%  \begin{tabular}{lllllll}
+%    \hline
+%    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
+%    \hline
+%     \textit{lstm} & 0.765 & 0.278 & 21.00 & 11.42 & 0.872 & 0.160\\
+%     \textit{rshm-ets} & 0. & 0. & . & . & . & 0.\\
+%     \textit{\textbf{rshm-tbats}} & 0.728 & 0.245 & 21.02 & 13.54 & 0.840 & 0.159\\
+%    \hline
+%     \textit{lstm-ws} & 0.758 & 0.271 & 20.89 & 11.46 & 0.867 & 0.163\\
+%     \textit{rshm-ets-ws} & 0. & 0. & . & . & . & 0.\\
+%     \textit{\textbf{rshm-tbats-ws}} & 0.731 & 0.248 & 21.10 & 13.53 & 0.844 & 16.23\\
+%    \hline
+%  \end{tabular}
+%\label{tab:metricresultsws}
+%\end{table*}
 

### 2021-12-01 iclr2022/hybridmodel_iclr.tex
add ets results and confusion matrix

@@
      \textit{arima} & 0.826 & - & 23.63 & - & 0.949 & -\\
+     \textit{ets} & 0.807 & - & 23.58 & - & 0.937 & -\\
+     \textit{hybrid-withws-ets} & 0.769 & 0.004 & 22.69 & 0.126 & 0.901 & 0.007\\
      \textit{stlm} & 0.770 & - & 22.05 & - & 0.882 & -\\
+     \textit{hybrid-nows-ets} & 0.759 & 0.001 & 22.16 & 0.026 & 0.875 & 0.001\\
      \textit{tbats} & 0.745 & - & 21.13 & - & 0.850 & -\\
@@
      \textit{arima} & 0.821 & - & 23.69 & - & 0.951 & -\\
+     \textit{ets} & 0.801 & - & 24.18 & - & 0.944 & -\\
+     \textit{hybrid-nows-ets} & 0.768 & 0.002 & 22.91 & 0.111 & 0.902 & 0.005\\
      \textit{stlm} & 0.765 & - & 22.22 & - & 0.885 & -\\
@@
 \label{tab:metricresults}
+\end{table*}
+
+\begin{table*}
+  \caption{\textit{tbats} model confusion matrix}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 327 & 1607 & 82 \\
+    true-flat-trend & 195 & 5586 & 232 \\
+    true-inc-trend & 68 & 1585 & 318 \\
+    \hline
+  \end{tabular}
+  \caption{\textit{hybrid} model confusion matrix}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 250 & 1747 & 19 \\
+    true-flat-trend & 131 & 5802 & 80 \\
+    true-inc-trend & 33 & 1639 & 299 \\
+    \hline
+  \end{tabular}
+  \caption{\textit{hybrid-withws} model confusion matrix}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 615 & 1365 & 36 \\
+    true-flat-trend & 510 & 5374 & 129 \\
+    true-inc-trend & 65 & 1444 & 462 \\
+    \hline
+  \end{tabular}
+\label{tab:tbatsclass}
+\end{table*}
+
+\begin{table*}
+  \caption{\textit{lstm} model confusion matrix}
+  \centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 447 & 1539 & 30 \\
+    true-flat-trend & 444 & 5324 & 245 \\
+    true-inc-trend & 66 & 1410 & 495 \\
+    \hline
+  \end{tabular}
+  \caption{\textit{lstm-withws} model confusion matrix}
+  %\centering
+  \begin{tabular}{llll}
+    \hline
+    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
+    \hline
+	true-dec-trend & 796 & 1161 & 59 \\
+    true-flat-trend & 1053 & 4701 & 259 \\
+    true-inc-trend & 90 & 1259 & 622 \\
+    \hline
+  \end{tabular}
+\label{tab:lstmclass}
 \end{table*}

### 2021-12-01 hermes_paper/hermes_paper.tex
add new dir hybrid model paper

--- 2021-12-01 iclr2022/hybridmodel_iclr.tex
@@
 \usepackage{graphicx}
-
-\title{Hybrid recurrent model for regime switching nonstationary time series}
+%\setlength{\tabcolsep}{10pt}
+%\renewcommand{\arraystretch}{1.5}
+
+\title{HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series}
 
@@
 \newcommand{\stat}{f}
-\newcommand{\statparam}{\theta_{stat}}
+\newcommand{\statparam}{\theta_{predictor}}
 \newcommand{\fullstat}{{\bf \stat}}
@@
 \newcommand{\meants}{\Bar{\ts}}
-\newcommand{\rnnwindow}{{\bf \rnn}}
-\newcommand{\rnn}{z}
+\newcommand{\rnnwindow}{{\bf \rnninput}}
+\newcommand{\rnninput}{z}
+\newcommand{\rnn}{\textsc{rnn}}
+\newcommand{\rnnparam}{\theta_{corrector}}
 \newcommand{\err}{err}
@@
 \newcommand{\classifier}{\mathrm{RNN}_c}
-\newcommand{\rnnparam}{\theta}
 \newcommand{\remainder}{r}
@@
 This hidden state is assumed to be a Markov chain such that at each time step the received observation is a random function of the corresponding latent data.
-Although hidden states are modeled as a Markov chain (or a mixing process)  the observations arising therefrom present a highly complex statistical structure.
+Although hidden states are modeled as a Markov chain (or a mixing process), the observations arising therefrom present a highly complex statistical structure.
 %Introducing latent hidden states, they assume that the predictive distribution is not unique and constant in time but multiple and lead by the values of the hidden states changing during time.
@@
 
-Following this work, we present in this paper a new hyrbid recurrent model for time series forecasting with inclusion of external weak signals.
+%Following this work, we present in this paper a new hyrbid recurrent model for time series forecasting with inclusion of external weak signals.
 %We design a more general hybrid framework including the original multiplicative model and a new additive one.
-Our approach enriches existing hybrid models by incorporating an unobserved regime switching feature to account for the need of a neural network based correction.
+%Our approach enriches existing hybrid models by incorporating an unobserved regime switching feature to account for the need of a neural network based correction.
 In order to leverage external signals, we modify the hybrid framework to allow the regime shift and the  global error-corrector neural network to deal with external data.
+
+Following this work, we present in this paper HERMES, a new hybrid recurrent model time series forecasting with inclusion of external weak signals.
 By adding our fashion external weak signals in our proposed framework, we show the real potential of the hybrid approach: a global neural network, able to leverage large amount of data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of any parametric models.
+%Our new hybrid framework is divided in two parts.
+As a first step, we compute a per-time-series forecast for each trend using any kind of parametric models.
+Then, gathering information of the first prediction and external variables, a global error corrector neural network is trained to correct weaknesses of the first forecast.
 
@@
 We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
-We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of two RNN.
+%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of two RNN.
 We use a per time series statistical model to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
 Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
+We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model and a global error-corrector neural network train on all the time series.
+We use a per time series parametric model to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
+Then, gathering information of the first prediction and external variables, we use a recurrent neural networks to correct the predictions provided by the first collection of per-time-series models.
 
@@
 
-\subsection{Per time series statistical model}
+\subsection{Per time series predictor}
 %The first step in our additive hybrid model is to consider, for each time series, an exponential smoothing  statistical model.
@@
 $m \in \mathbb{N}$ is the seasonality (4 for quarterly, 12 for monthly or 52 for weekly time series).
-The time-series-specific models compute, for each sequence, a first $\lag$-ahead prediction based on the past.
-For all $1\leqslant n \leqslant N$, we note $\stat^n_{\statparam^n}$ the $n$-th parametric model of the the $n$-th sequence where $\statparam^n$ are  unknown parameters.
-Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$ and the estimated  parameters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the time-series-specific forecasts $\{\tspred^{stat,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+The time-series-specific predictors compute, for each sequence, a first $\lag$-ahead prediction based on the past.
+For all $1\leqslant n \leqslant N$, we note $\stat^n(.;statparam^n)$ the $n$-th parametric model of the $n$-th sequence where $\statparam^n$ are  unknown parameters.
+Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$ and the estimated  parameters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the time-series-specific forecasts $\{\tspred^{pred,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
 $$
-\tspred^{stat,n}_{T+i|T} = \stat^n_{\statparam^n}(\ts^n_{1:T})_i\,.
+\tspred^{pred,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i\,.
 $$
 
-During the M4 competition, the hybrid model of \cite{smyl2020hybrid} is based on a multiplicative exponential smoothing model as the time-series-specific model.
+During the M4 competition, the hybrid model of \cite{smyl2020hybrid} was based on a multiplicative exponential smoothing model as the time-series-specific predictor.
 However, on sporadic time series, this choice could lead to poor result and instability.
@@
 The first one use an  exponential smoothing as reference similar to \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results.
-The main complexity is in the next stage: training a global RNN to correct the per-time-series statistical models when the statistical models provide poor performance.
-\textcolor{red}{Plutot dire ici que l'on souhaite corriger des erreurs specifiques: et introduire les types de trends mal predites que l'on souhaite corriger.}
+The main complexity is in the next stage: training a global RNN corrector to improve the per-time-series statistical models when the parametric models start showing weaknesses.
+
+As weakness to correct, we detected and defined two main forms for a univariate parametric forecast as define above.
+The first one is a weakness of definition, when the model is not well define for its forecasting task.
+For instance, an additive model provide good predictions on time series with additive seasonality but show difficulties with multiplicative one.
+The second form, harder to detect and correct, is the weakness of information.
+For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence.
+In somes cases, these changes depend on external variables not considered by univariate parametric models.
+The difficulty is that we mainly unknow the exact influence of external variables on the main signal.
+It is on this point that our new hybrid framework shows its true potential: introduce a global RNN train on all the time series and able to consider and leverage external signals.\textcolor{red}{Plutot dire ici que l'on souhaite corriger des erreurs specifiques: et introduire les types de trends mal predites que l'on souhaite corriger.}
 % Indeed, depending on time series, some family of parametric models can achieve really heterogeneous level of accuracy. 
@@
 
-\subsection{Regime switching error-corrector recurrent model}
-
-%At this stage, we want to train a global RNN, trained on all the N sequences and able to understand and correct the weaknesses of the first per-time-series parametric models.
+\subsection{Error-corrector recurrent model}
+
+At this stage, we want to train a global RNN, trained on all the N sequences and able to understand and correct the weaknesses of the first per-time-series parametric models.
+This task requires a thorough data pre-processing for two main reasons.
+Firstly, we want to give to the RNN the best input in order to understand the first collection of forecasts and predict their future errors.
+Secondly,as we did not suppose any assumption about the scale of our time series, we have to carefully normalize them before feeding our RNN with.
+In this way, we define the following pre-processing :
 %At this stage, we can write that for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
@@
 %$$
-In this paper, we introduce a model based on a latent regime.
+%In this paper, we introduce a model based on a latent regime.
 In regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence and the final forecast of our framework is the prediction of the per-time-series parametric model.
@@
 % quantity that we note $\remainder$.
-Conditionally on $\{\fullts^n\}_{1\leqslant n\leqslant N}$, our regime-switching model is:
-
-$$
-\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \hiddenregime^n_T \cdot \remainder^{n}_{T+i} + \varepsilon^n_{T+i} = \stat^n_{\statparam^n}(\ts^n_{1:T})_i + \hiddenregime^n_T \cdot \remainder^{n}_{T+i} + \varepsilon^n_{T+i}\,,
-$$
-where $\{\varepsilon^n_{T+i}\}_{1\leqslant i\leqslant \lag}$ are independent random variables, $U^n_T$ is an unobserved regime switching Bernoulli random variable and $\{\remainder^n_{T+i}\}_{1\leqslant i\leqslant \lag}$ is the random error term to be estimated.
+%Conditionally on $\{\fullts^n\}_{1\leqslant n\leqslant N}$, our regime-switching model is:
+
+%$$
+%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \hiddenregime^n_T \cdot \remainder^{n}_{T+i} + \varepsilon^n_{T+i} = \stat^n_{\statparam^n}(\ts^n_{1:T})_i + \hiddenregime^n_T \cdot \remainder^{n}_{T+i} + \varepsilon^n_{T+i}\,,
+%$$
+%where $\{\varepsilon^n_{T+i}\}_{1\leqslant i\leqslant \lag}$ are independent random variables, $U^n_T$ is an unobserved regime switching Bernoulli random variable and $\{\remainder^n_{T+i}\}_{1\leqslant i\leqslant \lag}$ is the random error term to be estimated.
 %In the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainder$.
@@
 
-To estimate this model, we introduce our new regime swithing error-corrector framework.
+%To estimate this model, we introduce our new regime swithing error-corrector framework.
 We train two global RNN on all sequences, a classifier ($\classifier$) and a predictor ($\predictor$).
@@
 Let $\window \in \mathbb{N}$ be the window size, usually this window is equal to the forecast horizon $\window = \lag$.
-Consider the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnn^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$,
+We define as our RNN input the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$,
 $$
-\rnn^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{stat,n}_{T-w+i|T}}{\meants^n_T}\,,
+\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+i|T}}{\meants^n_T}\,,
 $$
 where $ \meants^n_T = \sum_{i = 1}^{w}  \ts^n_{T-w+i}/w$.
-We use this sequence as input of  $\classifier$ and $\predictor$.
+
+We note $\rnn(.;\rnnparam)$ the recurrent neural network model where $\rnnparam$ are  unknown parameters.
+Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\{\rnnparam\}$, the error-corrector predictions $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+$$
+\tspred^{corr,n}_{T+i|T} = \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\ \,.
+$$
+
+Our hybrid model forecast is finally given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by:
+
+\begin{equation}
+\label{eq:nows:full:model}
+\tspred^n_{T+i|T}  = \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\
+\end{equation}
+
+%We use this sequence as input of  $\classifier$ and $\predictor$.
 %Write, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,H\}$, $\err^{n,T}_{T+i|T} = \ts^n_{T+i} - \etspred^{ets,n}_{T+i|T}$.
- Given $\rnnwindow^n_T$, the proposed regime swithing error-corrector reccurent model is given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by :
-\begin{align*}
-\ts^n_{T+i}  &= \tspred^{stat,n}_{T-w+i|T} +  \hat{\hiddenregime}^n_T \cdot \hat{\remainder}^{n}_{T+i} + \varepsilon^n_{T+i}\,, \\
-\hat{\hiddenregime}^n_T &= \mathbf{1}_{\classifier(\rnnwindow^n_T) > \threshold}\,, \\
-\hat{\remainder}^{n}_{T+i} &= \predictor(\rnnwindow^n_T)_{T+i} \cdot \meants^n_T\,.
-\end{align*}
-
-where $\mathbf{1}$ is the indicator function and $\threshold$ a threshold parameter.
+% Given $\rnnwindow^n_T$, the proposed regime swithing error-corrector reccurent model is given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by :
+%\begin{align*}
+%\ts^n_{T+i}  &= \tspred^{stat,n}_{T-w+i|T} +  \hat{\hiddenregime}^n_T \cdot \hat{\remainder}^{n}_{T+i} + \varepsilon^n_{T+i}\,, \\
+%\hat{\hiddenregime}^n_T &= \mathbf{1}_{\classifier(\rnnwindow^n_T) > \threshold}\,, \\
+%\hat{\remainder}^{n}_{T+i} &= \predictor(\rnnwindow^n_T)_{T+i} \cdot \meants^n_T\,.
+%\end{align*}
+
+%where $\mathbf{1}$ is the indicator function and $\threshold$ a threshold parameter.
 
@@
 
-Using a time-series-specific statistical model, the hybrid network achieves striking accuracy on single sequences.
-Then, the shared recurrent neural network relies on the strength of machine learning methods at leveraging a huge quantities of heterogeneous data.
+Using well-fitted time-series-specific parametric models, our hybrid network corrects the first form of weakness and achieves striking accuracy on our dataset.
+Then, for the second form of weakness, the shared recurrent neural network relies on the strength of machine learning methods at leveraging a huge quantities of heterogeneous data.
 In addition to the $N$ target time series, we consider $K \times N$ external sequences indexed from $0$ to $T$.
@@
 $$
-\fullconcatinput^n_T = \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}= \{\rnn^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
+\fullconcatinput^n_T = \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}= \{\rnninput^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
 $$
@@
 \begin{equation}
-\label{eq:full:model}
-\ts^n_{T+i}  = \tspred^{stat,n}_{T-w+i|T} +  \mathbf{1}_{\classifier(\fullconcatinput^n_T) > \threshold} \cdot \predictor(\fullconcatinput^n_T)_{T+i} \cdot \meants^n_T + \varepsilon^n_{T+i}\,,
+\label{eq:withws:full:model}
+\tspred^n_{T+i|T}  = \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\fullconcatinput^n_T;\rnnparam)_i \cdot \meants^n_T\
 \end{equation}
+
 An illustration of our proposed architecture is displayed in Figure~\ref{fig:architecture}.
@@
   \centering
-    \includegraphics[width=1\linewidth]{figure/Regime_switching_recurrent_model}
+    \includegraphics[width=1\linewidth]{figure/HERMES_archi.png}
   \caption{Hybrid model with weak signals architecture.}
@@
 
-\subsection{Hidden regime}
-
-As the regime is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
+%\subsection{Hidden regime}
+
+%As the regime is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
 Therefore we use Fisher's identity to compute the score function and write a gradient ascent algorithm to estimate simultaneously the weights of RNN-p and of RNN-c denoted by $\rnnparam = \{\rnnparam_c,\rnnparam_p\}$.
 The score is
-\begin{equation}
-\label{eq:score}
-\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h}\right]\,,
-\end{equation}
-where the joint likelihood $p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T}) = p_\theta(U_T^n|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$ is given by \eqref{eq:full:model} and the expectation is under the posterior distribution of $U_T^n$ given $\ts^n_{1:T+h}$.
+%\begin{equation}
+%\label{eq:score}
+%\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h}\right]\,,
+%\end{equation}
+%where the joint likelihood $p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T}) = p_\theta(U_T^n|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$ is given by \eqref{eq:full:model} and the expectation is under the posterior distribution of $U_T^n$ given $\ts^n_{1:T+h}$.
 Write $\omega_p^n = \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T+h})$.
 Note that
-$$
-\omega^n \propto \mathbb{P}_{\theta}(U_T^n = 1|\ts^n_{1:T})p_{\theta}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\,,
-$$
-where $ \mathbb{P}_{\theta}(U_T^n = 1|\ts^n_{1:T})$ is parameterized by $\classifier$ and the predictive probability density $p_{\theta}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})$ is parameterized by $\predictor$ and the statistical model.
-Then, by \eqref{eq:score},
-\begin{multline*}
-\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \omega^n\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})\\
-+ (1-\omega^n)\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,.
-\end{multline*}
-The loss function is then given by
-$$
-\theta\mapsto - \omega^n \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})- (1-\omega^n) \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,.
-$$
-A complete description of the training process can be found in Appendix.
+%$$
+%\omega^n \propto \mathbb{P}_{\theta}(U_T^n = 1|\ts^n_{1:T})p_{\theta}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\,,
+%$$
+%where $ \mathbb{P}_{\theta}(U_T^n = 1|\ts^n_{1:T})$ is parameterized by $\classifier$ and the predictive probability density $p_{\theta}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})$ is parameterized by $\predictor$ and the statistical model.
+%Then, by \eqref{eq:score},
+%\begin{multline*}
+%\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \omega^n\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})\\
+%+ (1-\omega^n)\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,.
+%\end{multline*}
+%The loss function is then given by
+%$$
+%\theta\mapsto - \omega^n \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})- (1-\omega^n) \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,.
+%$$
+%A complete description of the training process can be found in Appendix.
 
@@
   \centering
-  \resizebox{\textwidth}{!}{
-  \begin{tabular}{lllllllllll}
-    \hline
-    &  Top  & Pants & Short & Skirt & Dress & Coat & Shoes & Color & Texture &  \\
-    \hline
-United States & 411/208 & 149/112 & 47/22 & 29/- & 20/- & 208/151 & 293/86 & 38/44 & 85/81\\
-     Europe & 409/228 &  134/114 & 48/21 & 28/- & 20/- & 211/159 & 303/78 & 41/42 & 87/74\\
-     Japan &  403/218 & 136/107 & 49/31 & 28/- &  23/- & 185/149 &  311/78 & 46/42 &  92/65\\
-     China &  424/202 & 147/114 & 46/29 & 27/- &  27/- & 178/161 &  310/78 & 41/47 &  88/77\\
-     Brazil &  431/222 & 134/117 & 49/27 & 30/- &  28/- & 203/152 & 311/76 & 48/41 & 107/84\\
-     \hline
-     Total & 2078/1078 & 700/564 & 239/130 & 142/- & 118/- & 985/772 & 1528/396 & 214/216 & 459/381 & \numberts\\
-    \hline
+  \resizebox{0.85\width}{!}{
+  \begin{tabular}{l||llllllllll}
+    %hline
+    \\
+    &  \textbf{Top}  & \textbf{Pants} & \textbf{Short} & \textbf{Skirt} & \textbf{Dress} & \textbf{Coat} & \textbf{Shoes} & \textbf{Color} & \textbf{Texture} &  \\
+    \hline
+    \hline
+    \\
+\textbf{United States} & 411/208 & 149/112 & 47/22 & 29/- & 20/- & 208/151 & 293/86 & 38/44 & 85/81\\
+     \textbf{Europe} & 409/228 &  134/114 & 48/21 & 28/- & 20/- & 211/159 & 303/78 & 41/42 & 87/74\\
+     \textbf{Japan} &  403/218 & 136/107 & 49/31 & 28/- &  23/- & 185/149 &  311/78 & 46/42 &  92/65\\
+     \textbf{China} &  424/202 & 147/114 & 46/29 & 27/- &  27/- & 178/161 &  310/78 & 41/47 &  88/77\\
+     \textbf{Brazil} &  431/222 & 134/117 & 49/27 & 30/- &  28/- & 203/152 & 311/76 & 48/41 & 107/84\\
+     \\
+     %\hline
+     \textbf{Total} & 2078/1078 & 700/564 & 239/130 & 142/- & 118/- & 985/772 & 1528/396 & 214/216 & 459/381 & \textbf{\numberts}\\
+    %\hline
   \end{tabular}
@@
   \centering
-    \includegraphics[width=1.\linewidth]{figure/emergering_trend.png}
+    \includegraphics[width=1.\linewidth]{figure/emerging_trend}
   \caption{A shoes trend of our dataset.
@@
 
-To train our hybrid model, we split our dataset into three blocks, train,eval and test sets.
+To train our hybrid model, we split our dataset into three blocks, train, eval and test sets.
 We use the 3 first years as our train set, we keep the 4th year for our eval set and we hide the last year for our test set.
-Each set is made of weekly time series.
-We train our hyrid model to compute a one-year ahead prediction with $\window$ and $\lag$ equal to 52.
-In order to increase our train set, we use a moving window that provide 53 input/output couples per sequences, being 530000 couples in total.
-An example of our splitting is shown in  Figure~\ref{fig:train_eval_test_set}.
-All our code is developed in Python using the Tensorflow library.
-It allows the use of a GPU to speed up the trainig process.
+We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52.
+Using the two first year of our train set, we fit a first per-time-series parametric model for each time series.
+With the resulting collection of local models, we compute a first forecast of the third year for each sequence.
+Using these forecasts, we preprocess our time series and finally determine our RNN inputs.
+We can, then, train our RNN at understanding and correcting the previous collection of parametric model's forecasts.
+In the same way, for the eval set, we fit a second time our per-time-series predictors using the three first years and we forecast the fourth year.
+We preprocess our time series and we evaluate how our error-corrector RNN is able to improve the first collection of predictions of the fourth year.
+At the end, we repeat the same process for the last year and compute our final accuracy measures. An example of our splitting is shown in  Figure~\ref{fig:train_eval_test_set}.
+%We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52.
+For each time series, we fitted 3 per-time-series parametric models: We fit the first one using the 2 first years and compute a forecast of the thrid year.
+
+%In order to increase our train set, we use a moving window that provide 53 input/output couples per sequences, being 530000 couples in total.
 
@@
 This model is also compared to an hybrid model with an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}.
-For $\classifier$ and $\predictor$, we built an architecture summarized in Figure~\ref{fig:rnnarchi}.
-There are both composed of 3 LSTM layer and a different final Dense layer to provide the correct output.
-After the $\classifier$ final dense layer, we add a sigmoid activation to return a probability.
-We use 2 Adam otpimizers with the same learning rate equal to $5\cdot 10^{-6}$ and the batch size is  64.
-The eval set is used to fix the $\threshold$ parameter that determine, depending of the output of $\predictor$, when use the $\predictor$ correction.
+For the neural network part, we built an architecture summarized in Figure~\ref{fig:rnnarchi}.
+It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension.
+We use a classical Adam otpimizer with a learning rate equal to 0.005 and a batch size equal to 64.
+For our loss function, we tested several metrics and we finally converged on the following one :
+
+$$
+l(\ts^n_{T+1:T+\lag},\tspred^n_{T+1:T+\lag|T}) = \frac{\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|}{\meants^n_T}
+$$
+%
+
+All our code is developed in Python using the Tensorflow library. It allows the use of a GPU to speed up the trainig process.
 
@@
   \centering
-    \includegraphics[width=0.8\linewidth]{figure/rnn_archi}
+    \includegraphics[width=0.8\linewidth]{figure/lstm_archi}
   \caption{$\classifier$ and $\predictor$ architecture.}
@@
 
-Against these models, we propose two versions of our regime switching hybrid recurrent model (rshm) called respectively rshm-ets and rshm-tbats according to the per-time-series model choice.
+Against these models, we propose two versions of our hybrid model (hermes) called respectively hermes-ets and herles-tbats according to the per-time-series model choice.
 %Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}.
@@
 %To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}). 
-For our two versions, we propose a version without our weak signal called \textit{rshm-ets} and \textit{rshm-tbats}.
+For our two versions, we propose a version without our weak signal called \textit{hermes-ets} and \textit{hermes-tbats}.
 Then we evaluate our hybrid framework with the inclusion of our weak signals (ws) referred to as \textit{rshm-ets-ws} and \textit{rshm-tbats-ws}.
@@
 On the test set, the year 2019, we have 1871 increasing trends, 2016 decreasing trends and 6113 flat trends.
-In addition to the accuracy metrics, we also compare the different methods on this classification task.
+In addition to the accuracy metrics, we also compare the different methods on this classification task and especially difference between methode using weak signal or not.
 
@@
 For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
+  %\centering
   \centering
-  \begin{tabular}{lllllll}
-    \hline
-    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
-    \hline
-     \textit{snaive} & 0.881 & - & 25.27 & - & 1. & -\\
-     \textit{thetam}  & 0.844 & - & 24.17 & - & 0.970 & -\\
-     \textit{arima} & 0.826 & - & 23.63 & - & 0.949 & -\\
-     \textit{ets} & 0.807 & - & 23.58 & - & 0.937 & -\\
-     \textit{hybrid-withws-ets} & 0.769 & 0.004 & 22.69 & 0.126 & 0.901 & 0.007\\
-     \textit{stlm} & 0.770 & - & 22.05 & - & 0.882 & -\\
-     \textit{hybrid-nows-ets} & 0.759 & 0.001 & 22.16 & 0.026 & 0.875 & 0.001\\
-     \textit{tbats} & 0.745 & - & 21.13 & - & 0.850 & -\\
-     \textit{lstm-withws} & 0.728 & 0.004 & 20.18 & 0.085 & 0.837 & 0.004\\
-     \textit{lstm-nows} & 0.724 & 0.003 & 20.08 & 0.052  & 0.825 & 0.004\\
-     \textit{hybrid-withws} & 0.713 & 0.005 & 20.53 & 0.170 & 0.825 & 0.009\\
-     \textit{hybrid-nows} & 0.715 & 0.002 & 20.41 & 0.056 & 0.816 & 0.002\\
-    \hline
+  \resizebox{1.2\width}{!}{
+  \begin{tabular}{l||llllllllll}
+   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
+    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
+    \hline
+	\hline
+     \textit{snaive} && 0.881 & - && 25.27 & - && 1. & -\\
+     \textit{thetam}  && 0.844 & - && 24.17 & - && 0.970 & -\\
+     \textit{arima} && 0.826 & - && 23.63 & - && 0.949 & -\\
+     \textit{ets} && 0.807 & - && 23.58 & - && 0.937 & -\\
+     \textit{hybrid-withws-ets} && 0.769 & 0.004 && 22.69 & 0.126 && 0.901 & 0.007\\
+     \textit{stlm} && 0.770 & - && 22.05 & - && 0.882 & -\\
+     \textit{hybrid-nows-ets} && 0.759 & 0.001 && 22.16 & 0.026 && 0.875 & 0.001\\
+     \textit{tbats} && 0.745 & - && 21.13 & - && 0.850 & -\\
+     \textit{lstm-withws} && 0.728 & 0.004 && 20.18 & 0.085 && 0.837 & 0.004\\
+     \textit{lstm-nows} && 0.724 & 0.003 && 20.08 & 0.052  && 0.825 & 0.004\\
+     \textit{hybrid-withws} && 0.713 & 0.005 && 20.53 & 0.170 && 0.825 & 0.009\\
+     \textbf{\textit{hybrid-nows}} && \textbf{0.715} & 0.002 && \textbf{20.41} & 0.056 && \textbf{0.816} & 0.002\\
+    %\hline
   \end{tabular}
+  }
 \label{tab:metricresults}
@@
 
-\bibliography{iclr2022_conference}
-\bibliographystyle{iclr2022_conference}
+\bibliography{hermes_paper}
+\bibliographystyle{hermes_paper}
 
@@
 
-\section{Hidden regime algorithm}
-
-In our framework, we assume that our sequence are generated with 2 hidden regime.
+%\section{Hidden regime algorithm}
+%
+%In our framework, we assume that our sequence are generated with 2 hidden regime.
 As this regime, noted $\hiddenregime$, is never observed, we use the Expectation Maximization (EM) algorithm to write our loss function:
-We note $\rnnparam^{(t)} = \{\rnnparam_c^{(t)},\rnnparam_p^{(t)}\}$ the weights of $\classifier$ and of $\predictor$ at a fixed epoch $t$.
-
-As the EM algorithm, we want to compute the following value :
-
-\begin{align}
-\mathbb{Q}^n(\rnnparam|\rnnparam^{(t)}) &= \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h},\rnnparam^{(t)}\right]\ \\
-& = \sum_{j} p(U_T^n = j|\ts^n_{1:T+h},\rnnparam^{(t)}) \times \textcolor{red}{\nabla_\theta} \log p_\theta(\ts^n_{T+1:T+h},U_T^n = j|\ts^n_{1:T}) \\
-& = \sum_{j} p(U_T^n = j|\ts^n_{1:T+h},\rnnparam^{(t)}) \times \textcolor{red}{\nabla_\theta}\log[p_\theta(U_T^n = j|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n = j,\ts^n_{1:T})]
-\end{align}
-
-where $ \mathbb{P}_{\theta}(U_T^n = 1|\ts^n_{1:T})$ is parameterized by $\classifier$ and the predictive probability density $p_{\theta}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})$ is parameterized by $\predictor$ and the statistical model.
-
-Write $\omega_{\rnnparam^{(t)}}^n = \mathbb{P}(U_T^n = 1|\ts^n_{1:T+h},\rnnparam^{(t)})$. We have:
-
-\begin{align*}
-\omega_{\rnnparam^{(t)}}^n &= \mathbb{P}_(U_T^n = 1|\ts^n_{1:T+h},\rnnparam^{(t)}) \\
-& =  \frac{p(\ts^n_{T+1:T+h},U_T^n = 1|\ts^n_{1:T},\rnnparam^{(t)})}{p_(\ts^n_{T+1:T+h}|\ts^n_{1:T})} \\
-& =  \frac{p(\ts^n_{T+1:T+h}|U_T^n = 1,\ts^n_{1:T},\rnnparam^{(t)}) \times p(U_T^n = 1|\ts^n_{1:T},\rnnparam^{(t)})}{\sum_{U_T^n}p(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T},\rnnparam^{(t)}) \times p(U_T^n|\ts^n_{1:T},\rnnparam^{(t)})}
-\end{align*}
-
-where , $\mathbb{P}(U_T^n=1|\ts^n_{1:T},\rnnparam^{(t)})$ is the output of $\classifier$ at epoch $t$ and the predictive probability density $p(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})$ is compute with the output of $\predictor$ at epoch $t$.
-
-To compute our final loss function, we have to define the predictive probability density $p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$.
-
-In our model final equation~\ref{eq:full:model}, we assume that $\varepsilon^n_{T+i}$ are independent and follow a Laplace distribution.
-
-We have for the regime 0 :
-
-\begin{align*}
-p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) &= \prod_{i=1}^{h}\frac{1}{2b}e^{\frac{1}{b}|\ts^n_{T+i}  - \tspred^{stat,n}_{T+i|T}|} \\
-& = \frac{1}{(2b)^h}e^{\frac{1}{b}\sum_{i=1}^{h}|\ts^n_{T+i}  - \tspred^{stat,n}_{T+i|T}|}
-\end{align*}
-
-and for the regime 1 :
-\begin{align*}
-p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) &= \frac{1}{(2b)^h}e^{\frac{1}{b}\sum_{i=1}^{h}|\ts^n_{T+i}  - \tspred^{stat,n}_{T-w+i|T}-\meants^n_T \cdot \predictor(\fullconcatinput^n_T)_{T+i} |}
-\end{align*}
-
-with $b$ and constant that we fixed at $ \meants^n_T = \sum_{i = 1}^{w}  \ts^n_{T-w+i}/w$.
-
-Finally, we have all the values to compute the loss function :
-
-$$
-\theta\mapsto - \omega_{\rnnparam^{(t)}}^n \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})
-- (1-\omega_{\rnnparam^{(t)}}^n) \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,, \\
-$$
-where no gradient is computed on $\omega_{\rnnparam^{(t)}}^n$.
+%%We note $\rnnparam^{(t)} = \{\rnnparam_c^{(t)},\rnnparam_p^{(t)}\}$ the weights of $\classifier$ and of $\predictor$ at a fixed epoch $t$.
+%
+%As the EM algorithm, we want to compute the following value :
+%
+%\begin{align}
+%\mathbb{Q}^n(\rnnparam|\rnnparam^{(t)}) &= \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h},\rnnparam^{(t)}\right]\ \\
+%& = \sum_{j} p(U_T^n = j|\ts^n_{1:T+h},\rnnparam^{(t)}) \times \textcolor{red}{\nabla_\theta} \log p_\theta(\ts^n_{T+1:T+h},U_T^n = j|\ts^n_{1:T}) \\
+%& = \sum_{j} p(U_T^n = j|\ts^n_{1:T+h},\rnnparam^{(t)}) \times \textcolor{red}{\nabla_\theta}\log[p_\theta(U_T^n = j|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n = j,\ts^n_{1:T})]
+%\end{align}
+%
+%where $ \mathbb{P}_{\theta}(U_T^n = 1|\ts^n_{1:T})$ is parameterized by $\classifier$ and the predictive probability density $p_{\theta}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})$ is parameterized by $\predictor$ and the statistical model.
+%
+%Write $\omega_{\rnnparam^{(t)}}^n = \mathbb{P}(U_T^n = 1|\ts^n_{1:T+h},\rnnparam^{(t)})$. We have:
+%
+%\begin{align*}
+%\omega_{\rnnparam^{(t)}}^n &= \mathbb{P}_(U_T^n = 1|\ts^n_{1:T+h},\rnnparam^{(t)}) \\
+%& =  \frac{p(\ts^n_{T+1:T+h},U_T^n = 1|\ts^n_{1:T},\rnnparam^{(t)})}{p_(\ts^n_{T+1:T+h}|\ts^n_{1:T})} \\
+%& =  \frac{p(\ts^n_{T+1:T+h}|U_T^n = 1,\ts^n_{1:T},\rnnparam^{(t)}) \times p(U_T^n = 1|\ts^n_{1:T},\rnnparam^{(t)})}{\sum_{U_T^n}p(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T},\rnnparam^{(t)}) \times p(U_T^n|\ts^n_{1:T},\rnnparam^{(t)})}
+%\end{align*}
+%
+%where , $\mathbb{P}(U_T^n=1|\ts^n_{1:T},\rnnparam^{(t)})$ is the output of $\classifier$ at epoch $t$ and the predictive probability density $p(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})$ is compute with the output of $\predictor$ at epoch $t$.
+%
+%To compute our final loss function, we have to define the predictive probability density $p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$.
+%
+%In our model final equation~\ref{eq:full:model}, we assume that $\varepsilon^n_{T+i}$ are independent and follow a Laplace distribution.
+%
+%We have for the regime 0 :
+%
+%\begin{align*}
+%p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) &= \prod_{i=1}^{h}\frac{1}{2b}e^{\frac{1}{b}|\ts^n_{T+i}  - \tspred^{stat,n}_{T+i|T}|} \\
+%& = \frac{1}{(2b)^h}e^{\frac{1}{b}\sum_{i=1}^{h}|\ts^n_{T+i}  - \tspred^{stat,n}_{T+i|T}|}
+%\end{align*}
+%
+%and for the regime 1 :
+%\begin{align*}
+%p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) &= \frac{1}{(2b)^h}e^{\frac{1}{b}\sum_{i=1}^{h}|\ts^n_{T+i}  - \tspred^{stat,n}_{T-w+i|T}-\meants^n_T \cdot \predictor(\fullconcatinput^n_T)_{T+i} |}
+%\end{align*}
+%
+%with $b$ and constant that we fixed at $ \meants^n_T = \sum_{i = 1}^{w}  \ts^n_{T-w+i}/w$.
+%
+%Finally, we have all the values to compute the loss function :
+%
+%$$
+%\theta\mapsto - \omega_{\rnnparam^{(t)}}^n \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})
+%- (1-\omega_{\rnnparam^{(t)}}^n) \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,, \\
+%$$
+%where no gradient is computed on $\omega_{\rnnparam^{(t)}}^n$. 
+%
 

### 2021-12-01 hermes_paper/hermes_paper.tex
a few updates

@@
 
-Following this work, we present in this paper HERMES, a new hybrid recurrent model time series forecasting with inclusion of external weak signals.
-By adding our fashion external weak signals in our proposed framework, we show the real potential of the hybrid approach: a global neural network, able to leverage large amount of data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of any parametric models.
+Following this work, we present in this paper HERMES, a new hybrid recurrent model for time series forecasting with inclusion of external signals.
+Our new framework is divided in two levels: local predictors and a global corrector.
+In a first time, given a group of sequence, we compute a per-time-series prediction using any kind of parametric models.
+In a second time, we train a global neural network to understand, evaluate and correct the forecast weaknesses of the first collection of models.
+By adding external weak signals in our proposed framework, we show the real potential of the hybrid approach: a global neural network, able to leverage large amount of data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of any parametric models.
 %Our new hybrid framework is divided in two parts.
@@
 
+%Section~\ref{sec:hybrid} describes our hybrid framework which consists of a per-time-series parametric model and a recurrent neural network combining the target sequences with external weak signals
+
 The paper is organized as follow.
-Section~\ref{sec:hybrid} describes our hybrid framework which consists of a per-time-series parametric model and a recurrent neural network combining the target sequences with external weak signals.
+Section~\ref{sec:hybrid} describes our hybrid framework.
 Then, we present our new fashion dataset in Section~\ref{sec:dataset}.
 Section~\ref{sec:exp} describes our results and comparisons with several benchmarks.
-Finally, we conclude our paper and detail research perspectives in Section~\ref{sec:discussion}.
+Finally, we conclude our paper and detail research perspectives in Section~\ref{sec:discussion} and Section~\ref{sec:conclusion}.
 
@@
 Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
-We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model and a global error-corrector neural network train on all the time series.
-We use a per time series parametric model to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
-Then, gathering information of the first prediction and external variables, we use a recurrent neural networks to correct the predictions provided by the first collection of per-time-series models.
+We introduce a new hybrid approach for time series forecasting  composed of two parts: first per-time-series parametric models, the predictors, and a global error-corrector neural network train on all the time series, the corrector.
+We use  per-time-series parametric models to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
+Then, gathering information of the first predictions and external variables, we use a recurrent neural networks to correct the predictions provided by the first collection of per-time-series models.
 
@@
 
-\subsection{Per time series predictor}
+\subsection{Per-time-series predictors}
 %The first step in our additive hybrid model is to consider, for each time series, an exponential smoothing  statistical model.
@@
 The time-series-specific predictors compute, for each sequence, a first $\lag$-ahead prediction based on the past.
-For all $1\leqslant n \leqslant N$, we note $\stat^n(.;statparam^n)$ the $n$-th parametric model of the $n$-th sequence where $\statparam^n$ are  unknown parameters.
+For all $1\leqslant n \leqslant N$, we note $\stat^n(.;\statparam^n)$ the $n$-th parametric model of the $n$-th sequence where $\statparam^n$ are  unknown parameters.
 Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$ and the estimated  parameters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the time-series-specific forecasts $\{\tspred^{pred,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
@@
 
-Let $\window \in \mathbb{N}$ be the window size, usually this window is equal to the forecast horizon $\window = \lag$.
+Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$.
 We define as our RNN input the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$,
@@
 $$
-where $ \meants^n_T = \sum_{i = 1}^{w}  \ts^n_{T-w+i}/w$.
+where $ \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}$.
 
@@
 In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the family.
-Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for our two RNN,
+Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for our RNN,
 $$
@@
 We use the 3 first years as our train set, we keep the 4th year for our eval set and we hide the last year for our test set.
-We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52.
+We train our hyrid model to compute a one-year ahead prediction, $\lag$ equal to 52, and we set the window size $\window$ equal to 104.
 Using the two first year of our train set, we fit a first per-time-series parametric model for each time series.
@@
 For the first parametric per-time-series models, we used existing Python or R librarys to estimate the different parameters $\statparam^n$.
-There are then fixed during the training of the recurrent models.
-The proposed hybrid model introduced in this numerical section is the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771}.
-This model is also compared to an hybrid model with an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}.
-For the neural network part, we built an architecture summarized in Figure~\ref{fig:rnnarchi}.
+These parameters could move during the training of the hybrid model proposed during the M4 competition.
+In our framework, there are fixed during the training of the recurrent models.
+In this section we propose two versions of HERMES depending of the choice of local parametric models.
+The first one use as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}.
+The second one use as predictors the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves striking accuracy results on our fashion dataset.
+For the neural network part, we built an architecture summarized in Figure~\ref{fig:rnn_architecture}.
 It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension.
-We use a classical Adam otpimizer with a learning rate equal to 0.005 and a batch size equal to 64.
+We use a classical Adam optimizer with a learning rate equal to 0.005 and a batch size equal to 64.
 For our loss function, we tested several metrics and we finally converged on the following one :
@@
     \includegraphics[width=1.\linewidth]{figure/train_eval_test_set}
-  \caption{$\classifier$ and $\predictor$ architecture.}
+  \caption{Temporal split for our training process}
 \label{fig:train_eval_test_set}
@@
 As benchmarks, we chose several well-known statistical methods and deep learning approaches.
-Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels, tbats} , we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
-\textit{snaive} forecasts are only the repetition of the last same past period.
+Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels},  \texttt{tbats} , we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
+The forecast of the \textit{snaive} method is only the repetition of the last same past period.
 \textit{ets} model is an additive exponential smoothing with a level component and a seasonal component.
@@
 For our two versions, we propose a version without our weak signal called \textit{hermes-ets} and \textit{hermes-tbats}.
-Then we evaluate our hybrid framework with the inclusion of our weak signals (ws) referred to as \textit{rshm-ets-ws} and \textit{rshm-tbats-ws}.
+Then we evaluate our hybrid framework with the inclusion of our weak signals (ws) referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}.
 In order to provide a fair comparison, we also train a \textit{lstm} with the weak signals named \textit{lstm-ws}.

### 2021-12-01 hermes_paper/hermes_paper.tex
several updates

@@
 %\textcolor{blue}{Result on 1000ts}  \\
-%For our 3 metrics and for each model, we compute the average and standard deviation on all our sequences on the final year on the \numberts sequences. Results are shown in the Table ???.  
+
+\textbf{10000 Heuritech Fashion time series global accuracy}
+
+For our 3 metrics and for each model, we compute the average on all our sequences \numberts on the final year.
+Results are displayed in the Table~\ref{tab:metricresults}.
+For our model using neural networks, we trained 10 models with different seeds and compute the average and the standard deviation for the three metrics.
+For the statistical models, we can see a large domination of the TBATS model with an OWA equal to 0.850.
+It is one of the main reasons why we use this model on one of our HERMES frameworks as the predictor model.
+However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825.
+
+Considering our new HERMES approach, we see a large domination of our \textit{hermes-tbats} version with a OWA equal to 0.816 and a strong stability across the different trainings.
+Regarding \textit{hermes-ets}, we see a huge increase compared to its predictor choice \textit{ets} with a descrease from 0.937 to 0.875 in term of OWA.
+However, its accuracy remains low in comparison to the \textit{lstm} benchmarck or our HERMES's second version using Tbats.
+Some examples of forecast are given in the Figure~\ref{}.
+In Figure~\ref{}, we displayed some examples of our HERMES model and some weaknessess that it is able to understand and accurately correct.
+
+\begin{table*}
+  \caption{Results summary on our 10000ts Fashion dataset.
+For each metric, we compute the average on all our time series.
+For our approaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.\\}
+  \centering
+  \resizebox{1.2\width}{!}{
+  \begin{tabular}{l||llllllllll}
+   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
+    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
+    \hline
+	\hline
+	\rule{0pt}{2ex} \\
+     \textit{snaive} && 0.881 & - && 25.27 & - && 1. & -\\
+     \textit{thetam}  && 0.844 & - && 24.17 & - && 0.970 & -\\
+     \textit{arima} && 0.826 & - && 23.63 & - && 0.949 & -\\
+     \textit{ets} && 0.807 & - && 23.58 & - && 0.937 & -\\
+     \textit{hermes-ets-ws} && 0.769 & 0.004 && 22.69 & 0.126 && 0.901 & 0.007\\
+     \textit{stlm} && 0.770 & - && 22.05 & - && 0.882 & -\\
+     \textit{hermes-ets} && 0.759 & 0.001 && 22.16 & 0.026 && 0.875 & 0.001\\
+     \textit{tbats} && 0.745 & - && 21.13 & - && 0.850 & -\\
+     \textit{lstm-ws} && 0.728 & 0.004 && 20.18 & 0.085 && 0.837 & 0.004\\
+     \textit{lstm} && 0.724 & 0.003 && 20.08 & 0.052  && 0.825 & 0.004\\
+     \textit{hermes-tbats-ws} && 0.713 & 0.005 && 20.53 & 0.170 && 0.825 & 0.009\\
+     \textbf{\textit{hermes-tbats}} && \textbf{0.715} & 0.002 && \textbf{20.41} & 0.056 && \textbf{0.816} & 0.002\\
+    %\hline
+  \end{tabular}
+  }
+\label{tab:metricresults}
+\end{table*}
+
+\textbf{10000 Heuritech Fashion time series classification task}
+
+An interesting constat is that models using our weak signals underperform their relative without-weak-signals models on all our 3 metrics.
+We see an exception for our \textit{hermes-tabts-ws} that slightly outperform it relative \textit{hermes-tabts} in term of MASE (0.713 compare to 0.715) but its not clearly significative compare to the standard deviation.
+The impact of our weak signal is reveal with our classification result.
+
+When we compare our classification results between the \textit{tbats} model and our hybrid method \textit{hermes-tbats} given in Table~\ref{tab:tbatsclass}, we note an impresive diminution of that we called an "unforgiveable error" : forecast an increase instead of a decrease and vice versa.
+We divide the number of this error by 3 with only a slightly decrease of the number of correct increase/decrease prediction.
+However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of "unforgivable error".
+
+When we look at the result of \textit{lstm-ws} and \textit{lstm} displayed in Table~\ref{tab:lstmclass}, we can also note an rise of the number of correct prediction but with an important increase of the number of classification errors.
+
+\begin{table}
+  \caption{\textit{tbats}, \textit{hermes-tbats} and \textit{hermes-tbats-ws} models confusion matrix}
+  \vspace{0.2cm}
+  \centering
+  \vspace{0.2cm}
+  \par \textit{tbats} model confusion matrix\\
+  \vspace{0.2cm}
+  \resizebox{1.2\width}{!}{
+  \begin{tabular}{l||llll}
+    && pred-dec  & pred-flat & pred-inc  \\
+    \hline
+    \hline
+    \rule{0pt}{2ex} \\
+	true-dec && 327 & 1607 & 82 \\
+    true-flat && 195 & 5586 & 232 \\
+    true-inc && 68 & 1585 & 318 \\
+  \end{tabular}
+  }
+  \vspace{0.2cm}
+  \par \textit{hermes-tbats} model confusion matrix\\
+  \vspace{0.2cm}
+  \centering
+  \resizebox{1.2\width}{!}{
+  \begin{tabular}{l||llll}
+    && pred-dec  & pred-flat & pred-inc  \\
+    \hline
+    \hline
+    \rule{0pt}{2ex} \\
+	true-dec && 250 & 1747 & 19 \\
+    true-flat && 131 & 5802 & 80 \\
+    true-inc && 33 & 1639 & 299 \\\
+  \end{tabular}
+  }
+  \centering
+  \vspace{0.2cm}
+  \par \textit{hermes-tbats-ws} model confusion matrix\\
+  \vspace{0.2cm}
+  \resizebox{1.2\width}{!}{
+  \begin{tabular}{l||llll}
+    && pred-dec  & pred-flat & pred-inc  \\
+    \hline
+    \hline
+    \rule{0pt}{2ex} \\
+	true-dec && 615 & 1365 & 36 \\
+    true-flat && 510 & 5374 & 129 \\
+    true-inc && 65 & 1444 & 462 \\
+  \end{tabular}
+  }
+\label{tab:tbatsclass}
+\end{table}
+
+\begin{table*}
+  \caption{\textit{lstm} and \textit{lstm-ws} model confusion matrix}
+  \vspace{0.2cm}
+  \centering
+  \vspace{0.2cm}
+  \par \textit{lstm} model confusion matrix\\
+  \vspace{0.2cm}
+  \resizebox{1.2\width}{!}{
+  \begin{tabular}{l||llll}
+    && pred-dec  & pred-flat & pred-inc  \\
+    \hline
+    \hline
+    \rule{0pt}{2ex} \\
+	true-dec && 447 & 1539 & 30 \\
+    true-flat && 444 & 5324 & 245 \\
+    true-inc && 66 & 1410 & 495 \\
+  \end{tabular}
+  }
+  \centering
+  \vspace{0.2cm}
+  \par \textit{lstm-ws} model confusion matrix\\
+  \vspace{0.2cm}
+  \resizebox{1.2\width}{!}{
+  \begin{tabular}{l||llll}
+   	&& pred-dec  & pred-flat & pred-inc  \\
+    \hline
+    \hline
+    \rule{0pt}{2ex} \\
+	true-dec && 796 & 1161 & 59 \\
+    true-flat && 1053 & 4701 & 259 \\
+    true-inc && 90 & 1259 & 622 \\
+  \end{tabular}
+  }
+\label{tab:lstmclass}
+\end{table*}
 %Table~\ref{tab:metricresults} summarize the results of all our benchmark models and our 2 hybrid methods for the 3 metrics described above.
@@
 
+\textbf{Importance of the size of the dataset}
+
+In addition to our results on our fashion dataset gathering 10000 time series, we also investigate the behaviours of our HERMES model when it is trained on smaller dataset.
+We did 2 experiences, we train our models on a dataset of 1000 time series and on a dataset of 100 time series.
+Results are given in Table~\ref{tab:1000metricresults} and Table~\ref{tab:100metricresults}.
+
+With these investigations, we can make two remarks.
+First, our hybrid framework \textit{hermes-tbats} achieves the first position in term of global accuracy on both datasets.
+Due to the strengh of its per-time-series predictor TBATS, our hybrid model succeds at correcting some of its weaknesses and logically reach a striking final accuracy.
+Secondly, we can note that the accuracy of the full neural network \textit{lstm} decrease according to the dataset size.
+With a small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} can largely outperform its accuracy level.
+In fact, neural networks need a large amount of data to perform well on a complex task.
+However, with our hybrid framework, the neural network task is largely easier than create a full prediction from scratch.
+Consequently our approach needs less data to succeed at performing well.
+
 \begin{table*}
-  \caption{Results summary on our 10000ts Fashion dataset.
-For each metric, we compute the average on all our time series.
-For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
-  %\centering
+  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series.
+For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.\\}
   \centering
@@
 	\hline
-     \textit{snaive} && 0.881 & - && 25.27 & - && 1. & -\\
-     \textit{thetam}  && 0.844 & - && 24.17 & - && 0.970 & -\\
-     \textit{arima} && 0.826 & - && 23.63 & - && 0.949 & -\\
-     \textit{ets} && 0.807 & - && 23.58 & - && 0.937 & -\\
-     \textit{hybrid-withws-ets} && 0.769 & 0.004 && 22.69 & 0.126 && 0.901 & 0.007\\
-     \textit{stlm} && 0.770 & - && 22.05 & - && 0.882 & -\\
-     \textit{hybrid-nows-ets} && 0.759 & 0.001 && 22.16 & 0.026 && 0.875 & 0.001\\
-     \textit{tbats} && 0.745 & - && 21.13 & - && 0.850 & -\\
-     \textit{lstm-withws} && 0.728 & 0.004 && 20.18 & 0.085 && 0.837 & 0.004\\
-     \textit{lstm-nows} && 0.724 & 0.003 && 20.08 & 0.052  && 0.825 & 0.004\\
-     \textit{hybrid-withws} && 0.713 & 0.005 && 20.53 & 0.170 && 0.825 & 0.009\\
-     \textbf{\textit{hybrid-nows}} && \textbf{0.715} & 0.002 && \textbf{20.41} & 0.056 && \textbf{0.816} & 0.002\\
-    %\hline
+	\rule{0pt}{2ex} \\
+     \textit{snaive} && 0.871 & - && 25.29 & - && 1. & -\\
+     \textit{thetam}  && 0.849 & - && 24.58 & - && 0.980 & -\\
+     \textit{arima} && 0.821 & - && 23.69 & - && 0.951 & -\\
+     \textit{ets} && 0.801 & - && 24.18 & - && 0.944 & -\\
+     \textit{stlm} && 0.765 & - && 22.22 & - && 0.885 & -\\
+     \textit{lstm-nows} && 0.740 & 0.007 && 20.56 & 0.154 && 0.856 & 0.008\\
+     \textit{tbats} && 0.734 & - && 21.19 & - && 0.847 & -\\
+     \textbf{\textit{hybrid-nows}} && \textbf{0.719} & 0.002 && \textbf{20.79} & 0.094 && \textbf{0.833} & 0.004\\
   \end{tabular}
   }
-\label{tab:metricresults}
+\label{tab:1000metricresults}
 \end{table*}
 
-\begin{table*}
-  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series.
+%\begin{table*}
+%  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series.
 For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
-  \centering
-  \begin{tabular}{lllllll}
-    \hline
-    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
-    \hline
-     \textit{snaive} & 0.871 & - & 25.29 & - & 1. & -\\
-     \textit{thetam}  & 0.849 & - & 24.58 & - & 0.980 & -\\
-     \textit{arima} & 0.821 & - & 23.69 & - & 0.951 & -\\
-     \textit{ets} & 0.801 & - & 24.18 & - & 0.944 & -\\
-     \textit{hybrid-nows-ets} & 0.768 & 0.002 & 22.91 & 0.111 & 0.902 & 0.005\\
-     \textit{stlm} & 0.765 & - & 22.22 & - & 0.885 & -\\
-     \textit{lstm-nows} & 0.740 & 0.007 & 20.56 & 0.154 & 0.856 & 0.008\\
-     \textit{tbats} & 0.734 & - & 21.19 & - & 0.847 & -\\
-     \textit{hybrid-nows} & 0.719 & 0.002 & 20.79 & 0.094 & 0.833 & 0.004\\
-    \hline
-  \end{tabular}
-\label{tab:metricresults}
-\end{table*}
-
+%  \centering
+%  \begin{tabular}{lllllll}
+%    \hline
+%    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
+%    \hline
+%     \textit{snaive} & 0.871 & - & 25.29 & - & 1. & -\\
+%     \textit{thetam}  & 0.849 & - & 24.58 & - & 0.980 & -\\
+%     \textit{arima} & 0.821 & - & 23.69 & - & 0.951 & -\\
+%     \textit{ets} & 0.801 & - & 24.18 & - & 0.944 & -\\
+%     \textit{hybrid-nows-ets} & 0.768 & 0.002 & 22.91 & 0.111 & 0.902 & 0.005\\
+%     \textit{stlm} & 0.765 & - & 22.22 & - & 0.885 & -\\
+%     \textit{lstm-nows} & 0.740 & 0.007 & 20.56 & 0.154 & 0.856 & 0.008\\
+%     \textit{tbats} & 0.734 & - & 21.19 & - & 0.847 & -\\
+%     \textit{hybrid-nows} & 0.719 & 0.002 & 20.79 & 0.094 & 0.833 & 0.004\\
+%    \hline
+%  \end{tabular}
+%\label{tab:metricresults}
+%\end{table*}
 \begin{table*}
@@
 For each metric, we compute the average on all our time series.
-For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
-  \centering
-  \begin{tabular}{lllllll}
-    \hline
-    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
-    \hline
-     \textit{snaive} & 0.876 & - & 26.98 & - & 1. & -\\
-     \textit{thetam}  & 0.823 & - & 25.11 & - & 0.944 & -\\
-     \textit{arima} & 0.814 & - & 24.61 & - & 0.940 & -\\
-     \textit{lstm-nows} & 0.767 & 0.045 & 22.22 & 0.848 & 0.877 & 0.051\\
-     \textit{stlm} & 0.742 & - & 23.03 & - & 0.863 & -\\
-     \textit{tbats} & 0.745 & - & 22.16 & - & 0.856 & -\\
-     \textit{hybrid-nows} & 0.739 & 0.003 & 22.31 & 0.083 & 0.845 & 0.003\\
-    \hline
+For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.\\}
+  \centering
+  \resizebox{1.2\width}{!}{
+  \begin{tabular}{l||llllllllll}
+   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
+    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
+    \hline
+	\hline
+	\rule{0pt}{2ex} \\
+     \textit{snaive} && 0.876 & - && 26.98 & - && 1. & -\\
+     \textit{thetam}  && 0.823 & - && 25.11 & - && 0.944 & -\\
+     \textit{arima} && 0.814 & - && 24.61 & - && 0.940 & -\\
+     \textit{lstm-nows} && 0.767 & 0.045 && 22.22 & 0.848 && 0.877 & 0.051\\
+     \textit{stlm} && 0.742 & - && 23.03 & - & 0.863 & -\\
+     \textit{tbats} && 0.745 & - && 22.16 & - & 0.856 & -\\
+     \textbf{\textit{hybrid-nows}} && \textbf{0.739} & 0.003 && \textbf{22.31} & 0.083 && \textbf{0.845} & 0.003\\
   \end{tabular}
-\label{tab:metricresults}
+  }
+\label{tab:100metricresults}
 \end{table*}
-
-\begin{table*}
-  \caption{\textit{tbats} model confusion matrix}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 327 & 1607 & 82 \\
-    true-flat-trend & 195 & 5586 & 232 \\
-    true-inc-trend & 68 & 1585 & 318 \\
-    \hline
-  \end{tabular}
-  \caption{\textit{hybrid} model confusion matrix}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 250 & 1747 & 19 \\
-    true-flat-trend & 131 & 5802 & 80 \\
-    true-inc-trend & 33 & 1639 & 299 \\
-    \hline
-  \end{tabular}
-  \caption{\textit{hybrid-withws} model confusion matrix}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 615 & 1365 & 36 \\
-    true-flat-trend & 510 & 5374 & 129 \\
-    true-inc-trend & 65 & 1444 & 462 \\
-    \hline
-  \end{tabular}
-\label{tab:tbatsclass}
-\end{table*}
-
-\begin{table*}
-  \caption{\textit{lstm} model confusion matrix}
-  \centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 447 & 1539 & 30 \\
-    true-flat-trend & 444 & 5324 & 245 \\
-    true-inc-trend & 66 & 1410 & 495 \\
-    \hline
-  \end{tabular}
-  \caption{\textit{lstm-withws} model confusion matrix}
-  %\centering
-  \begin{tabular}{llll}
-    \hline
-    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-    \hline
-	true-dec-trend & 796 & 1161 & 59 \\
-    true-flat-trend & 1053 & 4701 & 259 \\
-    true-inc-trend & 90 & 1259 & 622 \\
-    \hline
-  \end{tabular}
-\label{tab:lstmclass}
-\end{table*}
-
-%We also compute for each method a confusion matrix on the increase/flat/decreasing classification task.
-Our two hybrid models show interesting results.
-They achieve a better accuracy by detecting new increasing/decreasing trends or reducing the number of huge errors, predicting the opposite change direction.
-For example \textit{rshm-tbats} divide by 2 the number of classification errors of its reference.
-Another interesting result is that \textit{lstm} predicts only flat trends.
-
-%\begin{table*}
-%  \caption{\textit{ets} model confusion matrix}
-%  \centering
-%  \begin{tabular}{llll}
-%    \hline
-%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-%    \hline
-%	true-dec-trend & 43 & 145 & 20 \\
-%    true-flat-trend & 43 & 544 & 34 \\
-%    true-inc-trend & 16 & 122 & 33 \\
-%    \hline
-%  \end{tabular}
-%  \caption{\textit{rshm-ets} model confusion matrix}
-%  \centering
-%  \begin{tabular}{llll}
-%    \hline
-%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-%    \hline
-%	true-dec-trend & 0 & 0 & 0 \\
-%    true-flat-trend & 0 & 0 & 0 \\
-%    true-inc-trend & 0 & 0 & 0 \\
-%    \hline
-%  \end{tabular}
-%  \caption{\textit{rshm-ets-ws} model confusion matrix}
-%  \centering
-%  \begin{tabular}{llll}
-%    \hline
-%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-%    \hline
-%	true-dec-trend & 0 & 0 & 0 \\
-%    true-flat-trend & 0 & 0 & 0 \\
-%    true-inc-trend & 0 & 0 & 0 \\
-%    \hline
-%  \end{tabular}
-%\label{tab:etsclass}
-%\end{table*}
-
-%\begin{table*}
-%  \caption{\textit{tbats} model confusion matrix}
-%  \centering
-%  \begin{tabular}{llll}
-%    \hline
-%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-%    \hline
-%	true-dec-trend & 33 & 167 & 8 \\
-%    true-flat-trend & 21 & 578 & 22 \\
-%    true-inc-trend & 7 & 136 & 28 \\
-%    \hline
-%  \end{tabular}
-%  \caption{\textit{rshm-tbats} model confusion matrix}
-%  \centering
-%  \begin{tabular}{llll}
-%    \hline
-%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-%    \hline
-%	true-dec-trend & 27 & 174 & 7 \\
-%    true-flat-trend & 11 & 597 & 13 \\
-%    true-inc-trend & 5 & 140 & 26 \\
-%    \hline
-%  \end{tabular}
-%  \caption{\textit{rshm-tbats-ws} model confusion matrix}
-%  \centering
-%  \begin{tabular}{llll}
-%    \hline
-%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-%    \hline
-%	true-dec-trend & 26 & 171 & 11 \\
-%    true-flat-trend & 17 & 579 & 25 \\
-%    true-inc-trend & 3 & 136 & 32 \\
-%    \hline
-%  \end{tabular}
-%\label{tab:tbatsclass}
-%\end{table*}
-
-%\begin{table*}
-%  \caption{\textit{lstm} model confusion matrix}
-%  \centering
-%  \begin{tabular}{llll}
-%    \hline
-%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-%    \hline
-%	true-dec-trend & 0 & 208 & 0 \\
-%    true-flat-trend & 0 & 621 & 0 \\
-%    true-inc-trend & 0 & 171 & 0 \\
-%    \hline
-%  \end{tabular}
-%  \caption{\textit{lstm-ws} model confusion matrix}
-%  %\centering
-%  \begin{tabular}{llll}
-%    \hline
-%    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
-%    \hline
-%	true-dec-trend & 1 & 205 & 2 \\
-%    true-flat-trend & 2 & 619 & 0 \\
-%    true-inc-trend & 0 & 168 & 3 \\
-%    \hline
-%  \end{tabular}
-%\label{tab:lstmclass}
-%\end{table*}
 
@@
 On these 118 trends,   the \textit{tbats} has an OWA equal to 0.893 and with the regime switching model correction, we reach an OWA equal to 0.868.
-
-%\begin{table*}
-%  \caption{Results summary on our Fashion dataset. We compare methods without our weak signal and than method but train with our weak signals as an additional input}
-%  \centering
-%  \begin{tabular}{lllllll}
-%    \hline
-%    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
-%    \hline
-%     \textit{lstm} & 0.765 & 0.278 & 21.00 & 11.42 & 0.872 & 0.160\\
-%     \textit{rshm-ets} & 0. & 0. & . & . & . & 0.\\
-%     \textit{\textbf{rshm-tbats}} & 0.728 & 0.245 & 21.02 & 13.54 & 0.840 & 0.159\\
-%    \hline
-%     \textit{lstm-ws} & 0.758 & 0.271 & 20.89 & 11.46 & 0.867 & 0.163\\
-%     \textit{rshm-ets-ws} & 0. & 0. & . & . & . & 0.\\
-%     \textit{\textbf{rshm-tbats-ws}} & 0.731 & 0.248 & 21.10 & 13.53 & 0.844 & 16.23\\
-%    \hline
-%  \end{tabular}
-%\label{tab:metricresultsws}
-%\end{table*}
 
@@
 This result shows that our hybrid framework is robust and reach constant accuracy level on large dataset.
-
-%With our results, we can make two interesting conclusions.
-Firstly, the regime switching hybrid framework is a really promising framework.
-By mixing the performance of local parametric models and a global DNN, our two versions clearly outperform traditional statistical methods.
-Furthermore, this framework is totally suited for dealing with external signals.
-With a fine pre-processing and a well-designed architecture, our two models succeed at leveraging our complex extra data and reach an impressive accuracy levels.
-Secondly, our results bring to light the quality of our new Fashion dataset.
-We saw that the full LSTM model \textit{lstm} outperforms all time series specific models.
-This show that our dataset is well suited to train complex neural network architectures able to learn information cross sequences.
-With the addition of our weak signals, we give a totally new dimension to our fashion dataset.
-Our results show that our external weak signals hide a complex but usable predictive power by DNN architecture.
-By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting.
 
@@
 
-With our results, we can make two interesting conclusions.
-Firstly, the regime switching hybrid framework is a really promising framework.
-By mixing the performance of local parametric models and a global DNN, our two versions clearly outperform traditional statistical methods.
+With our results, we can make several interesting conclusions.
+Firstly, our new HERMES hybrid framework is a really promising framework.
+By mixing the performance of local parametric models and a global DNN, our \textit{hermes-tbats} version clearly outperform traditional statistical methods and full neural network models.
 Furthermore, this framework is totally suited for dealing with external signals.
-With a fine pre-processing and a well-designed architecture, our two models succeed at leveraging our complex extra data and reach impressive accuracy levels.
+With a fine pre-processing and a well-designed architecture, our hybrid framework succeed at leveraging our complex extra data and reach impressive accuracy level in term of classification.
 Secondly, our results bring to light the quality of our new Fashion dataset.
-We saw that the full LSTM model \textit{lstm} outperforms all time series specific models.
-This shows that our dataset is well suited to train complex neural network architectures able to learn information cross sequences.
-With the addition of our weak signals, we give a totally new dimension to our fashion dataset.
-Our results show that our external weak signals hide a complex but usable predictive power by DNN architecture.
+We saw that the full LSTM model \textit{lstm} outperforms all time series specific models when it is trained with the biggest dataset of 10000 time series but not with the smaller ones.
+This shows that complex neural network architectures involve large amount of data to be train and our full dataset is well suited for this.
+Finally, with the addition of our weak signals, we give a totally new dimension to our new hybrid architecture and our fashion dataset.
+Our results show that our external weak signals hide a complex but usable predictive power by our HERMES model.
+However, we believe that it remains a lot of ways to explore in order to leverage the full potential of these chaotic signals.
 
@@
 In this paper, we propose the first hybrid model including external weak signals for time series forecasting.
-We show that hybrid framework is a really promising way.
-With its extended error-corrector DNN part, it is clearly well-suited for dealing with any kind of external signals in order to correct weaknesses of first parametric models.
-Furthermore, With our general framework, we show that the hybrid model is able to include any kind of any per-time-series models.
-Thereby, future research explorations would be to evaluate its framework with different per-time-series approaches and understand relationships between first parametric model choice and final hybrid model accuracy.
-For our regime switching recurrent error-corrector, we assumed the existence of only 2 regimes.
-A logical exploration would be to extend our framework with multiple regimes: change the binary RNN classifier to a multi-label classifier and train several regime-specialized RNN predictors.
-
-With this first contribution, we join the first fashion dataset gathering \numberts\ mode times series and a complex collection of extra signals.
+We show that hybrid framework is a really promising way and with its extended error-corrector DNN part, it is clearly well-suited for dealing with any kind of external signals.
+Furthermore, our general framework shows that the hybrid model is able to include any kind of any per-time-series models.
+Depending of the use cases, the nature of the observed time series, users can choose the best parametric models, correct some of its weaknessess and finally increase its accuracy with the HERMES framework.
+Thereby, future research explorations would be to evaluate its framework with a large collection of per-time-series approaches and understand relationships between first parametric model choice and final hybrid model accuracy.
+Is it the best parametric model always the best choice in our HERMES framework ?
+A other promising exploration would be to challenge the error-corrector DNN model with an other one using Transformer or a collection of DNN specialized on specific kind of weaknessess.
+
+With this first contribution, we join the first fashion dataset gathering \numberts\ fashion times series and a complex collection of external signals.
 We believe that this dataset hide really fine dynamics and interactions where complex models would express their potential.

### 2021-12-01 hermes_paper/hermes_paper.tex
some updates

@@
 \usepackage{graphicx}
+\iclrfinalcopy
 %\setlength{\tabcolsep}{10pt}
@@
 \begin{table*}
-  \caption{Fashion time series overview. For each couple geozone/category, we give the number of female and male trends (Female/Male)}
+  \caption{Fashion time series overview. For each couple geozone/category, we give the number of female and male trends (Female/Male)\\}
   \label{sample-table}
@@
   \resizebox{0.85\width}{!}{
-  \begin{tabular}{l||llllllllll}
+  \begin{tabular}{l||lllllllll}
     %hline
     \\
-    &  \textbf{Top}  & \textbf{Pants} & \textbf{Short} & \textbf{Skirt} & \textbf{Dress} & \textbf{Coat} & \textbf{Shoes} & \textbf{Color} & \textbf{Texture} &  \\
+    &  \textbf{Top}  & \textbf{Pants} & \textbf{Short} & \textbf{Skirt} & \textbf{Dress} & \textbf{Coat} & \textbf{Shoes} & \textbf{Color} & \textbf{Texture}  \\
     \hline
@@
      %\hline
-     \textbf{Total} & 2078/1078 & 700/564 & 239/130 & 142/- & 118/- & 985/772 & 1528/396 & 214/216 & 459/381 & \textbf{\numberts}\\
+     \textbf{Total} & 2078/1078 & 700/564 & 239/130 & 142/- & 118/- & 985/772 & 1528/396 & 214/216 & 459/381\\
     %\hline
@@
 However, its accuracy remains low in comparison to the \textit{lstm} benchmarck or our HERMES's second version using Tbats.
-Some examples of forecast are given in the Figure~\ref{}.
-In Figure~\ref{}, we displayed some examples of our HERMES model and some weaknessess that it is able to understand and accurately correct.
+In Figure~\ref{fig:hybrid-examples}, we displayed some examples of our HERMES model and some weaknessess that it is able to understand and accurately correct.
 
@@
 \end{table*}
+
+\begin{figure}
+  \centering
+    \includegraphics[width=1.\linewidth]{figure/hybrid_model_examples}
+  \caption{\textit{hermes-tbats} forecast examples.
+In green the prediction of the per-time-series predictors \textit{tbats}.
+In red the final forecast of our hermes hybrid model \textit{hermes-tbats}.}
+\label{fig:hybrid-examples}
+\end{figure}
 
@@
 
-\section{Fashion Dataset overview}
+\%section{Fashion Dataset overview}
 
@@
 
-\section{Additional results, explorations and examples.}
+%\section{Additional results, explorations and examples.}
 

### 2021-12-02 hermes_paper/hermes_paper.tex
Fixed bug in caption

@@
 \begin{table*}
-  \caption{Fashion time series overview. For each couple geozone/category, we give the number of female and male trends (Female/Male)\\}
+  \caption{Fashion time series overview. For each couple geozone/category, we give the number of female and male trends (Female/Male)}
   \label{sample-table}
@@
 For each metric, we compute the average on all our time series.
-For our approaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.\\}
+For our approaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
   \centering
@@
   \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series.
-For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.\\}
+For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
   \centering
@@
 For each metric, we compute the average on all our time series.
-For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.\\}
+For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
   \centering

### 2021-12-02 hermes_paper/hermes_paper.tex
Fixed bug in biblio
several updates

@@
 Recurrent neural networks are appealing to tackle our forecasting problem due to their capability of leveraging external data.
-Recently, hybrid models combining DNN architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \citep{zhang2003time,jianwei2019novel,bandara2020lstm}.
+Recently, hybrid models combining deep neural network (DNN) architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \citep{zhang2003time,jianwei2019novel,bandara2020lstm}.
 The approach providing the most striking results was proposed in  \citep{smyl2020hybrid} in the context of the M4 forecasting competition \citep{makridakis2020m4}.
@@
 Section~\ref{sec:exp} describes our results and comparisons with several benchmarks.
-Finally, we conclude our paper and detail research perspectives in Section~\ref{sec:discussion} and Section~\ref{sec:conclusion}.
+Finally, we detail research perspectives and conclude our paper in Section~\ref{sec:discussion} and Section~\ref{sec:conclusion}.
 
@@
 Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
-We introduce a new hybrid approach for time series forecasting  composed of two parts: first per-time-series parametric models, the predictors, and a global error-corrector neural network train on all the time series, the corrector.
+We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, the predictors, and a global error-corrector neural network train on all the time series, the corrector.
 We use  per-time-series parametric models to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
@@
 This task requires a thorough data pre-processing for two main reasons.
-Firstly, we want to give to the RNN the best input in order to understand the first collection of forecasts and predict their future errors.
-Secondly,as we did not suppose any assumption about the scale of our time series, we have to carefully normalize them before feeding our RNN with.
+Firstly, we want to give to the RNN the best input in order to understand the initial collection of forecasts and predict their future errors.
+Secondly, as we did not suppose any assumption about the scale of our time series, we have to carefully normalize them before feeding our RNN with.
 In this way, we define the following pre-processing :
@@
 The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 different categories and 5 geozones.
-An overview of it can be found in table 1.
+An overview of it can be found in Table 1.
 
@@
 We preprocess our time series and we evaluate how our error-corrector RNN is able to improve the first collection of predictions of the fourth year.
-At the end, we repeat the same process for the last year and compute our final accuracy measures. An example of our splitting is shown in  Figure~\ref{fig:train_eval_test_set}.
+At the end, we repeat the same process for the fifth year and compute our final accuracy measures. An example of our temporal split is shown in  Figure~\ref{fig:train_eval_test_set}.
 %We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52.
@@
 For the first parametric per-time-series models, we used existing Python or R librarys to estimate the different parameters $\statparam^n$.
-These parameters could move during the training of the hybrid model proposed during the M4 competition.
-In our framework, there are fixed during the training of the recurrent models.
+During the M4 competition, parameters of the exponential smoothing of the porposed hybrid model could move during the training.
+In our framework,
+$\{\statparam^n\}_{1\leqslant n \leqslant N}$ are fixed during the training of the recurrent models.
 In this section we propose two versions of HERMES depending of the choice of local parametric models.
@@
 
-Against these models, we propose two versions of our hybrid model (hermes) called respectively hermes-ets and herles-tbats according to the per-time-series model choice.
+Against these models, we propose two versions of HERMES called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
 %Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}.
@@
 %To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}).  
-For our two versions, we propose a version without our weak signal called \textit{hermes-ets} and \textit{hermes-tbats}.
-Then we evaluate our hybrid framework with the inclusion of our weak signals (ws) referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}.
+Moreover, we evaluate our hybrid framework with the inclusion of our weak signals (ws) referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}.
 In order to provide a fair comparison, we also train a \textit{lstm} with the weak signals named \textit{lstm-ws}.
@@
 A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes.
-In a given year, we define an increasing trend as a trend that does more than 10\% of growth in terms of Year and Year.In the same way, we define a decreasing trend as a trend that declines by 10\% or more.
+In a given year, we define an increasing trend as a trend that does more than 10\% of growth in terms of Year and Year.
+In the same way, we define a decreasing trend as a trend that declines by 10\% or more.
 We classify other trends as flat trends.
@@
 
-For our 3 metrics and for each model, we compute the average on all our sequences \numberts on the final year.
+For our 3 metrics and for each model, we compute the average on all our sequences \numberts~  on the final year.
 Results are displayed in the Table~\ref{tab:metricresults}.
@@
 For the statistical models, we can see a large domination of the TBATS model with an OWA equal to 0.850.
-It is one of the main reasons why we use this model on one of our HERMES frameworks as the predictor model.
+It is one of the main motivations why we use this model on our best HERMES candidate as the predictor model.
 However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825.
@@
 However, its accuracy remains low in comparison to the \textit{lstm} benchmarck or our HERMES's second version using Tbats.
-In Figure~\ref{fig:hybrid-examples}, we displayed some examples of our HERMES model and some weaknessess that it is able to understand and accurately correct.
+In Figure~\ref{fig:hybrid-examples}, we displayed some examples of \textit{hermes-tbats} model and some weaknessess that it is able to understand and accurately correct.
 
@@
 
-An interesting constat is that models using our weak signals underperform their relative without-weak-signals models on all our 3 metrics.
-We see an exception for our \textit{hermes-tabts-ws} that slightly outperform it relative \textit{hermes-tabts} in term of MASE (0.713 compare to 0.715) but its not clearly significative compare to the standard deviation.
-The impact of our weak signal is reveal with our classification result.
+An interesting constat is that models using our weak signals slightly underperform their relative without-weak-signals models on all our 3 metrics.
+We see an exception for our \textit{hermes-tabts-ws} that outperform its relative \textit{hermes-tabts} in term of MASE (0.713 compare to 0.715) but it is not clearly significative compare to the standard deviation.
+The impact of our weak signal is revealed with our classification results.
 
 When we compare our classification results between the \textit{tbats} model and our hybrid method \textit{hermes-tbats} given in Table~\ref{tab:tbatsclass}, we note an impresive diminution of that we called an "unforgiveable error" : forecast an increase instead of a decrease and vice versa.
-We divide the number of this error by 3 with only a slightly decrease of the number of correct increase/decrease prediction.
+We divide the number of this error by 3 with only a slightly decrease of the number of correct increase/decrease predictions.
 However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of "unforgivable error".
@@
 
-In addition to our results on our fashion dataset gathering 10000 time series, we also investigate the behaviours of our HERMES model when it is trained on smaller dataset.
+In addition to our results on our fashion dataset gathering 10000 time series, we also investigate the behaviours of our HERMES model when it is trained on smaller datasets.
 We did 2 experiences, we train our models on a dataset of 1000 time series and on a dataset of 100 time series.
@@
 
-With these investigations, we can make two remarks.
+With these investigations, we can make two important remarks.
 First, our hybrid framework \textit{hermes-tbats} achieves the first position in term of global accuracy on both datasets.
@@
 With a small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} can largely outperform its accuracy level.
-In fact, neural networks need a large amount of data to perform well on a complex task.
-However, with our hybrid framework, the neural network task is largely easier than create a full prediction from scratch.
-Consequently our approach needs less data to succeed at performing well.
+In fact, learn how to compute a full prediction from scratch is a complex task and for a neural network, it evolves a large amout of data.
+Nevertheless, with our hybrid framework, the RNN task is largely simplify.
+Our achitectures logicaly needs less data to be train and perform well.
 
@@
 With our results, we can make several interesting conclusions.
-Firstly, our new HERMES hybrid framework is a really promising framework.
+Firstly, our new HERMES framework is a really promising framework.
 By mixing the performance of local parametric models and a global DNN, our \textit{hermes-tbats} version clearly outperform traditional statistical methods and full neural network models.
@@
 \bibliography{hermes_paper}
-\bibliographystyle{hermes_paper}
+\bibliographystyle{apalike}
 
@@
 
-\%section{Fashion Dataset overview}
+%\section{Fashion Dataset overview}
 

### 2021-12-02 hermes_paper/hermes_paper.tex
Intro

--- 2021-12-02 hermes_paper/hermes_paper.tex
@@
 Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
-The exponential smoothing model \citep{RePEc:inm:oropre:v:9:y:1961:i:5:p:673-685} or the ARIMA with the Box-Jenkins approach \citep{box2015time} are for instance very popular parametric linear generative models.
-Hidden Markov models (HMM) are also widespread and presuppose that available observations are defined using missing data, possibly lying in a high dimensional state space, describing the dynamical system.
+The exponential smoothing model \citep{RePEc:inm:oropre:v:9:y:1961:i:5:p:673-685}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \cite{doi:10.1198/jasa.2011.tm09771}, or the ARIMA with the Box-Jenkins approach \citep{box2015time} are for instance very popular parametric linear generative models.
+Hidden Markov models (HMM) are also widespread and presuppose that available observations are defined using missing data describing the dynamical system.
 This hidden state is assumed to be a Markov chain such that at each time step the received observation is a random function of the corresponding latent data.
-Although hidden states are modeled as a Markov chain (or a mixing process), the observations arising therefrom present a highly complex statistical structure.
+Although hidden states are modeled as a Markov chain, the observations arising therefrom present a highly complex statistical structure.
 %Introducing latent hidden states, they assume that the predictive distribution is not unique and constant in time but multiple and lead by the values of the hidden states changing during time.
@@
 In this new context, classical time series specific statistical models show limitations when dealing with numerous heterogeneous data.
-Recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \citep{ hochreiter1997long,vaswani2017attention, salinas2020deepar, li2019enhancing, lim2019temporal}.
+Recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \citep{ hochreiter1997long,vaswani2017attention, 8614252, li2019enhancing, lim2019temporal,salinas2020deepar}.
 %In the past decades, with the impressive results of deep neural networks (DNN) in vision or language, some time series forecasting applications have been proposed.
-Significant improvements have been achieved with Reccurent Neural Network and its Long Short-Term Memory (LSTM) or Gated Recurrent Unit (GRU)  declinations \citep{8614252}. 
-A good example is the DeepAR model \citep{salinas2020deepar}.
-Based on a LSTM architecture, it can predict accurate probability distributions of the future of a sequence.
+%Significant improvements have been achieved with Reccurent Neural Network and its Long Short-Term Memory (LSTM) or Gated Recurrent Unit (GRU)  declinations \citep{}. 
+The DeepAR model proposed in \citep{salinas2020deepar} provides a global model from many time series based on
+a multi-layer recurrent neural network with LSTM cells.
 More recently, applications using the Transformer model have been proposed  \citep{li2019enhancing}.
 A direct concurrent of the DeepAR model can be found with the Temporal Fusion Transformers (TFT) approach \citep{lim2019temporal}.
-Unfortunately, they suffer from two main weaknesses.
+Unfortunately, all these solutions suffer from two main weaknesses.
 Firstly, many of them are "black-boxes"  as the final forecast usually does not come with a statistical guarantee  although a few recent works focused on measuring uncertainty in recurrent neural networks, see  \cite{martin2020monte}.
-Secondly, without a fine prepossessing and well chosen hyper-parameters, these methods could lead to poor results and are often outperformed by traditional statistical models, see \cite{makridakis2018m4}.
+Secondly, without a fine prepossessing and well chosen hyper-parameters, these methods may lead to poor results and are often outperformed by traditional statistical models, see \cite{makridakis2018m4}.
 
@@
 Following this work, we present in this paper HERMES, a new hybrid recurrent model for time series forecasting with inclusion of external signals.
-Our new framework is divided in two levels: local predictors and a global corrector.
-In a first time, given a group of sequence, we compute a per-time-series prediction using any kind of parametric models.
-In a second time, we train a global neural network to understand, evaluate and correct the forecast weaknesses of the first collection of models.
-By adding external weak signals in our proposed framework, we show the real potential of the hybrid approach: a global neural network, able to leverage large amount of data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of any parametric models.
+Our model is decomposed  into two parts: local predictors and a global corrector.
+First, a per-time-series parametric statistical model is trained on all sequences.
+Then,  a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.
+By adding external weak signals in our proposed framework, we show the real potential of the hybrid approach: a global neural network, able to leverage large amount of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of any parametric models.
 %Our new hybrid framework is divided in two parts.

### 2021-12-02 hermes_paper/hermes_paper.tex
Correction section 2

@@
 Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
-We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, the predictors, and a global error-corrector neural network train on all the time series, the corrector.
+We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, the predictors, and a global error-corrector neural network train on all time series, the corrector.
 We use  per-time-series parametric models to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
@@
 During the M4 competition, the hybrid model of \cite{smyl2020hybrid} was based on a multiplicative exponential smoothing model as the time-series-specific predictor.
-However, on sporadic time series, this choice could lead to poor result and instability.
-In our approach, we decided to go deeper and provide a general framework able to deal with any kind of per-time-series models.
+However, on sporadic time series, this choice leads to poor result and instability.
+In this paper, we provide a general framework able to deal with any kind of per-time-series models.
 In Section~\ref{sec:exp}, we present two versions of our framework.
-The first one use an  exponential smoothing as reference similar to \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results.
-The main complexity is in the next stage: training a global RNN corrector to improve the per-time-series statistical models when the parametric models start showing weaknesses.
-
-As weakness to correct, we detected and defined two main forms for a univariate parametric forecast as define above.
-The first one is a weakness of definition, when the model is not well define for its forecasting task.
+The first one use an  exponential smoothing as reference similar to the baseline \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
+%The main complexity is in the next stage: training a global RNN corrector to improve the per-time-series statistical models when the parametric models start showing weaknesses.
+
+In the specific application of fashion trends prediction, we detected and defined two main forms of standard weaknesses for a univariate parametric forecast as defined above.
+The first one is a weakness of definition, when the model is not well defined for its forecasting task.
 For instance, an additive model provide good predictions on time series with additive seasonality but show difficulties with multiplicative one.
@@
 The difficulty is that we mainly unknow the exact influence of external variables on the main signal.
-It is on this point that our new hybrid framework shows its true potential: introduce a global RNN train on all the time series and able to consider and leverage external signals.\textcolor{red}{Plutot dire ici que l'on souhaite corriger des erreurs specifiques: et introduire les types de trends mal predites que l'on souhaite corriger.}
+It is on this point that our new hybrid framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals.
+
+\medskip
+
+\textcolor{red}{Ajouter ici une figure avec une ou deux series temporelles mal predites par le modele statistique et bien corrigees par le RNN pour illustrer le potentiel.}
 % Indeed, depending on time series, some family of parametric models can achieve really heterogeneous level of accuracy. 

### 2021-12-02 hermes_paper/hermes_paper.tex
Correction section 2

@@
 
-At this stage, we want to train a global RNN, trained on all the N sequences and able to understand and correct the weaknesses of the first per-time-series parametric models.
+The second part of our model is a global RNN, trained on all the $N$ sequences to correct the weaknesses of the first per-time-series parametric models.
 This task requires a thorough data pre-processing for two main reasons.
-Firstly, we want to give to the RNN the best input in order to understand the initial collection of forecasts and predict their future errors.
-Secondly, as we did not suppose any assumption about the scale of our time series, we have to carefully normalize them before feeding our RNN with.
-In this way, we define the following pre-processing :
+First, we provide  to the RNN the best input in order to understand the initial collection of forecasts and predict their future errors.
+Second, as we did not make any assumption about the scale of our time series, we have to carefully normalize them before feeding them to the RNN.
+Consider the following pre-processing. 
 %At this stage, we can write that for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
@@
 $$
-\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+i|T}}{\meants^n_T}\,,
+\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+i|T}}{\meants^n_T}\,,\quad\mbox{where}\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
 $$
-where $ \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}$.
 
 We note $\rnn(.;\rnnparam)$ the recurrent neural network model where $\rnnparam$ are  unknown parameters.
-Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\{\rnnparam\}$, the error-corrector predictions $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\rnnparam$, the error-corrector predictions $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
 $$
@@
 
-Using well-fitted time-series-specific parametric models, our hybrid network corrects the first form of weakness and achieves striking accuracy on our dataset.
-Then, for the second form of weakness, the shared recurrent neural network relies on the strength of machine learning methods at leveraging a huge quantities of heterogeneous data.
-In addition to the $N$ target time series, we consider $K \times N$ external sequences indexed from $0$ to $T$.
+Using well-fitted time-series-specific parametric models, our hybrid network corrects the first form of weakness and achieves striking accuracy on our dataset, \textcolor{red}{see Table~XXX}.
+Then, to correct the second form of weakness, in addition to the $N$ target time series, we consider $K \times N$ external sequences indexed from $0$ to $T$.
 For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ linked to the sequence $\fullts^n$.

### 2021-12-02 hermes_paper/hermes_paper.tex
Correction section 4

@@
 
+\medskip
+\textcolor{red}{Est-ce pertinent de decrire les outils de computer vision utilises pour construire le jeu de donnees ? Ou de decrire plus precisement la nature des $y$ consideres ? De }
+
 %With only the historical data, predict this breaking point is challenging and some time impossible.
@@
 Using these forecasts, we preprocess our time series and finally determine our RNN inputs.
-We can, then, train our RNN at understanding and correcting the previous collection of parametric model's forecasts.
 In the same way, for the eval set, we fit a second time our per-time-series predictors using the three first years and we forecast the fourth year.
@@
 
-For the first parametric per-time-series models, we used existing Python or R librarys to estimate the different parameters $\statparam^n$.
-During the M4 competition, parameters of the exponential smoothing of the porposed hybrid model could move during the training.
+For the first parametric per-time-series models, we used existing Python or R libraries to estimate the different parameters $\statparam^n$.
+%During the M4 competition, parameters of the exponential smoothing of the porposed hybrid model could move during the training.
 In our framework,
-$\{\statparam^n\}_{1\leqslant n \leqslant N}$ are fixed during the training of the recurrent models.
+%$\{\statparam^n\}_{1\leqslant n \leqslant N}$ are fixed during the training of the recurrent models. 
 In this section we propose two versions of HERMES depending of the choice of local parametric models.
@@
 For the neural network part, we built an architecture summarized in Figure~\ref{fig:rnn_architecture}.
-It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension.
-We use a classical Adam optimizer with a learning rate equal to 0.005 and a batch size equal to 64.
-For our loss function, we tested several metrics and we finally converged on the following one :
+It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension \textcolor{red}{Peut-on discuter/justifier ce choix ?}.
+We use a classical Adam optimizer with a learning rate equal to 0.005 and a batch size equal to 64 and the following loss function:
 
 $$
-l(\ts^n_{T+1:T+\lag},\tspred^n_{T+1:T+\lag|T}) = \frac{\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|}{\meants^n_T}
+\ell(\ts^n_{T+1:T+\lag},\tspred^n_{T+1:T+\lag|T}) = \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,.
 $$

### 2021-12-02 hermes_paper/hermes_paper.tex
Correction section 4

@@
 \textit{stlm} approach uses a multiplicative decomposition and models the seasonally adjusted time series with an exponential smoothing model.
-\textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast.
-\textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization.
+\textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast and \textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization.
 The last one \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters.
@@
 
-Against these models, we propose two versions of HERMES called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
+We propose two versions of HERMES called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
 %Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}.
@@
 \begin{align*}
-\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,\\
-\mathrm{sMAPE} &= \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}\,,\\
+\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,\quad \mathrm{sMAPE} = \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}\,,\\
 \mathrm{OWA} &= \frac{1}{2}\left(MASE/MASE_{snaive} + sMAPE/sMAPE_{snaive}\right)\,,
@@
 On the test set, the year 2019, we have 1871 increasing trends, 2016 decreasing trends and 6113 flat trends.
-In addition to the accuracy metrics, we also compare the different methods on this classification task and especially difference between methode using weak signal or not.
+In addition to the accuracy metrics, we also compare the different methods on this classification task and especially difference between method using weak signals or not.
 

### 2021-12-02 hermes_paper/hermes_paper.tex
Correction section 4

@@
 Regarding \textit{hermes-ets}, we see a huge increase compared to its predictor choice \textit{ets} with a descrease from 0.937 to 0.875 in term of OWA.
-However, its accuracy remains low in comparison to the \textit{lstm} benchmarck or our HERMES's second version using Tbats.
+However, its accuracy remains low in comparison to the \textit{lstm} benchmarck or HERMES using TBATS.
+Models using our weak signals perform similarly as without-weak-signals models on all our 3 metrics.
 In Figure~\ref{fig:hybrid-examples}, we displayed some examples of \textit{hermes-tbats} model and some weaknessess that it is able to understand and accurately correct.
@@
   \centering
-  \resizebox{1.2\width}{!}{
+  \resizebox{\textwidth}{!}{%
   \begin{tabular}{l||llllllllll}
@@
 In green the prediction of the per-time-series predictors \textit{tbats}.
-In red the final forecast of our hermes hybrid model \textit{hermes-tbats}.}
+In red the final forecast of our hermes hybrid model \textit{hermes-tbats}.\textcolor{red}{Utiliser plutot des "marker" (tirets, croix, etc.) car cela differencie mieux}}
 \label{fig:hybrid-examples}
@@
 
-An interesting constat is that models using our weak signals slightly underperform their relative without-weak-signals models on all our 3 metrics.
-We see an exception for our \textit{hermes-tabts-ws} that outperform its relative \textit{hermes-tabts} in term of MASE (0.713 compare to 0.715) but it is not clearly significative compare to the standard deviation.
  The impact of our weak signal is revealed with our classification results.
-
-When we compare our classification results between the \textit{tbats} model and our hybrid method \textit{hermes-tbats} given in Table~\ref{tab:tbatsclass}, we note an impresive diminution of that we called an "unforgiveable error" : forecast an increase instead of a decrease and vice versa.
-We divide the number of this error by 3 with only a slightly decrease of the number of correct increase/decrease predictions.
-However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of "unforgivable error".
+Classification results between the \textit{tbats} model and our hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impresive decrease of impactful errors: forecast an increase instead of a decrease and vice versa.
+Our \textit{hermes-tbats} divides  by 3 tis error rate in comparison to \textit{tbats} with only a slightly decrease of the number of correct increase/decrease predictions.
+However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of errors.
 
@@
   \vspace{0.2cm}
-  \resizebox{1.2\width}{!}{
   \begin{tabular}{l||llll}
@@
   \end{tabular}
-  }
   \vspace{0.2cm}
@@
   \centering
-  \resizebox{1.2\width}{!}{
   \begin{tabular}{l||llll}
@@
   \end{tabular}
-  }
   \centering
@@
   \end{tabular}
-  }
 \label{tab:tbatsclass}
@@
   \end{tabular}
-  }
 \label{tab:lstmclass}
@@
   \centering
-  \resizebox{1.2\width}{!}{
+ \resizebox{\textwidth}{!}{
   \begin{tabular}{l||llllllllll}
@@
   \centering
-  \resizebox{1.2\width}{!}{
+  \resizebox{\textwidth}{!}{
   \begin{tabular}{l||llllllllll}

### 2021-12-02 hermes_paper/hermes_paper.tex
Correction section 4

@@
 
-When we look at the result of \textit{lstm-ws} and \textit{lstm} displayed in Table~\ref{tab:lstmclass}, we can also note an rise of the number of correct prediction but with an important increase of the number of classification errors.
+When we look at the result of \textit{lstm-ws} and \textit{lstm} displayed in Table~\ref{tab:lstmclass}, we can also note a rise of the number of correct predictions but with an important increase of the number of classification errors.
 
@@
 In addition to our results on our fashion dataset gathering 10000 time series, we also investigate the behaviours of our HERMES model when it is trained on smaller datasets.
-We did 2 experiences, we train our models on a dataset of 1000 time series and on a dataset of 100 time series.
+We did 2 experiments, we train our models on a dataset of 1000 time series and on a dataset of 100 time series.
 Results are given in Table~\ref{tab:1000metricresults} and Table~\ref{tab:100metricresults}.
@@
 Due to the strengh of its per-time-series predictor TBATS, our hybrid model succeds at correcting some of its weaknesses and logically reach a striking final accuracy.
-Secondly, we can note that the accuracy of the full neural network \textit{lstm} decrease according to the dataset size.
+Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size is smaller.
 With a small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} can largely outperform its accuracy level.
-In fact, learn how to compute a full prediction from scratch is a complex task and for a neural network, it evolves a large amout of data.
-Nevertheless, with our hybrid framework, the RNN task is largely simplify.
-Our achitectures logicaly needs less data to be train and perform well.
+Learn how to compute a full prediction from scratch is a complex task and high-dimensional recurrent neural networks require  large amount of data.
+Nevertheless, with our hybrid framework, the RNN task is largely simplified.
+Our achitectures logicaly needs less data to be trained and to perform well.
 

### 2021-12-08 hermes_paper/hermes_paper.tex
several updates

@@
 \usepackage{graphicx}
+\usepackage{subcaption}
 \iclrfinalcopy
@@
 It is on this point that our new hybrid framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals.
+First forecast examples of our new hybrid model are given in Figure~\ref{fig:introexamples}
 
 \medskip
+
+\begin{figure}
+\centering
+\begin{subfigure}{1.\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/us_female_shoes}
+  \caption{Time series representing a shoes fashion trend for female in The United States}
+  \label{fig:introexamples:sub1}
+\end{subfigure}
+\begin{subfigure}{1.\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/br_female_texture_verticalstripe}
+  \caption{Time series representing the vertical stipes texture fashion trend for female in Brazil}
+  \label{fig:introexamples:sub2}
+\end{subfigure}
+\caption{Hermes forecast examples. In green the prediction of the TBATS per-time-series predictors. In red the final forecast of our HERMES hybrid model.}
+\label{fig:introexamples}
+\end{figure}
 
@@
 
-Using well-fitted time-series-specific parametric models, our hybrid network corrects the first form of weakness and achieves striking accuracy on our dataset, \textcolor{red}{see Table~XXX}.
+Using well-fitted time-series-specific parametric models, our hybrid network corrects the first form of weakness and achieves striking accuracy on our dataset, see Table~\ref{tab:metricresults}.
 Then, to correct the second form of weakness, in addition to the $N$ target time series, we consider $K \times N$ external sequences indexed from $0$ to $T$.
@@
 We provide the first dataset dedicated to fashion trends forecasting.
+Our fashion dataset is built with the suprising alliance of a high throughput computer vision system and experts of the fashion sphere.
+A team of deep learning engineers designed and trained a collection of vision neural networks at detecting clothes details: color, cloth type (pants, shoes, top etc...), form, size, texture etc...
+Then a second team of fashion experts aggregates these previous attributes and created thousands of fashion trends.
+Analysing every day images shared on social networks, we are finally able for the first time to create time series representing these thousands of fashion trends life on social media.
+
+Our raw sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
+Each value represents the number per week of analysed images where our vision system detected a specific fashion trend.
+However, in this paper, we present a normalized version of our signals in order to remove strong social media biases.
+Due to the increasing use of social media and user's change of behaviours, each trend is normalized by its top hierarchical parents and consequently lie between 0 and 1.
+We deseasonized the top hierarchical parent before normalized to not remove the season of the original sequence.
+An example of normalization can be found in Figure~\ref{fig:normalization} for a  trend.
+At the end, the proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 different categories and 5 geozones.
+An overview of it can be found in Table~\ref{tab:fashiondataset}.
+
+\begin{figure}
+\centering
+\begin{subfigure}{1.\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/cn_female_top_raw}
+  \caption{Time series representing the raw signal of a top fashion trend for female in China}
+  \label{fig:normalization:sub1}
+\end{subfigure}
+\begin{subfigure}{1.\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/cn_female_top_norm}
+  \caption{Time series representing the normalized signal of a top fashion trend for female in China.}
+  \label{fig:normalization:sub2}
+\end{subfigure}
+\caption{Example of difference between the raw sequence and the normalized one. In this example, we normalize by the deseasonalized global top fashion trend for female in China.}
+\label{fig:normalization}
+\end{figure}
+%We provide the first dataset dedicated to fashion trends forecasting.
 Our fashion dataset is built with a high throughput computer vision system analysing every day images shared on social networks.
@@
 \end{table*}
-
+\label{tab:fashiondataset}
 \subsection{Weak signal}
 
-In addition to this large dataset we design for each sequence several weak signals.
-Firstly, we create a specific fashion-oriented panel of micro-influencers.
 In theoretical fashion dynamics \citep{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
-With this specific panel, we aim at detecting the first waves announcing emerging trends or the collapse of other ones.
-By analyzing images shared by this specific panel on social media, we create a first weak signal named \textit{fashion-forwards} for each of the previous trends.
-We also analyzed only a specific part of social media users depending on the number of followers.
-With three thresholds we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high}.
-Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.These extra signals are frequently sparse for micro trends and they often lack interest in common fashion trends.
+In this way, we add to our large dataset several weak signals for each sequence.
+Firstly, we created a specific fashion-oriented panel of micro-influencers.
+With the same methodology than our main signals, we can represent our fashion trends life on social media on this specific population.
+we named \textit{fashion-forwards} this first weak signal.
+For instance, an impressive emerging fashion shoes trend with its linked \textit{fashion-forwards} weak singal is represented in Figure~\ref{fig:oneemergingtrend}.
+let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
+As we want to detect shifts between our main signal and our fashion forward signal and also normalize our weak signal, we compute the following input for our hybrid model :
+for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+$$
+\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}
+$$
+
+Secondly, we analyzed only specific parts of social media users depending on the number of followers.
+With three thresholds, 0-1350,1350-7000 and 7000+, we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high}.
+Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.
+let $\ts_t^{l,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{l,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences.
+Based on them, we compute 2 inputs for our hybrid model : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+
+\begin{align*}
+\ws^{l,n}_{t} = \frac{\ts_t^{l,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}
+\end{align*}
+
+At the end, we created 3 weak signals $\ws^{l}$,$\ws^{l}$ and $\ws^{h}$.
+They are frequently sparse for micro trends and they often lack interest in common fashion trends.
 However, in several examples, they are fundamental to detect the future fashion evolution.
@@
 
-As an example, an impressive emerging fashion trend is represented in Figure~\ref{fig:oneemergingtrend}, see other examples in Appendix~\ref{}.
+%As an example, an impressive emerging fashion trend is represented in Figure~\ref{fig:oneemergingtrend}, see other examples in Appendix~\ref{}.
 It shows the evolution of one shoe trend on social media and its linked \textit{fashion-forward} weak signal.
@@
   \centering
-    \includegraphics[width=1.\linewidth]{figure/emerging_trend}
+    \includegraphics[width=1.\linewidth]{figure/ff_example}
   \caption{A shoes trend of our dataset.
 In black the main signal and in red its associated \textit{fashion-forward} weak signal.
-The Gap between our two signals in the end of 2017/beginning of 2018 announces the future explosion of the fashion trend.}
+The shift between our two signals in the end of 2017/beginning of 2018 announces the future explosion of the fashion trend.}
 \label{fig:oneemergingtrend}
@@
 It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension \textcolor{red}{Peut-on discuter/justifier ce choix ?}.
-We use a classical Adam optimizer with a learning rate equal to 0.005 and a batch size equal to 64 and the following loss function:
+We use a classical Adam optimizer with a learning rate set at 0.005  and a batch size equal to 64 and the following loss function:
 
@@
 
-All our code is developed in Python using the Tensorflow library. It allows the use of a GPU to speed up the trainig process.
+Previous parameters was set with a grid search and our code is developed in Python using the Tensorflow library. It allows the use of a GPU to speed up the trainig process.
 
@@
 \centering
-    \includegraphics[width=1.\linewidth]{figure/hybrid_model_examples}
-  \caption{\textit{hermes-tbats} forecast examples.
+\begin{subfigure}{1.\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/us_female_top}
+  \caption{Time series representing a top fashion trend for female in The United States}
+  \label{fig:sub1}
+\end{subfigure}
+\begin{subfigure}{1.\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/cn_female_texture_horizontalstipe}
+  \caption{Time series representing the horizontal stipes texture fashion trend for female in China}
+  \label{fig:sub2}
+\end{subfigure}
+\caption{\textit{hermes-tbats} forecast examples. In green the prediction of the per-time-series predictors \textit{tbats}. In red the final forecast of our HERMES hybrid model \textit{hermes-tbats}.}
+\label{fig:test}
+\end{figure}
+
+%
+%\begin{figure}
+%  \centering
+%    \includegraphics[width=1.\linewidth]{figure/hybrid_model_examples}
+%  \caption{\textit{hermes-tbats} forecast examples.
 In green the prediction of the per-time-series predictors \textit{tbats}.
 In red the final forecast of our hermes hybrid model \textit{hermes-tbats}.\textcolor{red}{Utiliser plutot des "marker" (tirets, croix, etc.) car cela differencie mieux}}
-\label{fig:hybrid-examples}
-\end{figure}
+%\label{fig:hybrid-examples}
+%\end{figure}
 
@@
 \begin{table}
-  \caption{\textit{tbats}, \textit{hermes-tbats} and \textit{hermes-tbats-ws} models confusion matrix}
-  \vspace{0.2cm}
-  \centering
-  \vspace{0.2cm}
-  \par \textit{tbats} model confusion matrix\\
-  \vspace{0.2cm}
+  \caption{\textit{tbats}, \textit{hermes-tbats} and \textit{hermes-tbats-ws} models confusion matrix }
+  %\vspace{0.2cm}
+  %\textit{tbats} model confusion matrix \\
+  %\par \textit{tbats} model confusion matrix
+  %\vspace{0.2cm}
   \begin{tabular}{l||llll}
+  	&& \multicolumn{3}{c}{\textbf{\textit{tbats}}}\\
     && pred-dec  & pred-flat & pred-inc  \\
@@
   \end{tabular}
-  \vspace{0.2cm}
-  \par \textit{hermes-tbats} model confusion matrix\\
-  \vspace{0.2cm}
-  \centering
+  \vspace{1cm}
   \begin{tabular}{l||llll}
+  	&& \multicolumn{3}{c}{\textbf{\textit{hermes-tbats}}}\\
     && pred-dec  & pred-flat & pred-inc  \\
@@
     true-flat && 131 & 5802 & 80 \\
-    true-inc && 33 & 1639 & 299 \\\
+    true-inc && 33 & 1639 & 299 \\
   \end{tabular}
   \centering
-  \vspace{0.2cm}
-  \par \textit{hermes-tbats-ws} model confusion matrix\\
-  \vspace{0.2cm}
   \begin{tabular}{l||llll}
+    && \multicolumn{3}{c}{\textbf{\textit{hermes-tbats-ws}}}\\
     && pred-dec  & pred-flat & pred-inc  \\
@@
   \caption{\textit{lstm} and \textit{lstm-ws} model confusion matrix}
-  \vspace{0.2cm}
-  \centering
-  \vspace{0.2cm}
-  \par \textit{lstm} model confusion matrix\\
-  \vspace{0.2cm}
   \begin{tabular}{l||llll}
+    && \multicolumn{3}{c}{\textbf{\textit{lstm}}}\\
     && pred-dec  & pred-flat & pred-inc  \\
@@
   \end{tabular}
-  \centering
-  \vspace{0.2cm}
-  \par \textit{lstm-ws} model confusion matrix\\
-  \vspace{0.2cm}
   \begin{tabular}{l||llll}
+    && \multicolumn{3}{c}{\textbf{\textit{lstm-ws}}}\\
    	&& pred-dec  & pred-flat & pred-inc  \\
@@
      \textit{lstm-nows} && 0.767 & 0.045 && 22.22 & 0.848 && 0.877 & 0.051\\
-     \textit{stlm} && 0.742 & - && 23.03 & - & 0.863 & -\\
-     \textit{tbats} && 0.745 & - && 22.16 & - & 0.856 & -\\
+     \textit{stlm} && 0.742 & - && 23.03 & - && 0.863 & -\\
+     \textit{tbats} && 0.745 & - && 22.16 & - && 0.856 & -\\
      \textbf{\textit{hybrid-nows}} && \textbf{0.739} & 0.003 && \textbf{22.31} & 0.083 && \textbf{0.845} & 0.003\\

### 2021-12-10 hermes_paper/hermes_paper.tex
many updates

@@
 It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension \textcolor{red}{Peut-on discuter/justifier ce choix ?}.
-We use a classical Adam optimizer with a learning rate set at 0.005  and a batch size equal to 64 and the following loss function:
+We use a classical Adam optimizer with a learning rate set at 0.001 or 0.005, a batch size equal to 64 and the following loss function:
 
@@
 
-Previous parameters was set with a grid search and our code is developed in Python using the Tensorflow library. It allows the use of a GPU to speed up the trainig process.
+Previous parameters are all set with a grid search and our code is developed in Python using the Tensorflow library. It allows the use of a GPU to speed up the trainig process.
 
@@
 
-To compare the different methods, we use the same metrics as in the M4 competition: the Mean Absolute Scaled Error (MASE), the Symmetric Mean Absolute Percentage Error (sMAPE) and the final M4 competition metric, the Overall Weighted Average (OWA) of the sMAPE and the MASE defined as follows:
+To compare the different methods, we use the Mean Absolute Scaled Error (MASE).
+As our time series have complete different scale, from $10^{-5}$ to $10^{-1}$, we choose this metric to compute a fair error measure, totally independante of the scale of the sequence.
+The MASE metric is defined as follow:
+
 \begin{align*}
-\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,\quad \mathrm{sMAPE} = \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}\,,\\
-\mathrm{OWA} &= \frac{1}{2}\left(MASE/MASE_{snaive} + sMAPE/sMAPE_{snaive}\right)\,,
+\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}
 \end{align*}
 
-where $\hat{Y}$ is a model prediction, $\lag$ is the horizon, $m$ the seasonality and $MASE_{snaive}$ is the $MASE$ computed with the $snaive$ model prediction, idem for the $sMAPE_{snaive}$.
+%To compare the different methods, we use the same metrics as in the M4 competition: the Mean Absolute Scaled Error (MASE), the Symmetric Mean Absolute Percentage Error (sMAPE) and the final M4 competition metric, the Overall Weighted Average (OWA) of the sMAPE and the MASE defined as follows:
+%\begin{align*}
+%\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,\quad \mathrm{sMAPE} = \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}\,,\\
+%\mathrm{OWA} &= \frac{1}{2}\left(MASE/MASE_{snaive} + sMAPE/sMAPE_{snaive}\right)\,,
+%\end{align*}
+%
+%where $\hat{Y}$ is a model prediction, $\lag$ is the horizon, $m$ the seasonality and $MASE_{snaive}$ is the $MASE$ computed with the $snaive$ model prediction, idem for the $sMAPE_{snaive}$.
 
@@
 A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes.
-In a given year, we define an increasing trend as a trend that does more than 10\% of growth in terms of Year and Year.
-In the same way, we define a decreasing trend as a trend that declines by 10\% or more.
+In addition to the MASE accuracy metric, we also compare the different methods on a classification task and especially difference between method using weak signals or not.
+In a given year, we define an increasing trend as a trend that does more than 5\% of growth in terms of Year and Year.
+In the same way, we define a decreasing trend as a trend that declines by 5\% or more.
 We classify other trends as flat trends.
-On the test set, the year 2019, we have 1871 increasing trends, 2016 decreasing trends and 6113 flat trends.
-In addition to the accuracy metrics, we also compare the different methods on this classification task and especially difference between method using weak signals or not.
+With this threshold, our dataset is almost balanced on the test set : we have 3087 increasing trends, 3342 decreasing trends and 3571 flat trends.
+On the test set, we compute for each method the accuracy defined as follow :
+
+\begin{align*}
+\mathrm{ACCURACY} &= \frac{TP_{dec} + TP_{flat} + TP_{inc}}{TP_{dec} + TP_{flat} + TP_{inc} + FP_{dec} + FP_{flat} + FP_{inc}}
+\end{align*}
+
+where $TP_i$ is the number of time series correctly classified in the class $i$ and $FP_i$ is the number of time series miss classified in the class $i$.
 
@@
 Models using our weak signals perform similarly as without-weak-signals models on all our 3 metrics.
-In Figure~\ref{fig:hybrid-examples}, we displayed some examples of \textit{hermes-tbats} model and some weaknessess that it is able to understand and accurately correct.
+In Figure~\ref{fig:introexamples} and Figure~\ref{fig:examples}, we displayed some examples of \textit{hermes-tbats} model and some weaknessess that it is able to understand and accurately correct.
+
+%\begin{table*}
+%  \caption{Results summary on our 10000ts Fashion dataset.
+For each metric, we compute the average on all our time series.
+For our approaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
+%  \centering
+%  \resizebox{\textwidth}{!}{%
+%  \begin{tabular}{l||llllllllll}
+%   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
+%    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
+%    \hline
+%	\hline
+%	\rule{0pt}{2ex} \\
+%     \textit{snaive} && 0.881 & - && 25.27 & - && 1. & -\\
+%     \textit{thetam}  && 0.844 & - && 24.17 & - && 0.970 & -\\
+%     \textit{arima} && 0.826 & - && 23.63 & - && 0.949 & -\\
+%     \textit{ets} && 0.807 & - && 23.58 & - && 0.937 & -\\
+%     \textit{hermes-ets-ws} && 0.769 & 0.004 && 22.69 & 0.126 && 0.901 & 0.007\\
+%     \textit{stlm} && 0.770 & - && 22.05 & - && 0.882 & -\\
+%     \textit{hermes-ets} && 0.759 & 0.001 && 22.16 & 0.026 && 0.875 & 0.001\\
+%     \textit{tbats} && 0.745 & - && 21.13 & - && 0.850 & -\\
+%     \textit{lstm-ws} && 0.728 & 0.004 && 20.18 & 0.085 && 0.837 & 0.004\\
+%     \textit{lstm} && 0.724 & 0.003 && 20.08 & 0.052  && 0.825 & 0.004\\
+%     \textit{hermes-tbats-ws} && 0.713 & 0.005 && 20.53 & 0.170 && 0.825 & 0.009\\
+%     \textbf{\textit{hermes-tbats}} && \textbf{0.715} & 0.002 && \textbf{20.41} & 0.056 && \textbf{0.816} & 0.002\\
+%    %\hline
+%  \end{tabular}
+%  }
+%\label{tab:metricresults}
+%\end{table*}
 
@@
   \resizebox{\textwidth}{!}{%
-  \begin{tabular}{l||llllllllll}
-   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
-    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
+  \begin{tabular}{l||lllll|lllll}
+   &&\multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{ACCURACY}}&\\
+    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
+%    \hline
 	 \hline
-	\hline
-	\rule{0pt}{2ex} \\
-     \textit{snaive} && 0.881 & - && 25.27 & - && 1. & -\\
-     \textit{thetam}  && 0.844 & - && 24.17 & - && 0.970 & -\\
-     \textit{arima} && 0.826 & - && 23.63 & - && 0.949 & -\\
-     \textit{ets} && 0.807 & - && 23.58 & - && 0.937 & -\\
-     \textit{hermes-ets-ws} && 0.769 & 0.004 && 22.69 & 0.126 && 0.901 & 0.007\\
-     \textit{stlm} && 0.770 & - && 22.05 & - && 0.882 & -\\
-     \textit{hermes-ets} && 0.759 & 0.001 && 22.16 & 0.026 && 0.875 & 0.001\\
-     \textit{tbats} && 0.745 & - && 21.13 & - && 0.850 & -\\
-     \textit{lstm-ws} && 0.728 & 0.004 && 20.18 & 0.085 && 0.837 & 0.004\\
-     \textit{lstm} && 0.724 & 0.003 && 20.08 & 0.052  && 0.825 & 0.004\\
-     \textit{hermes-tbats-ws} && 0.713 & 0.005 && 20.53 & 0.170 && 0.825 & 0.009\\
-     \textbf{\textit{hermes-tbats}} && \textbf{0.715} & 0.002 && \textbf{20.41} & 0.056 && \textbf{0.816} & 0.002\\
+	 &&&&&&&&&&\\
+     \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
+     \textit{thetam}  && 0.844 && -&&& 0.482 && - &\\
+     \textit{arima} && 0.826 && -&&& 0.464 && - & \\
+     \textit{ets} && 0.805 && -&&& 0.449 && - & \\
+     \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
+     \textit{hermes-ets-ws} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
+     \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
+     \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
+     \textit{lstm-ws} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
+     \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
+     \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
+     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& \textbf{0.510} && 0.005 &\\
     %\hline
@@
   \caption{Time series representing a top fashion trend for female in The United States}
-  \label{fig:sub1}
+  \label{fig:examples:sub1}
 \end{subfigure}
@@
   \caption{Time series representing the horizontal stipes texture fashion trend for female in China}
-  \label{fig:sub2}
+  \label{fig:examples:sub2}
 \end{subfigure}
 \caption{\textit{hermes-tbats} forecast examples. In green the prediction of the per-time-series predictors \textit{tbats}. In red the final forecast of our HERMES hybrid model \textit{hermes-tbats}.}
-\label{fig:test}
+\label{fig:examples}
 \end{figure}
@@
 When we look at the result of \textit{lstm-ws} and \textit{lstm} displayed in Table~\ref{tab:lstmclass}, we can also note a rise of the number of correct predictions but with an important increase of the number of classification errors.
+
+%%\texttt{•}
 
@@
     \rule{0pt}{2ex} \\
-	true-dec && 327 & 1607 & 82 \\
-    true-flat && 195 & 5586 & 232 \\
-    true-inc && 68 & 1585 & 318 \\
+	true-dec && 902 & 2113 & 327 \\
+    true-flat && 351 & 2920 & 300 \\
+    true-inc && 300 & 2078 & 709 \\
   \end{tabular}
@@
     \rule{0pt}{2ex} \\
-	true-dec && 250 & 1747 & 19 \\
-    true-flat && 131 & 5802 & 80 \\
-    true-inc && 33 & 1639 & 299 \\
+	true-dec && 1261 & 1960 & 121 \\
+    true-flat && 549 & 2823 & 199 \\
+    true-inc && 214 & 2004 & 869 \\
   \end{tabular}
@@
     \rule{0pt}{2ex} \\
-	true-dec && 615 & 1365 & 36 \\
-    true-flat && 510 & 5374 & 129 \\
-    true-inc && 65 & 1444 & 462 \\
+	true-dec && 1956 & 1245 & 141 \\
+    true-flat && 1257 & 2087 & 227 \\
+    true-inc && 358 & 1620 & 1109 \\
   \end{tabular}
@@
 \end{table}
-
-\begin{table*}
-  \caption{\textit{lstm} and \textit{lstm-ws} model confusion matrix}
-  \begin{tabular}{l||llll}
-    && \multicolumn{3}{c}{\textbf{\textit{lstm}}}\\
-    && pred-dec  & pred-flat & pred-inc  \\
-    \hline
-    \hline
-    \rule{0pt}{2ex} \\
-	true-dec && 447 & 1539 & 30 \\
-    true-flat && 444 & 5324 & 245 \\
-    true-inc && 66 & 1410 & 495 \\
-  \end{tabular}
-  \begin{tabular}{l||llll}
-    && \multicolumn{3}{c}{\textbf{\textit{lstm-ws}}}\\
-   	&& pred-dec  & pred-flat & pred-inc  \\
-    \hline
-    \hline
-    \rule{0pt}{2ex} \\
-	true-dec && 796 & 1161 & 59 \\
-    true-flat && 1053 & 4701 & 259 \\
-    true-inc && 90 & 1259 & 622 \\
-  \end{tabular}
-\label{tab:lstmclass}
-\end{table*}
+%\begin{table*}
+%  \caption{\textit{lstm} and \textit{lstm-ws} model confusion matrix}
+%  \begin{tabular}{l||llll}
+%    && \multicolumn{3}{c}{\textbf{\textit{lstm}}}\\
+%    && pred-dec  & pred-flat & pred-inc  \\
+%    \hline
+%    \hline
+%    \rule{0pt}{2ex} \\
+%	true-dec && 447 & 1539 & 30 \\
+%    true-flat && 444 & 5324 & 245 \\
+%    true-inc && 66 & 1410 & 495 \\
+%  \end{tabular}
+%  \begin{tabular}{l||llll}
+%    && \multicolumn{3}{c}{\textbf{\textit{lstm-ws}}}\\
+%   	&& pred-dec  & pred-flat & pred-inc  \\
+%    \hline
+%    \hline
+%    \rule{0pt}{2ex} \\
+%	true-dec && 796 & 1161 & 59 \\
+%    true-flat && 1053 & 4701 & 259 \\
+%    true-inc && 90 & 1259 & 622 \\
+%  \end{tabular}
+%\label{tab:lstmclass}
+%\end{table*}
 %Table~\ref{tab:metricresults} summarize the results of all our benchmark models and our 2 hybrid methods for the 3 metrics described above.
@@
 
+%\begin{table*}
+%  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series.
+For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
+%  \centering
+% \resizebox{\textwidth}{!}{
+%  \begin{tabular}{l||llllllllll}
+%   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
+%    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
+%    \hline
+%	\hline
+%	\rule{0pt}{2ex} \\
+%     \textit{snaive} && 0.871 & - && 25.29 & - && 1. & -\\
+%     \textit{thetam}  && 0.849 & - && 24.58 & - && 0.980 & -\\
+%     \textit{arima} && 0.821 & - && 23.69 & - && 0.951 & -\\
+%     \textit{ets} && 0.801 & - && 24.18 & - && 0.944 & -\\
+%     \textit{stlm} && 0.765 & - && 22.22 & - && 0.885 & -\\
+%     \textit{lstm-nows} && 0.740 & 0.007 && 20.56 & 0.154 && 0.856 & 0.008\\
+%     \textit{tbats} && 0.734 & - && 21.19 & - && 0.847 & -\\
+%     \textbf{\textit{hybrid-nows}} && \textbf{0.719} & 0.002 && \textbf{20.79} & 0.094 && \textbf{0.833} & 0.004\\
+%  \end{tabular}
+%  }
+%\label{tab:1000metricresults}
+%\end{table*}
+
 \begin{table*}
-  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series.
+  \caption{Results summary on our 1000ts Fashion dataset and 100ts Fashion Dataset.For each metric, we compute the average on all our time series.
 For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
-  \centering
+%  \centering
  \resizebox{\textwidth}{!}{
-  \begin{tabular}{l||llllllllll}
-   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
-    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
+
+  \begin{tabular}{l||llll}
+    \multicolumn{4}{c}{1000 ts Fashion dataset}\vspace{0.5cm} \\
+    &&\multicolumn{2}{c}{\textbf{MASE}} \\
+    &&  \textit{mean}  & \textit{std}  \\
+%    \hline
 	 \hline
+	 &&& \\
+     \textit{snaive} && 0.871 & - \\
+     \textit{thetam}  && 0.849 & - \\
+     \textit{arima} && 0.821 & - \\
+     \textit{ets} && 0.801 & - \\
+     \textit{stlm} && 0.765 & - \\
+     \textit{lstm-nows} && 0.740 & 0.007 \\
+     \textit{tbats} && 0.734 & - \\
+     \textbf{\textit{hybrid-nows}} && \textbf{0.719} & 0.002 \\
+  \end{tabular}
+  \quad
+  \begin{tabular}{l||llll}
+   \multicolumn{4}{c}{100 ts Fashion dataset}\vspace{0.5cm} \\
+   &&\multicolumn{2}{c}{\textbf{MASE}} \\
+    &&  \textit{mean}  & \textit{std}  \\
+%    \hline
 	\hline
-	\rule{0pt}{2ex} \\
-     \textit{snaive} && 0.871 & - && 25.29 & - && 1. & -\\
-     \textit{thetam}  && 0.849 & - && 24.58 & - && 0.980 & -\\
-     \textit{arima} && 0.821 & - && 23.69 & - && 0.951 & -\\
-     \textit{ets} && 0.801 & - && 24.18 & - && 0.944 & -\\
-     \textit{stlm} && 0.765 & - && 22.22 & - && 0.885 & -\\
-     \textit{lstm-nows} && 0.740 & 0.007 && 20.56 & 0.154 && 0.856 & 0.008\\
-     \textit{tbats} && 0.734 & - && 21.19 & - && 0.847 & -\\
-     \textbf{\textit{hybrid-nows}} && \textbf{0.719} & 0.002 && \textbf{20.79} & 0.094 && \textbf{0.833} & 0.004\\
+	 &&& \\
+     \textit{snaive} && 0.876 & - \\
+     \textit{thetam}  && 0.823 & - \\
+     \textit{arima} && 0.814 & - \\
+     \textit{ets} && 0.785 & - \\
+     \textit{lstm-nows} && 0.767 & 0.045 \\
+     \textit{stlm} && 0.742 & - \\
+     \textit{tbats} && 0.745 & - \\
+     \textbf{\textit{hybrid-nows}} && \textbf{0.739} & 0.003 \\
   \end{tabular}
@@
 %\end{table*}
-\begin{table*}
-  \caption{Results summary on our 100ts Fashion dataset.
+%\begin{table*}
+%  \caption{Results summary on our 100ts Fashion dataset.
 For each metric, we compute the average on all our time series.
 For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
-  \centering
-  \resizebox{\textwidth}{!}{
-  \begin{tabular}{l||llllllllll}
-   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
-    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
-    \hline
-	\hline
-	\rule{0pt}{2ex} \\
-     \textit{snaive} && 0.876 & - && 26.98 & - && 1. & -\\
-     \textit{thetam}  && 0.823 & - && 25.11 & - && 0.944 & -\\
-     \textit{arima} && 0.814 & - && 24.61 & - && 0.940 & -\\
-     \textit{lstm-nows} && 0.767 & 0.045 && 22.22 & 0.848 && 0.877 & 0.051\\
-     \textit{stlm} && 0.742 & - && 23.03 & - && 0.863 & -\\
-     \textit{tbats} && 0.745 & - && 22.16 & - && 0.856 & -\\
-     \textbf{\textit{hybrid-nows}} && \textbf{0.739} & 0.003 && \textbf{22.31} & 0.083 && \textbf{0.845} & 0.003\\
-  \end{tabular}
-  }
-\label{tab:100metricresults}
-\end{table*}
+%  \centering
+%  \resizebox{\textwidth}{!}{
+%  \begin{tabular}{l||llllllllll}
+%   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
+%    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
+%    \hline
+%	\hline
+%	\rule{0pt}{2ex} \\
+%     \textit{snaive} && 0.876 & - && 26.98 & - && 1. & -\\
+%     \textit{thetam}  && 0.823 & - && 25.11 & - && 0.944 & -\\
+%     \textit{arima} && 0.814 & - && 24.61 & - && 0.940 & -\\
+%     \textit{lstm-nows} && 0.767 & 0.045 && 22.22 & 0.848 && 0.877 & 0.051\\
+%     \textit{stlm} && 0.742 & - && 23.03 & - && 0.863 & -\\
+%     \textit{tbats} && 0.745 & - && 22.16 & - && 0.856 & -\\
+%     \textbf{\textit{hybrid-nows}} && \textbf{0.739} & 0.003 && \textbf{22.31} & 0.083 && \textbf{0.845} & 0.003\\
+%  \end{tabular}
+%  }
+%\label{tab:100metricresults}
+%\end{table*}
 

### 2021-12-10 hermes_paper/hermes_paper.tex
Minor changes

@@
   \centering
-  \includegraphics[width=1.\linewidth]{figure/us_female_shoes}
+  \includegraphics[width=.8\linewidth]{figure/us_female_shoes}
   \caption{Time series representing a shoes fashion trend for female in The United States}
@@
   \centering
-  \includegraphics[width=1.\linewidth]{figure/br_female_texture_verticalstripe}
+  \includegraphics[width=.8\linewidth]{figure/br_female_texture_verticalstripe}
   \caption{Time series representing the vertical stipes texture fashion trend for female in Brazil}
@@
 \end{subfigure}
-\caption{Hermes forecast examples. In green the prediction of the TBATS per-time-series predictors. In red the final forecast of our HERMES hybrid model.}
+\caption{Hermes forecast examples.
+In green the prediction of the TBATS per-time-series predictors.
+In red the final forecast of our HERMES hybrid model.
+\textcolor{red}{Ajouter une legende (courbes et axes) et augmenter la police des ticks en abscisses et ordonnées}}
 \label{fig:introexamples}
@@
 
-\textcolor{red}{Ajouter ici une figure avec une ou deux series temporelles mal predites par le modele statistique et bien corrigees par le RNN pour illustrer le potentiel.}
 % Indeed, depending on time series, some family of parametric models can achieve really heterogeneous level of accuracy. 
@@
 
-We note $\rnn(.;\rnnparam)$ the recurrent neural network model where $\rnnparam$ are  unknown parameters.
+Let $\rnn(.;\rnnparam)$ be the recurrent neural network model where $\rnnparam$ are  unknown parameters.
 Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\rnnparam$, the error-corrector predictions $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
@@
 \label{eq:nows:full:model}
-\tspred^n_{T+i|T}  = \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\
+\tspred^n_{T+i|T}  = \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\,.
 \end{equation}
@@
 For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ linked to the sequence $\fullts^n$.
-We note $\fullws^n = \{\{\ws_t^{n,k}\}_{1\leqslant t \leqslant T}\}_{1\leqslant k \leqslant K}$ all the values of the family of weak signals linked to the $n$-th sequence.
-In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the family.
-Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for our RNN,
+Let  $\fullws^n = \{\{\ws_t^{n,k}\}_{1\leqslant t \leqslant T}\}_{1\leqslant k \leqslant K}$ be all the values of the weak signals linked to the $n$-th sequence.
+In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the sequence.
+Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for the RNN,
 $$
@@
 $$
-Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ our final model becomes:
+Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ the final prediction becomes:
 %$$
@@
 Our fashion dataset is built with the suprising alliance of a high throughput computer vision system and experts of the fashion sphere.
-A team of deep learning engineers designed and trained a collection of vision neural networks at detecting clothes details: color, cloth type (pants, shoes, top etc...), form, size, texture etc...
-Then a second team of fashion experts aggregates these previous attributes and created thousands of fashion trends.
+A team of deep learning engineers designed and trained a collection of vision neural networks at detecting clothes details: color, cloth type (pants, shoes, top etc...), form, size, texture etc.
+Then a second team of fashion experts aggregated these previous attributes and created thousands of fashion trends.
 Analysing every day images shared on social networks, we are finally able for the first time to create time series representing these thousands of fashion trends life on social media.
@@
 Our raw sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
-Each value represents the number per week of analysed images where our vision system detected a specific fashion trend.
-However, in this paper, we present a normalized version of our signals in order to remove strong social media biases.
-Due to the increasing use of social media and user's change of behaviours, each trend is normalized by its top hierarchical parents and consequently lie between 0 and 1.
-We deseasonized the top hierarchical parent before normalized to not remove the season of the original sequence.
+Each value represents the (normalized) number of analysed images per week where our vision system detected a specific fashion trend.
+%However, in this paper, we present a normalized version of our signals in order to remove strong social media biases.
+Due to the increasing use of social media and users changes of behaviour, each trend is normalized by its top hierarchical parents and consequently lies between 0 and 1.
+We deseasonized the top hierarchical parent before the normalizing step to keep the season of the original sequence.
 An example of normalization can be found in Figure~\ref{fig:normalization} for a  trend.
-At the end, the proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 different categories and 5 geozones.
+The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 different categories and 5 geozones.
 An overview of it can be found in Table~\ref{tab:fashiondataset}.
@@
 
-With in-house fashion experts, we selected especially a collection of $\numberts$ fashion trends in order to represent finely the issues that face the fashion industry.
-A large part of our time series are quite stable, their seasons and evolutions are regular.
-However, some sequences show interesting behaviours with sudden changes.
+With in-house fashion experts, we selected especially a collection of $\numberts$ fashion trends in order to represent finely the issues faced by the fashion industry.
+Some sequences show interesting behaviours with sudden changes.
 We call them emerging or declining trends depending on the change in direction.
@@
 \medskip
-\textcolor{red}{Est-ce pertinent de decrire les outils de computer vision utilises pour construire le jeu de donnees ? Ou de decrire plus precisement la nature des $y$ consideres ? De }
+%\textcolor{red}{Est-ce pertinent de decrire les outils de computer vision utilises pour construire le jeu de donnees ? Ou de decrire plus precisement la nature des $y$ consideres ? De }
 

### 2021-12-10 hermes_paper/hermes_paper.tex
Minor changes

@@
 Firstly, we created a specific fashion-oriented panel of micro-influencers.
-With the same methodology than our main signals, we can represent our fashion trends life on social media on this specific population.
+With the same methodology than for target signals, we can represent  fashion trends life on social media on this specific population.
 we named \textit{fashion-forwards} this first weak signal.
-For instance, an impressive emerging fashion shoes trend with its linked \textit{fashion-forwards} weak singal is represented in Figure~\ref{fig:oneemergingtrend}.
+For instance, an impressive emerging fashion shoes trend with its linked \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
 let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
-As we want to detect shifts between our main signal and our fashion forward signal and also normalize our weak signal, we compute the following input for our hybrid model :
+As we want to detect shifts between target signals and and fashion forward signal and also normalize the weak signal, we compute the following input for our hybrid model:
 for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
 $$
-\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}
+\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}\,.
 $$
@@
 Secondly, we analyzed only specific parts of social media users depending on the number of followers.
-With three thresholds, 0-1350,1350-7000 and 7000+, we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high}.
+With three thresholds, 0-1350,1350-7000 and 7000+, we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high} \textcolor{red}{Pas clair}.
 Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.
 let $\ts_t^{l,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{l,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences.
-Based on them, we compute 2 inputs for our hybrid model : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+Based on them, we compute two inputs for our hybrid model : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
 
@@
 
-At the end, we created 3 weak signals $\ws^{l}$,$\ws^{l}$ and $\ws^{h}$.
+Therefore, we created three weak signals $\ws^{l}$,$\ws^{l}$ and $\ws^{h}$.
 They are frequently sparse for micro trends and they often lack interest in common fashion trends.
-However, in several examples, they are fundamental to detect the future fashion evolution.
+However, in several examples, they are fundamental to detect the future fashion evolution, \textcolor{red}{as illustrated in Section~\ref{}}.
 
@@
 
-To train our hybrid model, we split our dataset into three blocks, train, eval and test sets.
-We use the 3 first years as our train set, we keep the 4th year for our eval set and we hide the last year for our test set.
-We train our hyrid model to compute a one-year ahead prediction, $\lag$ equal to 52, and we set the window size $\window$ equal to 104.
-Using the two first year of our train set, we fit a first per-time-series parametric model for each time series.
+We split the dataset into three blocks, train, eval and test sets.
+We use the 3 first years as train set, keep the 4th year for the evaluation set and hide the last year for the test set.
+We trained the hyrid model to compute a one-year ahead prediction, $\lag$ equal to 52, and we set the window size $\window$ equal to 104.
+Using the two first year of the train set, we fit a first per-time-series parametric model for each time series.
 With the resulting collection of local models, we compute a first forecast of the third year for each sequence.
-Using these forecasts, we preprocess our time series and finally determine our RNN inputs.
+Using these forecasts, we preprocess  time series and finally compute the RNN inputs.
 In the same way, for the eval set, we fit a second time our per-time-series predictors using the three first years and we forecast the fourth year.
-We preprocess our time series and we evaluate how our error-corrector RNN is able to improve the first collection of predictions of the fourth year.
-At the end, we repeat the same process for the fifth year and compute our final accuracy measures. An example of our temporal split is shown in  Figure~\ref{fig:train_eval_test_set}.
+We preprocess time series and evaluate how the error-corrector RNN is able to improve the first collection of predictions of the fourth year.
+The same process is repeated for the fifth year and compute our final accuracy measures.
+An example of our temporal split is shown in  Figure~\ref{fig:train_eval_test_set}.
 %We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52.

### 2021-12-10 hermes_paper/hermes_paper.tex
Minor changes

@@
 %$\{\statparam^n\}_{1\leqslant n \leqslant N}$ are fixed during the training of the recurrent models. 
-In this section we propose two versions of HERMES depending of the choice of local parametric models.
-The first one use as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}.
-The second one use as predictors the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves striking accuracy results on our fashion dataset.
+We propose two versions of HERMES depending of the choice of local parametric models.
+The first one uses as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}.
+The second one uses as predictors the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves striking accuracy results on the fashion dataset.
 For the neural network part, we built an architecture summarized in Figure~\ref{fig:rnn_architecture}.
-It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension \textcolor{red}{Peut-on discuter/justifier ce choix ?}.
+It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension.
 We use a classical Adam optimizer with a learning rate set at 0.001 or 0.005, a batch size equal to 64 and the following loss function:
@@
 
-For our 3 metrics and for each model, we compute the average on all our sequences \numberts~  on the final year.
+For the two metrics and for each model, we compute the average on all our sequences \numberts~  on the final year.
 Results are displayed in the Table~\ref{tab:metricresults}.
-For our model using neural networks, we trained 10 models with different seeds and compute the average and the standard deviation for the three metrics.
-For the statistical models, we can see a large domination of the TBATS model with an OWA equal to 0.850.
+For our model using neural networks, we trained 10 models with different seeds and compute the average and the standard deviation.
+For the statistical models, we can see a large domination of TBATS.
 It is one of the main motivations why we use this model on our best HERMES candidate as the predictor model.
-However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825.
-
-Considering our new HERMES approach, we see a large domination of our \textit{hermes-tbats} version with a OWA equal to 0.816 and a strong stability across the different trainings.
-Regarding \textit{hermes-ets}, we see a huge increase compared to its predictor choice \textit{ets} with a descrease from 0.937 to 0.875 in term of OWA.
-However, its accuracy remains low in comparison to the \textit{lstm} benchmarck or HERMES using TBATS.
-Models using our weak signals perform similarly as without-weak-signals models on all our 3 metrics.
-In Figure~\ref{fig:introexamples} and Figure~\ref{fig:examples}, we displayed some examples of \textit{hermes-tbats} model and some weaknessess that it is able to understand and accurately correct.
+%However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825.
+\textcolor{red}{OWA dans le tableau ?}
+
+Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slighlty outperform the alternatives   in terms of MASE and are stable across the different trainings.
+Regarding \textit{hermes-ets},  its accuracy remains low in comparison to the \textit{lstm} benchmarck or HERMES using TBATS.
+
+Models using our weak signals perform similarly as without-weak-signals models for the MASE.
+In Figure~\ref{fig:introexamples}.
+Interestingly, weak signals sinificantly improve the accuracy in detecting emerging and declining trends.
+Figure~\ref{fig:examples}, we displayed some examples of \textit{hermes-tbats} model and some weaknessess that can be corrected.
 

### 2021-12-13 hermes_paper/hermes_paper.tex
a few updates

@@
   \centering
-  \includegraphics[width=.8\linewidth]{figure/us_female_shoes}
+  \includegraphics[width=1.\linewidth]{figure/us_female_shoes}
   \caption{Time series representing a shoes fashion trend for female in The United States}
@@
   \centering
-  \includegraphics[width=.8\linewidth]{figure/br_female_texture_verticalstripe}
+  \includegraphics[width=1.\linewidth]{figure/br_female_texture_verticalstripe}
   \caption{Time series representing the vertical stipes texture fashion trend for female in Brazil}
@@
 They are frequently sparse for micro trends and they often lack interest in common fashion trends.
-However, in several examples, they are fundamental to detect the future fashion evolution, \textcolor{red}{as illustrated in Section~\ref{}}.
+However, in several examples, they are fundamental to detect the future fashion evolution, as illustrated in Section~\ref{sec:exp}.
+\textcolor{red}{as illustrated in Section~\ref{}}.
 
@@
   \centering
-  \resizebox{\textwidth}{!}{%
+  \resizebox{0.85\textwidth}{!}{%
   \begin{tabular}{l||lllll|lllll}
@@
   \centering
-  \includegraphics[width=1.\linewidth]{figure/cn_female_texture_horizontalstipe}
+  \includegraphics[width=1.\linewidth]{figure/cn_female_texture_horizontalstripe}
   \caption{Time series representing the horizontal stipes texture fashion trend for female in China}
@@
 We did 2 experiments, we train our models on a dataset of 1000 time series and on a dataset of 100 time series.
-Results are given in Table~\ref{tab:1000metricresults} and Table~\ref{tab:100metricresults}.
+Results are given in Table~\ref{tab:1000metricresults}.
 
@@
 Due to the strengh of its per-time-series predictor TBATS, our hybrid model succeds at correcting some of its weaknesses and logically reach a striking final accuracy.
-Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size is smaller.
-With a small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} can largely outperform its accuracy level.
+Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decrease.
+On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperform its accuracy level.
 Learn how to compute a full prediction from scratch is a complex task and high-dimensional recurrent neural networks require  large amount of data.
@@
 For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
-%  \centering
- \resizebox{\textwidth}{!}{
+  \centering
+ \resizebox{0.85\textwidth}{!}{
 
@@
      \textit{tbats} && 0.734 & - \\
-     \textbf{\textit{hybrid-nows}} && \textbf{0.719} & 0.002 \\
+     \textbf{\textit{hermes-tbats}} && \textbf{0.719} & 0.002 \\
   \end{tabular}
@@
      \textit{tbats} && 0.745 & - \\
-     \textbf{\textit{hybrid-nows}} && \textbf{0.739} & 0.003 \\
+     \textbf{\textit{hermes-tbats}} && \textbf{0.739} & 0.003 \\
   \end{tabular}

### 2021-12-13 hermes_paper/hermes_paper.tex
dataset overview update

@@
 
+\subsection{Translate fashion to data}
+
+A collection of vision neural networks have been designed and trained  at detecting clothes details on pictures: cloth type (pants, shoes, top etc...), form, size,color,texture etc...
+Then, with the knowledge of a team of fashion experts, these clothes details was aggregated in order to define a fashion trend: a meaningfully combination of items that represents an existing trend in the fashion sphere.
+Analysing every day images shared on social networks with the previous computer vision system, we are finally able to translate the history of thousand of fashion trends in thousands of time series.
+All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
+Each value represents the number of posts in a week where vision algorithms detected the fashion trend on picture.
+As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization:sub1}.
+
 \subsection{Fashion dataset}
 
-We provide the first dataset dedicated to fashion trends forecasting.
+Due to the increasing use of social media and users change of behaviour, a throughput normalization is applied to the raw sequences.
+Each fashion trend is divided by its hierarchical parent category trend.
+Moreover, in order to not remove the season of all sequences, we deseasonalized the hierarchical parent category trend before dividing.
+For instance, as displayed in Figure~\ref{fig:normalization}, the raw Jersey Top trend for female in China is divided by the deseasonalized global Top trend for female in China.
+the final normalized sequence is expressed in share of category.
+
+In addition to this paper, a fashion dataset is proposed.
+It contains an sample of $\numberts$ anonymized and  normalized fashion trends for men and women, on 9 different categories and 5 geozones.
+An overview of it can be found in Table~\ref{tab:fashiondataset}.
+A collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry.
+Some sequences show interesting behaviours with sudden changes.
+We call them emerging or declining trends depending on the change in direction.
+A central point of this work is to accurately detect and forecast these trends.
+
+%We provide the first dataset dedicated to fashion trends forecasting.
 Our fashion dataset is built with the suprising alliance of a high throughput computer vision system and experts of the fashion sphere.
@@
 Then a second team of fashion experts aggregated these previous attributes and created thousands of fashion trends.
-Analysing every day images shared on social networks, we are finally able for the first time to create time series representing these thousands of fashion trends life on social media.
-
-Our raw sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
+%Analysing every day images shared on social networks, we are finally able for the first time to create time series representing these thousands of fashion trends life on social media.
+%
+%Our raw sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
 Each value represents the (normalized) number of analysed images per week where our vision system detected a specific fashion trend.
 %However, in this paper, we present a normalized version of our signals in order to remove strong social media biases.
-Due to the increasing use of social media and users changes of behaviour, each trend is normalized by its top hierarchical parents and consequently lies between 0 and 1.
+%Due to the increasing use of social media and users changes of behaviour, each trend is normalized by its top hierarchical parents and consequently lies between 0 and 1.
 We deseasonized the top hierarchical parent before the normalizing step to keep the season of the original sequence.
 An example of normalization can be found in Figure~\ref{fig:normalization} for a  trend.
-The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 different categories and 5 geozones.
+%The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 different categories and 5 geozones.
 An overview of it can be found in Table~\ref{tab:fashiondataset}.
@@
 
-With in-house fashion experts, we selected especially a collection of $\numberts$ fashion trends in order to represent finely the issues faced by the fashion industry.
+%With in-house fashion experts, we selected especially a collection of $\numberts$ fashion trends in order to represent finely the issues faced by the fashion industry.
 Some sequences show interesting behaviours with sudden changes.

### 2021-12-13 hermes_paper/hermes_paper.tex
weak signals part update

@@
 Then, with the knowledge of a team of fashion experts, these clothes details was aggregated in order to define a fashion trend: a meaningfully combination of items that represents an existing trend in the fashion sphere.
-Analysing every day images shared on social networks with the previous computer vision system, we are finally able to translate the history of thousand of fashion trends in thousands of time series.
+To represent finely the society behaviours based on social media, a group of thousands of random users, called a panel, have been created on several geolocalisations.
+Analysing every day images shared on social networks by these panels with the previous computer vision system, we are finally able to translate the history of thousand of fashion trends in thousands of time series.
 All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
-Each value represents the number of posts in a week where vision algorithms detected the fashion trend on picture.
+Each value represents the number of users posts in a week where vision algorithms detected the fashion trend on picture.
 As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization:sub1}.
@@
 In this way, we add to our large dataset several weak signals for each sequence.
-Firstly, we created a specific fashion-oriented panel of micro-influencers.
-With the same methodology than for target signals, we can represent  fashion trends life on social media on this specific population.
+
+Firstly, fashion experts found numerous social media influencers and created a specific ``fashion-oriented`` panel.
+With the same methodology than for the main panel, a normalized time series representing each fashion trend on this specific population is created.
 we named \textit{fashion-forwards} this first weak signal.
@@
 let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
-As we want to detect shifts between target signals and and fashion forward signal and also normalize the weak signal, we compute the following input for our hybrid model:
+As we want to detect shifts between the main signal and the fashion forward signal, we compute the following input for our hybrid model: 
 for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
@@
 $$
-
-Secondly, we analyzed only specific parts of social media users depending on the number of followers.
+values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.
+
+Secondly, depending of the number of followers, the general panel of users is divided in three: users with less than 1350 followers, users with a number of followers between 1350 and 7000 and users with more than 7000 followers.
+Repeating our methodology on each sub-panel, three normalized time series for each time series is created.
+Again, the motivation here is to detect behaviour gaps between different part of the society that could announce bigger changes in the main signal.
+let $\ts_t^{l,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{l,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences.
+Based on them, we compute two inputs for our hybrid model : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+
+\begin{align*}
+\ws^{l,n}_{t} = \frac{\ts_t^{l,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}
+\end{align*}  
+values close to 0.3 indicate a similar behaviour between the three sub-panels and the general panel.
+
+%Secondly, we analyzed only specific parts of social media users depending on the number of followers.
 With three thresholds, 0-1350,1350-7000 and 7000+, we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high} \textcolor{red}{Pas clair}.
@@
 Based on them, we compute two inputs for our hybrid model : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
-
-\begin{align*}
-\ws^{l,n}_{t} = \frac{\ts_t^{l,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}
-\end{align*}
-
-Therefore, we created three weak signals $\ws^{l}$,$\ws^{l}$ and $\ws^{h}$.
+%
+%\begin{align*}
+%\ws^{l,n}_{t} = \frac{\ts_t^{l,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}
+%\end{align*}
+
+In addition the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{l}$ and $\ws^{h}$ are added.
 They are frequently sparse for micro trends and they often lack interest in common fashion trends.

### 2021-12-14 hermes_paper/hermes_paper.tex
Conclusion update

@@
 
-\subsection{Discussion}
-\label{sec:discussion}
+%\subsection{Discussion}
+%\label{sec:discussion}
 
@@
 
-With our results, we can make several interesting conclusions.
+%With our results, we can make several interesting conclusions.
 Firstly, our new HERMES framework is a really promising framework.
@@
 
-In this paper, we propose the first hybrid model including external weak signals for time series forecasting.
+%In this paper, we propose the first hybrid model including external weak signals for time series forecasting.
 We show that hybrid framework is a really promising way and with its extended error-corrector DNN part, it is clearly well-suited for dealing with any kind of external signals.
@@
 
-With this first contribution, we join the first fashion dataset gathering \numberts\ fashion times series and a complex collection of external signals.
+%With this first contribution, we join the first fashion dataset gathering \numberts\ fashion times series and a complex collection of external signals.
 We believe that this dataset hide really fine dynamics and interactions where complex models would express their potential.
 By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting and pave the way for further explorations.
+
+The motivation of this paper was to present HERMES, a new hybird model for time series forecasting.
+This new framework is a really promising approach.
+By mixing the performance of local parametric models and a global neural network.
+The \textit{hermes-tbats} version clearly outperform traditional statistical methods and full neural network models.
+Furthermore, this new model is totally suited for dealing with external signals.
+With a fine pre-processing and a well-designed architecture, our hybrid framework succeed at leveraging our complex extra data and reach impressive accuracy level in term of classification.
+In addition to this article, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided.
+We believe that this dataset hide really fine dynamics and interactions where complex models would express their potential.
+By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting and pave the way for further explorations.
+As a possible future work, a different inclusion of the weak signals can be design in the HERMES architecture.
+Focusing on the example with huge change of behaviors, a fine analysis of the predictive power of the collection of weak signals can be done.
+In the same way, an interesting improvment of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses and activate or not by a latent space.
+This latent space can be drive by the historical data or by the weak signals.
+
+%final results bring to light the quality of our new Fashion dataset.
+We saw that the full LSTM model \textit{lstm} outperforms all time series specific models when it is trained with the biggest dataset of 10000 time series but not with the smaller ones.
+This shows that complex neural network architectures involve large amount of data to be train and our full dataset is well suited for this.
+Finally, with the addition of our weak signals, we give a totally new dimension to our new hybrid architecture and our fashion dataset.
+Our results show that our external weak signals hide a complex but usable predictive power by our HERMES model.
+However, we believe that it remains a lot of ways to explore in order to leverage the full potential of these chaotic signals.
+
+%With our results, we can make several interesting conclusions.
+Firstly, our new HERMES framework is a really promising framework.
+By mixing the performance of local parametric models and a global DNN, our \textit{hermes-tbats} version clearly outperform traditional statistical methods and full neural network models.
+Furthermore, this framework is totally suited for dealing with external signals.
+With a fine pre-processing and a well-designed architecture, our hybrid framework succeed at leveraging our complex extra data and reach impressive accuracy level in term of classification.
+Secondly, our results bring to light the quality of our new Fashion dataset.
+We saw that the full LSTM model \textit{lstm} outperforms all time series specific models when it is trained with the biggest dataset of 10000 time series but not with the smaller ones.
+This shows that complex neural network architectures involve large amount of data to be train and our full dataset is well suited for this.
+Finally, with the addition of our weak signals, we give a totally new dimension to our new hybrid architecture and our fashion dataset.
+Our results show that our external weak signals hide a complex but usable predictive power by our HERMES model.
+However, we believe that it remains a lot of ways to explore in order to leverage the full potential of these chaotic signals.
 

### 2021-12-14 hermes_paper/hermes_paper.tex
remove we/our formulation

@@
 Following this work, we present in this paper HERMES, a new hybrid recurrent model for time series forecasting with inclusion of external signals.
-Our model is decomposed  into two parts: local predictors and a global corrector.
+This new architecture is decomposed  into two parts: local predictors and a global corrector.
 First, a per-time-series parametric statistical model is trained on all sequences.
 Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.
-By adding external weak signals in our proposed framework, we show the real potential of the hybrid approach: a global neural network, able to leverage large amount of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of any parametric models.
+By adding external weak signals in the proposed framework, the real potential of the hybrid approach is revealed: a global neural network, able to leverage large amount of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of any parametric models.
 %Our new hybrid framework is divided in two parts.
@@
 The paper is organized as follow.
-Section~\ref{sec:hybrid} describes our hybrid framework.
-Then, we present our new fashion dataset in Section~\ref{sec:dataset}.
-Section~\ref{sec:exp} describes our results and comparisons with several benchmarks.
-Finally, we detail research perspectives and conclude our paper in Section~\ref{sec:discussion} and Section~\ref{sec:conclusion}.
+Section~\ref{sec:hybrid} describes the hybrid framework.
+Then, the new fashion dataset provided with this article is presented in Section~\ref{sec:dataset}.
+Section~\ref{sec:exp} describes the HERMES results and comparisons with several benchmarks.
+Finally, a general conclusion and some research perspectives are given in  Section~\ref{sec:conclusion}.
 
@@
 We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, the predictors, and a global error-corrector neural network train on all time series, the corrector.
-We use  per-time-series parametric models to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
-Then, gathering information of the first predictions and external variables, we use a recurrent neural networks to correct the predictions provided by the first collection of per-time-series models.
+Per-time-series parametric models are used to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
+Then, gathering information of the first predictions and external variables, a recurrent neural networks is trained to correct the predictions provided by the first collection of per-time-series models.
 
@@
 However, on sporadic time series, this choice leads to poor result and instability.
-In this paper, we provide a general framework able to deal with any kind of per-time-series models.
-In Section~\ref{sec:exp}, we present two versions of our framework.
+In this paper, a more general framework able to deal with any kind of per-time-series models is provided.
+In Section~\ref{sec:exp}, two versions of our framework are proposed.
 The first one use an  exponential smoothing as reference similar to the baseline \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
@@
 
-In the specific application of fashion trends prediction, we detected and defined two main forms of standard weaknesses for a univariate parametric forecast as defined above.
+In the specific application of fashion trends prediction, two main forms of standard weaknesses was detected and defined for an univariate parametric forecast as defined above.
 The first one is a weakness of definition, when the model is not well defined for its forecasting task.
@@
 In somes cases, these changes depend on external variables not considered by univariate parametric models.
-The difficulty is that we mainly unknow the exact influence of external variables on the main signal.
-It is on this point that our new hybrid framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals.
-First forecast examples of our new hybrid model are given in Figure~\ref{fig:introexamples}
+The difficulty is that the exact influence of external variables on the main signal are not mainly know.
+It is on this point that  the new HERMES framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals.
+First forecast examples of this new hybrid model are given in Figure~\ref{fig:introexamples}
 
@@
 
-The second part of our model is a global RNN, trained on all the $N$ sequences to correct the weaknesses of the first per-time-series parametric models.
+The second part of the model is a global RNN, trained on all the $N$ sequences to correct the weaknesses of the first per-time-series parametric models.
 This task requires a thorough data pre-processing for two main reasons.
-First, we provide  to the RNN the best input in order to understand the initial collection of forecasts and predict their future errors.
-Second, as we did not make any assumption about the scale of our time series, we have to carefully normalize them before feeding them to the RNN.
+First, without a well-design input, the RNN will not capable of understanding the initial collection of forecasts and predict their future errors.
+Second, as no assumption about the scale of our time series was made, inputs require a careful normalization before feeding them to the RNN.
 Consider the following pre-processing. 
@@
 Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$.
-We define as our RNN input the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$,
+the RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$,
 $$
@@
 
-Using well-fitted time-series-specific parametric models, our hybrid network corrects the first form of weakness and achieves striking accuracy on our dataset, see Table~\ref{tab:metricresults}.
-Then, to correct the second form of weakness, in addition to the $N$ target time series, we consider $K \times N$ external sequences indexed from $0$ to $T$.
+Using well-fitted time-series-specific parametric models, the new hybrid network corrects the first form of weakness and achieves striking accuracy on the provided fashion dataset, see Table~\ref{tab:metricresults}.
+Then, to correct the second form of weakness, in addition to the $N$ target time series, $K \times N$ external sequences indexed from $0$ to $T$ are considered.
 For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ linked to the sequence $\fullts^n$.
@@
 In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the sequence.
-Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for the RNN,
+Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, a new input for the RNN is defined:
 $$
@@
 \subsection{Translate fashion to data}
-
+\label{sec:dataset:a}
 A collection of vision neural networks have been designed and trained  at detecting clothes details on pictures: cloth type (pants, shoes, top etc...), form, size,color,texture etc...
@@
 \subsection{Fashion dataset}
+\label{sec:dataset:b}
 
@@
 An overview of it can be found in Table~\ref{tab:fashiondataset}.
-A collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry.
+this collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry.
 Some sequences show interesting behaviours with sudden changes.
-We call them emerging or declining trends depending on the change in direction.
+They are called them emerging or declining trends depending on the change in direction.
 A central point of this work is to accurately detect and forecast these trends.
@@
 In theoretical fashion dynamics \citep{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
-In this way, we add to our large dataset several weak signals for each sequence.
-
-Firstly, fashion experts found numerous social media influencers and created a specific ``fashion-oriented`` panel.
-With the same methodology than for the main panel, a normalized time series representing each fashion trend on this specific population is created.
+In this way, several weak signals for each sequence are added to the proposed large dataset.
+
+Firstly, numerous social media influencers was selectioned by hand and aggregatim them, a specific ``fashion-oriented`` panel was created.
+With the same methodology than for the main panel descibed in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created.
 we named \textit{fashion-forwards} this first weak signal.
@@
 let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
-As we want to detect shifts between the main signal and the fashion forward signal, we compute the following input for our hybrid model: 
+As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for our hybrid model: 
 for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
@@
 
-Secondly, depending of the number of followers, the general panel of users is divided in three: users with less than 1350 followers, users with a number of followers between 1350 and 7000 and users with more than 7000 followers.
-Repeating our methodology on each sub-panel, three normalized time series for each time series is created.
+Secondly, depending of the number of followers, the general panel of users is divided in three sub-groups: users with less than 1350 followers, users with a number of followers between 1350 and 7000 and users with more than 7000 followers.
+Repeating the previous methodology on each sub-panel, three normalized time series for each time series are created.
 Again, the motivation here is to detect behaviour gaps between different part of the society that could announce bigger changes in the main signal.
 let $\ts_t^{l,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{l,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences.
-Based on them, we compute two inputs for our hybrid model : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+Based on them, two inputs for our hybrid model are computed  : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
 
@@
 
-We split the dataset into three blocks, train, eval and test sets.
-We use the 3 first years as train set, keep the 4th year for the evaluation set and hide the last year for the test set.
-We trained the hyrid model to compute a one-year ahead prediction, $\lag$ equal to 52, and we set the window size $\window$ equal to 104.
-Using the two first year of the train set, we fit a first per-time-series parametric model for each time series.
-With the resulting collection of local models, we compute a first forecast of the third year for each sequence.
-Using these forecasts, we preprocess  time series and finally compute the RNN inputs.
-In the same way, for the eval set, we fit a second time our per-time-series predictors using the three first years and we forecast the fourth year.
-We preprocess time series and evaluate how the error-corrector RNN is able to improve the first collection of predictions of the fourth year.
-The same process is repeated for the fifth year and compute our final accuracy measures.
-An example of our temporal split is shown in  Figure~\ref{fig:train_eval_test_set}.
+For the needs of the training process, the dataset is temporally splitted into three blocks, train, eval and test sets.
+the 3 first years are used as the train set, the 4th year is kept for the evaluation set and the last year is hid for the test set.
+the hyrid model is trained to compute a one-year ahead prediction, $\lag$ equal to 52, and the window size $\window$ is fixed at 104.
+Using the two first year of the train set, a first per-time-series parametric model for each time series is fitted.
+With the resulting collection of local models, a forecast of the third year is computed for each sequence.
+Using these forecasts, RNN inputs are finally computed.
+for the eval set, per-time-series predictors are fitted a second time using the three first years and a forecasts of the fourth year are computed.
+The eval set is used during the training to control the learning of the RNN model and prevent overfitting.
+the per-time-series predictors are fitted a last time for the test set using the four first years.
+The final accuracy measures of all our models are computes on this test set.
+As an illustraation, an example of our temporal split is shown in Figure~\ref{fig:train_eval_test_set}.
 %We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52.
@@
 
-For the first parametric per-time-series models, we used existing Python or R libraries to estimate the different parameters $\statparam^n$.
+For the first parametric per-time-series models, existing Python or R libraries are used to estimate the different parameters $\statparam^n$.
 %During the M4 competition, parameters of the exponential smoothing of the porposed hybrid model could move during the training.
@@
 %$\{\statparam^n\}_{1\leqslant n \leqslant N}$ are fixed during the training of the recurrent models. 
-We propose two versions of HERMES depending of the choice of local parametric models.
+depending of the choice of local parametric models, two versions of HERMES are proposed.
 The first one uses as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}.
 The second one uses as predictors the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves striking accuracy results on the fashion dataset.
-For the neural network part, we built an architecture summarized in Figure~\ref{fig:rnn_architecture}.
+The neural network part architecture is summarized in Figure~\ref{fig:rnn_architecture}.
 It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension.
-We use a classical Adam optimizer with a learning rate set at 0.001 or 0.005, a batch size equal to 64 and the following loss function:
+A classical Adam optimizer is used with a learning rate set at 0.001 or 0.005, the batch size is fixed 64 and the loss function is defined as follow :
 
@@
 
-Previous parameters are all set with a grid search and our code is developed in Python using the Tensorflow library. It allows the use of a GPU to speed up the trainig process.
+The loss and previous parameters are all set with a grid search (additional materials can be found in Appendix).
+the code is developed in Python using the Tensorflow library.
+It allows the use of a GPU to speed up the trainig process.
 
@@
 
-As benchmarks, we chose several well-known statistical methods and deep learning approaches.
-Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels},  \texttt{tbats} , we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
+As benchmarks, Several well-known statistical methods and deep learning approaches was selected.
+Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels},  \texttt{tbats} , for each time series, a prediction was computed with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
 The forecast of the \textit{snaive} method is only the repetition of the last same past period.
@@
 A complete description and references for these models can be found in \citep{hyndman2020package}.
-As a deep learning approach, we considered a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52.
-
-We propose two versions of HERMES called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
+As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.
+Two versions of HERMES are proposed. They are called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
 %Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}.
@@
 %To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}).  
-Moreover, we evaluate our hybrid framework with the inclusion of our weak signals (ws) referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}.
-In order to provide a fair comparison, we also train a \textit{lstm} with the weak signals named \textit{lstm-ws}.
+Moreover, two versions with the inclusion of the weak signals (ws) are proposed .
+They are referred as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}.
+In order to provide a fair comparison, a \textit{lstm} with the weak signals named \textit{lstm-ws} is trained.
 
 To compare the different methods, we use the Mean Absolute Scaled Error (MASE).
-As our time series have complete different scale, from $10^{-5}$ to $10^{-1}$, we choose this metric to compute a fair error measure, totally independante of the scale of the sequence.
+As our time series have complete different scale, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, totally independante of the scale of the sequence.
 The MASE metric is defined as follow:
@@
 A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes.
-In addition to the MASE accuracy metric, we also compare the different methods on a classification task and especially difference between method using weak signals or not.
-In a given year, we define an increasing trend as a trend that does more than 5\% of growth in terms of Year and Year.
-In the same way, we define a decreasing trend as a trend that declines by 5\% or more.
-We classify other trends as flat trends.
-With this threshold, our dataset is almost balanced on the test set : we have 3087 increasing trends, 3342 decreasing trends and 3571 flat trends.
-On the test set, we compute for each method the accuracy defined as follow :
+In addition to the MASE accuracy metric, the different methods are also compared on a classification task and especially difference between methods using weak signals or not.
+In a given year, an increasing trend is defined as a trend that does more than 5\% of growth in terms of Year and Year.
+In the same way, a decreasing trend is defined as a trend that declines by 5\% or more.
+Other trends are classified as flat trends.
+With this threshold, the proposed fashion dataset is almost balanced on the test set : There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends.
+On the test set, for each method, the accuracy defined as follow is computed:
 
@@
 Results are displayed in the Table~\ref{tab:metricresults}.
-For our model using neural networks, we trained 10 models with different seeds and compute the average and the standard deviation.
-For the statistical models, we can see a large domination of TBATS.
-It is one of the main motivations why we use this model on our best HERMES candidate as the predictor model.
+For our model using neural networks, 10 models are trained  with different seeds.
+The average and the standard deviation of their results are computed and displayed.
+For the statistical models, TBATS largely dominate in term of MASE.
+It is one of the main motivations why this model is used on our best HERMES candidate as the predictor model.
 %However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825.
@@
 Interestingly, weak signals sinificantly improve the accuracy in detecting emerging and declining trends.
-Figure~\ref{fig:examples}, we displayed some examples of \textit{hermes-tbats} model and some weaknessess that can be corrected.
+Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} model and some weaknessess that can be corrected.
 
@@
 \begin{table*}
-  \caption{Results summary on our 10000ts Fashion dataset.
-For each metric, we compute the average on all our time series.
-For our approaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
+  \caption{Results summary on the 10000ts Fashion dataset.
+For each metric, the average on all our time series is computed.
+For approaches using neural network, 10 models are trained with different seeds.
+The mean and the standard deviation of the 10 results are displayed.}
   \centering
@@
 
- The impact of our weak signal is revealed with our classification results.
-Classification results between the \textit{tbats} model and our hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impresive decrease of impactful errors: forecast an increase instead of a decrease and vice versa.
-Our \textit{hermes-tbats} divides  by 3 tis error rate in comparison to \textit{tbats} with only a slightly decrease of the number of correct increase/decrease predictions.
+The impact of the weak signals are revealed with our classification results.
+Classification results between the \textit{tbats} model and the hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impresive decrease of impactful errors: forecast an increase instead of a decrease and vice versa.
+Our \textit{hermes-tbats} divides by 3 the error rate in comparison to \textit{tbats} with only a slightly decrease of the number of correct increase/decrease predictions.
 However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of errors.
 
-When we look at the result of \textit{lstm-ws} and \textit{lstm} displayed in Table~\ref{tab:lstmclass}, we can also note a rise of the number of correct predictions but with an important increase of the number of classification errors.
+%When we look at the result of \textit{lstm-ws} and \textit{lstm} displayed in Table~\ref{tab:lstmclass}, we can also note a rise of the number of correct predictions but with an important increase of the number of classification errors.
 
@@
 
-In addition to our results on our fashion dataset gathering 10000 time series, we also investigate the behaviours of our HERMES model when it is trained on smaller datasets.
-We did 2 experiments, we train our models on a dataset of 1000 time series and on a dataset of 100 time series.
+In addition to the results on the fashion dataset gathering 10000 time series, the behaviour of the HERMES model is analyzed when it is trained on smaller datasets.
+2 experiments was done, HERMES models was trained on a reduced dataset of 1000 time series and on a reduced dataset of 100 time series.
 Results are given in Table~\ref{tab:1000metricresults}.
 
-With these investigations, we can make two important remarks.
-First, our hybrid framework \textit{hermes-tbats} achieves the first position in term of global accuracy on both datasets.
-Due to the strengh of its per-time-series predictor TBATS, our hybrid model succeds at correcting some of its weaknesses and logically reach a striking final accuracy.
+With these investigations, two important remarks can be done.
+First, the hybrid framework \textit{hermes-tbats} achieves the first position in term of global accuracy on both datasets.
+Due to the strengh of its per-time-series predictor TBATS, the hybrid model succeds at correcting some of its weaknesses and logically reach a striking final accuracy.
 Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decrease.
@@
 Learn how to compute a full prediction from scratch is a complex task and high-dimensional recurrent neural networks require  large amount of data.
-Nevertheless, with our hybrid framework, the RNN task is largely simplified.
+Nevertheless, with the HERMES framework, the RNN task is largely simplified.
 Our achitectures logicaly needs less data to be trained and to perform well.
@@
 \begin{table*}
-  \caption{Results summary on our 1000ts Fashion dataset and 100ts Fashion Dataset.For each metric, we compute the average on all our time series.
-For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
+  \caption{Results summary on the 1000ts Fashion dataset and 100ts Fashion Dataset.For each metric, the average on all our time series is computed.
+For the two approaches using neural network, 10 models with different seeds are trained.
+the mean and the standard deviation of the 10 results are displayed.}
   \centering

### 2021-12-15 hermes_paper/hermes_paper.tex
minor changes

@@
 In somes cases, these changes depend on external variables not considered by univariate parametric models.
-The difficulty is that the exact influence of external variables on the main signal are not mainly know.
+The difficulty is that the exact influence of external variables on the main signal is not mainly know.
 It is on this point that  the new HERMES framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals.
@@
 This task requires a thorough data pre-processing for two main reasons.
-First, without a well-design input, the RNN will not capable of understanding the initial collection of forecasts and predict their future errors.
+First, without a well-design input, the RNN will not be capable of understanding the initial collection of forecasts and predict their future errors.
 Second, as no assumption about the scale of our time series was made, inputs require a careful normalization before feeding them to the RNN.
@@
 
-An illustration of our proposed architecture is displayed in Figure~\ref{fig:architecture}.
+An illustration of the proposed architecture is displayed in Figure~\ref{fig:architecture}.
 
@@
 
-Firstly, numerous social media influencers was selectioned by hand and aggregatim them, a specific ``fashion-oriented`` panel was created.
+Firstly, numerous social media influencers was selectioned by hand by fashion experts.
+By aggregating them, a specific ``fashion-oriented`` panel is created.
 With the same methodology than for the main panel descibed in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created.
@@
 
-In addition the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{l}$ and $\ws^{h}$ are added.
+In addition to the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{l}$ and $\ws^{h}$ are added.
 They are frequently sparse for micro trends and they often lack interest in common fashion trends.
-However, in several examples, they are fundamental to detect the future fashion evolution, as illustrated in Section~\ref{sec:exp}.
+However, in several examples, they are fundamental to detect the future fashion evolutions, as illustrated in Section~\ref{sec:exp}.
 \textcolor{red}{as illustrated in Section~\ref{}}.
@@
     \includegraphics[width=1.\linewidth]{figure/ff_example}
-  \caption{A shoes trend of our dataset.
+  \caption{A shoes trend of the fashion dataset.
 In black the main signal and in red its associated \textit{fashion-forward} weak signal.
-The shift between our two signals in the end of 2017/beginning of 2018 announces the future explosion of the fashion trend.}
+The shift between these two signals at the end of 2017/beginning of 2018 announces the future burst of the trend.}
 \label{fig:oneemergingtrend}
@@
 With the resulting collection of local models, a forecast of the third year is computed for each sequence.
-Using these forecasts, RNN inputs are finally computed.
+Corrector inputs are finally computed and the RNN is trained at correcting weaknesses of this first collection of third-year forecasts.
 for the eval set, per-time-series predictors are fitted a second time using the three first years and a forecasts of the fourth year are computed.
@@
 A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes.
-In addition to the MASE accuracy metric, the different methods are also compared on a classification task and especially difference between methods using weak signals or not.
+In addition to the MASE accuracy metric, the different methods are also evaluated on a classification task and especially difference between methods using weak signals or not.
 In a given year, an increasing trend is defined as a trend that does more than 5\% of growth in terms of Year and Year.
@@
 For the statistical models, TBATS largely dominate in term of MASE.
-It is one of the main motivations why this model is used on our best HERMES candidate as the predictor model.
+It is one of the main motivations why this model is used on the best HERMES candidate as the predictor model.
 %However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825.
@@
 Classification results between the \textit{tbats} model and the hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impresive decrease of impactful errors: forecast an increase instead of a decrease and vice versa.
-Our \textit{hermes-tbats} divides by 3 the error rate in comparison to \textit{tbats} with only a slightly decrease of the number of correct increase/decrease predictions.
-However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of errors.
+the \textit{hermes-tbats} model divides by 3 the error rate in comparison to \textit{tbats} with only a slightly decrease of the number of correct increase/decrease predictions.
+However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of impactful errors.
 
@@
 First, the hybrid framework \textit{hermes-tbats} achieves the first position in term of global accuracy on both datasets.
-Due to the strengh of its per-time-series predictor TBATS, the hybrid model succeds at correcting some of its weaknesses and logically reach a striking final accuracy.
-Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decrease.
-On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperform its accuracy level.
+Due to the strengh of its per-time-series predictor TBATS, the hybrid model succeds at correcting some of TBATS weaknesses and logically reach a striking final accuracy.
+Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases.
+On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms its accuracy level.
 Learn how to compute a full prediction from scratch is a complex task and high-dimensional recurrent neural networks require  large amount of data.
@@
 In the same way, an interesting improvment of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses and activate or not by a latent space.
-This latent space can be drive by the historical data or by the weak signals.
+This latent space can be drive by the historical data or even more by the weak signals.
 

### 2021-12-16 hermes_paper/hermes_paper.tex
Update Section 3

@@
 \label{sec:dataset:a}
-A collection of vision neural networks have been designed and trained  at detecting clothes details on pictures: cloth type (pants, shoes, top etc...), form, size,color,texture etc...
-Then, with the knowledge of a team of fashion experts, these clothes details was aggregated in order to define a fashion trend: a meaningfully combination of items that represents an existing trend in the fashion sphere.
-To represent finely the society behaviours based on social media, a group of thousands of random users, called a panel, have been created on several geolocalisations.
-Analysing every day images shared on social networks by these panels with the previous computer vision system, we are finally able to translate the history of thousand of fashion trends in thousands of time series.
+A collection of vision neural networks were designed and trained  at detecting clothes details on pictures: type of clothing (pants, shoes, tops, etc.), form, size, color, texture, etc.
+Then, fashion experts designed fashion trends by aggregating these clothes details: a meaningful combination of items that represent an existing trend in the fashion sphere.
+To represent finely human behaviors based on social media, a group of thousands of random users, called a panel, was created on several geolocalisations.
+Analysing every day images shared on social networks by these panels with our computer vision algorithms, we can translate the history of thousand of fashion trends in thousands of time series.
 All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
@@
 
-Due to the increasing use of social media and users change of behaviour, a throughput normalization is applied to the raw sequences.
+Due to the increasing use of social media and users change of behaviour, a normalization step is applied to the raw sequences.
 Each fashion trend is divided by its hierarchical parent category trend.
-Moreover, in order to not remove the season of all sequences, we deseasonalized the hierarchical parent category trend before dividing.
+Moreover, in order not to remove the seasonality of all sequences, we deseasonalized the hierarchical parent category trend before the normalization.
 For instance, as displayed in Figure~\ref{fig:normalization}, the raw Jersey Top trend for female in China is divided by the deseasonalized global Top trend for female in China.
-the final normalized sequence is expressed in share of category.
+The final normalized sequence is expressed in share of category.
 
@@
 
-\begin{table*}
-  \caption{Fashion time series overview. For each couple geozone/category, we give the number of female and male trends (Female/Male)}
-  \label{sample-table}
+\begin{table}
+
+  \caption{Fashion time series overview. For each couple geozone/category, we give the number of female and male trends (Female/Male).}
+\label{tab:fashiondataset}
   \centering
@@
   }
-\end{table*}
-\label{tab:fashiondataset}
+\end{table}
+
 \subsection{Weak signal}

### 2021-12-16 hermes_paper/hermes_paper.tex
Update Section 3

@@
 It is on this point that  the new HERMES framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals.
-First forecast examples of this new hybrid model are given in Figure~\ref{fig:introexamples}
-
-\medskip
+First forecast examples of this new hybrid model are given in Figure~\ref{fig:introexamples}.
 
@@
   \centering
-  \includegraphics[width=1.\linewidth]{figure/us_female_shoes}
-  \caption{Time series representing a shoes fashion trend for female in The United States}
+  \includegraphics[width=.9\linewidth]{figure/us_female_shoes}
+  \caption{Time series representing a shoes fashion trend for female in The United States.}
   \label{fig:introexamples:sub1}
@@
   \centering
-  \includegraphics[width=1.\linewidth]{figure/br_female_texture_verticalstripe}
-  \caption{Time series representing the vertical stipes texture fashion trend for female in Brazil}
+  \includegraphics[width=.9\linewidth]{figure/br_female_texture_verticalstripe}
+  \caption{Time series representing the vertical stipes texture fashion trend for female in Brazil.}
   \label{fig:introexamples:sub2}
 \end{subfigure}
-\caption{Hermes forecast examples.
-In green the prediction of the TBATS per-time-series predictors.
-In red the final forecast of our HERMES hybrid model.
-\textcolor{red}{Ajouter une legende (courbes et axes) et augmenter la police des ticks en abscisses et ordonnées}}
+\caption{Hermes forecast examples. In green the prediction of the TBATS per-time-series predictors. In red the final forecast of our HERMES hybrid model.}
 \label{fig:introexamples}
@@
 To represent finely human behaviors based on social media, a group of thousands of random users, called a panel, was created on several geolocalisations.
-Analysing every day images shared on social networks by these panels with our computer vision algorithms, we can translate the history of thousand of fashion trends in thousands of time series.
+Analysing every day images shared on social networks by these panels with our computer vision algorithms, we can translate the history of thousands of fashion trends in thousands of time series.
 All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
@@
 
-In addition to this paper, a fashion dataset is proposed.
-It contains an sample of $\numberts$ anonymized and  normalized fashion trends for men and women, on 9 different categories and 5 geozones.
+We therefore introduce a new dataset for fashion time series forecasting.
+It contains a sample of $\numberts$ anonymized and  normalized fashion trends for men and women, on 9 different categories and 5 geozones.
 An overview of it can be found in Table~\ref{tab:fashiondataset}.
 this collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry.
-Some sequences show interesting behaviours with sudden changes.
-They are called them emerging or declining trends depending on the change in direction.
-A central point of this work is to accurately detect and forecast these trends.
+For instance, some sequences show complex behaviours with sudden changes.
+They are called emerging or declining trends depending on the change in direction.
+A central point of this work is to accurately detect and forecast such trends.
 
@@
 
-Firstly, numerous social media influencers was selectioned by hand by fashion experts.
+Firstly, numerous social media influencers were selectioned by hand by fashion experts.
 By aggregating them, a specific ``fashion-oriented`` panel is created.
 With the same methodology than for the main panel descibed in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created.
-we named \textit{fashion-forwards} this first weak signal.
-For instance, an impressive emerging fashion shoes trend with its linked \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
-let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
-As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for our hybrid model: 
-for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+We named \textit{fashion-forwards} this first weak signal.
+For all trend $\{y_t\}_{1\leqslant t\leqslant T}$, let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
+As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for our hybrid model:  for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
 $$
@@
 $$
-values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.
+Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.
+For instance, an impressive emerging fashion shoes trend with its linked \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
 
@@
 Again, the motivation here is to detect behaviour gaps between different part of the society that could announce bigger changes in the main signal.
-let $\ts_t^{l,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{l,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences.
-Based on them, two inputs for our hybrid model are computed  : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
-
+Let $\ts_t^{\ell,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{\ell,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences.
+Two inputs for our hybrid model are computed: for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
 \begin{align*}
-\ws^{l,n}_{t} = \frac{\ts_t^{l,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}
+\ws^{\ell,n}_{t} = \frac{\ts_t^{\ell,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}
 \end{align*}  
@@
 
-In addition to the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{l}$ and $\ws^{h}$ are added.
+In addition to the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{\ell}$ and $\ws^{h}$ are added.
 They are frequently sparse for micro trends and they often lack interest in common fashion trends.
 However, in several examples, they are fundamental to detect the future fashion evolutions, as illustrated in Section~\ref{sec:exp}.
-\textcolor{red}{as illustrated in Section~\ref{}}.
 

### 2021-12-16 hermes_paper/hermes_paper.tex
Update Section 3

@@
 
-For the needs of the training process, the dataset is temporally splitted into three blocks, train, eval and test sets.
-the 3 first years are used as the train set, the 4th year is kept for the evaluation set and the last year is hid for the test set.
-the hyrid model is trained to compute a one-year ahead prediction, $\lag$ equal to 52, and the window size $\window$ is fixed at 104.
-Using the two first year of the train set, a first per-time-series parametric model for each time series is fitted.
+The dataset is temporally split into three blocks, {\em train}, {\em eval} and {\em test} sets.
+The 3 first years are used as the {\em train} set, the 4th year is kept for the {\em eval} set and the {\em test} set is made of the last year.
+The hyrid model is trained to compute a one-year ahead prediction, $\lag$ equal to 52, and the window size $\window$ is fixed at 104.
+Using the two first year of the {\em train} set, a first per-time-series parametric model for each time series is fitted.
 With the resulting collection of local models, a forecast of the third year is computed for each sequence.
 Corrector inputs are finally computed and the RNN is trained at correcting weaknesses of this first collection of third-year forecasts.
-for the eval set, per-time-series predictors are fitted a second time using the three first years and a forecasts of the fourth year are computed.
-The eval set is used during the training to control the learning of the RNN model and prevent overfitting.
-the per-time-series predictors are fitted a last time for the test set using the four first years.
-The final accuracy measures of all our models are computes on this test set.
-As an illustraation, an example of our temporal split is shown in Figure~\ref{fig:train_eval_test_set}.
+For the {\em eval} set, per-time-series predictors are fitted a second time using the three first years and a forecasts of the fourth year are computed.
+The {\em eval} set is used during the training to control the learning of the RNN model and prevent overfitting.
+The per-time-series predictors are fitted a last time for the {\em test} set using the four first years.
+The final accuracy measures of all our models are computed on this {\em test} set.
+As an illustration, an example of our temporal split is shown in Figure~\ref{fig:train_eval_test_set}.
 %We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52.
@@
 %$\{\statparam^n\}_{1\leqslant n \leqslant N}$ are fixed during the training of the recurrent models. 
-depending of the choice of local parametric models, two versions of HERMES are proposed.
+Depending of the choice of local parametric models, two versions of HERMES are proposed.
 The first one uses as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}.
-The second one uses as predictors the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves striking accuracy results on the fashion dataset.
+The second one uses the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves striking accuracy results on the fashion dataset.
 The neural network part architecture is summarized in Figure~\ref{fig:rnn_architecture}.
 It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension.
-A classical Adam optimizer is used with a learning rate set at 0.001 or 0.005, the batch size is fixed 64 and the loss function is defined as follow :
-
+A classical Adam optimizer is used with a learning rate set at 0.001 or 0.005, the batch size is fixed 64 and the loss function is defined as follows:
 $$
@@
 $$
-%
-
+This choice of $\mathrm{L}_1$  loss function is motivated by its robustness to outliers which accounts for some time series in the fashion industry with very specific behaviors.
 The loss and previous parameters are all set with a grid search (additional materials can be found in Appendix).

### 2021-12-16 hermes_paper/hermes_paper.tex
Update Section 4

@@
 
-As benchmarks, Several well-known statistical methods and deep learning approaches was selected.
-Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels},  \texttt{tbats} , for each time series, a prediction was computed with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
+As benchmarks, several widespread statistical methods and deep learning approaches were selected.
+Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels},  \texttt{tbats}, for each time series, predictions are computed with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
 The forecast of the \textit{snaive} method is only the repetition of the last same past period.
-\textit{ets} model is an additive exponential smoothing with a level component and a seasonal component.
-\textit{stlm} approach uses a multiplicative decomposition and models the seasonally adjusted time series with an exponential smoothing model.
-\textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast and \textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization.
-The last one \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters.
+The \textit{ets} model is an additive exponential smoothing with a level component and a seasonal component.
+The \textit{stlm} approach uses a multiplicative decomposition and models the seasonally adjusted time series with an exponential smoothing model.
+The \textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast and \textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization.
+Finally, \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters.
 A complete description and references for these models can be found in \citep{hyndman2020package}.
@@
 %To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}).  
-Moreover, two versions with the inclusion of the weak signals (ws) are proposed .
+Moreover, two versions with the inclusion of the weak signals (ws) are proposed.
 They are referred as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}.
@@
 To compare the different methods, we use the Mean Absolute Scaled Error (MASE).
-As our time series have complete different scale, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, totally independante of the scale of the sequence.
-The MASE metric is defined as follow:
-
+As our time series have complete different scale, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, independent of the scale of the sequence.
+The MASE metric is defined as follows:
 \begin{align*}
@@
 \end{align*}
-
 %To compare the different methods, we use the same metrics as in the M4 competition: the Mean Absolute Scaled Error (MASE), the Symmetric Mean Absolute Percentage Error (sMAPE) and the final M4 competition metric, the Overall Weighted Average (OWA) of the sMAPE and the MASE defined as follows:
@@
 %where $\hat{Y}$ is a model prediction, $\lag$ is the horizon, $m$ the seasonality and $MASE_{snaive}$ is the $MASE$ computed with the $snaive$ model prediction, idem for the $sMAPE_{snaive}$.
-
 Detecting emerging and declining trends is a crucial issue for the fashion industry.
@@
 In addition to the MASE accuracy metric, the different methods are also evaluated on a classification task and especially difference between methods using weak signals or not.
-In a given year, an increasing trend is defined as a trend that does more than 5\% of growth in terms of Year and Year.
+In a given year, an increasing trend is defined as a trend that does more than 5\% of growth with respect to the previous year.
 In the same way, a decreasing trend is defined as a trend that declines by 5\% or more.
 Other trends are classified as flat trends.
-With this threshold, the proposed fashion dataset is almost balanced on the test set : There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends.
-On the test set, for each method, the accuracy defined as follow is computed:
-
+With this threshold, the proposed fashion dataset is almost balanced on the {\em test} set: There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends.
+On the {\em test} set, for each method, the accuracy is defined as follows:
 \begin{align*}
-\mathrm{ACCURACY} &= \frac{TP_{dec} + TP_{flat} + TP_{inc}}{TP_{dec} + TP_{flat} + TP_{inc} + FP_{dec} + FP_{flat} + FP_{inc}}
+\mathrm{ACCURACY} &= \frac{TP_{dec} + TP_{flat} + TP_{inc}}{TP_{dec} + TP_{flat} + TP_{inc} + FP_{dec} + FP_{flat} + FP_{inc}}\,,
 \end{align*}
-
 where $TP_i$ is the number of time series correctly classified in the class $i$ and $FP_i$ is the number of time series miss classified in the class $i$.

### 2021-12-16 hermes_paper/hermes_paper.tex
Update Section 4

@@
 The average and the standard deviation of their results are computed and displayed.
-For the statistical models, TBATS largely dominate in term of MASE.
+For the statistical models, TBATS largely dominates the alternatives  in terms of MASE.
 It is one of the main motivations why this model is used on the best HERMES candidate as the predictor model.
@@
 Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slighlty outperform the alternatives in terms of MASE and are stable across the different trainings.
-Regarding \textit{hermes-ets},  its accuracy remains low in comparison to the \textit{lstm} benchmarck or HERMES using TBATS.
+Regarding \textit{hermes-ets},   although it is very similar to the baseline \cite{smyl2020hybrid}, its accuracy remains low in comparison to the \textit{lstm} benchmarck or HERMES using TBATS.
 

### 2021-12-17 hermes_paper/hermes_paper.tex
add m4 dataset results

@@
 %\textcolor{red}{If possible, a few results of the hybrid approach without weak signals on a dataset other than Heuritech.}
+
+\subsection{Result for M4 weekly dataset}
+
+\begin{table*}
+  \caption{Results summary on the m4 weekly dataset.
+For each metric, the average on all our time series is computed.
+For approaches using neural network, 10 models are trained with different seeds.
+The mean and the standard deviation of the 10 results are displayed.}
+  \centering
+  \resizebox{0.85\textwidth}{!}{%
+  \begin{tabular}{l||lllll|lllll|lllll}
+   &&\multicolumn{3}{c}{\textbf{SMAPE}} &&& \multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{OWA}}&\\
+    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}&&&  \textit{mean}  && \textit{std}& \\
+%    \hline
+	 \hline
+	 &&&&&&&&&&\\
+     \textit{MLP} && 21.349 && - &&& 13.568 && - &&& 3.608 && - &\\
+     \textit{RNN} && 15.220 && - &&& 5.132 && - &&& 1.755 && - &\\
+     \textit{snaive} && 9.161 && - &&& 2.777 && - &&& 1.000 && - &\\
+     \textit{SES} && 9.012 && - &&& 2.685 && - &&& 0.975 && - &\\
+     \textit{Theta} && 9.093 && - &&& 2.637 && - &&& 0.971 && - &\\
+     \textit{Holt} && 9.708 && - &&& 2.420 && - &&& 0.966 && - &\\
+     \textit{Com} && 8.944 && - &&& 2.432 && - &&& 0.926 && - &\\
+     \textit{Damped} && 8.866 && - &&& 2.404 && - &&& 0.917 && - &\\
+     \textit{Uber} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
+     \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.841 && - &\\
+     \textit{\textbf{hermer-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
+    %\hline
+  \end{tabular}
+  }
+\label{tab:metricresults}
+\end{table*}
 

### 2021-12-17 hermes_paper/hermes_paper.tex
add m4 dataset part

@@
 %\textcolor{red}{If possible, a few results of the hybrid approach without weak signals on a dataset other than Heuritech.}
-
-\subsection{Result for M4 weekly dataset}
-
-\begin{table*}
-  \caption{Results summary on the m4 weekly dataset.
-For each metric, the average on all our time series is computed.
-For approaches using neural network, 10 models are trained with different seeds.
-The mean and the standard deviation of the 10 results are displayed.}
-  \centering
-  \resizebox{0.85\textwidth}{!}{%
-  \begin{tabular}{l||lllll|lllll|lllll}
-   &&\multicolumn{3}{c}{\textbf{SMAPE}} &&& \multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{OWA}}&\\
-    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}&&&  \textit{mean}  && \textit{std}& \\
-%    \hline
-	 \hline
-	 &&&&&&&&&&\\
-     \textit{MLP} && 21.349 && - &&& 13.568 && - &&& 3.608 && - &\\
-     \textit{RNN} && 15.220 && - &&& 5.132 && - &&& 1.755 && - &\\
-     \textit{snaive} && 9.161 && - &&& 2.777 && - &&& 1.000 && - &\\
-     \textit{SES} && 9.012 && - &&& 2.685 && - &&& 0.975 && - &\\
-     \textit{Theta} && 9.093 && - &&& 2.637 && - &&& 0.971 && - &\\
-     \textit{Holt} && 9.708 && - &&& 2.420 && - &&& 0.966 && - &\\
-     \textit{Com} && 8.944 && - &&& 2.432 && - &&& 0.926 && - &\\
-     \textit{Damped} && 8.866 && - &&& 2.404 && - &&& 0.917 && - &\\
-     \textit{Uber} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
-     \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.841 && - &\\
-     \textit{\textbf{hermer-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
-    %\hline
-  \end{tabular}
-  }
-\label{tab:metricresults}
-\end{table*}
 
@@
 
+\subsection{Result for M4 weekly dataset}
+
+In addition to the previous results, a HERMES application is also done on the M4 weekly dataset.
+The M4 dataset gathers 359 weekly time series and shows 3 main differences compare to the fashion dataset.
+Firstly, sequences have not the same lenght with sequence lenghts lying between 93 and 2610 time steps.
+Secondly, as some of the sequences represent financial signals or some others are demographic sequences, the  359 time series show huge contrasting behaviours.
+Thirldy, compare to the fashion application, the horizon for the M4 competition is set to 13 for the weekly dataset.
+
+\textbf{Training}
+
+The sequence are firstly resized in order to egalize their lenghts.
+For the shorter ones: the eval and the test set is removed (the last 26 steps).
+Then the remaining number of entire year is duplicated in order to egalize all the sequence at the longest one : 2610 time steps.
+As per time series parametric model training time depends on the sequence lenght, all time series are then croped.
+At the end, with the addition of the previously removed eval and test set, 300 time steps are kept for each sequence as dataset used to train the HERMES approach.
+
+For this training, The horizon $h$ is set to 13 due to the M4 weekly test set size and the window size $w$ is fixed at 104.
+For the RNN part, the same architecture than describe in Figure~ \ref{fig:rnn_architecture} is used.
+The Adam optimizer is used with a learning rate fixed at 0.005 and a batch size set at 8.
+As the loss function, the same loss than the fashion application is used.
+As the M4 weekly dataset is small, a rolling window is used on the train set in order to increase the train number of example and improve the training.
+5 windows are computed for each sequence for the RNN train set.
+An overview of our train, eval, test set spit and the rolling window is givien in Figure~\ref{}.
+The previous parameters: window size, learning rate, batch size and the number of train window per time series are set using a grid search.
+
+\textbf{Benchmarks}
+
+The M4 competion provides a rich collection of benchmarks gatering statistical models and neural network approaches.
+The same candidates are used in this part as baseline.
+In addition, the hybrid model named \textit{Uber} of S.Smyl is added to provide a interesting comparison against the HERMES approach.
+For a complete description and references of the benchmarck models, see \cite{makridakis2020m4}.
+As a HERMES candidate, a version using TBATS is proposed and called \textit{hermes-tbats}.
+Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measure.
+A complete definition of these metrics is also proposed in \cite{makridakis2020m4}.
+
+\textbf{Results and discussion}
+
+The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}.
+Considering the HERMES approach, \textit{hermes-tbats} outperforms all the benchmarcks.
+This results is partially induce by the use of TBATS per-time-series predictors which achieves striking result also on the test set.
+Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}.
+With the second application, two importants conclusion can be done.
+Firstly, the striking results of \textit{hermes-tbats} confirm that the HERMES framework is a general framework, well suited for a large collection of forecasting tasks.
+Secondly, the accuracy gap between the 2 hybrid candidate validate the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.
+
+\begin{table*}
+  \caption{Results summary on the m4 weekly dataset.
+For each metric, the average on all our time series is computed.
+For approaches using neural network, 10 models are trained with different seeds.
+The mean and the standard deviation of the 10 results are displayed.}
+  \centering
+  \resizebox{0.85\textwidth}{!}{%
+  \begin{tabular}{l||lllll|lllll|lllll}
+   &&\multicolumn{3}{c}{\textbf{SMAPE}} &&& \multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{OWA}}&\\
+    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}&&&  \textit{mean}  && \textit{std}& \\
+%    \hline
+	 \hline
+	 &&&&&&&&&&\\
+     \textit{MLP} && 21.349 && - &&& 13.568 && - &&& 3.608 && - &\\
+     \textit{RNN} && 15.220 && - &&& 5.132 && - &&& 1.755 && - &\\
+     \textit{snaive} && 9.161 && - &&& 2.777 && - &&& 1.000 && - &\\
+     \textit{SES} && 9.012 && - &&& 2.685 && - &&& 0.975 && - &\\
+     \textit{Theta} && 9.093 && - &&& 2.637 && - &&& 0.971 && - &\\
+     \textit{Holt} && 9.708 && - &&& 2.420 && - &&& 0.966 && - &\\
+     \textit{Com} && 8.944 && - &&& 2.432 && - &&& 0.926 && - &\\
+     \textit{Damped} && 8.866 && - &&& 2.404 && - &&& 0.917 && - &\\
+     \textit{Uber} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
+     \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.8 && - &\\
+     \textit{\textbf{hermer-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
+    %\hline
+  \end{tabular}
+  }
+\label{tab:m4metricresults}
+\end{table*}
+
 \section{Conclusion}

### 2021-12-17 hermes_paper/hermes_paper.tex
small correction

@@
 Considering the HERMES approach, \textit{hermes-tbats} outperforms all the benchmarcks.
-This results is partially induce by the use of TBATS per-time-series predictors which achieves striking result also on the test set.
+This results is partially induced by the use of TBATS per-time-series predictors which achieves striking results on the test set.
 Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}.
-With the second application, two importants conclusion can be done.
+With this second application, two importants conclusion can be done.
 Firstly, the striking results of \textit{hermes-tbats} confirm that the HERMES framework is a general framework, well suited for a large collection of forecasting tasks.
-Secondly, the accuracy gap between the 2 hybrid candidate validate the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.
+Secondly, the accuracy gap between the 2 hybrid candidates validate the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.
 

### 2021-12-21 hermes_paper/hermes_paper.tex
add Appendix part

@@
 
+\textcolor{blue}{reformuler}
 The sequence are firstly resized in order to egalize their lenghts.
@@
 As per time series parametric model training time depends on the sequence lenght, all time series are then croped.
-At the end, with the addition of the previously removed eval and test set, 300 time steps are kept for each sequence as dataset used to train the HERMES approach.
+At the end, with the addition of the previously removed eval and test set, 300 time steps are kept for each sequence.
 
@@
 5 windows are computed for each sequence for the RNN train set.
-An overview of our train, eval, test set spit and the rolling window is givien in Figure~\ref{}.
+An overview of our train, eval, test set split and the resizing of the shorter sequences is given in Figure~\ref{}.
 The previous parameters: window size, learning rate, batch size and the number of train window per time series are set using a grid search.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=1.\linewidth]{figure/M4_dataset}
+  \caption{One of the shortest sequences of the M4 weekly dataset (93 time steps).
+In order to fit its predictor, the last complete year is duplicated in order to reach a total lenght of 300 time steps.}
+\label{fig:m4dataset}
+\end{figure}
 
@@
 The same candidates are used in this part as baseline.
-In addition, the hybrid model named \textit{Uber} of S.Smyl is added to provide a interesting comparison against the HERMES approach.
+In addition, the hybrid model named \textit{Uber} of S.Smyl is added to provide an interesting comparison against the HERMES approach.
 For a complete description and references of the benchmarck models, see \cite{makridakis2020m4}.
@@
 Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}.
-With this second application, two importants conclusion can be done.
+With this second application, two important conclusions can be done.
 Firstly, the striking results of \textit{hermes-tbats} confirm that the HERMES framework is a general framework, well suited for a large collection of forecasting tasks.
@@
 
-%\section{Fashion Dataset overview}
+\section{M4 weekly dataset and results}
+
+\section{Training parameters and loss}
+
+\subsection{Loss grid search on the Fashion Dataset}
+
+Using deep learning models in time series forecasting is a appealing way to achieve higher levels of accuracy.
+However, it induces two main issues.
+First, have a large enough dataset to train the model as illustrated in Section~\ref{sec:exp}.
+Second, find a correct loss to train the model.
+For the second point, the main difficulty is that a dataset can gather contrasting time series in terms of scale.
+These differences can impact the loss behaviour and finally the training.
+For the HERMES architecture, some loss candidates were defined for the training : the Mean Absolute Error (MAE), the Mean Square Error (MSE),  the Scaled Mean Absolute Error (SMAE) and the Scaled Mean Square Error (SMSE).
+The loss functions are defined as follows :
+
+$$
+MAE = \frac{1}{\lag}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,,\quad  MSE = \frac{1}{\lag}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|
+$$
+$$
+SMAE = \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,,\quad  SMSE = \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|
+$$
+
+For each loss, 10 \textit{hermese-tbats-ws} models have been trained with different seeds and the final mean and standard deviation are given in Figure~\ref{}.
+The final Scaled Mean Absolute Error reach the lower MASE and was selected to train all the HERMES model in this paper.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=1.\linewidth]{figure/loss_function}
+  \caption{MASE accuray for the \textit{hermes-tbats-ws} model depending of the loss used during the RNN training.
+For each loss, 10 models with different seed have been trained.
+The mean and the standard deviation are represented with a point and a vertical line.}
+\label{fig:loss_function}
+\end{figure}
+
+\subsection{Parameters grid search on the M4 weekly Dataset}
+
+The HERMES framework get several parameters to set correctly in order to reach acceptable level of accuracy.
+For instance, a overview of the learning rate, batch size and number of window per time series grid search for the M4 weekly dataset is shown in this part.
+For each parameters, a collection of 10 \textit{hermes-tbats} models have been trained with a range of values and the final OWA was calculated.
+As in the Figure~\ref{fig:loss_function}, the mean and the standard deviation of each groups of 10 trainings is displayed in Figure~\ref{}.
+For the final \textit{hermes-tbats} model of the M4 weekly dataset, the grid search fixed the following setup : 3 windows per time series, the batch size set to 8 and the optimizer's learning rate equal to 0.005.
+
+\begin{figure}
+\centering
+\begin{subfigure}{1.\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/m4_nb_of_window}
+  \caption{result of the HERMES model on the M4 dataset model depending of the number of windows provided per time series to the RNN corrector}
+  \label{fig:m4parameter:sub1}
+\end{subfigure}
+\begin{subfigure}{1.\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/m4_batch_size}
+  \caption{result of the HERMES model on the M4 dataset model depending of the size of the batch size}
+  \label{fig:m4parameter:sub2}
+\end{subfigure}
+\begin{subfigure}{1.\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/m4_learning_rate}
+  \caption{result of the HERMES model on the M4 dataset model depending of learning rate of the optimizer}
+  \label{fig:m4parameter:sub3}
+\end{subfigure}
+\caption{Example of difference between the raw sequence and the normalized one. In this example, we normalize by the deseasonalized global top fashion trend for female in China.}
+\label{fig:m4parameter}
+\end{figure}
 

### 2021-12-21 hermes_paper/hermes_ieee.tex
Added IEEE version

--- 2021-12-21 hermes_paper/hermes_paper.tex
@@
-\documentclass{article} % For LaTeX2e
-\usepackage{iclr2022_conference,times}
-
-% Optional math commands from https://github.com/goodfeli/dlbook_notation.
+%% bare_jrnl.tex
+%% V1.4b
+%% 2015/08/26
+%% by Michael Shell
+%% see http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
+%% journal paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/pkg/ieeetran
+%% and
+%% http://www.ieee.org/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE!
+%% User assumes all risk.
+%% In no event shall the IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%*************************************************************************
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. The IEEE's font choices and paper sizes can   ***
+% *** trigger bugs that do not appear when using other class files.       ***                          ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+\documentclass[lettersize,journal]{IEEEtran}
+%
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[journal]{../sty/IEEEtran}
+
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/pkg/ifpdf
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
+%
+\usepackage{cite}
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of the IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off
+% such as if a citation ever needs to be enclosed in parenthesis.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 5.0 (2009-03-20) and later if using hyperref.sty.
+% The latest version can be obtained at:
+% http://www.ctan.org/pkg/cite
+% The documentation is contained in the cite.sty file itself.
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\usepackage[pdftex]{graphicx}
+\ifCLASSINFOpdf
+  % \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  % \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation
+% can be obtained at:
+% http://www.ctan.org/pkg/graphicx
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found at:
+% http://www.ctan.org/pkg/epslatex
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
+\usepackage{amsmath,amssymb}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics.
+%
+% Note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/amsmath
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/pkg/algorithms
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/pkg/algorithmicx
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/array
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+% *** SUBFIGURE PACKAGES ***
+\ifCLASSOPTIONcompsoc
+ \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+\else
+ \usepackage[caption=false,font=footnotesize]{subfig}
+\fi
+% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
+% for subfigure.sty, the latter of which is no longer maintained and is
+% incompatible with some LaTeX packages including fixltx2e. However,
+% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
+% which will override IEEEtran.cls' handling of captions and this will result
+% in non-IEEE style figure/table captions. To prevent this problem, be sure
+% and invoke subfig.sty's "caption=false" package option (available since
+% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
+% handling of captions.
+% Note that the Computer Society format requires a larger sans serif font
+% than the serif footnote size font used in traditional IEEE formatting
+% and thus the need to invoke different subfig.sty package options depending
+% on whether compsoc mode has been enabled.
+%
+% The latest version and documentation of subfig.sty can be obtained at:
+% http://www.ctan.org/pkg/subfig
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure.
+% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
+% corrections already built into the system in which case a warning will
+% be issued if an attempt is made to load fixltx2e.sty as it is no longer
+% needed.
+% The latest version and documentation can be found at:
+% http://www.ctan.org/pkg/fixltx2e
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/stfloats
+% Do not use the stfloats baselinefloat ability as the IEEE does not allow
+% \baselineskip to stretch. Authors submitting work to the IEEE should note
+% that the IEEE rarely uses double column equations and that authors should try
+% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
+% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
+% such ways.
+% Do not attempt to use stfloats with fixltx2e as they are incompatible.
+% Instead, use Morten Hogholm'a dblfloatfix which combines the features
+% of both fixltx2e and stfloats:
+%
+% \usepackage{dblfloatfix}
+% The latest version can be found at:
+% http://www.ctan.org/pkg/dblfloatfix
+
+%\ifCLASSOPTIONcaptionsoff
+%  \usepackage[nomarkers]{endfloat}
+% \let\MYoriglatexcaption\caption
+% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
+%\fi
+% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and
+% Axel Sommerfeldt. This package may be useful when used in conjunction with
+% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
+% submissions have lists of figures/tables at the end of the paper and that
+% figures/tables without any captions are placed on a page by themselves at
+% the end of the document. If needed, the draftcls IEEEtran class option or
+% \CLASSINPUTbaselinestretch interface can be used to increase the line
+% spacing as well. Be sure and use the nomarkers option of endfloat to
+% prevent endfloat from "marking" where the figures would have been placed
+% in the text. The two hack lines of code above are a slight modification of
+% that suggested by in the endfloat docs (section 8.4.1) to ensure that
+% the full captions always appear in the list of figures/tables - even if
+% the user used the short optional argument of \caption[]{}.
+% IEEE papers do not typically make use of \caption[]'s optional argument,
+% so this should not be an issue. A similar trick can be used to disable
+% captions of packages such as subfig.sty that lack options to turn off
+% the subcaptions:
+% For subfig.sty:
+% \let\MYorigsubfloat\subfloat
+% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
+% However, the above trick will not work if both optional arguments of
+% the \subfloat command are used. Furthermore, there needs to be a
+% description of each subfigure *somewhere* and endfloat does not add
+% subfigure captions to its list of figures. Thus, the best approach is to
+% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
+% and instead reference/explain all the subfigures within the main caption.
+% The latest version of endfloat.sty and its documentation can obtained at:
+% http://www.ctan.org/pkg/endfloat
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
+% later in the document, say, to conditionally put the References on a
+% page by themselves.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/url
+% Basically, \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+\usepackage{booktabs}
+\usepackage{url,xcolor}
+
 \input{math_commands.tex}
-
-\usepackage{hyperref}
-\usepackage{url}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\iclrfinalcopy
-%\setlength{\tabcolsep}{10pt}
-%\renewcommand{\arraystretch}{1.5}
-
-\title{HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series}
-
-\author{Etienne DAVID \\
-Heuritech \\
-Paris \\
-\texttt{etienne.david@heuritech.com} \\
-\And
-Sylvain Le Corff \\
-Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC \\
-Institut Polytechnique de Paris, Palaiseau \\
-\texttt{sylvain.le$\_$corff@telecom-sudparis.eu} \\
-\And 
-Jean Bellot \\
-Heuritech \\
-Paris \\
-\texttt{jean.bellot@heuritech.com} \\
-}
-
-% The \author macro works with any number of authors. There are two commands
-% used to separate the names and addresses of multiple authors: \And and \AND.
-%
-% Using \And between authors leaves it to \LaTeX{} to determine where to break
-% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
-% puts 3 of 4 authors names on the first line, and the last on the second
-% line, try using \AND instead of \And before the third author name.
-
 \newcommand{\fix}{\marginpar{FIX}}
@@
 
-%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
 \begin{document}
-
+%
+% paper title
+% Titles are generally capitalized except for words such as a, an, and, as,
+% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+% not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired.
+% Do not put math or special symbols in the title.
+\title{HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series}
+%
+%
+% author names and IEEE memberships
+% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+% a structure at a ~ so this keeps an author's name from being broken across
+% two lines.
+% use \thanks{} to gain access to the first footnote area
+% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+% was not built to handle multiple paragraphs
+%
+
+\author{Etienne David\thanks{Etienne David: Heuritech, France.}, Sylvain Le Corff\thanks{Sylvain Le Corff:  Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC, Institut Polytechnique de Paris, France.} and~ Jean Bellot\thanks{Jean Bellot: Heuritech, France.}}
+%        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
+%\thanks{M. Shell was with the Department
+%of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
+%GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
+%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
+%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
+
+% note the % following the last \IEEEmembership and also \thanks -
+% these prevent an unwanted space from occurring between the last author name
+% and the end of the author line. i.e., if you had this:
+%
+% \author{....lastname \thanks{...} \thanks{...} }
+%                     ^------------^------------^----Do not want these spaces!
+%
+% a space would be appended to the last name and could cause every name on that
+% line to be shifted left slightly. This is one of those "LaTeX things". For
+% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+% "AB" then you have to do: "\textbf{A}\textbf{B}"
+% \thanks is no different in this regard, so shield the last } of each \thanks
+% that ends a line with a % and do not let a space in before the next \thanks.
+% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+% you are supposed to have spaces between the names. For what it is worth,
+% this is a minor point as most people would not even notice if the said evil
+% space somehow managed to creep in.
+
+% The paper headers
+%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
+%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
+
+% The only time the second header will appear is for the odd numbered pages
+% after the title page when using the twoside option.
+%
+% *** Note that you probably will NOT want to include the author's ***
+% *** name in the headers of peer review papers.                   ***
+% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+% you desire.
+
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark.
+
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
+
+% make the title area
 \maketitle
 
+% As a general rule, do not put math, special symbols or citations
+% in the abstract or keywords.
 \begin{abstract}
@@
 
+% Note that keywords are not normally used for peerreview papers.
+\begin{IEEEkeywords}
+Hybrid models, Recurrent neural networks, Time series.
+\end{IEEEkeywords}
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
+
 \section{Introduction}
-
-Multivariate time series forecasting is a widespread statistical problem with  many applications, see for instance \citep{sarkka2013bayesian, douc2014nonlinear, zucchini2017hidden} and the numerous references therein.
+\label{sec:introduction}
+
+Multivariate time series forecasting is a widespread statistical problem with  many applications, see for instance \cite{sarkka2013bayesian, douc2014nonlinear, zucchini2017hidden} and the numerous references therein.
  %Due to the diversity of applications and use cases, a multitude of models have been proposed. 
@@
 Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
-The exponential smoothing model \citep{RePEc:inm:oropre:v:9:y:1961:i:5:p:673-685}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \cite{doi:10.1198/jasa.2011.tm09771}, or the ARIMA with the Box-Jenkins approach \citep{box2015time} are for instance very popular parametric linear generative models.
+The exponential smoothing model \cite{RePEc:inm:oropre:v:9:y:1961:i:5:p:673-685}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \cite{doi:10.1198/jasa.2011.tm09771}, or the ARIMA with the Box-Jenkins approach \cite{box2015time} are for instance very popular parametric linear generative models.
 Hidden Markov models (HMM) are also widespread and presuppose that available observations are defined using missing data describing the dynamical system.
@@
  In various applications where signals exhibit non-stationarities such as trends and seasonality, classical HMM are not adapted.
-However, \citep{touron2017modeling}  recently proposed seasonal HMM, assuming that transition probabilities between the states, as well as the emission distributions, are not constant in time but evolve in a periodic manner.
-Strong consistency results were established in \citep{touron2019consistency} and Expectation Maximization based numerical experiments were proposed.
+However, \cite{touron2017modeling}  recently proposed seasonal HMM, assuming that transition probabilities between the states, as well as the emission distributions, are not constant in time but evolve in a periodic manner.
+Strong consistency results were established in \cite{touron2019consistency} and Expectation Maximization based numerical experiments were proposed.
 Altough these works provide promising results, HMM are computationally expensive to train and are not yet well studied for seasonal  sequences with thousands of components.
 
- %However, for a large part of applications, parametric generative approaches show limitation to capture  complexity. Accurate candidates can be found with latent data models.
-
-%During the past decades, forecasting applications have taken a totally new proportion. 
 In many fields, single or few time series have become thousands of sequences with complex statistical structures.
 In this new context, classical time series specific statistical models show limitations when dealing with numerous heterogeneous data.
-Recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \citep{ hochreiter1997long,vaswani2017attention, 8614252, li2019enhancing, lim2019temporal,salinas2020deepar}.
-%In the past decades, with the impressive results of deep neural networks (DNN) in vision or language, some time series forecasting applications have been proposed.
-%Significant improvements have been achieved with Reccurent Neural Network and its Long Short-Term Memory (LSTM) or Gated Recurrent Unit (GRU)  declinations \citep{}. 
-The DeepAR model proposed in \citep{salinas2020deepar} provides a global model from many time series based on
-a multi-layer recurrent neural network with LSTM cells.
-More recently, applications using the Transformer model have been proposed  \citep{li2019enhancing}.
-A direct concurrent of the DeepAR model can be found with the Temporal Fusion Transformers (TFT) approach \citep{lim2019temporal}.
+Recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \cite{ hochreiter1997long,vaswani2017attention, 8614252, li2019enhancing, lim2019temporal,salinas2020deepar}.
+The DeepAR model proposed in \cite{salinas2020deepar} provides a global model from many time series based on a multi-layer recurrent neural network with LSTM cells.
+More recently, applications using the Transformer model have been proposed  \cite{li2019enhancing}.
+A direct concurrent of the DeepAR model can be found with the Temporal Fusion Transformers (TFT) approach \cite{lim2019temporal}.
 Unfortunately, all these solutions suffer from two main weaknesses.
@@
 Recurrent neural networks are appealing to tackle our forecasting problem due to their capability of leveraging external data.
-Recently, hybrid models combining deep neural network (DNN) architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \citep{zhang2003time,jianwei2019novel,bandara2020lstm}.
-The approach providing the most striking results was proposed in  \citep{smyl2020hybrid} in the context of the M4 forecasting competition \citep{makridakis2020m4}.
+Recently, hybrid models combining deep neural network (DNN) architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \cite{zhang2003time,jianwei2019novel,bandara2020lstm}.
+The approach providing the most striking results was proposed in  \cite{smyl2020hybrid} in the context of the M4 forecasting competition \cite{makridakis2020m4}.
 Given a large dataset, a per-time-series multiplicative exponential smoothing model is introduced to estimate simple but fundamental components for each time series and compute a first prediction.
 Then a global recurrent neural network is trained on the entire dataset to correct errors of the previous exponential smoothing models.
-%With this process, the hybrid approach succeeds at mixing strengths of both model families: robustness of the time series specific parametric models and the power of neural network at learn complex dynamics on large dataset.
-%However, the hybrid model has not been designed to deal with external signals even if it include a neural network.
-
-%Following this work, we present in this paper a new hyrbid recurrent model for time series forecasting with inclusion of external weak signals.
-%We design a more general hybrid framework including the original multiplicative model and a new additive one.
-%Our approach enriches existing hybrid models by incorporating an unobserved regime switching feature to account for the need of a neural network based correction.
-In order to leverage external signals, we modify the hybrid framework to allow the regime shift and the  global error-corrector neural network to deal with external data.
 
@@
 By adding external weak signals in the proposed framework, the real potential of the hybrid approach is revealed: a global neural network, able to leverage large amount of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of any parametric models.
-%Our new hybrid framework is divided in two parts.
-As a first step, we compute a per-time-series forecast for each trend using any kind of parametric models.
-Then, gathering information of the first prediction and external variables, a global error corrector neural network is trained to correct weaknesses of the first forecast.
-
-%Section~\ref{sec:hybrid} describes our hybrid framework which consists of a per-time-series parametric model and a recurrent neural network combining the target sequences with external weak signals
 
@@
 \label{sec:hybrid}
-%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global RNN.
-We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
-%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of two RNN.
-We use a per time series statistical model to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
-Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
 We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, the predictors, and a global error-corrector neural network train on all time series, the corrector.
@@
 
-%It is assumed that for all $1\leqslant n \leqslant N$, $\fullts^n$ is a seasonal time series with a season equal to $m \in \mathbb{N}$, $m$ equals 4 for quarterly, 12 for monthly or 52 for weekly time series.
-However, no restriction in term of scale and noise distributions are assumed in the generative law of each time series.
-
 \subsection{Per-time-series predictors}
-%The first step in our additive hybrid model is to consider, for each time series, an exponential smoothing  statistical model.
-%The time-series-specific models compute, for each sequence, two components,  level  and  seasonality.
-For all $1\leqslant n \leqslant N$ and $0\leqslant t \leqslant T$, let $\lvl_t^n$ be the value of the $n$-th level component at time $t$ and  $\fulllvl^n = \{\lvl_t^n\}_{0\leqslant t \leqslant T}$ be all the values of this level component.
-For all $1\leqslant n \leqslant N$ and $-m+1\leqslant t \leqslant T$, let $\seas_t^n$ be the value of the $n$-th seasonality component at time $t$ and  $\fullseas^n = \{\seas_t^n\}_{-m+1\leqslant t \leqslant T}$ be all the values of this season component.
-$m \in \mathbb{N}$ is the seasonality (4 for quarterly, 12 for monthly or 52 for weekly time series).
 The time-series-specific predictors compute, for each sequence, a first $\lag$-ahead prediction based on the past.
@@
 The first one use an  exponential smoothing as reference similar to the baseline \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
-%The main complexity is in the next stage: training a global RNN corrector to improve the per-time-series statistical models when the parametric models start showing weaknesses.
 
@@
 \centering
-\begin{subfigure}{1.\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{figure/us_female_shoes}
-  \caption{Time series representing a shoes fashion trend for female in The United States.}
-  \label{fig:introexamples:sub1}
-\end{subfigure}
-\begin{subfigure}{1.\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{figure/br_female_texture_verticalstripe}
-  \caption{Time series representing the vertical stipes texture fashion trend for female in Brazil.}
-  \label{fig:introexamples:sub2}
-\end{subfigure}
-\caption{Hermes forecast examples. In green the prediction of the TBATS per-time-series predictors. In red the final forecast of our HERMES hybrid model.}
+%\begin{subfigure}{1.\textwidth}
+ % \centering
+  \includegraphics[width=\linewidth]{figure/us_female_shoes}
+  %\caption{Time series representing a shoes fashion trend for female in The United States.}
+ % \label{fig:introexamples:sub1}
+%\end{subfigure}
+%\begin{subfigure}{1.\textwidth}
+  %\centering
+  \includegraphics[width=\linewidth]{figure/br_female_texture_verticalstripe}
+ % \caption{Time series representing the vertical stipes texture fashion trend for female in Brazil.}
+  %\label{fig:introexamples:sub2}
+%\end{subfigure}
+\caption{Hermes forecast examples.
+In green the prediction of the TBATS per-time-series predictors.
+In red the final forecast of our HERMES hybrid model.
+(Top) Time series representing a shoes fashion trend for female in The United States.
+(Bottom) Time series representing the vertical stipes texture fashion trend for female in Brazil.}
 \label{fig:introexamples}
 \end{figure}
-
-% Indeed, depending on time series, some family of parametric models can achieve really heterogeneous level of accuracy. 
-%For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n, \lvl^n_0, \{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters, $\lvl^n_0$ the first level term and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms.
-Given the sequence $\fullts^n$ and the parameters $\Theta^n$ , the two components  $\fulllvl^n$ and $\fullseas^n$ are computed as follow :
-%We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ \textcolor{red}{issue with the time index ?} and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
-%\begin{align*}
-    %\lvl^n_{t} &= \lsmooth^n (\ts^n_t - \seas^n_{t-m}) + (1- \lsmooth^n)\lvl^n_{t-1}\,, \\
-    %\seas^n_t &= \ssmooth^n (\ts^n_t - \lvl^n_{t-1}) + (1 - \ssmooth^n)\seas^n_{t-1}\,. 
-%\end{align*}
-
-%For all $1\leqslant n \leqslant N$, given the level component $\fulllvl^n$, the seasonality component $\fullseas^n$ and the forecast horizon $\lag \in \mathbb{N}$, the exponential smoothing forecast $\{\etspred^{ets,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ is, for all $i \in \{1,\ldots,\lag\}$,
-%$$
-%\etspred^{ets,n}_{T+i|T} = \lvl^n_T + \seas^n_{T+i-m(k+1)}\,,
-%$$
-%where $k = \lfloor(i-1)/m\rfloor$.
-
-%For this first stage, we decided to use an additive exponential smoothing for many reasons: firstly, it is easily understandable and it is pretty robust for any kind of sequences.
-
-%This statistical model offers a fine approach to normalize and deseasonnalize the sequences.
-In addition, with its two recurrent equations only, it is simple to code and incorporate in a larger framework using deep learning model and GPUs.
-However, other statistical methods could have been used as the basis of our hybrid approach.
-For example, S.
-Smyl created his hybrid model with a multiplicative exponential smoothing model instead of the additive form.
-At the end, The main complexity is in the next stage: succeed in training a global RNN to understand all the per-time-series statistical models and correct their mistakes.
 
@@
 Consider the following pre-processing.
-%At this stage, we can write that for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
-%$$
-%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \varepsilon^n_{T+i}\,,
-%$$
-%In this paper, we introduce a model based on a latent regime.
-In regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence and the final forecast of our framework is the prediction of the per-time-series parametric model.
-Conversely, in regime 1, the first parametric forecast is unaccurate and it remains a residual random error term that can be estimated.
-% quantity that we note $\remainder$.
-%Conditionally on $\{\fullts^n\}_{1\leqslant n\leqslant N}$, our regime-switching model is:
-
-%$$
-%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \hiddenregime^n_T \cdot \remainder^{n}_{T+i} + \varepsilon^n_{T+i} = \stat^n_{\statparam^n}(\ts^n_{1:T})_i + \hiddenregime^n_T \cdot \remainder^{n}_{T+i} + \varepsilon^n_{T+i}\,,
-%$$
-%where $\{\varepsilon^n_{T+i}\}_{1\leqslant i\leqslant \lag}$ are independent random variables, $U^n_T$ is an unobserved regime switching Bernoulli random variable and $\{\remainder^n_{T+i}\}_{1\leqslant i\leqslant \lag}$ is the random error term to be estimated.
-%In the regime 1, the first parametric forecast is unaccurate and it remains a non-forecasted quantity that we note $\remainder$.
-%For this regime, we have for all $i \in \{1,\ldots,\lag\}$ :
-%$$
-%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \remainder^{n}_{T+i} + \varepsilon^n_{T+i}\,,
-%$$
-
-%To estimate this model, we introduce our new regime swithing error-corrector framework.
-We train two global RNN on all sequences, a classifier ($\classifier$) and a predictor ($\predictor$).
-We train the classifier to estimate the law of the Bernoulli random variable $\hiddenregime^n_T$ and we train the predictor to predict $\{\remainder^{n}_{T+i}\}_{1\leqslant i\leqslant \lag}$.
-However, these two tasks require a thorough data pre-processing and with our collection of parametric models, we propose first to normalize and deseasonalize the RNNs inputs.
-
-%Then, we train a global RNN on all sequences to compute a correction of the initial prediction.
-%Then, we train a global RNN on all sequences to compute a correction of the initial prediction.
-%We motivate this choice for two reasons.
-Firstly, pure machine learning methods achieve relatively poor results in time series forecasting.
-Turning a full forecasting task into a correcting task largely simplifies the RNN goals.
-%This task requires a thorough data pre-processing and with our collection of parametric models, we propose a fine way to normalize and deseasonalize the RNN inputs and outputs.
-%We describe bellow how we design a RNN able to understand the first exponential smoothing models and estimate a correction of their forecasting errors.
 
@@
 \end{equation}
-
-%We use this sequence as input of  $\classifier$ and $\predictor$.
-%Write, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,H\}$, $\err^{n,T}_{T+i|T} = \ts^n_{T+i} - \etspred^{ets,n}_{T+i|T}$.
-% Given $\rnnwindow^n_T$, the proposed regime swithing error-corrector reccurent model is given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by :
-%\begin{align*}
-%\ts^n_{T+i}  &= \tspred^{stat,n}_{T-w+i|T} +  \hat{\hiddenregime}^n_T \cdot \hat{\remainder}^{n}_{T+i} + \varepsilon^n_{T+i}\,, \\
-%\hat{\hiddenregime}^n_T &= \mathbf{1}_{\classifier(\rnnwindow^n_T) > \threshold}\,, \\
-%\hat{\remainder}^{n}_{T+i} &= \predictor(\rnnwindow^n_T)_{T+i} \cdot \meants^n_T\,.
-%\end{align*}
-
-%where $\mathbf{1}$ is the indicator function and $\threshold$ a threshold parameter.
-
-%Consider then a recurrent neural network denoted by RNN-p which aims at predicting the exponential smoothing error.
-Given $\rnnwindow^n_T$, the proposed model is given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by
-%$$
-%\ts^n_{T+i}  = \tspred^{stat,n}_{T-w+i|T-w} +  U^n_T\times\meants^n_T\times \rnnmodel_p(\rnnwindow^n_T)_{T+i} + \varepsilon^n_{T+i}\,,%\\
-%  &= \stat^n(\ts^n_{1:T}|\statparam^n)_i +  U^n_T\times\meants^n_T\times \rnnmodel_p(\rnnwindow^n_T)_{T+i} + \varepsilon^n_{T+i}\,,
-%$$
-%where $\{\varepsilon^n_{T+i}\}_{i\leqslant 1}$ are independent random variables with a Laplace distribution and $U^n_T$ an unobserved regime switching Bernoulli random variable.
-The random variable $U^n_T$ allows to provide RNN-p corrections only when ETS prediction is not sharp enough \textcolor{red}{Show in appendix cases where ETS alone is enough and cases where correction is required}.
-The law of $U^n_T$ is parameterized by a recurrent neural network denoted by RNN-c with the same input than RNN-p.
-%\begin{align*}
-%U^n_T = \mathbf{1}_{\rnnmodel_p(\rnnwindow^n_T) > \threshold}
-%\end{align*}
-%$$
-%\ts^n_{T+i} = \rnnmodel(\rnnwindow^n_T)_{T+i} = \frac{\hat{\err}^{n,T}_{T+i|T}}{\meants^n_T}
-%$$
-%Finally, for all $1\leqslant n \leqslant N$, the  final forecast of the model is $\{\tspred^{n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$, where, for all $i \in \{1,\ldots,\lag\}$ :
-%\begin{align*}
-%\tspred^n_{T+i|T}  &= \etspred^{ets,n}_{T+i|T} +  \meants^n_T\times \rnnmodel(\rnnwindow^n_T)_{T+i}\,,\\
-%  &= \lvl^n_T + \seas^n_{T+i-m(k+1)} + \hat{\err}^{n,T}_{T+i|T}\,.
-%\end{align*}
 
@@
 
-%\subsection{Hidden regime}
-
-%As the regime is not observed, the loglikelihood of the observations cannot be written explicitly to train the model.
-Therefore we use Fisher's identity to compute the score function and write a gradient ascent algorithm to estimate simultaneously the weights of RNN-p and of RNN-c denoted by $\rnnparam = \{\rnnparam_c,\rnnparam_p\}$.
-The score is
-%\begin{equation}
-%\label{eq:score}
-%\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h}\right]\,,
-%\end{equation}
-%where the joint likelihood $p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T}) = p_\theta(U_T^n|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$ is given by \eqref{eq:full:model} and the expectation is under the posterior distribution of $U_T^n$ given $\ts^n_{1:T+h}$.
-Write $\omega_p^n = \mathbb{P}_{\theta_p}(U_T^n = 1|\ts^n_{1:T+h})$.
-Note that
-%$$
-%\omega^n \propto \mathbb{P}_{\theta}(U_T^n = 1|\ts^n_{1:T})p_{\theta}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})\,,
-%$$
-%where $ \mathbb{P}_{\theta}(U_T^n = 1|\ts^n_{1:T})$ is parameterized by $\classifier$ and the predictive probability density $p_{\theta}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})$ is parameterized by $\predictor$ and the statistical model.
-%Then, by \eqref{eq:score},
-%\begin{multline*}
-%\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h}|\ts^n_{1:T}) = \omega^n\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})\\
-%+ (1-\omega^n)\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,.
-%\end{multline*}
-%The loss function is then given by
-%$$
-%\theta\mapsto - \omega^n \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})- (1-\omega^n) \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,.
-%$$
-%A complete description of the training process can be found in Appendix.
-
 \section{Fashion dataset with external weak signals}
 \label{sec:dataset}
-%In image of language processing, there are available reference datasets covering varieties of applications.
-However, for time series forecasting, there is a lack of large, rich and public datasets where neural network approaches can express their potential.
-%\textcolor{red}{Other datasets for time series (see Alice paper on the SMC Transformer): air quality, weather, energy, Covid.
-These datasets exist but no easy weak signals to derive from them i guess.
-}
-%M4 and M5 competitions\textcolor{red}{Add link in footnote} provide a large amount of time series data but they show several limitations.
-For example, the M4 dataset does not propose external signals in addition to the target time series.
-Conversely, the M5 dataset does include weak signals, but like other sales datasets \citep{C.Favorita}, it includes a majority of sporadic time series that cannot be included straightforwadly in a statistical model, see \citep{makridakis2020m5}.
-With this paper, we aim at overcoming this limitation of available datasets for time series forecasting with the first fashion dataset including external weak signals.
-
-%With this paper, we provide the first dataset dedicated to fashion.
-Our fashion dataset is built with a high throughput computer vision systems analysing every day images shared on social networks.
-Aggregating detected clothes by trends, we create for the first time thousand of time series representing fashion trends life on social media.
-Moreover, our sequences show desirable properties.
-They have all the same length, weekly time step, shared behaviours, no sporadic sequence and no missing values.
-We provide publicly a selection of $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
-An overview of it can be found in table 1.
 
@@
 
-%We provide the first dataset dedicated to fashion trends forecasting.
-Our fashion dataset is built with the suprising alliance of a high throughput computer vision system and experts of the fashion sphere.
-A team of deep learning engineers designed and trained a collection of vision neural networks at detecting clothes details: color, cloth type (pants, shoes, top etc...), form, size, texture etc.
-Then a second team of fashion experts aggregated these previous attributes and created thousands of fashion trends.
-%Analysing every day images shared on social networks, we are finally able for the first time to create time series representing these thousands of fashion trends life on social media.
-%
-%Our raw sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
-Each value represents the (normalized) number of analysed images per week where our vision system detected a specific fashion trend.
-%However, in this paper, we present a normalized version of our signals in order to remove strong social media biases.
-%Due to the increasing use of social media and users changes of behaviour, each trend is normalized by its top hierarchical parents and consequently lies between 0 and 1.
-We deseasonized the top hierarchical parent before the normalizing step to keep the season of the original sequence.
-An example of normalization can be found in Figure~\ref{fig:normalization} for a  trend.
-%The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 different categories and 5 geozones.
-An overview of it can be found in Table~\ref{tab:fashiondataset}.
-
 \begin{figure}
 \centering
-\begin{subfigure}{1.\textwidth}
-  \centering
+%\begin{subfigure}{1.\textwidth}
+ % \centering
   \includegraphics[width=1.\linewidth]{figure/cn_female_top_raw}
-  \caption{Time series representing the raw signal of a top fashion trend for female in China}
-  \label{fig:normalization:sub1}
-\end{subfigure}
-\begin{subfigure}{1.\textwidth}
-  \centering
+%  \caption{Time series representing the raw signal of a top fashion trend for female in China}
+ % \label{fig:normalization:sub1}
+%\end{subfigure}
+%\begin{subfigure}{1.\textwidth}
+ % \centering
   \includegraphics[width=1.\linewidth]{figure/cn_female_top_norm}
-  \caption{Time series representing the normalized signal of a top fashion trend for female in China.}
-  \label{fig:normalization:sub2}
-\end{subfigure}
-\caption{Example of difference between the raw sequence and the normalized one. In this example, we normalize by the deseasonalized global top fashion trend for female in China.}
+  %\caption{Time series representing the normalized signal of a top fashion trend for female in China.}
+  %\label{fig:normalization:sub2}
+%\end{subfigure}
+\caption{Example of difference between the raw sequence and the normalized one.
+In this example, we normalize by the deseasonalized global top fashion trend for female in China.
+(Top) Time series representing the raw signal of a top fashion trend for female in China.
+(Bottom) Time series representing the normalized signal of a top fashion trend for female in China.}
 \label{fig:normalization}
 \end{figure}
-%We provide the first dataset dedicated to fashion trends forecasting.
-Our fashion dataset is built with a high throughput computer vision system analysing every day images shared on social networks.
-Aggregating detected clothes by trends, we create for the first time thousands of time series representing fashion trends life on social media.
-Our sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
-Each time series is normalized in order to remove social networks biases and their values lie between 0 and 1.
-The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 different categories and 5 geozones.
-An overview of it can be found in Table 1.
-
-%With in-house fashion experts, we selected especially a collection of $\numberts$ fashion trends in order to represent finely the issues faced by the fashion industry.
-Some sequences show interesting behaviours with sudden changes.
-We call them emerging or declining trends depending on the change in direction.
-A central point of our work is to accurately detect and forecast these trends.
-
-\medskip
-%\textcolor{red}{Est-ce pertinent de decrire les outils de computer vision utilises pour construire le jeu de donnees ? Ou de decrire plus precisement la nature des $y$ consideres ? De }
-
-%With only the historical data, predict this breaking point is challenging and some time impossible.
-
-%a large part of this One central point is to accurately detect and forecast these trends.
-
-%Our sequences show several desirable properties: same length (from 2015-01-05 to 2020-09-01), same yearly seasonality, shared behaviours and no missing values.
-We provide publicly a selection of $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
-An overview of it can be found in table 1.
-
-%a rich dataset gathering 14000 time series of fashion trend occurance on social medias.
-we build our  Every day images shared on social networks are analyzed thanks to a high throughput computer vision systems.
-Aggregating detected clothes by trends, we create thousands of time series with the same good properties: : from 2015-01-05 to 2020-09-01.
-Each time series is normalized in order to remove social networks biases and their values lie between 0 and 1.
-The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
-An overview of it can be found in table 1.
-
-%Heuritech is the first company to adopt a data-intensive approach  for the fashion forecasting. 
-%Every day images shared on social networks are analyzed thanks to a high throughput computer vision systems.
-Aggregating detected clothes by trends, we create thousands of time series with the same good properties: same weekly seasonality, shared behaviours and the same length: from 2015-01-05 to 2020-09-01 \textcolor{red}{Add a few details here or in the appendix}.
-Each time series is normalized in order to remove social networks biases and their values lie between 0 and 1.
-The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 differents categories and 5 geozones.
-An overview of it can be found in table 1.
-
-\begin{table}
-
+
+\begin{table*}
   \caption{Fashion time series overview. For each couple geozone/category, we give the number of female and male trends (Female/Male).}
@@
 
-In theoretical fashion dynamics \citep{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
+In theoretical fashion dynamics \cite{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
 In this way, several weak signals for each sequence are added to the proposed large dataset.
@@
 
-%Secondly, we analyzed only specific parts of social media users depending on the number of followers.
-With three thresholds, 0-1350,1350-7000 and 7000+, we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high} \textcolor{red}{Pas clair}.
-Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.
-let $\ts_t^{l,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{l,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences.
-Based on them, we compute two inputs for our hybrid model : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
-%
-%\begin{align*}
-%\ws^{l,n}_{t} = \frac{\ts_t^{l,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}
-%\end{align*}
-
 In addition to the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{\ell}$ and $\ws^{h}$ are added.
@@
 However, in several examples, they are fundamental to detect the future fashion evolutions, as illustrated in Section~\ref{sec:exp}.
-
-%\subsection{Emerging/Declining fashion trend}
-
-%One of the main objectifs of the fashion industry is to correctly understand and anticipate the futur tendances. 
-%With in-house fashion experts, we selected a collection of $\tsnumber$ fashion trend representing finely the issues that face the fashion industry.
-Our dataset gather 3 types of trends, the common trends, the declining trends and the emerging trends.
-
-%A large part of our time series are regular, their evolutions are slow and constant in time.
-
-%A large part of these trends are commom, their evolutions are regular and well anticipated. In addition to these trends, we find two
-
-%One of the today main objectifs of the fashion industry is to drastically reduce the massive waste due to wrong inventory decisions, see for instance \citep{}.
-With our new dataset, we want to create a focus at detecting precisely
-
-%The first one represents users with few followers, the second one is made of users with a moderate amount of followers and the last one gathers superstar and users of any fields with thousands of influencers.
-Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal.
-
-%At the end, we have for each trends 4 linked weak signals representing this trends on a specific panel of social media users.
-These extra signals are frequently sparse for micro trends and they often lack of interest for common fashion trends.
-However on several examples, they are fundamental to detect the future fashion evolution.
-
-%\subsection{Example}
-
-%As an example, an impressive emerging fashion trend is represented in Figure~\ref{fig:oneemergingtrend}, see other examples in Appendix~\ref{}.
-It shows the evolution of one shoe trend on social media and its linked \textit{fashion-forward} weak signal.
-During the first 3 years, common users and the panel of mode-influencers share the same behaviour.
-The trend started to boom in the mainstream people during the first month of 2018.
-However, we can detect early signals in the fashion-forward panel at the end of 2017.
-Early adopters started to change their behaviour and show more frequently the trend on social media.
-With fashion influence dynamics, the new tendency spreads to every part of social media users.
-Finally, after a peak reached at the end of 2018 for the fashion-influencers, a regular decrease appeared.
-%They leave gradually the old trend to focus more on the latest or propose new ones.
 
@@
 \label{sec:exp}
-%In this section, we evaluate how our hybrid framework is able to deal with the fashion dataset and leverage our complex external weak signals.
-To lead our experience, we keep hide the last year of each time series as our test set.
-For each method and each time series, based on the first five years of data, we predict the last year and compute our accuracy on it.
 
@@
 As an illustration, an example of our temporal split is shown in Figure~\ref{fig:train_eval_test_set}.
-%We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52.
-For each time series, we fitted 3 per-time-series parametric models: We fit the first one using the 2 first years and compute a forecast of the thrid year.
-
-%In order to increase our train set, we use a moving window that provide 53 input/output couples per sequences, being 530000 couples in total.
 
 For the first parametric per-time-series models, existing Python or R libraries are used to estimate the different parameters $\statparam^n$.
-%During the M4 competition, parameters of the exponential smoothing of the porposed hybrid model could move during the training.
-In our framework,
-%$\{\statparam^n\}_{1\leqslant n \leqslant N}$ are fixed during the training of the recurrent models. 
 Depending of the choice of local parametric models, two versions of HERMES are proposed.
@@
 \end{figure}
-
-%To train our hybrid models, we made the choice of don't using the original code of the hybrid method provided during the M4 competition.
-Indeed, the proposed implementation is difficult to use in a more general framework and it is quite slow because it doesn't enable the use of GPU.
-Thereby, we propose with this paper, a new version of the hybrid framework, including the original multiplicative model and the new additive one.
-%Our code is developed in Python using the Tensorflow library and it allows the use of a GPU to speed up the training process contrary to other methods \textcolor{red}{\cite{} developed for the M4 competition}.
-In addition, our approach offers the possibility of providing forecasts for a totally  new collection of sequences without retraining the entire hybrid model.
-Given a new time series,  the weights of the error-corrector recurrent model are frozen and only the new time-series-specific statistical model has to be trained.% It remains the responsibility of the users to provide new sequences sharing same behaviours than the dataset using for the training to keep the same accuracy level.
-
-%For more details about the general hybrid training, a complete description of the training process can be found in the M4 hybrid model paper or in an interesting application of the method on electric load forecasting, see \citep{dudek2020hybrid}.
-
-%\textcolor{red}{Detail here or in the appendix the training details: number of samples, optimizers, learning rates, etc.}
-
-%\vspace{.2cm}
-
-%\textcolor{red}{Detail Train/test split.}
 
@@
 Finally, \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters.
-A complete description and references for these models can be found in \citep{hyndman2020package}.
+A complete description and references for these models can be found in \cite{hyndman2020package}.
 As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.
-Two versions of HERMES are proposed. They are called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
-%Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}.
-The first one, that we name \textit{rshm-ets}, is the hybrid model with an additive exponential smoothing model as parametric model.
-For the second one, we use the TBATS approach as paramteric model and we named it \textit{rshm-tbats}.
-%To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}).  
+Two versions of HERMES are proposed.
+They are called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
 Moreover, two versions with the inclusion of the weak signals (ws) are proposed.
@@
 \end{align*}
-%To compare the different methods, we use the same metrics as in the M4 competition: the Mean Absolute Scaled Error (MASE), the Symmetric Mean Absolute Percentage Error (sMAPE) and the final M4 competition metric, the Overall Weighted Average (OWA) of the sMAPE and the MASE defined as follows:
-%\begin{align*}
-%\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,\quad \mathrm{sMAPE} = \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}\,,\\
-%\mathrm{OWA} &= \frac{1}{2}\left(MASE/MASE_{snaive} + sMAPE/sMAPE_{snaive}\right)\,,
-%\end{align*}
-%
-%where $\hat{Y}$ is a model prediction, $\lag$ is the horizon, $m$ the seasonality and $MASE_{snaive}$ is the $MASE$ computed with the $snaive$ model prediction, idem for the $sMAPE_{snaive}$.
 Detecting emerging and declining trends is a crucial issue for the fashion industry.
@@
 
-%As detecting emerging and declining trends is a fondamental issue that is facing the fashion industry, we evaluate also the different methods on this task.
-In a given year, we define an increasing trend as a trend that do more than 10\% of growth in term of Year and Year.A decreasing trend is a trend that decline of -10\% or more.
-We classify the other trend as flat trend.
-On the test set, the year 2019, we have 1871 increasing trends, 2016 decreasing trends and 6113 flat trends.
-We evaluate all the methods on this classification task.
-
-%\textcolor{red}{where $\mathrm{smape_{snaive}}$ and $\mathrm{mase_{snaive}}$ are}.
-
-%\subsection{Results for XXX Dataset}
-%\textcolor{red}{If possible, a few results of the hybrid approach without weak signals on a dataset other than Heuritech.}
-
 \subsection{Result for Heuritech Fashion dataset}
-
-%\textcolor{red}{Add a figure of a time series with all models (and others in Appendix).}
-
-%\vspace{.2cm}
-
-%\textcolor{red}{Add a table with the results on the trends classifications used in Heuritech.}
-
-%\textcolor{blue}{Result on 1000ts}  \\
 
@@
 It is one of the main motivations why this model is used on the best HERMES candidate as the predictor model.
-%However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825.
-\textcolor{red}{OWA dans le tableau ?}
 
@@
 Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} model and some weaknessess that can be corrected.
-
-%\begin{table*}
-%  \caption{Results summary on our 10000ts Fashion dataset.
-For each metric, we compute the average on all our time series.
-For our approaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
-%  \centering
-%  \resizebox{\textwidth}{!}{%
-%  \begin{tabular}{l||llllllllll}
-%   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
-%    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
-%    \hline
-%	\hline
-%	\rule{0pt}{2ex} \\
-%     \textit{snaive} && 0.881 & - && 25.27 & - && 1. & -\\
-%     \textit{thetam}  && 0.844 & - && 24.17 & - && 0.970 & -\\
-%     \textit{arima} && 0.826 & - && 23.63 & - && 0.949 & -\\
-%     \textit{ets} && 0.807 & - && 23.58 & - && 0.937 & -\\
-%     \textit{hermes-ets-ws} && 0.769 & 0.004 && 22.69 & 0.126 && 0.901 & 0.007\\
-%     \textit{stlm} && 0.770 & - && 22.05 & - && 0.882 & -\\
-%     \textit{hermes-ets} && 0.759 & 0.001 && 22.16 & 0.026 && 0.875 & 0.001\\
-%     \textit{tbats} && 0.745 & - && 21.13 & - && 0.850 & -\\
-%     \textit{lstm-ws} && 0.728 & 0.004 && 20.18 & 0.085 && 0.837 & 0.004\\
-%     \textit{lstm} && 0.724 & 0.003 && 20.08 & 0.052  && 0.825 & 0.004\\
-%     \textit{hermes-tbats-ws} && 0.713 & 0.005 && 20.53 & 0.170 && 0.825 & 0.009\\
-%     \textbf{\textit{hermes-tbats}} && \textbf{0.715} & 0.002 && \textbf{20.41} & 0.056 && \textbf{0.816} & 0.002\\
-%    %\hline
-%  \end{tabular}
-%  }
-%\label{tab:metricresults}
-%\end{table*}
 
@@
 \centering
-\begin{subfigure}{1.\textwidth}
-  \centering
+%\begin{subfigure}{1.\textwidth}
+ % \centering
   \includegraphics[width=1.\linewidth]{figure/us_female_top}
-  \caption{Time series representing a top fashion trend for female in The United States}
-  \label{fig:examples:sub1}
-\end{subfigure}
-\begin{subfigure}{1.\textwidth}
-  \centering
+  %\caption{Time series representing a top fashion trend for female in The United States}
+  %\label{fig:examples:sub1}
+%\end{subfigure}
+%\begin{subfigure}{1.\textwidth}
+ % \centering
   \includegraphics[width=1.\linewidth]{figure/cn_female_texture_horizontalstripe}
-  \caption{Time series representing the horizontal stipes texture fashion trend for female in China}
-  \label{fig:examples:sub2}
-\end{subfigure}
-\caption{\textit{hermes-tbats} forecast examples. In green the prediction of the per-time-series predictors \textit{tbats}. In red the final forecast of our HERMES hybrid model \textit{hermes-tbats}.}
+  %\caption{Time series representing the horizontal stipes texture fashion trend for female in China}
+  %\label{fig:examples:sub2}
+%\end{subfigure}
+\caption{\textit{hermes-tbats} forecast examples.
+In green the prediction of the per-time-series predictors \textit{tbats}.
+In red the final forecast of our HERMES hybrid model \textit{hermes-tbats}.
+(Top) Time series representing a top fashion trend for female in The United States.
+(Bottom) Time series representing the horizontal stipes texture fashion trend for female in China.}
 \label{fig:examples}
 \end{figure}
-
-%
-%\begin{figure}
-%  \centering
-%    \includegraphics[width=1.\linewidth]{figure/hybrid_model_examples}
-%  \caption{\textit{hermes-tbats} forecast examples.
-In green the prediction of the per-time-series predictors \textit{tbats}.
-In red the final forecast of our hermes hybrid model \textit{hermes-tbats}.\textcolor{red}{Utiliser plutot des "marker" (tirets, croix, etc.) car cela differencie mieux}}
-%\label{fig:hybrid-examples}
-%\end{figure}
 
@@
 However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of impactful errors.
-
-%When we look at the result of \textit{lstm-ws} and \textit{lstm} displayed in Table~\ref{tab:lstmclass}, we can also note a rise of the number of correct predictions but with an important increase of the number of classification errors.
-
-%%\texttt{•}
 
@@
 \end{table}
-%\begin{table*}
-%  \caption{\textit{lstm} and \textit{lstm-ws} model confusion matrix}
-%  \begin{tabular}{l||llll}
-%    && \multicolumn{3}{c}{\textbf{\textit{lstm}}}\\
-%    && pred-dec  & pred-flat & pred-inc  \\
-%    \hline
-%    \hline
-%    \rule{0pt}{2ex} \\
-%	true-dec && 447 & 1539 & 30 \\
-%    true-flat && 444 & 5324 & 245 \\
-%    true-inc && 66 & 1410 & 495 \\
-%  \end{tabular}
-%  \begin{tabular}{l||llll}
-%    && \multicolumn{3}{c}{\textbf{\textit{lstm-ws}}}\\
-%   	&& pred-dec  & pred-flat & pred-inc  \\
-%    \hline
-%    \hline
-%    \rule{0pt}{2ex} \\
-%	true-dec && 796 & 1161 & 59 \\
-%    true-flat && 1053 & 4701 & 259 \\
-%    true-inc && 90 & 1259 & 622 \\
-%  \end{tabular}
-%\label{tab:lstmclass}
-%\end{table*}
-%Table~\ref{tab:metricresults} summarize the results of all our benchmark models and our 2 hybrid methods for the 3 metrics described above.
-Values are errors averaged over our \numberts on the test set.
-For the statistical models, we can see a large domination of the TBATS model with an OWA equal to 0.847.
-It is one of the main reasons why we use this model on one of our hybrid frameworks as the parametric model.
-However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates.
-This result shows that, with a large dataset, deep learning models can outperform the traditional approaches on average.
-An example of prediction of all the benchmark methods is displayed in the Figure~\ref{fig:forecastexample}.Our two different regime switching hybrid models achieve a higher level of accuracy compared to their references.
-For the \textit{rshm-ets}, we pass from ???
-for the \textit{ets} model alone to ????
-for the hybrid model.
-Its $\classifier$ threshold $\threshold$ was fixed at ???.
-With this threshold, the error-corrector model correct ????
-sequences of the $\numberts$.
-On these corrected time series, compared to the \textit{ets} approach, our approach MASE falls from ???
-to ???.
-However \textit{rshm-ets} doesn't succeed at outperforming some of the benchmark models, for example \textit{tbats} of \textit{lstm}.
-The \textit{rshm-tbats} version clearly outperforms all the previous models.
-Based on a \textit{tbats} model, which already achieves an interesting level of accuracy, \textit{rshm-tbats} reach the higher level with a MASE equal to 0.728 and and the lower OWA equal to 0.840.
-With a threshold fixed at 0.5, this version of our hybrid framework corrects 294 TBATS predictions.
-On these 294 trends, the \textit{tbats} has an OWA equal to 0.867 and with the regime switching model correction, we reach an OWA equal to 0.845.
-An example of prediction of our two regime-switching hybrid recurrent model is presented in the Figure~\ref{fig:hybridforecast}.
-Other additional examples and results can be found in Appendix.
-
-%\begin{figure}
-%  \centering
-%    \includegraphics[width=1.\linewidth]{figure/example_prediction}
-%  \caption{Example of benchmarck models's predictions on an emerging trend}
-%\label{fig:forecastexample}
-%\end{figure}
-
-%\begin{figure}
-%  \centering
-%    \includegraphics[width=1.\linewidth]{figure/rshm_tbats_prediction_example}
-%  \caption{Example of the \textit{rshm-ets} model prediction.
-In blue the ets reference and in red the $\predictor$ correction.
-$%\classifier$ return ???
-that is greater than its threshold ???: we use then the correction.}
-%  \centering
-%    \includegraphics[width=1.\linewidth]{figure/rshm_tbats_prediction_example}
-%  \caption{Example of the \textit{rshm-tbats} model prediction.
-In blue the Tbats reference and in red the $\predictor$ correction.
-$\classifier$ return 0.537 that is greater than its threshold 0.5: we use the RNN correction.}
-%\label{fig:hybridforecast}
-%\end{figure}
 
@@
 Our achitectures logicaly needs less data to be trained and to perform well.
-
-%\begin{table*}
-%  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series.
-For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
-%  \centering
-% \resizebox{\textwidth}{!}{
-%  \begin{tabular}{l||llllllllll}
-%   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
-%    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
-%    \hline
-%	\hline
-%	\rule{0pt}{2ex} \\
-%     \textit{snaive} && 0.871 & - && 25.29 & - && 1. & -\\
-%     \textit{thetam}  && 0.849 & - && 24.58 & - && 0.980 & -\\
-%     \textit{arima} && 0.821 & - && 23.69 & - && 0.951 & -\\
-%     \textit{ets} && 0.801 & - && 24.18 & - && 0.944 & -\\
-%     \textit{stlm} && 0.765 & - && 22.22 & - && 0.885 & -\\
-%     \textit{lstm-nows} && 0.740 & 0.007 && 20.56 & 0.154 && 0.856 & 0.008\\
-%     \textit{tbats} && 0.734 & - && 21.19 & - && 0.847 & -\\
-%     \textbf{\textit{hybrid-nows}} && \textbf{0.719} & 0.002 && \textbf{20.79} & 0.094 && \textbf{0.833} & 0.004\\
-%  \end{tabular}
-%  }
-%\label{tab:1000metricresults}
-%\end{table*}
 
@@
 
-%\begin{table*}
-%  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series.
-For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
-%  \centering
-%  \begin{tabular}{lllllll}
-%    \hline
-%    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
-%    \hline
-%     \textit{snaive} & 0.871 & - & 25.29 & - & 1. & -\\
-%     \textit{thetam}  & 0.849 & - & 24.58 & - & 0.980 & -\\
-%     \textit{arima} & 0.821 & - & 23.69 & - & 0.951 & -\\
-%     \textit{ets} & 0.801 & - & 24.18 & - & 0.944 & -\\
-%     \textit{hybrid-nows-ets} & 0.768 & 0.002 & 22.91 & 0.111 & 0.902 & 0.005\\
-%     \textit{stlm} & 0.765 & - & 22.22 & - & 0.885 & -\\
-%     \textit{lstm-nows} & 0.740 & 0.007 & 20.56 & 0.154 & 0.856 & 0.008\\
-%     \textit{tbats} & 0.734 & - & 21.19 & - & 0.847 & -\\
-%     \textit{hybrid-nows} & 0.719 & 0.002 & 20.79 & 0.094 & 0.833 & 0.004\\
-%    \hline
-%  \end{tabular}
-%\label{tab:metricresults}
-%\end{table*}
-%\begin{table*}
-%  \caption{Results summary on our 100ts Fashion dataset.
-For each metric, we compute the average on all our time series.
-For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
-%  \centering
-%  \resizebox{\textwidth}{!}{
-%  \begin{tabular}{l||llllllllll}
-%   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
-%    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
-%    \hline
-%	\hline
-%	\rule{0pt}{2ex} \\
-%     \textit{snaive} && 0.876 & - && 26.98 & - && 1. & -\\
-%     \textit{thetam}  && 0.823 & - && 25.11 & - && 0.944 & -\\
-%     \textit{arima} && 0.814 & - && 24.61 & - && 0.940 & -\\
-%     \textit{lstm-nows} && 0.767 & 0.045 && 22.22 & 0.848 && 0.877 & 0.051\\
-%     \textit{stlm} && 0.742 & - && 23.03 & - && 0.863 & -\\
-%     \textit{tbats} && 0.745 & - && 22.16 & - && 0.856 & -\\
-%     \textbf{\textit{hybrid-nows}} && \textbf{0.739} & 0.003 && \textbf{22.31} & 0.083 && \textbf{0.845} & 0.003\\
-%  \end{tabular}
-%  }
-%\label{tab:100metricresults}
-%\end{table*}
-
-%The Table~\ref{tab:metricresultsws},Table~\ref{tab:etsclass} and Table~\ref{tab:tbatsclass} presents how our candidates are able to understand and leverage our weak signals in terms of accuracy and classification.
-The full lstm approach shows a slight increase, from 0.872 to 0.867 for the OWA metric, and correctly predicts 4 increasing/decreasing trends.
-\textcolor{blue}{No for now, WIP} A real improvement is shown by our proposed regime switching framework.
-With a threshold fixed at 0.465, this version of our hybrid framework corrects 118 TBATS predictions.
-On these 118 trends,   the \textit{tbats} has an OWA equal to 0.893 and with the regime switching model correction, we reach an OWA equal to 0.868.
-
-%In a first place, Table 2 shows the final accuracy of the statistical models, the LSTM model and our 2 hybrid models without external data.
-Even without the weak signals, our 2 hybrid approaches largely outperform the statistical references.
-The multiplicative model show the best accuracy with a OWA equal to 0.875.
-We can note that the additive model slightly under-performs the traditional multiplicative one on average.
-This doesn't show a weakness of the additive version but more that a large part of our dataset is more-suited for multiplicative modelization.
-At the end, the strength of training both methods, additive and multiplicative, is in the final porposed ensembling \textit{ensembling} that combines the two approaches with the FForma ensembling.
-
-%In a second place, Table 3 shows the evaluation of our 4 trained hybrid models: the 2 previous ones without weak signals, and our 2 full hybrid models with weak signals.
-We present also the accuracy of a simple LSTM model with and without weak signals.
-We can show the impressive improvement due to our external signals.
-Again, the multiplicative method achieves the best accuracy with OWA metric equal to 0.860.
-We propose like previously, an ensembling mixing our two full hybrid models with weak signals and it reach the high level of accuracy with an OWA equal to 0.849.
-
-%In a third place, table 4 presents the result of our inference process.
-We split our dataset in five equal parts of 2800 sequences and hide the last year for each trends.
-Then, like a cross validation, we train a model on 4 parts and compute its accuracy on the last one on the last year.
-The model never saw the last part so we use our inference process to compute predictions.
-With a permutation of the parts, we can repeat the process and train 5 models, each trained on a specific pool of 4 parts and tested on the remaining part of the dataset.
-For each hybrid model (additive/multiplicative with and without weak signals) Table 4 shows the average accuracy and the Standard Deviation of the 5 trained hybrid models.
-We can see that our inference process achieve really accurate results and practically the same that our hybrid models trained on the entire dataset.
-These results prove that, even without having seen a sequence during the training, if the time series share same behaviours that the training sample, our hybrid approaches can perfectly compute accurate predictions.
-Furthermore, the Standard Deviation is really low for all our metrics.
-This result shows that our hybrid framework is robust and reach constant accuracy level on large dataset.
-
-%\subsection{Discussion}
-%\label{sec:discussion}
-
-%With our results, we can make two interesting conclusions.
-Firstly, the regime switching hybrid framework is a really promising framework.
-By mixing the performance of local parametric models and a global DNN, our two versions clearly outperform traditional statistical methods.
-Furthermore, this framework is totally suited for dealing with external signals.
-With a fine pre-processing and a well-designed architecture, our two models succeed at leveraging our complex extra data and reach impressive accuracy levels.
-Secondly, our results bring to light the quality of our new Fashion dataset.
-We saw that the full LSTM model \textit{lstm} outperforms all time series specific models.
-This shows that our dataset is well suited to train complex neural network architectures able to learn information cross sequences.
-With the addition of our weak signals, we give a totally new dimension to our fashion dataset.
-Our results show that our external weak signals hide a complex but usable predictive power by DNN architecture.
-By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting.
-
-%With our results, we can make several interesting conclusions.
-Firstly, our new HERMES framework is a really promising framework.
-By mixing the performance of local parametric models and a global DNN, our \textit{hermes-tbats} version clearly outperform traditional statistical methods and full neural network models.
-Furthermore, this framework is totally suited for dealing with external signals.
-With a fine pre-processing and a well-designed architecture, our hybrid framework succeed at leveraging our complex extra data and reach impressive accuracy level in term of classification.
-Secondly, our results bring to light the quality of our new Fashion dataset.
-We saw that the full LSTM model \textit{lstm} outperforms all time series specific models when it is trained with the biggest dataset of 10000 time series but not with the smaller ones.
-This shows that complex neural network architectures involve large amount of data to be train and our full dataset is well suited for this.
-Finally, with the addition of our weak signals, we give a totally new dimension to our new hybrid architecture and our fashion dataset.
-Our results show that our external weak signals hide a complex but usable predictive power by our HERMES model.
-However, we believe that it remains a lot of ways to explore in order to leverage the full potential of these chaotic signals.
-
-%\begin{table*}
- % \caption{Comparison between our hybrid models without and with our external weak signals, (Mean/Median)}
-  %\label{sample-table}
-  %\centering
-  %\begin{tabular}{lllllll}
-   % \hline
-    %&  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std \\
-    %\hline
-    %lstm & 0.881/0.824 & 0.34 & 24.41/21.56 & 12.81 & 0.895/0.885 & 0.11 \\
-    %lstm-ws & 0.869/0.814 & 0.33 & 24.56/21.33 & 14.40 & 0.890/0.874 & 0.132 \\
-    % hybrid-add & 0.863/0.812  & 0.32 & 24.17/21.36 & 13.0 & 0.877/0.880 & 0.08 \\
-     %hybrid-mul & 0.858/0.817 & 0.30 & 24.06/21.30 & 13.0 & 0.876/0.873 & 0.11 \\
-  %   hybrid-add-ws & 0.852/0.807 & 0.30 & 24.03/21.17 & 13.0 & 0.872/0.869 & 0.10 \\
-%     hybrid-mul-ws & 0.836/0.798 & 0.29 & 23.67/20.87 & 12.9 & 0.860/0.858 & 0.12 \\
- %    Ensembling & 0.827/0.787 & 0.29 & 23.43/20.63 & 12.8 & 0.849/0.849 & 0.11\\
-  %  \hline
-  %\end{tabular}
-%\end{table*}
-
-%\begin{table*}
- % \caption{Cross-Validation.
-we split our dataset in 5 equal parts.
-We train for each hybrid approach, 5 models on 4 specific parts of the dataset and we test them of the remaining parts with our inference process.}
-  %\label{sample-table}
-  %\centering
- % \begin{tabular}{lllllll}
-  %  \hline
-   % &  MASE  & MASE-std & SMAPE & SMAPE-std & OWA & OWA-std \\
-   % \hline
-   %  hybrid-add & 0.861  & 0.004 & 24.16 & 0.18 & 0.877 & 0.002 \\
-   %  hybrid-mul & 0.856 & 0.008 & 23.95 & 0.25 & 0.870 & 0.005 \\
-   %  hybrid-add-ws & 0.848 & 0.004 & 24.00 & 0.18 & 0.869 & 0.002 \\
-   %  hybrid-mul-ws & 0.844 & 0.010 & 23.74 & .20 & 0.863 & 0.006 \\
-   % \hline
-  %\end{tabular}
-%\end{table*}
-
 \subsection{Result for M4 weekly dataset}
@@
 \label{sec:conclusion}
-%In this paper, we propose the first hybrid model including external weak signals for time series forecasting.
-We show that hybrid framework is a really promising way.
-With its extended error-corrector DNN part, it is clearly well-suited for dealing with any kind of external signals in order to correct weaknesses of first parametric models.
-Furthermore, With our additive version, we show that the hybrid model is not frozen in it original form.
-Thereby, future research explorations would be to improve its framework with new per-time-series approaches and test new error-corrector DNN part like the recent Transformer model.
-
-%In this paper, we propose the first hybrid model including external weak signals for time series forecasting.
-We show that hybrid framework is a really promising way and with its extended error-corrector DNN part, it is clearly well-suited for dealing with any kind of external signals.
-Furthermore, our general framework shows that the hybrid model is able to include any kind of any per-time-series models.
-Depending of the use cases, the nature of the observed time series, users can choose the best parametric models, correct some of its weaknessess and finally increase its accuracy with the HERMES framework.
-Thereby, future research explorations would be to evaluate its framework with a large collection of per-time-series approaches and understand relationships between first parametric model choice and final hybrid model accuracy.
-Is it the best parametric model always the best choice in our HERMES framework ?
-A other promising exploration would be to challenge the error-corrector DNN model with an other one using Transformer or a collection of DNN specialized on specific kind of weaknessess.
-
-%With this first contribution, we join the first fashion dataset gathering \numberts\ fashion times series and a complex collection of external signals.
-We believe that this dataset hide really fine dynamics and interactions where complex models would express their potential.
-By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting and pave the way for further explorations.
-
 The motivation of this paper was to present HERMES, a new hybird model for time series forecasting.
@@
 
-%final results bring to light the quality of our new Fashion dataset.
-We saw that the full LSTM model \textit{lstm} outperforms all time series specific models when it is trained with the biggest dataset of 10000 time series but not with the smaller ones.
-This shows that complex neural network architectures involve large amount of data to be train and our full dataset is well suited for this.
-Finally, with the addition of our weak signals, we give a totally new dimension to our new hybrid architecture and our fashion dataset.
-Our results show that our external weak signals hide a complex but usable predictive power by our HERMES model.
-However, we believe that it remains a lot of ways to explore in order to leverage the full potential of these chaotic signals.
-
-%With our results, we can make several interesting conclusions.
-Firstly, our new HERMES framework is a really promising framework.
-By mixing the performance of local parametric models and a global DNN, our \textit{hermes-tbats} version clearly outperform traditional statistical methods and full neural network models.
-Furthermore, this framework is totally suited for dealing with external signals.
-With a fine pre-processing and a well-designed architecture, our hybrid framework succeed at leveraging our complex extra data and reach impressive accuracy level in term of classification.
-Secondly, our results bring to light the quality of our new Fashion dataset.
-We saw that the full LSTM model \textit{lstm} outperforms all time series specific models when it is trained with the biggest dataset of 10000 time series but not with the smaller ones.
-This shows that complex neural network architectures involve large amount of data to be train and our full dataset is well suited for this.
-Finally, with the addition of our weak signals, we give a totally new dimension to our new hybrid architecture and our fashion dataset.
-Our results show that our external weak signals hide a complex but usable predictive power by our HERMES model.
-However, we believe that it remains a lot of ways to explore in order to leverage the full potential of these chaotic signals.
-
-\bibliography{hermes_paper}
-\bibliographystyle{apalike}
-
-\appendix
+\appendices
+
+%\renewcommand{\thetable}{A\arabic{table}}
+%\renewcommand{\thefigure}{A\arabic{figure}}
+%\setcounter{table}{0}
+%\setcounter{figure}{0}
 
@@
 \centering
-\begin{subfigure}{1.\textwidth}
-  \centering
+%\begin{subfigure}{1.\textwidth}
+ % \centering
   \includegraphics[width=1.\linewidth]{figure/m4_nb_of_window}
-  \caption{result of the HERMES model on the M4 dataset model depending of the number of windows provided per time series to the RNN corrector}
-  \label{fig:m4parameter:sub1}
-\end{subfigure}
-\begin{subfigure}{1.\textwidth}
-  \centering
+  %\caption{result of the HERMES model on the M4 dataset model depending of the number of windows provided per time series to the RNN corrector}
+ % \label{fig:m4parameter:sub1}
+%\end{subfigure}
+%\begin{subfigure}{1.\textwidth}
+ % \centering
   \includegraphics[width=1.\linewidth]{figure/m4_batch_size}
-  \caption{result of the HERMES model on the M4 dataset model depending of the size of the batch size}
-  \label{fig:m4parameter:sub2}
-\end{subfigure}
-\begin{subfigure}{1.\textwidth}
-  \centering
+  %\caption{result of the HERMES model on the M4 dataset model depending of the size of the batch size}
+  %\label{fig:m4parameter:sub2}
+%\end{subfigure}
+%\begin{subfigure}{1.\textwidth}
+  %\centering
   \includegraphics[width=1.\linewidth]{figure/m4_learning_rate}
-  \caption{result of the HERMES model on the M4 dataset model depending of learning rate of the optimizer}
-  \label{fig:m4parameter:sub3}
-\end{subfigure}
-\caption{Example of difference between the raw sequence and the normalized one. In this example, we normalize by the deseasonalized global top fashion trend for female in China.}
+  %\caption{result of the HERMES model on the M4 dataset model depending of learning rate of the optimizer}
+  %\label{fig:m4parameter:sub3}
+%\end{subfigure}
+\caption{Example of difference between the raw sequence and the normalized one.
+In this example, we normalize by the deseasonalized global top fashion trend for female in China.
+(Top) result of the HERMES model on the M4 dataset model depending of the number of windows provided per time series to the RNN corrector.
+(Middle) Result of the HERMES model on the M4 dataset model depending of the size of the batch size.
+(Bottom) Result of the HERMES model on the M4 dataset model depending of learning rate of the optimizer.}
 \label{fig:m4parameter}
@@
 
-%\section{Hidden regime algorithm}
-%
-%In our framework, we assume that our sequence are generated with 2 hidden regime.
-As this regime, noted $\hiddenregime$, is never observed, we use the Expectation Maximization (EM) algorithm to write our loss function:
-%%We note $\rnnparam^{(t)} = \{\rnnparam_c^{(t)},\rnnparam_p^{(t)}\}$ the weights of $\classifier$ and of $\predictor$ at a fixed epoch $t$.
-%
-%As the EM algorithm, we want to compute the following value :
-%
-%\begin{align}
-%\mathbb{Q}^n(\rnnparam|\rnnparam^{(t)}) &= \mathbb{E}\left[\nabla_\theta \log p_\theta(\ts^n_{T+1:T+h},U_T^n|\ts^n_{1:T})\middle|\ts^n_{1:T+h},\rnnparam^{(t)}\right]\ \\
-%& = \sum_{j} p(U_T^n = j|\ts^n_{1:T+h},\rnnparam^{(t)}) \times \textcolor{red}{\nabla_\theta} \log p_\theta(\ts^n_{T+1:T+h},U_T^n = j|\ts^n_{1:T}) \\
-%& = \sum_{j} p(U_T^n = j|\ts^n_{1:T+h},\rnnparam^{(t)}) \times \textcolor{red}{\nabla_\theta}\log[p_\theta(U_T^n = j|\ts^n_{1:T})p_\theta(\ts^n_{T+1:T+h}|U_T^n = j,\ts^n_{1:T})]
-%\end{align}
-%
-%where $ \mathbb{P}_{\theta}(U_T^n = 1|\ts^n_{1:T})$ is parameterized by $\classifier$ and the predictive probability density $p_{\theta}(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})$ is parameterized by $\predictor$ and the statistical model.
-%
-%Write $\omega_{\rnnparam^{(t)}}^n = \mathbb{P}(U_T^n = 1|\ts^n_{1:T+h},\rnnparam^{(t)})$. We have:
-%
-%\begin{align*}
-%\omega_{\rnnparam^{(t)}}^n &= \mathbb{P}_(U_T^n = 1|\ts^n_{1:T+h},\rnnparam^{(t)}) \\
-%& =  \frac{p(\ts^n_{T+1:T+h},U_T^n = 1|\ts^n_{1:T},\rnnparam^{(t)})}{p_(\ts^n_{T+1:T+h}|\ts^n_{1:T})} \\
-%& =  \frac{p(\ts^n_{T+1:T+h}|U_T^n = 1,\ts^n_{1:T},\rnnparam^{(t)}) \times p(U_T^n = 1|\ts^n_{1:T},\rnnparam^{(t)})}{\sum_{U_T^n}p(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T},\rnnparam^{(t)}) \times p(U_T^n|\ts^n_{1:T},\rnnparam^{(t)})}
-%\end{align*}
-%
-%where , $\mathbb{P}(U_T^n=1|\ts^n_{1:T},\rnnparam^{(t)})$ is the output of $\classifier$ at epoch $t$ and the predictive probability density $p(\ts^n_{T+1:T+h}|U_T^n=1,\ts^n_{1:T})$ is compute with the output of $\predictor$ at epoch $t$.
-%
-%To compute our final loss function, we have to define the predictive probability density $p_\theta(\ts^n_{T+1:T+h}|U_T^n,\ts^n_{1:T})$.
-%
-%In our model final equation~\ref{eq:full:model}, we assume that $\varepsilon^n_{T+i}$ are independent and follow a Laplace distribution.
-%
-%We have for the regime 0 :
-%
-%\begin{align*}
-%p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) &= \prod_{i=1}^{h}\frac{1}{2b}e^{\frac{1}{b}|\ts^n_{T+i}  - \tspred^{stat,n}_{T+i|T}|} \\
-%& = \frac{1}{(2b)^h}e^{\frac{1}{b}\sum_{i=1}^{h}|\ts^n_{T+i}  - \tspred^{stat,n}_{T+i|T}|}
-%\end{align*}
-%
-%and for the regime 1 :
-%\begin{align*}
-%p_\theta(\ts^n_{T+1:T+h}|U_T^n=0,\ts^n_{1:T}) &= \frac{1}{(2b)^h}e^{\frac{1}{b}\sum_{i=1}^{h}|\ts^n_{T+i}  - \tspred^{stat,n}_{T-w+i|T}-\meants^n_T \cdot \predictor(\fullconcatinput^n_T)_{T+i} |}
-%\end{align*}
-%
-%with $b$ and constant that we fixed at $ \meants^n_T = \sum_{i = 1}^{w}  \ts^n_{T-w+i}/w$.
-%
-%Finally, we have all the values to compute the loss function :
-%
-%$$
-%\theta\mapsto - \omega_{\rnnparam^{(t)}}^n \log p_\theta(\ts^n_{T+1:T+h},U_T^n=1|\ts^n_{1:T})
-%- (1-\omega_{\rnnparam^{(t)}}^n) \log p_\theta(\ts^n_{T+1:T+h},U_T^n=0|\ts^n_{1:T})\,, \\
-%$$
-%where no gradient is computed on $\omega_{\rnnparam^{(t)}}^n$. 
-%
-
-%\section{Additional results, explorations and examples.}
-
+% use section* for acknowledgment
+%\section*{Acknowledgment}
+%
+%
+%The authors would like to thank...
+
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+% \ifCLASSOPTIONcaptionsoff
+%   \newpage
+% \fi
+\newpage
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+\bibliography{hermes_paper}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+%\begin{thebibliography}{1}
+%
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+%
+%\end{thebibliography}
+
+% biography section
+%
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+
+%\begin{IEEEbiography}{Michael Shell}
+%Biography text here.
+%\end{IEEEbiography}
+
+% if you will not have a photo at all:
+%\begin{IEEEbiographynophoto}{John Doe}
+%Biography text here.
+%\end{IEEEbiographynophoto}
+
+% insert where needed to balance the two columns on the last page with
+% biographies
+%\newpage
+
+%\begin{IEEEbiographynophoto}{Jane Doe}
+%Biography text here.
+%\end{IEEEbiographynophoto}
+
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
+
+% that's all folks
 \end{document}

### 2021-12-21 hermes_paper/hermes_ieee.tex
A few corrections + Figures/Tables updates

@@
 
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \label{fig:introexamples}
-\end{figure}
+\end{figure*}
 
@@
 $$
-\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+i|T}}{\meants^n_T}\,,\quad\mbox{where}\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
+\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+i|T}}{\meants^n_T}\,,\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
 $$
@@
 
-\begin{equation}
+\begin{align}
 \label{eq:nows:full:model}
-\tspred^n_{T+i|T}  = \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\,.
-\end{equation}
+\tspred^n_{T+i|T}  &= \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} \\
+&= \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\,.\nonumber
+\end{align}
 
@@
 Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, a new input for the RNN is defined:
-$$
-\fullconcatinput^n_T = \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}= \{\rnninput^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
-$$
+\begin{align*}
+\fullconcatinput^n_T &= \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}\\
+&= \{\rnninput^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
+\end{align*}
 Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ the final prediction becomes:
@@
 %$$
-\begin{equation}
+\begin{align}
 \label{eq:withws:full:model}
-\tspred^n_{T+i|T}  = \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\fullconcatinput^n_T;\rnnparam)_i \cdot \meants^n_T\
-\end{equation}
-
+\tspred^n_{T+i|T}  &= \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T}\\
+& = \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\fullconcatinput^n_T;\rnnparam)_i \cdot \meants^n_T\,.\nonumber
+\end{align}
 An illustration of the proposed architecture is displayed in Figure~\ref{fig:architecture}.
@@
 Each value represents the number of users posts in a week where vision algorithms detected the fashion trend on picture.
-As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization:sub1}.
+As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization}.
 
@@
 \label{fig:normalization}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
@@
 \label{fig:oneemergingtrend}
-\end{figure}
+\end{figure*}
 
@@
 \label{fig:train_eval_test_set}
-\end{figure}
+\end{figure*}
 
@@
 \begin{align*}
-\mathrm{ACCURACY} &= \frac{TP_{dec} + TP_{flat} + TP_{inc}}{TP_{dec} + TP_{flat} + TP_{inc} + FP_{dec} + FP_{flat} + FP_{inc}}\,,
+\mathrm{ACCURACY} &= \frac{TP}{TP + FP}\,,
 \end{align*}
-where $TP_i$ is the number of time series correctly classified in the class $i$ and $FP_i$ is the number of time series miss classified in the class $i$.
+where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series miss classified in the class $i$.
 
@@
 \label{fig:examples}
-\end{figure}
+\end{figure*}
 

### 2021-12-21 hermes_paper/hermes_ieee.tex
A few corrections + Figures/Tables updates

@@
 
-\textbf{10000 Heuritech Fashion time series global accuracy}
-
-For the two metrics and for each model, we compute the average on all our sequences \numberts~  on the final year.
+\textbf{10000 Heuritech Fashion time series global accuracy.
+}For the two metrics and for each model, we compute the average on all our sequences \numberts~  on the final year.
 Results are displayed in the Table~\ref{tab:metricresults}.
@@
 
-\begin{table*}
+\begin{table}
   \caption{Results summary on the 10000ts Fashion dataset.
@@
   \centering
-  \resizebox{0.85\textwidth}{!}{%
+%  \resizebox{0.85\textwidth}{!}{%
   \begin{tabular}{l||lllll|lllll}
@@
   \end{tabular}
-  }
+%  }
 \label{tab:metricresults}
-\end{table*}
+\end{table}
 
@@
 
-\textbf{10000 Heuritech Fashion time series classification task}
-
-The impact of the weak signals are revealed with our classification results.
+\textbf{10000 Heuritech Fashion time series classification task.
+} The impact of the weak signals are revealed with our classification results.
 Classification results between the \textit{tbats} model and the hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impresive decrease of impactful errors: forecast an increase instead of a decrease and vice versa.
@@
   %\vspace{0.2cm}
+\centering
   \begin{tabular}{l||llll}
@@
     true-flat && 351 & 2920 & 300 \\
-    true-inc && 300 & 2078 & 709 \\
+    true-inc && 300 & 2078 & 709 
   \end{tabular}
-  \vspace{1cm}
+
+\vspace{.2cm}
+
   \begin{tabular}{l||llll}
@@
     true-flat && 549 & 2823 & 199 \\
-    true-inc && 214 & 2004 & 869 \\
+    true-inc && 214 & 2004 & 869 
   \end{tabular}
-  \centering
+
+\vspace{.2cm}
+
   \begin{tabular}{l||llll}
@@
     true-flat && 1257 & 2087 & 227 \\
-    true-inc && 358 & 1620 & 1109 \\
+    true-inc && 358 & 1620 & 1109 
   \end{tabular}
@@
 
-\textbf{Importance of the size of the dataset}
-
-In addition to the results on the fashion dataset gathering 10000 time series, the behaviour of the HERMES model is analyzed when it is trained on smaller datasets.
+\textbf{Size of the dataset.
+} In addition to the results on the fashion dataset gathering 10000 time series, the behaviour of the HERMES model is analyzed when it is trained on smaller datasets.
 2 experiments was done, HERMES models was trained on a reduced dataset of 1000 time series and on a reduced dataset of 100 time series.
@@
 
-\begin{table*}
-  \caption{Results summary on the 1000ts Fashion dataset and 100ts Fashion Dataset.For each metric, the average on all our time series is computed.
+\begin{table}
+  \caption{Results summary on the 1000ts Fashion dataset and 100ts Fashion Dataset.
+For each metric, the average on all our time series is computed.
 For the two approaches using neural network, 10 models with different seeds are trained.
@@
   \centering
- \resizebox{0.85\textwidth}{!}{
-
+% \resizebox{0.85\textwidth}{!}{ 
   \begin{tabular}{l||llll}
@@
   \end{tabular}
-  \quad
+
+\vspace{.2cm}
+
   \begin{tabular}{l||llll}
@@
   \end{tabular}
-  }
+%  }
 \label{tab:1000metricresults}
-\end{table*}
+\end{table}
 
@@
 \label{fig:m4dataset}
-\end{figure}
+\end{figure*}
 
@@
   \centering
-  \resizebox{0.85\textwidth}{!}{%
+ % \resizebox{0.85\textwidth}{!}{%
   \begin{tabular}{l||lllll|lllll|lllll}
@@
   \end{tabular}
-  }
+%  }
 \label{tab:m4metricresults}

### 2021-12-21 hermes_paper/hermes_ieee.tex
A few corrections + Figures/Tables updates

@@
 
-In addition to the previous results, a HERMES application is also done on the M4 weekly dataset.
-The M4 dataset gathers 359 weekly time series and shows 3 main differences compare to the fashion dataset.
-Firstly, sequences have not the same lenght with sequence lenghts lying between 93 and 2610 time steps.
-Secondly, as some of the sequences represent financial signals or some others are demographic sequences, the  359 time series show huge contrasting behaviours.
-Thirldy, compare to the fashion application, the horizon for the M4 competition is set to 13 for the weekly dataset.
+We also assessed the performance of HERMES using the M4 weekly dataset \cite{makridakis2020m4}.
+The M4 dataset gathers 359 weekly time series and shows 3 main differences compare to our proposed fashion dataset.
+Firstly, sequences do not have the same length with sequence lengths lying between 93 and 2610 time steps.
+Secondly, as some of the sequences represent financial signals or some others are demographic sequences, the  359 time series show very distinct behaviours.
+Thirldy, compare to the fashion application, the time horizon of the prediction is set to 13 for the weekly dataset.
 
@@
 For the HERMES architecture, some loss candidates were defined for the training : the Mean Absolute Error (MAE), the Mean Square Error (MSE),  the Scaled Mean Absolute Error (SMAE) and the Scaled Mean Square Error (SMSE).
-The loss functions are defined as follows :
-
-$$
-MAE = \frac{1}{\lag}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,,\quad  MSE = \frac{1}{\lag}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|
-$$
-$$
-SMAE = \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,,\quad  SMSE = \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|
-$$
-
+The loss functions are defined as follows:
+\begin{align*}
+MAE &= \frac{1}{\lag}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,,\\
+MSE &= \frac{1}{\lag}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\\
+SMAE &= \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,,\\
+SMSE &= \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,.
+\end{align*}
 For each loss, 10 \textit{hermese-tbats-ws} models have been trained with different seeds and the final mean and standard deviation are given in Figure~\ref{}.

### 2021-12-22 hermes_paper/hermes_ieee.tex
Corrections - Intro

@@
 We first provide the first fashion dataset gathering \numberts\ weekly fashion time series.
-As influence dynamics are the key of emerging trend detection, we associate with each time series several external weak signals representing behaviors of influencers towards the trend.
+As influence dynamics are the key of emerging trend detection, we associate with each time series several external weak signals representing behaviors of influencers.
 Secondly, to leverage such a complex and rich dataset, we propose a new hybrid forecasting model.
 Our approach combines per-time-series parametric models with seasonal components and a global recurrent neural network to include sporadic external signals.
-This hybrid model provides state-of-the-art results on the fashion dataset, and illustrates the benefit of the contribution of external weak signals.
+This hybrid model provides state-of-the-art results on the proposed fashion dataset, on the weekly time series of the M4 competition \cite{makridakis2018m4}, and illustrates the benefit of the contribution of external weak signals.
 \end{abstract}
@@
 Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
-The exponential smoothing model \cite{RePEc:inm:oropre:v:9:y:1961:i:5:p:673-685}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \cite{doi:10.1198/jasa.2011.tm09771}, or the ARIMA with the Box-Jenkins approach \cite{box2015time} are for instance very popular parametric linear generative models.
+The exponential smoothing model \cite{RePEc:inm:oropre:v:9:y:1961:i:5:p:673-685}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \cite{doi:10.1198/jasa.2011.tm09771}, or the ARIMA with the Box-Jenkins approach \cite{box2015time} are for instance very popular parametric generative models.
 Hidden Markov models (HMM) are also widespread and presuppose that available observations are defined using missing data describing the dynamical system.
 This hidden state is assumed to be a Markov chain such that at each time step the received observation is a random function of the corresponding latent data.
-Although hidden states are modeled as a Markov chain, the observations arising therefrom present a highly complex statistical structure.
+Although hidden states are modeled as a Markov chain, the observations arising therefrom have a complex statistical structure.
 %Introducing latent hidden states, they assume that the predictive distribution is not unique and constant in time but multiple and lead by the values of the hidden states changing during time.
@@
 
-In many fields, single or few time series have become thousands of sequences with complex statistical structures.
+In many fields, single or few time series have become thousands of sequences with various statistical properties.
 In this new context, classical time series specific statistical models show limitations when dealing with numerous heterogeneous data.
@@
 More recently, applications using the Transformer model have been proposed  \cite{li2019enhancing}.
-A direct concurrent of the DeepAR model can be found with the Temporal Fusion Transformers (TFT) approach \cite{lim2019temporal}.
+The Temporal Fusion Transformers (TFT) approach is a direct alternative to the DeepAR model \cite{lim2019temporal}.
 Unfortunately, all these solutions suffer from two main weaknesses.
-Firstly, many of them are "black-boxes"  as the final forecast usually does not come with a statistical guarantee  although a few recent works focused on measuring uncertainty in recurrent neural networks, see  \cite{martin2020monte}.
-Secondly, without a fine prepossessing and well chosen hyper-parameters, these methods may lead to poor results and are often outperformed by traditional statistical models, see \cite{makridakis2018m4}.
-
-In this paper, we consider  new time series forecasting application referred to as {\em fashion trends prediction}.
-Based on a cutting-edge image recognition technology, we built the first fashion dataset containing \numberts\ sequences representing the apparition of fashion trends on social media per week from 01-01-2015 to 01-01-2019.
-Our fashion time series has very appealing properties: they have all the same length, same seasonality, no missing value and the absence of sparse time series even for niche trends.
-The originality of our dataset come from the fact that additional external weak signals can be introduced.
-With our fashion expertise, we detected several groups of fashion users with a high influence power.
-Analysing their specific behaviours on social medias, we add to each time series, 4 external weak signals representing the same fashion trends but on a sub-category of users.
-We call them weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal.
-With this totally new application, we aim at designing a model able to deal with our large fashion dataset, leverage our complex external weak signals and finally provide the most accurate forecasts.
+Firstly, many of them are black-boxes  as the final forecast usually does not come with a statistical guarantee  although a few recent works focused on measuring uncertainty in recurrent neural networks, see  \cite{martin2020monte}.
+Secondly, without a fine prepossessing and well chosen hyper-parameters, these methods may lead to poor results and be outperformed by traditional statistical models, see \cite{makridakis2018m4}.
+
+In this paper, we consider a  new time series forecasting application referred to as {\em fashion trends prediction}.
+Based on a cutting-edge image recognition technology, we built the first fashion dataset containing \numberts\ weekly sequences  of fashion trends on social media  from 01-01-2015 to 01-01-2019.
+This dataset has very appealing properties:  all time series have the same length, same seasonality, no missing value and there is no sparse time series even for niche trends.
+The originality of our dataset comes from the fact that additional external weak signals can also be introduced.
+With our fashion expertise, we detected several groups of highly influential fashion users.
+Analysing their specific behaviours on social media, we associate with each time series, 4 external weak signals representing the same fashion trends on a sub-category of users.
+They are called weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal.
+With this totally new application, we aim at designing a model able to deal with such a large dataset, leveraging  complex external weak signals and finally providing the most accurate forecasts.
 
@@
 The approach providing the most striking results was proposed in  \cite{smyl2020hybrid} in the context of the M4 forecasting competition \cite{makridakis2020m4}.
-Given a large dataset, a per-time-series multiplicative exponential smoothing model is introduced to estimate simple but fundamental components for each time series and compute a first prediction.
-Then a global recurrent neural network is trained on the entire dataset to correct errors of the previous exponential smoothing models.
+Given a large dataset, a per-time-series multiplicative exponential smoothing model was introduced to estimate simple but fundamental components for each time series and compute a first prediction.
+Then a global recurrent neural network was trained on the entire dataset to correct errors of the previous exponential smoothing models.
 
@@
 This new architecture is decomposed  into two parts: local predictors and a global corrector.
-First, a per-time-series parametric statistical model is trained on all sequences.
+First, a per-time-series parametric statistical model is trained on each sequence.
 Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.
-By adding external weak signals in the proposed framework, the real potential of the hybrid approach is revealed: a global neural network, able to leverage large amount of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of any parametric models.
+The external weak signals reveal the real potential of the hybrid approach: a global neural network, able to leverage large amount of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.
 
 The paper is organized as follow.
-Section~\ref{sec:hybrid} describes the hybrid framework.
+Section~\ref{sec:hybrid} introduces the proposed hybrid model.
 Then, the new fashion dataset provided with this article is presented in Section~\ref{sec:dataset}.

### 2021-12-22 hermes_paper/hermes_ieee.tex
Corrections - Section 2

@@
 \newcommand{\fullts}{{\bf \ts}}
-\newcommand{\tspred}{\hat{\ts}}
+\newcommand{\tspred}{\widehat{\ts}}
 \newcommand{\stat}{f}
@@
 \label{sec:hybrid}
-We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, the predictors, and a global error-corrector neural network train on all time series, the corrector.
-Per-time-series parametric models are used to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
+We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, and a global error-corrector neural network train on all time series.
+Per-time-series parametric models are used to learn local behaviours, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
 Then, gathering information of the first predictions and external variables, a recurrent neural networks is trained to correct the predictions provided by the first collection of per-time-series models.
@@
 $$
-
 During the M4 competition, the hybrid model of \cite{smyl2020hybrid} was based on a multiplicative exponential smoothing model as the time-series-specific predictor.
-However, on sporadic time series, this choice leads to poor result and instability.
+However, on sporadic time series, this choice leads to poor results and instability.
 In this paper, a more general framework able to deal with any kind of per-time-series models is provided.
 In Section~\ref{sec:exp}, two versions of our framework are proposed.
-The first one use an  exponential smoothing as reference similar to the baseline \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
-
-In the specific application of fashion trends prediction, two main forms of standard weaknesses was detected and defined for an univariate parametric forecast as defined above.
+The first one is based on an  exponential smoothing as a reference similar to the baseline \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
+
+In the specific application of fashion trends prediction, two main forms of standard weaknesses were detected and defined for univariate parametric forecasts.
 The first one is a weakness of definition, when the model is not well defined for its forecasting task.
-For instance, an additive model provide good predictions on time series with additive seasonality but show difficulties with multiplicative one.
+For instance, an additive model provides good predictions on time series with additive seasonality but fails at handling multiplicative seasonalities.
 The second form, harder to detect and correct, is the weakness of information.
@@
 In somes cases, these changes depend on external variables not considered by univariate parametric models.
-The difficulty is that the exact influence of external variables on the main signal is not mainly know.
+The difficulty is that the exact influence of external variables on the main signal is mostly unknown.
 It is on this point that  the new HERMES framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals.
@@
 The second part of the model is a global RNN, trained on all the $N$ sequences to correct the weaknesses of the first per-time-series parametric models.
-This task requires a thorough data pre-processing for two main reasons.
-First, without a well-design input, the RNN will not be capable of understanding the initial collection of forecasts and predict their future errors.
-Second, as no assumption about the scale of our time series was made, inputs require a careful normalization before feeding them to the RNN.
-Consider the following pre-processing.
+This task requires a thorough data pre-processing as recurrent neural networks training is highly sensitive to the scale of the data and requires well-designed inputs.
+Since no assumption about the scale of our time series was made, inputs require a careful normalization before being fed to the RNN.
 
@@
 $$
-
 Let $\rnn(.;\rnnparam)$ be the recurrent neural network model where $\rnnparam$ are  unknown parameters.
@@
 $$
-
-Our hybrid model forecast is finally given, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$, by:
-
+Our hybrid model forecast is, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$,
 \begin{align}
@@
 Then, to correct the second form of weakness, in addition to the $N$ target time series, $K \times N$ external sequences indexed from $0$ to $T$ are considered.
-For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ linked to the sequence $\fullts^n$.
-Let  $\fullws^n = \{\{\ws_t^{n,k}\}_{1\leqslant t \leqslant T}\}_{1\leqslant k \leqslant K}$ be all the values of the weak signals linked to the $n$-th sequence.
+For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ associated with the sequence $\fullts^n$.
+Let  $\fullws^n = \{\{\ws_t^{n,k}\}_{1\leqslant t \leqslant T}\}_{1\leqslant k \leqslant K}$ be all the values of the weak signals associated with the $n$-th sequence.
 In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the sequence.
@@
 \end{align}
-An illustration of the proposed architecture is displayed in Figure~\ref{fig:architecture}.
+An illustration of the proposed  model is displayed in Figure~\ref{fig:architecture}.
 

### 2021-12-22 hermes_paper/hermes_ieee.tex
Corrections - Section 3

@@
 this collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry.
-For instance, some sequences show complex behaviours with sudden changes.
-They are called emerging or declining trends depending on the change in direction.
+For instance, some sequences show complex behaviours with sudden changes (emerging or declining trends).
 A central point of this work is to accurately detect and forecast such trends.
@@
 \begin{table*}
-  \caption{Fashion time series overview. For each couple geozone/category, we give the number of female and male trends (Female/Male).}
+  \caption{Fashion time series overview. For each couple geozone/category, the table gives the number of trends (Female/Male).}
 \label{tab:fashiondataset}
@@
 In theoretical fashion dynamics \cite{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
-In this way, several weak signals for each sequence are added to the proposed large dataset.
+In this way, several weak signals for each sequence are added to the proposed dataset.
 
@@
 We named \textit{fashion-forwards} this first weak signal.
-For all trend $\{y_t\}_{1\leqslant t\leqslant T}$, let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
+For all trends $\{y_t\}_{1\leqslant t\leqslant T}$, let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
 As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for our hybrid model:  for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
@@
 Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.
-For instance, an impressive emerging fashion shoes trend with its linked \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
+For instance, an impressive emerging fashion shoes trend with its \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
 
@@
 Repeating the previous methodology on each sub-panel, three normalized time series for each time series are created.
-Again, the motivation here is to detect behaviour gaps between different part of the society that could announce bigger changes in the main signal.
+Again, the motivation here is to detect behaviour gaps between different parts of the society that could lead to changes in the main signal.
 Let $\ts_t^{\ell,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{\ell,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences.

### 2021-12-22 hermes_paper/hermes_ieee.tex
Corrections - Section 4 - Fashion

@@
 \subsection{Training}
-
 The dataset is temporally split into three blocks, {\em train}, {\em eval} and {\em test} sets.
@@
 The first one uses as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}.
-The second one uses the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves striking accuracy results on the fashion dataset.
-The neural network part architecture is summarized in Figure~\ref{fig:rnn_architecture}.
+The second one uses the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves the best accuracy results on the fashion dataset.
+The neural network architecture is summarized in Figure~\ref{fig:rnn_architecture}.
 It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension.
@@
 The loss and previous parameters are all set with a grid search (additional materials can be found in Appendix).
-the code is developed in Python using the Tensorflow library.
-It allows the use of a GPU to speed up the trainig process.
+The code is developed in Python using the Tensorflow library.
+It allows the use of GPU to speed up the trainig process.
 
@@
 Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels},  \texttt{tbats}, for each time series, predictions are computed with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
-The forecast of the \textit{snaive} method is only the repetition of the last same past period.
+The forecast of the \textit{snaive} method is only the repetition of the last past period.
 The \textit{ets} model is an additive exponential smoothing with a level component and a seasonal component.
 The \textit{stlm} approach uses a multiplicative decomposition and models the seasonally adjusted time series with an exponential smoothing model.
-The \textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast and \textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization.
+The \textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast and \textit{tbats} uses a trigonometrical seasonality.
 Finally, \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters.
@@
 Moreover, two versions with the inclusion of the weak signals (ws) are proposed.
-They are referred as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}.
+They are referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}.
 In order to provide a fair comparison, a \textit{lstm} with the weak signals named \textit{lstm-ws} is trained.
@@
 \begin{align*}
-\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}
+\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,.
 \end{align*}
@@
 \end{align*}
-where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series miss classified in the class $i$.
+where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series missclassified in the class $i$.
 
@@
 \textbf{10000 Heuritech Fashion time series global accuracy.
-}For the two metrics and for each model, we compute the average on all our sequences \numberts~  on the final year.
-Results are displayed in the Table~\ref{tab:metricresults}.
+}For the two metrics and for each model, we compute the average on all sequences   on the final year.
+Results are displayed in Table~\ref{tab:metricresults}.
 For our model using neural networks, 10 models are trained  with different seeds.
@@
 Models using our weak signals perform similarly as without-weak-signals models for the MASE.
-In Figure~\ref{fig:introexamples}.
 Interestingly, weak signals sinificantly improve the accuracy in detecting emerging and declining trends.
@@
 \textbf{10000 Heuritech Fashion time series classification task.
-} The impact of the weak signals are revealed with our classification results.
-Classification results between the \textit{tbats} model and the hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impresive decrease of impactful errors: forecast an increase instead of a decrease and vice versa.
-the \textit{hermes-tbats} model divides by 3 the error rate in comparison to \textit{tbats} with only a slightly decrease of the number of correct increase/decrease predictions.
+} Classification results between the \textit{tbats} model and the hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impresive decrease of impactful errors: i.e.
+forecasting an increase instead of a decrease and vice versa.
+The \textit{hermes-tbats} model divides by 3 the error rate in comparison to \textit{tbats} with only a slight decrease of the number of correct increase/decrease predictions.
 However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of impactful errors.
@@
 \textbf{Size of the dataset.
-} In addition to the results on the fashion dataset gathering 10000 time series, the behaviour of the HERMES model is analyzed when it is trained on smaller datasets.
-2 experiments was done, HERMES models was trained on a reduced dataset of 1000 time series and on a reduced dataset of 100 time series.
+} In addition to the results on the fashion dataset gathering 10000 time series, the behaviour of the HERMES model is analyzed when it is trained on smaller datasets: two experiments were performed, HERMES models were trained on a reduced dataset of 1000 time series and on a reduced dataset of 100 time series.
 Results are given in Table~\ref{tab:1000metricresults}.
 
-With these investigations, two important remarks can be done.
-First, the hybrid framework \textit{hermes-tbats} achieves the first position in term of global accuracy on both datasets.
-Due to the strengh of its per-time-series predictor TBATS, the hybrid model succeds at correcting some of TBATS weaknesses and logically reach a striking final accuracy.
+First, the hybrid framework \textit{hermes-tbats} achieves the best performance in term of global accuracy on both datasets.
+Due to the strengh of its per-time-series predictor TBATS, the hybrid model succeeds at correcting some of TBATS weaknesses and logically reaches a satisfactory final accuracy.
 Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases.
 On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms its accuracy level.
-Learn how to compute a full prediction from scratch is a complex task and high-dimensional recurrent neural networks require  large amount of data.
+Providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require  large amount of data to do so.
 Nevertheless, with the HERMES framework, the RNN task is largely simplified.
-Our achitectures logicaly needs less data to be trained and to perform well.
+Our model logicaly needs less data to be trained and to obtain interesting performance.
 

### 2021-12-22 hermes_paper/hermes_ieee.tex
Corrections - Section 4 - M4 + conclusion

@@
 We also assessed the performance of HERMES using the M4 weekly dataset \cite{makridakis2020m4}.
-The M4 dataset gathers 359 weekly time series and shows 3 main differences compare to our proposed fashion dataset.
+The M4 dataset gathers 359 weekly time series and has 3 main differences compared to our proposed fashion dataset.
 Firstly, sequences do not have the same length with sequence lengths lying between 93 and 2610 time steps.
-Secondly, as some of the sequences represent financial signals or some others are demographic sequences, the  359 time series show very distinct behaviours.
-Thirldy, compare to the fashion application, the time horizon of the prediction is set to 13 for the weekly dataset.
-
-\textbf{Training}
-
-\textcolor{blue}{reformuler}
-The sequence are firstly resized in order to egalize their lenghts.
-For the shorter ones: the eval and the test set is removed (the last 26 steps).
-Then the remaining number of entire year is duplicated in order to egalize all the sequence at the longest one : 2610 time steps.
-As per time series parametric model training time depends on the sequence lenght, all time series are then croped.
-At the end, with the addition of the previously removed eval and test set, 300 time steps are kept for each sequence.
-
-For this training, The horizon $h$ is set to 13 due to the M4 weekly test set size and the window size $w$ is fixed at 104.
-For the RNN part, the same architecture than describe in Figure~ \ref{fig:rnn_architecture} is used.
-The Adam optimizer is used with a learning rate fixed at 0.005 and a batch size set at 8.
-As the loss function, the same loss than the fashion application is used.
-As the M4 weekly dataset is small, a rolling window is used on the train set in order to increase the train number of example and improve the training.
-5 windows are computed for each sequence for the RNN train set.
-An overview of our train, eval, test set split and the resizing of the shorter sequences is given in Figure~\ref{}.
-The previous parameters: window size, learning rate, batch size and the number of train window per time series are set using a grid search.
+Secondly, as some of the sequences represent financial signals or some others are demographic sequences, the  359 time series have very distinct scales and dynamics.
+Thirldy, compared to the previous fashion application, the time horizon of the prediction is set to 13 for the weekly dataset.
+
+\textbf{Training.
+} The sequences are firstly resized in order to obatain a dataset with fixed time horizon.
+The eval and the test sets are removed for the shortest sequences (the last 26 steps).
+Then, the remaining number of entire year is duplicated in order to egalize all the sequence at the longest one : 2610 time steps \textcolor{red}{Pas sur de comprendre, reformuler}.
+As per time series parametric model training time depends on the sequence length, all time series are then croped.
+Finally, with the addition of the previously removed eval and test sets, 300 time steps are kept for each sequence \textcolor{red}{Pas sur de comprendre, reformuler}.
+
+The horizon $h$ is set to 13 due to the M4 weekly test set size and the window size $w$ is set to 104.
+For the RNN part, the same architecture as the one described in Figure~ \ref{fig:rnn_architecture} is used.
+The Adam optimizer is used with a learning rate  equal to  0.005 and a batch size set to 8.
+As the M4 weekly dataset is small, a rolling window is used on the train set in order to increase the train number of examples and improve training results.
+Five windows are computed for each sequence for the RNN train set.
+An overview of our train, eval, test set split and the resizing of the shortest sequences is given in Figure~\ref{}.
+The previous parameters: window size, learning rate, batch size and the number of train windows per time series are set using a grid search, see Appendix~\ref{}.
 
@@
   \caption{One of the shortest sequences of the M4 weekly dataset (93 time steps).
-In order to fit its predictor, the last complete year is duplicated in order to reach a total lenght of 300 time steps.}
+In order to fit its predictor, the last complete year is duplicated in order to reach a total length of 300 time steps.}
 \label{fig:m4dataset}
@@
 
-\textbf{Benchmarks}
-
-The M4 competion provides a rich collection of benchmarks gatering statistical models and neural network approaches.
-The same candidates are used in this part as baseline.
-In addition, the hybrid model named \textit{Uber} of S.Smyl is added to provide an interesting comparison against the HERMES approach.
+\textbf{Benchmarks.
+} The M4 competion provides a rich collection of benchmarks gatering statistical models and neural network approaches.
+The same candidates are used in this part as baselines.
+In addition, the hybrid model named \textit{Uber} of S.Smyl is added.
 For a complete description and references of the benchmarck models, see \cite{makridakis2020m4}.
 As a HERMES candidate, a version using TBATS is proposed and called \textit{hermes-tbats}.
-Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measure.
-A complete definition of these metrics is also proposed in \cite{makridakis2020m4}.
-
-\textbf{Results and discussion}
-
-The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}.
+Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measures.
+A complete definition of these metrics is proposed in \cite{makridakis2020m4}, see also Appendix~\ref{}.
+
+\textbf{Results and discussion.
+} The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}.
 Considering the HERMES approach, \textit{hermes-tbats} outperforms all the benchmarcks.
@@
 Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}.
-With this second application, two important conclusions can be done.
+With this second application, two important conclusions can be made.
 Firstly, the striking results of \textit{hermes-tbats} confirm that the HERMES framework is a general framework, well suited for a large collection of forecasting tasks.
-Secondly, the accuracy gap between the 2 hybrid candidates validate the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.
+Secondly, the accuracy gap between the two hybrid candidates validates the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.
 
@@
 The motivation of this paper was to present HERMES, a new hybird model for time series forecasting.
-This new framework is a really promising approach.
-By mixing the performance of local parametric models and a global neural network.
-The \textit{hermes-tbats} version clearly outperform traditional statistical methods and full neural network models.
-Furthermore, this new model is totally suited for dealing with external signals.
-With a fine pre-processing and a well-designed architecture, our hybrid framework succeed at leveraging our complex extra data and reach impressive accuracy level in term of classification.
+By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks.
+Furthermore, this new model is totally suited to deal with external signals.
+With a fine pre-processing and a well-designed architecture, our hybrid framework succeeds at leveraging our complex extra data and reaches very promising accuracy levels in terms of classification.
 In addition to this article, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided.
-We believe that this dataset hide really fine dynamics and interactions where complex models would express their potential.
-By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting and pave the way for further explorations.
-As a possible future work, a different inclusion of the weak signals can be design in the HERMES architecture.
-Focusing on the example with huge change of behaviors, a fine analysis of the predictive power of the collection of weak signals can be done.
-In the same way, an interesting improvment of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses and activate or not by a latent space.
-This latent space can be drive by the historical data or even more by the weak signals.
+We believe that this dataset contains really fine dynamics and interactions where complex models would express their potential.
+By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
+As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.
+Focusing on the examples with huge changes of behaviors, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works.
+In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses.
+An interesting perspective is to add a latent discrete label to select dynamically the regime shifts, i.e.
+which corrector model to use on-the-fly.
 

### 2021-12-22 hermes_paper/hermes_ieee.tex
Corrections - Appendix

@@
 
-Using deep learning models in time series forecasting is a appealing way to achieve higher levels of accuracy.
+Using deep learning models in time series forecasting is an appealing way to achieve higher accuracy performance.
 However, it induces two main issues.
-First, have a large enough dataset to train the model as illustrated in Section~\ref{sec:exp}.
-Second, find a correct loss to train the model.
-For the second point, the main difficulty is that a dataset can gather contrasting time series in terms of scale.
+First, it requires a large enough dataset to train the model as illustrated in Section~\ref{sec:exp}.
+Second, the main difficulty is that a dataset can gather contrasting time series in terms of scale.
 These differences can impact the loss behaviour and finally the training.
-For the HERMES architecture, some loss candidates were defined for the training : the Mean Absolute Error (MAE), the Mean Square Error (MSE),  the Scaled Mean Absolute Error (SMAE) and the Scaled Mean Square Error (SMSE).
+For the HERMES architecture, some loss candidates were defined for the training: the Mean Absolute Error (MAE), the Mean Square Error (MSE),  the Scaled Mean Absolute Error (SMAE) and the Scaled Mean Square Error (SMSE).
 The loss functions are defined as follows:
@@
 For each loss, 10 \textit{hermese-tbats-ws} models have been trained with different seeds and the final mean and standard deviation are given in Figure~\ref{}.
-The final Scaled Mean Absolute Error reach the lower MASE and was selected to train all the HERMES model in this paper.
+The final Scaled Mean Absolute Error reaches the lowest MASE and was selected to train all the HERMES model in this paper.
 
@@
   \caption{MASE accuray for the \textit{hermes-tbats-ws} model depending of the loss used during the RNN training.
-For each loss, 10 models with different seed have been trained.
+For each loss, 10 models with different seeds have been trained.
 The mean and the standard deviation are represented with a point and a vertical line.}
@@
 
-The HERMES framework get several parameters to set correctly in order to reach acceptable level of accuracy.
-For instance, a overview of the learning rate, batch size and number of window per time series grid search for the M4 weekly dataset is shown in this part.
-For each parameters, a collection of 10 \textit{hermes-tbats} models have been trained with a range of values and the final OWA was calculated.
-As in the Figure~\ref{fig:loss_function}, the mean and the standard deviation of each groups of 10 trainings is displayed in Figure~\ref{}.
-For the final \textit{hermes-tbats} model of the M4 weekly dataset, the grid search fixed the following setup : 3 windows per time series, the batch size set to 8 and the optimizer's learning rate equal to 0.005.
+The HERMES model depends on several hyperparameters to set correctly in order to reach satisfactory performance.
+For instance, an overview of the learning rate, batch size and number of windows per time series grid search for the M4 weekly dataset is shown in Figure~\ref{}.
+For each parameter, a collection of 10 \textit{hermes-tbats} models have been trained with a range of values and the final OWA was calculated.
+As in the Figure~\ref{fig:loss_function}, the mean and the standard deviation of each group of 10 trainings is displayed in Figure~\ref{}.
+For the final \textit{hermes-tbats} model of the M4 weekly dataset, the grid search fixed the following setup : 3 windows per time series, the batch size set to 8 and the learning rate equal to 0.005.
 

### 2021-12-22 hermes_paper/hermes_paper.tex
Appendix M4 part update

@@
 
+The M4 weekly dataset is a collection of 359 time series with  contrasting behaviours and sizes.
+An overview of the dataset is given in Table~\ref{tab:m4dataset} and some example of sequences are given in Figure~\ref{fig:m4examples}.
+As sequences have not the same domain origin, the HERMES approach doesn't seem to be the best suited model for this forecasting task.
+However, on some examples as in Figure~\ref{fig:m4pred}, interesting corrections of the Tbats forecasts can be noted.
+
+\begin{table}
+
+  \caption{M4 weekly dataset overview. For each category, we give the number of sequences and the average length.}
+\label{tab:m4dataset}
+  \centering
+  \resizebox{1.\width}{!}{
+  \begin{tabular}{l||llllll}
+    %hline
+    \\
+    &  \textbf{Demographic}  & \textbf{Finance} & \textbf{Industry} & \textbf{Macro} & \textbf{Micro} & \textbf{Other} \\
+    \hline
+    \hline
+    \\
+	\textbf{Number of sequences} & 24 & 164 & 6 & 41 & 112 & 12 \\
+	\\
+    \textbf{average length} & 1659 & 1237 & 834 & 1264 & 473 & 1598 \\
+    \textbf{minimal length} & 1615 & 260 & 356 & 522 & \textbf{93} & 470 \\
+  \end{tabular}
+  }
+\end{table}
+
+\begin{figure}
+\centering
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/W10}
+  \caption{A time series from the ``Other`` category called \textit{W10}.}
+  \label{fig:m4examples:sub1}
+\end{subfigure} \quad
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/W20}
+  \caption{A time series from the ``Macro`` category called \textit{W20}.}
+  \label{fig:m4examples:sub1}
+\end{subfigure}
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/W220}
+  \caption{A time series from the \textit{Finance} category called \textit{W220}.}
+  \label{fig:m4examples:sub2}
+\end{subfigure}\quad
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/W354}
+  \caption{A time series from the \textit{Micro} category called \textit{W354}.}
+  \label{fig:m4examples:sub3}
+\end{subfigure}
+\caption{Examples of time series from the M4 weekly dataset.}
+\label{fig:m4examples}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}{1.\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/W133_pred}
+  \caption{\textit{tbats} and \textit{hermes-tbats} forecast of the \textit{W133} time series}
+  \label{fig:m4pred:sub1}
+\end{subfigure}
+\begin{subfigure}{1.\textwidth}
+  \centering
+  \includegraphics[width=1.\linewidth]{figure/W314_pred}
+  \caption{\textit{tbats} and \textit{hermes-tbats} forecast of the \textit{W314} time series}
+  \label{fig:m4pred:sub2}
+\end{subfigure}
+\caption{\textit{hermes-tbats} forecast examples on the M4 weekly dataset.
+In green the prediction of the per-time-series predictors \textit{tbats}.
+In red the final forecast of our HERMES hybrid model \textit{hermes-tbats}.}
+\label{fig:m4pred}
+\end{figure}
+
+However, on the M4 weekly dataset final accuracy, some models reach a higher accuracy than the HERMES framework.
+Except one approach, all of them are a combination of different models.
+It is commom in time series forecasting to aggregated various approachs to increase the robusness of the final forecast and in the same time achieve a better global accuracy.
+The best model on the M4 weekly dataset is not an ensembling and with a OWA equal to 0.739, outperforms the \textit{hermer-tbats} and all the M4 proposed models on the M4 weekly sub-dataset.
+This framework called \textit{Forecast Pro} is a model selection approach depending where a collection of parametric model are trained and selected depending of time series properties.
+A description and interesting remarks are discussed is \citep{DARIN2020135}
+An interessant reseach perspective can be to replace the tbats per-time-series predictor by this individual models which seems more suited for the M4 weekly forecasting task.
+
 \section{Training parameters and loss}
@@
 For each parameters, a collection of 10 \textit{hermes-tbats} models have been trained with a range of values and the final OWA was calculated.
-As in the Figure~\ref{fig:loss_function}, the mean and the standard deviation of each groups of 10 trainings is displayed in Figure~\ref{}.
+As in the Figure~\ref{fig:loss_function}, the mean and the standard deviation of each groups of 10 trainings is displayed in Figure~\ref{fig:m4parameter}.
 For the final \textit{hermes-tbats} model of the M4 weekly dataset, the grid search fixed the following setup : 3 windows per time series, the batch size set to 8 and the optimizer's learning rate equal to 0.005.

### 2021-12-31 hermes_paper/hermes_ieee.tex
several updates

@@
 % Do not put math or special symbols in the title.
-\title{HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series}
+\title{HERMES : Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}
 %
@@
 Our contribution is  twofold.
-We first provide the first fashion dataset gathering \numberts\ weekly fashion time series.
-As influence dynamics are the key of emerging trend detection, we associate with each time series several external weak signals representing behaviors of influencers.
+We first provide publicly the first fashion dataset gathering \numberts\ weekly fashion time series.
+As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviors of influencers.
 Secondly, to leverage such a complex and rich dataset, we propose a new hybrid forecasting model.
@@
 Strong consistency results were established in \cite{touron2019consistency} and Expectation Maximization based numerical experiments were proposed.
-Altough these works provide promising results, HMM are computationally expensive to train and are not yet well studied for seasonal  sequences with thousands of components.
+Although these works provide promising results, HMM are computationally expensive to train and are not yet well studied for seasonal  sequences with thousands of components.
 
@@
 Firstly, many of them are black-boxes  as the final forecast usually does not come with a statistical guarantee  although a few recent works focused on measuring uncertainty in recurrent neural networks, see  \cite{martin2020monte}.
-Secondly, without a fine prepossessing and well chosen hyper-parameters, these methods may lead to poor results and be outperformed by traditional statistical models, see \cite{makridakis2018m4}.
+Secondly, without a fine preprocessing and well chosen hyper-parameters, these methods may lead to poor results and be outperformed by traditional statistical models, see \cite{makridakis2018m4}.
 
@@
 With our fashion expertise, we detected several groups of highly influential fashion users.
-Analysing their specific behaviours on social media, we associate with each time series, 4 external weak signals representing the same fashion trends on a sub-category of users.
+Analyzing their specific behaviours on social media, we associate with each time series an external weak signal representing the same fashion trends on a sub-category of users.
 They are called weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal.
@@
 Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.
-The external weak signals reveal the real potential of the hybrid approach: a global neural network, able to leverage large amount of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.
-
-The paper is organized as follow.
+The external weak signals reveal the real potential of the hybrid approach: a global neural network, able to leverage large amounts of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.
+
+The paper is organized as follows.
 Section~\ref{sec:hybrid} introduces the proposed hybrid model.
@@
 Per-time-series parametric models are used to learn local behaviours, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
-Then, gathering information of the first predictions and external variables, a recurrent neural networks is trained to correct the predictions provided by the first collection of per-time-series models.
+Then, gathering information of the first predictions and external variables, a recurrent neural network is trained to correct the predictions provided by the first collection of per-time-series models.
 
@@
 In red the final forecast of our HERMES hybrid model.
-(Top) Time series representing a shoes fashion trend for female in The United States.
-(Bottom) Time series representing the vertical stipes texture fashion trend for female in Brazil.}
+(Top) Time series representing a shoes fashion trend for females in The United States.
+(Bottom) Time series representing the vertical stipes texture fashion trend for females in Brazil.}
 \label{fig:introexamples}
@@
 $$
-\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+i|T}}{\meants^n_T}\,,\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
+\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+i \equiv h|T}}{\meants^n_T}\,,\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
 $$
@@
     \includegraphics[width=1\linewidth]{figure/HERMES_archi.png}
-  \caption{Hybrid model with weak signals architecture.}
+  \caption{Architecture of the hybrid model with weak signals.}
 \label{fig:architecture}
@@
 Then, fashion experts designed fashion trends by aggregating these clothes details: a meaningful combination of items that represent an existing trend in the fashion sphere.
-To represent finely human behaviors based on social media, a group of thousands of random users, called a panel, was created on several geolocalisations.
-Analysing every day images shared on social networks by these panels with our computer vision algorithms, we can translate the history of thousands of fashion trends in thousands of time series.
+To finely represent human behaviours based on social media, a group of thousands of random users, called a panel, was created on several geolocalisations.
+Analyzing every day images shared on social networks by these panels with our computer vision algorithms, we can translate the history of thousands of fashion trends in thousands of time series.
 All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
@@
 
-Due to the increasing use of social media and users change of behaviour, a normalization step is applied to the raw sequences.
+Due to the increasing use of social media and users' change of behaviour, a normalization step is applied to the raw sequences.
 Each fashion trend is divided by its hierarchical parent category trend.
-Moreover, in order not to remove the seasonality of all sequences, we deseasonalized the hierarchical parent category trend before the normalization.
-For instance, as displayed in Figure~\ref{fig:normalization}, the raw Jersey Top trend for female in China is divided by the deseasonalized global Top trend for female in China.
+Moreover, in order to not remove the seasonality of all sequences, we deseasonalized the hierarchical parent category trend before the normalization.
+For instance, as displayed in Figure~\ref{fig:normalization}, the raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.
 The final normalized sequence is expressed in share of category.
@@
 We therefore introduce a new dataset for fashion time series forecasting.
-It contains a sample of $\numberts$ anonymized and  normalized fashion trends for men and women, on 9 different categories and 5 geozones.
+It contains a sample of $\numberts$ anonymized and  normalized fashion trends for men and women, in 9 different categories and 5 geozones.
 An overview of it can be found in Table~\ref{tab:fashiondataset}.
@@
 \caption{Example of difference between the raw sequence and the normalized one.
-In this example, we normalize by the deseasonalized global top fashion trend for female in China.
-(Top) Time series representing the raw signal of a top fashion trend for female in China.
-(Bottom) Time series representing the normalized signal of a top fashion trend for female in China.}
+In this example, we normalize by the deseasonalized global top fashion trend for females in China.
+(Top) Time series representing the raw signal of a top fashion trend for females in China.
+(Bottom) Time series representing the normalized signal of a top fashion trend for females in China.}
 \label{fig:normalization}
@@
 In theoretical fashion dynamics \cite{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
-In this way, several weak signals for each sequence are added to the proposed dataset.
-
-Firstly, numerous social media influencers were selectioned by hand by fashion experts.
+In this way, a weak signal for each sequence is added to the proposed dataset.
+
+Numerous social media influencers were selectioned by hand by fashion experts.
 By aggregating them, a specific ``fashion-oriented`` panel is created.
-With the same methodology than for the main panel descibed in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created.
-We named \textit{fashion-forwards} this first weak signal.
+With the same methodology as for the main panel described in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created.
+We named \textit{fashion-forwards} this weak signal.
 For all trends $\{y_t\}_{1\leqslant t\leqslant T}$, let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
@@
 
-Secondly, depending of the number of followers, the general panel of users is divided in three sub-groups: users with less than 1350 followers, users with a number of followers between 1350 and 7000 and users with more than 7000 followers.
+%Secondly, depending of the number of followers, the general panel of users is divided in three sub-groups: users with less than 1350 followers, users with a number of followers between 1350 and 7000 and users with more than 7000 followers.
 Repeating the previous methodology on each sub-panel, three normalized time series for each time series are created.
@@
 Two inputs for our hybrid model are computed: for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
-\begin{align*}
-\ws^{\ell,n}_{t} = \frac{\ts_t^{\ell,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}
-\end{align*}  
-values close to 0.3 indicate a similar behaviour between the three sub-panels and the general panel.
-
-In addition to the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{\ell}$ and $\ws^{h}$ are added.
+%\begin{align*}
+%\ws^{\ell,n}_{t} = \frac{\ts_t^{\ell,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}
+%\end{align*}  
+%values close to 0.3 indicate a similar behaviour between the three sub-panels and the general panel.
+%
+%In addition to the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{\ell}$ and $\ws^{h}$ are added.
 They are frequently sparse for micro trends and they often lack interest in common fashion trends.
@@
 The 3 first years are used as the {\em train} set, the 4th year is kept for the {\em eval} set and the {\em test} set is made of the last year.
-The hyrid model is trained to compute a one-year ahead prediction, $\lag$ equal to 52, and the window size $\window$ is fixed at 104.
-Using the two first year of the {\em train} set, a first per-time-series parametric model for each time series is fitted.
+The hybrid model is trained to compute a one-year ahead prediction, $\lag$ equal to 52, and the window size $\window$ is fixed at 104.
+Using the two first years of the {\em train} set, a first per-time-series parametric model for each time series is fitted.
 With the resulting collection of local models, a forecast of the third year is computed for each sequence.
 Corrector inputs are finally computed and the RNN is trained at correcting weaknesses of this first collection of third-year forecasts.
-For the {\em eval} set, per-time-series predictors are fitted a second time using the three first years and a forecasts of the fourth year are computed.
+For the {\em eval} set, per-time-series predictors are fitted a second time using the three first years and forecasts of the fourth year are computed.
 The {\em eval} set is used during the training to control the learning of the RNN model and prevent overfitting.
@@
 The neural network architecture is summarized in Figure~\ref{fig:rnn_architecture}.
-It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension.
+It is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
 A classical Adam optimizer is used with a learning rate set at 0.001 or 0.005, the batch size is fixed 64 and the loss function is defined as follows:
@@
 The code is developed in Python using the Tensorflow library.
-It allows the use of GPU to speed up the trainig process.
+It allows the use of GPU to speed up the training process.
 
@@
 To compare the different methods, we use the Mean Absolute Scaled Error (MASE).
-As our time series have complete different scale, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, independent of the scale of the sequence.
-The MASE metric is defined as follows:
+As our time series have completely different scales, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, independent of the scale of the sequence.
+The MASE metric is defined as follows, with $m$ the seasonal periods:
 \begin{align*}
@@
 A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes.
-In addition to the MASE accuracy metric, the different methods are also evaluated on a classification task and especially difference between methods using weak signals or not.
+In addition to the MASE accuracy metric, the different methods are also evaluated on a classification task and especially differences between methods using weak signals or not.
 In a given year, an increasing trend is defined as a trend that does more than 5\% of growth with respect to the previous year.
@@
 \end{align*}
-where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series missclassified in the class $i$.
+where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series misclassified in the class $i$.
 
@@
 \textbf{10000 Heuritech Fashion time series global accuracy.
-}For the two metrics and for each model, we compute the average on all sequences   on the final year.
+}For the two metrics and for each model, we compute the average on all sequences in the final year.
 Results are displayed in Table~\ref{tab:metricresults}.
@@
 
-Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slighlty outperform the alternatives in terms of MASE and are stable across the different trainings.
-Regarding \textit{hermes-ets},   although it is very similar to the baseline \cite{smyl2020hybrid}, its accuracy remains low in comparison to the \textit{lstm} benchmarck or HERMES using TBATS.
+Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slightly outperform the alternatives in terms of MASE and are stable across the different trainings.
+Regarding \textit{hermes-ets},   although it is very similar to the baseline \cite{smyl2020hybrid}, its accuracy remains low in comparison to the \textit{lstm} benchmark or HERMES using TBATS.
 
 Models using our weak signals perform similarly as without-weak-signals models for the MASE.
-Interestingly, weak signals sinificantly improve the accuracy in detecting emerging and declining trends.
-Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} model and some weaknessess that can be corrected.
+Interestingly, weak signals significantly improve the accuracy in detecting emerging and declining trends.
+Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} model and some weaknesses that can be corrected.
 
@@
 In red the final forecast of our HERMES hybrid model \textit{hermes-tbats}.
-(Top) Time series representing a top fashion trend for female in The United States.
-(Bottom) Time series representing the horizontal stipes texture fashion trend for female in China.}
+(Top) Time series representing a top fashion trend for females in The United States.
+(Bottom) Time series representing the horizontal stipes texture fashion trend for females in China.}
 \label{fig:examples}
@@
 \textbf{10000 Heuritech Fashion time series classification task.
-} Classification results between the \textit{tbats} model and the hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impresive decrease of impactful errors: i.e.
+} Classification results between the \textit{tbats} model and the hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impressive decrease of impactful errors: i.e.
 forecasting an increase instead of a decrease and vice versa.
@@
 
-First, the hybrid framework \textit{hermes-tbats} achieves the best performance in term of global accuracy on both datasets.
-Due to the strengh of its per-time-series predictor TBATS, the hybrid model succeeds at correcting some of TBATS weaknesses and logically reaches a satisfactory final accuracy.
+First, the hybrid framework \textit{hermes-tbats} achieves the best performance in terms of global accuracy on both datasets.
+Due to the strength of its per-time-series predictor TBATS, the hybrid model succeeds at correcting some of TBATS weaknesses and logically reaches a satisfactory final accuracy.
 Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases.
 On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms its accuracy level.
-Providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require  large amount of data to do so.
+Providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require  large amounts of data to do so.
 Nevertheless, with the HERMES framework, the RNN task is largely simplified.
-Our model logicaly needs less data to be trained and to obtain interesting performance.
+Our model logically needs less data to be trained and to obtain interesting performance.
 
 \begin{table}
-  \caption{Results summary on the 1000ts Fashion dataset and 100ts Fashion Dataset.
-For each metric, the average on all our time series is computed.
-For the two approaches using neural network, 10 models with different seeds are trained.
+  \caption{Results summary on the 1000 time series and 100 time series Fashion dataset.
+The MASE average on all our time series is computed.
+For the two approaches using a neural network, 10 models with different seeds are trained.
 the mean and the standard deviation of the 10 results are displayed.}
@@
   \begin{tabular}{l||llll}
-    \multicolumn{4}{c}{1000 ts Fashion dataset}\vspace{0.5cm} \\
+    \multicolumn{4}{c}{1000 time series Fashion dataset}\vspace{0.5cm} \\
     &&\multicolumn{2}{c}{\textbf{MASE}} \\
@@
 Secondly, as some of the sequences represent financial signals or some others are demographic sequences, the  359 time series have very distinct scales and dynamics.
-Thirldy, compared to the previous fashion application, the time horizon of the prediction is set to 13 for the weekly dataset.
+Thirdly, compared to the previous fashion application, the time horizon of the prediction is set to 13 for the weekly dataset.
 
 \textbf{Training.
-} The sequences are firstly resized in order to obatain a dataset with fixed time horizon.
+} The M4 dataset is firstly preprocessed in order to equalize all the sequences.
+This preliminary step is motivated by two reasons.
+First, as some sequences are short (93 time steps), they limit the window size $w$ of the RNN part and consequently the global accuracy of the HERMES approach.
+Second, the longer time series slow down the training of the collection of the first predictors especially for complex methods like TBATS.
+300 time steps are kept for each sequence in order to train the HERMES model.
+For the shorter sequences, the train set is duplicated in order to reach the length of 300.
+For the longer ones, they are cropped in order to keep the last 300 time steps.
+%The sequences are firstly resized in order to obatain a dataset with fixed time horizon.
 The eval and the test sets are removed for the shortest sequences (the last 26 steps).
@@
 The horizon $h$ is set to 13 due to the M4 weekly test set size and the window size $w$ is set to 104.
-For the RNN part, the same architecture as the one described in Figure~ \ref{fig:rnn_architecture} is used.
+For the RNN part, the same architecture as the one described in Figure~\ref{fig:rnn_architecture} is used.
 The Adam optimizer is used with a learning rate  equal to  0.005 and a batch size set to 8.
 As the M4 weekly dataset is small, a rolling window is used on the train set in order to increase the train number of examples and improve training results.
-Five windows are computed for each sequence for the RNN train set.
-An overview of our train, eval, test set split and the resizing of the shortest sequences is given in Figure~\ref{}.
-The previous parameters: window size, learning rate, batch size and the number of train windows per time series are set using a grid search, see Appendix~\ref{}.
+3 windows are computed for each sequence for the RNN train set.
+An overview of our train, eval, test set split and the resizing of the shortest sequences is given in Figure~\ref{fig:m4dataset}.
+The previous parameters: window size, learning rate, batch size and the number of train windows per time series are set using a grid search, see Appendix~\ref{sec:m4gridsearch}.
 
@@
 \textbf{Benchmarks.
-} The M4 competion provides a rich collection of benchmarks gatering statistical models and neural network approaches.
+} The M4 competition provides a rich collection of benchmarks emcompassing statistical models and neural network approaches.
 The same candidates are used in this part as baselines.
 In addition, the hybrid model named \textit{Uber} of S.Smyl is added.
-For a complete description and references of the benchmarck models, see \cite{makridakis2020m4}.
+For a complete description and references of the benchmark models, see \cite{makridakis2020m4}.
 As a HERMES candidate, a version using TBATS is proposed and called \textit{hermes-tbats}.
-Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measures.
-A complete definition of these metrics is proposed in \cite{makridakis2020m4}, see also Appendix~\ref{}.
+Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measure.
+A complete definition of these metrics is proposed in \cite{makridakis2020m4}, see also Appendix~\ref{sec:m4overview} for additional information about the M4 weekly dataset.
 
@@
 } The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}.
-Considering the HERMES approach, \textit{hermes-tbats} outperforms all the benchmarcks.
-This results is partially induced by the use of TBATS per-time-series predictors which achieves striking results on the test set.
+Considering the HERMES approach, \textit{hermes-tbats} outperforms all the benchmarks.
+This result is partially induced by the use of TBATS per-time-series predictors which achieves striking results on the test set.
 Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}.
@@
 For each metric, the average on all our time series is computed.
-For approaches using neural network, 10 models are trained with different seeds.
+For approaches using a neural network, 10 models are trained with different seeds.
 The mean and the standard deviation of the 10 results are displayed.}
@@
      \textit{Uber} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
-     \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.8 && - &\\
+     \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.841 && - &\\
      \textit{\textbf{hermer-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
@@
 As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.
-Focusing on the examples with huge changes of behaviors, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works.
+Focusing on the examples with huge changes of behaviours, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works.
 In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses.
@@
 \section{M4 weekly dataset and results}
+\label{sec:m4overview}
+
+The M4 weekly dataset is a collection of 359 time series with  contrasting behaviours and sizes.
+An overview of the dataset is given in Table~\ref{tab:m4dataset} and some example of sequences are given in Figure~\ref{fig:m4examples}.
+As sequences have not the same domain origin, the HERMES approach doesn't seem to be the best suited model for this forecasting task.
+However, on some examples as in Figure~\ref{fig:m4pred}, interesting corrections of the Tbats forecasts can be noted.
+
+\begin{table}
+
+  \caption{M4 weekly dataset overview. For each category, the number of sequences and the average length are given.}
+\label{tab:m4dataset}
+  \centering
+  \resizebox{1.\width}{!}{
+  \begin{tabular}{l||lll}
+    %hline
+    \\
+    &  \textbf{Nb. of sequences}  & \textbf{Avg. length} & \textbf{Min. length} \\
+    \hline
+    \hline
+    \\
+	\textbf{Demographic} & 24 & 1659 & 1615\\
+	\textbf{Finance} & 164 & 1237 & 260\\
+	\textbf{Industry} & 6 & 834 & 356\\
+	\textbf{Macro} & 41 & 1264 & 522\\
+	\textbf{Micro} & 112 & 473 & \textbf{93}\\
+	\textbf{Other} & 12 & 1598 & 470\\
+  \end{tabular}
+  }
+\end{table}
+
+\begin{figure}
+%\centering
+%\begin{subfigure}{.45\textwidth}
+%  \centering
+  \includegraphics[width=1.\linewidth]{figure/W10}
+%  \caption{A time series from the ``Other`` category called \textit{W10}.}
+  \label{fig:m4examples:sub1}
+%\end{subfigure} \quad
+%\begin{subfigure}{.45\textwidth}
+%  \centering
+  \includegraphics[width=1.\linewidth]{figure/W20}
+%  \caption{A time series from the ``Macro`` category called \textit{W20}.}
+%  \label{fig:m4examples:sub1}
+%\end{subfigure}
+%\begin{subfigure}{.45\textwidth}
+%  \centering
+  \includegraphics[width=1.\linewidth]{figure/W220}
+%  \caption{A time series from the \textit{Finance} category called \textit{W220}.}
+%  \label{fig:m4examples:sub2}
+%\end{subfigure}\quad
+%\begin{subfigure}{.45\textwidth}
+%  \centering
+  \includegraphics[width=1.\linewidth]{figure/W354}
+%  \caption{A time series from the \textit{Micro} category called \textit{W354}.}
+%  \label{fig:m4examples:sub3}
+%\end{subfigure}
+\caption{Examples of time series from the M4 weekly dataset.
+From Top to Bottom : time series called \textit{W10} from the \textit{Other} category,\textit{W20} from the \textit{Macro} category, \textit{W220} from the \textit{Finance} category and \textit{W354} from the \textit{Micro} category}
+\label{fig:m4examples}
+\end{figure}
+
+\begin{figure*}
+\centering
+% \begin{subfigure}{1.\textwidth}
+%  \centering
+  \includegraphics[width=1.\linewidth]{figure/W133_pred}
+%  \caption{\textit{tbats} and \textit{hermes-tbats} forecast of the \textit{W133} time series}
+%  \label{fig:m4pred:sub1}
+% \end{subfigure}
+% \begin{subfigure}{1.\textwidth}
+%  \centering
+  \includegraphics[width=1.\linewidth]{figure/W314_pred}
+%  \caption{\textit{tbats} and \textit{hermes-tbats} forecast of the \textit{W314} time series}
+%  \label{fig:m4pred:sub2}
+% \end{subfigure}
+\caption{\textit{hermes-tbats} forecast examples on the M4 weekly dataset.
+In green the prediction of the per-time-series predictors \textit{tbats}.
+In red the final forecast of our HERMES hybrid model \textit{hermes-tbats}.
+(Top) the \textit{W133} time series, (Bottom) the \textit{W314} time series.}
+\label{fig:m4pred}
+\end{figure*}
+
+Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset.
+Except one approach, all of them are a combination of different models in order to increase the robustness of the final forecast and at the same time achieve a better global accuracy.
+The remaining one is not an ensembling but a statistical framework called \textit{Forecast Pro}.
+It is not a single statistical model but a framework that chooses, depending on the sequence properties, the best statistical approach to forecast it.
+With a OWA equal to 0.739, it outperforms the \textit{hermer-tbats} and all the M4 proposed models on the M4 weekly sub-dataset.
+A description and interesting remarks about the \textit{Forecast Pro} model are discussed in \cite{DARIN2020135}.
+A promising research perspective can be to replace the TBATS per-time-series predictor by this model which seems more suited for the M4 weekly forecasting task.
 
@@
 \subsection{Loss grid search on the Fashion Dataset}
+\label{sec:heuritechgridsearch}
 
@@
 First, it requires a large enough dataset to train the model as illustrated in Section~\ref{sec:exp}.
-Second, the main difficulty is that a dataset can gather contrasting time series in terms of scale.
-These differences can impact the loss behaviour and finally the training.
-For the HERMES architecture, some loss candidates were defined for the training: the Mean Absolute Error (MAE), the Mean Square Error (MSE),  the Scaled Mean Absolute Error (SMAE) and the Scaled Mean Square Error (SMSE).
+Second, a dataset can hide contrasting time series in terms of scale, noise and behaviour.
+These differences can impact the loss and finally the training.
+For the HERMES architecture, some candidate losses were defined for the training: the Mean Absolute Error (MAE), the Mean Square Error (MSE),  the Scaled Mean Absolute Error (SMAE) and the Scaled Mean Square Error (SMSE).
 The loss functions are defined as follows:
@@
 MAE &= \frac{1}{\lag}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,,\\
-MSE &= \frac{1}{\lag}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\\
+MSE &= \frac{1}{\lag}\sum_{i=1}^{\lag}(\ts^n_{T+i} - \tspred^n_{T+i|T})^2\\
 SMAE &= \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,,\\
-SMSE &= \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,.
+SMSE &= \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}(\ts^n_{T+i} - \tspred^n_{T+i|T})^2\,.
 \end{align*}
-For each loss, 10 \textit{hermese-tbats-ws} models have been trained with different seeds and the final mean and standard deviation are given in Figure~\ref{}.
+For each loss, 10 \textit{hermes-tbats-ws} models have been trained with different seeds and the final mean and standard deviation are given in Figure~\ref{fig:loss_function}.
 The final Scaled Mean Absolute Error reaches the lowest MASE and was selected to train all the HERMES model in this paper.
@@
     \includegraphics[width=1.\linewidth]{figure/loss_function}
-  \caption{MASE accuray for the \textit{hermes-tbats-ws} model depending of the loss used during the RNN training.
+  \caption{MASE accuray for the \textit{hermes-tbats-ws} model depending on the loss used during the RNN training.
 For each loss, 10 models with different seeds have been trained.
@@
 \subsection{Parameters grid search on the M4 weekly Dataset}
-
-The HERMES model depends on several hyperparameters to set correctly in order to reach satisfactory performance.
-For instance, an overview of the learning rate, batch size and number of windows per time series grid search for the M4 weekly dataset is shown in Figure~\ref{}.
+\label{sec:m4gridsearch}
+
+In addition to the loss function, the HERMES model also depends on several hyperparameters to set correctly in order to reach satisfactory performance.
+For instance, an overview of the learning rate, batch size and number of windows per time series grid search for the M4 weekly dataset is shown in Figure~\ref{fig:m4parameter}.
 For each parameter, a collection of 10 \textit{hermes-tbats} models have been trained with a range of values and the final OWA was calculated.
-As in the Figure~\ref{fig:loss_function}, the mean and the standard deviation of each group of 10 trainings is displayed in Figure~\ref{}.
-For the final \textit{hermes-tbats} model of the M4 weekly dataset, the grid search fixed the following setup : 3 windows per time series, the batch size set to 8 and the learning rate equal to 0.005.
+As in the Figure~\ref{fig:loss_function}, the mean and the standard deviation of each group of 10 trainings is computed.
+For the final \textit{hermes-tbats} model of the M4 weekly dataset, the grid searchs fixed the following set of parameters : 3 windows per time series were used as the train set, the batch size was set to 8 and the learning rate was fixed to 0.005.
 
@@
 %\end{subfigure}
-\caption{Example of difference between the raw sequence and the normalized one.
-In this example, we normalize by the deseasonalized global top fashion trend for female in China.
-(Top) result of the HERMES model on the M4 dataset model depending of the number of windows provided per time series to the RNN corrector.
-(Middle) Result of the HERMES model on the M4 dataset model depending of the size of the batch size.
-(Bottom) Result of the HERMES model on the M4 dataset model depending of learning rate of the optimizer.}
+\caption{OWA for the \textit{hermes-tbats} model on the M4 weekly dataset depending on 3 parameters used during the RNN training: Number of moving windows per time series, the batch size and the learning rate.
+For each parameter, 10 models with different seeds have been trained.
+The mean and the standard deviation are represented with a point and a vertical.
+(Top) result of the HERMES model depending on the number of windows provided per time series to the RNN corrector.
+(Middle) Result of the HERMES model depending on the size of the batch size.
+(Bottom) Result of the HERMES model depending on the learning rate of the optimizer.}
 \label{fig:m4parameter}

### 2021-12-31 hermes_paper/hermes_ieee.tex
fix the z definition by adding a modulo

@@
 Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$.
-the RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$,
+the RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$, $1\leqslant i \leqslant w$ and $k = i - h\lfloor \frac{i}{h} \rfloor$
 $$
-\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+i \equiv h|T}}{\meants^n_T}\,,\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
+\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+k|T}}{\meants^n_T}\,,\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
 $$

### 2022-01-03 hermes_paper/hermes_ieee.tex
Final corrections

@@
 All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
-Each value represents the number of users posts in a week where vision algorithms detected the fashion trend on picture.
+Each value represents the number of users posts in a week where computer vision algorithms detected the fashion trend.
 As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization}.
@@
 
-Due to the increasing use of social media and users' change of behaviour, a normalization step is applied to the raw sequences.
+Due to the increasing use of social media and behaviour changes, a normalization step is applied to the raw sequences.
 Each fashion trend is divided by its hierarchical parent category trend.
@@
 An overview of it can be found in Table~\ref{tab:fashiondataset}.
-this collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry.
-For instance, some sequences show complex behaviours with sudden changes (emerging or declining trends).
+This collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry.
+For instance, some sequences show complex behaviours with sudden changes, referred to as emerging or declining trends.
 A central point of this work is to accurately detect and forecast such trends.
@@
 In theoretical fashion dynamics \cite{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
-In this way, a weak signal for each sequence is added to the proposed dataset.
-
+%In this way, a weak signal for each sequence is added to the proposed dataset.
 Numerous social media influencers were selectioned by hand by fashion experts.
@@
 \subsection{Training}
-The dataset is temporally split into three blocks, {\em train}, {\em eval} and {\em test} sets.
+The dataset is split into three blocks, {\em train}, {\em eval} and {\em test} sets.
 The 3 first years are used as the {\em train} set, the 4th year is kept for the {\em eval} set and the {\em test} set is made of the last year.
@@
 The final accuracy measures of all our models are computed on this {\em test} set.
-As an illustration, an example of our temporal split is shown in Figure~\ref{fig:train_eval_test_set}.
+As an illustration, an example of our split is shown in Figure~\ref{fig:train_eval_test_set}.
 
@@
 This choice of $\mathrm{L}_1$  loss function is motivated by its robustness to outliers which accounts for some time series in the fashion industry with very specific behaviors.
-The loss and previous parameters are all set with a grid search (additional materials can be found in Appendix).
+The loss and previous parameters are all set with a grid search (additional materials can be found in the Appendix).
 The code is developed in Python using the Tensorflow library.
@@
 In addition to the MASE accuracy metric, the different methods are also evaluated on a classification task and especially differences between methods using weak signals or not.
-In a given year, an increasing trend is defined as a trend that does more than 5\% of growth with respect to the previous year.
-In the same way, a decreasing trend is defined as a trend that declines by 5\% or more.
+In a given year, an increasing trend is defined as a trend that does more than 5\% of growth on average with respect to the previous year.
+In the same way, a decreasing trend is defined as a trend that declines by 5\% on average or more.
 Other trends are classified as flat trends.
@@
 Interestingly, weak signals significantly improve the accuracy in detecting emerging and declining trends.
-Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} model and some weaknesses that can be corrected.
+Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} models and some weaknesses that can be corrected.
 
@@
 For each metric, the average on all our time series is computed.
-For approaches using neural network, 10 models are trained with different seeds.
+For approaches using neural networks, 10 models are trained with different seeds.
 The mean and the standard deviation of the 10 results are displayed.}
@@
 First, the hybrid framework \textit{hermes-tbats} achieves the best performance in terms of global accuracy on both datasets.
-Due to the strength of its per-time-series predictor TBATS, the hybrid model succeeds at correcting some of TBATS weaknesses and logically reaches a satisfactory final accuracy.
+Due to the strength of its per-time-series predictor TBATS, the hybrid model succeeds at correcting TBATS  and reaches a satisfactory final accuracy.
 Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases.
@@
 Nevertheless, with the HERMES framework, the RNN task is largely simplified.
-Our model logically needs less data to be trained and to obtain interesting performance.
+Our model needs less data to be trained and to obtain interesting performance.
 
@@
 \textbf{Training.
-} The M4 dataset is firstly preprocessed in order to equalize all the sequences.
+} The M4 dataset is firstly preprocessed.
 This preliminary step is motivated by two reasons.
@@
 Second, the longer time series slow down the training of the collection of the first predictors especially for complex methods like TBATS.
-300 time steps are kept for each sequence in order to train the HERMES model.
+We kept 300 time steps  for each sequence in order to train the HERMES model.
 For the shorter sequences, the train set is duplicated in order to reach the length of 300.
-For the longer ones, they are cropped in order to keep the last 300 time steps.
+Longer sequences are cropped in order to keep the last 300 time steps.
 %The sequences are firstly resized in order to obatain a dataset with fixed time horizon.
@@
 
-The horizon $h$ is set to 13 due to the M4 weekly test set size and the window size $w$ is set to 104.
+The horizon $h$ is set to 13  and the window size $w$ is set to 104.
 For the RNN part, the same architecture as the one described in Figure~\ref{fig:rnn_architecture} is used.
@@
 As the M4 weekly dataset is small, a rolling window is used on the train set in order to increase the train number of examples and improve training results.
-3 windows are computed for each sequence for the RNN train set.
+Three windows are computed for each sequence for the RNN train set.
 An overview of our train, eval, test set split and the resizing of the shortest sequences is given in Figure~\ref{fig:m4dataset}.
@@
 As a HERMES candidate, a version using TBATS is proposed and called \textit{hermes-tbats}.
-Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measure.
+Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measures.
 A complete definition of these metrics is proposed in \cite{makridakis2020m4}, see also Appendix~\ref{sec:m4overview} for additional information about the M4 weekly dataset.
@@
 } The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}.
-Considering the HERMES approach, \textit{hermes-tbats} outperforms all the benchmarks.
+The HERMES approach \textit{hermes-tbats} outperforms all the benchmarks.
 This result is partially induced by the use of TBATS per-time-series predictors which achieves striking results on the test set.
@@
 With this second application, two important conclusions can be made.
-Firstly, the striking results of \textit{hermes-tbats} confirm that the HERMES framework is a general framework, well suited for a large collection of forecasting tasks.
+Firstly, the results provided by \textit{hermes-tbats} confirm that the HERMES approach is a general framework, well suited for a large collection of forecasting tasks.
 Secondly, the accuracy gap between the two hybrid candidates validates the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.
@@
 \label{sec:conclusion}
-The motivation of this paper was to present HERMES, a new hybird model for time series forecasting.
+The motivation of this paper was to present HERMES, a new hybird model for non stationary time series forecasting.
 By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks.
@@
 In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses.
-An interesting perspective is to add a latent discrete label to select dynamically the regime shifts, i.e.
-which corrector model to use on-the-fly.
+An interesting perspective is to add a latent discrete label to select dynamically the regime shifts.
 
@@
 The M4 weekly dataset is a collection of 359 time series with  contrasting behaviours and sizes.
-An overview of the dataset is given in Table~\ref{tab:m4dataset} and some example of sequences are given in Figure~\ref{fig:m4examples}.
-As sequences have not the same domain origin, the HERMES approach doesn't seem to be the best suited model for this forecasting task.
-However, on some examples as in Figure~\ref{fig:m4pred}, interesting corrections of the Tbats forecasts can be noted.
+An overview of the dataset is given in Table~\ref{tab:m4dataset} and some examples of sequences are given in Figure~\ref{fig:m4examples}.
+As sequences come from a wide diversity of sectors, the forecasting task is very challenging.
+However, on some examples as in Figure~\ref{fig:m4pred}, efficient corrections of the TBATS forecasts can be obtained.
 
@@
 \caption{Examples of time series from the M4 weekly dataset.
-From Top to Bottom : time series called \textit{W10} from the \textit{Other} category,\textit{W20} from the \textit{Macro} category, \textit{W220} from the \textit{Finance} category and \textit{W354} from the \textit{Micro} category}
+From Top to Bottom : time series called \textit{W10} from the \textit{Other} category, \textit{W20} from the \textit{Macro} category, \textit{W220} from the \textit{Finance} category and \textit{W354} from the \textit{Micro} category.}
 \label{fig:m4examples}
@@
 The remaining one is not an ensembling but a statistical framework called \textit{Forecast Pro}.
-It is not a single statistical model but a framework that chooses, depending on the sequence properties, the best statistical approach to forecast it.
+It is not a single statistical model but a framework that chooses, depending on the sequence properties, the best statistical approach.
 With a OWA equal to 0.739, it outperforms the \textit{hermer-tbats} and all the M4 proposed models on the M4 weekly sub-dataset.
 A description and interesting remarks about the \textit{Forecast Pro} model are discussed in \cite{DARIN2020135}.
-A promising research perspective can be to replace the TBATS per-time-series predictor by this model which seems more suited for the M4 weekly forecasting task.
+This model offers an interesting research perspective specifically for the M4 weekly forecasting task.
 
@@
 Second, a dataset can hide contrasting time series in terms of scale, noise and behaviour.
-These differences can impact the loss and finally the training.
+These differences can impact training performance.
 For the HERMES architecture, some candidate losses were defined for the training: the Mean Absolute Error (MAE), the Mean Square Error (MSE),  the Scaled Mean Absolute Error (SMAE) and the Scaled Mean Square Error (SMSE).
@@
 MAE &= \frac{1}{\lag}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,,\\
-MSE &= \frac{1}{\lag}\sum_{i=1}^{\lag}(\ts^n_{T+i} - \tspred^n_{T+i|T})^2\\
+MSE &= \frac{1}{\lag}\sum_{i=1}^{\lag}(\ts^n_{T+i} - \tspred^n_{T+i|T})^2\,,\\
 SMAE &= \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,,\\
@@
 As in the Figure~\ref{fig:loss_function}, the mean and the standard deviation of each group of 10 trainings is computed.
-For the final \textit{hermes-tbats} model of the M4 weekly dataset, the grid searchs fixed the following set of parameters : 3 windows per time series were used as the train set, the batch size was set to 8 and the learning rate was fixed to 0.005.
+For the final \textit{hermes-tbats} model of the M4 weekly dataset,  the following set of parameters was selected: 3 windows per time series were used as the train set, the batch size was set to 8 and the learning rate was fixed to 0.005.
 

### 2022-01-04 hermes_paper/hermes_ieee.tex
fix MASE formula and add a footprint

@@
 % Do not put math or special symbols in the title.
-\title{HERMES : Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}
+\title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}
 %
@@
 
-\author{Etienne David\thanks{Etienne David: Heuritech, France.}, Sylvain Le Corff\thanks{Sylvain Le Corff:  Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC, Institut Polytechnique de Paris, France.} and~ Jean Bellot\thanks{Jean Bellot: Heuritech, France.}}
+\author{Etienne David\thanks{Etienne David: Heuritech, France.}, Sylvain Le Corff\thanks{Sylvain Le Corff:  Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC, Institut Polytechnique de Paris, France.} and Jean Bellot\thanks{Jean Bellot: Heuritech, France.}}
 %        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
@@
 Our contribution is  twofold.
-We first provide publicly the first fashion dataset gathering \numberts\ weekly fashion time series.
+We first provide publicly\footnote[1]{lienversledataset} the first fashion dataset gathering \numberts\ weekly fashion time series.
 As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviors of influencers.
@@
 
-To compare the different methods, we use the Mean Absolute Scaled Error (MASE).
-As our time series have completely different scales, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, independent of the scale of the sequence.
-The MASE metric is defined as follows, with $m$ the seasonal periods:
+To compare the different methods, we use the Mean Absolute Scaled Error (MASE) for seasonal time series.
+As our sequences have completely different scales, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, independent of the scale of the sequence and suited for our seasonal fashion time series.
+The MASE metric is defined as follows, with $m$ the seasonal period:
 \begin{align*}
-\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,.
+\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{j=1}^h |Y_{T+j} - \hat{Y}_{T+j}| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,.
 \end{align*}
@@
 We believe that this dataset contains really fine dynamics and interactions where complex models would express their potential.
-By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
+By making it publicly available\footnotemark[1], we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
 As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.

### 2022-01-11 hermes_paper/hermes_ieee.tex
remove the Accuracy formula (confusing) and minor changes

@@
 
-\author{Etienne David\thanks{Etienne David: Heuritech, France.}, Sylvain Le Corff\thanks{Sylvain Le Corff:  Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC, Institut Polytechnique de Paris, France.} and Jean Bellot\thanks{Jean Bellot: Heuritech, France.}}
+\author{Etienne David\thanks{Etienne David: Heuritech, France.}, Jean Bellot\thanks{Jean Bellot: Heuritech, France.} and Sylvain Le Corff\thanks{Sylvain Le Corff:  Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC, Institut Polytechnique de Paris, France.}}
 %        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
@@
 Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$.
-the RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$, $1\leqslant i \leqslant w$ and $k = i - h\lfloor \frac{i}{h} \rfloor$
+The RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$, $1\leqslant i \leqslant w$ and $k = i - h\lfloor \frac{i}{h} \rfloor$
 $$
@@
     \includegraphics[width=1.\linewidth]{figure/train_eval_test_set}
-  \caption{Temporal split for our training process}
+  \caption{Temporal split for our training process. The three first years define our training set. The fourth year is used as our eval set and the final year is reserved for the test set.}
 \label{fig:train_eval_test_set}
@@
     \includegraphics[width=0.8\linewidth]{figure/lstm_archi}
-  \caption{$\classifier$ and $\predictor$ architecture.}
+  \caption{Architecture of the RNN corrector part of the HERMES framework. The same architecture is used in the \textit{lstm} benchmark model.}
 \label{fig:rnn_architecture}
@@
 With this threshold, the proposed fashion dataset is almost balanced on the {\em test} set: There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends.
-On the {\em test} set, for each method, the accuracy is defined as follows:
-\begin{align*}
-\mathrm{ACCURACY} &= \frac{TP}{TP + FP}\,,
-\end{align*}
-where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series misclassified in the class $i$.
+%On the {\em test} set, for each method, the accuracy is defined as follows:
+%\begin{align*}
+%\mathrm{ACCURACY} &= \frac{TP}{TP + FP}\,,
+%\end{align*}
+%where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series misclassified in the class $i$.
 
@@
   \begin{tabular}{l||lllll|lllll}
-   &&\multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{ACCURACY}}&\\
+   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
     &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
@@
      \textit{stlm} && 0.765 & - \\
-     \textit{lstm-nows} && 0.740 & 0.007 \\
+     \textit{lstm} && 0.740 & 0.007 \\
      \textit{tbats} && 0.734 & - \\
@@
      \textit{ets} && 0.785 & - \\
-     \textit{lstm-nows} && 0.767 & 0.045 \\
+     \textit{lstm} && 0.767 & 0.045 \\
      \textit{stlm} && 0.742 & - \\
@@
      \textit{Damped} && 8.866 && - &&& 2.404 && - &&& 0.917 && - &\\
-     \textit{Uber} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
+     \textit{S.Smyl} \cite{hyndman2020package} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
      \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.841 && - &\\
-     \textit{\textbf{hermer-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
+     \textit{\textbf{hermes-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
     %\hline
@@
 The mean and the standard deviation are represented with a point and a vertical.
-(Top) result of the HERMES model depending on the number of windows provided per time series to the RNN corrector.
+(Top) Result of the HERMES model depending on the number of windows provided per time series to the RNN corrector.
 (Middle) Result of the HERMES model depending on the size of the batch size.

### 2022-01-18 hermes_paper/hermes_ieee.tex
update the Forecast Pro part in appendex

@@
      \textit{arima} && 0.826 && -&&& 0.464 && - & \\
-     \textit{ets} && 0.805 && -&&& 0.449 && - & \\
+     \textit{ets} && 0.807 && -&&& 0.449 && - & \\
      \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
@@
 
-Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset.
+%Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset.
 Except one approach, all of them are a combination of different models in order to increase the robustness of the final forecast and at the same time achieve a better global accuracy.
@@
 This model offers an interesting research perspective specifically for the M4 weekly forecasting task.
+Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset.
+All of them are ensemble framework : a combination of different models in order to increase the robustness of the final forecast and the global accuracy.
+If this paper, only individual models were compared on the fashion dataset and on the M4 dataset.
+However, the HERMES framework, as any individual method, is perfectly suited to be include in an ensembling model like the FFORMA approach proposed in \cite{MONTEROMANSO202086}.
 

### 2022-01-18 hermes_paper/hermes_ieee.tex
update the m4 dataset appendix part

@@
 This model offers an interesting research perspective specifically for the M4 weekly forecasting task.
-Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset.
-All of them are ensemble framework : a combination of different models in order to increase the robustness of the final forecast and the global accuracy.
-If this paper, only individual models were compared on the fashion dataset and on the M4 dataset.
-However, the HERMES framework, as any individual method, is perfectly suited to be include in an ensembling model like the FFORMA approach proposed in \cite{MONTEROMANSO202086}.
+Looking at the final results of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset.
+All of them are ensemble frameworks: methods that mix different kinds of approaches to reach a higher final accuracy.
+As the M4 weekly dataset gathers really heterogeneous sequences, combining several methods to leverage their strengths appear to be a promising way.
+However in this paper, only individual models were evaluated in order to provide a fair comparison with the HERMES framework.
 

### 2022-01-19 hermes_paper/hermes_ieee.tex
Minor corrections in the introduction

@@
 
-\author{Etienne David\thanks{Etienne David: Heuritech, France.}, Jean Bellot\thanks{Jean Bellot: Heuritech, France.} and Sylvain Le Corff\thanks{Sylvain Le Corff:  Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC, Institut Polytechnique de Paris, France.}}
+\author{Etienne David\thanks{Etienne David: Heuritech, France.}, Jean Bellot\thanks{Jean Bellot: Heuritech, France.} and Sylvain Le Corff\thanks{Sylvain Le Corff:  Samovar, T\'el\'ecom SudParis, d\'epartement CITI, Institut Polytechnique de Paris, France.}}
 %        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
@@
  %Due to the diversity of applications and use cases, a multitude of models have been proposed. 
-Parametric generative models allow to provide explainable predictions with statistical guarantees based on a precise modeling of the predictive distributions of new data based on a record of past observations.
+Parametric generative models provide explainable predictions with statistical guarantees based on a precise modeling of the predictive distributions of new data based on a record of past observations.
 %The parameters of these models are usually estimated using a sequence of observations of the target time series.
@@
 Based on a cutting-edge image recognition technology, we built the first fashion dataset containing \numberts\ weekly sequences  of fashion trends on social media  from 01-01-2015 to 01-01-2019.
-This dataset has very appealing properties:  all time series have the same length, same seasonality, no missing value and there is no sparse time series even for niche trends.
+This dataset has very appealing properties:  all time series have the same length, no missing value and there is no sparse time series even for niche trends.
 The originality of our dataset comes from the fact that additional external weak signals can also be introduced.

### 2022-01-19 hermes_paper/hermes_paper.tex
Minor corrections in the introduction

@@
 Sylvain Le Corff \\
-Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC \\
+Samovar, T\'el\'ecom SudParis, d\'epartement CITI, \\
 Institut Polytechnique de Paris, Palaiseau \\
@@
  %Due to the diversity of applications and use cases, a multitude of models have been proposed. 
- Parametric generative models allow to provide explainable predictions with statistical guarantees based on a precise modeling of the predictive distributions of new data based on a record of past observations.
+ Parametric generative models provide explainable predictions with statistical guarantees based on a precise modeling of the predictive distributions of new data based on a record of past observations.
 %The parameters of these models are usually estimated using a sequence of observations of the target time series.
@@
 Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
-The exponential smoothing model \citep{RePEc:inm:oropre:v:9:y:1961:i:5:p:673-685}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \cite{doi:10.1198/jasa.2011.tm09771}, or the ARIMA with the Box-Jenkins approach \citep{box2015time} are for instance very popular parametric linear generative models.
+The exponential smoothing model \citep{RePEc:inm:oropre:v:9:y:1961:i:5:p:673-685}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \cite{doi:10.1198/jasa.2011.tm09771}, or the ARIMA with the Box-Jenkins approach \citep{box2015time} are for instance very popular parametric  models.
 Hidden Markov models (HMM) are also widespread and presuppose that available observations are defined using missing data describing the dynamical system.
@@
 Based on a cutting-edge image recognition technology, we built the first fashion dataset containing \numberts\ sequences representing the apparition of fashion trends on social media per week from 01-01-2015 to 01-01-2019.
-Our fashion time series has very appealing properties: they have all the same length, same seasonality, no missing value and the absence of sparse time series even for niche trends.
+Our fashion time series has very appealing properties: they have all the same length, no missing value and the absence of sparse time series even for niche trends.
 The originality of our dataset come from the fact that additional external weak signals can be introduced.
@@
 Recently, hybrid models combining deep neural network (DNN) architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \citep{zhang2003time,jianwei2019novel,bandara2020lstm}.
-The approach providing the most striking results was proposed in  \citep{smyl2020hybrid} in the context of the M4 forecasting competition \citep{makridakis2020m4}.
+The approach providing the most impressive results was proposed in  \citep{smyl2020hybrid} in the context of the M4 forecasting competition \citep{makridakis2020m4}.
 Given a large dataset, a per-time-series multiplicative exponential smoothing model is introduced to estimate simple but fundamental components for each time series and compute a first prediction.

### 2022-01-19 hermes_paper/hermes_ieee.tex
Minor corrections in Section 2

@@
 In Section~\ref{sec:exp}, two versions of our framework are proposed.
-The first one is based on an  exponential smoothing as a reference similar to the baseline \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
+The first one is based on an  exponential smoothing as a reference similar to the baseline \cite{smyl2020hybrid} and the second one uses a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
 
@@
 The difficulty is that the exact influence of external variables on the main signal is mostly unknown.
-It is on this point that  the new HERMES framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals.
-First forecast examples of this new hybrid model are given in Figure~\ref{fig:introexamples}.
+This motivates the introduction of a global RNN trained on all time series and able to consider and leverage external signals.
+First forecast examples of our new hybrid model are given in Figure~\ref{fig:introexamples}.
 
@@
 Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$.
-The RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$, $1\leqslant i \leqslant w$ and $k = i - h\lfloor \frac{i}{h} \rfloor$
+The RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$, $1\leqslant i \leqslant w$ and $k = i - h\lfloor i/h \rfloor$,
 $$
@@
 
-Using well-fitted time-series-specific parametric models, the new hybrid network corrects the first form of weakness and achieves striking accuracy on the provided fashion dataset, see Table~\ref{tab:metricresults}.
+Using well-fitted time-series-specific parametric models, the new hybrid network corrects the first form of weakness and provides very good performance on the fashion dataset, see Table~\ref{tab:metricresults}.
 Then, to correct the second form of weakness, in addition to the $N$ target time series, $K \times N$ external sequences indexed from $0$ to $T$ are considered.

### 2022-01-19 hermes_paper/hermes_ieee.tex
Minor corrections in Section 3

@@
 Each fashion trend is divided by its hierarchical parent category trend.
-Moreover, in order to not remove the seasonality of all sequences, we deseasonalized the hierarchical parent category trend before the normalization.
+Moreover, in order to avoid removing the seasonality of all sequences, we deseasonalized the hierarchical parent category trend before the normalization.
 For instance, as displayed in Figure~\ref{fig:normalization}, the raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.

### 2022-01-19 hermes_paper/hermes_ieee.tex
Minor modifications in Section 4

@@
 With the resulting collection of local models, a forecast of the third year is computed for each sequence.
-Corrector inputs are finally computed and the RNN is trained at correcting weaknesses of this first collection of third-year forecasts.
+Corrector inputs are finally computed and the RNN is trained at correcting this first collection of third-year forecasts.
 For the {\em eval} set, per-time-series predictors are fitted a second time using the three first years and forecasts of the fourth year are computed.
-The {\em eval} set is used during the training to control the learning of the RNN model and prevent overfitting.
+The {\em eval} set is used during  training to control the learning of the RNN model and prevent overfitting.
 The per-time-series predictors are fitted a last time for the {\em test} set using the four first years.
@@
 It is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
-A classical Adam optimizer is used with a learning rate set at 0.001 or 0.005, the batch size is fixed 64 and the loss function is defined as follows:
+A classical Adam optimizer is used with a learning rate set at 0.001 or 0.005, the batch size is fixed to 64 and the loss function is defined as follows:
 $$
@@
 This choice of $\mathrm{L}_1$  loss function is motivated by its robustness to outliers which accounts for some time series in the fashion industry with very specific behaviors.
-The loss and previous parameters are all set with a grid search (additional materials can be found in the Appendix).
+The loss and previous parameters are all set with a grid search (additional materials can be found in Appendix~B).
 The code is developed in Python using the Tensorflow library.
@@
 The \textit{hermes-tbats} model divides by 3 the error rate in comparison to \textit{tbats} with only a slight decrease of the number of correct increase/decrease predictions.
-However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of impactful errors.
+However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signals while keeping a relatively low number of impactful errors.
 
@@
 An overview of our train, eval, test set split and the resizing of the shortest sequences is given in Figure~\ref{fig:m4dataset}.
-The previous parameters: window size, learning rate, batch size and the number of train windows per time series are set using a grid search, see Appendix~\ref{sec:m4gridsearch}.
+The previous parameters: window size, learning rate, batch size and the number of train windows per time series are set using a grid search, see Appendix~B.
 
@@
 The HERMES approach \textit{hermes-tbats} outperforms all the benchmarks.
-This result is partially induced by the use of TBATS per-time-series predictors which achieves striking results on the test set.
+This result is partially induced by the use of TBATS per-time-series predictors which achieves very good results on the test set.
 Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}.

### 2022-01-22 hermes_paper/hermes_ieee.tex
Minor modifications in Section 5
add the fashion dataset link

@@
 Our contribution is  twofold.
-We first provide publicly\footnote[1]{lienversledataset} the first fashion dataset gathering \numberts\ weekly fashion time series.
+We first provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} the first fashion dataset gathering \numberts\ weekly fashion time series.
 As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviors of influencers.
@@
 We believe that this dataset contains really fine dynamics and interactions where complex models would express their potential.
-By making it publicly available\footnotemark[1], we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
+By making it publicly available\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}}, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
 As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.
@@
 In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses.
-An interesting perspective is to add a latent discrete label to select dynamically the regime shifts.
+A perspective is to add a latent discrete label to select dynamically the regime shifts.
 

### 2022-02-07 hal_arxiv/hermes_paper.tex
Add the HAL/arxiv version

--- 2022-01-22 hermes_paper/hermes_ieee.tex
@@
-%% bare_jrnl.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
+\documentclass[nolayout]{article}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\usepackage{authblk}
+\usepackage{amssymb,amsmath,amsthm}
+\usepackage[pdftex]{graphicx}
+\usepackage{footnote}
+\usepackage{url}
+\usepackage{times,dsfont}
+\usepackage{fancyhdr}
+\usepackage{geometry}
+\pagestyle{fancy}
 
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE!
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
+\title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}
+\date{}
 
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
+\author[$\dag$,*]{\'Etienne David}
+\author[*]{Jean Bellot}
+\author[$\dag$]{Sylvain Le Corff}
 
-\documentclass[lettersize,journal]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
+\affil[*]{{\small  Samovar, T\'el\'ecom SudParis,  D\'epartement CITI, Institut Polytechnique de Paris, France.}}
+\affil[*]{{\small Heuritech, Paris, France.}}
 
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
+\lhead{\'Etienne David, Jean Bellot, Sylvain Le Corff}
+\rhead{Nonparametric general translation HMM}
 
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\usepackage[pdftex]{graphicx}
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at:
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-\usepackage{amsmath,amssymb}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-\ifCLASSOPTIONcompsoc
- \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-\else
- \usepackage[caption=false,font=footnotesize]{subfig}
-\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and
-% Axel Sommerfeldt. This package may be useful when used in conjunction with
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-\usepackage{booktabs}
-\usepackage{url,xcolor}
-
-\input{math_commands.tex}
 \newcommand{\fix}{\marginpar{FIX}}
@@
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
 
-\author{Etienne David\thanks{Etienne David: Heuritech, France.}, Jean Bellot\thanks{Jean Bellot: Heuritech, France.} and Sylvain Le Corff\thanks{Sylvain Le Corff:  Samovar, T\'el\'ecom SudParis, d\'epartement CITI, Institut Polytechnique de Paris, France.}}
-%        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
-%\thanks{M. Shell was with the Department
-%of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
-%GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
-%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
-%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
-
-% note the % following the last \IEEEmembership and also \thanks -
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-%
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
-
-% The paper headers
-%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
-
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-%
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
 \maketitle
 
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
 \begin{abstract}
@@
 Our contribution is  twofold.
-We first provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} the first fashion dataset gathering \numberts\ weekly fashion time series.
+We first provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}}\footnote[2]{\url{https://github.com/etidav/f1fashiondataset}} the first fashion dataset gathering \numberts\ weekly fashion time series.
 As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviors of influencers.
@@
 
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-Hybrid models, Recurrent neural networks, Time series.
-\end{IEEEkeywords}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
+{\bf Keywords:} Hybrid models, Recurrent neural networks, Time series.
 
@@
 Multivariate time series forecasting is a widespread statistical problem with  many applications, see for instance \cite{sarkka2013bayesian, douc2014nonlinear, zucchini2017hidden} and the numerous references therein.
- %Due to the diversity of applications and use cases, a multitude of models have been proposed. 
 Parametric generative models provide explainable predictions with statistical guarantees based on a precise modeling of the predictive distributions of new data based on a record of past observations.
-%The parameters of these models are usually estimated using a sequence of observations of the target time series.
 Calibrating these models, for instance using maximum likelihood inference, often requires a fair amount of tuning to design a time series-specific model to provide  accurate forecasts and sharp confidence intervals.
@@
 Although hidden states are modeled as a Markov chain, the observations arising therefrom have a complex statistical structure.
-%Introducing latent hidden states, they assume that the predictive distribution is not unique and constant in time but multiple and lead by the values of the hidden states changing during time.
 In various applications where signals exhibit non-stationarities such as trends and seasonality, classical HMM are not adapted.
@@
 \centering
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=\linewidth]{figure/us_female_shoes}
-  %\caption{Time series representing a shoes fashion trend for female in The United States.}
- % \label{fig:introexamples:sub1}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
-  %\centering
-  \includegraphics[width=\linewidth]{figure/br_female_texture_verticalstripe}
- % \caption{Time series representing the vertical stipes texture fashion trend for female in Brazil.}
-  %\label{fig:introexamples:sub2}
-%\end{subfigure}
+  \includegraphics[width=\linewidth]{us_female_shoes}
+  \includegraphics[width=\linewidth]{br_female_texture_verticalstripe}
 \caption{Hermes forecast examples.
@@
 Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ the final prediction becomes:
-%$$
-%\tspred^n_{T+i|T} 
-%= \etspred^{ets,n}_{T+i|T} +  \rnnmodel(\fullconcatinput^n_T)_{T+i} \times \meants^n_T
-%$$
 \begin{align}
@@
 \centering
-    \includegraphics[width=1\linewidth]{figure/HERMES_archi.png}
+\includegraphics[width=1\textwidth]{HERMES_archi.png}
 \caption{Architecture of the hybrid model with weak signals.}
@@
 \centering
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/cn_female_top_raw}
-%  \caption{Time series representing the raw signal of a top fashion trend for female in China}
- % \label{fig:normalization:sub1}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/cn_female_top_norm}
-  %\caption{Time series representing the normalized signal of a top fashion trend for female in China.}
-  %\label{fig:normalization:sub2}
-%\end{subfigure}
+  \includegraphics[width=1.\linewidth]{cn_female_top_raw}
+  \includegraphics[width=1.\linewidth]{cn_female_top_norm}
 \caption{Example of difference between the raw sequence and the normalized one.
@@
   \begin{tabular}{l||lllllllll}
-    %hline
     \\
@@
      \\
-     %\hline
      \textbf{Total} & 2078/1078 & 700/564 & 239/130 & 142/- & 118/- & 985/772 & 1528/396 & 214/216 & 459/381\\
-    %\hline
   \end{tabular}
@@
 In theoretical fashion dynamics \cite{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
-%In this way, a weak signal for each sequence is added to the proposed dataset.
 Numerous social media influencers were selectioned by hand by fashion experts.
@@
 
-%Secondly, depending of the number of followers, the general panel of users is divided in three sub-groups: users with less than 1350 followers, users with a number of followers between 1350 and 7000 and users with more than 7000 followers.
-Repeating the previous methodology on each sub-panel, three normalized time series for each time series are created.
-Again, the motivation here is to detect behaviour gaps between different parts of the society that could lead to changes in the main signal.
-Let $\ts_t^{\ell,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{\ell,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences.
-Two inputs for our hybrid model are computed: for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
-%\begin{align*}
-%\ws^{\ell,n}_{t} = \frac{\ts_t^{\ell,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}
-%\end{align*}  
-%values close to 0.3 indicate a similar behaviour between the three sub-panels and the general panel.
-%
-%In addition to the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{\ell}$ and $\ws^{h}$ are added.
-They are frequently sparse for micro trends and they often lack interest in common fashion trends.
-However, in several examples, they are fundamental to detect the future fashion evolutions, as illustrated in Section~\ref{sec:exp}.
-
 \begin{figure*}
   \centering
-    \includegraphics[width=1.\linewidth]{figure/ff_example}
+    \includegraphics[width=1.\linewidth]{ff_example}
   \caption{A shoes trend of the fashion dataset.
@@
   \centering
-    \includegraphics[width=1.\linewidth]{figure/train_eval_test_set}
+    \includegraphics[width=1.\linewidth]{train_eval_test_set}
   \caption{Temporal split for our training process. The three first years define our training set. The fourth year is used as our eval set and the final year is reserved for the test set.}
@@
   \centering
-    \includegraphics[width=0.8\linewidth]{figure/lstm_archi}
+    \includegraphics[width=0.8\linewidth]{lstm_archi}
   \caption{Architecture of the RNN corrector part of the HERMES framework. The same architecture is used in the \textit{lstm} benchmark model.}
@@
 With this threshold, the proposed fashion dataset is almost balanced on the {\em test} set: There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends.
-%On the {\em test} set, for each method, the accuracy is defined as follows:
-%\begin{align*}
-%\mathrm{ACCURACY} &= \frac{TP}{TP + FP}\,,
-%\end{align*}
-%where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series misclassified in the class $i$.
 
@@
   \centering
-%  \resizebox{0.85\textwidth}{!}{%
   \begin{tabular}{l||lllll|lllll}
@@
     &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
-%    \hline
 	 \hline
@@
      \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& \textbf{0.510} && 0.005 &\\
-    %\hline
   \end{tabular}
-%  }
 \label{tab:metricresults}
@@
 \centering
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/us_female_top}
-  %\caption{Time series representing a top fashion trend for female in The United States}
-  %\label{fig:examples:sub1}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/cn_female_texture_horizontalstripe}
-  %\caption{Time series representing the horizontal stipes texture fashion trend for female in China}
-  %\label{fig:examples:sub2}
-%\end{subfigure}
+  \includegraphics[width=1.\linewidth]{us_female_top}
+  \includegraphics[width=1.\linewidth]{cn_female_texture_horizontalstripe}
 \caption{\textit{hermes-tbats} forecast examples.
@@
   \caption{\textit{tbats}, \textit{hermes-tbats} and \textit{hermes-tbats-ws} models confusion matrix }
-  %\vspace{0.2cm}
-  %\textit{tbats} model confusion matrix \\
-  %\par \textit{tbats} model confusion matrix
-  %\vspace{0.2cm}
 \centering
@@
   \end{tabular}
-
-\vspace{.2cm}
-
+\quad
   \begin{tabular}{l||llll}
@@
   \centering
-% \resizebox{0.85\textwidth}{!}{ 
+  \vspace{0.5cm}
   \begin{tabular}{l||llll}
@@
     &&  \textit{mean}  & \textit{std}  \\
-%    \hline
 	 \hline
@@
     &&  \textit{mean}  & \textit{std}  \\
-%    \hline
 	\hline
@@
   \end{tabular}
-%  }
 \label{tab:1000metricresults}
@@
 Longer sequences are cropped in order to keep the last 300 time steps.
-%The sequences are firstly resized in order to obatain a dataset with fixed time horizon.
-The eval and the test sets are removed for the shortest sequences (the last 26 steps).
-Then, the remaining number of entire year is duplicated in order to egalize all the sequence at the longest one : 2610 time steps \textcolor{red}{Pas sur de comprendre, reformuler}.
-As per time series parametric model training time depends on the sequence length, all time series are then croped.
-Finally, with the addition of the previously removed eval and test sets, 300 time steps are kept for each sequence \textcolor{red}{Pas sur de comprendre, reformuler}.
 
@@
   \centering
-    \includegraphics[width=1.\linewidth]{figure/M4_dataset}
+    \includegraphics[width=1.\linewidth]{M4_dataset}
   \caption{One of the shortest sequences of the M4 weekly dataset (93 time steps).
@@
   \centering
- % \resizebox{0.85\textwidth}{!}{%
   \begin{tabular}{l||lllll|lllll|lllll}
@@
     &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}&&&  \textit{mean}  && \textit{std}& \\
-%    \hline
 	 \hline
@@
      \textit{\textbf{hermes-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
-    %\hline
   \end{tabular}
-%  }
 \label{tab:m4metricresults}
@@
 We believe that this dataset contains really fine dynamics and interactions where complex models would express their potential.
-By making it publicly available\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}}, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
+By making it publicly available\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}}\footnote[2]{\url{https://github.com/etidav/f1fashiondataset}}, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
 As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.
@@
 
-\appendices
+\bibliographystyle{apalike}
+\bibliography{biblio}
 
-%\renewcommand{\thetable}{A\arabic{table}}
-%\renewcommand{\thefigure}{A\arabic{figure}}
-%\setcounter{table}{0}
-%\setcounter{figure}{0}
-
+\appendix
 \section{M4 weekly dataset and results}
@@
   \begin{tabular}{l||lll}
-    %hline
     \\
@@
 \begin{figure}
-%\centering
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W10}
-%  \caption{A time series from the ``Other`` category called \textit{W10}.}
-  \label{fig:m4examples:sub1}
-%\end{subfigure} \quad
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W20}
-%  \caption{A time series from the ``Macro`` category called \textit{W20}.}
-%  \label{fig:m4examples:sub1}
-%\end{subfigure}
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W220}
-%  \caption{A time series from the \textit{Finance} category called \textit{W220}.}
-%  \label{fig:m4examples:sub2}
-%\end{subfigure}\quad
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W354}
-%  \caption{A time series from the \textit{Micro} category called \textit{W354}.}
-%  \label{fig:m4examples:sub3}
-%\end{subfigure}
+  \includegraphics[width=.5\textwidth]{W10}
+  \includegraphics[width=.5\textwidth]{W20}
+  \includegraphics[width=0.5\textwidth]{W220}
+  \includegraphics[width=0.5\textwidth]{W354}
 \caption{Examples of time series from the M4 weekly dataset.
-From Top to Bottom : time series called \textit{W10} from the \textit{Other} category, \textit{W20} from the \textit{Macro} category, \textit{W220} from the \textit{Finance} category and \textit{W354} from the \textit{Micro} category.}
+From Top to Bottom, Left to Right : time series called \textit{W10} from the \textit{Other} category, \textit{W20} from the \textit{Macro} category, \textit{W220} from the \textit{Finance} category and \textit{W354} from the \textit{Micro} category.}
 \label{fig:m4examples}
@@
 \centering
-% \begin{subfigure}{1.\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W133_pred}
-%  \caption{\textit{tbats} and \textit{hermes-tbats} forecast of the \textit{W133} time series}
-%  \label{fig:m4pred:sub1}
-% \end{subfigure}
-% \begin{subfigure}{1.\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W314_pred}
-%  \caption{\textit{tbats} and \textit{hermes-tbats} forecast of the \textit{W314} time series}
-%  \label{fig:m4pred:sub2}
-% \end{subfigure}
+  \includegraphics[width=1.\linewidth]{W133_pred}
+  \includegraphics[width=1.\linewidth]{W314_pred}
 \caption{\textit{hermes-tbats} forecast examples on the M4 weekly dataset.
@@
 
-%Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset.
-Except one approach, all of them are a combination of different models in order to increase the robustness of the final forecast and at the same time achieve a better global accuracy.
-The remaining one is not an ensembling but a statistical framework called \textit{Forecast Pro}.
-It is not a single statistical model but a framework that chooses, depending on the sequence properties, the best statistical approach.
-With a OWA equal to 0.739, it outperforms the \textit{hermer-tbats} and all the M4 proposed models on the M4 weekly sub-dataset.
-A description and interesting remarks about the \textit{Forecast Pro} model are discussed in \cite{DARIN2020135}.
-This model offers an interesting research perspective specifically for the M4 weekly forecasting task.
 Looking at the final results of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset.
@@
   \centering
-    \includegraphics[width=1.\linewidth]{figure/loss_function}
+    \includegraphics[width=1.\linewidth]{loss_function}
   \caption{MASE accuray for the \textit{hermes-tbats-ws} model depending on the loss used during the RNN training.
@@
 \centering
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/m4_nb_of_window}
-  %\caption{result of the HERMES model on the M4 dataset model depending of the number of windows provided per time series to the RNN corrector}
- % \label{fig:m4parameter:sub1}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/m4_batch_size}
-  %\caption{result of the HERMES model on the M4 dataset model depending of the size of the batch size}
-  %\label{fig:m4parameter:sub2}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
-  %\centering
-  \includegraphics[width=1.\linewidth]{figure/m4_learning_rate}
-  %\caption{result of the HERMES model on the M4 dataset model depending of learning rate of the optimizer}
-  %\label{fig:m4parameter:sub3}
-%\end{subfigure}
+  \includegraphics[width=1.\linewidth]{m4_nb_of_window}
+  \includegraphics[width=1.\linewidth]{m4_batch_size}
+  \includegraphics[width=1.\linewidth]{m4_learning_rate}
 \caption{OWA for the \textit{hermes-tbats} model on the M4 weekly dataset depending on 3 parameters used during the RNN training: Number of moving windows per time series, the batch size and the learning rate.
@@
 
-% use section* for acknowledgment
-%\section*{Acknowledgment}
-%
-%
-%The authors would like to thank...
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-% \ifCLASSOPTIONcaptionsoff
-%   \newpage
-% \fi
-\newpage
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{hermes_paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%\begin{thebibliography}{1}
-%
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-%
-%\end{thebibliography}
-
-% biography section
-%
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-%\begin{IEEEbiography}{Michael Shell}
-%Biography text here.
-%\end{IEEEbiography}
-
-% if you will not have a photo at all:
-%\begin{IEEEbiographynophoto}{John Doe}
-%Biography text here.
-%\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-%\begin{IEEEbiographynophoto}{Jane Doe}
-%Biography text here.
-%\end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
 \end{document}

### 2022-03-14 signal_processing_elsevier/hermes_paper_elsevier.tex
Add signal processing eslevier paper

--- 2022-01-22 hermes_paper/hermes_ieee.tex
@@
-%% bare_jrnl.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE!
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-\documentclass[lettersize,journal]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\usepackage[pdftex]{graphicx}
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at:
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-\usepackage{amsmath,amssymb}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-\ifCLASSOPTIONcompsoc
- \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-\else
- \usepackage[caption=false,font=footnotesize]{subfig}
-\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and
-% Axel Sommerfeldt. This package may be useful when used in conjunction with
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-\usepackage{booktabs}
-\usepackage{url,xcolor}
-
-\input{math_commands.tex}
-\newcommand{\fix}{\marginpar{FIX}}
-\newcommand{\new}{\marginpar{NEW}}
+\documentclass[review]{elsarticle}
+
+\usepackage{lineno,hyperref}
+%\usepackage[utf8]{inputenc}
+%\usepackage[english]{babel}
+%\usepackage{authblk}
+\usepackage{amssymb,amsmath,amsthm}
+%\usepackage[pdftex]{graphicx}
+%\usepackage{footnote}
+%\usepackage{url}
+%\usepackage{times,dsfont}
+%\usepackage{fancyhdr}
+%\usepackage{geometry}
+%\pagestyle{fancy}
+\modulolinenumbers[5]
+
+\journal{Journal of \LaTeX\ Templates}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%% Elsevier bibliography styles
+%%%%%%%%%%%%%%%%%%%%%%%
+%% To change the style, put a % in front of the second line of the current style and
+%% remove the % from the second line of the style you would like to use.
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Numbered
+\bibliographystyle{model1-num-names}
+
+%% Numbered without titles
+%\bibliographystyle{model1a-num-names}
+
+%% Harvard
+%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
+%% Vancouver numbered
+%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+
+%% Vancouver name/year
+%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+
+%% APA style
+%\bibliographystyle{model5-names}\biboptions{authoryear}
+
+%% AMA style
+%\usepackage{numcompress}\bibliographystyle{model6-num-names}
+
+%% `Elsevier LaTeX' style
+%\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
+
+\begin{frontmatter}
+
 \title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-
-\author{Etienne David\thanks{Etienne David: Heuritech, France.}, Jean Bellot\thanks{Jean Bellot: Heuritech, France.} and Sylvain Le Corff\thanks{Sylvain Le Corff:  Samovar, T\'el\'ecom SudParis, d\'epartement CITI, Institut Polytechnique de Paris, France.}}
-%        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
-%\thanks{M. Shell was with the Department
-%of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
-%GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
-%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
-%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
-
-% note the % following the last \IEEEmembership and also \thanks -
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-%
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
-
-% The paper headers
-%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
-
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-%
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
+%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
+
+%% Group authors per affiliation:
+\author[mymainaddress,mysecondaryaddress]{Etienne DAVID}
+
+%% or include affiliations in footnotes:
+\author[mysecondaryaddress]{Jean BELLOT}
+
+\author[mymainaddress]{Sylvain LE CORFF}
+
+\address[mymainaddress]{\small  Samovar, T\'el\'ecom SudParis,  D\'epartement CITI, Institut Polytechnique de Paris, France.}
+\address[mysecondaryaddress]{Heuritech, 71 Rue Réaumur, 75002 Paris, France.}
+
 \begin{abstract}
-Developing models and algorithms to draw causal inference for time series is a long standing statistical problem.
+TDeveloping models and algorithms to draw causal inference for time series is a long standing statistical problem.
 It is crucial for many applications, in particular for fashion or retail industries, to make optimal inventory decisions and avoid massive wastes.
@@
 
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
+\begin{keyword}
 Hybrid models, Recurrent neural networks, Time series.
-\end{IEEEkeywords}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
+\end{keyword}
+
+\end{frontmatter}
+
+\linenumbers
 
@@
   \centering
-  \resizebox{0.85\width}{!}{
+  \resizebox{0.65\width}{!}{
   \begin{tabular}{l||lllllllll}
@@
   \centering
- % \resizebox{0.85\textwidth}{!}{%
+  \resizebox{\textwidth}{!}{
   \begin{tabular}{l||lllll|lllll|lllll}
@@
   \end{tabular}
-%  }
+  }
 \label{tab:m4metricresults}
@@
 
-\appendices
+%\appendices
 
@@
 
-\section{M4 weekly dataset and results}
+\section*{Appendix A. M4 weekly dataset and results}
 \label{sec:m4overview}
@@
   \centering
-  \resizebox{1.\width}{!}{
+  \resizebox{0.8\width}{!}{
   \begin{tabular}{l||lll}
@@
 %  \centering
-  \includegraphics[width=1.\linewidth]{figure/W354}
+%  \includegraphics[width=1.\linewidth]{figure/W354}
 %  \caption{A time series from the \textit{Micro} category called \textit{W354}.}
@@
 \caption{Examples of time series from the M4 weekly dataset.
-From Top to Bottom : time series called \textit{W10} from the \textit{Other} category, \textit{W20} from the \textit{Macro} category, \textit{W220} from the \textit{Finance} category and \textit{W354} from the \textit{Micro} category.}
+From Top to Bottom : time series called \textit{W10} from the \textit{Other} category, \textit{W20} from the \textit{Macro} category and \textit{W220} from the \textit{Finance} category.}
 \label{fig:m4examples}
@@
 
-\section{Training parameters and loss}
+\section*{Appendix B. Training parameters and loss}
 
@@
 
-% use section* for acknowledgment
-%\section*{Acknowledgment}
-%
-%
-%The authors would like to thank...
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-% \ifCLASSOPTIONcaptionsoff
-%   \newpage
-% \fi
-\newpage
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{hermes_paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%\begin{thebibliography}{1}
-%
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-%
-%\end{thebibliography}
-
-% biography section
-%
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-%\begin{IEEEbiography}{Michael Shell}
-%Biography text here.
-%\end{IEEEbiography}
-
-% if you will not have a photo at all:
-%\begin{IEEEbiographynophoto}{John Doe}
-%Biography text here.
-%\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-%\begin{IEEEbiographynophoto}{Jane Doe}
-%Biography text here.
-%\end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
+\section*{References}
+
+\bibliography{hermes_paper_elsevier}
+
 \end{document}

### 2022-11-02 signal_processing_elsevier/submission_ijf/cover_letter.tex
add first ijf submission

\documentclass[1p]{elsarticle}

\pagenumbering{gobble}
\makeatletter
\def\ps@pprintTitle{%
  \let\@oddhead\@empty
  \let\@evenhead\@empty
  \def\@oddfoot{\reset@font\hfil\thepage\hfil}
  \let\@evenfoot\@oddfoot
}
\makeatother

%\usepackage{lineno,hyperref}
\usepackage{hyperref}
%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel}
%\usepackage{authblk}
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\usepackage[OT1]{fontenc}

\usepackage{amssymb,amsmath,amsthm}
%\usepackage[pdftex]{graphicx}
%\usepackage{footnote}
%\usepackage{url}
%\usepackage{times,dsfont}
%\usepackage{fancyhdr}
%\usepackage{geometry}
%\pagestyle{fancy}
%\modulolinenumbers[5]

%\journal{Journal of \LaTeX\ Templates}

\begin{document}

\begin{frontmatter}

\title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}

\author{Etienne DAVID}

%% or include affiliations in footnotes:
\author{Jean BELLOT}

\author{Sylvain LE CORFF} 
\end{frontmatter}

\vspace{0.5cm}
Dear Editors,\vspace{0.5cm}

Please find attached our manuscript ”HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series”, which we
would like to submit for publication as a research article in your journal Elsevier International Journal of Forecasting.

\medskip

The fashion industry has produced many complex time series with seasonalities, trends and influences. To date, it has never really been studied by the signal processing community because of the lack of relevant data. In this work, we  aim at tackling this limitation, by translating the history of fashion trends to time series and proposing a new forecasting model able to accurately forecast them. First, by tracking thousands of fashion trends on social media with state-of-the-art computer vision approaches, we create a first fashion dataset gathering 10000 weekly fashion time series. As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviors of influencers. Secondly, to leverage such a complex and rich dataset, we propose a new hybrid forecasting model. Our approach combines per-time-series parametric models with seasonal components and a global recurrent neural network to include sporadic external signals. This hybrid model provides state-of-the-art results on the proposed fashion dataset, on the weekly time series of the M4 competition, and illustrates the benefit of the contribution of external weak signals.

\medskip

We would like to emphasize that contrary to some recent new forecasting studies, the fashion dataset studied in this paper will be publicly provided\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} upon publication of this work.

\medskip

%Firstly, based on complexe vision algorithms, we are able to track hundreds of fashion items on pictures shared on social media and draw the history of thousands of fashion trends. As the fashion sphere is highly driven by influence dynamics, we also define external signal representing behaviours of social media influencers for each trends, we call them ”weak signals”. With this paper, we provide publicly a sample of 10000 fashion time series and their linked ”weak signals”. ii) Secondly, as the previous sequences hide complexe dynamics and external signals, we introduce a new hybrid framework to accurately forecast them. This hybrid model combines per-time-series parametric models with seasonal components and a global recurrent neural network to include sporadic external signals. Our apporach provides state-of-the-art results on the proposed fashion dataset and also on the weekly time series dataset of the M4 competition.

We are looking forward to hearing from you.

\medskip

\indent Sincerely.

\medskip

Etienne David.

\end{document}

### 2022-11-02 signal_processing_elsevier/submission_ijf/hermes_paper_LaTeX_source_files/hermes_paper_elsevier.tex
add first ijf submission

--- 2022-03-14 signal_processing_elsevier/hermes_paper_elsevier.tex
@@
 %% Numbered
-\bibliographystyle{model1-num-names}
+%\bibliographystyle{model1-num-names}
 
@@
 %% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
+\bibliographystyle{model5-names}\biboptions{authoryear}
 
@@
 \begin{abstract}
-TDeveloping models and algorithms to draw causal inference for time series is a long standing statistical problem.
+Developing models and algorithms to draw causal inference for time series is a long standing statistical problem.
 It is crucial for many applications, in particular for fashion or retail industries, to make optimal inventory decisions and avoid massive wastes.
@@
 This motivates the introduction of a global RNN trained on all time series and able to consider and leverage external signals.
-First forecast examples of our new hybrid model are given in Figure~\ref{fig:introexamples}.
+First forecast example of our new hybrid model is given in Figure~\ref{fig:introexamples}.
 
@@
  % \centering
-  \includegraphics[width=\linewidth]{figure/us_female_shoes}
+  %\includegraphics[width=\linewidth]{figure/us_female_shoes}
   %\caption{Time series representing a shoes fashion trend for female in The United States.}
@@
 In red the final forecast of our HERMES hybrid model.
-(Top) Time series representing a shoes fashion trend for females in The United States.
+Time series representing the vertical stipes texture fashion trend for females in Brazil.}%(Top) Time series representing a shoes fashion trend for females in The United States.
 (Bottom) Time series representing the vertical stipes texture fashion trend for females in Brazil.}
@@
 \begin{table}
-  \caption{\textit{tbats}, \textit{hermes-tbats} and \textit{hermes-tbats-ws} models confusion matrix }
+  \caption{\textit{tbats}, \textit{hermes-tbats} and \textit{hermes-tbats-ws} models confusion matrix}
   %\vspace{0.2cm}
@@
 \centering
+\vspace{0.2cm}
+\resizebox{6cm}{!}{
   \begin{tabular}{l||llll}
@@
   \end{tabular}
-
+}
 \vspace{.2cm}
-
+\resizebox{6cm}{!}{
   \begin{tabular}{l||llll}
@@
   \end{tabular}
+}
 \label{tab:tbatsclass}
@@
  \centering
-% \resizebox{0.85\textwidth}{!}{ 
+ \resizebox{1.\textwidth}{!}{ 
   \begin{tabular}{l||llll}
@@
      \textbf{\textit{hermes-tbats}} && \textbf{0.719} & 0.002 \\
-  \end{tabular}
-
+  \end{tabular}\hspace{1cm}
 \vspace{.2cm}
@@
   \end{tabular}
-%  }
+ }
 \label{tab:1000metricresults}

### 2022-11-02 signal_processing_elsevier/submission_ijf/hermes_paper_LaTeX_source_files_double_blind/hermes_paper_blind_manuscript.tex
add first ijf submission

--- 2022-11-02 signal_processing_elsevier/submission_ijf/hermes_paper_LaTeX_source_files/hermes_paper_elsevier.tex
@@
 %% Group authors per affiliation:
-\author[mymainaddress,mysecondaryaddress]{Etienne DAVID}
+%\author[mymainaddress,mysecondaryaddress]{Etienne DAVID}
 
 %% or include affiliations in footnotes:
-\author[mysecondaryaddress]{Jean BELLOT}
+%\author[mysecondaryaddress]{Jean BELLOT}
 
-\author[mymainaddress]{Sylvain LE CORFF}
+%\author[mymainaddress]{Sylvain LE CORFF}
 
-\address[mymainaddress]{\small  Samovar, T\'el\'ecom SudParis,  D\'epartement CITI, Institut Polytechnique de Paris, France.}
-\address[mysecondaryaddress]{Heuritech, 71 Rue Réaumur, 75002 Paris, France.}
+%\address[mymainaddress]{\small  Samovar, T\'el\'ecom SudParis,  D\'epartement CITI, Institut Polytechnique de Paris, France.}
+%\address[mysecondaryaddress]{Heuritech, 71 Rue Réaumur, 75002 Paris, France.}
 
@@
 Our contribution is  twofold.
-We first provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} the first fashion dataset gathering \numberts\ weekly fashion time series.
+We first provide publicly the first fashion dataset gathering \numberts\ weekly fashion time series.
 As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviors of influencers.
@@
 \end{frontmatter}
+\newpage
 
@@
 
-\subsection{Result for Heuritech Fashion dataset}
+\subsection{Result for the Fashion dataset}
 
-\textbf{10000 Heuritech Fashion time series global accuracy.
+\textbf{10000 Fashion time series global accuracy.
 }For the two metrics and for each model, we compute the average on all sequences in the final year.
@@
 
-\textbf{10000 Heuritech Fashion time series classification task.
+\textbf{10000 Fashion time series classification task.
 } Classification results between the \textit{tbats} model and the hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impressive decrease of impactful errors: i.e.
@@
 We believe that this dataset contains really fine dynamics and interactions where complex models would express their potential.
-By making it publicly available\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}}, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
+By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
 As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.
@@
 \subsection{Loss grid search on the Fashion Dataset}
-\label{sec:heuritechgridsearch}
+\label{sec:gridsearch}
 

### 2022-11-02 signal_processing_elsevier/submission_ijf/hermes_paper_LaTeX_source_files_double_blind/hermes_paper_first_page.tex
add first ijf submission

--- 2022-11-02 signal_processing_elsevier/submission_ijf/hermes_paper_LaTeX_source_files/hermes_paper_elsevier.tex
@@
 %% Group authors per affiliation:
-\author[mymainaddress,mysecondaryaddress]{Etienne DAVID}
+\author[mymainaddress,mysecondaryaddress]{Etienne DAVID \corref{mycorrespondingauthor}}
+\cortext[mycorrespondingauthor]{Corresponding author}
+\ead{etienne.david@heuritech.com}
 
@@
 
-\address[mymainaddress]{\small  Samovar, T\'el\'ecom SudParis,  D\'epartement CITI, Institut Polytechnique de Paris, France.}
-\address[mysecondaryaddress]{Heuritech, 71 Rue Réaumur, 75002 Paris, France.}
+\address[mymainaddress]{\small  Samovar, T\'el\'ecom SudParis,  D\'epartement CITI, Institut Polytechnique de Paris, 9 rue Charles Fourier, 91011 EVRY, France.}
+\address[mysecondaryaddress]{Heuritech, 71 Rue Réaumur, 75002 PARIS, France.}
 
@@
 Our approach combines per-time-series parametric models with seasonal components and a global recurrent neural network to include sporadic external signals.
-This hybrid model provides state-of-the-art results on the proposed fashion dataset, on the weekly time series of the M4 competition \cite{makridakis2018m4}, and illustrates the benefit of the contribution of external weak signals.
+This hybrid model provides state-of-the-art results on the proposed fashion dataset, on the weekly time series of the M4 competition, and illustrates the benefit of the contribution of external weak signals.
 \end{abstract}
@@
 
-\linenumbers
-
-\section{Introduction}
-\label{sec:introduction}
-
-Multivariate time series forecasting is a widespread statistical problem with  many applications, see for instance \cite{sarkka2013bayesian, douc2014nonlinear, zucchini2017hidden} and the numerous references therein.
- %Due to the diversity of applications and use cases, a multitude of models have been proposed. 
-Parametric generative models provide explainable predictions with statistical guarantees based on a precise modeling of the predictive distributions of new data based on a record of past observations.
-%The parameters of these models are usually estimated using a sequence of observations of the target time series.
-Calibrating these models, for instance using maximum likelihood inference, often requires a fair amount of tuning to design a time series-specific model to provide  accurate forecasts and sharp confidence intervals.
-Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
-The exponential smoothing model \cite{RePEc:inm:oropre:v:9:y:1961:i:5:p:673-685}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \cite{doi:10.1198/jasa.2011.tm09771}, or the ARIMA with the Box-Jenkins approach \cite{box2015time} are for instance very popular parametric generative models.
-Hidden Markov models (HMM) are also widespread and presuppose that available observations are defined using missing data describing the dynamical system.
-This hidden state is assumed to be a Markov chain such that at each time step the received observation is a random function of the corresponding latent data.
-Although hidden states are modeled as a Markov chain, the observations arising therefrom have a complex statistical structure.
-%Introducing latent hidden states, they assume that the predictive distribution is not unique and constant in time but multiple and lead by the values of the hidden states changing during time.
-In various applications where signals exhibit non-stationarities such as trends and seasonality, classical HMM are not adapted.
-However, \cite{touron2017modeling}  recently proposed seasonal HMM, assuming that transition probabilities between the states, as well as the emission distributions, are not constant in time but evolve in a periodic manner.
-Strong consistency results were established in \cite{touron2019consistency} and Expectation Maximization based numerical experiments were proposed.
-Although these works provide promising results, HMM are computationally expensive to train and are not yet well studied for seasonal  sequences with thousands of components.
-
-In many fields, single or few time series have become thousands of sequences with various statistical properties.
-In this new context, classical time series specific statistical models show limitations when dealing with numerous heterogeneous data.
-Recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \cite{ hochreiter1997long,vaswani2017attention, 8614252, li2019enhancing, lim2019temporal,salinas2020deepar}.
-The DeepAR model proposed in \cite{salinas2020deepar} provides a global model from many time series based on a multi-layer recurrent neural network with LSTM cells.
-More recently, applications using the Transformer model have been proposed  \cite{li2019enhancing}.
-The Temporal Fusion Transformers (TFT) approach is a direct alternative to the DeepAR model \cite{lim2019temporal}.
-Unfortunately, all these solutions suffer from two main weaknesses.
-Firstly, many of them are black-boxes  as the final forecast usually does not come with a statistical guarantee  although a few recent works focused on measuring uncertainty in recurrent neural networks, see  \cite{martin2020monte}.
-Secondly, without a fine preprocessing and well chosen hyper-parameters, these methods may lead to poor results and be outperformed by traditional statistical models, see \cite{makridakis2018m4}.
-
-In this paper, we consider a  new time series forecasting application referred to as {\em fashion trends prediction}.
-Based on a cutting-edge image recognition technology, we built the first fashion dataset containing \numberts\ weekly sequences  of fashion trends on social media  from 01-01-2015 to 01-01-2019.
-This dataset has very appealing properties:  all time series have the same length, no missing value and there is no sparse time series even for niche trends.
-The originality of our dataset comes from the fact that additional external weak signals can also be introduced.
-With our fashion expertise, we detected several groups of highly influential fashion users.
-Analyzing their specific behaviours on social media, we associate with each time series an external weak signal representing the same fashion trends on a sub-category of users.
-They are called weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal.
-With this totally new application, we aim at designing a model able to deal with such a large dataset, leveraging  complex external weak signals and finally providing the most accurate forecasts.
-
-Recurrent neural networks are appealing to tackle our forecasting problem due to their capability of leveraging external data.
-Recently, hybrid models combining deep neural network (DNN) architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \cite{zhang2003time,jianwei2019novel,bandara2020lstm}.
-The approach providing the most striking results was proposed in  \cite{smyl2020hybrid} in the context of the M4 forecasting competition \cite{makridakis2020m4}.
-Given a large dataset, a per-time-series multiplicative exponential smoothing model was introduced to estimate simple but fundamental components for each time series and compute a first prediction.
-Then a global recurrent neural network was trained on the entire dataset to correct errors of the previous exponential smoothing models.
-
-Following this work, we present in this paper HERMES, a new hybrid recurrent model for time series forecasting with inclusion of external signals.
-This new architecture is decomposed  into two parts: local predictors and a global corrector.
-First, a per-time-series parametric statistical model is trained on each sequence.
-Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.
-The external weak signals reveal the real potential of the hybrid approach: a global neural network, able to leverage large amounts of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.
-
-The paper is organized as follows.
-Section~\ref{sec:hybrid} introduces the proposed hybrid model.
-Then, the new fashion dataset provided with this article is presented in Section~\ref{sec:dataset}.
-Section~\ref{sec:exp} describes the HERMES results and comparisons with several benchmarks.
-Finally, a general conclusion and some research perspectives are given in  Section~\ref{sec:conclusion}.
-
-\section{Hybrid model with external signals}
-\label{sec:hybrid}
-We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, and a global error-corrector neural network train on all time series.
-Per-time-series parametric models are used to learn local behaviours, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
-Then, gathering information of the first predictions and external variables, a recurrent neural network is trained to correct the predictions provided by the first collection of per-time-series models.
-
-Consider $N\geqslant 1$ time series.
-For all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$, let $\ts_t^n$ be the value of the $n$-th sequence at time $t$ and  $\fullts^n = \{\ts_t^n\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
-The objective of this paper is to propose a model to  forecast all time series in a given time frame  $\lag \in \mathbb{N}$, i.e.
-we aim at sampling $\{\ts^n_{T+1:T+\lag}\}_{1\leqslant n \leqslant N}$ based on $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$.
-
-\subsection{Per-time-series predictors}
-The time-series-specific predictors compute, for each sequence, a first $\lag$-ahead prediction based on the past.
-For all $1\leqslant n \leqslant N$, we note $\stat^n(.;\statparam^n)$ the $n$-th parametric model of the $n$-th sequence where $\statparam^n$ are  unknown parameters.
-Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$ and the estimated  parameters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the time-series-specific forecasts $\{\tspred^{pred,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
-$$
-\tspred^{pred,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i\,.
-$$
-During the M4 competition, the hybrid model of \cite{smyl2020hybrid} was based on a multiplicative exponential smoothing model as the time-series-specific predictor.
-However, on sporadic time series, this choice leads to poor results and instability.
-In this paper, a more general framework able to deal with any kind of per-time-series models is provided.
-In Section~\ref{sec:exp}, two versions of our framework are proposed.
-The first one is based on an  exponential smoothing as a reference similar to the baseline \cite{smyl2020hybrid} and the second one uses a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
-
-In the specific application of fashion trends prediction, two main forms of standard weaknesses were detected and defined for univariate parametric forecasts.
-The first one is a weakness of definition, when the model is not well defined for its forecasting task.
-For instance, an additive model provides good predictions on time series with additive seasonality but fails at handling multiplicative seasonalities.
-The second form, harder to detect and correct, is the weakness of information.
-For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence.
-In somes cases, these changes depend on external variables not considered by univariate parametric models.
-The difficulty is that the exact influence of external variables on the main signal is mostly unknown.
-This motivates the introduction of a global RNN trained on all time series and able to consider and leverage external signals.
-First forecast example of our new hybrid model is given in Figure~\ref{fig:introexamples}.
-
-\begin{figure*}
-\centering
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  %\includegraphics[width=\linewidth]{figure/us_female_shoes}
-  %\caption{Time series representing a shoes fashion trend for female in The United States.}
- % \label{fig:introexamples:sub1}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
-  %\centering
-  \includegraphics[width=\linewidth]{figure/br_female_texture_verticalstripe}
- % \caption{Time series representing the vertical stipes texture fashion trend for female in Brazil.}
-  %\label{fig:introexamples:sub2}
-%\end{subfigure}
-\caption{Hermes forecast examples.
-In green the prediction of the TBATS per-time-series predictors.
-In red the final forecast of our HERMES hybrid model.
-Time series representing the vertical stipes texture fashion trend for females in Brazil.}%(Top) Time series representing a shoes fashion trend for females in The United States.
-(Bottom) Time series representing the vertical stipes texture fashion trend for females in Brazil.}
-\label{fig:introexamples}
-\end{figure*}
-
-\subsection{Error-corrector recurrent model}
-
-The second part of the model is a global RNN, trained on all the $N$ sequences to correct the weaknesses of the first per-time-series parametric models.
-This task requires a thorough data pre-processing as recurrent neural networks training is highly sensitive to the scale of the data and requires well-designed inputs.
-Since no assumption about the scale of our time series was made, inputs require a careful normalization before being fed to the RNN.
-
-Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$.
-The RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$, $1\leqslant i \leqslant w$ and $k = i - h\lfloor i/h \rfloor$,
-$$
-\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+k|T}}{\meants^n_T}\,,\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
-$$
-Let $\rnn(.;\rnnparam)$ be the recurrent neural network model where $\rnnparam$ are  unknown parameters.
-Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\rnnparam$, the error-corrector predictions $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
-$$
-\tspred^{corr,n}_{T+i|T} = \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\ \,.
-$$
-Our hybrid model forecast is, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$,
-\begin{align}
-\label{eq:nows:full:model}
-\tspred^n_{T+i|T}  &= \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} \\
-&= \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\,.\nonumber
-\end{align}
-
-\subsection{Weak signal}
-
-Using well-fitted time-series-specific parametric models, the new hybrid network corrects the first form of weakness and provides very good performance on the fashion dataset, see Table~\ref{tab:metricresults}.
-Then, to correct the second form of weakness, in addition to the $N$ target time series, $K \times N$ external sequences indexed from $0$ to $T$ are considered.
-For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ associated with the sequence $\fullts^n$.
-Let  $\fullws^n = \{\{\ws_t^{n,k}\}_{1\leqslant t \leqslant T}\}_{1\leqslant k \leqslant K}$ be all the values of the weak signals associated with the $n$-th sequence.
-In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the sequence.
-Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, a new input for the RNN is defined:
-\begin{align*}
-\fullconcatinput^n_T &= \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}\\
-&= \{\rnninput^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
-\end{align*}
-Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ the final prediction becomes:
-%$$
-%\tspred^n_{T+i|T} 
-%= \etspred^{ets,n}_{T+i|T} +  \rnnmodel(\fullconcatinput^n_T)_{T+i} \times \meants^n_T
-%$$
-\begin{align}
-\label{eq:withws:full:model}
-\tspred^n_{T+i|T}  &= \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T}\\
-& = \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\fullconcatinput^n_T;\rnnparam)_i \cdot \meants^n_T\,.\nonumber
-\end{align}
-An illustration of the proposed  model is displayed in Figure~\ref{fig:architecture}.
-
-\begin{figure}
-  \centering
-    \includegraphics[width=1\linewidth]{figure/HERMES_archi.png}
-  \caption{Architecture of the hybrid model with weak signals.}
-\label{fig:architecture}
-\end{figure}
-
-\section{Fashion dataset with external weak signals}
-\label{sec:dataset}
-
-\subsection{Translate fashion to data}
-\label{sec:dataset:a}
-A collection of vision neural networks were designed and trained  at detecting clothes details on pictures: type of clothing (pants, shoes, tops, etc.), form, size, color, texture, etc.
-Then, fashion experts designed fashion trends by aggregating these clothes details: a meaningful combination of items that represent an existing trend in the fashion sphere.
-To finely represent human behaviours based on social media, a group of thousands of random users, called a panel, was created on several geolocalisations.
-Analyzing every day images shared on social networks by these panels with our computer vision algorithms, we can translate the history of thousands of fashion trends in thousands of time series.
-All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
-Each value represents the number of users posts in a week where computer vision algorithms detected the fashion trend.
-As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization}.
-
-\subsection{Fashion dataset}
-\label{sec:dataset:b}
-
-Due to the increasing use of social media and behaviour changes, a normalization step is applied to the raw sequences.
-Each fashion trend is divided by its hierarchical parent category trend.
-Moreover, in order to avoid removing the seasonality of all sequences, we deseasonalized the hierarchical parent category trend before the normalization.
-For instance, as displayed in Figure~\ref{fig:normalization}, the raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.
-The final normalized sequence is expressed in share of category.
-
-We therefore introduce a new dataset for fashion time series forecasting.
-It contains a sample of $\numberts$ anonymized and  normalized fashion trends for men and women, in 9 different categories and 5 geozones.
-An overview of it can be found in Table~\ref{tab:fashiondataset}.
-This collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry.
-For instance, some sequences show complex behaviours with sudden changes, referred to as emerging or declining trends.
-A central point of this work is to accurately detect and forecast such trends.
-
-\begin{figure*}
-\centering
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/cn_female_top_raw}
-%  \caption{Time series representing the raw signal of a top fashion trend for female in China}
- % \label{fig:normalization:sub1}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/cn_female_top_norm}
-  %\caption{Time series representing the normalized signal of a top fashion trend for female in China.}
-  %\label{fig:normalization:sub2}
-%\end{subfigure}
-\caption{Example of difference between the raw sequence and the normalized one.
-In this example, we normalize by the deseasonalized global top fashion trend for females in China.
-(Top) Time series representing the raw signal of a top fashion trend for females in China.
-(Bottom) Time series representing the normalized signal of a top fashion trend for females in China.}
-\label{fig:normalization}
-\end{figure*}
-
-\begin{table*}
-  \caption{Fashion time series overview. For each couple geozone/category, the table gives the number of trends (Female/Male).}
-\label{tab:fashiondataset}
-  \centering
-  \resizebox{0.65\width}{!}{
-  \begin{tabular}{l||lllllllll}
-    %hline
-    \\
-    &  \textbf{Top}  & \textbf{Pants} & \textbf{Short} & \textbf{Skirt} & \textbf{Dress} & \textbf{Coat} & \textbf{Shoes} & \textbf{Color} & \textbf{Texture}  \\
-    \hline
-    \hline
-    \\
-\textbf{United States} & 411/208 & 149/112 & 47/22 & 29/- & 20/- & 208/151 & 293/86 & 38/44 & 85/81\\
-     \textbf{Europe} & 409/228 &  134/114 & 48/21 & 28/- & 20/- & 211/159 & 303/78 & 41/42 & 87/74\\
-     \textbf{Japan} &  403/218 & 136/107 & 49/31 & 28/- &  23/- & 185/149 &  311/78 & 46/42 &  92/65\\
-     \textbf{China} &  424/202 & 147/114 & 46/29 & 27/- &  27/- & 178/161 &  310/78 & 41/47 &  88/77\\
-     \textbf{Brazil} &  431/222 & 134/117 & 49/27 & 30/- &  28/- & 203/152 & 311/76 & 48/41 & 107/84\\
-     \\
-     %\hline
-     \textbf{Total} & 2078/1078 & 700/564 & 239/130 & 142/- & 118/- & 985/772 & 1528/396 & 214/216 & 459/381\\
-    %\hline
-  \end{tabular}
-  }
-\end{table*}
-
-\subsection{Weak signal}
-
-In theoretical fashion dynamics \cite{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
-%In this way, a weak signal for each sequence is added to the proposed dataset.
-Numerous social media influencers were selectioned by hand by fashion experts.
-By aggregating them, a specific ``fashion-oriented`` panel is created.
-With the same methodology as for the main panel described in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created.
-We named \textit{fashion-forwards} this weak signal.
-For all trends $\{y_t\}_{1\leqslant t\leqslant T}$, let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
-As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for our hybrid model:  for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
-$$
-\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}\,.
-$$
-Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.
-For instance, an impressive emerging fashion shoes trend with its \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
-
-%Secondly, depending of the number of followers, the general panel of users is divided in three sub-groups: users with less than 1350 followers, users with a number of followers between 1350 and 7000 and users with more than 7000 followers.
-Repeating the previous methodology on each sub-panel, three normalized time series for each time series are created.
-Again, the motivation here is to detect behaviour gaps between different parts of the society that could lead to changes in the main signal.
-Let $\ts_t^{\ell,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{\ell,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences.
-Two inputs for our hybrid model are computed: for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
-%\begin{align*}
-%\ws^{\ell,n}_{t} = \frac{\ts_t^{\ell,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}
-%\end{align*}  
-%values close to 0.3 indicate a similar behaviour between the three sub-panels and the general panel.
-%
-%In addition to the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{\ell}$ and $\ws^{h}$ are added.
-They are frequently sparse for micro trends and they often lack interest in common fashion trends.
-However, in several examples, they are fundamental to detect the future fashion evolutions, as illustrated in Section~\ref{sec:exp}.
-
-\begin{figure*}
-  \centering
-    \includegraphics[width=1.\linewidth]{figure/ff_example}
-  \caption{A shoes trend of the fashion dataset.
-In black the main signal and in red its associated \textit{fashion-forward} weak signal.
-The shift between these two signals at the end of 2017/beginning of 2018 announces the future burst of the trend.}
-\label{fig:oneemergingtrend}
-\end{figure*}
-
-\section{Experimental results}
-\label{sec:exp}
-
-\subsection{Training}
-The dataset is split into three blocks, {\em train}, {\em eval} and {\em test} sets.
-The 3 first years are used as the {\em train} set, the 4th year is kept for the {\em eval} set and the {\em test} set is made of the last year.
-The hybrid model is trained to compute a one-year ahead prediction, $\lag$ equal to 52, and the window size $\window$ is fixed at 104.
-Using the two first years of the {\em train} set, a first per-time-series parametric model for each time series is fitted.
-With the resulting collection of local models, a forecast of the third year is computed for each sequence.
-Corrector inputs are finally computed and the RNN is trained at correcting this first collection of third-year forecasts.
-For the {\em eval} set, per-time-series predictors are fitted a second time using the three first years and forecasts of the fourth year are computed.
-The {\em eval} set is used during  training to control the learning of the RNN model and prevent overfitting.
-The per-time-series predictors are fitted a last time for the {\em test} set using the four first years.
-The final accuracy measures of all our models are computed on this {\em test} set.
-As an illustration, an example of our split is shown in Figure~\ref{fig:train_eval_test_set}.
-
-For the first parametric per-time-series models, existing Python or R libraries are used to estimate the different parameters $\statparam^n$.
-Depending of the choice of local parametric models, two versions of HERMES are proposed.
-The first one uses as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}.
-The second one uses the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves the best accuracy results on the fashion dataset.
-The neural network architecture is summarized in Figure~\ref{fig:rnn_architecture}.
-It is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
-A classical Adam optimizer is used with a learning rate set at 0.001 or 0.005, the batch size is fixed to 64 and the loss function is defined as follows:
-$$
-\ell(\ts^n_{T+1:T+\lag},\tspred^n_{T+1:T+\lag|T}) = \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,.
-$$
-This choice of $\mathrm{L}_1$  loss function is motivated by its robustness to outliers which accounts for some time series in the fashion industry with very specific behaviors.
-The loss and previous parameters are all set with a grid search (additional materials can be found in Appendix~B).
-The code is developed in Python using the Tensorflow library.
-It allows the use of GPU to speed up the training process.
-
-\begin{figure*}
-  \centering
-    \includegraphics[width=1.\linewidth]{figure/train_eval_test_set}
-  \caption{Temporal split for our training process. The three first years define our training set. The fourth year is used as our eval set and the final year is reserved for the test set.}
-\label{fig:train_eval_test_set}
-\end{figure*}
-
-\begin{figure}
-  \centering
-    \includegraphics[width=0.8\linewidth]{figure/lstm_archi}
-  \caption{Architecture of the RNN corrector part of the HERMES framework. The same architecture is used in the \textit{lstm} benchmark model.}
-\label{fig:rnn_architecture}
-\end{figure}
-
-\subsection{Benchmarks, hybrid models and Metrics}
-
-As benchmarks, several widespread statistical methods and deep learning approaches were selected.
-Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels},  \texttt{tbats}, for each time series, predictions are computed with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}.
-The forecast of the \textit{snaive} method is only the repetition of the last past period.
-The \textit{ets} model is an additive exponential smoothing with a level component and a seasonal component.
-The \textit{stlm} approach uses a multiplicative decomposition and models the seasonally adjusted time series with an exponential smoothing model.
-The \textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast and \textit{tbats} uses a trigonometrical seasonality.
-Finally, \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters.
-A complete description and references for these models can be found in \cite{hyndman2020package}.
-As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.
-Two versions of HERMES are proposed.
-They are called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
-Moreover, two versions with the inclusion of the weak signals (ws) are proposed.
-They are referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}.
-In order to provide a fair comparison, a \textit{lstm} with the weak signals named \textit{lstm-ws} is trained.
-
-To compare the different methods, we use the Mean Absolute Scaled Error (MASE) for seasonal time series.
-As our sequences have completely different scales, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, independent of the scale of the sequence and suited for our seasonal fashion time series.
-The MASE metric is defined as follows, with $m$ the seasonal period:
-\begin{align*}
-\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{j=1}^h |Y_{T+j} - \hat{Y}_{T+j}| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,.
-\end{align*}
-Detecting emerging and declining trends is a crucial issue for the fashion industry.
-A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes.
-In addition to the MASE accuracy metric, the different methods are also evaluated on a classification task and especially differences between methods using weak signals or not.
-In a given year, an increasing trend is defined as a trend that does more than 5\% of growth on average with respect to the previous year.
-In the same way, a decreasing trend is defined as a trend that declines by 5\% on average or more.
-Other trends are classified as flat trends.
-With this threshold, the proposed fashion dataset is almost balanced on the {\em test} set: There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends.
-%On the {\em test} set, for each method, the accuracy is defined as follows:
-%\begin{align*}
-%\mathrm{ACCURACY} &= \frac{TP}{TP + FP}\,,
-%\end{align*}
-%where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series misclassified in the class $i$.
-
-\subsection{Result for Heuritech Fashion dataset}
-
-\textbf{10000 Heuritech Fashion time series global accuracy.
-}For the two metrics and for each model, we compute the average on all sequences in the final year.
-Results are displayed in Table~\ref{tab:metricresults}.
-For our model using neural networks, 10 models are trained  with different seeds.
-The average and the standard deviation of their results are computed and displayed.
-For the statistical models, TBATS largely dominates the alternatives  in terms of MASE.
-It is one of the main motivations why this model is used on the best HERMES candidate as the predictor model.
-
-Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slightly outperform the alternatives in terms of MASE and are stable across the different trainings.
-Regarding \textit{hermes-ets},   although it is very similar to the baseline \cite{smyl2020hybrid}, its accuracy remains low in comparison to the \textit{lstm} benchmark or HERMES using TBATS.
-
-Models using our weak signals perform similarly as without-weak-signals models for the MASE.
-Interestingly, weak signals significantly improve the accuracy in detecting emerging and declining trends.
-Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} models and some weaknesses that can be corrected.
-
-\begin{table}
-  \caption{Results summary on the 10000ts Fashion dataset.
-For each metric, the average on all our time series is computed.
-For approaches using neural networks, 10 models are trained with different seeds.
-The mean and the standard deviation of the 10 results are displayed.}
-  \centering
-%  \resizebox{0.85\textwidth}{!}{%
-  \begin{tabular}{l||lllll|lllll}
-   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
-    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
-%    \hline
-	 \hline
-	 &&&&&&&&&&\\
-     \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
-     \textit{thetam}  && 0.844 && -&&& 0.482 && - &\\
-     \textit{arima} && 0.826 && -&&& 0.464 && - & \\
-     \textit{ets} && 0.807 && -&&& 0.449 && - & \\
-     \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
-     \textit{hermes-ets-ws} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
-     \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
-     \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
-     \textit{lstm-ws} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
-     \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
-     \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
-     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& \textbf{0.510} && 0.005 &\\
-    %\hline
-  \end{tabular}
-%  }
-\label{tab:metricresults}
-\end{table}
-
-\begin{figure*}
-\centering
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/us_female_top}
-  %\caption{Time series representing a top fashion trend for female in The United States}
-  %\label{fig:examples:sub1}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/cn_female_texture_horizontalstripe}
-  %\caption{Time series representing the horizontal stipes texture fashion trend for female in China}
-  %\label{fig:examples:sub2}
-%\end{subfigure}
-\caption{\textit{hermes-tbats} forecast examples.
-In green the prediction of the per-time-series predictors \textit{tbats}.
-In red the final forecast of our HERMES hybrid model \textit{hermes-tbats}.
-(Top) Time series representing a top fashion trend for females in The United States.
-(Bottom) Time series representing the horizontal stipes texture fashion trend for females in China.}
-\label{fig:examples}
-\end{figure*}
-
-\textbf{10000 Heuritech Fashion time series classification task.
-} Classification results between the \textit{tbats} model and the hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impressive decrease of impactful errors: i.e.
-forecasting an increase instead of a decrease and vice versa.
-The \textit{hermes-tbats} model divides by 3 the error rate in comparison to \textit{tbats} with only a slight decrease of the number of correct increase/decrease predictions.
-However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signals while keeping a relatively low number of impactful errors.
-
-\begin{table}
-  \caption{\textit{tbats}, \textit{hermes-tbats} and \textit{hermes-tbats-ws} models confusion matrix}
-  %\vspace{0.2cm}
-  %\textit{tbats} model confusion matrix \\
-  %\par \textit{tbats} model confusion matrix
-  %\vspace{0.2cm}
-\centering
-\vspace{0.2cm}
-\resizebox{6cm}{!}{
-  \begin{tabular}{l||llll}
-  	&& \multicolumn{3}{c}{\textbf{\textit{tbats}}}\\
-    && pred-dec  & pred-flat & pred-inc  \\
-    \hline
-    \hline
-    \rule{0pt}{2ex} \\
-	true-dec && 902 & 2113 & 327 \\
-    true-flat && 351 & 2920 & 300 \\
-    true-inc && 300 & 2078 & 709 
-  \end{tabular}
-}
-\vspace{.2cm}
-\resizebox{6cm}{!}{
-  \begin{tabular}{l||llll}
-  	&& \multicolumn{3}{c}{\textbf{\textit{hermes-tbats}}}\\
-    && pred-dec  & pred-flat & pred-inc  \\
-    \hline
-    \hline
-    \rule{0pt}{2ex} \\
-	true-dec && 1261 & 1960 & 121 \\
-    true-flat && 549 & 2823 & 199 \\
-    true-inc && 214 & 2004 & 869 
-  \end{tabular}
-}
-\vspace{.2cm}
-\resizebox{6cm}{!}{
-  \begin{tabular}{l||llll}
-    && \multicolumn{3}{c}{\textbf{\textit{hermes-tbats-ws}}}\\
-    && pred-dec  & pred-flat & pred-inc  \\
-    \hline
-    \hline
-    \rule{0pt}{2ex} \\
-	true-dec && 1956 & 1245 & 141 \\
-    true-flat && 1257 & 2087 & 227 \\
-    true-inc && 358 & 1620 & 1109 
-  \end{tabular}
-}
-\label{tab:tbatsclass}
-\end{table}
-
-\textbf{Size of the dataset.
-} In addition to the results on the fashion dataset gathering 10000 time series, the behaviour of the HERMES model is analyzed when it is trained on smaller datasets: two experiments were performed, HERMES models were trained on a reduced dataset of 1000 time series and on a reduced dataset of 100 time series.
-Results are given in Table~\ref{tab:1000metricresults}.
-
-First, the hybrid framework \textit{hermes-tbats} achieves the best performance in terms of global accuracy on both datasets.
-Due to the strength of its per-time-series predictor TBATS, the hybrid model succeeds at correcting TBATS  and reaches a satisfactory final accuracy.
-Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases.
-On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms its accuracy level.
-Providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require  large amounts of data to do so.
-Nevertheless, with the HERMES framework, the RNN task is largely simplified.
-Our model needs less data to be trained and to obtain interesting performance.
-
-\begin{table}
-  \caption{Results summary on the 1000 time series and 100 time series Fashion dataset.
-The MASE average on all our time series is computed.
-For the two approaches using a neural network, 10 models with different seeds are trained.
-the mean and the standard deviation of the 10 results are displayed.}
- \centering
- \resizebox{1.\textwidth}{!}{ 
-  \begin{tabular}{l||llll}
-    \multicolumn{4}{c}{1000 time series Fashion dataset}\vspace{0.5cm} \\
-    &&\multicolumn{2}{c}{\textbf{MASE}} \\
-    &&  \textit{mean}  & \textit{std}  \\
-%    \hline
-	 \hline
-	 &&& \\
-     \textit{snaive} && 0.871 & - \\
-     \textit{thetam}  && 0.849 & - \\
-     \textit{arima} && 0.821 & - \\
-     \textit{ets} && 0.801 & - \\
-     \textit{stlm} && 0.765 & - \\
-     \textit{lstm} && 0.740 & 0.007 \\
-     \textit{tbats} && 0.734 & - \\
-     \textbf{\textit{hermes-tbats}} && \textbf{0.719} & 0.002 \\
-  \end{tabular}\hspace{1cm}
-\vspace{.2cm}
-
-  \begin{tabular}{l||llll}
-   \multicolumn{4}{c}{100 ts Fashion dataset}\vspace{0.5cm} \\
-   &&\multicolumn{2}{c}{\textbf{MASE}} \\
-    &&  \textit{mean}  & \textit{std}  \\
-%    \hline
-	\hline
-	 &&& \\
-     \textit{snaive} && 0.876 & - \\
-     \textit{thetam}  && 0.823 & - \\
-     \textit{arima} && 0.814 & - \\
-     \textit{ets} && 0.785 & - \\
-     \textit{lstm} && 0.767 & 0.045 \\
-     \textit{stlm} && 0.742 & - \\
-     \textit{tbats} && 0.745 & - \\
-     \textbf{\textit{hermes-tbats}} && \textbf{0.739} & 0.003 \\
-  \end{tabular}
- }
-\label{tab:1000metricresults}
-\end{table}
-
-\subsection{Result for M4 weekly dataset}
-
-We also assessed the performance of HERMES using the M4 weekly dataset \cite{makridakis2020m4}.
-The M4 dataset gathers 359 weekly time series and has 3 main differences compared to our proposed fashion dataset.
-Firstly, sequences do not have the same length with sequence lengths lying between 93 and 2610 time steps.
-Secondly, as some of the sequences represent financial signals or some others are demographic sequences, the  359 time series have very distinct scales and dynamics.
-Thirdly, compared to the previous fashion application, the time horizon of the prediction is set to 13 for the weekly dataset.
-
-\textbf{Training.
-} The M4 dataset is firstly preprocessed.
-This preliminary step is motivated by two reasons.
-First, as some sequences are short (93 time steps), they limit the window size $w$ of the RNN part and consequently the global accuracy of the HERMES approach.
-Second, the longer time series slow down the training of the collection of the first predictors especially for complex methods like TBATS.
-We kept 300 time steps  for each sequence in order to train the HERMES model.
-For the shorter sequences, the train set is duplicated in order to reach the length of 300.
-Longer sequences are cropped in order to keep the last 300 time steps.
-%The sequences are firstly resized in order to obatain a dataset with fixed time horizon.
-The eval and the test sets are removed for the shortest sequences (the last 26 steps).
-Then, the remaining number of entire year is duplicated in order to egalize all the sequence at the longest one : 2610 time steps \textcolor{red}{Pas sur de comprendre, reformuler}.
-As per time series parametric model training time depends on the sequence length, all time series are then croped.
-Finally, with the addition of the previously removed eval and test sets, 300 time steps are kept for each sequence \textcolor{red}{Pas sur de comprendre, reformuler}.
-
-The horizon $h$ is set to 13  and the window size $w$ is set to 104.
-For the RNN part, the same architecture as the one described in Figure~\ref{fig:rnn_architecture} is used.
-The Adam optimizer is used with a learning rate  equal to  0.005 and a batch size set to 8.
-As the M4 weekly dataset is small, a rolling window is used on the train set in order to increase the train number of examples and improve training results.
-Three windows are computed for each sequence for the RNN train set.
-An overview of our train, eval, test set split and the resizing of the shortest sequences is given in Figure~\ref{fig:m4dataset}.
-The previous parameters: window size, learning rate, batch size and the number of train windows per time series are set using a grid search, see Appendix~B.
-
-\begin{figure*}
-  \centering
-    \includegraphics[width=1.\linewidth]{figure/M4_dataset}
-  \caption{One of the shortest sequences of the M4 weekly dataset (93 time steps).
-In order to fit its predictor, the last complete year is duplicated in order to reach a total length of 300 time steps.}
-\label{fig:m4dataset}
-\end{figure*}
-
-\textbf{Benchmarks.
-} The M4 competition provides a rich collection of benchmarks emcompassing statistical models and neural network approaches.
-The same candidates are used in this part as baselines.
-In addition, the hybrid model named \textit{Uber} of S.Smyl is added.
-For a complete description and references of the benchmark models, see \cite{makridakis2020m4}.
-As a HERMES candidate, a version using TBATS is proposed and called \textit{hermes-tbats}.
-Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measures.
-A complete definition of these metrics is proposed in \cite{makridakis2020m4}, see also Appendix~\ref{sec:m4overview} for additional information about the M4 weekly dataset.
-
-\textbf{Results and discussion.
-} The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}.
-The HERMES approach \textit{hermes-tbats} outperforms all the benchmarks.
-This result is partially induced by the use of TBATS per-time-series predictors which achieves very good results on the test set.
-Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}.
-With this second application, two important conclusions can be made.
-Firstly, the results provided by \textit{hermes-tbats} confirm that the HERMES approach is a general framework, well suited for a large collection of forecasting tasks.
-Secondly, the accuracy gap between the two hybrid candidates validates the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.
-
-\begin{table*}
-  \caption{Results summary on the m4 weekly dataset.
-For each metric, the average on all our time series is computed.
-For approaches using a neural network, 10 models are trained with different seeds.
-The mean and the standard deviation of the 10 results are displayed.}
-  \centering
-  \resizebox{\textwidth}{!}{
-  \begin{tabular}{l||lllll|lllll|lllll}
-   &&\multicolumn{3}{c}{\textbf{SMAPE}} &&& \multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{OWA}}&\\
-    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}&&&  \textit{mean}  && \textit{std}& \\
-%    \hline
-	 \hline
-	 &&&&&&&&&&\\
-     \textit{MLP} && 21.349 && - &&& 13.568 && - &&& 3.608 && - &\\
-     \textit{RNN} && 15.220 && - &&& 5.132 && - &&& 1.755 && - &\\
-     \textit{snaive} && 9.161 && - &&& 2.777 && - &&& 1.000 && - &\\
-     \textit{SES} && 9.012 && - &&& 2.685 && - &&& 0.975 && - &\\
-     \textit{Theta} && 9.093 && - &&& 2.637 && - &&& 0.971 && - &\\
-     \textit{Holt} && 9.708 && - &&& 2.420 && - &&& 0.966 && - &\\
-     \textit{Com} && 8.944 && - &&& 2.432 && - &&& 0.926 && - &\\
-     \textit{Damped} && 8.866 && - &&& 2.404 && - &&& 0.917 && - &\\
-     \textit{S.Smyl} \cite{hyndman2020package} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
-     \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.841 && - &\\
-     \textit{\textbf{hermes-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
-    %\hline
-  \end{tabular}
-  }
-\label{tab:m4metricresults}
-\end{table*}
-
-\section{Conclusion}
-\label{sec:conclusion}
-The motivation of this paper was to present HERMES, a new hybird model for non stationary time series forecasting.
-By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks.
-Furthermore, this new model is totally suited to deal with external signals.
-With a fine pre-processing and a well-designed architecture, our hybrid framework succeeds at leveraging our complex extra data and reaches very promising accuracy levels in terms of classification.
-In addition to this article, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided.
-We believe that this dataset contains really fine dynamics and interactions where complex models would express their potential.
-By making it publicly available\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}}, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
-As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.
-Focusing on the examples with huge changes of behaviours, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works.
-In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses.
-A perspective is to add a latent discrete label to select dynamically the regime shifts.
-
-%\appendices
-
-%\renewcommand{\thetable}{A\arabic{table}}
-%\renewcommand{\thefigure}{A\arabic{figure}}
-%\setcounter{table}{0}
-%\setcounter{figure}{0}
-
-\section*{Appendix A. M4 weekly dataset and results}
-\label{sec:m4overview}
-
-The M4 weekly dataset is a collection of 359 time series with  contrasting behaviours and sizes.
-An overview of the dataset is given in Table~\ref{tab:m4dataset} and some examples of sequences are given in Figure~\ref{fig:m4examples}.
-As sequences come from a wide diversity of sectors, the forecasting task is very challenging.
-However, on some examples as in Figure~\ref{fig:m4pred}, efficient corrections of the TBATS forecasts can be obtained.
-
-\begin{table}
-
-  \caption{M4 weekly dataset overview. For each category, the number of sequences and the average length are given.}
-\label{tab:m4dataset}
-  \centering
-  \resizebox{0.8\width}{!}{
-  \begin{tabular}{l||lll}
-    %hline
-    \\
-    &  \textbf{Nb. of sequences}  & \textbf{Avg. length} & \textbf{Min. length} \\
-    \hline
-    \hline
-    \\
-	\textbf{Demographic} & 24 & 1659 & 1615\\
-	\textbf{Finance} & 164 & 1237 & 260\\
-	\textbf{Industry} & 6 & 834 & 356\\
-	\textbf{Macro} & 41 & 1264 & 522\\
-	\textbf{Micro} & 112 & 473 & \textbf{93}\\
-	\textbf{Other} & 12 & 1598 & 470\\
-  \end{tabular}
-  }
-\end{table}
-
-\begin{figure}
-%\centering
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W10}
-%  \caption{A time series from the ``Other`` category called \textit{W10}.}
-  \label{fig:m4examples:sub1}
-%\end{subfigure} \quad
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W20}
-%  \caption{A time series from the ``Macro`` category called \textit{W20}.}
-%  \label{fig:m4examples:sub1}
-%\end{subfigure}
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W220}
-%  \caption{A time series from the \textit{Finance} category called \textit{W220}.}
-%  \label{fig:m4examples:sub2}
-%\end{subfigure}\quad
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-%  \includegraphics[width=1.\linewidth]{figure/W354}
-%  \caption{A time series from the \textit{Micro} category called \textit{W354}.}
-%  \label{fig:m4examples:sub3}
-%\end{subfigure}
-\caption{Examples of time series from the M4 weekly dataset.
-From Top to Bottom : time series called \textit{W10} from the \textit{Other} category, \textit{W20} from the \textit{Macro} category and \textit{W220} from the \textit{Finance} category.}
-\label{fig:m4examples}
-\end{figure}
-
-\begin{figure*}
-\centering
-% \begin{subfigure}{1.\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W133_pred}
-%  \caption{\textit{tbats} and \textit{hermes-tbats} forecast of the \textit{W133} time series}
-%  \label{fig:m4pred:sub1}
-% \end{subfigure}
-% \begin{subfigure}{1.\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W314_pred}
-%  \caption{\textit{tbats} and \textit{hermes-tbats} forecast of the \textit{W314} time series}
-%  \label{fig:m4pred:sub2}
-% \end{subfigure}
-\caption{\textit{hermes-tbats} forecast examples on the M4 weekly dataset.
-In green the prediction of the per-time-series predictors \textit{tbats}.
-In red the final forecast of our HERMES hybrid model \textit{hermes-tbats}.
-(Top) the \textit{W133} time series, (Bottom) the \textit{W314} time series.}
-\label{fig:m4pred}
-\end{figure*}
-
-%Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset.
-Except one approach, all of them are a combination of different models in order to increase the robustness of the final forecast and at the same time achieve a better global accuracy.
-The remaining one is not an ensembling but a statistical framework called \textit{Forecast Pro}.
-It is not a single statistical model but a framework that chooses, depending on the sequence properties, the best statistical approach.
-With a OWA equal to 0.739, it outperforms the \textit{hermer-tbats} and all the M4 proposed models on the M4 weekly sub-dataset.
-A description and interesting remarks about the \textit{Forecast Pro} model are discussed in \cite{DARIN2020135}.
-This model offers an interesting research perspective specifically for the M4 weekly forecasting task.
-Looking at the final results of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset.
-All of them are ensemble frameworks: methods that mix different kinds of approaches to reach a higher final accuracy.
-As the M4 weekly dataset gathers really heterogeneous sequences, combining several methods to leverage their strengths appear to be a promising way.
-However in this paper, only individual models were evaluated in order to provide a fair comparison with the HERMES framework.
-
-\section*{Appendix B. Training parameters and loss}
-
-\subsection{Loss grid search on the Fashion Dataset}
-\label{sec:heuritechgridsearch}
-
-Using deep learning models in time series forecasting is an appealing way to achieve higher accuracy performance.
-However, it induces two main issues.
-First, it requires a large enough dataset to train the model as illustrated in Section~\ref{sec:exp}.
-Second, a dataset can hide contrasting time series in terms of scale, noise and behaviour.
-These differences can impact training performance.
-For the HERMES architecture, some candidate losses were defined for the training: the Mean Absolute Error (MAE), the Mean Square Error (MSE),  the Scaled Mean Absolute Error (SMAE) and the Scaled Mean Square Error (SMSE).
-The loss functions are defined as follows:
-\begin{align*}
-MAE &= \frac{1}{\lag}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,,\\
-MSE &= \frac{1}{\lag}\sum_{i=1}^{\lag}(\ts^n_{T+i} - \tspred^n_{T+i|T})^2\,,\\
-SMAE &= \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,,\\
-SMSE &= \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}(\ts^n_{T+i} - \tspred^n_{T+i|T})^2\,.
-\end{align*}
-For each loss, 10 \textit{hermes-tbats-ws} models have been trained with different seeds and the final mean and standard deviation are given in Figure~\ref{fig:loss_function}.
-The final Scaled Mean Absolute Error reaches the lowest MASE and was selected to train all the HERMES model in this paper.
-
-\begin{figure}
-  \centering
-    \includegraphics[width=1.\linewidth]{figure/loss_function}
-  \caption{MASE accuray for the \textit{hermes-tbats-ws} model depending on the loss used during the RNN training.
-For each loss, 10 models with different seeds have been trained.
-The mean and the standard deviation are represented with a point and a vertical line.}
-\label{fig:loss_function}
-\end{figure}
-
-\subsection{Parameters grid search on the M4 weekly Dataset}
-\label{sec:m4gridsearch}
-
-In addition to the loss function, the HERMES model also depends on several hyperparameters to set correctly in order to reach satisfactory performance.
-For instance, an overview of the learning rate, batch size and number of windows per time series grid search for the M4 weekly dataset is shown in Figure~\ref{fig:m4parameter}.
-For each parameter, a collection of 10 \textit{hermes-tbats} models have been trained with a range of values and the final OWA was calculated.
-As in the Figure~\ref{fig:loss_function}, the mean and the standard deviation of each group of 10 trainings is computed.
-For the final \textit{hermes-tbats} model of the M4 weekly dataset,  the following set of parameters was selected: 3 windows per time series were used as the train set, the batch size was set to 8 and the learning rate was fixed to 0.005.
-
-\begin{figure}
-\centering
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/m4_nb_of_window}
-  %\caption{result of the HERMES model on the M4 dataset model depending of the number of windows provided per time series to the RNN corrector}
- % \label{fig:m4parameter:sub1}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/m4_batch_size}
-  %\caption{result of the HERMES model on the M4 dataset model depending of the size of the batch size}
-  %\label{fig:m4parameter:sub2}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
-  %\centering
-  \includegraphics[width=1.\linewidth]{figure/m4_learning_rate}
-  %\caption{result of the HERMES model on the M4 dataset model depending of learning rate of the optimizer}
-  %\label{fig:m4parameter:sub3}
-%\end{subfigure}
-\caption{OWA for the \textit{hermes-tbats} model on the M4 weekly dataset depending on 3 parameters used during the RNN training: Number of moving windows per time series, the batch size and the learning rate.
-For each parameter, 10 models with different seeds have been trained.
-The mean and the standard deviation are represented with a point and a vertical.
-(Top) Result of the HERMES model depending on the number of windows provided per time series to the RNN corrector.
-(Middle) Result of the HERMES model depending on the size of the batch size.
-(Bottom) Result of the HERMES model depending on the learning rate of the optimizer.}
-\label{fig:m4parameter}
-\end{figure}
-
-\section*{References}
-
-\bibliography{hermes_paper_elsevier}
-
 \end{document}

### 2022-11-02 signal_processing_elsevier/re-submission_ijf/Response_to_reviewers/hermes_paper_response_to_reviewers.tex
re-submission hermes

\documentclass[11pt]{article}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{xcolor}

\title{Cover letter for the revised version of IJF-D-22-00224}

\author{\'Etienne David et al.}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

We would like to thank the reviewers and the associate editor for attentively reading our work, the constructive feedback, and their appreciation of the paper. We are also grateful for the fast handling of the manuscript.
We have carefully considered all the comments of the reviewers. All the minor errors and typos listed by the reviewer have been corrected as suggested and you can find detailed responses to the comments below.

\subsection*{Major changes}

The first major change concerns the dataset description in Section 3. In section 3.1, an overview of the image recognition framework is provided with references to the main architectures used. In section 3.2, a more detailed explanation is given on how the images are translated to fashion time series and how they are normalized to remove social media bias. Finally, a clearer description of the external signal is provided in Section 3.3.

The second major change is the update of Section 4.4 concerning the M4 weekly dataset. We have added to the pool of benchmarks the top 3 models attaining the highest accuracy during the M4 competition on the weekly dataset. As these models are ensembling methods, an ensembling approach mixing 4 HERMES variations is proposed. This proposed ensembling achieves the same level of accuracy as the previous top 3 methods and illustrates that HERMES models can be easily introduced in an ensemble framework to provide more robust and accurate final predictions.

In addition to the two main changes, we want to highlight several additional updates. i) Figure 3 is updated to display a clearer big picture of the HERMES framework. ii) In Appendix A.3, a complete description of the proposed ensembling combining HERMES variations is added for completeness. iii) Finally, in Appendix B.2, we describe the entire grid search run on the M4 weekly dataset to set the hyperparameters of the HERMES architecture.

\subsection*{Reviewer 1}

\begin{itemize}
\item {\em ``In page 3, authors claim that they use cutting-edge image recognition techniques to create the "first fashion dataset". However, ... . Also, the target variable to forecast, "share of category" is also not clearly explained or provided the exact equations used to derive these values. ''} \medskip

\textbf{Author response:}  We agree perfectly with the referee and this comment has led to an important update of our paper to better describe the dataset. We have now presented more precisely the creation of the dataset: from the image recognition framework (Section 3.1) to the creation of the fashion time series and the "influencer" external signals (Section 3.2 and 3.3).

\item {\em ``Authors highlight that they avoid using ensemble-based benchmarks on M4 dataset for a fair comparison. However, HERMES also mimics a similar functionality to that of ensemble models (e.g., Boosting methodology found in the ML literature) as it uses a combination of methods.''} \medskip

\textbf{Author response:}  We thank the referee for this sensible suggestion that motivates an improvement of Section 4.4. In addition to the existing comparison between the HERMES model and a pool of benchmarks, a second comparison has been done between the 3 ensembling methods reaching the highest accuracy on the M4 weekly dataset and an ensembling combining 4 HERMES variations. The HERMES hybrid model can easily be included in an ensembling framework and the proposed ensembling method reaches the same accuracy level as the best approaches of the M4 competition.

\item {\em ``Authors must avoid the ambiguity in the paper. For example, in page 12, authors say "existing Python or R libraries are used to estimate the different parameters". Why do you use a "or" in this sentence? Authors must be more specific about what they implement (exact packages etc)''} \medskip

\textbf{Author response:}  We have now corrected parts with ambiguity as suggested.

\item {\em ``Authors use a subset of the fashion time series to demonstrate the use of HERMES on smaller dataset. Again, have not explained the details of the selection of subset of data. Are they randomly selected or handpicked?''} \medskip

\textbf{Author response:} There was indeed an oversight on this part. The two subsets of data are selected randomly and the text has been updated accordingly.

\item {\em ``Authors have used a grid-based methodology to determine the optimal parameters for the neural network-based methods but have not clearly mentioned the initial parameter ranges used in the experiments. In page 27, authors say that "have been trained with a range of values". To reproduce the results, it is important you provide these details (since you don't provide the source code, authors should at least make an effort to give these information)''} \medskip

\textbf{Author response:}  To complete Appendix B.1 where we present a grid search run on the loss function, we have added in Appendix B.2 a complete example of grid search run for all the hyperparameters of the HERMES architecture on the M4 weekly dataset.

\item {\em ``Authors must use consistent benchmarks across both datasets (ES-RNN benchmark missed in the Fashion dataset). Also haven't provided a statistical test to evaluate the significance of the differences of the results (the results are statistically significant or not)''} \medskip

\textbf{Author response:} We agree with the reviewer, the absence of the ES-RNN benchmark on the Fashion dataset is annoying. However, this choice has been motivated for two reasons: Firstly, the ES-RNN code base is developed in a non-usual code framework (Dynet) that could make the migration to Python difficult. A Python package exists but it is especially designed to work on the M4 dataset and we decided not to update the code to the Fashion dataset use case. Secondly, to compensate this absence: i) we partially replicate it with a method called \textit{hermes-ets} on the fashion dataset and ii) we run numerous experiments on the M4 weekly dataset to provide a complete comparison between the true ES-RNN and the HERMES approach.

\item {\em ``In page 15, it is also not clear about the exact classification algorithms used in the study. Authors don't not refer nor provide justification for the use of proposed the threshold (5\%) to label the time series into decreasing/flat/increasing trends. Of course, it helps to create a balance dataset, but that is not a valid justification to use this threshold. Need to import more evidence/justification from the fashion domain''} \medskip

\textbf{Author response:} We totally understand the expectations of the referee with this remark. However, the chosen threshold was selected to match the fashion industry practices. We decided to provide additional numerical simulations, for instance in the M4 setting, to illustrate the performance of the model instead of adding results with other thresholds which would not be used in practice.

\item {\em ``The performance of the RNN on the M4 weekly time series dataset seems to be poor. Given the proposed HERMES also use this algorithm (Figure 6) as a part of the framework, it is a bit surprising to see how it improves the accuracy after the inclusion of per series TBATS model (Hermes-tbats). I can understand why RNN model is underperforming (because the time series are heterogenous with different starting and end date, and if you globally train the model, without additional/external information, it will not pick up the correct signals).''} \medskip

\textbf{Author response:} We agreed with the reviewer that the M4 weekly dataset is a particularly challenging dataset for RNN approaches. For the RNN benchmark, the neural network has to rebuild the entire prediction while in the HERMES framework, the RNN part task is only to correct an already computed prediction. Thus, the final accuracy of the 4 HERMES variations is mainly supported by their collections of  per-time-series predictors. To illustrate this point, we have added Table A.7 in Appendix A which shows the accuracy of the predictors alone and included in the HERMES framework on the M4 weekly dataset. For each version, the RNN corrector always increases even slightly the final overall accuracy. Moreover, several interesting corrections of the RNN part can be noted as in Figure A.9.

\end{itemize}
\subsection*{Reviewer 2}
\begin{itemize}

\item {\em ``On p.7, in the formula above eq.1 It appears that z is centered around Ypred[T+k], with k=i-h[i/j] . I assume that i/j is an integer division. This is a strange formula, where h seems to be assumed to be equal seasonality. Also, why would you center the input by the output prediction value?''} \medskip

\textbf{Author response:} We thank the referee for this remark and we have now improved this part to give more motivation about our preprocessing. We center the input by the output prediction value for two reasons: i) to include the per-time-series prediction in the RNN input ii) to remove from the RNN input the fundamental patterns already learned by the per-time-series predictor.

\item {\em ``On p.13, fig.6 What is the meaning of e.g. (None,52,50) or (None,50)?''} \medskip

\textbf{Author response:} There was indeed a mistake in the figure 6, (None,52,50) and (None,50) are displayed in the graph without additional information. In order to shed more light on this point, we have decided to merge the RNN part architure and the overall HERMES architecture in a same figure (Figure 3). Information about the size of the LSTM and Dense layer are no longer represented but can be found in Section 4.1.

\item {\em ``On p.14, line 203 Why limit yourself to only one version of ETS (additive, seasonal, no trend I assume)''} \medskip

\textbf{Author response:} We totally agree with the referee. We have now introduced two different versions of the ETS model on the M4 weekly dataset. The first one is an ETS model with an additive trend, seasonality and noise and the second one is the multiplicative ETS with a multiplicative trend, seasonality and noise.

\item {\em ``On p. 18, lines 255-260 I would assume that reducing the dataset size 10 times, would necessitate an update the model/training hyperparameters. No?''} \medskip

\textbf{Author response:} We thank the reviewer for this sensible suggestion. In fact, for each new use case or experiment, a grid search can be run to improve the final accuracy of the HERMES architecture. However, we have noticed that the hyperparameters, except for the choice of the learning rate, do not impact significantly the final accuracy of the model. It is why we have decided not to change the hyperparameters for the experiments on the subsamples of the fashion dataset and also on the M4 weekly dataset, where the same hyperparameters are used for all the HERMES variations.

\item {\em ``On p.2, line 302; Table 5 You mention that a model called "Uber" is added. But I do not see it in table 5. Instead there is there a strange phrase "S.Smyl Hyndman et al. (2020)"''} \medskip

\textbf{Author response:} We have now corrected this
mistake.

\item {\em ``General remark: You fit an NN model on residuals from a tbats model. But tbats has some subversions, e.g. may or may not use Box-Cox transformation. I would suggest that passing to NN the fitted tbats model version could be useful.''} \medskip

\textbf{Author response:} In the hybrid model proposed by S.Smyl, the per-time-series ETS models are not fitted and the RNN part has consequently two tasks, set the parameters of the ETS models depending on the time series and correct their predictions. In the HERMES framework, the per-time-series predictor is first fitted using a Python package and then passed to the RNN corrector. This allows the proposed hybrid model to be built with any kind of per-time-series predictors, even complex one, depending on the use case.
\end{itemize}

\subsection*{Reviewer 3}
\begin{itemize}
\item {\em ``The paper gives the out of sample test results for all horizons, h=1, 2, …52 weeks. It is also interesting to see the performance of the methods separately for short (one week), medium (one month) and long term (one year) horizons.''} \medskip

\textbf{Author response:} With the applications on the Fashion dataset and the M4 weekly dataset, the HERMES approach has been tested with two different horizons: h=13 and h=52. Nevertheless, looking at the impact of the Influencer signal on the main signal (as displayed in Figure 1), it would be interesting to focus on a short term forecast. This point is not developed in this paper but is currently fueling our research work.

\item {\em ``Explain more clearly how you have constructed the values of weak signals.''} \medskip

\textbf{Author response:}  We agree perfectly with the referee and this comment has led to a major update of our paper. We have now presented more precisely the creation of the fashion time series and the "influencer" external signal (Section 3.2 and 3.3).

\item {\em `` Page 12: Explain why you have selected the window size as 104, also the same for M4 data. Are the results sensitive to window size?''} \medskip

\textbf{Author response:} So as to highlight the impact of the different hyperparameters of the HERMES architecture on the final accuracy, we have run a complete grid search on the M4 weekly data and displayed the result in Appendix B. The window size is a determinant parameter and we have noticed that giving at least two seasonal periods to the RNN corrector usually brings better results on average.

\item {\em ``Page 16, What is the Accuracy metric in table 2? Is it percentage of correct classification?''} \medskip

\textbf{Author response:} We have added a sentence at the end of Section 4.2 to describe the Accuracy metric.

\item {\em ``Page 18: Did you select your 1000 and 100 time series randomly?''} \medskip

\textbf{Author response:} There was indeed a oversight on this part. The two subsets of data are selected randomly and the text has been updated

\item {\em ``Write the definition of OWA.''} \medskip

\textbf{Author response:} We agree with the referee and we have added a section describing the OWA in Appendix A.

\item {\em ``The paper has some spelling mistakes and inconsistencies, e.g. in somes cases (Page 6) and SMAE and MASE (used in page 26). Correct the spelling and use the notations consistently.''} \medskip

\textbf{Author response:} We thank the reviewer and the text has been corrected accordingly.
\end{itemize}
\end{document}

### 2022-11-02 signal_processing_elsevier/re-submission_ijf/hermes_paper_LaTeX_source_files/hermes_paper_elsevier.tex
re-submission hermes

--- 2022-11-02 signal_processing_elsevier/submission_ijf/hermes_paper_LaTeX_source_files/hermes_paper_elsevier.tex
@@
 \usepackage{lineno,hyperref}
-%\usepackage[utf8]{inputenc}
-%\usepackage[english]{babel}
-%\usepackage{authblk}
 \usepackage{amssymb,amsmath,amsthm}
-%\usepackage[pdftex]{graphicx}
-%\usepackage{footnote}
-%\usepackage{url}
-%\usepackage{times,dsfont}
-%\usepackage{fancyhdr}
-%\usepackage{geometry}
-%\pagestyle{fancy}
+\usepackage{xcolor}
+\usepackage{pdfpages}
 \modulolinenumbers[5]
@@
 %% Group authors per affiliation:
-\author[mymainaddress,mysecondaryaddress]{Etienne DAVID}
+\author[mymainaddress,mysecondaryaddress]{\'Etienne DAVID}
 
@@
 Our contribution is  twofold.
-We first provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} the first fashion dataset gathering \numberts\ weekly fashion time series.
+We first provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} an appealing fashion dataset gathering \numberts\ weekly fashion time series.
 As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviors of influencers.
@@
 Our approach combines per-time-series parametric models with seasonal components and a global recurrent neural network to include sporadic external signals.
-This hybrid model provides state-of-the-art results on the proposed fashion dataset, on the weekly time series of the M4 competition \cite{makridakis2018m4}, and illustrates the benefit of the contribution of external weak signals.
+This hybrid model provides state-of-the-art results on the proposed fashion dataset, on the weekly time series of the M4 competition \cite{makridakis2018}, and illustrates the benefit of the contribution of external weak signals.
 \end{abstract}
@@
 
-Multivariate time series forecasting is a widespread statistical problem with  many applications, see for instance \cite{sarkka2013bayesian, douc2014nonlinear, zucchini2017hidden} and the numerous references therein.
- %Due to the diversity of applications and use cases, a multitude of models have been proposed. 
+Multivariate time series forecasting is a widespread statistical problem with  many applications, see for instance \cite{sarkka2013, douc2014, zucchini2017} and the numerous references therein.
 Parametric generative models provide explainable predictions with statistical guarantees based on a precise modeling of the predictive distributions of new data based on a record of past observations.
-%The parameters of these models are usually estimated using a sequence of observations of the target time series.
 Calibrating these models, for instance using maximum likelihood inference, often requires a fair amount of tuning to design a time series-specific model to provide  accurate forecasts and sharp confidence intervals.
 Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
-The exponential smoothing model \cite{RePEc:inm:oropre:v:9:y:1961:i:5:p:673-685}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \cite{doi:10.1198/jasa.2011.tm09771}, or the ARIMA with the Box-Jenkins approach \cite{box2015time} are for instance very popular parametric generative models.
+The exponential smoothing model \cite{Brown1961}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \cite{alysha2011}, or the ARIMA with the Box-Jenkins approach \cite{box2015} are for instance very popular parametric generative models.
 Hidden Markov models (HMM) are also widespread and presuppose that available observations are defined using missing data describing the dynamical system.
@@
 Although hidden states are modeled as a Markov chain, the observations arising therefrom have a complex statistical structure.
-%Introducing latent hidden states, they assume that the predictive distribution is not unique and constant in time but multiple and lead by the values of the hidden states changing during time.
 In various applications where signals exhibit non-stationarities such as trends and seasonality, classical HMM are not adapted.
-However, \cite{touron2017modeling}  recently proposed seasonal HMM, assuming that transition probabilities between the states, as well as the emission distributions, are not constant in time but evolve in a periodic manner.
-Strong consistency results were established in \cite{touron2019consistency} and Expectation Maximization based numerical experiments were proposed.
+However, \cite{touron2017}  recently proposed seasonal HMM, assuming that transition probabilities between the states, as well as the emission distributions, are not constant in time but evolve in a periodic manner.
+Strong consistency results were established in \cite{touron2019} and Expectation Maximization based numerical experiments were proposed.
 Although these works provide promising results, HMM are computationally expensive to train and are not yet well studied for seasonal  sequences with thousands of components.
@@
 In this new context, classical time series specific statistical models show limitations when dealing with numerous heterogeneous data.
-Recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \cite{ hochreiter1997long,vaswani2017attention, 8614252, li2019enhancing, lim2019temporal,salinas2020deepar}.
-The DeepAR model proposed in \cite{salinas2020deepar} provides a global model from many time series based on a multi-layer recurrent neural network with LSTM cells.
-More recently, applications using the Transformer model have been proposed  \cite{li2019enhancing}.
-The Temporal Fusion Transformers (TFT) approach is a direct alternative to the DeepAR model \cite{lim2019temporal}.
+Recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \cite{ hochreiter1997,vaswani2017, siami2018, li2019, lim2019,salinas2020}.
+The DeepAR model proposed in \cite{salinas2020} provides a global model from many time series based on a multi-layer recurrent neural network with LSTM cells.
+More recently, applications using the Transformer model have been proposed  \cite{li2019}.
+The Temporal Fusion Transformers (TFT) approach is a direct alternative to the DeepAR model \cite{lim2019}.
 Unfortunately, all these solutions suffer from two main weaknesses.
-Firstly, many of them are black-boxes  as the final forecast usually does not come with a statistical guarantee  although a few recent works focused on measuring uncertainty in recurrent neural networks, see  \cite{martin2020monte}.
-Secondly, without a fine preprocessing and well chosen hyper-parameters, these methods may lead to poor results and be outperformed by traditional statistical models, see \cite{makridakis2018m4}.
+Firstly, many of them are black-boxes  as the final forecast usually does not come with a statistical guarantee  although a few recent works focused on measuring uncertainty in recurrent neural networks, see  \cite{martin2020}.
+Secondly, without a fine preprocessing and well chosen hyperparameters, these methods may lead to poor results and be outperformed by traditional statistical models, see \cite{makridakis2018}.
 
-In this paper, we consider a  new time series forecasting application referred to as {\em fashion trends prediction}.
-Based on a cutting-edge image recognition technology, we built the first fashion dataset containing \numberts\ weekly sequences  of fashion trends on social media  from 01-01-2015 to 01-01-2019.
-This dataset has very appealing properties:  all time series have the same length, no missing value and there is no sparse time series even for niche trends.
-The originality of our dataset comes from the fact that additional external weak signals can also be introduced.
+In this paper, we consider an emerging time series forecasting application referred to as {\em fashion trends prediction}.
+In fashion and retails industries, accurately anticipating consumers' needs is vital and wrong decisions can lead to massive wastes.
+Analysing social media pictures to detect what clothes people are wearing, it is possible to translate the visibility of fashion items over time into time series.
+Consequently, models and algorithms can be trained to accurately anticipate and predict consumers' behaviours.
+In \cite{ma2020}, a  dataset is provided using social media pictures and an image recognition framework to detect several clothes: 2000 fashion time series are proposed with a weekly seasonality.
+However, only 3 years of historical data is available (144 data points) that may not be sufficient for some statistical approaches.
+In \cite{ma2020}, another dataset is presented gathering 8000 fashion sequences with an historical available data  increased to 5 years.
+Nevertheless, only 120 values are available for each fashion time series and the overall volume remains low for a large part of the sequences resulting in a lot of noise and no clear patterns.
+In this paper, we propose a new fashion dataset overcoming the weaknesses of the two previous ones.
+Based on cutting-edge image recognition algorithms \cite{ren2015,chollet2017}, we built a large fashion dataset containing \numberts\ weekly sequences of fashion trends on social media with 5 years of historical data from 01-01-2015 to 30-12-2019.
+This dataset has very appealing properties:  all time series have the same length (261 data points), no missing value and no sparse time series even for niche trends.
+Concerning fashion dynamics, some of them appear to be really volatile with nonlinear changes of dynamics resulting from the emergence of new tendencies.
+In this context, understanding early signals of the apparition of a trend is one of the key to accurately forecast the future of the fashion.
+Consequently, the originality of our dataset comes from the fact that additional external weak signals are introduced.
 With our fashion expertise, we detected several groups of highly influential fashion users.
@@
 They are called weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal.
-With this totally new application, we aim at designing a model able to deal with such a large dataset, leveraging  complex external weak signals and finally providing the most accurate forecasts.
+Figure \ref{fig:oneemergingtrend} shows an example of fashion time series with its linked influencers weak signal.
+Exploring this new way of representing fashion, we aim at designing a model able to deal with such a large dataset, leveraging  complex external weak signals and finally providing the most accurate forecasts.
 
 Recurrent neural networks are appealing to tackle our forecasting problem due to their capability of leveraging external data.
-Recently, hybrid models combining deep neural network (DNN) architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \cite{zhang2003time,jianwei2019novel,bandara2020lstm}.
-The approach providing the most striking results was proposed in  \cite{smyl2020hybrid} in the context of the M4 forecasting competition \cite{makridakis2020m4}.
+Recently, hybrid models combining deep neural network (DNN) architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \cite{zhang2003,jianwei2019,bandara2020}.
+The approach providing the most striking results was proposed in  \cite{smyl2020} in the context of the M4 forecasting competition \cite{makridakis2020}.
 Given a large dataset, a per-time-series multiplicative exponential smoothing model was introduced to estimate simple but fundamental components for each time series and compute a first prediction.
@@
 Finally, a general conclusion and some research perspectives are given in  Section~\ref{sec:conclusion}.
+
+\begin{figure*}
+  \centering
+    \includegraphics[width=1.\linewidth]{br_female_shoes_262}
+  \caption{A shoes trend of the fashion dataset.
+In black the main signal and in orange its associated \textit{fashion-forward} weak signal.
+The sudden explosion of the influencers signal at the end of 2018 announces the future burst of the trend in the mass market.}
+\label{fig:oneemergingtrend}
+\end{figure*}
 
@@
 Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$ and the estimated  parameters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the time-series-specific forecasts $\{\tspred^{pred,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
-$$
+\begin{equation}
+    \label{eq:predictors}
     \tspred^{pred,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i\,.
-$$
-During the M4 competition, the hybrid model of \cite{smyl2020hybrid} was based on a multiplicative exponential smoothing model as the time-series-specific predictor.
+\end{equation}
+During the M4 competition, the hybrid model of \cite{smyl2020} was based on a multiplicative exponential smoothing model as the time-series-specific predictor.
 However, on sporadic time series, this choice leads to poor results and instability.
@@
 In Section~\ref{sec:exp}, two versions of our framework are proposed.
-The first one is based on an  exponential smoothing as a reference similar to the baseline \cite{smyl2020hybrid} and the second one uses a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
+The first one is based on an  exponential smoothing as a reference similar to the baseline \cite{smyl2020} and the second one uses a TBATS model \cite{alysha2011} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
 
@@
 For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence.
-In somes cases, these changes depend on external variables not considered by univariate parametric models.
+In some cases, these changes depend on external variables not considered by univariate parametric models.
 The difficulty is that the exact influence of external variables on the main signal is mostly unknown.
@@
 \centering
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  %\includegraphics[width=\linewidth]{figure/us_female_shoes}
-  %\caption{Time series representing a shoes fashion trend for female in The United States.}
- % \label{fig:introexamples:sub1}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
-  %\centering
-  \includegraphics[width=\linewidth]{figure/br_female_texture_verticalstripe}
- % \caption{Time series representing the vertical stipes texture fashion trend for female in Brazil.}
-  %\label{fig:introexamples:sub2}
-%\end{subfigure}
-\caption{Hermes forecast examples.
+  \includegraphics[width=\linewidth]{br_female_texture_verticalstripe}
+\caption{Hermes forecast example on a time series representing the vertical stipes texture fashion trend for females in Brazil.
 In green the prediction of the TBATS per-time-series predictors.
-In red the final forecast of our HERMES hybrid model.
-Time series representing the vertical stipes texture fashion trend for females in Brazil.}%(Top) Time series representing a shoes fashion trend for females in The United States.
-(Bottom) Time series representing the vertical stipes texture fashion trend for females in Brazil.}
+In red the final forecast of our HERMES hybrid model.}
 \label{fig:introexamples}
@@
 Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$.
-The RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$, $1\leqslant i \leqslant w$ and $k = i - h\lfloor i/h \rfloor$,
+The RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$: for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$,
 $$
-\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+k|T}}{\meants^n_T}\,,\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
+\rnninput^{n,T}_{T-w+i|T} := \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+k|T}}{\meants^n_T}\,,\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
 $$
+where $k = i - h\lfloor i/h \rfloor$ with $\lfloor.
+\rfloor$ the floor function.
+With the numerator part $\ts^n_{T-w+i} -\tspred^{pred,n}_{T+k|T}$, the per-time-series prediction is included in the RNN input and all the fundamental patterns already learned by this first predictor are removed from the time series.
+Then the denominator $\meants^n_T$ is use to rescaled all input at the same level as the time series can have different scales.
+Another option could have been to divide directly  $\ts^n_{T-w+i}$ by $\tspred^{pred,n}_{T+k|T}$ but with time series hitting 0, this option is not valid.
 Let $\rnn(.;\rnnparam)$ be the recurrent neural network model where $\rnnparam$ are  unknown parameters.
@@
 
-Using well-fitted time-series-specific parametric models, the new hybrid network corrects the first form of weakness and provides very good performance on the fashion dataset, see Table~\ref{tab:metricresults}.
+Using well-fitted time-series-specific parametric models, the new hybrid network corrects the first form of weakness and provides appealing performance on the fashion dataset, see Table~\ref{tab:metricresults}.
 Then, to correct the second form of weakness, in addition to the $N$ target time series, $K \times N$ external sequences indexed from $0$ to $T$ are considered.
@@
 Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, a new input for the RNN is defined:
-\begin{align*}
-\fullconcatinput^n_T &= \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}\\
-&= \{\rnninput^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
-\end{align*}
+$$
+\fullconcatinput^n_T = \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}= \{\rnninput^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
+$$
 Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ the final prediction becomes:
-%$$
-%\tspred^n_{T+i|T} 
-%= \etspred^{ets,n}_{T+i|T} +  \rnnmodel(\fullconcatinput^n_T)_{T+i} \times \meants^n_T
-%$$
+
 \begin{align}
@@
   \centering
-    \includegraphics[width=1\linewidth]{figure/HERMES_archi.png}
-  \caption{Architecture of the hybrid model with weak signals.}
+    \includegraphics[width=1\linewidth]{paper_final_framework.png}
+  \caption{Architecture of the hybrid model with weak signals.
+The proposed framework can be decomposed in 5 steps: i) provide a time series.
+ii) (a) fit a first statistical model with the provided time series, (b) compute a first prediction and (c) preprocess the time series for the Global RNN.
+iii) If available, external signals can be added as part of the RNN input.
+iv) With a pre-trained RNN, compute a correction of the first statistical prediction.
+v) Compute the final forecast by adding the first time series prediction and the RNN correction.}
 \label{fig:architecture}
@@
 \label{sec:dataset:a}
-A collection of vision neural networks were designed and trained  at detecting clothes details on pictures: type of clothing (pants, shoes, tops, etc.), form, size, color, texture, etc.
-Then, fashion experts designed fashion trends by aggregating these clothes details: a meaningful combination of items that represent an existing trend in the fashion sphere.
-To finely represent human behaviours based on social media, a group of thousands of random users, called a panel, was created on several geolocalisations.
-Analyzing every day images shared on social networks by these panels with our computer vision algorithms, we can translate the history of thousands of fashion trends in thousands of time series.
-All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
-Each value represents the number of users posts in a week where computer vision algorithms detected the fashion trend.
-As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization}.
+
+Social media have appeared as an impressive data source to follow the evolution of fashion over the time.
+Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world.
+To do it automatically for thousands of trends, the following methodology was introduced.
+In the first place, a complete image dataset of 150 millions pictures is collected from different social media such as Instagram or Weibo.
+We targeted 5 strategic markets for the retail industry using posts localisation: the United States, Europe, Japan, Brazil and China.
+The second step consists in creating a powerful visual recognition framework to be able to detect clothes details on pictures like the type of clothing, the form, the size, the color, the texture, etc.
+To do so, the following framework is designed.
+\begin{enumerate}
+    \item First, an object detection model is trained to detect the position, the size and the general type of possible multiple fashion items on a picture.
+This localization model is based on the Faster-RCNN architecture introduced in \cite{ren2015}.
+Starting from weights trained on MS-COCO \cite{lin2014}, a fine-tune of the model is done on our data with a standard setup following the original paper.
+    \item  Additionally, several visual recognition models are trained at classifying a rich collection of 350 fashion details.
+We train one classifier for each category of fashion item: one for pants, another for tops, a third for shoes, etc.
+These models are all based on the Xception architecture introduced in \cite{chollet2017}.
+So as to trained them, large amount of social media pictures (between 200k and 800k training images depending on the category) have been manually tagged to constitute meaningful training datasets depending on the classification task.
+Architectures are first initialized with public weights trained on ImageNet \cite{russakovsky2014} and then fine tuned on the manually labeled dataset corresponding to their task.
+\end{enumerate}
+
+At inference time, we first apply the localisation model which predicts boxes of generic fashion items (tops, pants, shoes, dresses, etc.) for each image.
+Then, each fashion item is cropped from its full image, resized to the classifiers' input size ($299\times299\,$px) and fed into the related classifier: a top will be fed into the model trained on tops, etc.
+We obtain for each image a set of boxes, associated with a general category and a set of fine-grain attributes describing this object.
+As a final step, fashion experts aggregate those attributes to define relevant trends for the fashion and retails industry.
+
+The 150 million of social media pictures are analyzed with the visual recognition pipeline described below.
+Out of those images, we detected clothes in 96 millions posts making the final dataset used in this paper.
+We aggregate results by fashion trend definition over the time and  thousands of trends are finally translated from social media to time series.
+We note $y^{c,g,m,i}$ the final raw sequence representing the fashion trend $i$ of the cloth type $c$ for the gender $g$ on market $m$.
+At each time t, $y^{c,g,m,i}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $i$ of the cloth type $c$ for the gender $g$.
+
+As an illustration, an example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.
+
+\subsection{Fashion time series}
+\label{sec:dataset:b}
+
+Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences in order to remove bias.
+Thus, we define the following normalizing signal $\Tilde{y}^{c,g,m}$.
+This signal represents the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe).
+With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \cite{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$.
+The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$.
+Finally, for any fashion trend $i$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
+\begin{equation}
+    y^{i}_t = \frac{y^{c,g,m,i}_{t}}{\bar{y}^{c,g,m}_t}\,,
+\end{equation}
+where T denotes the number of available time steps.
+The time series $y^{c,g,m,i}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences.
+With this normalizing step, a majority of the social media bias are removed and the final normalized sequences are expressed in share of category.
+As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}.
+The raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.
+
+\begin{figure*}
+\centering
+  \includegraphics[width=1.\linewidth]{cn_female_top_raw}
+  \includegraphics[width=1.\linewidth]{cn_female_top_norm}
+\caption{Example of difference between the raw sequence and the normalized one for the Jersey top fashion trend for females in China.
+In this example, we normalize by the deseasonalized global top fashion trend for females in China.
+(Top) Time series representing the raw signal of the Jersey top fashion trend for females in China.
+(Bottom) Time series representing the normalized signal of the Jersey top fashion trend for females in China.}
+\label{fig:normalization}
+\end{figure*}
+
+\subsection{Weak signal}
+
+In theoretical fashion dynamics \cite{rogers1962}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
+So as too catch the early signal of the emergence of a trend, 6000 social media influencers were selectioned by hand by fashion experts.
+Aggregating them, a specific ``fashion-oriented`` panel is created.
+With the same methodology as for the main panel described in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created.
+We named \textit{fashion-forwards} this weak signal.
+For all fashion sequence $\{y^i_t\}_{1 \leq t \leq T}$, let $\{\ts^{f,i}_t\}_{1 \leq t \leq T}$ be the normalized sequence representing the behaviours of influencers regarding the fashion trend $i$.
+As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for the hybrid model: for all $t \in \{1,\ldots,T\}$ and any fashion trend $i$,
+$$
+\ws^{f,i}_{t} = \frac{\ts_t^{f,i}}{\ts_t^{f,i}+\ts_t^{i}}\,.
+$$
+where T denotes the number of available time steps.
+Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.
+For instance, an impressive emerging fashion shoes trend with its \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
 
 \subsection{Fashion dataset}
-\label{sec:dataset:b}
 
-Due to the increasing use of social media and behaviour changes, a normalization step is applied to the raw sequences.
-Each fashion trend is divided by its hierarchical parent category trend.
-Moreover, in order to avoid removing the seasonality of all sequences, we deseasonalized the hierarchical parent category trend before the normalization.
-For instance, as displayed in Figure~\ref{fig:normalization}, the raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.
-The final normalized sequence is expressed in share of category.
-
-We therefore introduce a new dataset for fashion time series forecasting.
-It contains a sample of $\numberts$ anonymized and  normalized fashion trends for men and women, in 9 different categories and 5 geozones.
-An overview of it can be found in Table~\ref{tab:fashiondataset}.
+With this paper, we provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} a sample of $\numberts$ normalized fashion trends for men and women, over 9 different categories and 5 different markets.
+Each sequence has 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
 This collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry.
@@
 A central point of this work is to accurately detect and forecast such trends.
-
-\begin{figure*}
-\centering
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/cn_female_top_raw}
-%  \caption{Time series representing the raw signal of a top fashion trend for female in China}
- % \label{fig:normalization:sub1}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/cn_female_top_norm}
-  %\caption{Time series representing the normalized signal of a top fashion trend for female in China.}
-  %\label{fig:normalization:sub2}
-%\end{subfigure}
-\caption{Example of difference between the raw sequence and the normalized one.
-In this example, we normalize by the deseasonalized global top fashion trend for females in China.
-(Top) Time series representing the raw signal of a top fashion trend for females in China.
-(Bottom) Time series representing the normalized signal of a top fashion trend for females in China.}
-\label{fig:normalization}
-\end{figure*}
+In addition, each fashion time series is linked with its associated normalized fashion forward signal as presented in the section above.
+An overview of the dataset can be found in Table~\ref{tab:fashiondataset}.
 
@@
 \end{table*}
-
-\subsection{Weak signal}
-
-In theoretical fashion dynamics \cite{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
-%In this way, a weak signal for each sequence is added to the proposed dataset.
-Numerous social media influencers were selectioned by hand by fashion experts.
-By aggregating them, a specific ``fashion-oriented`` panel is created.
-With the same methodology as for the main panel described in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created.
-We named \textit{fashion-forwards} this weak signal.
-For all trends $\{y_t\}_{1\leqslant t\leqslant T}$, let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
-As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for our hybrid model:  for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
-$$
-\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}\,.
-$$
-Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.
-For instance, an impressive emerging fashion shoes trend with its \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
-
-%Secondly, depending of the number of followers, the general panel of users is divided in three sub-groups: users with less than 1350 followers, users with a number of followers between 1350 and 7000 and users with more than 7000 followers.
-Repeating the previous methodology on each sub-panel, three normalized time series for each time series are created.
-Again, the motivation here is to detect behaviour gaps between different parts of the society that could lead to changes in the main signal.
-Let $\ts_t^{\ell,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{\ell,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences.
-Two inputs for our hybrid model are computed: for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
-%\begin{align*}
-%\ws^{\ell,n}_{t} = \frac{\ts_t^{\ell,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}
-%\end{align*}  
-%values close to 0.3 indicate a similar behaviour between the three sub-panels and the general panel.
-%
-%In addition to the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{\ell}$ and $\ws^{h}$ are added.
-They are frequently sparse for micro trends and they often lack interest in common fashion trends.
-However, in several examples, they are fundamental to detect the future fashion evolutions, as illustrated in Section~\ref{sec:exp}.
-
-\begin{figure*}
-  \centering
-    \includegraphics[width=1.\linewidth]{figure/ff_example}
-  \caption{A shoes trend of the fashion dataset.
-In black the main signal and in red its associated \textit{fashion-forward} weak signal.
-The shift between these two signals at the end of 2017/beginning of 2018 announces the future burst of the trend.}
-\label{fig:oneemergingtrend}
-\end{figure*}
 
@@
 
-For the first parametric per-time-series models, existing Python or R libraries are used to estimate the different parameters $\statparam^n$.
+For the first parametric per-time-series models, existing Python  libraries named \texttt{statsmodels} and  \texttt{tbats} are used to estimate the different parameters $\statparam^n$.
 Depending of the choice of local parametric models, two versions of HERMES are proposed.
-The first one uses as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}.
-The second one uses the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves the best accuracy results on the fashion dataset.
-The neural network architecture is summarized in Figure~\ref{fig:rnn_architecture}.
-It is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
+The first one uses as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020}.
+The second one uses the TBATS model of \cite{alysha2011} and  achieves the highest accuracy results on the fashion dataset.
+The neural network architecture is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
 A classical Adam optimizer is used with a learning rate set at 0.001 or 0.005, the batch size is fixed to 64 and the loss function is defined as follows:
@@
 This choice of $\mathrm{L}_1$ loss function is motivated by its robustness to outliers which accounts for some time series in the fashion industry with very specific behaviors.
-The loss and previous parameters are all set with a grid search (additional materials can be found in Appendix~B).
+The loss and previous parameters are all set with a complete grid search.
+See Appendix~\ref{sec:heuritechgridsearch} for additional results concerning the loss function choice and Appendix~\ref{sec:m4gridsearch} for a complete grid search example.
 The code is developed in Python using the Tensorflow library.
@@
 
-\begin{figure}
-  \centering
-    \includegraphics[width=0.8\linewidth]{figure/lstm_archi}
-  \caption{Architecture of the RNN corrector part of the HERMES framework. The same architecture is used in the \textit{lstm} benchmark model.}
-\label{fig:rnn_architecture}
-\end{figure}
-
 \subsection{Benchmarks, hybrid models and Metrics}
+\label{sec:fashiontraining}
 
@@
 Finally, \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters.
-A complete description and references for these models can be found in \cite{hyndman2020package}.
+A complete description and references for these models can be found in \cite{hyndman2020}.
 As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.
@@
 With this threshold, the proposed fashion dataset is almost balanced on the {\em test} set: There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends.
-%On the {\em test} set, for each method, the accuracy is defined as follows:
-%\begin{align*}
-%\mathrm{ACCURACY} &= \frac{TP}{TP + FP}\,,
-%\end{align*}
-%where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series misclassified in the class $i$.
+To compare the different methods on this classification task, the ACCURACY metric, defined as the percentage of correct classification, is used.
 
-\subsection{Result for Heuritech Fashion dataset}
+\subsection{Result for the Fashion dataset}
 
-\textbf{10000 Heuritech Fashion time series global accuracy.
+\textbf{10000 Fashion time series global accuracy.
 }For the two metrics and for each model, we compute the average on all sequences in the final year.
@@
 Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slightly outperform the alternatives in terms of MASE and are stable across the different trainings.
-Regarding \textit{hermes-ets},   although it is very similar to the baseline \cite{smyl2020hybrid}, its accuracy remains low in comparison to the \textit{lstm} benchmark or HERMES using TBATS.
+Regarding \textit{hermes-ets},   although it is very similar to the baseline \cite{smyl2020}, its accuracy remains low in comparison to the \textit{lstm} benchmark or HERMES using TBATS.
 
@@
   \caption{\textit{tbats}, \textit{hermes-tbats} and \textit{hermes-tbats-ws} models confusion matrix}
-  %\vspace{0.2cm}
-  %\textit{tbats} model confusion matrix \\
-  %\par \textit{tbats} model confusion matrix
-  %\vspace{0.2cm}
 \centering
@@
 \textbf{Size of the dataset.
-} In addition to the results on the fashion dataset gathering 10000 time series, the behaviour of the HERMES model is analyzed when it is trained on smaller datasets: two experiments were performed, HERMES models were trained on a reduced dataset of 1000 time series and on a reduced dataset of 100 time series.
+} In addition to the results on the fashion dataset gathering 10000 time series, the behaviour of the HERMES model is analyzed when it is trained on smaller datasets: two experiments were performed, HERMES models were trained on a reduce dataset of 1000 time series and on a reduced dataset of 100 time series.
+Both samples of time series are selected randomly.
 Results are given in Table~\ref{tab:1000metricresults}.
 
-First, the hybrid framework \textit{hermes-tbats} achieves the best performance in terms of global accuracy on both datasets.
-Due to the strength of its per-time-series predictor TBATS, the hybrid model succeeds at correcting TBATS  and reaches a satisfactory final accuracy.
-Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases.
-On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms its accuracy level.
+The hybrid framework \textit{hermes-tbats} achieves the best performance in terms of global accuracy on both datasets. 
+We can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases.
+On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms the \textit{lstm}.
 Providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require  large amounts of data to do so.
-Nevertheless, with the HERMES framework, the RNN task is largely simplified.
 Our model needs less data to be trained and to obtain interesting performance.
@@
   \caption{Results summary on the 1000 time series and 100 time series Fashion dataset.
-The MASE average on all our time series is computed.
+The MASE average on all the time series is computed.
 For the two approaches using a neural network, 10 models with different seeds are trained.
@@
 \subsection{Result for M4 weekly dataset}
+\label{sec:m4result}
 
-We also assessed the performance of HERMES using the M4 weekly dataset \cite{makridakis2020m4}.
-The M4 dataset gathers 359 weekly time series and has 3 main differences compared to our proposed fashion dataset.
-Firstly, sequences do not have the same length with sequence lengths lying between 93 and 2610 time steps.
-Secondly, as some of the sequences represent financial signals or some others are demographic sequences, the  359 time series have very distinct scales and dynamics.
-Thirdly, compared to the previous fashion application, the time horizon of the prediction is set to 13 for the weekly dataset.
+We also assessed the performance of HERMES using the M4 weekly dataset \cite{makridakis2020}.
+The M4 dataset gathers 359 weekly time series and has 3 main differences compared to the proposed fashion dataset.
+Firstly, sequences do not have the same length with sequences lying between 93 and 2610 time steps.
+Secondly, the 359 time series come from different sectors such that finance or Industry.
+Accordingly, they have very distinct scales and dynamics.
+Thirdly, compared to the previous fashion application, the time horizon of the prediction is set to 13 for the weekly dataset and no additional external signals are provided.
 
-\textbf{Training.
-} The M4 dataset is firstly preprocessed.
-This preliminary step is motivated by two reasons.
-First, as some sequences are short (93 time steps), they limit the window size $w$ of the RNN part and consequently the global accuracy of the HERMES approach.
-Second, the longer time series slow down the training of the collection of the first predictors especially for complex methods like TBATS.
-We kept 300 time steps  for each sequence in order to train the HERMES model.
-For the shorter sequences, the train set is duplicated in order to reach the length of 300.
-Longer sequences are cropped in order to keep the last 300 time steps.
-%The sequences are firstly resized in order to obatain a dataset with fixed time horizon.
-The eval and the test sets are removed for the shortest sequences (the last 26 steps).
-Then, the remaining number of entire year is duplicated in order to egalize all the sequence at the longest one : 2610 time steps \textcolor{red}{Pas sur de comprendre, reformuler}.
-As per time series parametric model training time depends on the sequence length, all time series are then croped.
-Finally, with the addition of the previously removed eval and test sets, 300 time steps are kept for each sequence \textcolor{red}{Pas sur de comprendre, reformuler}.
-
-The horizon $h$ is set to 13  and the window size $w$ is set to 104.
-For the RNN part, the same architecture as the one described in Figure~\ref{fig:rnn_architecture} is used.
-The Adam optimizer is used with a learning rate  equal to  0.005 and a batch size set to 8.
-As the M4 weekly dataset is small, a rolling window is used on the train set in order to increase the train number of examples and improve training results.
-Three windows are computed for each sequence for the RNN train set.
+\textbf{Training. }
+The M4 dataset is preprocessed as follows. As some sequences are short (93 time steps), they limit the window size $w$ of the RNN.  
+Consequently, 300 time steps are kept for each sequence.
+shorter sequences are duplicated in order to reach the length of 300 and longer sequences are cropped so as to keep the last 300 time steps.
 An overview of our train, eval, test set split and the resizing of the shortest sequences is given in Figure~\ref{fig:m4dataset}.
-The previous parameters: window size, learning rate, batch size and the number of train windows per time series are set using a grid search, see Appendix~B.
+Secondly, several M4 weekly time series have a large volume and a high level of variability.
+Consequently, Equation~\ref{eq:predictors} of the HERMES framework is changed to:
+\begin{equation}
+    \tspred^{pred,n}_{T+i|T} =\mbox{exp}\left( \stat^n(log\left(\ts^n_{1:T}\right);\statparam^n)_i\right)\,.
+\end{equation}
+This simple modification increases significantly the accuracy of the per-time-series predictors tested on the M4 weekly dataset while reducing the fitting time.
+As for the fashion dataset, a complete grid search is done on the M4 weekly dataset to fix hyperparameters of the HERMES architecture.
+The horizon $h$ is set to 13 and the window size $w$ to 104.
+For the RNN part, the same architecture as described in Section~\ref{sec:fashiontraining} is used.
+The Adam optimizer is used with a learning rate equal to  0.0005, the batch size is set to 8 and the MASE is directly used as the loss function.
+Finally a rolling window is applied on the train set so as to increase the number of examples and improve the training process.
+Three windows are computed per sequence for the RNN train set.
+Results of the grid search on the M4 weekly dataset can be found in \ref{sec:m4gridsearch}.
 
@@
   \centering
-    \includegraphics[width=1.\linewidth]{figure/M4_dataset}
+    \includegraphics[width=1.\linewidth]{M4_dataset}
   \caption{One of the shortest sequences of the M4 weekly dataset (93 time steps).
-In order to fit its predictor, the last complete year is duplicated in order to reach a total length of 300 time steps.}
+In order to fit its predictor, the last complete year of the train set is duplicated in order to reach a total length of 300 time steps.}
 \label{fig:m4dataset}
@@
 
-\textbf{Benchmarks.
-} The M4 competition provides a rich collection of benchmarks emcompassing statistical models and neural network approaches.
-The same candidates are used in this part as baselines.
+\textbf{Evaluation.
+} The proposed model is evaluated along with a rich collection of benchmarks provided by the M4 competition, encompassing statistical models and neural network approaches.
 In addition, the hybrid model named \textit{Uber} of S.Smyl is added.
-For a complete description and references of the benchmark models, see \cite{makridakis2020m4}.
+For a complete description and references of the benchmark models and the hybrid model \textit{Uber}, see \cite{makridakis2020} and \cite{smyl2020}.
 As a HERMES candidate, a version using TBATS is proposed and called \textit{hermes-tbats}.
-Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measures.
-A complete definition of these metrics is proposed in \cite{makridakis2020m4}, see also Appendix~\ref{sec:m4overview} for additional information about the M4 weekly dataset.
+We propose a focus on the top 3 models reaching the highest accuracy on the M4 weekly dataset.
+These three methods are based on an ensembling and combine various approaches.
+The first model is presented in \cite{darin2020} and called \textit{Darin \& Stellwagen}.
+The second model is introduced in \cite{petropoulos2020} and called \textit{Petropoulos \& Svetunkov}.
+Finally, a description of the third model  called \textit{Pawlikowski, et al.} can be found in \cite{pawlikowski2020}.
+An ensembling combining 4 HERMES variations is proposed.
+It is based on the FFORMA algorithm introduced in \cite{montero2020} and called \textit{fforma-hermes}.
+A complete description of the training process of the proposed ensembling is given in \ref{sec:fforma-hermes}.
+Following the M4 competition methodology, all the candidates are evaluated according to the MASE, the SMAPE and the OWA measures.
+A complete definition of these metrics is proposed in \cite{makridakis2020} and summarized in \ref{sec:m4overview}.
+See also \ref{sec:m4overview} for additional information about the M4 weekly dataset.
 
@@
 The HERMES approach \textit{hermes-tbats} outperforms all the benchmarks.
-This result is partially induced by the use of TBATS per-time-series predictors which achieves very good results on the test set.
+This result is partially induced by the use of TBATS per-time-series predictors which achieve impressively good results on the test set.
 Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}.
-With this second application, two important conclusions can be made.
-Firstly, the results provided by \textit{hermes-tbats} confirm that the HERMES approach is a general framework, well suited for a large collection of forecasting tasks.
-Secondly, the accuracy gap between the two hybrid candidates validates the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.
+For the ensembling methods, the proposed FFORMA model with 4 HERMES variations \textit{fforma-hermes} reaches the same high level of accuracy as the top 3 methods of the competition on the weekly dataset.
+The results provided by \textit{hermes-tbats} confirm that the HERMES model is well suited for a large collection of forecasting tasks even difficult ones with small datasets, heterogeneous time series and the absence of  additional useful external signals.
+Secondly, the accuracy gap between the proposed hybrid model and the approach proposed in \cite{smyl2020} illustrates the importance of a global framework able to leverage any kind of per-time-series predictors depending of the use cases.
+Finally, our model can be easily included as part of an ensembling method to improve the final robustness and accuracy of the predictions.
 
@@
      \textit{Damped} && 8.866 && - &&& 2.404 && - &&& 0.917 && - &\\
-     \textit{S.Smyl} \cite{hyndman2020package} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
-     \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.841 && - &\\
-     \textit{\textbf{hermes-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
-    %\hline
+     \textit{Uber} \cite{smyl2020} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
+     \textit{tbats} && 7.409 && - &&& 2.204 && - &&& 0.801 && - &\\
+     \textit{\textbf{hermes-tbats}} && \textbf{7.383} && 0.016 &&& \textbf{2.191} && 0.010 &&& \textbf{0.797} && 0.002 &\\
+    \hline
+    \textit{Pawlikowski, et al.} && 6.919 && - &&& 2.158 && - &&& 0.766 && - &\\
+    \textit{Petropoulos \& Svetunkov} && 6.726 && - &&& 2.133 && - &&& 0.751 && - &\\
+    \textit{Darin \& Stellwagen} && \textbf{6.582} && - &&& 2.107 && - &&& 0.739 && - &\\
+    \textbf{\textit{fforma-hermes}} && 6.614 && - &&& \textbf{2.058} && - &&& \textbf{0.732} && - &\\
+
   \end{tabular}
@@
 \label{sec:conclusion}
-The motivation of this paper was to present HERMES, a new hybird model for non stationary time series forecasting.
+In this paper, we propose  a new hybird model for non stationary time series forecasting.
 By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks.
 Furthermore, this new model is totally suited to deal with external signals.
-With a fine pre-processing and a well-designed architecture, our hybrid framework succeeds at leveraging our complex extra data and reaches very promising accuracy levels in terms of classification.
-In addition to this article, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided.
-We believe that this dataset contains really fine dynamics and interactions where complex models would express their potential.
+With a fine pre-processing and a well-designed architecture, the proposed hybrid framework succeeds at leveraging complex extra data and reaches promising accuracy levels.
+In addition, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided.
 By making it publicly available\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}}, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
 As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.
-Focusing on the examples with huge changes of behaviours, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works.
+Focusing on the examples with important changes of behaviours, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works.
 In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses.
@@
 
-%\appendices
+\appendix
 
-%\renewcommand{\thetable}{A\arabic{table}}
-%\renewcommand{\thefigure}{A\arabic{figure}}
-%\setcounter{table}{0}
-%\setcounter{figure}{0}
+\section{M4 weekly dataset, Ensembling training and results}
 
-\section*{Appendix A. M4 weekly dataset and results}
+\subsection{M4 weekly dataset}
 \label{sec:m4overview}
-
 The M4 weekly dataset is a collection of 359 time series with  contrasting behaviours and sizes.
 An overview of the dataset is given in Table~\ref{tab:m4dataset} and some examples of sequences are given in Figure~\ref{fig:m4examples}.
-As sequences come from a wide diversity of sectors, the forecasting task is very challenging.
-However, on some examples as in Figure~\ref{fig:m4pred}, efficient corrections of the TBATS forecasts can be obtained.
+This use case is not properly suited for the HERMES approach as the dataset is small and there is no clear link between time series.
+Moreover, no additional external signals are available that could help the RNN part to correct the first errors of the per-time-series predictors.
 
@@
 \begin{figure}
-%\centering
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W10}
-%  \caption{A time series from the ``Other`` category called \textit{W10}.}
+  \includegraphics[width=1.\linewidth]{W10}
   \label{fig:m4examples:sub1}
-%\end{subfigure} \quad
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W20}
-%  \caption{A time series from the ``Macro`` category called \textit{W20}.}
-%  \label{fig:m4examples:sub1}
-%\end{subfigure}
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W220}
-%  \caption{A time series from the \textit{Finance} category called \textit{W220}.}
-%  \label{fig:m4examples:sub2}
-%\end{subfigure}\quad
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-%  \includegraphics[width=1.\linewidth]{figure/W354}
-%  \caption{A time series from the \textit{Micro} category called \textit{W354}.}
-%  \label{fig:m4examples:sub3}
-%\end{subfigure}
+  \includegraphics[width=1.\linewidth]{W20}
+  \includegraphics[width=1.\linewidth]{W220}
 \caption{Examples of time series from the M4 weekly dataset.
@@
 \centering
-% \begin{subfigure}{1.\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W133_pred}
-%  \caption{\textit{tbats} and \textit{hermes-tbats} forecast of the \textit{W133} time series}
-%  \label{fig:m4pred:sub1}
-% \end{subfigure}
-% \begin{subfigure}{1.\textwidth}
-%  \centering
-  \includegraphics[width=1.\linewidth]{figure/W314_pred}
-%  \caption{\textit{tbats} and \textit{hermes-tbats} forecast of the \textit{W314} time series}
-%  \label{fig:m4pred:sub2}
-% \end{subfigure}
-\caption{\textit{hermes-tbats} forecast examples on the M4 weekly dataset.
-In green the prediction of the per-time-series predictors \textit{tbats}.
-In red the final forecast of our HERMES hybrid model \textit{hermes-tbats}.
-(Top) the \textit{W133} time series, (Bottom) the \textit{W314} time series.}
+  \includegraphics[width=1.\linewidth]{w133_hermes_prediction.png}
+  \includegraphics[width=1.\linewidth]{w262_hermes_prediction.png}
+\caption{forecast examples of HERMES variations on 2 time series of the M4 weekly dataset.
+At the top, the \textit{W133} time series is displayed with the prediction of the per-time-series predictor \textit{thetam} (green) and the final forecast of the HERMES hybrid model \textit{hermes-thetam} (red).
+At the bottom, the \textit{W262} time series is represented with the corresponding prediction of the per-time-series predictors \textit{ets-add} (green) and the HERMES correction of \textit{hermes-ets-add} (red).}
 \label{fig:m4pred}
@@
 
-%Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset.
-Except one approach, all of them are a combination of different models in order to increase the robustness of the final forecast and at the same time achieve a better global accuracy.
-The remaining one is not an ensembling but a statistical framework called \textit{Forecast Pro}.
-It is not a single statistical model but a framework that chooses, depending on the sequence properties, the best statistical approach.
-With a OWA equal to 0.739, it outperforms the \textit{hermer-tbats} and all the M4 proposed models on the M4 weekly sub-dataset.
-A description and interesting remarks about the \textit{Forecast Pro} model are discussed in \cite{DARIN2020135}.
-This model offers an interesting research perspective specifically for the M4 weekly forecasting task.
-Looking at the final results of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset.
-All of them are ensemble frameworks: methods that mix different kinds of approaches to reach a higher final accuracy.
-As the M4 weekly dataset gathers really heterogeneous sequences, combining several methods to leverage their strengths appear to be a promising way.
-However in this paper, only individual models were evaluated in order to provide a fair comparison with the HERMES framework.
+\subsection{M4 accuracy metrics}
+\label{sec:m4metric}
 
-\section*{Appendix B. Training parameters and loss}
+The M4 competition proposes 3 metrics to evaluate the different approaches: the mean absolute scaled error (MASE), the symmetric mean absolute percentage error (SMAPE) and the overall weighted average (OWA).
+MASE and SMAPE are defined as follow:
+\begin{align*}
+&\mathrm{MASE} = \frac{T-m}{h}\frac{\sum_{j=1}^h |Y_{T+j} - \hat{Y}_{T+j}| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,
+&\mathrm{SMAPE} = \frac{2}{h}\sum_{j=1}^h\frac{|Y_{T+j} - \hat{Y}_{T+j}|}{|Y_{T+j}| + |\hat{Y}_{T+j}|}\,,
+\end{align*}
+where h is the forecast horizon and m the length of the seasonality.
+The final OWA is computed by following these steps: i) compute the average MASE and SMAPE of a model.
+ii) Divide the previous results by the MASE and SMAPE computed with the benchmark method \textit{snaïve}.
+iii) Compute the OWA as the average of the relative MASE and SMAPE obtained is step ii).
+As an example on the m4 weekly dataset, the method \textit{hermes-tbats} gets a MASE of 7.383 and a SMAPE of 2.191.
+The benchmark method \textit{snaïve} obtains a MASE of 9.161 and a SMAPE of 2.777.
+Thus the OWA of  \textit{hermes-tbats} is equal to 0.797.
+\begin{equation*}
+    OWA_{\textit{hermes-tbats}} = \frac{1}{2}(\frac{7.282}{9.161} + \frac{2.191}{2.777}) \approx 0.797
+\end{equation*}
+
+\subsection{FFORMA ensembling with HERMES variations}
+\label{sec:fforma-hermes}
+
+In this section, a complete description of the proposed ensembling on the M4 weekly dataset is provided.
+In a first time, 4 HERMES variations are trained using different per-time-series predictors.
+The first one called \textit{hermes-tbats} uses TBATS and is presented in Section~\ref{sec:m4result}.
+The second version is called \textit{hermes-thetam} and use the Thetam method provided with the Python package \texttt{statsmodels}.
+The two remaining variations use as per-time-series predictors an additive or multiplicative exponential smoothing and are called respectively \textit{hermes-ets-add} and \textit{hermes-ets-mul}.
+As for Thetam, the Python package \texttt{statsmodels} is used to fit the different exponential smoothing models.
+Concerning the HERMES architecture, for simplicity, hyperparameters described in Section~\ref{sec:m4result} are used for each version but a grid search could have be run for each of them.
+10 models are trained per version with different seeds and the best one based on the eval set is kept for the ensemble model.
+In a second time, the FFORMA ensembling introduced in \cite{montero2020} is used to combine the 4 HERMES methods.
+The R package \texttt{M4metalearning} containing the FFORMA model is directly used without change of the hyperparameters, imported in Python with the library \texttt{Rpy2} and combined with the HERMES code base.
+
+\subsection{M4 weekly dataset results}
+
+In addition of the results provided is Section~\ref{sec:m4result}, Table~\ref{tab:m4hermesvariationsresults} displays the results of all the HERMES variations included in the FFORMA ensembling as well as the accuracy of the per-time-series predictors.
+In each cases, HERMES approaches always improve the predictors accuracy.
+These improves can appear slight but are justified regarding the absence of link between time series and the absence of additional useful external signals.
+Nevertheless, efficient corrections can be obtained on some examples as displayed in Figure~\ref{fig:m4pred}.
+
+\begin{table}
+  \caption{Results summary on the m4 weekly dataset of the HERMES variations.
+For each metric, the average on all the time series is computed.
+For approaches using a neural network, 10 models are trained with different seeds.
+The mean and the standard deviation of the 10 results are displayed.
+For the statistical models \textit{ets-add}, \textit{ets-mul} and \textit{thetam}, the Python package {\texttt{statsmodels}} is used.
+The Python package \texttt{tbats} is used for the \textit{tbats} approach.}
+  \centering
+  \resizebox{\textwidth}{!}{
+  \begin{tabular}{l||lllll|lllll|lllll}
+   &&\multicolumn{3}{c}{\textbf{SMAPE}} &&& \multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{OWA}}&\\
+    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}&&&  \textit{mean}  && \textit{std}& \\
+	 \hline
+	 &&&&&&&&&&\\
+     \textit{ets-mul} && 8.933 && - &&& 2.412 && - &&& 0.922 && - &\\
+     \textit{hermes-ets-mul} && 8.889 && 0.021 &&& 2.377 && 0.016 &&& 0.913 && 0.004 &\\
+     \textit{ets-add} && 8.929 && - &&& 2.410 && - &&& 0.921 && - &\\
+     \textit{hermes-ets-add} && 8.880 && 0.022 &&& 2.377 && 0.016 &&& 0.913 && 0.004 &\\
+     \textit{thetam} && 7.609 && - &&& 2.377 && - &&& 0.843 && - &\\
+     \textit{hermes-thetam} && 7.590 && 0.012 &&& 2.359 && 0.010 &&& 0.839 && 0.002 &\\
+     \textit{tbats} && 7.409 && - &&& 2.204 && - &&& 0.801 && - &\\
+     \textit{\textbf{hermes-tbats}} && \textbf{7.383} && 0.016 &&& \textbf{2.191} && 0.010 &&& \textbf{0.797} && 0.002 &\\
+  \end{tabular}
+  }
+\label{tab:m4hermesvariationsresults}
+\end{table}
+\section{Training parameters and loss}
 
@@
 For each loss, 10 \textit{hermes-tbats-ws} models have been trained with different seeds and the final mean and standard deviation are given in Figure~\ref{fig:loss_function}.
-The final Scaled Mean Absolute Error reaches the lowest MASE and was selected to train all the HERMES model in this paper.
+The final Scaled Mean Absolute Error reaches the lowest MASE and was selected to train all the HERMES models on the Fashion dataset.
 
@@
 For instance, an overview of the learning rate, batch size and number of windows per time series grid search for the M4 weekly dataset is shown in Figure~\ref{fig:m4parameter}.
-For each parameter, a collection of 10 \textit{hermes-tbats} models have been trained with a range of values and the final OWA was calculated.
+For each parameter, a collection of 10 \textit{hermes-tbats} models have been trained with different seeds and the final OWA was calculated.
 As in the Figure~\ref{fig:loss_function}, the mean and the standard deviation of each group of 10 trainings is computed.
@@
 \centering
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/m4_nb_of_window}
-  %\caption{result of the HERMES model on the M4 dataset model depending of the number of windows provided per time series to the RNN corrector}
- % \label{fig:m4parameter:sub1}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
- % \centering
-  \includegraphics[width=1.\linewidth]{figure/m4_batch_size}
-  %\caption{result of the HERMES model on the M4 dataset model depending of the size of the batch size}
-  %\label{fig:m4parameter:sub2}
-%\end{subfigure}
-%\begin{subfigure}{1.\textwidth}
-  %\centering
-  \includegraphics[width=1.\linewidth]{figure/m4_learning_rate}
-  %\caption{result of the HERMES model on the M4 dataset model depending of learning rate of the optimizer}
-  %\label{fig:m4parameter:sub3}
-%\end{subfigure}
-\caption{OWA for the \textit{hermes-tbats} model on the M4 weekly dataset depending on 3 parameters used during the RNN training: Number of moving windows per time series, the batch size and the learning rate.
+  \includegraphics[width=.49\linewidth]{m4_sliding_window.png}
+  \includegraphics[width=.49\linewidth]{m4_learning_rate.png}
+  \includegraphics[width=1.\linewidth]{m4_batch_size.png}
+  \includegraphics[width=.49\linewidth]{m4_window_size.png}
+  \includegraphics[width=.49\linewidth]{m4_lstm_dim.png}
+\caption{OWA for the \textit{hermes-tbats} model on the eval set of the M4 weekly dataset.
+5 hyperparameters used during the RNN training are tested: the number of moving windows per time series (top left), the learning rate (top right), the batch size (middle), the window size for the RNN input (bottom left) and the dimension of the LSTM layers output (bottom right).
 For each parameter, 10 models with different seeds have been trained.
-The mean and the standard deviation are represented with a point and a vertical.
-(Top) Result of the HERMES model depending on the number of windows provided per time series to the RNN corrector.
-(Middle) Result of the HERMES model depending on the size of the batch size.
-(Bottom) Result of the HERMES model depending on the learning rate of the optimizer.}
+The mean and the standard deviation of the OWA on the eval set are represented with a point and a vertical line.}
 \label{fig:m4parameter}
 \end{figure}
-
-\section*{References}
 

### 2023-01-16 signal_processing_elsevier/re-submission_ijf/hermes_paper_LaTeX_source_files/hermes_paper_elsevier.tex
update ijf re-submission

@@
 The loss and previous parameters are all set with a complete grid search.
-See Appendix~\ref{sec:heuritechgridsearch} for additional results concerning the loss function choice and Appendix~\ref{sec:m4gridsearch} for a complete grid search example.
+See \ref{sec:fashiongridsearch} for additional results concerning the loss function choice and \ref{sec:m4gridsearch} for a complete grid search example.
 The code is developed in Python using the Tensorflow library.
@@
   \centering
-    \includegraphics[width=1.\linewidth]{M4_dataset}
+    \includegraphics[width=1.\linewidth]{m4_dataset}
   \caption{One of the shortest sequences of the M4 weekly dataset (93 time steps).
@@
 \begin{figure}
-  \includegraphics[width=1.\linewidth]{W10}
+  \includegraphics[width=1.\linewidth]{w10}
   \label{fig:m4examples:sub1}
-  \includegraphics[width=1.\linewidth]{W20}
-  \includegraphics[width=1.\linewidth]{W220}
+  \includegraphics[width=1.\linewidth]{w20}
+  \includegraphics[width=1.\linewidth]{w220}
 \caption{Examples of time series from the M4 weekly dataset.
@@
 \subsection{Loss grid search on the Fashion Dataset}
-\label{sec:heuritechgridsearch}
+\label{sec:fashiongridsearch}
 

### 2023-01-16 signal_processing_elsevier/re-submission_ijf/hermes_paper_LaTeX_source_files_double_blind/hermes_paper_blind_manuscript.tex
re-submission hermes
update ijf re-submission

--- 2022-11-02 signal_processing_elsevier/re-submission_ijf/hermes_paper_LaTeX_source_files/hermes_paper_elsevier.tex
@@
 %% Group authors per affiliation:
-\author[mymainaddress,mysecondaryaddress]{\'Etienne DAVID}
+%\author[mymainaddress,mysecondaryaddress]{Etienne DAVID}
 
 %% or include affiliations in footnotes:
-\author[mysecondaryaddress]{Jean BELLOT}
+%\author[mysecondaryaddress]{Jean BELLOT}
 
-\author[mymainaddress]{Sylvain LE CORFF}
+%\author[mymainaddress]{Sylvain LE CORFF}
 
-\address[mymainaddress]{\small  Samovar, T\'el\'ecom SudParis,  D\'epartement CITI, Institut Polytechnique de Paris, France.}
-\address[mysecondaryaddress]{Heuritech, 71 Rue Réaumur, 75002 Paris, France.}
+%\address[mymainaddress]{\small  Samovar, T\'el\'ecom SudParis,  D\'epartement CITI, Institut Polytechnique de Paris, France.}
+%\address[mysecondaryaddress]{Heuritech, 71 Rue Réaumur, 75002 Paris, France.}
 
@@
 Our contribution is  twofold.
-We first provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} an appealing fashion dataset gathering \numberts\ weekly fashion time series.
+We first provide publicly an appealing fashion dataset gathering \numberts\ weekly fashion time series.
 As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviors of influencers.
@@
 
-With this paper, we provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} a sample of $\numberts$ normalized fashion trends for men and women, over 9 different categories and 5 different markets.
+With this paper, we provide publicly a sample of $\numberts$ normalized fashion trends for men and women, over 9 different categories and 5 different markets.
 Each sequence has 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
@@
 In addition, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided.
-By making it publicly available\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}}, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
+By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
 As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.

### 2023-01-16 tmlr_submission/hermes_paper_submission/hermes_paper.tex
add tmlr submission

--- 2023-01-16 signal_processing_elsevier/re-submission_ijf/hermes_paper_LaTeX_source_files/hermes_paper_elsevier.tex
@@
-\documentclass[review]{elsarticle}
+\documentclass[10pt]{article} % For LaTeX2e
+\usepackage{tmlr}
+% If accepted, instead use the following line for the camera-ready submission:
+%\usepackage[accepted]{tmlr}
+% To de-anonymize and remove mentions to TMLR (for example for posting to preprint servers), instead use the following:
+%\usepackage[preprint]{tmlr}
 
-\usepackage{lineno,hyperref}
+% Optional math commands from https://github.com/goodfeli/dlbook_notation.
+\input{math_commands.tex}
+
+\usepackage{hyperref}
+\usepackage{url}
 \usepackage{amssymb,amsmath,amsthm}
-\usepackage{xcolor}
-\usepackage{pdfpages}
-\modulolinenumbers[5]
-
-\journal{Journal of \LaTeX\ Templates}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
-%\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage[pdftex]{graphicx}
 
@@
 
+\title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}
+
+% Authors must not appear in the submitted version. They should be hidden
+% as long as the tmlr package is used without the [accepted] or [preprint] options.
+% Non-anonymous submissions will be rejected without review.
+
+\author{\name \'Etienne David \email etienne.david@heuritech.com \\
+      \addr SAMOVAR, Télécom SudParis,\\
+      Institut Polytechnique de Paris, 91120 Palaiseau, France
+      \AND
+      \name Jean Bellot \email jean.bellot@heuritech.com \\
+      \addr Heuritech, \\
+      6 Rue de Braque, 75003 Paris
+      \AND
+      \name Sylvain Le Corff \email sylvain.lecorff@gmail.com\\
+      \addr LPSM, \\
+      Sorbonne Université, UMR CNRS 8001, 75005, Paris
+      }
+
+% The \author macro works with any number of authors. Use \AND 
+% to separate the names and addresses of multiple authors.
+
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
+
+\def\month{01}  % Insert correct month for camera-ready version
+\def\year{2023} % Insert correct year for camera-ready version
+\def\openreview{\url{https://openreview.net/forum?id=XXXX}} % Insert correct link to OpenReview for camera-ready version
+
 \begin{document}
 
-\begin{frontmatter}
-
-\title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}
-%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
-
-%% Group authors per affiliation:
-\author[mymainaddress,mysecondaryaddress]{\'Etienne DAVID}
-
-%% or include affiliations in footnotes:
-\author[mysecondaryaddress]{Jean BELLOT}
-
-\author[mymainaddress]{Sylvain LE CORFF}
-
-\address[mymainaddress]{\small  Samovar, T\'el\'ecom SudParis,  D\'epartement CITI, Institut Polytechnique de Paris, France.}
-\address[mysecondaryaddress]{Heuritech, 71 Rue Réaumur, 75002 Paris, France.}
+\maketitle
 
@@
 Our approach combines per-time-series parametric models with seasonal components and a global recurrent neural network to include sporadic external signals.
-This hybrid model provides state-of-the-art results on the proposed fashion dataset, on the weekly time series of the M4 competition \cite{makridakis2018}, and illustrates the benefit of the contribution of external weak signals.
+This hybrid model provides state-of-the-art results on the proposed fashion dataset, on the weekly time series of the M4 competition \citep{makridakis2018}, and illustrates the benefit of the contribution of external weak signals.
 \end{abstract}
-
-\begin{keyword}
-Hybrid models, Recurrent neural networks, Time series.
-\end{keyword}
-
-\end{frontmatter}
-
-\linenumbers
 
@@
 \label{sec:introduction}
-
-Multivariate time series forecasting is a widespread statistical problem with  many applications, see for instance \cite{sarkka2013, douc2014, zucchini2017} and the numerous references therein.
+Multivariate time series forecasting is a widespread statistical problem with  many applications, see for instance \citet{sarkka2013, douc2014, zucchini2017} and the numerous references therein.
 Parametric generative models provide explainable predictions with statistical guarantees based on a precise modeling of the predictive distributions of new data based on a record of past observations.
@@
 Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
-The exponential smoothing model \cite{Brown1961}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \cite{alysha2011}, or the ARIMA with the Box-Jenkins approach \cite{box2015} are for instance very popular parametric generative models.
+The exponential smoothing model \citep{Brown1961}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \citep{alysha2011}, or the ARIMA with the Box-Jenkins approach \citep{box2015} are for instance very popular parametric generative models.
 Hidden Markov models (HMM) are also widespread and presuppose that available observations are defined using missing data describing the dynamical system.
@@
 In various applications where signals exhibit non-stationarities such as trends and seasonality, classical HMM are not adapted.
-However, \cite{touron2017}  recently proposed seasonal HMM, assuming that transition probabilities between the states, as well as the emission distributions, are not constant in time but evolve in a periodic manner.
-Strong consistency results were established in \cite{touron2019} and Expectation Maximization based numerical experiments were proposed.
+However, \citet{touron2017}  recently proposed seasonal HMM, assuming that transition probabilities between the states, as well as the emission distributions, are not constant in time but evolve in a periodic manner.
+Strong consistency results were established in \citet{touron2019} and Expectation Maximization based numerical experiments were proposed.
 Although these works provide promising results, HMM are computationally expensive to train and are not yet well studied for seasonal  sequences with thousands of components.
@@
 In this new context, classical time series specific statistical models show limitations when dealing with numerous heterogeneous data.
-Recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \cite{ hochreiter1997,vaswani2017, siami2018, li2019, lim2019,salinas2020}.
-The DeepAR model proposed in \cite{salinas2020} provides a global model from many time series based on a multi-layer recurrent neural network with LSTM cells.
-More recently, applications using the Transformer model have been proposed  \cite{li2019}.
-The Temporal Fusion Transformers (TFT) approach is a direct alternative to the DeepAR model \cite{lim2019}.
+Recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \citet{ hochreiter1997,vaswani2017, siami2018, li2019, lim2019,salinas2020}.
+The DeepAR model proposed in \citet{salinas2020} provides a global model from many time series based on a multi-layer recurrent neural network with LSTM cells.
+More recently, applications using the Transformer model have been proposed  \citep{li2019}.
+The Temporal Fusion Transformers (TFT) approach is a direct alternative to the DeepAR model \citep{lim2019}.
 Unfortunately, all these solutions suffer from two main weaknesses.
-Firstly, many of them are black-boxes  as the final forecast usually does not come with a statistical guarantee  although a few recent works focused on measuring uncertainty in recurrent neural networks, see  \cite{martin2020}.
-Secondly, without a fine preprocessing and well chosen hyperparameters, these methods may lead to poor results and be outperformed by traditional statistical models, see \cite{makridakis2018}.
+Firstly, many of them are black-boxes  as the final forecast usually does not come with a statistical guarantee  although a few recent works focused on measuring uncertainty in recurrent neural networks, see  \citet{martin2020}.
+Secondly, without a fine preprocessing and well chosen hyperparameters, these methods may lead to poor results and be outperformed by traditional statistical models, see \citet{makridakis2018}.
 
@@
 Consequently, models and algorithms can be trained to accurately anticipate and predict consumers' behaviours.
-In \cite{ma2020}, a  dataset is provided using social media pictures and an image recognition framework to detect several clothes: 2000 fashion time series are proposed with a weekly seasonality.
+In \citet{ma2020}, a  dataset is provided using social media pictures and an image recognition framework to detect several clothes: 2000 fashion time series are proposed with a weekly seasonality.
 However, only 3 years of historical data is available (144 data points) that may not be sufficient for some statistical approaches.
-In \cite{ma2020}, another dataset is presented gathering 8000 fashion sequences with an historical available data  increased to 5 years.
+In \citet{ma2020}, another dataset is presented gathering 8000 fashion sequences with an historical available data  increased to 5 years.
 Nevertheless, only 120 values are available for each fashion time series and the overall volume remains low for a large part of the sequences resulting in a lot of noise and no clear patterns.
 In this paper, we propose a new fashion dataset overcoming the weaknesses of the two previous ones.
-Based on cutting-edge image recognition algorithms \cite{ren2015,chollet2017}, we built a large fashion dataset containing \numberts\ weekly sequences of fashion trends on social media with 5 years of historical data from 01-01-2015 to 30-12-2019.
+Based on cutting-edge image recognition algorithms \citep{ren2015,chollet2017}, we built a large fashion dataset containing \numberts\ weekly sequences of fashion trends on social media with 5 years of historical data from 01-01-2015 to 30-12-2019.
 This dataset has very appealing properties:  all time series have the same length (261 data points), no missing value and no sparse time series even for niche trends.
@@
 Recurrent neural networks are appealing to tackle our forecasting problem due to their capability of leveraging external data.
-Recently, hybrid models combining deep neural network (DNN) architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \cite{zhang2003,jianwei2019,bandara2020}.
-The approach providing the most striking results was proposed in  \cite{smyl2020} in the context of the M4 forecasting competition \cite{makridakis2020}.
+Recently, hybrid models combining deep neural network (DNN) architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \citet{zhang2003,jianwei2019,bandara2020}.
+The approach providing the most striking results was proposed in  \citet{smyl2020} in the context of the M4 forecasting competition \citep{makridakis2020}.
 Given a large dataset, a per-time-series multiplicative exponential smoothing model was introduced to estimate simple but fundamental components for each time series and compute a first prediction.
@@
 \end{equation}
-During the M4 competition, the hybrid model of \cite{smyl2020} was based on a multiplicative exponential smoothing model as the time-series-specific predictor.
+During the M4 competition, the hybrid model of \citet{smyl2020} was based on a multiplicative exponential smoothing model as the time-series-specific predictor.
 However, on sporadic time series, this choice leads to poor results and instability.
@@
 In Section~\ref{sec:exp}, two versions of our framework are proposed.
-The first one is based on an  exponential smoothing as a reference similar to the baseline \cite{smyl2020} and the second one uses a TBATS model \cite{alysha2011} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
+The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020} and the second one uses a TBATS model \citep{alysha2011} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
 
@@
 
-\section{Fashion dataset with external weak signals}
+section{Fashion dataset with external weak signals}
 \label{sec:dataset}
@@
     \item First, an object detection model is trained to detect the position, the size and the general type of possible multiple fashion items on a picture.
-This localization model is based on the Faster-RCNN architecture introduced in \cite{ren2015}.
-Starting from weights trained on MS-COCO \cite{lin2014}, a fine-tune of the model is done on our data with a standard setup following the original paper.
+This localization model is based on the Faster-RCNN architecture introduced in \citet{ren2015}.
+Starting from weights trained on MS-COCO \citep{lin2014}, a fine-tune of the model is done on our data with a standard setup following the original paper.
     \item  Additionally, several visual recognition models are trained at classifying a rich collection of 350 fashion details.
 We train one classifier for each category of fashion item: one for pants, another for tops, a third for shoes, etc.
-These models are all based on the Xception architecture introduced in \cite{chollet2017}.
+These models are all based on the Xception architecture introduced in \citet{chollet2017}.
 So as to trained them, large amount of social media pictures (between 200k and 800k training images depending on the category) have been manually tagged to constitute meaningful training datasets depending on the classification task.
-Architectures are first initialized with public weights trained on ImageNet \cite{russakovsky2014} and then fine tuned on the manually labeled dataset corresponding to their task.
+Architectures are first initialized with public weights trained on ImageNet \citep{russakovsky2014} and then fine tuned on the manually labeled dataset corresponding to their task.
 \end{enumerate}
@@
 This signal represents the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe).
-With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \cite{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$.
+With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$.
 The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$.
@@
 
-In theoretical fashion dynamics \cite{rogers1962}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
+In theoretical fashion dynamics \citep{rogers1962}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
 So as too catch the early signal of the emergence of a trend, 6000 social media influencers were selectioned by hand by fashion experts.
@@
 Depending of the choice of local parametric models, two versions of HERMES are proposed.
-The first one uses as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020}.
-The second one uses the TBATS model of \cite{alysha2011} and  achieves the highest accuracy results on the fashion dataset.
+The first one uses as predictors an additive exponential smoothing model as a reference close to \citet{smyl2020}.
+The second one uses the TBATS model of \citet{alysha2011} and  achieves the highest accuracy results on the fashion dataset.
 The neural network architecture is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
@@
 Finally, \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters.
-A complete description and references for these models can be found in \cite{hyndman2020}.
+A complete description and references for these models can be found in \citet{hyndman2020}.
 As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.
@@
 Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slightly outperform the alternatives in terms of MASE and are stable across the different trainings.
-Regarding \textit{hermes-ets},   although it is very similar to the baseline \cite{smyl2020}, its accuracy remains low in comparison to the \textit{lstm} benchmark or HERMES using TBATS.
+Regarding \textit{hermes-ets},   although it is very similar to the baseline \citet{smyl2020}, its accuracy remains low in comparison to the \textit{lstm} benchmark or HERMES using TBATS.
 
@@
 
-We also assessed the performance of HERMES using the M4 weekly dataset \cite{makridakis2020}.
+We also assessed the performance of HERMES using the M4 weekly dataset \citep{makridakis2020}.
 The M4 dataset gathers 359 weekly time series and has 3 main differences compared to the proposed fashion dataset.
@@
 In addition, the hybrid model named \textit{Uber} of S.Smyl is added.
-For a complete description and references of the benchmark models and the hybrid model \textit{Uber}, see \cite{makridakis2020} and \cite{smyl2020}.
+For a complete description and references of the benchmark models and the hybrid model \textit{Uber}, see \citet{makridakis2020} and \citet{smyl2020}.
 As a HERMES candidate, a version using TBATS is proposed and called \textit{hermes-tbats}.
@@
 These three methods are based on an ensembling and combine various approaches.
-The first model is presented in \cite{darin2020} and called \textit{Darin \& Stellwagen}.
-The second model is introduced in \cite{petropoulos2020} and called \textit{Petropoulos \& Svetunkov}.
-Finally, a description of the third model  called \textit{Pawlikowski, et al.} can be found in \cite{pawlikowski2020}.
+The first model is presented in \citet{darin2020} and called \textit{Darin \& Stellwagen}.
+The second model is introduced in \citet{petropoulos2020} and called \textit{Petropoulos \& Svetunkov}.
+Finally, a description of the third model  called \textit{Pawlikowski, et al.} can be found in \citet{pawlikowski2020}.
 An ensembling combining 4 HERMES variations is proposed.
-It is based on the FFORMA algorithm introduced in \cite{montero2020} and called \textit{fforma-hermes}.
+It is based on the FFORMA algorithm introduced in \citet{montero2020} and called \textit{fforma-hermes}.
 A complete description of the training process of the proposed ensembling is given in \ref{sec:fforma-hermes}.
 Following the M4 competition methodology, all the candidates are evaluated according to the MASE, the SMAPE and the OWA measures.
-A complete definition of these metrics is proposed in \cite{makridakis2020} and summarized in \ref{sec:m4overview}.
+A complete definition of these metrics is proposed in \citet{makridakis2020} and summarized in \ref{sec:m4overview}.
 See also \ref{sec:m4overview} for additional information about the M4 weekly dataset.
@@
 The results provided by \textit{hermes-tbats} confirm that the HERMES model is well suited for a large collection of forecasting tasks even difficult ones with small datasets, heterogeneous time series and the absence of  additional useful external signals.
-Secondly, the accuracy gap between the proposed hybrid model and the approach proposed in \cite{smyl2020} illustrates the importance of a global framework able to leverage any kind of per-time-series predictors depending of the use cases.
+Secondly, the accuracy gap between the proposed hybrid model and the approach proposed in \citet{smyl2020} illustrates the importance of a global framework able to leverage any kind of per-time-series predictors depending of the use cases.
 Finally, our model can be easily included as part of an ensembling method to improve the final robustness and accuracy of the predictions.
@@
      \textit{Damped} && 8.866 && - &&& 2.404 && - &&& 0.917 && - &\\
-     \textit{Uber} \cite{smyl2020} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
+     \textit{Uber} \citet{smyl2020} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
      \textit{tbats} && 7.409 && - &&& 2.204 && - &&& 0.801 && - &\\
@@
 
+\bibliography{hermes_paper}
+\bibliographystyle{tmlr}
+
 \appendix
-
 \section{M4 weekly dataset, Ensembling training and results}
@@
 10 models are trained per version with different seeds and the best one based on the eval set is kept for the ensemble model.
-In a second time, the FFORMA ensembling introduced in \cite{montero2020} is used to combine the 4 HERMES methods.
+In a second time, the FFORMA ensembling introduced in \citet{montero2020} is used to combine the 4 HERMES methods.
 The R package \texttt{M4metalearning} containing the FFORMA model is directly used without change of the hyperparameters, imported in Python with the library \texttt{Rpy2} and combined with the HERMES code base.
@@
 
-\bibliography{hermes_paper_elsevier}
-
 \end{document}

### 2023-01-26 tmlr_submission/hermes_paper_submission/hermes_paper.tex
update introduction

@@
 We first provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} an appealing fashion dataset gathering \numberts\ weekly fashion time series.
-As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviors of influencers.
+As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviours of influencers.
 Secondly, to leverage such a complex and rich dataset, we propose a new hybrid forecasting model.
@@
 In fashion and retails industries, accurately anticipating consumers' needs is vital and wrong decisions can lead to massive wastes.
-Analysing social media pictures to detect what clothes people are wearing, it is possible to translate the visibility of fashion items over time into time series.
-Consequently, models and algorithms can be trained to accurately anticipate and predict consumers' behaviours.
+With the explosion of social network and the recent advances in image recognition, it is possible to translate the visibility of fashion items on social media over time into time series.
+Consequently, models and algorithms can be trained to accurately anticipate and predict consumer behaviour.
 In \citet{ma2020}, a  dataset is provided using social media pictures and an image recognition framework to detect several clothes: 2000 fashion time series are proposed with a weekly seasonality.
@@
 Based on cutting-edge image recognition algorithms \citep{ren2015,chollet2017}, we built a large fashion dataset containing \numberts\ weekly sequences of fashion trends on social media with 5 years of historical data from 01-01-2015 to 30-12-2019.
-This dataset has very appealing properties:  all time series have the same length (261 data points), no missing value and no sparse time series even for niche trends.
+This dataset has very appealing properties:  all time series have the same length (261 data points), there is no missing value and there is no sparse time series even for niche trends.
 Concerning fashion dynamics, some of them appear to be really volatile with nonlinear changes of dynamics resulting from the emergence of new tendencies.
@@
 $$
-This choice of $\mathrm{L}_1$ loss function is motivated by its robustness to outliers which accounts for some time series in the fashion industry with very specific behaviors.
+This choice of $\mathrm{L}_1$ loss function is motivated by its robustness to outliers which accounts for some time series in the fashion industry with very specific behaviours.
 The loss and previous parameters are all set with a complete grid search.

### 2023-01-26 tmlr_submission/hermes_paper_submission/hermes_paper.tex
change sections order and add a figure

@@
 They are called weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal.
-Figure \ref{fig:oneemergingtrend} shows an example of fashion time series with its linked influencers weak signal.
 Exploring this new way of representing fashion, we aim at designing a model able to deal with such a large dataset, leveraging  complex external weak signals and finally providing the most accurate forecasts.
@@
 The paper is organized as follows.
-Section~\ref{sec:hybrid} introduces the proposed hybrid model.
-Then, the new fashion dataset provided with this article is presented in Section~\ref{sec:dataset}.
-Section~\ref{sec:exp} describes the HERMES results and comparisons with several benchmarks.
+Section~\ref{sec:dataset} presents the new fashion dataset provided with this article.
+Then, the proposed forecasting approach HERMES is presented in Section~\ref{sec:hybrid}.
+Section~\ref{sec:exp} describes the model results and comparisons with several benchmarks on the 2 different use cases: the fashion dataset and the M4 competition weekly dataset.
 Finally, a general conclusion and some research perspectives are given in  Section~\ref{sec:conclusion}.
+
+\section{From social media to fashion time series}
+\label{sec:dataset}
+
+\begin{figure*}
+  \centering
+    \includegraphics[width=1.\linewidth]{pipeline_archi}
+  \caption{From social media to fashion time series.
+a) A complete image dataset of 150 millions of pictures is collected from social media users localized on 5 strategic markets.
+b) A visual recognition pipeline is applying on images.
+Global fashion items are detected with a collection of fine-grain attributes.
+c) Result are aggregated by fashion trend definition over the time and normalized in order to remove social media bias.
+The fashion time series are created.}
+\label{fig:pipeline}
+\end{figure*}
+
+\subsection{Translate fashion to data}
+\label{sec:dataset:a}
+
+Social media have appeared as an impressive data source to follow the evolution of fashion over the time.
+Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world.
+To do it automatically for thousands of trends, the following methodology was introduced.
+In the first place, a complete image dataset of 150 millions pictures is collected from different social media such as Instagram or Weibo.
+We targeted 5 strategic markets for the retail industry using posts localisation: the United States, Europe, Japan, Brazil and China.
+The second step consists in creating a powerful visual recognition framework to be able to detect clothes details on pictures like the type of clothing, the form, the size, the color, the texture, etc.
+To do so, the following framework is designed.
+\begin{enumerate}
+    \item First, an object detection model is trained to detect the position, the size and the general type of possible multiple fashion items on a picture.
+This localization model is based on the Faster-RCNN architecture introduced in \citet{ren2015}.
+Starting from weights trained on MS-COCO \citep{lin2014}, a fine-tune of the model is done on our data with a standard setup following the original paper.
+    \item  Additionally, several visual recognition models are trained at classifying a rich collection of 350 fashion details.
+We train one classifier for each category of fashion item: one for pants, another for tops, a third for shoes, etc.
+These models are all based on the Xception architecture introduced in \citet{chollet2017}.
+So as to trained them, large amount of social media pictures (between 200k and 800k training images depending on the category) have been manually tagged to constitute meaningful training datasets depending on the classification task.
+Architectures are first initialized with public weights trained on ImageNet \citep{russakovsky2014} and then fine tuned on the manually labeled dataset corresponding to their task.
+\end{enumerate}
+
+At inference time, we first apply the localisation model which predicts boxes of generic fashion items (tops, pants, shoes, dresses, etc.) for each image.
+Then, each fashion item is cropped from its full image, resized to the classifiers' input size ($299\times299\,$px) and fed into the related classifier: a top will be fed into the model trained on tops, etc.
+We obtain for each image a set of boxes, associated with a general category and a set of fine-grain attributes describing this object.
+As a final step, fashion experts aggregate those attributes to define relevant trends for the fashion and retails industry.
+
+The 150 million of social media pictures are analyzed with the visual recognition pipeline described below.
+Out of those images, we detected clothes in 96 millions posts making the final dataset used in this paper.
+We aggregate results by fashion trend definition over the time and  thousands of trends are finally translated from social media to time series.
+We note $y^{c,g,m,i}$ the final raw sequence representing the fashion trend $i$ of the cloth type $c$ for the gender $g$ on market $m$.
+At each time t, $y^{c,g,m,i}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $i$ of the cloth type $c$ for the gender $g$.
+As an illustration, an example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.
 
@@
 
-\section{Hybrid model with external signals}
+\subsection{Removing social media bias}
+\label{sec:dataset:b}
+
+Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,i}$ in order to remove bias.
+Thus, we define the following normalizing signal $\Tilde{y}^{c,g,m}$.
+This signal represents the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe).
+With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$.
+The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$.
+Finally, for any fashion trend $i$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
+\begin{equation}
+    y^{i}_t = \frac{y^{c,g,m,i}_{t}}{\bar{y}^{c,g,m}_t}\,,
+\end{equation}
+where T denotes the number of available time steps.
+The time series $y^{c,g,m,i}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences.
+With this normalizing step, a majority of the social media bias are removed and the final normalized sequences are expressed in share of category.
+As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}.
+The raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.
+
+\begin{figure*}
+\centering
+  \includegraphics[width=1.\linewidth]{cn_female_top_raw}
+  \includegraphics[width=1.\linewidth]{cn_female_top_norm}
+\caption{Example of difference between the raw sequence and the normalized one for the Jersey top fashion trend for females in China.
+In this example, we normalize by the deseasonalized global top fashion trend for females in China.
+(Top) Time series representing the raw signal of the Jersey top fashion trend for females in China.
+(Bottom) Time series representing the normalized signal of the Jersey top fashion trend for females in China.}
+\label{fig:normalization}
+\end{figure*}
+
+\subsection{Weak signal}
+
+In theoretical fashion dynamics \citep{rogers1962}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
+So as too catch the early signal of the emergence of a trend, 6000 social media influencers were selectioned by hand by fashion experts.
+Aggregating them, a specific ``fashion-oriented`` panel is created.
+With the same methodology as for the main panel described in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created.
+We named \textit{fashion-forwards} this weak signal.
+For all fashion sequence $\{y^i_t\}_{1 \leq t \leq T}$, let $\{\ts^{f,i}_t\}_{1 \leq t \leq T}$ be the normalized sequence representing the behaviours of influencers regarding the fashion trend $i$.
+As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for the hybrid model: for all $t \in \{1,\ldots,T\}$ and any fashion trend $i$,
+$$
+\ws^{f,i}_{t} = \frac{\ts_t^{f,i}}{\ts_t^{f,i}+\ts_t^{i}}\,.
+$$
+where T denotes the number of available time steps.
+Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.
+For instance, an impressive emerging fashion shoes trend with its \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
+
+\subsection{Fashion dataset}
+
+With this paper, we provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} a sample of $\numberts$ normalized fashion trends for men and women, over 9 different categories and 5 different markets.
+Each sequence has 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
+This collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry.
+For instance, some sequences show complex behaviours with sudden changes, referred to as emerging or declining trends.
+A central point of this work is to accurately detect and forecast such trends.
+In addition, each fashion time series is linked with its associated normalized fashion forward signal as presented in the section above.
+An overview of the dataset can be found in Table~\ref{tab:fashiondataset}.
+
+\begin{table*}
+  \caption{Fashion time series overview. For each couple geozone/category, the table gives the number of trends (Female/Male).}
+\label{tab:fashiondataset}
+  \centering
+  \resizebox{0.65\width}{!}{
+  \begin{tabular}{l||lllllllll}
+    \\
+    &  \textbf{Top}  & \textbf{Pants} & \textbf{Short} & \textbf{Skirt} & \textbf{Dress} & \textbf{Coat} & \textbf{Shoes} & \textbf{Color} & \textbf{Texture}  \\
+    \hline
+    \hline
+    \\
+\textbf{United States} & 411/208 & 149/112 & 47/22 & 29/- & 20/- & 208/151 & 293/86 & 38/44 & 85/81\\
+     \textbf{Europe} & 409/228 &  134/114 & 48/21 & 28/- & 20/- & 211/159 & 303/78 & 41/42 & 87/74\\
+     \textbf{Japan} &  403/218 & 136/107 & 49/31 & 28/- &  23/- & 185/149 &  311/78 & 46/42 &  92/65\\
+     \textbf{China} &  424/202 & 147/114 & 46/29 & 27/- &  27/- & 178/161 &  310/78 & 41/47 &  88/77\\
+     \textbf{Brazil} &  431/222 & 134/117 & 49/27 & 30/- &  28/- & 203/152 & 311/76 & 48/41 & 107/84\\
+     \\
+     \textbf{Total} & 2078/1078 & 700/564 & 239/130 & 142/- & 118/- & 985/772 & 1528/396 & 214/216 & 459/381\\
+  \end{tabular}
+  }
+\end{table*}
+
+\section{The HERMES approach: a new hybrid model for time series forecasting}
 \label{sec:hybrid}
@@
 \end{figure}
-
-section{Fashion dataset with external weak signals}
-\label{sec:dataset}
-
-\subsection{Translate fashion to data}
-\label{sec:dataset:a}
-
-Social media have appeared as an impressive data source to follow the evolution of fashion over the time.
-Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world.
-To do it automatically for thousands of trends, the following methodology was introduced.
-In the first place, a complete image dataset of 150 millions pictures is collected from different social media such as Instagram or Weibo.
-We targeted 5 strategic markets for the retail industry using posts localisation: the United States, Europe, Japan, Brazil and China.
-The second step consists in creating a powerful visual recognition framework to be able to detect clothes details on pictures like the type of clothing, the form, the size, the color, the texture, etc.
-To do so, the following framework is designed.
-\begin{enumerate}
-    \item First, an object detection model is trained to detect the position, the size and the general type of possible multiple fashion items on a picture.
-This localization model is based on the Faster-RCNN architecture introduced in \citet{ren2015}.
-Starting from weights trained on MS-COCO \citep{lin2014}, a fine-tune of the model is done on our data with a standard setup following the original paper.
-    \item  Additionally, several visual recognition models are trained at classifying a rich collection of 350 fashion details.
-We train one classifier for each category of fashion item: one for pants, another for tops, a third for shoes, etc.
-These models are all based on the Xception architecture introduced in \citet{chollet2017}.
-So as to trained them, large amount of social media pictures (between 200k and 800k training images depending on the category) have been manually tagged to constitute meaningful training datasets depending on the classification task.
-Architectures are first initialized with public weights trained on ImageNet \citep{russakovsky2014} and then fine tuned on the manually labeled dataset corresponding to their task.
-\end{enumerate}
-
-At inference time, we first apply the localisation model which predicts boxes of generic fashion items (tops, pants, shoes, dresses, etc.) for each image.
-Then, each fashion item is cropped from its full image, resized to the classifiers' input size ($299\times299\,$px) and fed into the related classifier: a top will be fed into the model trained on tops, etc.
-We obtain for each image a set of boxes, associated with a general category and a set of fine-grain attributes describing this object.
-As a final step, fashion experts aggregate those attributes to define relevant trends for the fashion and retails industry.
-
-The 150 million of social media pictures are analyzed with the visual recognition pipeline described below.
-Out of those images, we detected clothes in 96 millions posts making the final dataset used in this paper.
-We aggregate results by fashion trend definition over the time and  thousands of trends are finally translated from social media to time series.
-We note $y^{c,g,m,i}$ the final raw sequence representing the fashion trend $i$ of the cloth type $c$ for the gender $g$ on market $m$.
-At each time t, $y^{c,g,m,i}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $i$ of the cloth type $c$ for the gender $g$.
-
-As an illustration, an example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.
-
-\subsection{Fashion time series}
-\label{sec:dataset:b}
-
-Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences in order to remove bias.
-Thus, we define the following normalizing signal $\Tilde{y}^{c,g,m}$.
-This signal represents the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe).
-With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$.
-The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$.
-Finally, for any fashion trend $i$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
-\begin{equation}
-    y^{i}_t = \frac{y^{c,g,m,i}_{t}}{\bar{y}^{c,g,m}_t}\,,
-\end{equation}
-where T denotes the number of available time steps.
-The time series $y^{c,g,m,i}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences.
-With this normalizing step, a majority of the social media bias are removed and the final normalized sequences are expressed in share of category.
-As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}.
-The raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.
-
-\begin{figure*}
-\centering
-  \includegraphics[width=1.\linewidth]{cn_female_top_raw}
-  \includegraphics[width=1.\linewidth]{cn_female_top_norm}
-\caption{Example of difference between the raw sequence and the normalized one for the Jersey top fashion trend for females in China.
-In this example, we normalize by the deseasonalized global top fashion trend for females in China.
-(Top) Time series representing the raw signal of the Jersey top fashion trend for females in China.
-(Bottom) Time series representing the normalized signal of the Jersey top fashion trend for females in China.}
-\label{fig:normalization}
-\end{figure*}
-
-\subsection{Weak signal}
-
-In theoretical fashion dynamics \citep{rogers1962}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
-So as too catch the early signal of the emergence of a trend, 6000 social media influencers were selectioned by hand by fashion experts.
-Aggregating them, a specific ``fashion-oriented`` panel is created.
-With the same methodology as for the main panel described in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created.
-We named \textit{fashion-forwards} this weak signal.
-For all fashion sequence $\{y^i_t\}_{1 \leq t \leq T}$, let $\{\ts^{f,i}_t\}_{1 \leq t \leq T}$ be the normalized sequence representing the behaviours of influencers regarding the fashion trend $i$.
-As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for the hybrid model: for all $t \in \{1,\ldots,T\}$ and any fashion trend $i$,
-$$
-\ws^{f,i}_{t} = \frac{\ts_t^{f,i}}{\ts_t^{f,i}+\ts_t^{i}}\,.
-$$
-where T denotes the number of available time steps.
-Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.
-For instance, an impressive emerging fashion shoes trend with its \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
-
-\subsection{Fashion dataset}
-
-With this paper, we provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} a sample of $\numberts$ normalized fashion trends for men and women, over 9 different categories and 5 different markets.
-Each sequence has 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
-This collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry.
-For instance, some sequences show complex behaviours with sudden changes, referred to as emerging or declining trends.
-A central point of this work is to accurately detect and forecast such trends.
-In addition, each fashion time series is linked with its associated normalized fashion forward signal as presented in the section above.
-An overview of the dataset can be found in Table~\ref{tab:fashiondataset}.
-
-\begin{table*}
-  \caption{Fashion time series overview. For each couple geozone/category, the table gives the number of trends (Female/Male).}
-\label{tab:fashiondataset}
-  \centering
-  \resizebox{0.65\width}{!}{
-  \begin{tabular}{l||lllllllll}
-    \\
-    &  \textbf{Top}  & \textbf{Pants} & \textbf{Short} & \textbf{Skirt} & \textbf{Dress} & \textbf{Coat} & \textbf{Shoes} & \textbf{Color} & \textbf{Texture}  \\
-    \hline
-    \hline
-    \\
-\textbf{United States} & 411/208 & 149/112 & 47/22 & 29/- & 20/- & 208/151 & 293/86 & 38/44 & 85/81\\
-     \textbf{Europe} & 409/228 &  134/114 & 48/21 & 28/- & 20/- & 211/159 & 303/78 & 41/42 & 87/74\\
-     \textbf{Japan} &  403/218 & 136/107 & 49/31 & 28/- &  23/- & 185/149 &  311/78 & 46/42 &  92/65\\
-     \textbf{China} &  424/202 & 147/114 & 46/29 & 27/- &  27/- & 178/161 &  310/78 & 41/47 &  88/77\\
-     \textbf{Brazil} &  431/222 & 134/117 & 49/27 & 30/- &  28/- & 203/152 & 311/76 & 48/41 & 107/84\\
-     \\
-     \textbf{Total} & 2078/1078 & 700/564 & 239/130 & 142/- & 118/- & 985/772 & 1528/396 & 214/216 & 459/381\\
-  \end{tabular}
-  }
-\end{table*}
 

### 2023-02-01 tmlr_submission/hermes_paper_submission/hermes_paper.tex
Minor modifications Sections 1 and 2

@@
 a) A complete image dataset of 150 millions of pictures is collected from social media users localized on 5 strategic markets.
-b) A visual recognition pipeline is applying on images.
+b) A visual recognition pipeline is applied on images.
 Global fashion items are detected with a collection of fine-grain attributes.
-c) Result are aggregated by fashion trend definition over the time and normalized in order to remove social media bias.
-The fashion time series are created.}
+c) Results are aggregated by fashion trend over time and normalized in order to remove social media bias.
+}
 \label{fig:pipeline}
@@
 This localization model is based on the Faster-RCNN architecture introduced in \citet{ren2015}.
-Starting from weights trained on MS-COCO \citep{lin2014}, a fine-tune of the model is done on our data with a standard setup following the original paper.
+Starting from weights trained on MS-COCO \citep{lin2014}, the model is fine-tuned with our data with a standard setup following the original paper.
     \item  Additionally, several visual recognition models are trained at classifying a rich collection of 350 fashion details.
@@
 
-The 150 million of social media pictures are analyzed with the visual recognition pipeline described below.
+The 150 million of social media pictures are analyzed with this visual recognition pipeline.
 Out of those images, we detected clothes in 96 millions posts making the final dataset used in this paper.
@@
 The time series $y^{c,g,m,i}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences.
-With this normalizing step, a majority of the social media bias are removed and the final normalized sequences are expressed in share of category.
+With this normalizing step, most of the social media bias is removed and the final normalized sequences are expressed in share of category.
 As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}.
@@
 Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.
-For instance, an impressive emerging fashion shoes trend with its \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
+For instance, an  emerging fashion shoes trend with its \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
 

### 2023-02-01 tmlr_submission/hermes_paper_submission/hermes_paper.tex
Minor updates in remaining sections

@@
 
-\section{The HERMES approach: a new hybrid model for time series forecasting}
+\section{HERMES: a new hybrid model for time series forecasting}
 \label{sec:hybrid}
 We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, and a global error-corrector neural network train on all time series.
-Per-time-series parametric models are used to learn local behaviours, to normalize sequences by removing trends and seasonality,  and to compute a first forecast.
-Then, gathering information of the first predictions and external variables, a recurrent neural network is trained to correct the predictions provided by the first collection of per-time-series models.
+Per-time-series parametric models are used in particular to learn local behaviours and to normalize sequences by removing trends and seasonality.
+Then,  a recurrent neural network driven by the weak signals is trained to correct these per-time-series models.
 
@@
 \subsection{Per-time-series predictors}
-The time-series-specific predictors compute, for each sequence, a first $\lag$-ahead prediction based on the past.
+%The time-series-specific predictors compute, for each sequence, a first $\lag$-ahead prediction based on the past. 
 For all $1\leqslant n \leqslant N$, we note $\stat^n(.;\statparam^n)$ the $n$-th parametric model of the $n$-th sequence where $\statparam^n$ are  unknown parameters.
@@
 
-In the specific application of fashion trends prediction, two main forms of standard weaknesses were detected and defined for univariate parametric forecasts.
+%In the specific application of fashion trends prediction, two main forms of standard weaknesses were detected and defined for univariate parametric forecasts.
 The first one is a weakness of definition, when the model is not well defined for its forecasting task.
@@
 
-Using well-fitted time-series-specific parametric models, the new hybrid network corrects the first form of weakness and provides appealing performance on the fashion dataset, see Table~\ref{tab:metricresults}.
-Then, to correct the second form of weakness, in addition to the $N$ target time series, $K \times N$ external sequences indexed from $0$ to $T$ are considered.
+%Using well-fitted time-series-specific parametric models, the new hybrid network corrects the first form of weakness and provides appealing performance on the fashion dataset, see Table~\ref{tab:metricresults}.
+%Then, to correct the second form of weakness, 
+In addition to the $N$ target time series, $K \times N$ external sequences indexed from $0$ to $T$ are considered.
 For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ associated with the sequence $\fullts^n$.

### 2023-02-02 tmlr_submission/hermes_paper_submission/hermes_paper.tex
Minor updates on Section 3

@@
 In theoretical fashion dynamics \citep{rogers1962}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
-So as too catch the early signal of the emergence of a trend, 6000 social media influencers were selectioned by hand by fashion experts.
+So as to catch the early signal of the emergence of a trend, 6000 social media influencers were selectioned by hand by fashion experts.
 Aggregating them, a specific ``fashion-oriented`` panel is created.
@@
 This motivates the introduction of a global RNN trained on all time series and able to consider and leverage external signals.
-First forecast example of our new hybrid model is given in Figure~\ref{fig:introexamples}.
 
@@
 This task requires a thorough data pre-processing as recurrent neural networks training is highly sensitive to the scale of the data and requires well-designed inputs.
-Since no assumption about the scale of our time series was made, inputs require a careful normalization before being fed to the RNN.
 
@@
 $$
-Our hybrid model forecast is, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$,
+Thus, if no external signals are available, the final hermes  forecast is, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$,
 \begin{align}
@@
 %Then, to correct the second form of weakness, 
-In addition to the $N$ target time series, $K \times N$ external sequences indexed from $0$ to $T$ are considered.
+In addition to the $N$ target time series, $K \times N$ external sequences indexed from $0$ to $T$ are now considered.
 For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ associated with the sequence $\fullts^n$.
-Let  $\fullws^n = \{\{\ws_t^{n,k}\}_{1\leqslant t \leqslant T}\}_{1\leqslant k \leqslant K}$ be all the values of the weak signals associated with the $n$-th sequence.
-In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the sequence.
+Let  $\fullws^n = \{\{\ws_t^{n,k}\}_{1\leqslant t \leqslant T}\}_{1\leqslant k \leqslant K}$ be all the values of the external signals.
+In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the external sequences.
 Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, a new input for the RNN is defined:
@@
 \end{align}
-An illustration of the proposed  model is displayed in Figure~\ref{fig:architecture}.
+An illustration of the proposed  model is displayed in Figure~\ref{fig:architecture} and a first forecast example is given in Figure~\ref{fig:introexamples}..
 

### 2023-02-06 tmlr_submission/hermes_paper_submission/hermes_paper.tex
Update Section 4

@@
 As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviours of influencers.
-Secondly, to leverage such a complex and rich dataset, we propose a new hybrid forecasting model.
+Secondly, to leverage such a complex and rich dataset, we propose a new hybrid forecasting model\footnote[2]{\url{https://github.com/etidav/HERMES}}.
 Our approach combines per-time-series parametric models with seasonal components and a global recurrent neural network to include sporadic external signals.
@@
 The neural network architecture is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
-A classical Adam optimizer is used with a learning rate set at 0.001 or 0.005, the batch size is fixed to 64 and the loss function is defined as follows:
+A classical Adam optimizer is used with a learning rate and a batch size set using a grid search.
+The loss function is defined as follows:
 $$
@@
 See \ref{sec:fashiongridsearch} for additional results concerning the loss function choice and \ref{sec:m4gridsearch} for a complete grid search example.
-The code is developed in Python using the Tensorflow library.
+The code is developed in Python using the Tensorflow library and publicly available\footnote[1]{\url{https://github.com/etidav/HERMES}}.
 It allows the use of GPU to speed up the training process.
@@
 As our sequences have completely different scales, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, independent of the scale of the sequence and suited for our seasonal fashion time series.
-The MASE metric is defined as follows, with $m$ the seasonal period:
+The MASE metric is defined as follows, with $T$ the length of the time series, $m$ the seasonal period and $h$ the horizon:
 \begin{align*}
@@
 With this threshold, the proposed fashion dataset is almost balanced on the {\em test} set: There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends.
-To compare the different methods on this classification task, the ACCURACY metric, defined as the percentage of correct classification, is used.
+To compare the different methods on this classification task, the accuracy metric, defined as the percentage of correct classification, is used.
 
@@
 Results are displayed in Table~\ref{tab:metricresults}.
-For our model using neural networks, 10 models are trained  with different seeds.
+For methods using neural networks, 10 models are trained  with different seeds.
 The average and the standard deviation of their results are computed and displayed.
@@
 \textbf{Size of the dataset.
-} In addition to the results on the fashion dataset gathering 10000 time series, the behaviour of the HERMES model is analyzed when it is trained on smaller datasets: two experiments were performed, HERMES models were trained on a reduce dataset of 1000 time series and on a reduced dataset of 100 time series.
-Both samples of time series are selected randomly.
+} In addition to the results on the whole fashion dataset, the robustness of the HERMES model is analyzed when it is trained on smaller datasets.
+Two experiments are performed on a sub sample of respectively 1000 and 100 randomly selected time series.
 Results are given in Table~\ref{tab:1000metricresults}.
-
 The hybrid framework \textit{hermes-tbats} achieves the best performance in terms of global accuracy on both datasets.
@@
 Providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require large amounts of data to do so.
-Our model needs less data to be trained and to obtain interesting performance.
+By contrast, the HERMES approach can rely on its first statistical part and consequently needs less data to be trained and to obtain interesting performance.
 
@@
  \centering
- \resizebox{1.\textwidth}{!}{ 
+ \resizebox{0.8\textwidth}{!}{ 
   \begin{tabular}{l||llll}
@@
 For the RNN part, the same architecture as described in Section~\ref{sec:fashiontraining} is used.
-The Adam optimizer is used with a learning rate equal to  0.0005, the batch size is set to 8 and the MASE is directly used as the loss function.
+The Adam optimizer is used and the MASE is directly used as the loss function.
 Finally a rolling window is applied on the train set so as to increase the number of examples and improve the training process.
-Three windows are computed per sequence for the RNN train set.
-Results of the grid search on the M4 weekly dataset can be found in \ref{sec:m4gridsearch}.
+The number of slinding windows, the learning rate, the batch size, the RNN architecture and input size are set using a grid search and detailled in \ref{sec:m4gridsearch}.
 

### 2023-04-24 tmlr_submission/hermes_paper_submission/hermes_paper.tex
add anonymized github link

@@
 Our contribution is  twofold.
-We first provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} an appealing fashion dataset gathering \numberts\ weekly fashion time series.
+We first provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} an appealing fashion dataset gathering \numberts\ weekly fashion time series.
 As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviours of influencers.
-Secondly, to leverage such a complex and rich dataset, we propose a new hybrid forecasting model\footnote[2]{\url{https://github.com/etidav/HERMES}}.
+Secondly, to leverage such a complex and rich dataset, we propose a new hybrid forecasting model\footnotemark.
 Our approach combines per-time-series parametric models with seasonal components and a global recurrent neural network to include sporadic external signals.
@@
 
-With this paper, we provide publicly\footnote[1]{\url{http://files.heuritech.com/raw_files/f1_fashion_dataset.tar.xz}} a sample of $\numberts$ normalized fashion trends for men and women, over 9 different categories and 5 different markets.
+With this paper, we provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} a sample of $\numberts$ normalized fashion trends for men and women, over 9 different categories and 5 different markets.
 Each sequence has 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
@@
 See \ref{sec:fashiongridsearch} for additional results concerning the loss function choice and \ref{sec:m4gridsearch} for a complete grid search example.
-The code is developed in Python using the Tensorflow library and publicly available\footnote[1]{\url{https://github.com/etidav/HERMES}}.
+The code is developed in Python using the Tensorflow library and publicly available\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}}.
 It allows the use of GPU to speed up the training process.

### 2023-05-16 tmlr_submission/hermes_paper_revision/answers_reviews.tex
add answers_reviews.tex in the tlmr revision dir

\documentclass[10pt]{article} % For LaTeX2e
\usepackage{tmlr}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{tmlr}
% To de-anonymize and remove mentions to TMLR (for example for posting to preprint servers), instead use the following:
%\usepackage[preprint]{tmlr}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{amssymb,amsmath,amsthm}
\usepackage[pdftex]{graphicx}

\title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}

% Authors must not appear in the submitted version. They should be hidden
% as long as the tmlr package is used without the [accepted] or [preprint] options.
% Non-anonymous submissions will be rejected without review.

\author{\name \'Etienne David \email etienne.david@heuritech.com \\
      \addr SAMOVAR, Télécom SudParis,\\
      Institut Polytechnique de Paris, 91120 Palaiseau, France
      \AND
      \name Jean Bellot \email jean.bellot@heuritech.com \\
      \addr Heuritech, \\
      6 Rue de Braque, 75003 Paris
      \AND
      \name Sylvain Le Corff \email sylvain.lecorff@gmail.com\\
      \addr LPSM, \\
      Sorbonne Université, UMR CNRS 8001, 75005, Paris
      }

% The \author macro works with any number of authors. Use \AND 
% to separate the names and addresses of multiple authors.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\def\month{01}  % Insert correct month for camera-ready version
\def\year{2023} % Insert correct year for camera-ready version
\def\openreview{\url{https://openreview.net/forum?id=XXXX}} % Insert correct link to OpenReview for camera-ready version

\begin{document}

\maketitle

We would like to thank the reviewers and the associate editor for their constructive feedback, and their appreciation of the paper. We have carefully considered all the comments listed by the reviewers and we proposed a revision of the paper accordingly. You can find below an overview of the major modifications of the manuscript followed by detailed responses to the reviewers.

\section*{Major changes}

\section*{Reviewer 1}

\begin{itemize}
	\item {\em ``The paper does not provide a clear motivation or literature review for the choice of per-time-series models.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper could benefit from a more detailed discussion of the limitations of the proposed approach and potential avenues for future work.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper could also benefit from a more thorough comparison with existing methods, including a discussion of their strengths and weaknesses in relation to the proposed approach.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should provide a clear motivation or literature review for the choice of per-time-series models.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should explain why exponential smoothing and TBATS are chosen as the predictors, and how they compare to other possible choices such as ARIMA or HMM.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should compare with more existing methods.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should explain how HERMES handles different types of time series, such as stationary, non-stationary, seasonal, or sporadic.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should discuss the potential positive and negative impacts of the proposed model and dataset on the society and the environment.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should address the privacy and consent issues of using social media images and data to construct the fashion dataset and the weak signals.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should explain how the data is collected, processed, and anonymized, and what are the ethical and legal implications of this process.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should also acknowledge the potential risks or biases of using social media data to represent fashion trends, such as cultural diversity, inclusivity, or sustainability.''} \medskip
	\textbf{Author response:} \\	
\end{itemize}

\section*{Reviewer 2}

\begin{itemize}
	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\		
\end{itemize}

\subsection*{Reviewer 3}

\begin{itemize}
	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\		
\end{itemize}

\end{document}

### 2023-05-19 tmlr_submission/hermes_paper_revision/hermes_paper.tex
update revision with new results

--- 2023-04-24 tmlr_submission/hermes_paper_submission/hermes_paper.tex
@@
 With our fashion expertise, we detected several groups of highly influential fashion users.
-Analyzing their specific behaviours on social media, we associate with each time series an external weak signal representing the same fashion trends on a sub-category of users.
+Analyzing their specific behaviours on social media, we associate with each time series an external weak signal representing the same fashion trends on \textcolor{gray}{a} \textcolor{orange}{this} sub-category of users.
 They are called weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal.
@@
 Following this work, we present in this paper HERMES, a new hybrid recurrent model for time series forecasting with inclusion of external signals.
-This new architecture is decomposed  into two parts: local predictors and a global corrector.
+This new architecture is decomposed  into two parts: \textcolor{gray}{local predictors and a global corrector.
 First, a per-time-series parametric statistical model is trained on each sequence.
-Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.
-The external weak signals reveal the real potential of the hybrid approach: a global neural network, able to leverage large amounts of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.
+Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.} \textcolor{orange}{i) First, a per-time-series parametric statistical model is trained on each sequence.
+ii) Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.} The external weak signals reveal the real potential of the hybrid approach: a global neural network, able to leverage large amounts of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.
 
@@
 Then, the proposed forecasting approach HERMES is presented in Section~\ref{sec:hybrid}.
-Section~\ref{sec:exp} describes the model results and comparisons with several benchmarks on the 2 different use cases: the fashion dataset and the M4 competition weekly dataset.
+Section~\ref{sec:exp} describes the model results and comparisons with several benchmarks on \textcolor{gray}{the} 2 different use cases: the fashion dataset and the M4 competition weekly dataset.
 Finally, a general conclusion and some research perspectives are given in  Section~\ref{sec:conclusion}.
@@
 \end{equation}
+
 During the M4 competition, the hybrid model of \citet{smyl2020} was based on a multiplicative exponential smoothing model as the time-series-specific predictor.
@@
 In this paper, a more general framework able to deal with any kind of per-time-series models is provided.
-In Section~\ref{sec:exp}, two versions of our framework are proposed.
-The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020} and the second one uses a TBATS model \citep{alysha2011} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.
+\textcolor{orange}{Thus, the choice of the parametric model can be adjusted depending on the nature of the time series.
+The only limitation is the computation time.
+For instance, hidden Markov models or ARIMA models are powerfull parametric methodes but they are also computational expensive to fit.
+Choosing these approaches as per-time-series predictor may considerably slow the overall training process of the hybrid model.
+In Section~\ref{sec:exp}, three declinations of the hybrid framework are presented using different per-time-series predictors.
+The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020}, the second one use a method called Thetam as per-time-series predictor \citep{hyndman2020} and the last one uses a TBATS model \citep{alysha2011}.} \textcolor{gray}{In Section~\ref{sec:exp}, two versions of our framework are proposed.
+The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020} and the second one uses a TBATS model \citep{alysha2011} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.}
 
-%In the specific application of fashion trends prediction, two main forms of standard weaknesses were detected and defined for univariate parametric forecasts.
-The first one is a weakness of definition, when the model is not well defined for its forecasting task.
-For instance, an additive model provides good predictions on time series with additive seasonality but fails at handling multiplicative seasonalities.
-The second form, harder to detect and correct, is the weakness of information.
 For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence.
@@
 A complete description and references for these models can be found in \citet{hyndman2020}.
-As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.
-Two versions of HERMES are proposed.
+\textcolor{orange}{As deep learning apporaches, two recurrent neural networks are proposed.
+They are both composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52.
+The first one (called \textit{lstm}) has only access to the main signal while the second one (called \textit{lstm-ws}) has access to the main and the external signal.} \textcolor{gray}{As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.}
+
+\textcolor{orange}{
+A strength of the proposed HERMES framework is that it can handle any kind of parametric model.
+This choice of per-time-series predictor is central in the approach and have to be done regarding the use case and the nature of the time series.
+Thus, three declinations of the HERMES approach are proposed on the Fashion dataset using different per-time-series predictors: Ets, Tbats and Thetam.
+They are called respectively \textit{hermes-ets}, \textit{hermes-tbats} and \textit{hermes-thetam} according to the per-time-series model choice.
+For each of them, a variation with the inclusion of the weak signals (\textit{-ws}) is presented.}
+\textcolor{gray}{Two versions of HERMES are proposed.
 They are called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
@@
 They are referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}.
-In order to provide a fair comparison, a \textit{lstm} with the weak signals named \textit{lstm-ws} is trained.
+In order to provide a fair comparison, a \textit{lstm} with the weak signals named \textit{lstm-ws} is trained.}
 
@@
 
-Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slightly outperform the alternatives in terms of MASE and are stable across the different trainings.
-Regarding \textit{hermes-ets},   although it is very similar to the baseline \citet{smyl2020}, its accuracy remains low in comparison to the \textit{lstm} benchmark or HERMES using TBATS.
+\textcolor{orange}{Considering the new HERMES approaches, all the different versions show consequent improvements regarding their per-time-series predictors in terms of MASE.
+\textit{Hermes-tbats} largely outperforms the two other declinations and all the benchmarks on the fashion dataset.
+This result highlight to important point of the proposed hybrid model: i) The final accuracy of the model is strongly impacted by the choice of per-time-series predictor ii) If the per-time-series predictor is well chosen regarding the nature of the time series, the resulting HERMES model can show impressive results and outperformance state-of-the-art approaches.}
+\textcolor{gray}{Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slightly outperform the alternatives in terms of MASE and are stable across the different trainings.
+Regarding \textit{hermes-ets},   although it is very similar to the baseline \citet{smyl2020}, its accuracy remains low in comparison to the \textit{lstm} benchmark or HERMES using TBATS.}
 
+\textcolor{orange}{Regarding the impact of the weak signals, improvement in terms of MASE remains low between methodes without and with the weak signal.
+However, an interesting improvement can be noted with the accuracy metric.
+Weak signals seem to grandtully help methods using them to better detect emerging and declining trends.
+Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} predictions and illustrates some Tbats weaknesses that can be corrected by the hybrid approach.}
+\textcolor{gray}{
 Models using our weak signals perform similarly as without-weak-signals models for the MASE.
 Interestingly, weak signals significantly improve the accuracy in detecting emerging and declining trends.
-Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} models and some weaknesses that can be corrected.
+Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} models and some weaknesses that can be corrected.}
 
@@
      \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
-     \textit{thetam}  && 0.844 && -&&& 0.482 && - &\\
+     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.0.845} && \textcolor{orange}{-} &&& \textcolor{orange}{0.463} && \textcolor{orange}{-}\\
      \textit{arima} && 0.826 && -&&& 0.464 && - & \\
      \textit{ets} && 0.807 && -&&& 0.449 && - & \\
+     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.485} && \textcolor{orange}{-}\\
      \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
      \textit{hermes-ets-ws} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
+     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.764} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.497} && \textcolor{orange}{0.005}\\
+     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.760} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.520}} && \textcolor{orange}{0.01}\\
      \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
@@
      \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
-     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& \textbf{0.510} && 0.005 &\\
+     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& 0.510 && 0.005 &\\
   \end{tabular}
@@
 By contrast, the HERMES approach can rely on its first statistical part and consequently needs less data to be trained and to obtain interesting performance.
+\textcolor{orange}{We can nevertheless note that the gain brought by the error-corrector recurrent model decreases as the size of the dataset diminish.}
 
@@
      \textit{snaive} && 0.871 & - \\
-     \textit{thetam}  && 0.849 & - \\
+     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.837} & \textcolor{orange}{-} \\
      \textit{arima} && 0.821 & - \\
-     \textit{ets} && 0.801 & - \\
+     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.801} & \textcolor{orange}{-} \\
+     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.788} & \textcolor{orange}{-} \\
+     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.768} & \textcolor{orange}{0.005} \\
      \textit{stlm} && 0.765 & - \\
+     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.764} & \textcolor{orange}{0.004} \\
      \textit{lstm} && 0.740 & 0.007 \\
@@
      \textit{snaive} && 0.876 & - \\
-     \textit{thetam}  && 0.823 & - \\
+     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.822} & \textcolor{orange}{-} \\
      \textit{arima} && 0.814 & - \\
-     \textit{ets} && 0.785 & - \\
+     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.808} & \textcolor{orange}{0.006} \\
+     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.792} & \textcolor{orange}{0.003} \\
+     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.786} & \textcolor{orange}{-} \\
+     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.767} & \textcolor{orange}{-} \\
      \textit{lstm} && 0.767 & 0.045 \\
@@
 \appendix
+
 \section{M4 weekly dataset, Ensembling training and results}

### 2023-05-22 tmlr_submission/hermes_paper_revision/hermes_paper.tex
add new result for tmlr revision

@@
 A complete description and references for these models can be found in \citet{hyndman2020}.
-\textcolor{orange}{As deep learning apporaches, two recurrent neural networks are proposed.
-They are both composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52.
-The first one (called \textit{lstm}) has only access to the main signal while the second one (called \textit{lstm-ws}) has access to the main and the external signal.} \textcolor{gray}{As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.}
+\textcolor{orange}{To complete the statistical benchmarks, the Prophet model introduced in \citet{Taylor2017} is proposed and implemented with the available package bearing the same name \texttt{prophet}.
+As deep learning apporaches, Three models based on recurrent neural networks are proposed.
+They are called \textit{lstm}, \textit{lstm-ws} and \textit{deepar}.
+Concerning \textit{lstm} and \textit{lstm-ws}, they are both composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52.
+The first one (\textit{lstm}) has only access to the main signal while the second one (\textit{lstm-ws}) has access to the main and the external signal.
+The last approach is the recent state-of-the-art model called DeepAR and introduced in \citet{salinas2020}.
+The python package \texttt{GluonTS} \citep{Alexandrov2020} was used to train the DeepAR approach on the fashion dataset and a grisearch on the main parameters have been done.} \textcolor{gray}{As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.}
 
@@
 \textit{Hermes-tbats} largely outperforms the two other declinations and all the benchmarks on the fashion dataset.
-This result highlight to important point of the proposed hybrid model: i) The final accuracy of the model is strongly impacted by the choice of per-time-series predictor ii) If the per-time-series predictor is well chosen regarding the nature of the time series, the resulting HERMES model can show impressive results and outperformance state-of-the-art approaches.}
+This result highlight to important point of the proposed hybrid model: i) The final accuracy of the model is strongly impacted by the choice of per-time-series predictor ii) If the per-time-series predictor is well chosen regarding the nature of the time series, the resulting HERMES model can show impressive results and outperformance state-of-the-art approaches such as DeepAR.}
 \textcolor{gray}{Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slightly outperform the alternatives in terms of MASE and are stable across the different trainings.
@@
      \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
-     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.0.845} && \textcolor{orange}{-} &&& \textcolor{orange}{0.463} && \textcolor{orange}{-}\\
+     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.845} && \textcolor{orange}{-} &&& \textcolor{orange}{0.463} && \textcolor{orange}{-}\\
      \textit{arima} && 0.826 && -&&& 0.464 && - & \\
@@
      \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.764} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.497} && \textcolor{orange}{0.005}\\
-     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.760} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.520}} && \textcolor{orange}{0.01}\\
+     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.760} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.520}} && \textcolor{orange}{0.010}\\
      \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
+     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.752} && \textcolor{orange}{0.018} &&& \textcolor{orange}{0.459} && \textcolor{orange}{0.015}\\
      \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
@@
 We can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases.
-On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms the \textit{lstm}.
-Providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require large amounts of data to do so.
+On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms \textcolor{orange}{deep-model-based approach such as \textit{lstm} of \textit{deepar}}.
+In fact, providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require large amounts of data to do so.
 By contrast, the HERMES approach can rely on its first statistical part and consequently needs less data to be trained and to obtain interesting performance.
@@
      \textit{lstm} && 0.740 & 0.007 \\
+     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.738} & \textcolor{orange}{0.017} \\
      \textit{tbats} && 0.734 & - \\
@@
      \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.808} & \textcolor{orange}{0.006} \\
+     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.804} & \textcolor{orange}{0.024} \\
      \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.792} & \textcolor{orange}{0.003} \\

### 2023-05-23 tmlr_submission/hermes_paper_revision/hermes_paper.tex
minor change introduction

@@
 Our contribution is  twofold.
-We first provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} an appealing fashion dataset gathering \numberts\ weekly fashion time series.
+We first provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} an appealing \textcolor{gray}{fashion} dataset gathering \numberts\ weekly fashion time series.
 As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviours of influencers.
@@
 Multivariate time series forecasting is a widespread statistical problem with  many applications, see for instance \citet{sarkka2013, douc2014, zucchini2017} and the numerous references therein.
-Parametric generative models provide explainable predictions with statistical guarantees based on a precise modeling of the predictive distributions of new data based on a record of past observations.
-Calibrating these models, for instance using maximum likelihood inference, often requires a fair amount of tuning to design a time series-specific model to provide  accurate forecasts and sharp confidence intervals.
-Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
+Parametric generative models provide explainable predictions with statistical guarantees \textcolor{gray}{based on} \textcolor{orange}{owing to} a precise modeling of the predictive distributions of new data based on a record of past observations.
+\textcolor{gray}{Calibrating these models, for instance using maximum likelihood inference, often requires a fair amount of tuning to design a time series-specific model to provide  accurate forecasts and sharp confidence intervals.} \textcolor{orange}{Calibrating these models, for instance using maximum likelihood inference, often requires a fair amount of tuning so as to design time-series-specific models able to provide  accurate forecasts and sharp confidence intervals.} Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
 The exponential smoothing model \citep{Brown1961}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \citep{alysha2011}, or the ARIMA with the Box-Jenkins approach \citep{box2015} are for instance very popular parametric generative models.
@@
 In many fields, single or few time series have become thousands of sequences with various statistical properties.
-In this new context, classical time series specific statistical models show limitations when dealing with numerous heterogeneous data.
-Recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \citet{ hochreiter1997,vaswani2017, siami2018, li2019, lim2019,salinas2020}.
+In this new context, classical \textcolor{gray}{time series specific} \textcolor{orange}{time-series-specific} specific statistical models show limitations when dealing with numerous heterogeneous data.
+\textcolor{orange}{By constrast,} recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \citet{ hochreiter1997,vaswani2017, siami2018, li2019, lim2019,salinas2020}.
 The DeepAR model proposed in \citet{salinas2020} provides a global model from many time series based on a multi-layer recurrent neural network with LSTM cells.

### 2023-05-26 tmlr_submission/hermes_paper_revision/hermes_paper.tex
add new section in Appendice

@@
 
+\textcolor{orange}{
+\section{Fashion dataset: a study of sub-samples of time series sharing the same behaviour}
+}
+\textcolor{orange}{
+On a large dataset as the Fashion dataset, looking at aggregated metrics can often hide relevant results, especially on sub-samples sharing the same behaviours.
+To illustrate this point, a study of 4 sub-samples of the Fashion dataset is proposed in this section.
+Their are defined as follows:
+\begin{itemize}
+\item \textbf{disrupting time series}: In retail and fashion industries, a strategic issue is to correctly anticipate new trends that will burst or collapse in the next weeks, months or years.
+To detect these sub sample of trends in the Fashion dataset, the following approach is proposed: Using the \textit{snaive} model, a prediction of the last year is computed for each trend and the linked MASE.
+Finally, the dirsupting time series are the 1000 time series with the highest MASE.
+\item \textbf{stable time series}: By contrast, a group a stable trend a presented.
+To define them, the same methodology as the previous group is used.
+We define them as the time series where the \textit{snaive} prediction reachs the lowest MASE.
+\item \textbf{seasonal time series}: Another relevant group of time series is sequences showing a strong seasonal patern.
+So as to detect them, we compute for each trend the seasonality strength metric introduced in \citet{wang2006}.
+The seasonal time series group is the 1000 fashion time series with highest seasonality strength.
+\item \textbf{noisy time series}: Finally, several time series of the Fashion dataset represent niche trends only worn and posted on social media by a few people.
+The average volume for these sequences is low resulting in sporadic and noisy time series difficult to forecast.
+In order to detect them, we use the seasonality and trend strenght metrics presented in \citet{wang2006}.
+For each time series, the average of these two quantities is computed and we define the time series group as the 1000 sequences with the lowest averages.
+\end{itemize}
+Table~\ref{tab:fashionsubsample} displays the MASE of each models introduced in Section~\ref{sec:exp} on the 4 sub-samples of time series.
+Several relevant results can be highlited.
+Firstly, models using the influencer weak signals strongly outperform other candidates on the disruptive time series.
+This result is even more visible with the HERMES approach where variations using the weak signals are always better than the ones without.
+These results illustrate the really predictive strenght of the influencer signals proposed in the Fashion dataset and prove empirically the impact of influencers on the fashion industries.
+Secondly, on stable time series and seasonal time series, a relevant interest of the hybrid approach is revealed.
+Looking at the result of \textit{hermes-tbats}, we can see that this hybrid model can use the strength of \textit{tbats} to compute a first accurate prediction and then, use the strength of a global neural network to understand more complex patterns.
+This strenght is even more visible on seasonal time series where hybrid approach largely outperform then neural network models presented in the benchmarks.
+Finally, on noisy time series, we can see that neural network methodes reach the highest accuracy and are the less impacted by these difficult trend.
+Futhermore, for all the HERMES approaches, we can note that the final hybrid predictions and the per-time-series models' predictions are the same.
+The error-correction model doesn't try to predict the noise and let the per-time-series models' predictions as they are.}
+
+\begin{table}
+  \caption{Results summary on 4 differents sub-sample of  Fashion time series: i) disrupting time series, ii) stable time series, iii) seasonal time series and iv) noisy time series.}\vspace{0.5cm} 
+ \centering
+ \resizebox{0.8\textwidth}{!}{
+  \begin{tabular}{l||llll}
+    \multicolumn{4}{c}{\textit{disrupting} time series}\\
+    &&\multicolumn{2}{c}{\textbf{MASE}} \\
+    &&  \textit{mean}  & \textit{std}  \\
+	 \hline
+	 &&& \\
+     \textit{snaive} && 1.455 & -\\ 
+	 \textit{thetam} && 1.314 & -\\ 
+	 \textit{ets} && 1.27 & -\\ 
+	 \textit{arima} && 1.256 & -\\ 
+	 \textit{tbats} && 1.229 & -\\ 
+	 \textit{hermes-thetam} && 1.209 & 0.005\\ 
+	 \textit{hermes-ets} && 1.202 & 0.007\\ 
+	 \textit{stlm} && 1.198 & -\\ 
+	 \textit{hermes-tbats} && 1.195 & 0.01\\ 
+	 \textit{prophet} && 1.193 & -\\ 
+	 \textit{deepar} && 1.18 & 0.03\\ 
+	 \textit{lstm} && 1.15 & 0.01\\ 
+	 \textit{hermes-thetam-ws} && 1.145 & 0.019\\ 
+	 \textit{hermes-ets-ws} && 1.131 & 0.024\\ 
+	 \textit{hermes-tbats-ws} && 1.092 & 0.007\\ 
+	 \textit{lstm-ws} && 1.086 & 0.009\\  \vspace{0.5cm}\\
+  \end{tabular}\hspace{1cm}
+  \begin{tabular}{l||llll}
+   \multicolumn{4}{c}{\textit{stable} time series}\\
+   &&\multicolumn{2}{c}{\textbf{MASE}} \\
+    &&  \textit{mean}  & \textit{std}  \\
+	\hline
+	 &&& \\
+     \textit{prophet} && 0.629 & -\\ 
+	 \textit{thetam} && 0.615 & -\\ 
+	 \textit{ets} && 0.611 & -\\ 
+	 \textit{arima} && 0.565 & -\\ 
+	 \textit{hermes-ets-ws} && 0.555 & 0.007\\ 
+	 \textit{snaive} && 0.536 & -\\  
+	 \textit{deepar} && 0.531 & 0.024\\ 
+ 	 \textit{hermes-thetam-ws} && 0.522 & 0.004\\ 
+	 \textit{hermes-ets} && 0.518 & 0.002\\ 
+	 \textit{stlm} && 0.513 & -\\ 
+	 \textit{hermes-thetam} && 0.508 & 0.005\\ 
+	 \textit{tbats} && 0.501 & -\\ 
+	 \textit{lstm-ws} && 0.492 & 0.007\\ 
+	 \textit{hermes-tbats-ws} && 0.477 & 0.008\\ 
+	 \textit{lstm} && 0.47 & 0.004\\ 
+	 \textit{hermes-tbats} && 0.451 & 0.002\\  \vspace{0.5cm}\\
+  \end{tabular}
+ }
+ \resizebox{0.8\textwidth}{!}{ 
+  \begin{tabular}{l||llll}
+    \multicolumn{4}{c}{\textit{seasonal} time series}\\
+    &&\multicolumn{2}{c}{\textbf{MASE}} \\
+    &&  \textit{mean}  & \textit{std}  \\
+	 \hline
+	 &&& \\
+     \textit{snaive} && 0.895 & -\\ 
+	 \textit{ets} && 0.895 & -\\ 
+	 \textit{prophet} && 0.851 & -\\ 
+	 \textit{deepar} && 0.836 & 0.035\\ 
+	 \textit{lstm-ws} && 0.829 & 0.014\\ 
+	 \textit{thetam} && 0.826 & -\\ 
+	 \textit{lstm} && 0.823 & 0.013\\ 
+	 \textit{hermes-thetam} && 0.815 & 0.008\\ 
+	 \textit{tbats} && 0.81 & -\\ 
+	 \textit{hermes-ets-ws} && 0.809 & 0.01\\ 
+	 \textit{hermes-thetam-ws} && 0.808 & 0.008\\ 
+	 \textit{arima} && 0.805 & -\\ 
+	 \textit{stlm} && 0.786 & -\\ 
+	 \textit{hermes-ets} && 0.785 & 0.003\\ 
+	 \textit{hermes-tbats-ws} && 0.777 & 0.012\\ 
+	 \textit{hermes-tbats} && 0.772 & 0.003\\ 
+  \end{tabular}\hspace{1cm}
+  \begin{tabular}{l||llll}
+   \multicolumn{4}{c}{\textit{noisy} time series}\\
+   &&\multicolumn{2}{c}{\textbf{MASE}} \\
+    &&  \textit{mean}  & \textit{std}  \\
+	\hline
+	 &&& \\
+     \textit{snaive} && 0.842 & -\\ 
+	 \textit{hermes-ets-ws} && 0.739 & 0.005\\ 
+	 \textit{hermes-ets} && 0.726 & 0.002\\ 
+	 \textit{ets} && 0.721 & -\\ 
+	 \textit{thetam} && 0.717 & -\\ 
+	 \textit{stlm} && 0.715 & -\\ 
+	 \textit{prophet} && 0.698 & -\\ 
+	 \textit{arima} && 0.696 & -\\ 
+	 \textit{hermes-thetam-ws} && 0.672 & 0.003\\ 
+	 \textit{hermes-thetam} && 0.669 & 0.001\\ 
+	 \textit{deepar} && 0.661 & 0.007\\ 
+	 \textit{hermes-tbats-ws} && 0.647 & 0.006\\ 
+	 \textit{tbats} && 0.646 & -\\ 
+	 \textit{hermes-tbats} && 0.644 & 0.003\\ 
+	 \textit{lstm-ws} && 0.637 & 0.004\\ 
+	 \textit{lstm} && 0.636 & 0.003\\
+  \end{tabular}
+ }
+ \label{tab:fashionsubsample}
+\end{table}
+
 \section{M4 weekly dataset, Ensembling training and results}

### 2023-05-30 tmlr_submission/hermes_paper_revision/hermes_paper.tex
Update hermes_paper.tex

@@
 First, a per-time-series parametric statistical model is trained on each sequence.
-Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.} \textcolor{orange}{i) First, a per-time-series parametric statistical model is trained on each sequence.
-ii) Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.} The external weak signals reveal the real potential of the hybrid approach: a global neural network, able to leverage large amounts of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.
+Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.} \textcolor{orange}{First, a per-time-series parametric statistical model is trained on each sequence.
+Then, a global recurrent neural network is trained to evaluate and correct the forecast of the first collection of models.} The external weak signals reveal the real potential of the hybrid approach: a global neural network, able to leverage large amounts of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.
 
@@
 \textcolor{orange}{Thus, the choice of the parametric model can be adjusted depending on the nature of the time series.
-The only limitation is the computation time.
-For instance, hidden Markov models or ARIMA models are powerfull parametric methodes but they are also computational expensive to fit.
-Choosing these approaches as per-time-series predictor may considerably slow the overall training process of the hybrid model.
-In Section~\ref{sec:exp}, three declinations of the hybrid framework are presented using different per-time-series predictors.
+The only limitation is the computation time as we aim at forecasting thousands of time series simultaneously.
+For instance, hidden Markov models provide a very appealing framework but inference of such models requires computationally costly iterative procedures such as Expecation Maximization-based algorithms often combined with Monte Carlo estimates of unknown expectations.
+Choosing these approaches as per-time-series predictor would considerably slow the overall training process of the hybrid model.}
+
+\textcolor{orange}{In Section~\ref{sec:exp}, we introduce three declinations of the hybrid framework  using different per-time-series predictors to highlight the adaptability of our approach.
 The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020}, the second one use a method called Thetam as per-time-series predictor \citep{hyndman2020} and the last one uses a TBATS model \citep{alysha2011}.} \textcolor{gray}{In Section~\ref{sec:exp}, two versions of our framework are proposed.
@@
 A complete description and references for these models can be found in \citet{hyndman2020}.
-\textcolor{orange}{To complete the statistical benchmarks, the Prophet model introduced in \citet{Taylor2017} is proposed and implemented with the available package bearing the same name \texttt{prophet}.
-As deep learning apporaches, Three models based on recurrent neural networks are proposed.
-They are called \textit{lstm}, \textit{lstm-ws} and \textit{deepar}.
+
+\textcolor{orange}{We also compare our model with recent recent deep learning architectures for time series.
+The Prophet model introduced in \citet{Taylor2017} is proposed and implemented with the available package bearing the same name \texttt{prophet}, and three models based on recurrent neural networks called \textit{lstm}, \textit{lstm-ws} and \textit{deepar} are used.
 Concerning \textit{lstm} and \textit{lstm-ws}, they are both composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52.
-The first one (\textit{lstm}) has only access to the main signal while the second one (\textit{lstm-ws}) has access to the main and the external signal.
+The first one (\textit{lstm}) has only access to the main signal while the second one (\textit{lstm-ws}) has also access to the external signal.
 The last approach is the recent state-of-the-art model called DeepAR and introduced in \citet{salinas2020}.
-The python package \texttt{GluonTS} \citep{Alexandrov2020} was used to train the DeepAR approach on the fashion dataset and a grisearch on the main parameters have been done.} \textcolor{gray}{As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.}
+The Python package \texttt{GluonTS} \citep{Alexandrov2020} was used to train DeepAR on the fashion dataset with a gridsearch to tune the main hyperparameters.} \textcolor{gray}{As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.}
 
@@
 A strength of the proposed HERMES framework is that it can handle any kind of parametric model.
-This choice of per-time-series predictor is central in the approach and have to be done regarding the use case and the nature of the time series.
 Thus, three declinations of the HERMES approach are proposed on the Fashion dataset using different per-time-series predictors: Ets, Tbats and Thetam.
@@
 
-\textcolor{orange}{Considering the new HERMES approaches, all the different versions show consequent improvements regarding their per-time-series predictors in terms of MASE.
+\textcolor{orange}{All the different versions of HERMES show consequent improvements regarding their per-time-series predictors in terms of MASE.
 \textit{Hermes-tbats} largely outperforms the two other declinations and all the benchmarks on the fashion dataset.
-This result highlight to important point of the proposed hybrid model: i) The final accuracy of the model is strongly impacted by the choice of per-time-series predictor ii) If the per-time-series predictor is well chosen regarding the nature of the time series, the resulting HERMES model can show impressive results and outperformance state-of-the-art approaches such as DeepAR.}
+This result highlights two important features of the proposed hybrid model: i) the final accuracy of the model is strongly impacted by the choice of the per-time-series predictor and ii) if the per-time-series predictor is well chosen regarding the nature of the time series, the resulting HERMES model outperforms state-of-the-art approaches such as DeepAR.}
 \textcolor{gray}{Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slightly outperform the alternatives in terms of MASE and are stable across the different trainings.
@@
 
-\textcolor{orange}{Regarding the impact of the weak signals, improvement in terms of MASE remains low between methodes without and with the weak signal.
-However, an interesting improvement can be noted with the accuracy metric.
-Weak signals seem to grandtully help methods using them to better detect emerging and declining trends.
+\textcolor{orange}{Regarding the impact of the weak signals, Table~\ref{tab:metricresults} highlights an interesting improvement of the accuracy metric when weak signals are included.
 Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} predictions and illustrates some Tbats weaknesses that can be corrected by the hybrid approach.}
@@
 By contrast, the HERMES approach can rely on its first statistical part and consequently needs less data to be trained and to obtain interesting performance.
-\textcolor{orange}{We can nevertheless note that the gain brought by the error-corrector recurrent model decreases as the size of the dataset diminish.}
+\textcolor{orange}{We can nevertheless note that the gain brought by the error-corrector recurrent model decreases as the size of the dataset diminishes.}
 

### 2023-05-30 tmlr_submission/hermes_paper_revision/answers_reviewer_1.tex
add answers_revierwer_1.tex

\documentclass[10pt]{article} % For LaTeX2e
\usepackage{tmlr}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{tmlr}
% To de-anonymize and remove mentions to TMLR (for example for posting to preprint servers), instead use the following:
%\usepackage[preprint]{tmlr}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{amssymb,amsmath,amsthm}
\usepackage[pdftex]{graphicx}

\title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}

% Authors must not appear in the submitted version. They should be hidden
% as long as the tmlr package is used without the [accepted] or [preprint] options.
% Non-anonymous submissions will be rejected without review.

\author{\name \'Etienne David \email etienne.david@heuritech.com \\
      \addr SAMOVAR, Télécom SudParis,\\
      Institut Polytechnique de Paris, 91120 Palaiseau, France
      \AND
      \name Jean Bellot \email jean.bellot@heuritech.com \\
      \addr Heuritech, \\
      6 Rue de Braque, 75003 Paris
      \AND
      \name Sylvain Le Corff \email sylvain.lecorff@gmail.com\\
      \addr LPSM, \\
      Sorbonne Université, UMR CNRS 8001, 75005, Paris
      }

% The \author macro works with any number of authors. Use \AND 
% to separate the names and addresses of multiple authors.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\def\month{01}  % Insert correct month for camera-ready version
\def\year{2023} % Insert correct year for camera-ready version
\def\openreview{\url{https://openreview.net/forum?id=XXXX}} % Insert correct link to OpenReview for camera-ready version

\begin{document}

\maketitle

We would like to thank the reviewer for his appreciation of the paper and his constructive feedback. We have carefully considered all the listed comments and we will propose a revision of the paper accordingly when all the reviews will be published. In the meantime, you can find below detailed responses to the reviewer's remarks and an overview of some of the  modifications that will be added in the revision of the manuscript.

\section*{Detailed responses}

\subsection*{Requested changes:}

\begin{itemize}

	\item {\em ``The paper should provide a clear motivation or literature review for the choice of per-time-series models.''} \medskip

	\textbf{Author response:} We thank the referee for this remark and we acknowledge that we did not discuss enough about the choice of per-time-series models in the proposed paper. This comment has led to additional justifications and discussions to bring more clarity on this point. We highlight the major parameters that can guide this choice and show that the main limitation for this choice is the computational time of the per-time-series models. In addition, in the experiment section, a third HERMES variation is added using the Thetam approach as the per-times-series model. Table~\ref{tab:metricresults} presents the new version of Table 2 of the paper with the new HERMES candidate that we call \textit{hermes-thetam}. Changes between the old and the new version are written in orange. With three HERMES approaches using different per-time-series models, we want to highlight that numerous statistical approaches can be included in the proposed hybrid framework and that this choice impacts the final behaviour of the model.\\

	\item {\em ``The paper should explain why exponential smoothing and TBATS are chosen as the predictors, and how they compare to other possible choices such as ARIMA or HMM.''} \medskip

	\textbf{Author response:} We thank the referee for this remark. Indeed, The choice of the per-time-series model is really important in the proposed hybrid framework and it has to be done attentively. A main limitation in this choice is the computational time of the per-time-series models to be correctly fitted. For instance, training a HMM with the EM algorithm on thousands of time series would take days of computation. The same conclusion can be done with the ARIMA approach. Too many parameters have to be fitted and even with multiprocessing, we found that this method is too expensive to be trained on a large dataset such as the fashion dataset. Concerning TBATS, Exponential smoothing and Thetam, correctly fitting them with existing Python packages is possible in an acceptable time, from a few minutes for exponential smoothing models to a couple of hours for TBATS. To clarify this point in the paper, several justifications and comments are added in the text.\\

	\item {\em ``The paper should compare with more existing methods.''} \medskip

	\textbf{Author response:} We agree with this suggestion and this comment has led to the addition of 2 new methods in the pool of benchmark. First, the Prophet method introduced in \citet{Taylor2017} is trained and evaluated on the fashion dataset using the Python package bearing the same name \texttt{prophet}. We show that its results are not at the level of the hybrid one on the whole fashion dataset, but it starts to show a relevant accuracy level on the use case where only 100 time series are accessible. Secondly, the recent and powerful DeepAR method introduced in \citet{salinas2020} is added  and trained with the Python package \texttt{Gluonts} \citep{Alexandrov2020}. This method shows striking results on the fashion dataset and is a strong competitor of the proposed hybrid approach. As an illustration, Table~\ref{tab:metricresults} presents the new version of the Table 2 of the paper with the two new models: Prophet and DeepAR. Changes between the old and the new version are written in orange.\\

	\item {\em ``The paper should explain how HERMES handles different types of time series, such as stationary, non-stationary, seasonal, or sporadic.''} \medskip

	\textbf{Author response:} We thank the referee for this remark that leads to a new part in the appendix where 4 sub-sample of the Fashion dataset are built and forecasted separately. The first one called \textit{disrupting} time series gathers the most difficult sequences to forecast. The second one called \textit{stable} time series defines a sample of fashion time series that are stable from a year to another. The third one called \textit{seasonal} time series gathers sequences showing a strong seasonality. Finally, the last group represents the most sporadic and noisy time series of the fashion time series. Looking at the predictions of each model on these sub-sample, interesting results can be noted and a deeper analysis of the hybrid approach, the fashion dataset and the interest of the external signal is provided. Table~\ref{tab:fashionsubsample} shows the results of each method on the 4 sub-samples and it will be added in appendix as well as a section describing more precisely how the 4 samples are built.\\
\end{itemize}

\begin{table}
  \caption{Results summary on the 10000ts Fashion dataset. For each metric, the average on all our time series is computed. For approaches using neural networks, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed.}
  \centering
  \begin{tabular}{l||lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.845} && \textcolor{orange}{-} &&& \textcolor{orange}{0.463} && \textcolor{orange}{-}\\
     \textit{arima} && 0.826 && -&&& 0.464 && - & \\
     \textit{ets} && 0.807 && -&&& 0.449 && - & \\
     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.485} && \textcolor{orange}{-}\\
     \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
     \textit{hermes-ets-ws} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.764} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.497} && \textcolor{orange}{0.005}\\
     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.760} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.520}} && \textcolor{orange}{0.010}\\
     \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.752} && \textcolor{orange}{0.018} &&& \textcolor{orange}{0.459} && \textcolor{orange}{0.015}\\
     \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
     \textit{lstm-ws} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
     \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
     \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& 0.510 && 0.005 &\\
  \end{tabular}
\label{tab:metricresults}
\end{table}

\begin{table}
  \caption{Results summary on 4 differents sub-sample of  Fashion time series: i) disrupting time series, ii) stable time series, iii) seasonal time series and iv) noisy time series.}\vspace{0.5cm} 
 \centering
 \resizebox{0.8\textwidth}{!}{
  \begin{tabular}{l||llll}
    \multicolumn{4}{c}{\textit{disrupting} time series}\\
    &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
	 \hline
	 &&& \\
     \textit{snaive} && 1.455 & -\\ 
	 \textit{thetam} && 1.314 & -\\ 
	 \textit{ets} && 1.27 & -\\ 
	 \textit{arima} && 1.256 & -\\ 
	 \textit{tbats} && 1.229 & -\\ 
	 \textit{hermes-thetam} && 1.209 & 0.005\\ 
	 \textit{hermes-ets} && 1.202 & 0.007\\ 
	 \textit{stlm} && 1.198 & -\\ 
	 \textit{hermes-tbats} && 1.195 & 0.01\\ 
	 \textit{prophet} && 1.193 & -\\ 
	 \textit{deepar} && 1.18 & 0.03\\ 
	 \textit{lstm} && 1.15 & 0.01\\ 
	 \textit{hermes-thetam-ws} && 1.145 & 0.019\\ 
	 \textit{hermes-ets-ws} && 1.131 & 0.024\\ 
	 \textit{hermes-tbats-ws} && 1.092 & 0.007\\ 
	 \textit{lstm-ws} && 1.086 & 0.009\\  \vspace{0.5cm}\\
  \end{tabular}\hspace{1cm}
  \begin{tabular}{l||llll}
   \multicolumn{4}{c}{\textit{stable} time series}\\
   &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
	\hline
	 &&& \\
     \textit{prophet} && 0.629 & -\\ 
	 \textit{thetam} && 0.615 & -\\ 
	 \textit{ets} && 0.611 & -\\ 
	 \textit{arima} && 0.565 & -\\ 
	 \textit{hermes-ets-ws} && 0.555 & 0.007\\ 
	 \textit{snaive} && 0.536 & -\\  
	 \textit{deepar} && 0.531 & 0.024\\ 
 	 \textit{hermes-thetam-ws} && 0.522 & 0.004\\ 
	 \textit{hermes-ets} && 0.518 & 0.002\\ 
	 \textit{stlm} && 0.513 & -\\ 
	 \textit{hermes-thetam} && 0.508 & 0.005\\ 
	 \textit{tbats} && 0.501 & -\\ 
	 \textit{lstm-ws} && 0.492 & 0.007\\ 
	 \textit{hermes-tbats-ws} && 0.477 & 0.008\\ 
	 \textit{lstm} && 0.47 & 0.004\\ 
	 \textit{hermes-tbats} && 0.451 & 0.002\\  \vspace{0.5cm}\\
  \end{tabular}
 }
 \resizebox{0.8\textwidth}{!}{ 
  \begin{tabular}{l||llll}
    \multicolumn{4}{c}{\textit{seasonal} time series}\\
    &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
	 \hline
	 &&& \\
     \textit{snaive} && 0.895 & -\\ 
	 \textit{ets} && 0.895 & -\\ 
	 \textit{prophet} && 0.851 & -\\ 
	 \textit{deepar} && 0.836 & 0.035\\ 
	 \textit{lstm-ws} && 0.829 & 0.014\\ 
	 \textit{thetam} && 0.826 & -\\ 
	 \textit{lstm} && 0.823 & 0.013\\ 
	 \textit{hermes-thetam} && 0.815 & 0.008\\ 
	 \textit{tbats} && 0.81 & -\\ 
	 \textit{hermes-ets-ws} && 0.809 & 0.01\\ 
	 \textit{hermes-thetam-ws} && 0.808 & 0.008\\ 
	 \textit{arima} && 0.805 & -\\ 
	 \textit{stlm} && 0.786 & -\\ 
	 \textit{hermes-ets} && 0.785 & 0.003\\ 
	 \textit{hermes-tbats-ws} && 0.777 & 0.012\\ 
	 \textit{hermes-tbats} && 0.772 & 0.003\\ 
  \end{tabular}\hspace{1cm}
  \begin{tabular}{l||llll}
   \multicolumn{4}{c}{\textit{noisy} time series}\\
   &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
	\hline
	 &&& \\
     \textit{snaive} && 0.842 & -\\ 
	 \textit{hermes-ets-ws} && 0.739 & 0.005\\ 
	 \textit{hermes-ets} && 0.726 & 0.002\\ 
	 \textit{ets} && 0.721 & -\\ 
	 \textit{thetam} && 0.717 & -\\ 
	 \textit{stlm} && 0.715 & -\\ 
	 \textit{prophet} && 0.698 & -\\ 
	 \textit{arima} && 0.696 & -\\ 
	 \textit{hermes-thetam-ws} && 0.672 & 0.003\\ 
	 \textit{hermes-thetam} && 0.669 & 0.001\\ 
	 \textit{deepar} && 0.661 & 0.007\\ 
	 \textit{hermes-tbats-ws} && 0.647 & 0.006\\ 
	 \textit{tbats} && 0.646 & -\\ 
	 \textit{hermes-tbats} && 0.644 & 0.003\\ 
	 \textit{lstm-ws} && 0.637 & 0.004\\ 
	 \textit{lstm} && 0.636 & 0.003\\
  \end{tabular}
 }
 \label{tab:fashionsubsample}
\end{table}

\subsection*{Broader Impact Concerns:}

\begin{itemize}
	\item {\em ``The paper should discuss the potential positive and negative impacts of the proposed model and dataset on the society and the environment.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should address the privacy and consent issues of using social media images and data to construct the fashion dataset and the weak signals.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should explain how the data is collected, processed, and anonymized, and what are the ethical and legal implications of this process.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should also acknowledge the potential risks or biases of using social media data to represent fashion trends, such as cultural diversity, inclusivity, or sustainability.''} \medskip
	\textbf{Author response:} \\	
\end{itemize}

\bibliography{hermes_paper}
\bibliographystyle{tmlr}

\end{document}

### 2023-05-31 tmlr_submission/hermes_paper_revision/answers_reviewer_1.tex
finish a v0 of answer_reviewer_1.tex

@@
 	\item {\em ``The paper should discuss the potential positive and negative impacts of the proposed model and dataset on the society and the environment.''} \medskip
-	\textbf{Author response:} \\
+
+	\textbf{Author response:} We agree with the suggestion of the referee and this point is now developed in the discussion Section.
+The proposed dataset and the HERMES model relies on neural networks and consequently, they have an impact on the environment.
+However, the aim of this work is to show that it is possible to better forecast and anticipate consumers behaviours in the retail and fashion industry.
+With a better anticipation of consumer needs, companies could better adjust their production, reduce massive wastes due to their overstocks and finally offset the environmental cost of this work.
+\\
 
 	\item {\em ``The paper should address the privacy and consent issues of using social media images and data to construct the fashion dataset and the weak signals.''} \medskip
-	\textbf{Author response:} \\
+
+	\textbf{Author response:} We thank the referee for this remark and several information concerning this issue have been added in Section 2.
+The whole creation of the dataset respects the privacy and data protection regulations, including the General Data Protection Regulation.
+Concerning the image recovery on social media, only public accounts have been analysed and the accounts name were anonymized before any processing.
+Concerning the time series, all the trends names have been anonymized and only macro information such as the geolocalisation, the type of cloth and the gender are revealed publicly.\\
 
 	\item {\em ``The paper should explain how the data is collected, processed, and anonymized, and what are the ethical and legal implications of this process.''} \medskip
-	\textbf{Author response:} \\
+
+	\textbf{Author response:} We agree with the referee and  we added several sentences in the Section 2 to clarify this point. \\
 
 	\item {\em ``The paper should also acknowledge the potential risks or biases of using social media data to represent fashion trends, such as cultural diversity, inclusivity, or sustainability.''} \medskip
-	\textbf{Author response:} \\	
+
+	\textbf{Author response:} We totally agree with the referee.
+The question of representing the fashion sphere through social media raises a lot of interrogation.
+First of all, an important part of this work was to design a correct normalization process to remove the most visible biases bring with social media.
+Then, by proposing time series splitted by geo zone, we have tried to have an accurate representation of the diversity of behaviours that exists all around the world.
+We acknowledge that the proposed geozones may seem large.
+A future work could be to built trends at country level.
+Finally, by proposing a global model to forecast all the fashion trends, it is possible that rare patterns may not be correctly learned by the proposed framework.
+A future relevant work would be to learn models with latent processes and an unsupervised learning to explore more deeper the time series included in the Fashion dataset.\\
 \end{itemize}

### 2023-05-31 tmlr_submission/hermes_paper_revision/answers_reviewer_1.tex
update of the main text and answer to the first reviewer

@@
 The whole creation of the dataset respects the privacy and data protection regulations, including the General Data Protection Regulation.
-Concerning the image recovery on social media, only public accounts have been analysed and the accounts name were anonymized before any processing.
+Concerning the image recovery on social media, only public accounts have been analysed and no potential private information were used, saved or revealed during the whole process.
 Concerning the time series, all the trends names have been anonymized and only macro information such as the geolocalisation, the type of cloth and the gender are revealed publicly.\\

### 2023-05-31 tmlr_submission/hermes_paper_revision/hermes_paper.tex
update of the main text and answer to the first reviewer

@@
 We targeted 5 strategic markets for the retail industry using posts localisation: the United States, Europe, Japan, Brazil and China.
+\textcolor{orange}{With compliance of the privacy and data protection, only public accounts are used and no potential private information are used, saved or revealed during the whole process.}
 The second step consists in creating a powerful visual recognition framework to be able to detect clothes details on pictures like the type of clothing, the form, the size, the color, the texture, etc.
@@
 An overview of the dataset can be found in Table~\ref{tab:fashiondataset}.
+\textcolor{orange}{For privacy issues, all the trends names are anonymized and for each trend, only the following macro information are revealed: the geolocalisation, the gender and the cloth type.}
 
@@
 In addition, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided.
-By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
+\textcolor{orange}{We show that it is possible to represent and understand fashion through its representation on social media.
+Futhermore, with a special focus done on the behaviour of influencers, it become possible to better anticipate consumers needs and avoid massive wastes due to overstocks.} By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
 As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.

### 2023-06-01 tmlr_submission/hermes_paper_revision/hermes_paper.tex
update hermes paper regarding remarks of the second review

@@
 
+\textcolor{orange}{In this section, performance of the hybrid model are presented and compared with a rich collection of other approaches. the HERMES framework is evaluated on two different use cases:
+\begin{itemize}
+	\item a first application is proposed on the Fashion dataset.
+The HERMES model is trained at forecasting the fashion time series one year ahead (h=52).
+This use case is mostly guided by the fashion and retail industry where clothes collection are usually prepared one year or more in advance.
+As additionals signals representing influencers behaviours are available, a focus is also done on the capability of the HERMES approach to leverage these weak signals.
+	\item A second application is proposed on the weekly dataset of the m4 competition \citep{makridakis2018}.
+This use case is completely different from the previous one.
+based on the competition's rules, the forecasting horizon is set to 13 an no external signals are available.
+Futhermore, the proposed times series come from different sectors, have variable lengths and show contrasting behaviours.
+\end{itemize}
+}
+
 \subsection{Training}
@@
 As an illustration, an example of our split is shown in Figure~\ref{fig:train_eval_test_set}.
+\textcolor{orange}{Looking at this figure, we can note that fashion time series have just enough historical data to perform the proposed train/eval/test split.
+Therefore, the common solution of applying a rolling window to increase the different splits can't be used of the Fashion dataset.
+At the end, only one couple input/output is provided for each split per time series.}
 
@@
 \begin{table}
-  \caption{Results summary on the 10000ts Fashion dataset.
+  \caption{Results summary on the 10000 time series of the Fashion dataset.
 For each metric, the average on all our time series is computed.
@@
 \begin{table}
-  \caption{Results summary on the 1000 time series and 100 time series Fashion dataset.
+  \caption{Results summary on 1000 time series and 100 time series of the Fashion dataset.
 The MASE average on all the time series is computed.
 For the two approaches using a neural network, 10 models with different seeds are trained.
-the mean and the standard deviation of the 10 results are displayed.}
- \centering
- \resizebox{0.8\textwidth}{!}{ 
-  \begin{tabular}{l||llll}
-    \multicolumn{4}{c}{1000 time series Fashion dataset}\vspace{0.5cm} \\
-    &&\multicolumn{2}{c}{\textbf{MASE}} \\
-    &&  \textit{mean}  & \textit{std}  \\
-	 \hline
-	 &&& \\
-     \textit{snaive} && 0.871 & - \\
-     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.837} & \textcolor{orange}{-} \\
-     \textit{arima} && 0.821 & - \\
-     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.801} & \textcolor{orange}{-} \\
-     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.788} & \textcolor{orange}{-} \\
-     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.768} & \textcolor{orange}{0.005} \\
-     \textit{stlm} && 0.765 & - \\
-     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.764} & \textcolor{orange}{0.004} \\
-     \textit{lstm} && 0.740 & 0.007 \\
-     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.738} & \textcolor{orange}{0.017} \\
-     \textit{tbats} && 0.734 & - \\
-     \textbf{\textit{hermes-tbats}} && \textbf{0.719} & 0.002 \\
+the mean and the standard deviation of the 10 results are displayed.\vspace{0.5cm}}
+ \centering
+ \resizebox{1.\textwidth}{!}{ 
+ \begin{tabular}{l||lllll|lllll}
+   \multicolumn{11}{c}{1000 time series Fashion dataset}\vspace{0.5cm}\\
+   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
+   &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
+	 \hline
+	 &&&&&&&&&&\\
+     \textit{snaive} && 0.871 && - &&& \textcolor{orange}{0.383} && \textcolor{orange}{-} &\\
+     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.837} && \textcolor{orange}{-} &&& \textcolor{orange}{0.484} && \textcolor{orange}{-} &\\
+     \textit{arima} && 0.821 && - &&& \textcolor{orange}{0.472} && \textcolor{orange}{-} &\\
+     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.801} && \textcolor{orange}{-} &&& \textcolor{orange}{0.469} && \textcolor{orange}{-} &\\
+     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.788} && \textcolor{orange}{-} &&& \textcolor{orange}{0.476} && \textcolor{orange}{-} &\\
+     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.767} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.482} && \textcolor{orange}{0.009} &\\
+     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.476} && \textcolor{orange}{0.009} &\\
+      \textcolor{orange}{\textit{hermes-ets-ws}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.507}} && \textcolor{orange}{0.013} &\\
+     \textit{stlm} && 0.765 && - &&& \textcolor{orange}{0.493} && \textcolor{orange}{-} &\\
+     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.763} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.501} && \textcolor{orange}{0.009} &\\
+     \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.740} && \textcolor{orange}{0.007} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
+     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.738} && \textcolor{orange}{0.017} &&& \textcolor{orange}{0.465} && \textcolor{orange}{0.013} &\\
+     \textit{tbats} && 0.734 && - &&& \textcolor{orange}{0.466} && \textcolor{orange}{-} &\\
+     \textcolor{orange}{\textit{lstm-ws}} && \textcolor{orange}{0.731} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.492} && \textcolor{orange}{0.012} &\\
+     \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.721} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
+     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws}}} && \textcolor{orange}{0.717} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.500} && \textcolor{orange}{0.010} &\\
+
   \end{tabular}\hspace{1cm}
@@
 
-  \begin{tabular}{l||llll}
-   \multicolumn{4}{c}{100 ts Fashion dataset}\vspace{0.5cm} \\
-   &&\multicolumn{2}{c}{\textbf{MASE}} \\
-    &&  \textit{mean}  & \textit{std}  \\
-	\hline
-	 &&& \\
-     \textit{snaive} && 0.876 & - \\
-     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.822} & \textcolor{orange}{-} \\
-     \textit{arima} && 0.814 & - \\
-     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.808} & \textcolor{orange}{0.006} \\
-     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.804} & \textcolor{orange}{0.024} \\
-     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.792} & \textcolor{orange}{0.003} \\
-     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.786} & \textcolor{orange}{-} \\
-     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.767} & \textcolor{orange}{-} \\
-     \textit{lstm} && 0.767 & 0.045 \\
-     \textit{stlm} && 0.742 & - \\
-     \textit{tbats} && 0.745 & - \\
-     \textbf{\textit{hermes-tbats}} && \textbf{0.739} & 0.003 \\
+  \begin{tabular}{l||lllll|lllll}
+   \multicolumn{11}{c}{100 time series Fashion dataset}\vspace{0.5cm}\\
+   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
+   &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
+	 \hline
+	 &&&&&&&&&&\\
+     \textit{snaive} && 0.876 && - &&& \textcolor{orange}{0.330} && \textcolor{orange}{-} &\\
+     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.822} && \textcolor{orange}{-} &&& \textcolor{orange}{0.470} && \textcolor{orange}{-} &\\
+     \textit{arima} && 0.814 && - &&& \textcolor{orange}{0.400} && \textcolor{orange}{-} &\\
+     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.812} && \textcolor{orange}{0.009} &&& \textcolor{orange}{0.446} && \textcolor{orange}{0.031} &\\
+     \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.015} &&& \textcolor{orange}{0.446} && \textcolor{orange}{0.049} &\\
+     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.008} &&& \textcolor{orange}{0.479} && \textcolor{orange}{0.024} &\\
+     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.804} && \textcolor{orange}{0.024} &&& \textcolor{orange}{0.393} && \textcolor{orange}{0.029} &\\
+     \textcolor{orange}{\textit{hermes-ets-ws}} && \textcolor{orange}{0.792} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.386} && \textcolor{orange}{0.010} &\\
+     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.790} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.374} && \textcolor{orange}{0.005} &\\
+     \textcolor{orange}{\textit{lstm-ws}} && \textcolor{orange}{0.789} && \textcolor{orange}{0.010} &&& \textcolor{orange}{0.485} && \textcolor{orange}{0.036} &\\
+     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.400} && \textcolor{orange}{-} &\\
+     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.767} && \textcolor{orange}{-} &&& \textcolor{orange}{\textbf{0.490}} && \textcolor{orange}{-} &\\
+     \textit{tbats} && 0.745 && - &&& \textcolor{orange}{0.440} && \textcolor{orange}{-} &\\
+     \textit{stlm} && 0.742 && - &&& \textcolor{orange}{0.450} && \textcolor{orange}{-} &\\
+     \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.741} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.462} && \textcolor{orange}{0.021} &\\
+     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws}}} && \textcolor{orange}{\textbf{0.737}} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.486} && \textcolor{orange}{0.027} &\\
   \end{tabular}
@@
 The Adam optimizer is used and the MASE is directly used as the loss function.
-Finally a rolling window is applied on the train set so as to increase the number of examples and improve the training process.
-The number of slinding windows, the learning rate, the batch size, the RNN architecture and input size are set using a grid search and detailled in \ref{sec:m4gridsearch}.
+\textcolor{gray}{Finally a rolling window is applied on the train set so as to increase the number of examples and improve the training process.} \textcolor{orange}{As some of the m4 weekly time series have many years of historical data, a rolling window is finally applied on the train set so as to increase the number of examples and improve the training process.} The number of slinding windows, the learning rate, the batch size, the RNN architecture and input size are set using a grid search and detailled in \ref{sec:m4gridsearch}.
 

### 2023-06-01 tmlr_submission/hermes_paper_revision/answers_reviewer_2.tex
add answers_reviewer_2.tex

\documentclass[10pt]{article} % For LaTeX2e
\usepackage{tmlr}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{tmlr}
% To de-anonymize and remove mentions to TMLR (for example for posting to preprint servers), instead use the following:
%\usepackage[preprint]{tmlr}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{amssymb,amsmath,amsthm}
\usepackage[pdftex]{graphicx}

\title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}

% Authors must not appear in the submitted version. They should be hidden
% as long as the tmlr package is used without the [accepted] or [preprint] options.
% Non-anonymous submissions will be rejected without review.

\author{\name \'Etienne David \email etienne.david@heuritech.com \\
      \addr SAMOVAR, Télécom SudParis,\\
      Institut Polytechnique de Paris, 91120 Palaiseau, France
      \AND
      \name Jean Bellot \email jean.bellot@heuritech.com \\
      \addr Heuritech, \\
      6 Rue de Braque, 75003 Paris
      \AND
      \name Sylvain Le Corff \email sylvain.lecorff@gmail.com\\
      \addr LPSM, \\
      Sorbonne Université, UMR CNRS 8001, 75005, Paris
      }

% The \author macro works with any number of authors. Use \AND 
% to separate the names and addresses of multiple authors.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\def\month{01}  % Insert correct month for camera-ready version
\def\year{2023} % Insert correct year for camera-ready version
\def\openreview{\url{https://openreview.net/forum?id=XXXX}} % Insert correct link to OpenReview for camera-ready version

\begin{document}

\maketitle

We would like to thank the reviewer for his appreciation of the paper and his constructive feedback. We have carefully considered all the listed comments and we will proposed a revision of the paper accordingly when all the reviews will be published. In the meantime, you can find below detailed responses to the reviewer's remarks and an overview of some of the  modifications that will be added in the revision of the manuscript.

\section*{Detailed responses}

\subsection*{Requested changes:}
\begin{itemize}
	\item {\em ``The evaluation would be more complete if performance for model trained with weak signals is reported for smaller subsets of data. Also the classification performance should be reported for smaller datasets.''} \medskip

	\textbf{Author response:} We thank the referee for this remark. In fact, only results for method without weak signals were presented on the smaller datasets in Table 4. The original idea was to illustrate that the proposed hybrid framework seems to be a better solution on small datasets than methods only using neural networks. However, we agree with the referee and for completeness, all the models and metrics presented on the whole Fashion dataset are now also presented in Table 4. As an illustration, Table~\ref{tab:1000metricresults} presents the new version of the Table 4 of the revised paper.\\

	\item {\em ``The authors should also consider reporting results for multiple temporal splits of data''} \medskip

	\textbf{Author response:} We totally understand the expectations of the referee with this remark. As the Fashion time series only have 5 years of historical data, Figure 6 illustrates that we have just enough historical data for the proposed split train/eval/test. It is then difficult to propose different splits (using rolling windows for instance) unless the forecast horizon is reduced. However, this option is not really relevant as clothes collection are usually prepared one year or more in advance in the fashion industry. In order to evaluate the HERMES model on a different forecasting task, we propose the second application on the M4 dataset where the horizon is set to 13, the eval set is reduced and a moving window is applied on the training part of the time series to increase the size of the trainng set. Several sentences and an introductive paragraphe have been added in the experimental section to bring more clarity on this point and highlight the difference between the Fashion application case and the M4's one.\\

	\item {\em ``It seems that there is no concept of trend birth and death in the proposed dataset. It would be nice if the authors can clarify if that is true and why is that the case
.''} \medskip

	\textbf{Author response:} We agree with the referee for this remark and we acknowledge that we did not proposed a clear exploration of this concept in the proposed work. Detecting trend birth and death is one of the main challenge of the fashion industry nowaday. Thus, an aim of this work is to illustrate that analysing social media and influencers seems to be a promising way to tackle this issue. To clarify this point, a new part in the appendix has been added where 4 sub-sample of the Fashion dataset are built and forecasted separately. One of them is  called \textit{disrupting} time series and gathers the most difficult sequences to forecast: the fashion trends that burst or collapse on the last year of data. On this particular group, we show that methods using the influencers external signal reach the highest accuracy and largely outperforms the other approaches. Table~\ref{tab:fashionsubsample} presents these results and will be added in the revised version of the paper.\\		
\end{itemize}

\begin{table}
  \caption{Results summary on 1000 time series and 100 time series of the Fashion dataset. The MASE average on all the time series is computed. For the two approaches using a neural network, 10 models with different seeds are trained. the mean and the standard deviation of the 10 results are displayed.\vspace{0.5cm}}
 \centering
 \resizebox{1.\textwidth}{!}{ 
 \begin{tabular}{l||lllll|lllll}
   \multicolumn{11}{c}{1000 time series Fashion dataset}\vspace{0.5cm}\\
   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
   &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.871 && - &&& \textcolor{orange}{0.383} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.837} && \textcolor{orange}{-} &&& \textcolor{orange}{0.484} && \textcolor{orange}{-} &\\
     \textit{arima} && 0.821 && - &&& \textcolor{orange}{0.472} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.801} && \textcolor{orange}{-} &&& \textcolor{orange}{0.469} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.788} && \textcolor{orange}{-} &&& \textcolor{orange}{0.476} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.767} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.482} && \textcolor{orange}{0.009} &\\
     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.476} && \textcolor{orange}{0.009} &\\
      \textcolor{orange}{\textit{hermes-ets-ws}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.507}} && \textcolor{orange}{0.013} &\\
     \textit{stlm} && 0.765 && - &&& \textcolor{orange}{0.493} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.763} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.501} && \textcolor{orange}{0.009} &\\
     \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.740} && \textcolor{orange}{0.007} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.738} && \textcolor{orange}{0.017} &&& \textcolor{orange}{0.465} && \textcolor{orange}{0.013} &\\
     \textit{tbats} && 0.734 && - &&& \textcolor{orange}{0.466} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{lstm-ws}} && \textcolor{orange}{0.731} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.492} && \textcolor{orange}{0.012} &\\
     \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.721} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws}}} && \textcolor{orange}{0.717} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.500} && \textcolor{orange}{0.010} &\\

  \end{tabular}\hspace{1cm}
\vspace{.2cm}

  \begin{tabular}{l||lllll|lllll}
   \multicolumn{11}{c}{100 time series Fashion dataset}\vspace{0.5cm}\\
   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
   &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.876 && - &&& \textcolor{orange}{0.330} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.822} && \textcolor{orange}{-} &&& \textcolor{orange}{0.470} && \textcolor{orange}{-} &\\
     \textit{arima} && 0.814 && - &&& \textcolor{orange}{0.400} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.812} && \textcolor{orange}{0.009} &&& \textcolor{orange}{0.446} && \textcolor{orange}{0.031} &\\
     \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.015} &&& \textcolor{orange}{0.446} && \textcolor{orange}{0.049} &\\
     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.008} &&& \textcolor{orange}{0.479} && \textcolor{orange}{0.024} &\\
     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.804} && \textcolor{orange}{0.024} &&& \textcolor{orange}{0.393} && \textcolor{orange}{0.029} &\\
     \textcolor{orange}{\textit{hermes-ets-ws}} && \textcolor{orange}{0.792} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.386} && \textcolor{orange}{0.010} &\\
     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.790} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.374} && \textcolor{orange}{0.005} &\\
     \textcolor{orange}{\textit{lstm-ws}} && \textcolor{orange}{0.789} && \textcolor{orange}{0.010} &&& \textcolor{orange}{0.485} && \textcolor{orange}{0.036} &\\
     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.400} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.767} && \textcolor{orange}{-} &&& \textcolor{orange}{\textbf{0.490}} && \textcolor{orange}{-} &\\
     \textit{tbats} && 0.745 && - &&& \textcolor{orange}{0.440} && \textcolor{orange}{-} &\\
     \textit{stlm} && 0.742 && - &&& \textcolor{orange}{0.450} && \textcolor{orange}{-} &\\
     \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.741} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.462} && \textcolor{orange}{0.021} &\\
     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws}}} && \textcolor{orange}{\textbf{0.737}} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.486} && \textcolor{orange}{0.027} &\\
  \end{tabular}
 }
\label{tab:1000metricresults}
\end{table}

\begin{table}
  \caption{Results summary on a sub-sample of Fashion time series named \textit{disrupting} time series.}\vspace{0.5cm} 
 \centering
 \resizebox{0.5\textwidth}{!}{
  \begin{tabular}{l||llll}
    \multicolumn{4}{c}{\textit{disrupting} time series}\\
    &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
	 \hline
	 &&& \\
     \textit{snaive} && 1.455 & -\\ 
	 \textit{thetam} && 1.314 & -\\ 
	 \textit{ets} && 1.27 & -\\ 
	 \textit{arima} && 1.256 & -\\ 
	 \textit{tbats} && 1.229 & -\\ 
	 \textit{hermes-thetam} && 1.209 & 0.005\\ 
	 \textit{hermes-ets} && 1.202 & 0.007\\ 
	 \textit{stlm} && 1.198 & -\\ 
	 \textit{hermes-tbats} && 1.195 & 0.01\\ 
	 \textit{prophet} && 1.193 & -\\ 
	 \textit{deepar} && 1.18 & 0.03\\ 
	 \textit{lstm} && 1.15 & 0.01\\ 
	 \textit{hermes-thetam-ws} && 1.145 & 0.019\\ 
	 \textit{hermes-ets-ws} && 1.131 & 0.024\\ 
	 \textit{hermes-tbats-ws} && 1.092 & 0.007\\ 
	 \textit{lstm-ws} && 1.086 & 0.009\\  \vspace{0.5cm}\\
  \end{tabular}\hspace{1cm}
  }
 \label{tab:fashionsubsample}
\end{table}

\subsection*{Broader Impact Concerns:}
\begin{itemize}
	\item {\em `The work releases a new dataset in the public domain, which is derived from social media activity of a large number of user across multiple regions. It would be in order if the authors clarify whether due to the data collection or the release of the fashion dataset, there will be any implications for individuals' privacy whose data were utilized for this work.`''} \medskip

	\textbf{Author response:} We thank the referee for this remark and several information concerning this issue have been added in Section 2. The whole creation of the dataset respects the privacy and data protection regulations, including the General Data Protection Regulation. Concerning the image recovery on social media, only public accounts have been analysed and no potential private information were used, saved or revealed during the whole process. Concerning the time series, all the trends names have been anonymized and only macro information such as the geolocalisation, the type of cloth and the gender are revealed publicly. \\		
\end{itemize}

\end{document}

### 2023-06-05 tmlr_submission/hermes_paper_revision/answers_reviewer_1.tex
Update answers_reviewer_1.tex

--- 2023-05-30 tmlr_submission/hermes_paper_revision/answers_reviewer_1.tex
@@
 
-We would like to thank the reviewer for his appreciation of the paper and his constructive feedback.
-We have carefully considered all the listed comments and we will propose a revision of the paper accordingly when all the reviews will be published.
-In the meantime, you can find below detailed responses to the reviewer's remarks and an overview of some of the  modifications that will be added in the revision of the manuscript.
+We would like to thank the reviewer for the appreciation of the paper and the constructive feedback.
+We have carefully considered all comments and we will propose a revision of the paper accordingly when all reviews will be published.
+In the meantime, you can find below detailed responses and an overview of some of the  modifications that will be added in the revised manuscript.
 
@@
 
-	\textbf{Author response:} We thank the referee for this remark and we acknowledge that we did not discuss enough about the choice of per-time-series models in the proposed paper.
-This comment has led to additional justifications and discussions to bring more clarity on this point.
-We highlight the major parameters that can guide this choice and show that the main limitation for this choice is the computational time of the per-time-series models.
-In addition, in the experiment section, a third HERMES variation is added using the Thetam approach as the per-times-series model.
+	\textbf{Author response:} We thank the referee for this remark and we acknowledge that we did not discuss enough the choice of per-time-series models in the paper.
+This comment has led to additional justifications and discussions, in particular we discuss the use of state space models.
+We highlight that the main limitation for this choice is the computational time required to train the per-time-series models.
+In addition, in the experiment section, a third HERMES variation is added using Thetam as the per-times-series model.
 Table~\ref{tab:metricresults} presents the new version of Table 2 of the paper with the new HERMES candidate that we call \textit{hermes-thetam}.
 Changes between the old and the new version are written in orange.
-With three HERMES approaches using different per-time-series models, we want to highlight that numerous statistical approaches can be included in the proposed hybrid framework and that this choice impacts the final behaviour of the model.\\
+We believe that the three HERMES approaches using different per-time-series models highlight the flexibility of the hybrid framework.\\
 
@@
 	\textbf{Author response:} We thank the referee for this remark.
-Indeed, The choice of the per-time-series model is really important in the proposed hybrid framework and it has to be done attentively.
-A main limitation in this choice is the computational time of the per-time-series models to be correctly fitted.
-For instance, training a HMM with the EM algorithm on thousands of time series would take days of computation.
-The same conclusion can be done with the ARIMA approach.
-Too many parameters have to be fitted and even with multiprocessing, we found that this method is too expensive to be trained on a large dataset such as the fashion dataset.
-Concerning TBATS, Exponential smoothing and Thetam, correctly fitting them with existing Python packages is possible in an acceptable time, from a few minutes for exponential smoothing models to a couple of hours for TBATS.
-To clarify this point in the paper, several justifications and comments are added in the text.\\
+The main limitation is the computational time required to train these models, as the dataset contains thousands of time series.
+For instance, training a HMM with the EM algorithm, or training ARIMA on thousands of time series would increase significantly the computational cost.
+Concerning TBATS, Exponential smoothing and Thetam, correctly fitting them with existing Python packages is possible in an reasonable time, from a few minutes for exponential smoothing models to a couple of hours for TBATS.
+We believe that our experiment section, in particular with the additional simulations, highlights the flexibility of the hybrid approach and the numerical results motivate the use of TBATS eventhough other models could be used.
+To clarify this point in the paper, several justifications and comments were added in the text.\\
 
@@
 
-	\textbf{Author response:} We agree with this suggestion and this comment has led to the addition of 2 new methods in the pool of benchmark.
-First, the Prophet method introduced in \citet{Taylor2017} is trained and evaluated on the fashion dataset using the Python package bearing the same name \texttt{prophet}.
-We show that its results are not at the level of the hybrid one on the whole fashion dataset, but it starts to show a relevant accuracy level on the use case where only 100 time series are accessible.
-Secondly, the recent and powerful DeepAR method introduced in \citet{salinas2020} is added  and trained with the Python package \texttt{Gluonts} \citep{Alexandrov2020}.
+	\textbf{Author response:} We agree with this suggestion and this comment has led to the addition of 2 new methods as benchmarks.
+First, the Prophet method introduced in \citet{Taylor2017} is trained and evaluated on the fashion dataset using the Python package  \texttt{prophet}.
+We show that it leads to poor results in comparison to our model on the whole fashion dataset, and a comparable accuracy on the use case where only 100 time series are accessible.
+Secondly, the recent DeepAR method introduced in \citet{salinas2020} is added  and trained with the Python package \texttt{Gluonts} \citep{Alexandrov2020}.
 This method shows striking results on the fashion dataset and is a strong competitor of the proposed hybrid approach.
@@
 
-	\textbf{Author response:} We thank the referee for this remark that leads to a new part in the appendix where 4 sub-sample of the Fashion dataset are built and forecasted separately.
+	\textbf{Author response:} We thank the referee for this remark that led to a new part in the appendix where 4 sub-samples of the Fashion dataset are built and forecasted separately.
 The first one called \textit{disrupting} time series gathers the most difficult sequences to forecast.
 The second one called \textit{stable} time series defines a sample of fashion time series that are stable from a year to another.
-The third one called \textit{seasonal} time series gathers sequences showing a strong seasonality.
+The third one called \textit{seasonal} time series gathers sequences with a huge sasonality.
 Finally, the last group represents the most sporadic and noisy time series of the fashion time series.
-Looking at the predictions of each model on these sub-sample, interesting results can be noted and a deeper analysis of the hybrid approach, the fashion dataset and the interest of the external signal is provided.
+We added the predictions of each model on these sub-samples and extended the analysis of the hybrid approach, the fashion dataset and the use of external signals.
 Table~\ref{tab:fashionsubsample} shows the results of each method on the 4 sub-samples and it will be added in appendix as well as a section describing more precisely how the 4 samples are built.\\
@@
 	\item {\em ``The paper should discuss the potential positive and negative impacts of the proposed model and dataset on the society and the environment.''} \medskip
-	\textbf{Author response:} \\
+
+	\textbf{Author response:} We agree with the suggestion of the referee and this point is now developed in the discussion section.
+We discuss the impact of training deep architectures and the computational cost of the proposed approach.
+However,we highlight that the aim of this work is to show that it is possible to better forecast and anticipate consumers behaviours in the retail and fashion industry.
+With a better anticipation of consumer needs, companies could better adjust their production, reduce massive wastes due to their overstocks and finally offset the environmental cost of this work.
+\\
 
 	\item {\em ``The paper should address the privacy and consent issues of using social media images and data to construct the fashion dataset and the weak signals.''} \medskip
-	\textbf{Author response:} \\
+
+	\textbf{Author response:} We thank the referee for this remark and several information concerning this issue were added in Section 2.
+The whole creation of the dataset respects the privacy and data protection regulations, including the General Data Protection Regulation.
+Concerning the image recovery on social media, only public accounts have been analysed and no potential private information were used, saved or revealed during the whole process.
+Concerning the time series, all the trends names have been anonymized and only macro information such as the geolocalisation, the type of cloth and the gender are revealed publicly.
+\\
 
 	\item {\em ``The paper should explain how the data is collected, processed, and anonymized, and what are the ethical and legal implications of this process.''} \medskip
-	\textbf{Author response:} \\
+
+	\textbf{Author response:} We agree with the referee and  details were added  in  Section 2. \\
 
 	\item {\em ``The paper should also acknowledge the potential risks or biases of using social media data to represent fashion trends, such as cultural diversity, inclusivity, or sustainability.''} \medskip
-	\textbf{Author response:} \\	
+
+	\textbf{Author response:} We totally agree with the referee.
+First of all, an important part of this work was to design a correct normalization process to remove the most visible biases brought by social media.
+Then, by proposing time series splitted by geo zone, we have tried to propose an accurate representation of the diversity of behaviours that exists in each region.
+We acknowledge that the proposed geozones may seem large.
+A future work could be to built trends at country level.
+Finally, by proposing a global model to forecast all the fashion trends, it is possible that rare patterns may not be correctly learned by the proposed framework.
+A future relevant work would be to learn models with latent states and an unsupervised learning.
 \end{itemize}

### 2023-06-05 tmlr_submission/hermes_paper_revision/answers_reviewer_2.tex
Update answers_reviewer_2.tex

@@
 
-We would like to thank the reviewer for his appreciation of the paper and his constructive feedback.
-We have carefully considered all the listed comments and we will proposed a revision of the paper accordingly when all the reviews will be published.
-In the meantime, you can find below detailed responses to the reviewer's remarks and an overview of some of the  modifications that will be added in the revision of the manuscript.
+We would like to thank the reviewer for the appreciation of the paper and the constructive feedback.
+We have carefully considered all comments and we will propose a revision of the paper accordingly when all reviews will be published.
+In the meantime, you can find below detailed responses and an overview of some of the  modifications that will be added in the revised manuscript.
 
@@
 	\textbf{Author response:} We thank the referee for this remark.
-In fact, only results for method without weak signals were presented on the smaller datasets in Table 4.
+In fact, only results for methods without weak signals were presented on the smaller datasets in Table 4.
 The original idea was to illustrate that the proposed hybrid framework seems to be a better solution on small datasets than methods only using neural networks.
@@
 
-	\textbf{Author response:} We totally understand the expectations of the referee with this remark.
+	\textbf{Author response:} We understand this remark.
 As the Fashion time series only have 5 years of historical data, Figure 6 illustrates that we have just enough historical data for the proposed split train/eval/test.
@@
 However, this option is not really relevant as clothes collection are usually prepared one year or more in advance in the fashion industry.
+
 In order to evaluate the HERMES model on a different forecasting task, we propose the second application on the M4 dataset where the horizon is set to 13, the eval set is reduced and a moving window is applied on the training part of the time series to increase the size of the trainng set.
-Several sentences and an introductive paragraphe have been added in the experimental section to bring more clarity on this point and highlight the difference between the Fashion application case and the M4's one.\\
+A paragraph was added in the experiment section to clarify this point and highlight the difference between the Fashion application case and the M4's one.\\
 
@@
 
-	\textbf{Author response:} We agree with the referee for this remark and we acknowledge that we did not proposed a clear exploration of this concept in the proposed work.
-Detecting trend birth and death is one of the main challenge of the fashion industry nowaday.
+	\textbf{Author response:} We agree with the referee.
+Detecting trend birth and death is one of the main challenge of the fashion industry.
 Thus, an aim of this work is to illustrate that analysing social media and influencers seems to be a promising way to tackle this issue.
-To clarify this point, a new part in the appendix has been added where 4 sub-sample of the Fashion dataset are built and forecasted separately.
+To clarify this point, a new part in the appendix was added where 4 sub-samples of the Fashion dataset are built and forecasted separately.
 One of them is  called \textit{disrupting} time series and gathers the most difficult sequences to forecast: the fashion trends that burst or collapse on the last year of data.
@@
 
-	\textbf{Author response:} We thank the referee for this remark and several information concerning this issue have been added in Section 2.
-The whole creation of the dataset respects the privacy and data protection regulations, including the General Data Protection Regulation.
+	\textbf{Author response:} We thank the referee for this remark and several information concerning this issue were added in Section 2.
+The whole design of the dataset respects the privacy and data protection regulations, including the General Data Protection Regulation.
 Concerning the image recovery on social media, only public accounts have been analysed and no potential private information were used, saved or revealed during the whole process.

### 2023-06-06 tmlr_submission/hermes_paper_revision/answers_reviewer_1.tex
update answers revierwer

@@
 	\textbf{Author response:} We thank the referee for this remark that led to a new part in the appendix where 4 sub-samples of the Fashion dataset are built and forecasted separately.
-The first one called \textit{disrupting} time series gathers the most difficult sequences to forecast.
-The second one called \textit{stable} time series defines a sample of fashion time series that are stable from a year to another.
-The third one called \textit{seasonal} time series gathers sequences with a huge sasonality.
-Finally, the last group represents the most sporadic and noisy time series of the fashion time series.
+Their are defined as follows:
+\begin{itemize}
+	\item \textbf{disrupting time series}: In retail and fashion industries, a strategic issue is to correctly anticipate new trends that will burst or collapse in the next weeks, months or years.
+To detect these sub sample of trends in the Fashion dataset, the following approach is proposed: Using the \textit{snaive} model, a prediction of the last year and its linked MASE is computed for each trend.
+Finally, the dirsupting time series are the 1000 time series with the highest MASE.
+	\item \textbf{stable time series}: By contrast, a group a stable trend a presented.
+To define them, the same methodology as the previous group is used.
+We define them as the time series where the \textit{snaive} prediction reachs the lowest MASE.
+	\item \textbf{seasonal time series}: Another relevant group of time series is sequences showing a strong seasonal patern.
+So as to detect them, we compute for each trend the seasonality strength metric introduced in \citet{wang2006}.
+The seasonal time series group is the 1000 fashion time series with highest seasonality strength.
+	\item \textbf{noisy time series}: Finally, several time series of the Fashion dataset represent niche trends only worn and posted on social media by a few people.
+The average volume for these sequences is low resulting in sporadic and noisy time series difficult to forecast.
+In order to detect them, we use the seasonality and trend strenght metrics presented in \citet{wang2006}.
+For each time series, the average of these two quantities is computed and we define the time series group as the 1000 sequences with the lowest averages.
+\end{itemize}
 We added the predictions of each model on these sub-samples and extended the analysis of the hybrid approach, the fashion dataset and the use of external signals.
@@
 We discuss the impact of training deep architectures and the computational cost of the proposed approach.
-However,we highlight that the aim of this work is to show that it is possible to better forecast and anticipate consumers behaviours in the retail and fashion industry.
+However, we highlight that the aim of this work is to show that it is possible to better forecast and anticipate consumers behaviours in the retail and fashion industry.
 With a better anticipation of consumer needs, companies could better adjust their production, reduce massive wastes due to their overstocks and finally offset the environmental cost of this work.

### 2023-06-08 tmlr_submission/hermes_paper_revision/hermes_paper.tex
Update hermes_paper.tex

@@
 \textcolor{orange}{Thus, the choice of the parametric model can be adjusted depending on the nature of the time series.
-The only limitation is the computation time as we aim at forecasting thousands of time series simultaneously.
+The only limitation is the computational time as we aim at forecasting thousands of time series simultaneously.
 For instance, hidden Markov models provide a very appealing framework but inference of such models requires computationally costly iterative procedures such as Expecation Maximization-based algorithms often combined with Monte Carlo estimates of unknown expectations.
-Choosing these approaches as per-time-series predictor would considerably slow the overall training process of the hybrid model.}
+Choosing these approaches as per-time-series predictors would considerably slow the overall training process of the hybrid model.}
 
 \textcolor{orange}{In Section~\ref{sec:exp}, we introduce three declinations of the hybrid framework  using different per-time-series predictors to highlight the adaptability of our approach.
-The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020}, the second one use a method called Thetam as per-time-series predictor \citep{hyndman2020} and the last one uses a TBATS model \citep{alysha2011}.} \textcolor{gray}{In Section~\ref{sec:exp}, two versions of our framework are proposed.
+The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020}, the second one uses Thetam as per-time-series predictor \citep{hyndman2020} and the last one uses a TBATS model \citep{alysha2011}.} \textcolor{gray}{In Section~\ref{sec:exp}, two versions of our framework are proposed.
 The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020} and the second one uses a TBATS model \citep{alysha2011} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.}
@@
 
-\textcolor{orange}{In this section, performance of the hybrid model are presented and compared with a rich collection of other approaches. the HERMES framework is evaluated on two different use cases:
+\textcolor{orange}{In this section, performance of the hybrid model are presented and compared with a several other approaches. the HERMES framework is evaluated on two different use cases.
 \begin{itemize}
-	\item a first application is proposed on the Fashion dataset.
+	\item A first application is proposed on the Fashion dataset.
 The HERMES model is trained at forecasting the fashion time series one year ahead (h=52).
-This use case is mostly guided by the fashion and retail industry where clothes collection are usually prepared one year or more in advance.
-As additionals signals representing influencers behaviours are available, a focus is also done on the capability of the HERMES approach to leverage these weak signals.
-	\item A second application is proposed on the weekly dataset of the m4 competition \citep{makridakis2018}.
-This use case is completely different from the previous one.
-based on the competition's rules, the forecasting horizon is set to 13 an no external signals are available.
-Futhermore, the proposed times series come from different sectors, have variable lengths and show contrasting behaviours.
+This use case is mostly guided by the fashion and retail industry where clothes collections are usually prepared one year or more in advance.
+As additional signals representing influencers behaviours are available, this allows  to set the focus on the ability of our framework to leverage these weak signals.
+	\item A second application is proposed on the weekly dataset of the M4 competition \citep{makridakis2018}.
+Based on the competition's rules, the forecasting horizon is set to 13 and no external signals are available.
+Futhermore, the proposed times series come from different sectors and have variable lengths.
 \end{itemize}
@@
 As an illustration, an example of our split is shown in Figure~\ref{fig:train_eval_test_set}.
-\textcolor{orange}{Looking at this figure, we can note that fashion time series have just enough historical data to perform the proposed train/eval/test split.
-Therefore, the common solution of applying a rolling window to increase the different splits can't be used of the Fashion dataset.
-At the end, only one couple input/output is provided for each split per time series.}
+\textcolor{orange}{Note that we have just enough historical data to perform the proposed train/eval/test split.
+Therefore, the common solution of applying a rolling window to increase the different splits cannot be used.
+Only one couple input/output is provided for each split per time series.}
 

### 2023-06-08 tmlr_submission/hermes_paper_revision/answers_reviewer_2.tex
update answers revierwer
update RGPD answer

@@
 One of them is called \textit{disrupting} time series and gathers the most difficult sequences to forecast: the fashion trends that burst or collapse on the last year of data.
+We define them as follows: using the \textit{snaive} model, a prediction of the last year and its linked MASE is computed for each trend.
+The \textit{dirsupting} time series are the 1000 time series where the \textit{snaive} prediction reachs the highest MASE.
 On this particular group, we show that methods using the influencers external signal reach the highest accuracy and largely outperforms the other approaches.
@@
 Concerning the image recovery on social media, only public accounts have been analysed and no potential private information were used, saved or revealed during the whole process.
-Concerning the time series, all the trends names have been anonymized and only macro information such as the geolocalisation, the type of cloth and the gender are revealed publicly.
+Concerning the time series, as they represent aggregate and normalized signals, no users' personal information can be tracked down.
 \\

### 2023-06-08 tmlr_submission/hermes_paper_revision/answers_reviewer_1_tmlr_format.tex
add answers reviewer with tmlr format

--- 2023-06-05 tmlr_submission/hermes_paper_revision/answers_reviewer_1.tex
@@
 
-\title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}
-
 % Authors must not appear in the submitted version. They should be hidden
@@
 % Non-anonymous submissions will be rejected without review.
-
-\author{\name \'Etienne David \email etienne.david@heuritech.com \\
-      \addr SAMOVAR, Télécom SudParis,\\
-      Institut Polytechnique de Paris, 91120 Palaiseau, France
-      \AND
-      \name Jean Bellot \email jean.bellot@heuritech.com \\
-      \addr Heuritech, \\
-      6 Rue de Braque, 75003 Paris
-      \AND
-      \name Sylvain Le Corff \email sylvain.lecorff@gmail.com\\
-      \addr LPSM, \\
-      Sorbonne Université, UMR CNRS 8001, 75005, Paris
-      }
 
@@
 
-\maketitle
+\textcolor{orange}{j'ai coupé la réponse en trois pour pouvoir respecter la limite de 5000 mots.
+L'endroit ou je peux ecrire la réponse ne compile pas les tableaux en latex par contre, je les ai donc enlevé.
+Pareil pour les citations que j'ai écrit en dur.}
+\bigskip
+
+Response to review (first part).\vspace{0.2cm}
 
@@
 We have carefully considered all comments and we will propose a revision of the paper accordingly when all reviews will be published.
-In the meantime, you can find below detailed responses and an overview of some of the  modifications that will be added in the revised manuscript.
+In the meantime, you can find below responses to some of the remarks:
 
-\section*{Detailed responses}
-
-\subsection*{Requested changes:}
-
-\begin{itemize}
-
-	\item {\em ``The paper should provide a clear motivation or literature review for the choice of per-time-series models.''} \medskip
-
-	\textbf{Author response:} We thank the referee for this remark and we acknowledge that we did not discuss enough the choice of per-time-series models in the paper.
+- We acknowledge that we did not discuss enough the choice of per-time-series models in the paper.
 This comment has led to additional justifications and discussions, in particular we discuss the use of state space models.
@@
 In addition, in the experiment section, a third HERMES variation is added using Thetam as the per-times-series model.
-Table~\ref{tab:metricresults} presents the new version of Table 2 of the paper with the new HERMES candidate that we call \textit{hermes-thetam}.
-Changes between the old and the new version are written in orange.
-We believe that the three HERMES approaches using different per-time-series models highlight the flexibility of the hybrid framework.\\
 
-	\item {\em ``The paper should explain why exponential smoothing and TBATS are chosen as the predictors, and how they compare to other possible choices such as ARIMA or HMM.''} \medskip
-
-	\textbf{Author response:} We thank the referee for this remark.
-The main limitation is the computational time required to train these models, as the dataset contains thousands of time series.
+- Concerning the choice of per-times-series model, the main limitation is the computational time required to train these models, as the dataset contains thousands of time series.
 For instance, training a HMM with the EM algorithm, or training ARIMA on thousands of time series would increase significantly the computational cost.
@@
 We believe that our experiment section, in particular with the additional simulations, highlights the flexibility of the hybrid approach and the numerical results motivate the use of TBATS eventhough other models could be used.
-To clarify this point in the paper, several justifications and comments were added in the text.\\
+To clarify this point in the paper, several justifications and comments were added in the text.
 
-	\item {\em ``The paper should compare with more existing methods.''} \medskip
+- Your third remark has led to the addition of 2 new methods as benchmarks.
+First, the Prophet method introduced in Taylor $\&$ Letham (2017) is trained and evaluated on the fashion dataset using the Python package 'prophet'.
+We show that it leads to poor results in comparison to our model on the whole fashion dataset, and a comparable accuracy on the use case where only 100 time series are accessible.
+Secondly, the recent DeepAR method introduced in Salinas et al.
+(2020) is added  and trained with the Python package 'Gluonts' (Alexandrov et al., 2020).
+This method shows striking results on the fashion dataset and is a strong competitor of the proposed hybrid approach.
 
-	\textbf{Author response:} We agree with this suggestion and this comment has led to the addition of 2 new methods as benchmarks.
-First, the Prophet method introduced in \citet{Taylor2017} is trained and evaluated on the fashion dataset using the Python package  \texttt{prophet}.
-We show that it leads to poor results in comparison to our model on the whole fashion dataset, and a comparable accuracy on the use case where only 100 time series are accessible.
-Secondly, the recent DeepAR method introduced in \citet{salinas2020} is added  and trained with the Python package \texttt{Gluonts} \citep{Alexandrov2020}.
-This method shows striking results on the fashion dataset and is a strong competitor of the proposed hybrid approach.
-As an illustration, Table~\ref{tab:metricresults} presents the new version of the Table 2 of the paper with the two new models: Prophet and DeepAR.
-Changes between the old and the new version are written in orange.\\
+Citation:
 
-	\item {\em ``The paper should explain how HERMES handles different types of time series, such as stationary, non-stationary, seasonal, or sporadic.''} \medskip
+Alexander Alexandrov, Konstantinos Benidis, Michael Bohlke-Schneider, Valentin Flunkert, Jan Gasthaus, Tim Januschowski, Danielle C.
+Maddix, Syama Rangapuram, David Salinas, Jasper Schulz, Lorenzo Stella, Ali Caner Türkmen, and Yuyang Wang.
+GluonTS: Probabilistic and Neural Time Series Modeling in Python.
+Journal of Machine Learning Research, 21(116):1–6, 2020.
+URL http://jmlr.org/papers/v21/
+19-820.html.
 
-	\textbf{Author response:} We thank the referee for this remark that led to a new part in the appendix where 4 sub-samples of the Fashion dataset are built and forecasted separately.
-The first one called \textit{disrupting} time series gathers the most difficult sequences to forecast.
-The second one called \textit{stable} time series defines a sample of fashion time series that are stable from a year to another.
-The third one called \textit{seasonal} time series gathers sequences with a huge sasonality.
-Finally, the last group represents the most sporadic and noisy time series of the fashion time series.
+David Salinas, Valentin Flunkert, Jan Gasthaus, and Tim Januschowski.
+DeepAR: Probabilistic forecasting with autoregressive recurrent networks.
+International Journal of Forecasting, 36(3):1181–1191, 2020.
+
+Sean Taylor and Benjamin Letham. Forecasting at scale. The American Statistician, 72, 09 2017. doi:10.1080/00031305.2017.1380080.
+
+Response to review (second part).\vspace{0.2cm}
+
+- We thank the referee for the remark concerning the analysis of diffrent types of time series.
+This comment led to a new part in the appendix where 4 sub-samples of the Fashion dataset are built and forecasted separately.
+Their are defined as follows:
+	- disrupting time series: In retail and fashion industries, a strategic issue is to correctly anticipate new trends that will burst or collapse in the next weeks, months or years.
+To detect these sub sample of trends in the Fashion dataset, the following approach is proposed: Using the 'snaive' model, a prediction of the last year and its linked MASE is computed for each trend.
+Finally, the dirsupting time series are the 1000 time series with the highest MASE.
+	-stable time series: By contrast, a group a stable trend a presented.
+To define them, the same methodology as the previous group is used.
+We define them as the time series where the snaive prediction reachs the lowest MASE.
+	-seasonal time series: Another relevant group of time series is sequences showing a strong seasonal patern.
+So as to detect them, we compute for each trend the seasonality strength metric introduced in Wang et al.
+(2006).
+The seasonal time series group is the 1000 fashion time series with highest seasonality strength.
+	-noisy time series: Finally, several time series of the Fashion dataset represent niche trends only worn and posted on social media by a few people.
+The average volume for these sequences is low resulting in sporadic and noisy time series difficult to forecast.
+In order to detect them, we use the seasonality and trend strenght metrics presented in Wang et al.
+(2006).
+For each time series, the average of these two quantities is computed and we define the time series group as the 1000 sequences with the lowest averages.
 We added the predictions of each model on these sub-samples and extended the analysis of the hybrid approach, the fashion dataset and the use of external signals.
-Table~\ref{tab:fashionsubsample} shows the results of each method on the 4 sub-samples and it will be added in appendix as well as a section describing more precisely how the 4 samples are built.\\
-\end{itemize}
+A table showing the results of each method on the 4 sub-samples will be added in appendix as well as a section describing more precisely how the 4 samples are built.
 
-\begin{table}
-  \caption{Results summary on the 10000ts Fashion dataset.
-For each metric, the average on all our time series is computed.
-For approaches using neural networks, 10 models are trained with different seeds.
-The mean and the standard deviation of the 10 results are displayed.}
-  \centering
-  \begin{tabular}{l||lllll|lllll}
-   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
-    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
-	 \hline
-	 &&&&&&&&&&\\
-     \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
-     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.845} && \textcolor{orange}{-} &&& \textcolor{orange}{0.463} && \textcolor{orange}{-}\\
-     \textit{arima} && 0.826 && -&&& 0.464 && - & \\
-     \textit{ets} && 0.807 && -&&& 0.449 && - & \\
-     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.485} && \textcolor{orange}{-}\\
-     \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
-     \textit{hermes-ets-ws} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
-     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.764} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.497} && \textcolor{orange}{0.005}\\
-     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.760} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.520}} && \textcolor{orange}{0.010}\\
-     \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
-     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.752} && \textcolor{orange}{0.018} &&& \textcolor{orange}{0.459} && \textcolor{orange}{0.015}\\
-     \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
-     \textit{lstm-ws} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
-     \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
-     \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
-     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& 0.510 && 0.005 &\\
-  \end{tabular}
-\label{tab:metricresults}
-\end{table}
+Citation:
 
-\begin{table}
-  \caption{Results summary on 4 differents sub-sample of  Fashion time series: i) disrupting time series, ii) stable time series, iii) seasonal time series and iv) noisy time series.}\vspace{0.5cm} 
- \centering
- \resizebox{0.8\textwidth}{!}{
-  \begin{tabular}{l||llll}
-    \multicolumn{4}{c}{\textit{disrupting} time series}\\
-    &&\multicolumn{2}{c}{\textbf{MASE}} \\
-    &&  \textit{mean}  & \textit{std}  \\
-	 \hline
-	 &&& \\
-     \textit{snaive} && 1.455 & -\\ 
-	 \textit{thetam} && 1.314 & -\\ 
-	 \textit{ets} && 1.27 & -\\ 
-	 \textit{arima} && 1.256 & -\\ 
-	 \textit{tbats} && 1.229 & -\\ 
-	 \textit{hermes-thetam} && 1.209 & 0.005\\ 
-	 \textit{hermes-ets} && 1.202 & 0.007\\ 
-	 \textit{stlm} && 1.198 & -\\ 
-	 \textit{hermes-tbats} && 1.195 & 0.01\\ 
-	 \textit{prophet} && 1.193 & -\\ 
-	 \textit{deepar} && 1.18 & 0.03\\ 
-	 \textit{lstm} && 1.15 & 0.01\\ 
-	 \textit{hermes-thetam-ws} && 1.145 & 0.019\\ 
-	 \textit{hermes-ets-ws} && 1.131 & 0.024\\ 
-	 \textit{hermes-tbats-ws} && 1.092 & 0.007\\ 
-	 \textit{lstm-ws} && 1.086 & 0.009\\  \vspace{0.5cm}\\
-  \end{tabular}\hspace{1cm}
-  \begin{tabular}{l||llll}
-   \multicolumn{4}{c}{\textit{stable} time series}\\
-   &&\multicolumn{2}{c}{\textbf{MASE}} \\
-    &&  \textit{mean}  & \textit{std}  \\
-	\hline
-	 &&& \\
-     \textit{prophet} && 0.629 & -\\ 
-	 \textit{thetam} && 0.615 & -\\ 
-	 \textit{ets} && 0.611 & -\\ 
-	 \textit{arima} && 0.565 & -\\ 
-	 \textit{hermes-ets-ws} && 0.555 & 0.007\\ 
-	 \textit{snaive} && 0.536 & -\\  
-	 \textit{deepar} && 0.531 & 0.024\\ 
- 	 \textit{hermes-thetam-ws} && 0.522 & 0.004\\ 
-	 \textit{hermes-ets} && 0.518 & 0.002\\ 
-	 \textit{stlm} && 0.513 & -\\ 
-	 \textit{hermes-thetam} && 0.508 & 0.005\\ 
-	 \textit{tbats} && 0.501 & -\\ 
-	 \textit{lstm-ws} && 0.492 & 0.007\\ 
-	 \textit{hermes-tbats-ws} && 0.477 & 0.008\\ 
-	 \textit{lstm} && 0.47 & 0.004\\ 
-	 \textit{hermes-tbats} && 0.451 & 0.002\\  \vspace{0.5cm}\\
-  \end{tabular}
- }
- \resizebox{0.8\textwidth}{!}{ 
-  \begin{tabular}{l||llll}
-    \multicolumn{4}{c}{\textit{seasonal} time series}\\
-    &&\multicolumn{2}{c}{\textbf{MASE}} \\
-    &&  \textit{mean}  & \textit{std}  \\
-	 \hline
-	 &&& \\
-     \textit{snaive} && 0.895 & -\\ 
-	 \textit{ets} && 0.895 & -\\ 
-	 \textit{prophet} && 0.851 & -\\ 
-	 \textit{deepar} && 0.836 & 0.035\\ 
-	 \textit{lstm-ws} && 0.829 & 0.014\\ 
-	 \textit{thetam} && 0.826 & -\\ 
-	 \textit{lstm} && 0.823 & 0.013\\ 
-	 \textit{hermes-thetam} && 0.815 & 0.008\\ 
-	 \textit{tbats} && 0.81 & -\\ 
-	 \textit{hermes-ets-ws} && 0.809 & 0.01\\ 
-	 \textit{hermes-thetam-ws} && 0.808 & 0.008\\ 
-	 \textit{arima} && 0.805 & -\\ 
-	 \textit{stlm} && 0.786 & -\\ 
-	 \textit{hermes-ets} && 0.785 & 0.003\\ 
-	 \textit{hermes-tbats-ws} && 0.777 & 0.012\\ 
-	 \textit{hermes-tbats} && 0.772 & 0.003\\ 
-  \end{tabular}\hspace{1cm}
-  \begin{tabular}{l||llll}
-   \multicolumn{4}{c}{\textit{noisy} time series}\\
-   &&\multicolumn{2}{c}{\textbf{MASE}} \\
-    &&  \textit{mean}  & \textit{std}  \\
-	\hline
-	 &&& \\
-     \textit{snaive} && 0.842 & -\\ 
-	 \textit{hermes-ets-ws} && 0.739 & 0.005\\ 
-	 \textit{hermes-ets} && 0.726 & 0.002\\ 
-	 \textit{ets} && 0.721 & -\\ 
-	 \textit{thetam} && 0.717 & -\\ 
-	 \textit{stlm} && 0.715 & -\\ 
-	 \textit{prophet} && 0.698 & -\\ 
-	 \textit{arima} && 0.696 & -\\ 
-	 \textit{hermes-thetam-ws} && 0.672 & 0.003\\ 
-	 \textit{hermes-thetam} && 0.669 & 0.001\\ 
-	 \textit{deepar} && 0.661 & 0.007\\ 
-	 \textit{hermes-tbats-ws} && 0.647 & 0.006\\ 
-	 \textit{tbats} && 0.646 & -\\ 
-	 \textit{hermes-tbats} && 0.644 & 0.003\\ 
-	 \textit{lstm-ws} && 0.637 & 0.004\\ 
-	 \textit{lstm} && 0.636 & 0.003\\
-  \end{tabular}
- }
- \label{tab:fashionsubsample}
-\end{table}
+Xiaozhe Wang, Kate Smith, and Rob Hyndman. Characteristic-based clustering for time series data. Data mining and knowledge Discovery, 13:335–364, 2006.
 
-\subsection*{Broader Impact Concerns:}
+Response to review (third part).\vspace{0.2cm}
 
-\begin{itemize}
-	\item {\em ``The paper should discuss the potential positive and negative impacts of the proposed model and dataset on the society and the environment.''} \medskip
+- The point concerning the impact of the proposed work on the society and environement is now developed in the discussion section.
+We discuss the impact of training deep architectures and the computational cost of the proposed approach.
+However, we highlight that the aim of this work is to show that it is possible to better forecast and anticipate consumers behaviours in the retail and fashion industry.
+With a better anticipation of consumer needs, companies could better adjust their production, reduce massive wastes due to their overstocks and finally offset the environmental cost of this work.
 
-	\textbf{Author response:} We agree with the suggestion of the referee and this point is now developed in the discussion section.
-We discuss the impact of training deep architectures and the computational cost of the proposed approach.
-However,we highlight that the aim of this work is to show that it is possible to better forecast and anticipate consumers behaviours in the retail and fashion industry.
-With a better anticipation of consumer needs, companies could better adjust their production, reduce massive wastes due to their overstocks and finally offset the environmental cost of this work.
-\\
-
-	\item {\em ``The paper should address the privacy and consent issues of using social media images and data to construct the fashion dataset and the weak signals.''} \medskip
-
-	\textbf{Author response:} We thank the referee for this remark and several information concerning this issue were added in Section 2.
+- We thank the referee for the remark pointing out privacy issues of using social media images.
+Several information concerning this issue were added in Section 2.
 The whole creation of the dataset respects the privacy and data protection regulations, including the General Data Protection Regulation.
@@
 Concerning the time series, all the trends names have been anonymized and only macro information such as the geolocalisation, the type of cloth and the gender are revealed publicly.
-\\
+Concerning the time series, as they represent aggregate and normalized signals, no users' personal information can be tracked down.
 
-	\item {\em ``The paper should explain how the data is collected, processed, and anonymized, and what are the ethical and legal implications of this process.''} \medskip
-
-	\textbf{Author response:} We agree with the referee and  details were added  in  Section 2. \\
-
-	\item {\em ``The paper should also acknowledge the potential risks or biases of using social media data to represent fashion trends, such as cultural diversity, inclusivity, or sustainability.''} \medskip
-
-	\textbf{Author response:} We totally agree with the referee.
+- Concerning the potential risks or biases of using social media data, we totally agree with the referee.
 First of all, an important part of this work was to design a correct normalization process to remove the most visible biases brought by social media.
@@
 Finally, by proposing a global model to forecast all the fashion trends, it is possible that rare patterns may not be correctly learned by the proposed framework.
-A future relevant work would be to learn models with latent states and an unsupervised learning.
-\end{itemize}
-
-\bibliography{hermes_paper}
-\bibliographystyle{tmlr}
+A future relevant work would be to learn models with latent states and an unsupervised learning
 

### 2023-06-08 tmlr_submission/hermes_paper_revision/answers_reviewer_2_tmlr_format.tex
add answers reviewer with tmlr format

--- 2023-06-08 tmlr_submission/hermes_paper_revision/answers_reviewer_2.tex
@@
 
-\maketitle
+Response to review.\vspace{0.2cm}
 
@@
 We have carefully considered all comments and we will propose a revision of the paper accordingly when all reviews will be published.
-In the meantime, you can find below detailed responses and an overview of some of the  modifications that will be added in the revised manuscript.
+In the meantime, you can find below responses to some of the remarks:
 
-\section*{Detailed responses}
-
-\subsection*{Requested changes:}
-\begin{itemize}
-	\item {\em ``The evaluation would be more complete if performance for model trained with weak signals is reported for smaller subsets of data.
-Also the classification performance should be reported for smaller datasets.''} \medskip
-
-	\textbf{Author response:} We thank the referee for this remark.
-In fact, only results for methods without weak signals were presented on the smaller datasets in Table 4.
+- In fact, only results for methods without weak signals were presented on the smaller datasets in Table 4.
 The original idea was to illustrate that the proposed hybrid framework seems to be a better solution on small datasets than methods only using neural networks.
 However, we agree with the referee and for completeness, all the models and metrics presented on the whole Fashion dataset are now also presented in Table 4.
-As an illustration, Table~\ref{tab:1000metricresults} presents the new version of the Table 4 of the revised paper.\\
 
-	\item {\em ``The authors should also consider reporting results for multiple temporal splits of data''} \medskip
-
-	\textbf{Author response:} We understand this remark.
+- We understand the remark concerning absence of results for multiple temporal splits of data.
 As the Fashion time series only have 5 years of historical data, Figure 6 illustrates that we have just enough historical data for the proposed split train/eval/test.
@@
 However, this option is not really relevant as clothes collection are usually prepared one year or more in advance in the fashion industry.
+In order to evaluate the HERMES model on a different forecasting task, we propose the second application on the M4 dataset where the horizon is set to 13, the eval set is reduced and a moving window is applied on the training part of the time series to increase the size of the trainng set.
+A paragraph was added in the experiment section to clarify this point and highlight the difference between the Fashion application case and the M4's one.
 
-In order to evaluate the HERMES model on a different forecasting task, we propose the second application on the M4 dataset where the horizon is set to 13, the eval set is reduced and a moving window is applied on the training part of the time series to increase the size of the trainng set.
-A paragraph was added in the experiment section to clarify this point and highlight the difference between the Fashion application case and the M4's one.\\
-
-	\item {\em ``It seems that there is no concept of trend birth and death in the proposed dataset. It would be nice if the authors can clarify if that is true and why is that the case
-.''} \medskip
-
-	\textbf{Author response:} We agree with the referee.
-Detecting trend birth and death is one of the main challenge of the fashion industry.
+- Detecting trend birth and death is one of the main challenge of the fashion industry.
 Thus, an aim of this work is to illustrate that analysing social media and influencers seems to be a promising way to tackle this issue.
 To clarify this point, a new part in the appendix was added where 4 sub-samples of the Fashion dataset are built and forecasted separately.
-One of them is called \textit{disrupting} time series and gathers the most difficult sequences to forecast: the fashion trends that burst or collapse on the last year of data.
-We define them as follows: using the \textit{snaive} model, a prediction of the last year and its linked MASE is computed for each trend.
-The \textit{dirsupting} time series are the 1000 time series where the \textit{snaive} prediction reachs the highest MASE.
+One of them is called 'disrupting' time series and gathers the most difficult sequences to forecast: the fashion trends that burst or collapse on the last year of data.
+We define them as follows: using the 'snaive' model, a prediction of the last year and its linked MASE is computed for each trend.
+The  'dirsupting' time series are the 1000 time series where the 'snaive' prediction reachs the highest MASE.
 On this particular group, we show that methods using the influencers external signal reach the highest accuracy and largely outperforms the other approaches.
-Table~\ref{tab:fashionsubsample} presents these results and will be added in the revised version of the paper.\\
-\end{itemize}
 
-\begin{table}
-  \caption{Results summary on 1000 time series and 100 time series of the Fashion dataset.
-The MASE average on all the time series is computed.
-For the two approaches using a neural network, 10 models with different seeds are trained.
-the mean and the standard deviation of the 10 results are displayed.\vspace{0.5cm}}
- \centering
- \resizebox{1.\textwidth}{!}{ 
- \begin{tabular}{l||lllll|lllll}
-   \multicolumn{11}{c}{1000 time series Fashion dataset}\vspace{0.5cm}\\
-   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
-   &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
-	 \hline
-	 &&&&&&&&&&\\
-     \textit{snaive} && 0.871 && - &&& \textcolor{orange}{0.383} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.837} && \textcolor{orange}{-} &&& \textcolor{orange}{0.484} && \textcolor{orange}{-} &\\
-     \textit{arima} && 0.821 && - &&& \textcolor{orange}{0.472} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.801} && \textcolor{orange}{-} &&& \textcolor{orange}{0.469} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.788} && \textcolor{orange}{-} &&& \textcolor{orange}{0.476} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.767} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.482} && \textcolor{orange}{0.009} &\\
-     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.476} && \textcolor{orange}{0.009} &\\
-      \textcolor{orange}{\textit{hermes-ets-ws}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.507}} && \textcolor{orange}{0.013} &\\
-     \textit{stlm} && 0.765 && - &&& \textcolor{orange}{0.493} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.763} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.501} && \textcolor{orange}{0.009} &\\
-     \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.740} && \textcolor{orange}{0.007} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
-     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.738} && \textcolor{orange}{0.017} &&& \textcolor{orange}{0.465} && \textcolor{orange}{0.013} &\\
-     \textit{tbats} && 0.734 && - &&& \textcolor{orange}{0.466} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{lstm-ws}} && \textcolor{orange}{0.731} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.492} && \textcolor{orange}{0.012} &\\
-     \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.721} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
-     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws}}} && \textcolor{orange}{0.717} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.500} && \textcolor{orange}{0.010} &\\
-
-  \end{tabular}\hspace{1cm}
-\vspace{.2cm}
-
-  \begin{tabular}{l||lllll|lllll}
-   \multicolumn{11}{c}{100 time series Fashion dataset}\vspace{0.5cm}\\
-   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
-   &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
-	 \hline
-	 &&&&&&&&&&\\
-     \textit{snaive} && 0.876 && - &&& \textcolor{orange}{0.330} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.822} && \textcolor{orange}{-} &&& \textcolor{orange}{0.470} && \textcolor{orange}{-} &\\
-     \textit{arima} && 0.814 && - &&& \textcolor{orange}{0.400} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.812} && \textcolor{orange}{0.009} &&& \textcolor{orange}{0.446} && \textcolor{orange}{0.031} &\\
-     \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.015} &&& \textcolor{orange}{0.446} && \textcolor{orange}{0.049} &\\
-     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.008} &&& \textcolor{orange}{0.479} && \textcolor{orange}{0.024} &\\
-     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.804} && \textcolor{orange}{0.024} &&& \textcolor{orange}{0.393} && \textcolor{orange}{0.029} &\\
-     \textcolor{orange}{\textit{hermes-ets-ws}} && \textcolor{orange}{0.792} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.386} && \textcolor{orange}{0.010} &\\
-     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.790} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.374} && \textcolor{orange}{0.005} &\\
-     \textcolor{orange}{\textit{lstm-ws}} && \textcolor{orange}{0.789} && \textcolor{orange}{0.010} &&& \textcolor{orange}{0.485} && \textcolor{orange}{0.036} &\\
-     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.400} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.767} && \textcolor{orange}{-} &&& \textcolor{orange}{\textbf{0.490}} && \textcolor{orange}{-} &\\
-     \textit{tbats} && 0.745 && - &&& \textcolor{orange}{0.440} && \textcolor{orange}{-} &\\
-     \textit{stlm} && 0.742 && - &&& \textcolor{orange}{0.450} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.741} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.462} && \textcolor{orange}{0.021} &\\
-     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws}}} && \textcolor{orange}{\textbf{0.737}} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.486} && \textcolor{orange}{0.027} &\\
-  \end{tabular}
- }
-\label{tab:1000metricresults}
-\end{table}
-
-\begin{table}
-  \caption{Results summary on a sub-sample of Fashion time series named \textit{disrupting} time series.}\vspace{0.5cm} 
- \centering
- \resizebox{0.5\textwidth}{!}{
-  \begin{tabular}{l||llll}
-    \multicolumn{4}{c}{\textit{disrupting} time series}\\
-    &&\multicolumn{2}{c}{\textbf{MASE}} \\
-    &&  \textit{mean}  & \textit{std}  \\
-	 \hline
-	 &&& \\
-     \textit{snaive} && 1.455 & -\\ 
-	 \textit{thetam} && 1.314 & -\\ 
-	 \textit{ets} && 1.27 & -\\ 
-	 \textit{arima} && 1.256 & -\\ 
-	 \textit{tbats} && 1.229 & -\\ 
-	 \textit{hermes-thetam} && 1.209 & 0.005\\ 
-	 \textit{hermes-ets} && 1.202 & 0.007\\ 
-	 \textit{stlm} && 1.198 & -\\ 
-	 \textit{hermes-tbats} && 1.195 & 0.01\\ 
-	 \textit{prophet} && 1.193 & -\\ 
-	 \textit{deepar} && 1.18 & 0.03\\ 
-	 \textit{lstm} && 1.15 & 0.01\\ 
-	 \textit{hermes-thetam-ws} && 1.145 & 0.019\\ 
-	 \textit{hermes-ets-ws} && 1.131 & 0.024\\ 
-	 \textit{hermes-tbats-ws} && 1.092 & 0.007\\ 
-	 \textit{lstm-ws} && 1.086 & 0.009\\  \vspace{0.5cm}\\
-  \end{tabular}\hspace{1cm}
-  }
- \label{tab:fashionsubsample}
-\end{table}
-
-\subsection*{Broader Impact Concerns:}
-\begin{itemize}
-	\item {\em `The work releases a new dataset in the public domain, which is derived from social media activity of a large number of user across multiple regions.
-It would be in order if the authors clarify whether due to the data collection or the release of the fashion dataset, there will be any implications for individuals' privacy whose data were utilized for this work.`''} \medskip
-
-	\textbf{Author response:} We thank the referee for this remark and several information concerning this issue were added in Section 2.
+- We thank the referee for the remark on potential privacy issues resulting from the use of social media images.
+Several information concerning these issues were added in Section 2.
 The whole design of the dataset respects the privacy and data protection regulations, including the General Data Protection Regulation.
@@
 Concerning the time series, as they represent aggregate and normalized signals, no users' personal information can be tracked down.
-\\
-\end{itemize}
 

### 2023-06-13 tmlr_submission/hermes_paper_revision/answers_reviewer_1_tmlr_format.tex
update title

@@
 
-Response to review (first part).\vspace{0.2cm}
+\textbf{Response to review (first part)}.\vspace{0.2cm}
 
@@
 
-Response to review (second part).\vspace{0.2cm}
+\textbf{Response to review (second part)}.\vspace{0.2cm}
 
@@
 
-Response to review (third part).\vspace{0.2cm}
+\textbf{Response to review (third part)}.\vspace{0.2cm}
 

### 2023-06-28 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex
add the third review

--- 2023-06-05 tmlr_submission/hermes_paper_revision/answers_reviewer_2.tex
@@
 We would like to thank the reviewer for the appreciation of the paper and the constructive feedback.
-We have carefully considered all comments and we will propose a revision of the paper accordingly when all reviews will be published.
+We have carefully considered all comments and we will propose a revision of the paper accordingly.
 In the meantime, you can find below detailed responses and an overview of some of the  modifications that will be added in the revised manuscript.
@@
 \begin{itemize}
-	\item {\em ``The evaluation would be more complete if performance for model trained with weak signals is reported for smaller subsets of data.
-Also the classification performance should be reported for smaller datasets.''} \medskip
+	\item {\em ``The reliability of the data is important for the use of this data by third parties.
+Please explain in detail how the human processing was done.
+Also, to what extent can machine failures be included in image processing?
+Do humans correct them?''} \medskip
 
-	\textbf{Author response:} We thank the referee for this remark.
-In fact, only results for methods without weak signals were presented on the smaller datasets in Table 4.
-The original idea was to illustrate that the proposed hybrid framework seems to be a better solution on small datasets than methods only using neural networks.
-However, we agree with the referee and for completeness, all the models and metrics presented on the whole Fashion dataset are now also presented in Table 4.
-As an illustration, Table~\ref{tab:1000metricresults} presents the new version of the Table 4 of the revised paper.\\
+	\textbf{Author response:} \\
 
-	\item {\em ``The authors should also consider reporting results for multiple temporal splits of data''} \medskip
+	\item {\em ``In publishing the data, it would be good to add a little more analysis of the characteristics of the data.
+For example, basic statistics for each market, statistics for the Weak signal $w^{f,i}_t$, etc.''} \medskip
 
-	\textbf{Author response:} We understand this remark.
-As the Fashion time series only have 5 years of historical data, Figure 6 illustrates that we have just enough historical data for the proposed split train/eval/test.
-It is then difficult to propose different splits (using rolling windows for instance) unless the forecast horizon is reduced.
-However, this option is not really relevant as clothes collection are usually prepared one year or more in advance in the fashion industry.
+	\textbf{Author response:} \\
 
-In order to evaluate the HERMES model on a different forecasting task, we propose the second application on the M4 dataset where the horizon is set to 13, the eval set is reduced and a moving window is applied on the training part of the time series to increase the size of the trainng set.
-A paragraph was added in the experiment section to clarify this point and highlight the difference between the Fashion application case and the M4's one.\\
+	\item {\em ``It is written that represents the index of fashion trends, but it is unclear what exactly it refers to. Does it correspond to a product/item?''} \medskip
 
-	\item {\em ``It seems that there is no concept of trend birth and death in the proposed dataset. It would be nice if the authors can clarify if that is true and why is that the case
-.''} \medskip
+	\textbf{Author response:}\\
 
-	\textbf{Author response:} We agree with the referee.
-Detecting trend birth and death is one of the main challenge of the fashion industry.
-Thus, an aim of this work is to illustrate that analysing social media and influencers seems to be a promising way to tackle this issue.
-To clarify this point, a new part in the appendix was added where 4 sub-samples of the Fashion dataset are built and forecasted separately.
-One of them is  called \textit{disrupting} time series and gathers the most difficult sequences to forecast: the fashion trends that burst or collapse on the last year of data.
-On this particular group, we show that methods using the influencers external signal reach the highest accuracy and largely outperforms the other approaches.
-Table~\ref{tab:fashionsubsample} presents these results and will be added in the revised version of the paper.\\
+	\item {\em ``I didn't know what statistic was $\hat{y}^{c,g,m}$. Could you please explain it in detail?''} \medskip
+
+	\textbf{Author response:}\\
+
+	\item {\em ``It may be a good idea to modify the structure of Section 3.
+It is better to explain the hybrid model (4) at first.
+Then, elaborate on the motivation behind the formulation of (4).
+The output of the RNN appears to represent the weights in summing $f^(.)$ and $\bar{y}^n_{T}$.
+Is that correct?
+Also, when is one of $y^{pred}$ and $y^{corr}$ more dominant than the other?
+The cost function described in Section 4.1 should be moved to Section 3.''} \medskip
+
+	\textbf{Author response:}\\
+
+	\item {\em ``It would be good to add a discussion of the limitations of this study.
+Other external factors could be various, such as advertisements.
+This study focuses on the correlation between weak signals and trends, not causality.
+This should be clearly stated.
+As seen in Figure 2, the effect of the external factor is accompanied by a time delay.
+It would be interesting to analyze how such time delays vary by fashion category and market.
+It would also be interesting to incorporate this into machine learning models.''} \medskip
+
+	\textbf{Author response:}\\
+
+	\item {\em ``In Table 2, it would be good to clarify which methods can handle weak signals and which cannot.
+Then, please clarify by experiment that it is effective to construct a hybrid model by the weighted sum of two terms as in the proposed method (4).''} \medskip
+
+	\textbf{Author response:}\\
+
+	\item {\em ``Minor issues: i)The term "causal inference" appears in the abstract, but it is not discussed in this study and should be changed to another term.
+ii) The proposed method, HERMES, does not specify what it stands for.
+iii) Please cite Figure 1 in the text.
+iv) Please change the "t" in "At each time t" in section 2.1 to italic.''} \medskip
+
+	\textbf{Author response:} \textcolor{orange}{correction faites sauf pour la remarque sur HERMES.
+Peut etre que dans la réponse on pourra dire que c'est pour Hybird ERro-corrector Model with inclusion of External Signals ...}\\
 \end{itemize}
-
-\begin{table}
-  \caption{Results summary on 1000 time series and 100 time series of the Fashion dataset.
-The MASE average on all the time series is computed.
-For the two approaches using a neural network, 10 models with different seeds are trained.
-the mean and the standard deviation of the 10 results are displayed.\vspace{0.5cm}}
- \centering
- \resizebox{1.\textwidth}{!}{ 
- \begin{tabular}{l||lllll|lllll}
-   \multicolumn{11}{c}{1000 time series Fashion dataset}\vspace{0.5cm}\\
-   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
-   &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
-	 \hline
-	 &&&&&&&&&&\\
-     \textit{snaive} && 0.871 && - &&& \textcolor{orange}{0.383} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.837} && \textcolor{orange}{-} &&& \textcolor{orange}{0.484} && \textcolor{orange}{-} &\\
-     \textit{arima} && 0.821 && - &&& \textcolor{orange}{0.472} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.801} && \textcolor{orange}{-} &&& \textcolor{orange}{0.469} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.788} && \textcolor{orange}{-} &&& \textcolor{orange}{0.476} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.767} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.482} && \textcolor{orange}{0.009} &\\
-     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.476} && \textcolor{orange}{0.009} &\\
-      \textcolor{orange}{\textit{hermes-ets-ws}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.507}} && \textcolor{orange}{0.013} &\\
-     \textit{stlm} && 0.765 && - &&& \textcolor{orange}{0.493} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.763} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.501} && \textcolor{orange}{0.009} &\\
-     \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.740} && \textcolor{orange}{0.007} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
-     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.738} && \textcolor{orange}{0.017} &&& \textcolor{orange}{0.465} && \textcolor{orange}{0.013} &\\
-     \textit{tbats} && 0.734 && - &&& \textcolor{orange}{0.466} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{lstm-ws}} && \textcolor{orange}{0.731} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.492} && \textcolor{orange}{0.012} &\\
-     \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.721} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
-     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws}}} && \textcolor{orange}{0.717} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.500} && \textcolor{orange}{0.010} &\\
-
-  \end{tabular}\hspace{1cm}
-\vspace{.2cm}
-
-  \begin{tabular}{l||lllll|lllll}
-   \multicolumn{11}{c}{100 time series Fashion dataset}\vspace{0.5cm}\\
-   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
-   &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
-	 \hline
-	 &&&&&&&&&&\\
-     \textit{snaive} && 0.876 && - &&& \textcolor{orange}{0.330} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.822} && \textcolor{orange}{-} &&& \textcolor{orange}{0.470} && \textcolor{orange}{-} &\\
-     \textit{arima} && 0.814 && - &&& \textcolor{orange}{0.400} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.812} && \textcolor{orange}{0.009} &&& \textcolor{orange}{0.446} && \textcolor{orange}{0.031} &\\
-     \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.015} &&& \textcolor{orange}{0.446} && \textcolor{orange}{0.049} &\\
-     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.008} &&& \textcolor{orange}{0.479} && \textcolor{orange}{0.024} &\\
-     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.804} && \textcolor{orange}{0.024} &&& \textcolor{orange}{0.393} && \textcolor{orange}{0.029} &\\
-     \textcolor{orange}{\textit{hermes-ets-ws}} && \textcolor{orange}{0.792} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.386} && \textcolor{orange}{0.010} &\\
-     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.790} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.374} && \textcolor{orange}{0.005} &\\
-     \textcolor{orange}{\textit{lstm-ws}} && \textcolor{orange}{0.789} && \textcolor{orange}{0.010} &&& \textcolor{orange}{0.485} && \textcolor{orange}{0.036} &\\
-     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.400} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.767} && \textcolor{orange}{-} &&& \textcolor{orange}{\textbf{0.490}} && \textcolor{orange}{-} &\\
-     \textit{tbats} && 0.745 && - &&& \textcolor{orange}{0.440} && \textcolor{orange}{-} &\\
-     \textit{stlm} && 0.742 && - &&& \textcolor{orange}{0.450} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.741} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.462} && \textcolor{orange}{0.021} &\\
-     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws}}} && \textcolor{orange}{\textbf{0.737}} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.486} && \textcolor{orange}{0.027} &\\
-  \end{tabular}
- }
-\label{tab:1000metricresults}
-\end{table}
-
-\begin{table}
-  \caption{Results summary on a sub-sample of Fashion time series named \textit{disrupting} time series.}\vspace{0.5cm} 
- \centering
- \resizebox{0.5\textwidth}{!}{
-  \begin{tabular}{l||llll}
-    \multicolumn{4}{c}{\textit{disrupting} time series}\\
-    &&\multicolumn{2}{c}{\textbf{MASE}} \\
-    &&  \textit{mean}  & \textit{std}  \\
-	 \hline
-	 &&& \\
-     \textit{snaive} && 1.455 & -\\ 
-	 \textit{thetam} && 1.314 & -\\ 
-	 \textit{ets} && 1.27 & -\\ 
-	 \textit{arima} && 1.256 & -\\ 
-	 \textit{tbats} && 1.229 & -\\ 
-	 \textit{hermes-thetam} && 1.209 & 0.005\\ 
-	 \textit{hermes-ets} && 1.202 & 0.007\\ 
-	 \textit{stlm} && 1.198 & -\\ 
-	 \textit{hermes-tbats} && 1.195 & 0.01\\ 
-	 \textit{prophet} && 1.193 & -\\ 
-	 \textit{deepar} && 1.18 & 0.03\\ 
-	 \textit{lstm} && 1.15 & 0.01\\ 
-	 \textit{hermes-thetam-ws} && 1.145 & 0.019\\ 
-	 \textit{hermes-ets-ws} && 1.131 & 0.024\\ 
-	 \textit{hermes-tbats-ws} && 1.092 & 0.007\\ 
-	 \textit{lstm-ws} && 1.086 & 0.009\\  \vspace{0.5cm}\\
-  \end{tabular}\hspace{1cm}
-  }
- \label{tab:fashionsubsample}
-\end{table}
-
-\subsection*{Broader Impact Concerns:}
-\begin{itemize}
-	\item {\em `The work releases a new dataset in the public domain, which is derived from social media activity of a large number of user across multiple regions.
-It would be in order if the authors clarify whether due to the data collection or the release of the fashion dataset, there will be any implications for individuals' privacy whose data were utilized for this work.`''} \medskip
-
-	\textbf{Author response:} We thank the referee for this remark and several information concerning this issue were added in Section 2.
-The whole design of the dataset respects the privacy and data protection regulations, including the General Data Protection Regulation.
-Concerning the image recovery on social media, only public accounts have been analysed and no potential private information were used, saved or revealed during the whole process.
-Concerning the time series, all the trends names have been anonymized and only macro information such as the geolocalisation, the type of cloth and the gender are revealed publicly.
-\\
-\end{itemize}
-
 \end{document}

### 2023-06-28 tmlr_submission/hermes_paper_revision/hermes_paper.tex
add minor remarks of reviewer 3

@@
 \begin{abstract}
-Developing models and algorithms to draw causal inference for time series is a long standing statistical problem.
+Developing models and algorithms to draw \textcolor{gray}{causal inference} \textcolor{orange}{predictions} for time series is a long standing statistical problem.
 It is crucial for many applications, in particular for fashion or retail industries, to make optimal inventory decisions and avoid massive wastes.
@@
 
+\textcolor{orange}{Social Networks have appeared as an impressive data source to follow the evolution of fashion over the time.
+Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world.
+To do it automatically for thousands of trends, the following methodology is introduced in this section and summarized in Figure~\ref{fig:pipeline}.}
+
 \begin{figure*}
@@
 
-Social media have appeared as an impressive data source to follow the evolution of fashion over the time.
+\textcolor{gray}{Social media have appeared as an impressive data source to follow the evolution of fashion over the time.
 Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world.
-To do it automatically for thousands of trends, the following methodology was introduced.
-In the first place, a complete image dataset of 150 millions pictures is collected from different social media such as Instagram or Weibo.
+To do it automatically for thousands of trends, the following methodology was introduced.} In the first place, a complete image dataset of 150 millions pictures is collected from different social media such as Instagram or Weibo.
 We targeted 5 strategic markets for the retail industry using posts localisation: the United States, Europe, Japan, Brazil and China.
-\textcolor{orange}{With compliance of the privacy and data protection, only public accounts are used and no potential private information are used, saved or revealed during the whole process.}
+\textcolor{orange}{With compliance of the privacy and data protection, only public accounts are selected and no potential private information are used, saved or revealed during the whole process.}
 The second step consists in creating a powerful visual recognition framework to be able to detect clothes details on pictures like the type of clothing, the form, the size, the color, the texture, etc.
@@
 We note $y^{c,g,m,i}$ the final raw sequence representing the fashion trend $i$ of the cloth type $c$ for the gender $g$ on market $m$.
-At each time t, $y^{c,g,m,i}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $i$ of the cloth type $c$ for the gender $g$.
-As an illustration, an example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.
+At each time $t$, $y^{c,g,m,i}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $i$ of the cloth type $c$ for the gender $g$.
+As an illustration, example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.
 
@@
 
-\textcolor{orange}{In this section, performance of the hybrid model are presented and compared with a several other approaches. the HERMES framework is evaluated on two different use cases.
+\textcolor{orange}{In this section, performance of the hybrid model are presented and compared with several other approaches. the HERMES framework is evaluated on two different use cases.
 \begin{itemize}

### 2023-06-28 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex
update answer to the reviewer 3

@@
 Please explain in detail how the human processing was done.
-Also, to what extent can machine failures be included in image processing?
-Do humans correct them?''} \medskip
+Also, to what extent can machine failures be included in image processing ?
+Do humans correct them ?''} \medskip
 
-	\textbf{Author response:} \\
+	\textbf{Author response:} We thank the referee for this remark.
+Regarding the data-acquisition pipeline presented in section 2, the human actions are limited.
+The first human processing occured during the training of the visual recognition models where manually labeled dataset are used.
+The second human processing is at the step where the fashion trends are defined.
+All the attributes detecting by the vision recognition models are not relevant for the fashion industry by themself.
+For instance the shape of a clothing' collar.
+A general collar shape is not relevant by itself but it is when it is link to a mini dress with a particular color and texture.
+These associations of fine-grain attributes are define by a team of fashion experts and are not provided with the paper.
+Concerning the machine failures, all the visual recognition used to build this paper have been trained with a standard processus implying a train, a eval and a test set.
+Thus, models showing poor performance in terms of accuracy and recall in the test set have not been used in the proposed pipeline.
+\\
 
@@
 
-	\textbf{Author response:} \\
+	\textbf{Author response:} We agree with the referee and we aknowledge that we have not enough presented the diversity of behaviours hidden in the proposed fashion dataset.
+So as to improve this point, a new section is added in appendice of the revised version of the paper where 4 differents sub-samples of time series sharing the same behaviour are studied separately.
+A \\
 
@@
 
-	\textbf{Author response:}\\
+	\textbf{Author response:} We understand this remark and a sentence has been added in the revised paper to clarify this point.
+The index of fashion trends represent the name of the fashion cloth relevant for the fashion industry.
+It can be just one attribute detected by a visaul recognition model (for instance the fashion trend "sneaker") but it can also be a combination of several attributes (for instance the A-line dress is a combination of a collar shape and a dress shape attribute).
+As the fashion trends' name are anonymized in the proposed dataset, the architecture behind the fashion trends definition is not presented in this paper.
+\\
 
@@
 
-	\textbf{Author response:}\\
+	\textbf{Author response:} We are not sure of the notation in the question of the referee, in the paper we introduce $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$ but not $\hat{y}^{c,g,m}$.
+If it is a mistake, we present bellow a explanation of the two statistic $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$
+	\begin{itemize}
+	\item $\Tilde{y}^{c,g,m}$ is the time series representing the behaviour of the global cloth type $c$ for the gender $g$ on the market $m$.
+It can be for exemple the time series representing the evolution of the general pants for female in Europe.
+The sequence $\Tilde{y}^{c,g,m}$ is then used to normalized each time series $y^{c,g,m,i}$ with the same $c$, $g$ and $m$.
+All the fashion trends of pants for female in Europe are normalized by the time series representing the general pants for female in Europe.
+	\item $\bar{y}^{c,g,m}$ is the time series $\Tilde{y}^{c,g,m}$ where the seasonality component have been removed.
+The seasonality component is removed as we only want remove the social media bias with the normalization step and not remove or change the seasonaly of the proposed fashion trends.
+	\end{itemize}
 
@@
 Then, elaborate on the motivation behind the formulation of (4).
-The output of the RNN appears to represent the weights in summing $f^(.)$ and $\bar{y}^n_{T}$.
+The output of the RNN appears to represent the weights in summing $f^n(.)$ and $\bar{y}^n_{T}$.
 Is that correct?
@@
 
-	\textbf{Author response:}\\
+	\textbf{Author response:}We tank the referee for this remark.
+In the proposed method, $\bar{y}^n_{T}$ is a scaling factor to rescaled inputs and ouputs of the Neural network  output.
+Note that $f^n(.)$ represent the parametric model learned and that is different for every time series.
+By constrast, the reccurent neural network denoted $RNN()$ in the paper is global and the same network is used for every time series.
+It is why we need to use a rescale factor as we do not assume that all the time series have the same volumne.
+The faction of the final prediction due to $y^{pred}$ or $y^{corr}$ is variable and repose on the nature of the time series (and the external signal if it is provided to the corrector).
+A good illustration of this point is presented in a new section that will be added in the appendice of the revised paper.
+In this section, we study the accuracy of the HERMES model on a sub sample of time series with a high level of noise.
+On this sub-sample, the difference of accuracy between the predictor alone and the predictor plus the corrector is null.
+The final prediction of the HERMES model relies only on $y^{pred}$ on this specific sub-sample.
+Finally, we decided to present the cost function in the Experiment section and not in the section presenting the model as the choice of the loss function can change depending of the use case.
+For the Fashion dataset, we selected the L1 loss function to train the HERMES variations based on a gridsearch.
+For the M4 dataset, the MASE has been used.
+\\
 
@@
 
-	\textbf{Author response:}\\
+	\textbf{Author response:} We thank the referee for this remark.
+In this paper, we illustrate that the use of external signals is decisive in the detection of burst of collapse of fashion trends.
+However, we acknowledge that we let a reccurent neural network entirely leverage these signals and consequently, we lost the interpretability of the impact of the external signal on the main signal.
+A future work would be to study more closely how the external signal could be in advance of the main signal.
+How many time in advance are we able to detect a trend burst based on the influencer signal, etc...\\
 
@@
 
-	\textbf{Author response:}\\
+	\textbf{Author response:} We totally agree with the referee.
+In the revised version of the paper, a stars is added in Table 2 and Table 4 to specify which methods has access to the weak signals and which has not.
+In addition, in Table 4, results of HERMES declination with and without the weak signal are added.
+Finally, so as to provide more benchmark, the Prophet method, the DeepAR model and a third HERMES variation are added for the Fashion use case.\\
 
@@
 
-	\textbf{Author response:} \textcolor{orange}{correction faites sauf pour la remarque sur HERMES.
-Peut etre que dans la réponse on pourra dire que c'est pour Hybird ERro-corrector Model with inclusion of External Signals ...}\\
+	\textbf{Author response:} We thank the referee for these remarks and the text has been corrected accordingly.
+Concerning the remark on the name of the proposed model, HERMES stands of Hybrid ERror-corrector Model with inclusion of External Signals.\\
 \end{itemize}

### 2023-06-28 tmlr_submission/hermes_paper_revision/hermes_paper.tex
update of the paper regarding the review 3

@@
 As a final step, fashion experts aggregate those attributes to define relevant trends for the fashion and retails industry.
+\textcolor{orange}{We call them fashion trends and they are denoted by the index $i$ in the rest of the paper.}
 
@@
 \end{equation}
+\textcolor{red}{Je crois que la notation n'est pas très claire ici.
+Je ne devrais pas mettre un $i$ car on le confond avec le i désignant le non d'un vétement.
+Peut etre qu'il faudrait que je remplace $i$ par $j$ dans le début du papier et au moment ou je définis le $i$, je dis que c'est l'id général de la trend qui regroupe c, g, m et j.}
+
 where T denotes the number of available time steps.
@@
 For the first parametric per-time-series models, existing Python  libraries named \texttt{statsmodels} and  \texttt{tbats} are used to estimate the different parameters $\statparam^n$.
-Depending of the choice of local parametric models, two versions of HERMES are proposed.
+\textcolor{gray}{Depending on the choice of local parametric models, three versions of HERMES are proposed.
 The first one uses as predictors an additive exponential smoothing model as a reference close to \citet{smyl2020}.
-The second one uses the TBATS model of \citet{alysha2011} and  achieves the highest accuracy results on the fashion dataset.
-The neural network architecture is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
+The second one uses the TBATS model of \citet{alysha2011} and  achieves the highest accuracy results on the fashion dataset.} \textcolor{orange}{Three versions of HERMES are proposed on the Fashion dataset using different local parametric models.
+The first one uses as predictors an additive exponential smoothing model as a reference close to \citet{smyl2020}.
+The second one is based on the Thetam parametric model \citep{hyndman2020}.
+Finally the last one relies on the TBATS model of \citet{alysha2011} and  achieves the highest accuracy results on the fashion dataset.
+For all the declinations,} the neural network architecture is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
 A classical Adam optimizer is used with a learning rate and a batch size set using a grid search.
@@
 This choice of $\mathrm{L}_1$ loss function is motivated by its robustness to outliers which accounts for some time series in the fashion industry with very specific behaviours.
-The loss and previous parameters are all set with a complete grid search.
+The loss and previous parameters are all set with a complete grid search \textcolor{orange}{and have to be adapted regarding the use case}.
 See \ref{sec:fashiongridsearch} for additional results concerning the loss function choice and \ref{sec:m4gridsearch} for a complete grid search example.
@@
 The results provided by \textit{hermes-tbats} confirm that the HERMES model is well suited for a large collection of forecasting tasks even difficult ones with small datasets, heterogeneous time series and the absence of  additional useful external signals.
-Secondly, the accuracy gap between the proposed hybrid model and the approach proposed in \citet{smyl2020} illustrates the importance of a global framework able to leverage any kind of per-time-series predictors depending of the use cases.
+Secondly, the accuracy gap between the proposed hybrid model and the approach proposed in \citet{smyl2020} illustrates the importance of a global framework able to leverage any kind of per-time-series predictors depending on the use cases.
 Finally, our model can be easily included as part of an ensembling method to improve the final robustness and accuracy of the predictions.

### 2023-06-29 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex
update answers_reviewer_3.tex

--- 2023-06-28 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex
@@
 Please explain in detail how the human processing was done.
-Also, to what extent can machine failures be included in image processing?
-Do humans correct them?''} \medskip
+Also, to what extent can machine failures be included in image processing ?
+Do humans correct them ?''} \medskip
 
-	\textbf{Author response:} \\
+	\textbf{Author response:} We thank the referee for this remark.
+Regarding the data-acquisition pipeline presented in section 2, the human actions are limited.
+The only human processing comes at the step where the fashion trends are defined.
+Attributes detected by the vision recognition models can be linked to identify relevant trends for the fashion industry.
+For instance, the A-line dress is identified where a dress is detected with a particular length, a particular shape and a particular collar shape, all of these details detected with different models.
+These associations of fine-grain attributes are defined by a team of fashion experts and are not provided with the paper.
+Concerning the machine failures, all the visual recognition models used to build the proposed dataset have been trained with a standard process involving a train, a eval and a test set.
+Thus, models showing poor performance in terms of accuracy and recall on the test set have been dismissed.\\
 
@@
 
-	\textbf{Author response:} \\
+	\textbf{Author response:} We agree with the referee and we acknowledge that we have not sufficiently presented the diversity of behaviours hidden in the proposed fashion dataset.
+So as to improve this point, a new section is added in appendix of the revised version of the paper where 4 different sub-samples of time series sharing the same behaviour are studied separately.
+\\
 
@@
 
-	\textbf{Author response:}\\
+	\textbf{Author response:} We understand this remark and further information has been added in the revised paper to clarify this point.
+The index of fashion trends represents the name of a fashion clothing relevant for the fashion industry.
+It can be just one attribute detected by a visual recognition model (ex: the sneakers) but it can also be a combination of several attributes (ex: the A-line dress).
+As the fashion trends' names are anonymized in the proposed dataset, the architecture behind the fashion trends definition is not presented in this paper.\\
 
@@
 
-	\textbf{Author response:}\\
+	\textbf{Author response:} We are not sure of the notation in the question of the referee, in the paper we introduce $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$ but not $\hat{y}^{c,g,m}$.
+We present below a explanation of the two statistic $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$
+	\begin{itemize}
+	\item $\Tilde{y}^{c,g,m}$ is the time series representing the behaviour of the global cloth type $c$ for the gender $g$ on the market $m$.
+It can be for example the time series representing the evolution of the general pants for females in Europe.
+The sequence $\Tilde{y}^{c,g,m}$ is then used to normalize each time series $y^{c,g,m,i}$ with the same $c$, $g$ and $m$.
+All the fashion trends of pants for females in Europe are normalized by the time series representing the general pants for females in Europe.
+	\item $\bar{y}^{c,g,m}$ is the time series $\Tilde{y}^{c,g,m}$ where the seasonality component has been removed.
+The seasonality component is removed as we only want to remove social media bias with the normalization step and not remove or change the seasonality of the proposed fashion trends.
+	\end{itemize}
 
@@
 
-	\textbf{Author response:}\\
+	\textbf{Author response:} We thank the referee for this remark.
+In the proposed method, $f^n(.)$ represents a time-series-specific parametric model, the model $f^n(y^n_{1:T},\theta^n_{predictor})$ is linked to the time series $y^n_{1:T}$.
+By contrast, the recurrent neural network denoted $RNN()$ in the paper is global: the same network is used for every time series.
+It is why we introduce $\bar{y}^n_T$ to rescale inputs and outputs of $RNN()$ as we do not assume that all the time series have the same volume.
+The fraction of the final prediction due to $y^{pred}$ or $y^{corr}$ is variable and depends on the nature of the time series (and the external signal if it is provided to the corrector model).
+A good illustration of this point is presented in a new section added in the appendix of the revised paper.
+In this section, we study the accuracy of the HERMES model on sub-samples of time series sharing the same behaviour.
+On the sub-sample of time series with a high level of noise, predictions of the HERMES model seem to rely only on $y^{pred}$.
+By contrast, on a sub-sample called 'disrupting trend', we can see that $y^{corr}$ strongly impacts the final prediction resulting in an improvement of the final accuracy of the HERMES model.
+Concerning the cost function described in Section 4.1, we decided to present this part in the Experiments section and not in the section presenting the model as the choice of the loss function can change depending on the use case.
+For instance, the L1 loss function was selected to train the HERMES variations on the Fashion dataset while the MASE loss has been used for the M4 dataset.\\
 
@@
 
-	\textbf{Author response:}\\
+	\textbf{Author response:} We thank the referee for this remark and a discussion section is added on the revised paper presenting the limit of the dataset and the limit of the proposed method.
+As future works on the dataset, we attempt to build a second fashion dataset gathering more time series and additional external signals such as fashion shows signals, brands signals etc...
+Concerning the forecasting model, we are working on a new model using hidden states to be able more finely to leverage  the impact of external signals on the main signal.\
 
@@
 
-	\textbf{Author response:}\\
+	\textbf{Author response:} We totally agree with the referee.
+In the revised version of the paper, a star is added in Table 2 and Table 4 to specify which methods have access to the weak signals and which do not.
+In addition, in Table 4, results of HERMES declination with and without the weak signal are added.
+Finally, so as to provide more benchmarks, the Prophet method, the DeepAR model and a third HERMES variation are added for the Fashion use case.\\
 

### 2023-06-29 tmlr_submission/hermes_paper_revision/hermes_paper.tex
update revised version of the paper

@@
 In many fields, single or few time series have become thousands of sequences with various statistical properties.
-In this new context, classical \textcolor{gray}{time series specific} \textcolor{orange}{time-series-specific} specific statistical models show limitations when dealing with numerous heterogeneous data.
+In this new context, classical \textcolor{gray}{time series specific} \textcolor{orange}{time-series-specific} statistical models show limitations when dealing with numerous heterogeneous data.
 \textcolor{orange}{By constrast,} recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \citet{ hochreiter1997,vaswani2017, siami2018, li2019, lim2019,salinas2020}.
@@
 First, a per-time-series parametric statistical model is trained on each sequence.
-Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.} \textcolor{orange}{First, a per-time-series parametric statistical model is trained on each sequence.
-Then, a global recurrent neural network is trained to evaluate and correct the forecast of the first collection of models.} The external weak signals reveal the real potential of the hybrid approach: a global neural network, able to leverage large amounts of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.
+Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.
+The external weak signals} \textcolor{orange}{First, a per-time-series parametric statistical model is trained on each sequence.
+Then, a global recurrent neural network is trained to evaluate and correct the forecast of the first collection of models.
+The ability to deal with external signals} reveal the real potential of the hybrid approach: a global neural network, able to leverage large amounts of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.
 
@@
 We targeted 5 strategic markets for the retail industry using posts localisation: the United States, Europe, Japan, Brazil and China.
-\textcolor{orange}{With compliance of the privacy and data protection, only public accounts are selected and no potential private information are used, saved or revealed during the whole process.}
+\textcolor{orange}{With compliance of privacy and data protection, only public accounts are selected and no potential private information is used, saved or revealed during the whole process.}
 The second step consists in creating a powerful visual recognition framework to be able to detect clothes details on pictures like the type of clothing, the form, the size, the color, the texture, etc.
@@
 As a final step, fashion experts aggregate those attributes to define relevant trends for the fashion and retails industry.
-\textcolor{orange}{We call them fashion trends and they are denoted by the index $i$ in the rest of the paper.}
+\textcolor{orange}{We call them fashion trends.
+They can be just one attribute detected by a visual recognition model, for example the sneakers fashion trend.
+They can also be a combination of several attributes, for instance the A-line dress fashion trend which is a combination of several attributes (dress length, collar shape, etc..) each one detected with a specific vision recognition model.}
 
@@
 We aggregate results by fashion trend definition over the time and  thousands of trends are finally translated from social media to time series.
-We note $y^{c,g,m,i}$ the final raw sequence representing the fashion trend $i$ of the cloth type $c$ for the gender $g$ on market $m$.
-At each time $t$, $y^{c,g,m,i}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $i$ of the cloth type $c$ for the gender $g$.
+We note $y^{c,g,m,\textcolor{orange}{j}}$ the final raw sequence representing the fashion trend $\textcolor{orange}{j}$ of the cloth type $c$ for the gender $g$ on market $m$.
+At each time $t$, $y^{c,g,m,\textcolor{orange}{j}}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $\textcolor{orange}{j}$ of the cloth type $c$ for the gender $g$.
 As an illustration, example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.
@@
 
-Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,i}$ in order to remove bias.
+Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,\textcolor{orange}{j}}$ in order to remove bias.
 Thus, we define the following normalizing signal $\Tilde{y}^{c,g,m}$.
@@
 The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$.
-Finally, for any fashion trend $i$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
+Finally, for any fashion trend $\textcolor{orange}{j}$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
 \begin{equation}
-    y^{i}_t = \frac{y^{c,g,m,i}_{t}}{\bar{y}^{c,g,m}_t}\,,
+    y^{i}_t = \frac{y^{c,g,m,\textcolor{orange}{j}}_{t}}{\bar{y}^{c,g,m}_t}\,,
 \end{equation}
@@
 
-where T denotes the number of available time steps.
-The time series $y^{c,g,m,i}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences.
+where T denotes the number of available time steps \textcolor{orange}{and $i$ represent a unique identifier summarizing the 4 information $c$, $g$, $m$ and $j$}.
+The time series $y^{c,g,m,\textcolor{orange}{j}}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences.
 With this normalizing step, most of the social media bias is removed and the final normalized sequences are expressed in share of category.
@@
 The only limitation is the computational time as we aim at forecasting thousands of time series simultaneously.
-For instance, hidden Markov models provide a very appealing framework but inference of such models requires computationally costly iterative procedures such as Expecation Maximization-based algorithms often combined with Monte Carlo estimates of unknown expectations.
+For instance, hidden Markov models provide a very appealing framework but inference of such models requires computationally costly iterative procedures such as Expectation Maximization-based algorithms often combined with Monte Carlo estimates of unknown expectations.
 Choosing these approaches as per-time-series predictors would considerably slow the overall training process of the hybrid model.}
@@
 
-\textcolor{orange}{In this section, performance of the hybrid model are presented and compared with several other approaches. the HERMES framework is evaluated on two different use cases.
+\textcolor{orange}{In this section, performance of the hybrid model is assessed and compared with several other approaches. The HERMES framework is evaluated on two different use cases.
 \begin{itemize}
-	\item A first application is proposed on the Fashion dataset.
+	\item A first application is proposed on the fashion dataset.
 The HERMES model is trained at forecasting the fashion time series one year ahead (h=52).
@@
 Based on the competition's rules, the forecasting horizon is set to 13 and no external signals are available.
-Futhermore, the proposed times series come from different sectors and have variable lengths.
+Furthermore, the M4 weekly time series come from different sectors and have variable lengths.
 \end{itemize}
@@
 
-\subsection{Training}
-The dataset is split into three blocks, {\em train}, {\em eval} and {\em test} sets.
+\textcolor{orange}{\subsection{Fashion use case}}
+
+\textcolor{orange}{\subsubsection{Training}}
+The fashion dataset is split into three blocks, {\em train}, {\em eval} and {\em test} sets.
 The 3 first years are used as the {\em train} set, the 4th year is kept for the {\em eval} set and the {\em test} set is made of the last year.
@@
 The first one uses as predictors an additive exponential smoothing model as a reference close to \citet{smyl2020}.
-The second one uses the TBATS model of \citet{alysha2011} and  achieves the highest accuracy results on the fashion dataset.} \textcolor{orange}{Three versions of HERMES are proposed on the Fashion dataset using different local parametric models.
-The first one uses as predictors an additive exponential smoothing model as a reference close to \citet{smyl2020}.
-The second one is based on the Thetam parametric model \citep{hyndman2020}.
-Finally the last one relies on the TBATS model of \citet{alysha2011} and  achieves the highest accuracy results on the fashion dataset.
-For all the declinations,} the neural network architecture is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
+The second one uses the TBATS model of \citet{alysha2011} and  achieves the highest accuracy results on the fashion dataset.
+The neural network architecture} \textcolor{orange}{The architecture of the recurrent neural network corrector model} is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
 A classical Adam optimizer is used with a learning rate and a batch size set using a grid search.
@@
 
-\subsection{Benchmarks, hybrid models and Metrics}
+\textcolor{orange}{\subsubsection{Benchmarks, hybrid models and metrics}}
 \label{sec:fashiontraining}
@@
 
-\textcolor{orange}{We also compare our model with recent recent deep learning architectures for time series.
+\textcolor{orange}{We also compare our model with recent deep learning architectures for time series.
 The Prophet model introduced in \citet{Taylor2017} is proposed and implemented with the available package bearing the same name \texttt{prophet}, and three models based on recurrent neural networks called \textit{lstm}, \textit{lstm-ws} and \textit{deepar} are used.
 Concerning \textit{lstm} and \textit{lstm-ws}, they are both composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52.
-The first one (\textit{lstm}) has only access to the main signal while the second one (\textit{lstm-ws}) has also access to the external signal.
+The first one (\textit{lstm}) has only access to the main signal while the second one (\textit{lstm-ws}) has access to the external signal.
 The last approach is the recent state-of-the-art model called DeepAR and introduced in \citet{salinas2020}.
@@
 
-\textcolor{orange}{
-A strength of the proposed HERMES framework is that it can handle any kind of parametric model.
-Thus, three declinations of the HERMES approach are proposed on the Fashion dataset using different per-time-series predictors: Ets, Tbats and Thetam.
-They are called respectively \textit{hermes-ets}, \textit{hermes-tbats} and \textit{hermes-thetam} according to the per-time-series model choice.
+\textcolor{orange}{A strength of the proposed HERMES framework is that it can handle any kind of parametric model.
+Thus, three versions of HERMES are proposed on the fashion dataset using different local parametric models.
+The first one uses as predictors an additive exponential smoothing model as a reference close to \citet{smyl2020}.
+The second one is based on the Thetam parametric model \citep{hyndman2020}.
+Finally the last one relies on the TBATS model of \citet{alysha2011} and  achieves the highest accuracy results on the fashion dataset.
+Declinations are called respectively \textit{hermes-ets}, \textit{hermes-tbats} and \textit{hermes-thetam} according to the per-time-series model choice.
 For each of them, a variation with the inclusion of the weak signals (\textit{-ws}) is presented.}
@@
 
-\subsection{Result for the Fashion dataset}
+\textcolor{orange}{\subsubsection{Results}}
 
@@
 It is one of the main motivations why this model is used on the best HERMES candidate as the predictor model.
-
-\textcolor{orange}{All the different versions of HERMES show consequent improvements regarding their per-time-series predictors in terms of MASE.
-\textit{Hermes-tbats} largely outperforms the two other declinations and all the benchmarks on the fashion dataset.
-This result highlights two important features of the proposed hybrid model: i) the final accuracy of the model is strongly impacted by the choice of the per-time-series predictor and ii) if the per-time-series predictor is well chosen regarding the nature of the time series, the resulting HERMES model outperforms state-of-the-art approaches such as DeepAR.}
+\textcolor{orange}{All HERMES versions show consequent improvements regarding their per-time-series predictors in terms of MASE.
+\textit{hermes-tbats} outperforms the two other declinations and all the benchmarks on the fashion dataset.
+This result highlights two important features of the proposed hybrid model: i) the final accuracy of the model is strongly impacted by the choice of the per-time-series predictor and ii) if the per-time-series predictor is well chosen regarding the nature of the time series, the resulting HERMES model seems to outperforms other state-of-the-art approaches.}
 \textcolor{gray}{Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slightly outperform the alternatives in terms of MASE and are stable across the different trainings.
@@
 \begin{table}
-  \caption{Results summary on the 10000 time series of the Fashion dataset.
+  \caption{Results summary on the 10000 time series of the fashion dataset.
 For each metric, the average on all our time series is computed.
 For approaches using neural networks, 10 models are trained with different seeds.
-The mean and the standard deviation of the 10 results are displayed.}
+The mean and the standard deviation of the 10 results are displayed.
+\textcolor{orange}{Models with a $^*$ in their name have access to the influencers external signal.}}
   \centering
@@
      \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
-     \textit{hermes-ets-ws} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
+     \textit{hermes-ets-ws*} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
      \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.764} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.497} && \textcolor{orange}{0.005}\\
-     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.760} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.520}} && \textcolor{orange}{0.010}\\
+     \textcolor{orange}{\textit{hermes-thetam-ws*}} && \textcolor{orange}{0.760} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.520}} && \textcolor{orange}{0.010}\\
      \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
@@
      \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
-     \textit{lstm-ws} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
+     \textit{lstm-ws*} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
      \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
      \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
-     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& 0.510 && 0.005 &\\
+     \textbf{\textit{hermes-tbats-ws*}} && \textbf{0.712} && 0.004 &&& 0.510 && 0.005 &\\
   \end{tabular}
@@
 Results are given in Table~\ref{tab:1000metricresults}.
-The hybrid framework \textit{hermes-tbats} achieves the best performance in terms of global accuracy on both datasets.
+The hybrid framework \textit{hermes-tbats-ws} achieves the best performance in terms of global accuracy on both datasets.
 We can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases.
-On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms \textcolor{orange}{deep-model-based approach such as \textit{lstm} of \textit{deepar}}.
+On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms \textcolor{orange}{deep-model-based approaches such as \textit{lstm} of \textit{deepar}}.
 In fact, providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require large amounts of data to do so.
@@
 \begin{table}
-  \caption{Results summary on 1000 time series and 100 time series of the Fashion dataset.
+  \caption{Results summary on 1000 time series and 100 time series of the fashion dataset.
 The MASE average on all the time series is computed.
 For the two approaches using a neural network, 10 models with different seeds are trained.
-the mean and the standard deviation of the 10 results are displayed.\vspace{0.5cm}}
+the mean and the standard deviation of the 10 results are displayed.
+\textcolor{orange}{Models with a $^*$ in their name have access to the influencers external signal.}\vspace{0.5cm}}
  \centering
@@
  \begin{tabular}{l||lllll|lllll}
-   \multicolumn{11}{c}{1000 time series Fashion dataset}\vspace{0.5cm}\\
+   \multicolumn{11}{c}{1000 time series fashion dataset}\vspace{0.5cm}\\
    &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
@@
      \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.476} && \textcolor{orange}{0.009} &\\
-      \textcolor{orange}{\textit{hermes-ets-ws}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.507}} && \textcolor{orange}{0.013} &\\
+      \textcolor{orange}{\textit{hermes-ets-ws*}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.507}} && \textcolor{orange}{0.013} &\\
      \textit{stlm} && 0.765 && - &&& \textcolor{orange}{0.493} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.763} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.501} && \textcolor{orange}{0.009} &\\
+     \textcolor{orange}{\textit{hermes-thetam-ws*}} && \textcolor{orange}{0.763} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.501} && \textcolor{orange}{0.009} &\\
      \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.740} && \textcolor{orange}{0.007} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
@@
      \textit{tbats} && 0.734 && - &&& \textcolor{orange}{0.466} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{lstm-ws}} && \textcolor{orange}{0.731} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.492} && \textcolor{orange}{0.012} &\\
+     \textcolor{orange}{\textit{lstm-ws*}} && \textcolor{orange}{0.731} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.492} && \textcolor{orange}{0.012} &\\
      \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.721} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
-     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws}}} && \textcolor{orange}{0.717} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.500} && \textcolor{orange}{0.010} &\\
+     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws*}}} && \textcolor{orange}{0.717} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.500} && \textcolor{orange}{0.010} &\\
 
@@
   \begin{tabular}{l||lllll|lllll}
-   \multicolumn{11}{c}{100 time series Fashion dataset}\vspace{0.5cm}\\
+   \multicolumn{11}{c}{100 time series fashion dataset}\vspace{0.5cm}\\
    &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
@@
      \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.015} &&& \textcolor{orange}{0.446} && \textcolor{orange}{0.049} &\\
-     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.008} &&& \textcolor{orange}{0.479} && \textcolor{orange}{0.024} &\\
+     \textcolor{orange}{\textit{hermes-thetam-ws*}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.008} &&& \textcolor{orange}{0.479} && \textcolor{orange}{0.024} &\\
      \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.804} && \textcolor{orange}{0.024} &&& \textcolor{orange}{0.393} && \textcolor{orange}{0.029} &\\
-     \textcolor{orange}{\textit{hermes-ets-ws}} && \textcolor{orange}{0.792} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.386} && \textcolor{orange}{0.010} &\\
+     \textcolor{orange}{\textit{hermes-ets-ws*}} && \textcolor{orange}{0.792} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.386} && \textcolor{orange}{0.010} &\\
      \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.790} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.374} && \textcolor{orange}{0.005} &\\
-     \textcolor{orange}{\textit{lstm-ws}} && \textcolor{orange}{0.789} && \textcolor{orange}{0.010} &&& \textcolor{orange}{0.485} && \textcolor{orange}{0.036} &\\
+     \textcolor{orange}{\textit{lstm-ws*}} && \textcolor{orange}{0.789} && \textcolor{orange}{0.010} &&& \textcolor{orange}{0.485} && \textcolor{orange}{0.036} &\\
      \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.400} && \textcolor{orange}{-} &\\
@@
      \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.741} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.462} && \textcolor{orange}{0.021} &\\
-     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws}}} && \textcolor{orange}{\textbf{0.737}} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.486} && \textcolor{orange}{0.027} &\\
+     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws*}}} && \textcolor{orange}{\textbf{0.737}} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.486} && \textcolor{orange}{0.027} &\\
   \end{tabular}
@@
 
-\subsection{Result for M4 weekly dataset}
+\textcolor{orange}{\subsection{M4 competition use case}}
 \label{sec:m4result}
@@
 
-\textbf{Training. }
+\textcolor{orange}{\subsubsection{Training}}
 The M4 dataset is preprocessed as follows. As some sequences are short (93 time steps), they limit the window size $w$ of the RNN.  
@@
 
-\textbf{Evaluation.
-} The proposed model is evaluated along with a rich collection of benchmarks provided by the M4 competition, encompassing statistical models and neural network approaches.
+\textcolor{orange}{\subsubsection{Evaluation}}
+The proposed model is evaluated along with a rich collection of benchmarks provided by the M4 competition, encompassing statistical models and neural network approaches.
 In addition, the hybrid model named \textit{Uber} of S.Smyl is added.
@@
 
-\textbf{Results and discussion.
-} The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}.
+\textcolor{orange}{\subsubsection{Results}}
+The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}.
 The HERMES approach \textit{hermes-tbats} outperforms all the benchmarks.
@@
 \textcolor{orange}{We show that it is possible to represent and understand fashion through its representation on social media.
-Futhermore, with a special focus done on the behaviour of influencers, it become possible to better anticipate consumers needs and avoid massive wastes due to overstocks.} By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
+Furthermore, with a special focus on the behaviour of influencers, it becomes possible to better anticipate consumers' needs and avoid massive wastes due to overstocks.} By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
 As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.
@@
 \textcolor{orange}{
-\section{Fashion dataset: a study of sub-samples of time series sharing the same behaviour}
+\section{Fashion dataset: a study of sub samples of time series sharing the same behaviour}
 }
 \textcolor{orange}{
-On a large dataset as the Fashion dataset, looking at aggregated metrics can often hide relevant results, especially on sub-samples sharing the same behaviours.
-To illustrate this point, a study of 4 sub-samples of the Fashion dataset is proposed in this section.
+On a large dataset as the fashion dataset, looking at aggregated metrics can often hide relevant results, especially on sub samples sharing the same behaviours.
+To illustrate this point, a study of 4 sub samples of the fashion dataset is proposed in this section.
 Their are defined as follows:
@@
 \item \textbf{disrupting time series}: In retail and fashion industries, a strategic issue is to correctly anticipate new trends that will burst or collapse in the next weeks, months or years.
-To detect these sub sample of trends in the Fashion dataset, the following approach is proposed: Using the \textit{snaive} model, a prediction of the last year is computed for each trend and the linked MASE.
-Finally, the dirsupting time series are the 1000 time series with the highest MASE.
-\item \textbf{stable time series}: By contrast, a group a stable trend a presented.
+To detect this sub sample of trends in the fashion dataset, the following approach is proposed: Using the \textit{snaive} model, a prediction of the last year of data is computed for each trend and the associated MASE.
+The disrupting time series are defined as the 1000 time series where the snaive prediction got the highest MASE.
+\item \textbf{stable time series}: By contrast, a group of stable trends is presented.
 To define them, the same methodology as the previous group is used.
-We define them as the time series where the \textit{snaive} prediction reachs the lowest MASE.
-\item \textbf{seasonal time series}: Another relevant group of time series is sequences showing a strong seasonal patern.
+We define them as the 1000 time series where the \textit{snaive} prediction reached the lowest MASE.
+\item \textbf{seasonal time series}: Another relevant group of time series is sequences showing a strong seasonal pattern.
 So as to detect them, we compute for each trend the seasonality strength metric introduced in \citet{wang2006}.
-The seasonal time series group is the 1000 fashion time series with highest seasonality strength.
-\item \textbf{noisy time series}: Finally, several time series of the Fashion dataset represent niche trends only worn and posted on social media by a few people.
+The seasonal time series group is the 1000 fashion time series with the highest seasonality strength metric.
+\item \textbf{noisy time series}: Finally, several time series of the fashion dataset represent niche trends only worn and posted on social media by a few people.
 The average volume for these sequences is low resulting in sporadic and noisy time series difficult to forecast.
-In order to detect them, we use the seasonality and trend strenght metrics presented in \citet{wang2006}.
-For each time series, the average of these two quantities is computed and we define the time series group as the 1000 sequences with the lowest averages.
+In order to detect them, we use the seasonality and trend strength metrics presented in \citet{wang2006}.
+For each time series, the average of these two quantities is computed and we define the time series group as the 1000 sequences with the lowest average.
 \end{itemize}
-Table~\ref{tab:fashionsubsample} displays the MASE of each models introduced in Section~\ref{sec:exp} on the 4 sub-samples of time series.
-Several relevant results can be highlited.
+Table~\ref{tab:fashionsubsample} displays the MASE of each model introduced in Section~\ref{sec:exp} on the 4 sub samples of time series.
+Several relevant results can be highlighted.
 Firstly, models using the influencer weak signals strongly outperform other candidates on the disruptive time series.
 This result is even more visible with the HERMES approach where variations using the weak signals are always better than the ones without.
-These results illustrate the really predictive strenght of the influencer signals proposed in the Fashion dataset and prove empirically the impact of influencers on the fashion industries.
+These results illustrate the really predictive strength of the influencer signals proposed in the fashion dataset and prove empirically the impact of influencers on the fashion industries.
 Secondly, on stable time series and seasonal time series, a relevant interest of the hybrid approach is revealed.
 Looking at the result of \textit{hermes-tbats}, we can see that this hybrid model can use the strength of \textit{tbats} to compute a first accurate prediction and then, use the strength of a global neural network to understand more complex patterns.
-This strenght is even more visible on seasonal time series where hybrid approach largely outperform then neural network models presented in the benchmarks.
-Finally, on noisy time series, we can see that neural network methodes reach the highest accuracy and are the less impacted by these difficult trend.
-Futhermore, for all the HERMES approaches, we can note that the final hybrid predictions and the per-time-series models' predictions are the same.
-The error-correction model doesn't try to predict the noise and let the per-time-series models' predictions as they are.}
+This strength is even more visible on seasonal time series where hybrid approaches largely outperform neural network models presented in the benchmarks.
+Finally, on noisy time series, we can see that neural network methods reach the highest accuracy and are the least impacted by these difficult trends.
+Furthermore, for all the HERMES approaches, we can note that the final hybrid predictions and the per-time-series models' predictions are the same.
+The error-correction model does not try to predict the noise and lets the per-time-series models' predictions as they are.}
 
 \begin{table}
-  \caption{Results summary on 4 differents sub-sample of  Fashion time series: i) disrupting time series, ii) stable time series, iii) seasonal time series and iv) noisy time series.}\vspace{0.5cm} 
+  \caption{\textcolor{orange}{Results summary on 4 differents sub sample of  Fashion time series: i) disrupting time series, ii) stable time series, iii) seasonal time series and iv) noisy time series.
+Models with a $^*$ in their name have access to the influencers external signal.}}\vspace{0.5cm}
  \centering
@@
 	 \textit{lstm} && 1.15 & 0.01\\ 
-	 \textit{hermes-thetam-ws} && 1.145 & 0.019\\ 
-	 \textit{hermes-ets-ws} && 1.131 & 0.024\\ 
-	 \textit{hermes-tbats-ws} && 1.092 & 0.007\\ 
-	 \textit{lstm-ws} && 1.086 & 0.009\\  \vspace{0.5cm}\\
+	 \textit{hermes-thetam-ws*} && 1.145 & 0.019\\ 
+	 \textit{hermes-ets-ws*} && 1.131 & 0.024\\ 
+	 \textit{hermes-tbats-ws*} && 1.092 & 0.007\\ 
+	 \textit{lstm-ws*} && 1.086 & 0.009\\  \vspace{0.5cm}\\
   \end{tabular}\hspace{1cm}
@@
 	 \textit{arima} && 0.565 & -\\ 
-	 \textit{hermes-ets-ws} && 0.555 & 0.007\\ 
+	 \textit{hermes-ets-ws*} && 0.555 & 0.007\\ 
 	 \textit{snaive} && 0.536 & -\\  
 	 \textit{deepar} && 0.531 & 0.024\\ 
- 	 \textit{hermes-thetam-ws} && 0.522 & 0.004\\ 
+ 	 \textit{hermes-thetam-ws*} && 0.522 & 0.004\\ 
 	 \textit{hermes-ets} && 0.518 & 0.002\\ 
@@
 	 \textit{tbats} && 0.501 & -\\ 
-	 \textit{lstm-ws} && 0.492 & 0.007\\ 
-	 \textit{hermes-tbats-ws} && 0.477 & 0.008\\ 
+	 \textit{lstm-ws*} && 0.492 & 0.007\\ 
+	 \textit{hermes-tbats-ws*} && 0.477 & 0.008\\ 
 	 \textit{lstm} && 0.47 & 0.004\\ 
@@
 	 \textit{deepar} && 0.836 & 0.035\\ 
-	 \textit{lstm-ws} && 0.829 & 0.014\\ 
+	 \textit{lstm-ws*} && 0.829 & 0.014\\ 
 	 \textit{thetam} && 0.826 & -\\ 
@@
 	 \textit{tbats} && 0.81 & -\\ 
-	 \textit{hermes-ets-ws} && 0.809 & 0.01\\ 
-	 \textit{hermes-thetam-ws} && 0.808 & 0.008\\ 
+	 \textit{hermes-ets-ws*} && 0.809 & 0.01\\ 
+	 \textit{hermes-thetam-ws*} && 0.808 & 0.008\\ 
 	 \textit{arima} && 0.805 & -\\ 
@@
 	 \textit{hermes-ets} && 0.785 & 0.003\\ 
-	 \textit{hermes-tbats-ws} && 0.777 & 0.012\\ 
+	 \textit{hermes-tbats-ws*} && 0.777 & 0.012\\ 
 	 \textit{hermes-tbats} && 0.772 & 0.003\\ 
@@
      \textit{snaive} && 0.842 & -\\ 
-	 \textit{hermes-ets-ws} && 0.739 & 0.005\\ 
+	 \textit{hermes-ets-ws*} && 0.739 & 0.005\\ 
 	 \textit{hermes-ets} && 0.726 & 0.002\\ 
@@
 	 \textit{arima} && 0.696 & -\\ 
-	 \textit{hermes-thetam-ws} && 0.672 & 0.003\\ 
+	 \textit{hermes-thetam-ws*} && 0.672 & 0.003\\ 
 	 \textit{hermes-thetam} && 0.669 & 0.001\\ 
 	 \textit{deepar} && 0.661 & 0.007\\ 
-	 \textit{hermes-tbats-ws} && 0.647 & 0.006\\ 
+	 \textit{hermes-tbats-ws*} && 0.647 & 0.006\\ 
 	 \textit{tbats} && 0.646 & -\\ 
 	 \textit{hermes-tbats} && 0.644 & 0.003\\ 
-	 \textit{lstm-ws} && 0.637 & 0.004\\ 
+	 \textit{lstm-ws*} && 0.637 & 0.004\\ 
 	 \textit{lstm} && 0.636 & 0.003\\
@@
 
-\subsection{Loss grid search on the Fashion Dataset}
+\subsection{Loss grid search on the fashion Dataset}
 \label{sec:fashiongridsearch}
@@
 For each loss, 10 \textit{hermes-tbats-ws} models have been trained with different seeds and the final mean and standard deviation are given in Figure~\ref{fig:loss_function}.
-The final Scaled Mean Absolute Error reaches the lowest MASE and was selected to train all the HERMES models on the Fashion dataset.
+The final Scaled Mean Absolute Error reaches the lowest MASE and was selected to train all the HERMES models on the fashion dataset.
 

### 2023-06-29 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex
minor update of ansers_reviewer_3.tex

@@
 
-	\textbf{Author response:} We thank the referee for this remark and a discussion section is added on the revised paper presenting the limit of the dataset and the limit of the proposed method.
+	\textbf{Author response:} We thank the referee for this remark and sipplementary information has been added in the result sections and in appendix of the revised paper.
 As future works on the dataset, we attempt to build a second fashion dataset gathering more time series and additional external signals such as fashion shows signals, brands signals etc...

### 2023-07-03 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex
Updated paper and answer to reviewer 3

@@
 	\textbf{Author response:} We thank the referee for this remark.
-Regarding the data-acquisition pipeline presented in section 2, the human actions are limited.
+Regarding the data-acquisition pipeline presented in Section 2, the human actions are limited.
 The only human processing comes at the step where the fashion trends are defined.
-Attributes detected by the vision recognition models can be linked to identify relevant trends for the fashion industry.
+The features are automatically detected by the vision recognition models.
+Then, we only define trends that are relevant for the fashion industry.
 For instance, the A-line dress is identified where a dress is detected with a particular length, a particular shape and a particular collar shape, all of these details detected with different models.
@@
 Concerning the machine failures, all the visual recognition models used to build the proposed dataset have been trained with a standard process involving a train, a eval and a test set.
-Thus, models showing poor performance in terms of accuracy and recall on the test set have been dismissed.\\
+Thus, models showing poor performance in terms of accuracy and recall on the test set have been dismissed.
+Please note that the data acquisition pipeline has been detailed and extended in Section 2.
+\\
 
@@
 It can be just one attribute detected by a visual recognition model (ex: the sneakers) but it can also be a combination of several attributes (ex: the A-line dress).
-As the fashion trends' names are anonymized in the proposed dataset, the architecture behind the fashion trends definition is not presented in this paper.\\
+As the fashion trends names are anonymized in the proposed dataset, the architecture behind the fashion trends definition is not presented in this paper.\\
 
@@
 	\textbf{Author response:} We are not sure of the notation in the question of the referee, in the paper we introduce $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$ but not $\hat{y}^{c,g,m}$.
-We present below a explanation of the two statistic $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$
+We present below a explanation of the two statistic $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$ which is now detailed in the paper.
 	\begin{itemize}
-	\item $\Tilde{y}^{c,g,m}$ is the time series representing the behaviour of the global cloth type $c$ for the gender $g$ on the market $m$.
+	\item $\Tilde{y}^{c,g,m}$ is the time series representing the behaviour of the global cloth type $c$ for the gender $g$ on the market $m$ \textcolor{red}{Est-ce que cela sifnifie que $\Tilde{y}^{c,g,m}$  est la somme sur $i$ (ou sur $j$ dans la nouvelle notation du papier) des $y^{c,g,m,i}$ ?
+Si oui, il faut le dire ici et dans le papier, c'est plus explicite.}.
 It can be for example the time series representing the evolution of the general pants for females in Europe.
@@
 
-	\textbf{Author response:} We thank the referee for this remark and sipplementary information has been added in the result sections and in appendix of the revised paper.
+	\textbf{Author response:} We thank the referee for this remark and supplementary information has been added in the result sections and in appendix of the revised paper.
 As future works on the dataset, we attempt to build a second fashion dataset gathering more time series and additional external signals such as fashion shows signals, brands signals etc...
-Concerning the forecasting model, we are working on a new model using hidden states to be able more finely to leverage  the impact of external signals on the main signal.\
+
+ Concerning the forecasting model, we agree that desining models to explain the time delay between weak signals shifts and their consequences on the target signals is an interesting objective.
+We believe that this is out of the scope of the present paper but this is the topic of an ongoing work using hidden states to leverage  the impact of external signals on the main signal.\
 
@@
 
-	\textbf{Author response:} We totally agree with the referee.
-In the revised version of the paper, a star is added in Table 2 and Table 4 to specify which methods have access to the weak signals and which do not.
-In addition, in Table 4, results of HERMES declination with and without the weak signal are added.
+	\textbf{Author response:}  In the revised version of the paper, a star is added in Table 2 and Table 4 to specify which methods have access to the weak signals and which do not.
+In addition, in Table 4, results of HERMES declinations with and without the weak signals are added.
 Finally, so as to provide more benchmarks, the Prophet method, the DeepAR model and a third HERMES variation are added for the Fashion use case.\\

### 2023-07-03 tmlr_submission/hermes_paper_revision/hermes_paper.tex
Updated paper and answer to reviewer 3

@@
 \begin{abstract}
-Developing models and algorithms to draw \textcolor{gray}{causal inference} \textcolor{orange}{predictions} for time series is a long standing statistical problem.
+Developing models and algorithms to \textcolor{orange}{predict nonstationary} time series is a long standing statistical problem.
 It is crucial for many applications, in particular for fashion or retail industries, to make optimal inventory decisions and avoid massive wastes.
@@
 Our contribution is  twofold.
-We first provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} an appealing \textcolor{gray}{fashion} dataset gathering \numberts\ weekly fashion time series.
+We first provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} a \textcolor{gray}{fashion} dataset gathering \numberts\ weekly fashion time series.
 As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviours of influencers.
-Secondly, to leverage such a complex and rich dataset, we propose a new hybrid forecasting model\footnotemark.
+Secondly, to leverage such a dataset, we propose a new hybrid forecasting model\footnotemark.
 Our approach combines per-time-series parametric models with seasonal components and a global recurrent neural network to include sporadic external signals.
@@
 In this paper, we propose a new fashion dataset overcoming the weaknesses of the two previous ones.
-Based on cutting-edge image recognition algorithms \citep{ren2015,chollet2017}, we built a large fashion dataset containing \numberts\ weekly sequences of fashion trends on social media with 5 years of historical data from 01-01-2015 to 30-12-2019.
+Based on recent image recognition algorithms \citep{ren2015,chollet2017}, we built a large fashion dataset containing \numberts\ weekly sequences of fashion trends on social media with 5 years of historical data from 01-01-2015 to 30-12-2019.
 This dataset has very appealing properties:  all time series have the same length (261 data points), there is no missing value and there is no sparse time series even for niche trends.
@@
 Section~\ref{sec:dataset} presents the new fashion dataset provided with this article.
-Then, the proposed forecasting approach HERMES is presented in Section~\ref{sec:hybrid}.
-Section~\ref{sec:exp} describes the model results and comparisons with several benchmarks on \textcolor{gray}{the} 2 different use cases: the fashion dataset and the M4 competition weekly dataset.
+Then, the proposed forecasting approach  is presented in Section~\ref{sec:hybrid}.
+Section~\ref{sec:exp} describes the experiments and comparisons with several benchmarks on \textcolor{gray}{the} 2 different use cases: the fashion dataset and the M4 competition weekly dataset.
 Finally, a general conclusion and some research perspectives are given in  Section~\ref{sec:conclusion}.
@@
 
-\textcolor{orange}{Social Networks have appeared as an impressive data source to follow the evolution of fashion over the time.
+%\textcolor{orange}{Social Networks have appeared as an impressive data source to follow the evolution of fashion over the time.
 Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world.
@@
 
-\textcolor{gray}{Social media have appeared as an impressive data source to follow the evolution of fashion over the time.
+%\textcolor{gray}{Social media have appeared as an impressive data source to follow the evolution of fashion over the time.
 Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world.
-To do it automatically for thousands of trends, the following methodology was introduced.} In the first place, a complete image dataset of 150 millions pictures is collected from different social media such as Instagram or Weibo.
+To do it automatically for thousands of trends, the following methodology was introduced.}
+An image dataset of 150 millions pictures is collected from different social media such as Instagram or Weibo.
 We targeted 5 strategic markets for the retail industry using posts localisation: the United States, Europe, Japan, Brazil and China.
@@
 Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,\textcolor{orange}{j}}$ in order to remove bias.
-Thus, we define the following normalizing signal $\Tilde{y}^{c,g,m}$.
-This signal represents the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe).
+Let $\Tilde{y}^{c,g,m}$ be the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe).
 With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$.
@@
 Peut etre qu'il faudrait que je remplace $i$ par $j$ dans le début du papier et au moment ou je définis le $i$, je dis que c'est l'id général de la trend qui regroupe c, g, m et j.}
+\textcolor{blue}{ok, cela me para\^it clair}
 

### 2023-07-03 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex
Minor updates review + answer R3

@@
 	\textbf{Author response:} We agree with the referee and we acknowledge that we have not sufficiently presented the diversity of behaviours hidden in the proposed fashion dataset.
-So as to improve this point, a new section is added in appendix of the revised version of the paper where 4 different sub-samples of time series sharing the same behaviour are studied separately.
+So as to improve this point, a new section is added in appendix of the revised version of the paper where 4 different sub-samples of time series are defined and studied separately.
 \\

### 2023-07-03 tmlr_submission/hermes_paper_revision/hermes_paper.tex
Minor updates review + answer R3

@@
 The only limitation is the computational time as we aim at forecasting thousands of time series simultaneously.
-For instance, hidden Markov models provide a very appealing framework but inference of such models requires computationally costly iterative procedures such as Expectation Maximization-based algorithms often combined with Monte Carlo estimates of unknown expectations.
+For instance, hidden Markov models provide a very interesting framework but inference of such models requires computationally costly iterative procedures such as Expectation Maximization-based algorithms often combined with Monte Carlo estimates of unknown expectations.
 Choosing these approaches as per-time-series predictors would considerably slow the overall training process of the hybrid model.}
@@
 
-For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence.
+For non stationary time series, changes of behaviours are not always predictable using the past of the sequence.
 In some cases, these changes depend on external variables not considered by univariate parametric models.
@@
 The mean and the standard deviation of the 10 results are displayed.
-\textcolor{orange}{Models with a $^*$ in their name have access to the influencers external signal.}}
+\textcolor{orange}{Models with a $^*$ in their name have access to the external signal.}}
   \centering
@@
 the mean and the standard deviation of the 10 results are displayed.
-\textcolor{orange}{Models with a $^*$ in their name have access to the influencers external signal.}\vspace{0.5cm}}
+\textcolor{orange}{Models with a $^*$ in their name have access to the external signal.}\vspace{0.5cm}}
  \centering
@@
 In addition, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided.
-\textcolor{orange}{We show that it is possible to represent and understand fashion through its representation on social media.
-Furthermore, with a special focus on the behaviour of influencers, it becomes possible to better anticipate consumers' needs and avoid massive wastes due to overstocks.} By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
+\textcolor{orange}{We show that it is possible to represent fashion data with time series and introduce statistical models based on social media data.
+}% Furthermore, with a special focus on the behaviour of influencers, it becomes possible to better anticipate consumers' needs and avoid massive wastes due to overstocks.}
+ By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
 As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.

### 2023-07-04 tmlr_submission/hermes_paper_revision/hermes_paper.tex
minor changes
removing the grey sentences

@@
 Our contribution is  twofold.
-We first provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} a \textcolor{gray}{fashion} dataset gathering \numberts\ weekly fashion time series.
+We first provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} a dataset gathering \numberts\ weekly fashion time series.
 As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviours of influencers.
@@
 Multivariate time series forecasting is a widespread statistical problem with  many applications, see for instance \citet{sarkka2013, douc2014, zucchini2017} and the numerous references therein.
-Parametric generative models provide explainable predictions with statistical guarantees \textcolor{gray}{based on} \textcolor{orange}{owing to} a precise modeling of the predictive distributions of new data based on a record of past observations.
-\textcolor{gray}{Calibrating these models, for instance using maximum likelihood inference, often requires a fair amount of tuning to design a time series-specific model to provide  accurate forecasts and sharp confidence intervals.} \textcolor{orange}{Calibrating these models, for instance using maximum likelihood inference, often requires a fair amount of tuning so as to design time-series-specific models able to provide  accurate forecasts and sharp confidence intervals.} Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
+Parametric generative models provide explainable predictions with statistical guarantees \textcolor{orange}{owing to} a precise modeling of the predictive distributions of new data based on a record of past observations.
+\textcolor{orange}{Calibrating these models, for instance using maximum likelihood inference, often requires a fair amount of tuning so as to design time-series-specific models able to provide  accurate forecasts and sharp confidence intervals.} Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
 The exponential smoothing model \citep{Brown1961}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \citep{alysha2011}, or the ARIMA with the Box-Jenkins approach \citep{box2015} are for instance very popular parametric generative models.
@@
 In many fields, single or few time series have become thousands of sequences with various statistical properties.
-In this new context, classical \textcolor{gray}{time series specific} \textcolor{orange}{time-series-specific} statistical models show limitations when dealing with numerous heterogeneous data.
+In this new context, classical \textcolor{orange}{time-series-specific} statistical models show limitations when dealing with numerous heterogeneous data.
 \textcolor{orange}{By constrast,} recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \citet{ hochreiter1997,vaswani2017, siami2018, li2019, lim2019,salinas2020}.
@@
 With our fashion expertise, we detected several groups of highly influential fashion users.
-Analyzing their specific behaviours on social media, we associate with each time series an external weak signal representing the same fashion trends on \textcolor{gray}{a} \textcolor{orange}{this} sub-category of users.
+Analyzing their specific behaviours on social media, we associate with each time series an external weak signal representing the same fashion trends on \textcolor{orange}{this} sub-category of users.
 They are called weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal.
@@
 Following this work, we present in this paper HERMES, a new hybrid recurrent model for time series forecasting with inclusion of external signals.
-This new architecture is decomposed  into two parts: \textcolor{gray}{local predictors and a global corrector.
-First, a per-time-series parametric statistical model is trained on each sequence.
-Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.
-The external weak signals} \textcolor{orange}{First, a per-time-series parametric statistical model is trained on each sequence.
+This new architecture is decomposed  into two parts: \textcolor{orange}{First, a per-time-series parametric statistical model is trained on each sequence.
 Then, a global recurrent neural network is trained to evaluate and correct the forecast of the first collection of models.
@@
 Then, the proposed forecasting approach is presented in Section~\ref{sec:hybrid}.
-Section~\ref{sec:exp} describes the experiments and comparisons with several benchmarks on \textcolor{gray}{the} 2 different use cases: the fashion dataset and the M4 competition weekly dataset.
+Section~\ref{sec:exp} describes the experiments and comparisons with several benchmarks on 2 different use cases: the fashion dataset and the M4 competition weekly dataset.
 Finally, a general conclusion and some research perspectives are given in  Section~\ref{sec:conclusion}.
@@
 
-%\textcolor{gray}{Social media have appeared as an impressive data source to follow the evolution of fashion over the time.
-Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world.
-To do it automatically for thousands of trends, the following methodology was introduced.}
 An image dataset of 150 millions pictures is collected from different social media such as Instagram or Weibo.
@@
 \end{equation}
-\textcolor{red}{Je crois que la notation n'est pas très claire ici.
-Je ne devrais pas mettre un $i$ car on le confond avec le i désignant le non d'un vétement.
-Peut etre qu'il faudrait que je remplace $i$ par $j$ dans le début du papier et au moment ou je définis le $i$, je dis que c'est l'id général de la trend qui regroupe c, g, m et j.}
-\textcolor{blue}{ok, cela me para\^it clair}
 
@@
 \textcolor{orange}{In Section~\ref{sec:exp}, we introduce three declinations of the hybrid framework  using different per-time-series predictors to highlight the adaptability of our approach.
-The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020}, the second one uses Thetam as per-time-series predictor \citep{hyndman2020} and the last one uses a TBATS model \citep{alysha2011}.} \textcolor{gray}{In Section~\ref{sec:exp}, two versions of our framework are proposed.
-The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020} and the second one uses a TBATS model \citep{alysha2011} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.}
+The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020}, the second one uses Thetam as per-time-series predictor \citep{hyndman2020} and the last one uses a TBATS model \citep{alysha2011}.}
 
@@
 For the first parametric per-time-series models, existing Python  libraries named \texttt{statsmodels} and  \texttt{tbats} are used to estimate the different parameters $\statparam^n$.
-\textcolor{gray}{Depending on the choice of local parametric models, three versions of HERMES are proposed.
-The first one uses as predictors an additive exponential smoothing model as a reference close to \citet{smyl2020}.
-The second one uses the TBATS model of \citet{alysha2011} and  achieves the highest accuracy results on the fashion dataset.
-The neural network architecture} \textcolor{orange}{The architecture of the recurrent neural network corrector model} is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
+\textcolor{orange}{The architecture of the recurrent neural network corrector model} is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
 A classical Adam optimizer is used with a learning rate and a batch size set using a grid search.
@@
 The last approach is the recent state-of-the-art model called DeepAR and introduced in \citet{salinas2020}.
-The Python package \texttt{GluonTS} \citep{Alexandrov2020} was used to train DeepAR on the fashion dataset with a gridsearch to tune the main hyperparameters.} \textcolor{gray}{As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.}
+The Python package \texttt{GluonTS} \citep{Alexandrov2020} was used to train DeepAR on the fashion dataset with a gridsearch to tune the main hyperparameters.}
 
@@
 For each of them, a variation with the inclusion of the weak signals (\textit{-ws}) is presented.}
-\textcolor{gray}{Two versions of HERMES are proposed.
-They are called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
-Moreover, two versions with the inclusion of the weak signals (ws) are proposed.
-They are referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}.
-In order to provide a fair comparison, a \textit{lstm} with the weak signals named \textit{lstm-ws} is trained.}
 
@@
 This result highlights two important features of the proposed hybrid model: i) the final accuracy of the model is strongly impacted by the choice of the per-time-series predictor and ii) if the per-time-series predictor is well chosen regarding the nature of the time series, the resulting HERMES model seems to outperforms other state-of-the-art approaches.}
-\textcolor{gray}{Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slightly outperform the alternatives in terms of MASE and are stable across the different trainings.
-Regarding \textit{hermes-ets},   although it is very similar to the baseline \citet{smyl2020}, its accuracy remains low in comparison to the \textit{lstm} benchmark or HERMES using TBATS.}
 
@@
 Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} predictions and illustrates some Tbats weaknesses that can be corrected by the hybrid approach.}
-\textcolor{gray}{
-Models using our weak signals perform similarly as without-weak-signals models for the MASE.
-Interestingly, weak signals significantly improve the accuracy in detecting emerging and declining trends.
-Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} models and some weaknesses that can be corrected.}
 
@@
 The Adam optimizer is used and the MASE is directly used as the loss function.
-\textcolor{gray}{Finally a rolling window is applied on the train set so as to increase the number of examples and improve the training process.} \textcolor{orange}{As some of the m4 weekly time series have many years of historical data, a rolling window is finally applied on the train set so as to increase the number of examples and improve the training process.} The number of slinding windows, the learning rate, the batch size, the RNN architecture and input size are set using a grid search and detailled in \ref{sec:m4gridsearch}.
+\textcolor{orange}{As some of the m4 weekly time series have many years of historical data, a rolling window is finally applied on the train set so as to increase the number of examples and improve the training process.} The number of slinding windows, the learning rate, the batch size, the RNN architecture and input size are set using a grid search and detailled in \ref{sec:m4gridsearch}.
 
@@
   \caption{\textcolor{orange}{Results summary on 4 differents sub sample of  Fashion time series: i) disrupting time series, ii) stable time series, iii) seasonal time series and iv) noisy time series.
-Models with a $^*$ in their name have access to the influencers external signal.}}\vspace{0.5cm}
+Models with a $^*$ in their name have access to the external signal.}}\vspace{0.5cm}
  \centering

### 2023-07-04 tmlr_submission/hermes_paper_revision/hermes_paper.tex
add a discussion section

@@
 As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}.
-The raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.
+\textcolor{orange}{In this example, the raw and normalized time series of the Jersey top trend for females in China ($y^{c,g,m,j}$ with $c$=Top,  $g$=Female, $m$=China and  $j$=Jersey top) are presented.
+So as to compute the normalized signal, the raw time series of the Jersey top trend for females in China is divied by the deseasonalized raw time series representing the global Top trend for female in China.}
 
@@
 \caption{Example of difference between the raw sequence and the normalized one for the Jersey top fashion trend for females in China.
-In this example, we normalize by the deseasonalized global top fashion trend for females in China.
-(Top) Time series representing the raw signal of the Jersey top fashion trend for females in China.
+In this example, \textcolor{orange}{the Jersey top fashion raw time series for females in China is normalized} by the deseasonalized global top raw time series for females in China.
+\textcolor{orange}{The final normalized time series is finally expresssed as a share of the global catagery.} (Top) Time series representing the raw signal of the Jersey top fashion trend for females in China.
 (Bottom) Time series representing the normalized signal of the Jersey top fashion trend for females in China.}
@@
 
+\textcolor{orange}{
+\subsection{Discussion}
+Results of the two previous forecasting tasks illustrate that the proposed hybrid method is a general framework, easily adaptable to different use cases and showing remarkable accuracy results able to compete with other state-of-the-art methods.
+With its neural network component, it is also able to leverage any kind of external signals, which is starting to become essential in more and more forecasting applications.
+However, the presented method also shows some weaknesses listed above:
+\begin{itemize}
+\item With the inclusion of a neural network at the end of the framework, the interpretability of the final prediction of the HERMES method is not possible.
+For instance, the use of the external signal can not be easily assessed and confidence intervals provided by the statistical predictors are no longer valid when they are used in the hybrid framework.
+A possible idea already studied in the literature is to reverse the order by using first a neural network to compute a set of parameters that is then used by an interpretable model (see for instance the DeepAR model introduced in \cite{salinas2020}.)
+\item The proposed hybrid approach can be computationally long to train and to use in inference.
+Compared to neural-network-based models, the statistical component of the hybrid model has to be retrained for every new time series.
+For HERMES variations using a complexe statistical predictor like TBATS, this step can be expensive especially on large datasets.
+\item In the Fashion use case, the inclusion and use of the external signals by the HERMES model seems to be sub-optimal.
+For several examples, the external signal starts to burst but the HERMES approach does not use this information to totally change the first parametric prediction and forecast a burst of the main signal.
+A possible explanation is that the external signals are relevant only in a few fashion time series.
+Knowing when and how to use them correctly seems to be too difficult for the corrector component part.
+An ongoing work is to use several neural network models specialized on different uses of the external signals.
+Then depending on the past of the time series and the external signals, a hidden state could be used to choose which neural network correctors.
+In addition to bringing more flexibility on the use of the external signals, this promising work could also improve the interpretability of the final prediction depending at which specialized neural network model was chosen in the final prediction.
+\end{itemize}
+}
 \section{Conclusion}
 \label{sec:conclusion}
-In this paper, we propose  a new hybird model for non stationary time series forecasting.
+In this paper, we propose a new hybrid model for non stationary time series forecasting.
 By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks.
@@
 In addition, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided.
-\textcolor{orange}{We show that it is possible to represent fashion data with time series and introduce statistical models based on social media data.
-}% Furthermore, with a special focus on the behaviour of influencers, it becomes possible to better anticipate consumers' needs and avoid massive wastes due to overstocks.}
- By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
+\textcolor{orange}{We show that it is possible to represent fashion data with time series and introduce statistical models based on social media data.} By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
 As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.

### 2023-07-04 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex
update answers_reviewer_3.tex

@@
 	\textbf{Author response:} We are not sure of the notation in the question of the referee, in the paper we introduce $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$ but not $\hat{y}^{c,g,m}$.
-We present below a explanation of the two statistic $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$ which is now detailed in the paper.
+We present below a explanation of the two statistic $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$:
 	\begin{itemize}
-	\item $\Tilde{y}^{c,g,m}$ is the time series representing the behaviour of the global cloth type $c$ for the gender $g$ on the market $m$ \textcolor{red}{Est-ce que cela sifnifie que $\Tilde{y}^{c,g,m}$  est la somme sur $i$ (ou sur $j$ dans la nouvelle notation du papier) des $y^{c,g,m,i}$ ?
-Si oui, il faut le dire ici et dans le papier, c'est plus explicite.}.
+	\item $\Tilde{y}^{c,g,m}$ is the time series representing the behaviour of the global cloth type $c$ for the gender $g$ on the market $m$.
 It can be for example the time series representing the evolution of the general pants for females in Europe.
@@
 	\end{itemize}	
+To remove all gray area on this topic, additional information (regarding the Jersey Top normalization example) has been added at the end of Section 2.2 and in the legend to Figure 3.
 
@@
 
-	\textbf{Author response:} We thank the referee for this remark and supplementary information has been added in the result sections and in appendix of the revised paper.
+	\textbf{Author response:} We thank the referee for this remark and supplementary information has been added in the result sections and in the appendix of the revised paper.
 As future works on the dataset, we attempt to build a second fashion dataset gathering more time series and additional external signals such as fashion shows signals, brands signals etc...
-
- Concerning the forecasting model, we agree that desining models to explain the time delay between weak signals shifts and their consequences on the target signals is an interesting objective.
-We believe that this is out of the scope of the present paper but this is the topic of an ongoing work using hidden states to leverage  the impact of external signals on the main signal.\
+Concerning the forecasting model, we acknowledge that we did not discuss enough about the limits of the proposed approach.
+In the revised version of the paper, a discussion section is added at the end of Section 4.
+For instance, we agree that designing models to explain the time delay between weak signals shifts and their consequences on the target signals is an interesting objective.
+We believe that this is out of the scope of the present paper but this is the topic of an ongoing work using hidden states to leverage  the impact of external signals on the main signal.\\
 

### 2023-07-05 tmlr_submission/hermes_paper_revision/hermes_paper.tex
minor changes

@@
 \textcolor{orange}{In this example, the raw and normalized time series of the Jersey top trend for females in China ($y^{c,g,m,j}$ with $c$=Top, $g$=Female, $m$=China and $j$=Jersey top) are presented.
-So as to compute the normalized signal, the raw time series of the Jersey top trend for females in China is divied by the deseasonalized raw time series representing the global Top trend for female in China.}
+So as to compute the normalized signal, the raw time series of the Jersey top trend for females in China is divied by the deseasonalized raw time series representing the global Top trend for female in China ($\bar{y}^{c,g,m}$ with $c$=Top, $g$=Female and $m$=China).}
 

### 2023-07-06 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex
updates of Jean on the main paper + answer reviewer 3

@@
 Then, we only define trends that are relevant for the fashion industry.
-For instance, the A-line dress is identified where a dress is detected with a particular length, a particular shape and a particular collar shape, all of these details detected with different models.
+For instance, the Mini A-line dress fashion trend is identified where the dress category is detected with a particular shape and a particular length, all of these details detected with different models.
 These associations of fine-grain attributes are defined by a team of fashion experts and are not provided with the paper.
@@
 The index of fashion trends represents the name of a fashion clothing relevant for the fashion industry.
-It can be just one attribute detected by a visual recognition model (ex: the sneakers) but it can also be a combination of several attributes (ex: the A-line dress).
+It can be just one attribute detected by a visual recognition model (ex: the Sneakers) but it can also be a combination of several attributes (ex: the Slim Sole Retro Basketball Sneakers).
 As the fashion trends names are anonymized in the proposed dataset, the architecture behind the fashion trends definition is not presented in this paper.\\

### 2023-07-06 tmlr_submission/hermes_paper_revision/hermes_paper.tex
updates of Jean on the main paper + answer reviewer 3

@@
 They can be just one attribute detected by a visual recognition model, for example the sneakers fashion trend.
-They can also be a combination of several attributes, for instance the A-line dress fashion trend which is a combination of several attributes (dress length, collar shape, etc..) each one detected with a specific vision recognition model.}
+They can also be a combination of several attributes, for instance the Mini A-line dress fashion trend which is a combination of several attributes (dress length, shape, category,...) each one detected with a specific vision recognition model.}
 
@@
 An overview of the dataset can be found in Table~\ref{tab:fashiondataset}.
-\textcolor{orange}{For privacy issues, all the trends names are anonymized and for each trend, only the following macro information are revealed: the geolocalisation, the gender and the cloth type.}
+\textcolor{orange}{All the trends names are anonymized and for each trend, only the following macro information are revealed: the geolocalisation, the gender and the cloth type.}
 

### 2023-07-09 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex
Update answers_reviewer_3.tex

@@
 These associations of fine-grain attributes are defined by a team of fashion experts and are not provided with the paper.
+
 Concerning the machine failures, all the visual recognition models used to build the proposed dataset have been trained with a standard process involving a train, a eval and a test set. 
 Thus, models showing poor performance in terms of accuracy and recall on the test set have been dismissed.
-Please note that the data acquisition pipeline has been detailed and extended in Section 2.
-\\
+No additional human correction has been done.
+In the proposed paper, we focus on time series prediction so this has a limited impact on our claims.
+Of course improving visual recognition models would modify slightly the dataset but the time series  prediction challenges would remain similar.
+
+Please note that the data acquisition pipeline has been detailed and extended in Section 2. \\
 
@@
 	\textbf{Author response:} We agree with the referee and we acknowledge that we have not sufficiently presented the diversity of behaviours hidden in the proposed fashion dataset.
-So as to improve this point, a new section is added in appendix of the revised version of the paper where 4 different sub-samples of time series are defined and studied separately.
+So as to improve this point, a new section is added in the appendix of the revised version of the paper where 4 different sub-samples of time series are defined and studied separately.
 \\
@@
 It can be just one attribute detected by a visual recognition model (ex: the Sneakers) but it can also be a combination of several attributes (ex: the Slim Sole Retro Basketball Sneakers).
-As the fashion trends names are anonymized in the proposed dataset, the architecture behind the fashion trends definition is not presented in this paper.\\
+As the fashion trends names are anonymized in the proposed dataset, the architecture used to define the fashion trends is not presented in this paper.\\
 
@@
 It can be for example the time series representing the evolution of the general pants for females in Europe.
-The sequence $\Tilde{y}^{c,g,m}$ is then used to normalize each time series $y^{c,g,m,i}$ with the same $c$, $g$ and $m$.
+The sequence $\Tilde{y}^{c,g,m}$ is then used to normalize each time series $y^{c,g,m,j}$ with the same $c$, $g$ and $m$.
 All the fashion trends of pants for females in Europe are normalized by the time series representing the general pants for females in Europe.
@@
 	\end{itemize}	
-To remove all gray area on this topic, additional information (regarding the Jersey Top normalization example) has been added at the end of Section 2.2 and in the legend to Figure 3.
+Additional information (regarding the Jersey Top normalization example) has been added at the end of Section 2.2 and in the legend to Figure 3.
 
@@
 The fraction of the final prediction due to $y^{pred}$ or $y^{corr}$ is variable and depends on the nature of the time series (and the external signal if it is provided to the corrector model).
-A good illustration of this point is presented in a new section added in the appendix of the revised paper.
+An illustration is presented in a new section added in the appendix of the revised paper.
 In this section, we study the accuracy of the HERMES model on sub-samples of time series sharing the same behaviour.

### 2023-07-10 tmlr_submission/hermes_paper_revision/hermes_paper.tex
Update hermes_paper.tex

@@
 \subsection{Discussion}
-Results of the two previous forecasting tasks illustrate that the proposed hybrid method is a general framework, easily adaptable to different use cases and showing remarkable accuracy results able to compete with other state-of-the-art methods.
-With its neural network component, it is also able to leverage any kind of external signals, which is starting to become essential in more and more forecasting applications.
-However, the presented method also shows some weaknesses listed above:
+Results of the two previous forecasting tasks illustrate that the proposed hybrid method is a general framework, easily adaptable to different use cases and able to compete with other state-of-the-art methods.
+With its neural network component, it is also able to leverage any kind of external signals, which which could become essential in more and more forecasting applications.
+The experiments highlight some limitations that may be the topic of future works.
 \begin{itemize}
-\item With the inclusion of a neural network at the end of the framework, the interpretability of the final prediction of the HERMES method is not possible.
-For instance, the use of the external signal can not be easily assessed and confidence intervals provided by the statistical predictors are no longer valid when they are used in the hybrid framework.
-A possible idea already studied in the literature is to reverse the order by using first a neural network to compute a set of parameters that is then used by an interpretable model (see for instance the DeepAR model introduced in \cite{salinas2020}.)
-\item The proposed hybrid approach can be computationally long to train and to use in inference.
-Compared to neural-network-based models, the statistical component of the hybrid model has to be retrained for every new time series.
+\item In its current form, the use of the neural network prevents the interpretability of the final prediction.
+The use of the external signal can not be easily assessed and no confidence intervals are provided with the hybrid framework.
+Future works can focus on designing more intepretable models, using for instance Bayesian neural networks, or combining neural networks with state space models.
+\item The proposed hybrid approach can be computationally intensive, for instance  compared to classical neural-network-based models.
+A solution to improve this limitation is to propose new  procedures to train jointly both parts of the model with mini batches of observations.
+%, the statistical component of the hybrid model has to be retrained for every new time series.
 For HERMES variations using a complexe statistical predictor like TBATS, this step can be expensive especially on large datasets.
-\item In the Fashion use case, the inclusion and use of the external signals by the HERMES model seems to be sub-optimal.
-For several examples, the external signal starts to burst but the HERMES approach does not use this information to totally change the first parametric prediction and forecast a burst of the main signal.
-A possible explanation is that the external signals are relevant only in a few fashion time series.
-Knowing when and how to use them correctly seems to be too difficult for the corrector component part.
-An ongoing work is to use several neural network models specialized on different uses of the external signals.
-Then depending on the past of the time series and the external signals, a hidden state could be used to choose which neural network correctors.
-In addition to bringing more flexibility on the use of the external signals, this promising work could also improve the interpretability of the final prediction depending at which specialized neural network model was chosen in the final prediction.
+\item In the Fashion use case, the inclusion and use of the external signals could be improved as the external signals are relevant only in a few fashion time series.
+An ongoing work is to use several neural networks specialized on different uses of the external signals.
+Depending on the past of the time series and the external signals, a hidden state could be used to switch between models.% In addition to bringing more flexibility on the use of the external signals, this promising work could also improve the interpretability of the final prediction depending at which specialized neural network model was chosen in the final prediction.
 \end{itemize}

### 2023-07-10 tmlr_submission/hermes_paper_revision/hermes_paper.tex
Update hermes_paper.tex

@@
 \textcolor{orange}{
-On a large dataset as the fashion dataset, looking at aggregated metrics can often hide relevant results, especially on sub samples sharing the same behaviours.
-To illustrate this point, a study of 4 sub samples of the fashion dataset is proposed in this section.
-Their are defined as follows:
+A study of 4 subsamples of the fashion dataset is proposed in this section. They are defined as follows.
 \begin{itemize}
-\item \textbf{disrupting time series}: In retail and fashion industries, a strategic issue is to correctly anticipate new trends that will burst or collapse in the next weeks, months or years.
-To detect this sub sample of trends in the fashion dataset, the following approach is proposed: Using the \textit{snaive} model, a prediction of the last year of data is computed for each trend and the associated MASE.
-The disrupting time series are defined as the 1000 time series where the snaive prediction got the highest MASE.
-\item \textbf{stable time series}: By contrast, a group of stable trends is presented.
-To define them, the same methodology as the previous group is used.
-We define them as the 1000 time series where the \textit{snaive} prediction reached the lowest MASE.
-\item \textbf{seasonal time series}: Another relevant group of time series is sequences showing a strong seasonal pattern.
-So as to detect them, we compute for each trend the seasonality strength metric introduced in \citet{wang2006}.
-The seasonal time series group is the 1000 fashion time series with the highest seasonality strength metric.
+\item \textbf{disrupting time series}: in retail and fashion industries, a strategic issue is to correctly anticipate new trends that will burst or collapse in the next weeks, months or years.
+To detect this subsample of trends in the fashion dataset, the following approach is proposed: using the \textit{snaive} model, a prediction of the last year of data is computed for each trend with the associated MASE.
+The disrupting time series are defined as the 1000 time series where the snaive prediction has  the highest MASE.
+\item \textbf{stable time series}: by contrast, a group of stable trends is presented. They are the 1000 time series where the \textit{snaive} prediction with the lowest MASE. 
+\item \textbf{seasonal time series}: we compute for each trend the seasonality strength metric introduced in \citet{wang2006}.
+The seasonal time series group are the 1000 fashion time series with the highest seasonality strength metric.
 \item \textbf{noisy time series}: Finally, several time series of the fashion dataset represent niche trends only worn and posted on social media by a few people.
@@
 In order to detect them, we use the seasonality and trend strength metrics presented in \citet{wang2006}.
-For each time series, the average of these two quantities is computed and we define the time series group as the 1000 sequences with the lowest average.
+For each time series, the mean of these two quantities is computed and we define the time series group as the 1000 sequences with the lowest average.
 \end{itemize}
-Table~\ref{tab:fashionsubsample} displays the MASE of each model introduced in Section~\ref{sec:exp} on the 4 sub samples of time series.
+Table~\ref{tab:fashionsubsample} displays the MASE of each model introduced in Section~\ref{sec:exp} on the 4 subsamples of time series.
 Several relevant results can be highlighted.
 Firstly, models using the influencer weak signals strongly outperform other candidates on the disruptive time series.
-This result is even more visible with the HERMES approach where variations using the weak signals are always better than the ones without.
-These results illustrate the really predictive strength of the influencer signals proposed in the fashion dataset and prove empirically the impact of influencers on the fashion industries.
-Secondly, on stable time series and seasonal time series, a relevant interest of the hybrid approach is revealed.
-Looking at the result of \textit{hermes-tbats}, we can see that this hybrid model can use the strength of \textit{tbats} to compute a first accurate prediction and then, use the strength of a global neural network to understand more complex patterns.
-This strength is even more visible on seasonal time series where hybrid approaches largely outperform neural network models presented in the benchmarks.
-Finally, on noisy time series, we can see that neural network methods reach the highest accuracy and are the least impacted by these difficult trends.
-Furthermore, for all the HERMES approaches, we can note that the final hybrid predictions and the per-time-series models' predictions are the same.
-The error-correction model does not try to predict the noise and lets the per-time-series models' predictions as they are.}
+This result is even more visible with the HERMES approach where models using the weak signals are always better than the ones without.
+These results illustrate empirically the impact of weak signals on final predictions.
+Secondly, results of \textit{hermes-tbats} on stable time series and seasonal time series, highlight the interest in using an hybrid model.
+This  is even more visible on seasonal time series where hybrid approaches largely outperform neural network models presented in the benchmarks.
+Finally, on noisy time series, we can see that neural network models reach the highest accuracy.
+Furthermore, for all the HERMES approaches, we can note that the final hybrid predictions and the per-time-series predictions are the same.}
 
 \begin{table}
-  \caption{\textcolor{orange}{Results summary on 4 differents sub sample of  Fashion time series: i) disrupting time series, ii) stable time series, iii) seasonal time series and iv) noisy time series.
+  \caption{\textcolor{orange}{Results summary on 4 differents subsamples of  Fashion time series: i) disrupting time series, ii) stable time series, iii) seasonal time series and iv) noisy time series.
 Models with a $^*$ in their name have access to the external signal.}}\vspace{0.5cm}

### 2023-07-10 tmlr_submission/hermes_paper_revision/hermes_paper.tex
Update hermes_paper.tex

@@
 iii) Compute the OWA as the average of the relative MASE and SMAPE obtained is step ii).
-As an example on the m4 weekly dataset, the method \textit{hermes-tbats} gets a MASE of 7.383 and a SMAPE of 2.191.
-The benchmark method \textit{snaïve} obtains a MASE of 9.161 and a SMAPE of 2.777.
+As an example on the M4 weekly dataset, the method \textit{hermes-tbats} has a MASE of 7.383 and a SMAPE of 2.191.
+The benchmark method \textit{snaïve} has a MASE of 9.161 and a SMAPE of 2.777.
 Thus the OWA of  \textit{hermes-tbats} is equal to 0.797.
-\begin{equation*}
-    OWA_{\textit{hermes-tbats}} = \frac{1}{2}(\frac{7.282}{9.161} + \frac{2.191}{2.777}) \approx 0.797
-\end{equation*}
+%\begin{equation*}
+%    OWA_{\textit{hermes-tbats}} = \frac{1}{2}(\frac{7.282}{9.161} + \frac{2.191}{2.777}) \approx 0.797
+%\end{equation*}
 

### 2023-07-10 tmlr_submission/hermes_paper_revision/answers_reviewer_4.tex
add answers_reviewer_4.tex

\documentclass[10pt]{article} % For LaTeX2e
\usepackage{tmlr}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{tmlr}
% To de-anonymize and remove mentions to TMLR (for example for posting to preprint servers), instead use the following:
%\usepackage[preprint]{tmlr}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{amssymb,amsmath,amsthm}
\usepackage[pdftex]{graphicx}

\title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}

% Authors must not appear in the submitted version. They should be hidden
% as long as the tmlr package is used without the [accepted] or [preprint] options.
% Non-anonymous submissions will be rejected without review.

\author{\name \'Etienne David \email etienne.david@heuritech.com \\
      \addr SAMOVAR, Télécom SudParis,\\
      Institut Polytechnique de Paris, 91120 Palaiseau, France
      \AND
      \name Jean Bellot \email jean.bellot@heuritech.com \\
      \addr Heuritech, \\
      6 Rue de Braque, 75003 Paris
      \AND
      \name Sylvain Le Corff \email sylvain.lecorff@gmail.com\\
      \addr LPSM, \\
      Sorbonne Université, UMR CNRS 8001, 75005, Paris
      }

% The \author macro works with any number of authors. Use \AND 
% to separate the names and addresses of multiple authors.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\def\month{01}  % Insert correct month for camera-ready version
\def\year{2023} % Insert correct year for camera-ready version
\def\openreview{\url{https://openreview.net/forum?id=XXXX}} % Insert correct link to OpenReview for camera-ready version

\begin{document}

\maketitle

We would like to thank the reviewer for the appreciation of the paper and the constructive feedback. We have carefully considered all comments and we will propose a revision of the paper accordingly. In the meantime, you can find below detailed responses and an overview of some of the  modifications that will be added in the revised manuscript.

\section*{Detailed responses}

\subsection*{Requested changes:}
\begin{itemize}
	\item {\em ``Clearly define the terms like trend and cloth type using examples.''} \medskip

	\textbf{Author response:} We thank the referee for this remark and we acknowledge that we have not presented enough the definition of what we call a fashion trend. In the revision of the article, additional information has been added to clarify this point as well as a complete example of the Jersey top trend for women in China.\\

	\item {\em ``Section 2 should be described in a top-down manner if the resulting dataset is claimed to be one of the main contributions. Describe first what the resulting data looks like, then explain how you generated it.''} \medskip

	\textbf{Author response:} We understand the remark of the reviewer and reversing the order could be a nicer way to present the fashion dataset. However, regarding the reviewing timeline, we will not be able to deeply change the structure of Section 2 before the end of the process. We apologize for that and we hope that the current structure of Section 2 with the modification made in the revised version is acceptable.\\

	\item {\em ``It is not clear if the authors are calming technical contributions in the preprocess approaches. If so, the authors need to validate the specific choices like (1). The figure looks like a cherry-picked example.''} \medskip

	\textbf{Author response:} We thank the referee for this remark. The preprocess approach presented in (1) is not presented as a technical contribution but more as a straightforward way to normalize data from social networks. In fact, as the popularity of social media has increased since the last few years, it is easier to collect data nowaday than in 2015. This principle is illustrated in the first graph of Figure 3 where the raw volume of the Jersey top time series is continuously increasing from 2015 to 2020. The question here is to understand if this increase of visibility is a consequence of the increase of the users interest in the Jersey top or just the increase of social media use. In (1) we propose to divide each proposed time series by a norm time series presenting the same social media bias. For instance, the Jersey top from female in China is normalized by the time series representing the evolution of the general Top from female in China. Regarding the second graph of Figure 3, we can see that the normalized signal of the Jersey top is flat. We can conclude that the increase of the raw signal of this time series is only due to the increase of the volume collected through the years and not the explosion of the visibility of this trend on social media.\\

	\item {\em ``The univariate model adopted is not clearly described. What is the model?''} \medskip

	\textbf{Author response:} We thank the referee for this remark. One of the novelties of the proposed approach is that we present a general hybrid framework able to include any kind of univariate model and it is why we only introduced a general $f^n()$ in Section 3. We acknowledge that this strength of the proposed model was not sufficiently highlighted in the original paper. Consequently, additional information has been added in Section 3 and a third HERMES variation has been added in Section 4 to illustrate this point.\\

	\item {\em ``The term "error correction" sounds misleading as there is not such an explicit algorithm to compute the error. Perhaps the second term of (3) should be called just the correction term. ''} \medskip

	\textbf{Author response:} We call the second term of (3) "error correction" to illustrate that its purpose is to anticipate future errors of the time-series parametric models and correct them. We agree that calling it "correction term" also seems appropriate and the two terms could be used interchangeably.\\

	\item {\em ``I need methodological validation on (4). Apparently, the scaling of the input of RNN is critical to serving the RNN term as the coefficient of the correction term.''} \medskip

	\textbf{Author response:} The 10000 time series in the fashion dataset have different volumes, from $10^-5$ for niche trends to $10^-1$ for common trends. As we want to train the RNN part on the whole dataset to learn cross dynamics, the normalization step of the RNN input is inevitable. Two methods have been tested and are discussed at the end of Section 3.2. i) We can normalize the RNN input by directly dividing it by the prediction of the univariate model prediction. ii) We can normalize the RNN input by the mean volume of the time series. The first solution presents a main issue that it shows instabilities with time series closed to 0 and it can simply not be used if the prediction of the univariate model prediction hits 0. Consequently, the second solution is used in the proposed hybrid framework.\\
\end{itemize}
\end{document}

### 2023-07-11 tmlr_submission/hermes_paper_revision/answers_reviewer_4.tex
Update answers_reviewer_4.tex

@@
 	\textbf{Author response:} We thank the referee for this remark and we acknowledge that we have not presented enough the definition of what we call a fashion trend.
-In the revision of the article, additional information has been added to clarify this point as well as a complete example of the Jersey top trend for women in China.\\
+In the revision of the article, additional information has been added to clarify this point as well as a complete example of the Jersey top trend for women in China.
+We also provided additional information on the dataset and on the fashion time series in Section 2 of the revised paper.\\
 
@@
 However, regarding the reviewing timeline, we will not be able to deeply change the structure of Section 2 before the end of the process.
-We apologize for that and we hope that the current structure of Section 2 with the modification made in the revised version is acceptable.\\
+We apologize for that and we hope that the current structure of Section 2 and all the modifications made in the revised version are  acceptable.\\
 
@@
 	\textbf{Author response:} We thank the referee for this remark.
-The preprocess approach presented in (1) is not presented as a technical contribution but more as a straightforward way to normalize data from social networks.
-In fact, as the popularity of social media has increased since the last few years, it is easier to collect data nowaday than in 2015.
+The preprocess approach presented in (1) is not presented as a technical contribution but  a  way to normalize data from social networks.
+We gave a few details to explain this normalization in order to explain how the dataset provided with the paper was produced.
+In Section 2, we explain the process to obtain time series from social media data.
+These steps are not a contribution as we only used standard signal processing techniques.
+However, we believe that they help understanding the dataset which is a first contribution of the paper as it is proposed publicly.
+The presentation of the dataset has been modified in Section 2 and in Appendix A, we hope that this clarifies the contribution of the paper.\\
+
+%In fact, as the popularity of social media has increased since the last few years, it is easier to collect data nowaday than in 2015.
 This principle is illustrated in the first graph of Figure 3 where the raw volume of the Jersey top time series is continuously increasing from 2015 to 2020.

### 2023-07-11 tmlr_submission/hermes_paper_revision/answers_reviewer_4.tex
Update answers_reviewer_4.tex

@@
 One of the novelties of the proposed approach is that we present a general hybrid framework able to include any kind of univariate model and it is why we only introduced a general $f^n()$ in Section 3.
+In the paper we propose different models: exponential smoothing, Thetam and TBATS.
+These models are given with the references as they are not the contribution of the paper, but could be added in the appendix if necessary.
+
 We acknowledge that this strength of the proposed model was not sufficiently highlighted in the original paper.
@@
 
-	\textbf{Author response:} The 10000 time series in the fashion dataset have different volumes, from $10^-5$ for niche trends to $10^-1$ for common trends.
+	\textbf{Author response:} The 10000 time series in the fashion dataset have different volumes, from $10^{-5}$ for niche trends to $10^{-1}$ for common trends.
 As we want to train the RNN part on the whole dataset to learn cross dynamics, the normalization step of the RNN input is inevitable.

### 2023-07-11 tmlr_submission/hermes_paper_revision/answers_reviewer_4.tex
Update answers_reviewer_4.tex

@@
 	\textbf{Author response:} We thank the referee for this remark.
-One of the novelties of the proposed approach is that we present a general hybrid framework able to include any kind of univariate model and it is why we only introduced a general $f^n()$ in Section 3.
+One of the novelties of the proposed approach is that we present a general hybrid framework able to include all univariate models and it is why we only introduced a general notation $f^n()$ in Section 3 for this model.
 In the paper we propose different models: exponential smoothing, Thetam and TBATS.
@@
 
-We acknowledge that this strength of the proposed model was not sufficiently highlighted in the original paper.
+We acknowledge that this feature of the proposed model was not sufficiently highlighted in the original paper.
 Consequently, additional information has been added in Section 3 and a third HERMES variation has been added in Section 4 to illustrate this point.\\
@@
 Two methods have been tested and are discussed at the end of Section 3.2.
-i) We can normalize the RNN input by directly dividing it by the prediction of the univariate model prediction.
-ii) We can normalize the RNN input by the mean volume of the time series.
-The first solution presents a main issue that it shows instabilities with time series closed to 0 and it can simply not be used if the prediction of the univariate model prediction hits 0.
-Consequently, the second solution is used in the proposed hybrid framework.\\
+i) The RNN input can be normalized by directly dividing it by the prediction of the univariate model prediction.
+ii) The RNN input can be normalized by the mean volume of the time series.
+The first solution presents a main issue that it shows instabilities with time series close to 0 and it can simply not be used if the prediction of the univariate model prediction hits 0.
+Consequently, the second solution is used in the proposed hybrid framework.
+
+Of course, other scaling procedures could be used.
+In this paper this is not the main topic of interest and this step is used to design a training procedure that can deal with thousands of time series.
+Analyzing in detail the impact of the scaling procedure on the overall training is left for future works.\\
 \end{itemize}

### 2023-07-12 tmlr_submission/hermes_paper_revision/hermes_paper.tex
minor change (correction term)

@@
 Let $\rnn(.;\rnnparam)$ be the recurrent neural network model where $\rnnparam$ are  unknown parameters.
-Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\rnnparam$, the error-corrector predictions $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\rnnparam$, the \textcolor{orange}{correction terms} $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
 $$
@@
 For the first parametric per-time-series models, existing Python  libraries named \texttt{statsmodels} and  \texttt{tbats} are used to estimate the different parameters $\statparam^n$.
-\textcolor{orange}{The architecture of the recurrent neural network corrector model} is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
+\textcolor{orange}{The architecture of the recurrent neural network error-corrector model} is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
 A classical Adam optimizer is used with a learning rate and a batch size set using a grid search.

### 2023-07-12 tmlr_submission/hermes_paper_revision/answers_reviewer_4.tex
update answers_reviewer_4.tex

@@
 
-	\textbf{Author response:} We call the second term of (3) "error correction" to illustrate that its purpose is to anticipate future errors of the time-series parametric models and correct them.
-We agree that calling it "correction term" also seems appropriate and the two terms could be used interchangeably.\\
+	\textbf{Author response:} We thank the referee for these remarks and the text has been corrected accordingly.\\
 

### 2023-07-20 tmlr_submission/hermes_paper_revision/answers_reviewer_4.tex
add modif linked to the second answer of the 4th reviewer

@@
 Analyzing in detail the impact of the scaling procedure on the overall training is left for future works.\\
+
+	\item {\em ``I understand the review was delayed.
+My comment is based on the original submission.
+If the data preprocessing is a sort of heuristic chosen in an ad hoc manner (that's perfectly fine, if you are not claiming technical contributions there), you may want to mention it clearly to avoid confusion.''} \medskip
+
+	\textbf{Author response: We agree with the referee and the  the text has been corrected accordingly.}
+
 \end{itemize}

### 2023-07-20 tmlr_submission/hermes_paper_revision/hermes_paper.tex
add modif linked to the second answer of the 4th reviewer

@@
 Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,\textcolor{orange}{j}}$ in order to remove bias.
-Let $\Tilde{y}^{c,g,m}$ be the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe).
+\textcolor{orange}{The pre-processing of data presented in this section does not constitute a technical contribution.
+We present this step in depth to clearly explain how fashion time series are constructed.} Let $\Tilde{y}^{c,g,m}$ be the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe).
 With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$.

### 2023-07-22 tmlr_submission/hermes_paper_revision/hermes_paper.tex
update revised paper

@@
 \textcolor{orange}{The pre-processing of data presented in this section does not constitute a technical contribution.
-We present this step in depth to clearly explain how fashion time series are constructed.} Let $\Tilde{y}^{c,g,m}$ be the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe).
+This step is presented in depth to  explain how the dataset provided with this paper is constructed.} Let $\Tilde{y}^{c,g,m}$ be the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe).
 With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$.

### 2023-08-22 tmlr_submission/hermes_paper_revision/hermes_paper.tex
camera-ready version

--- 2023-07-12 tmlr_submission/hermes_paper_revision/hermes_paper.tex
@@
 \documentclass[10pt]{article} % For LaTeX2e
-\usepackage{tmlr}
+%\usepackage{tmlr}
 % If accepted, instead use the following line for the camera-ready submission:
-%\usepackage[accepted]{tmlr}
+\usepackage[accepted]{tmlr}
 % To de-anonymize and remove mentions to TMLR (for example for posting to preprint servers), instead use the following:
@@
 
-\def\month{01}  % Insert correct month for camera-ready version
+\def\month{08}  % Insert correct month for camera-ready version
 \def\year{2023} % Insert correct year for camera-ready version
-\def\openreview{\url{https://openreview.net/forum?id=XXXX}} % Insert correct link to OpenReview for camera-ready version
+\def\openreview{\url{https://openreview.net/forum?id=4ofFo7D5GL&noteId=QnOhD911vc}} % Insert correct link to OpenReview for camera-ready version
 
@@
 \begin{abstract}
-Developing models and algorithms to \textcolor{orange}{predict nonstationary} time series is a long standing statistical problem.
+Developing models and algorithms to predict nonstationary time series is a long standing statistical problem.
 It is crucial for many applications, in particular for fashion or retail industries, to make optimal inventory decisions and avoid massive wastes.
@@
 Multivariate time series forecasting is a widespread statistical problem with  many applications, see for instance \citet{sarkka2013, douc2014, zucchini2017} and the numerous references therein.
-Parametric generative models provide explainable predictions with statistical guarantees \textcolor{orange}{owing to} a precise modeling of the predictive distributions of new data based on a record of past observations.
-\textcolor{orange}{Calibrating these models, for instance using maximum likelihood inference, often requires a fair amount of tuning so as to design time-series-specific models able to provide  accurate forecasts and sharp confidence intervals.} Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
+Parametric generative models provide explainable predictions with statistical guarantees owing to a precise modeling of the predictive distributions of new data based on a record of past observations.
+Calibrating these models, for instance using maximum likelihood inference, often requires a fair amount of tuning so as to design time-series-specific models able to provide  accurate forecasts and sharp confidence intervals.
+Depending on the use case, statistical properties of the signal and the available data, many families of models have been proposed for time series.
 The exponential smoothing model \citep{Brown1961}, the Trigonometric Box-Cox transform, ARMA errors, Trend, and Seasonal components model (TBATS) \citep{alysha2011}, or the ARIMA with the Box-Jenkins approach \citep{box2015} are for instance very popular parametric generative models.
@@
 In many fields, single or few time series have become thousands of sequences with various statistical properties.
-In this new context, classical \textcolor{orange}{time-series-specific} statistical models show limitations when dealing with numerous heterogeneous data.
-\textcolor{orange}{By constrast,} recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \citet{ hochreiter1997,vaswani2017, siami2018, li2019, lim2019,salinas2020}.
+In this new context, classical time-series-specific statistical models show limitations when dealing with numerous heterogeneous data.
+By constrast, recurrent neural networks and recent sequence to sequence deep learning architectures offer very appealing numerical alternatives thanks to their capability of leveraging any kind of heterogeneous multivariate data, see for instance \citet{ hochreiter1997,vaswani2017, siami2018, li2019, lim2019,salinas2020}.
 The DeepAR model proposed in \citet{salinas2020} provides a global model from many time series based on a multi-layer recurrent neural network with LSTM cells.
@@
 With our fashion expertise, we detected several groups of highly influential fashion users.
-Analyzing their specific behaviours on social media, we associate with each time series an external weak signal representing the same fashion trends on \textcolor{orange}{this} sub-category of users.
+Analyzing their specific behaviours on social media, we associate with each time series an external weak signal representing the same fashion trends on this sub-category of users.
 They are called weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal.
@@
 Following this work, we present in this paper HERMES, a new hybrid recurrent model for time series forecasting with inclusion of external signals.
-This new architecture is decomposed  into two parts: \textcolor{orange}{First, a per-time-series parametric statistical model is trained on each sequence.
+This new architecture is decomposed  into two parts: First, a per-time-series parametric statistical model is trained on each sequence.
 Then, a global recurrent neural network is trained to evaluate and correct the forecast of the first collection of models.
-The ability to deal with external signals} reveal the real potential of the hybrid approach: a global neural network, able to leverage large amounts of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.
+The ability to deal with external signals reveal the real potential of the hybrid approach: a global neural network, able to leverage large amounts of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.
 
@@
 \label{sec:dataset}
-
-%\textcolor{orange}{Social Networks have appeared as an impressive data source to follow the evolution of fashion over the time.
-Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world.
-To do it automatically for thousands of trends, the following methodology is introduced in this section and summarized in Figure~\ref{fig:pipeline}.}
 
@@
 We targeted 5 strategic markets for the retail industry using posts localisation: the United States, Europe, Japan, Brazil and China.
-\textcolor{orange}{With compliance of privacy and data protection, only public accounts are selected and no potential private information is used, saved or revealed during the whole process.}
+With compliance of privacy and data protection, only public accounts are selected and no potential private information is used, saved or revealed during the whole process.
 The second step consists in creating a powerful visual recognition framework to be able to detect clothes details on pictures like the type of clothing, the form, the size, the color, the texture, etc.
@@
 As a final step, fashion experts aggregate those attributes to define relevant trends for the fashion and retails industry.
-\textcolor{orange}{We call them fashion trends.
+We call them fashion trends.
 They can be just one attribute detected by a visual recognition model, for example the sneakers fashion trend.
-They can also be a combination of several attributes, for instance the Mini A-line dress fashion trend which is a combination of several attributes (dress length, shape, category,...) each one detected with a specific vision recognition model.}
+They can also be a combination of several attributes, for instance the Mini A-line dress fashion trend which is a combination of several attributes (dress length, shape, category,...) each one detected with a specific vision recognition model.
 
@@
 We aggregate results by fashion trend definition over the time and  thousands of trends are finally translated from social media to time series.
-We note $y^{c,g,m,\textcolor{orange}{j}}$ the final raw sequence representing the fashion trend $\textcolor{orange}{j}$ of the cloth type $c$ for the gender $g$ on market $m$.
-At each time $t$, $y^{c,g,m,\textcolor{orange}{j}}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $\textcolor{orange}{j}$ of the cloth type $c$ for the gender $g$.
+We note $y^{c,g,m,j}$ the final raw sequence representing the fashion trend $j$ of the cloth type $c$ for the gender $g$ on market $m$.
+At each time $t$, $y^{c,g,m,j}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $j$ of the cloth type $c$ for the gender $g$.
 As an illustration, example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.
@@
 
-Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,\textcolor{orange}{j}}$ in order to remove bias.
+Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,j}$ in order to remove bias.
+The pre-processing of data presented in this section does not constitute a technical contribution.
+This step is presented in depth to  explain how the dataset provided with this paper is constructed.
 Let $\Tilde{y}^{c,g,m}$ be the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe).
@@
 The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$.
-Finally, for any fashion trend $\textcolor{orange}{j}$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
+Finally, for any fashion trend $j$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
 \begin{equation}
-    y^{i}_t = \frac{y^{c,g,m,\textcolor{orange}{j}}_{t}}{\bar{y}^{c,g,m}_t}\,,
+    y^{i}_t = \frac{y^{c,g,m,j}_{t}}{\bar{y}^{c,g,m}_t}\,,
 \end{equation}
 
-where T denotes the number of available time steps \textcolor{orange}{and $i$ represent a unique identifier summarizing the 4 information $c$, $g$, $m$ and $j$}.
-The time series $y^{c,g,m,\textcolor{orange}{j}}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences.
+where T denotes the number of available time steps and $i$ represent a unique identifier summarizing the 4 information $c$, $g$, $m$ and $j$.
+The time series $y^{c,g,m,j}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences.
 With this normalizing step, most of the social media bias is removed and the final normalized sequences are expressed in share of category.
 As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}.
-\textcolor{orange}{In this example, the raw and normalized time series of the Jersey top trend for females in China ($y^{c,g,m,j}$ with $c$=Top, $g$=Female, $m$=China and $j$=Jersey top) are presented.
-So as to compute the normalized signal, the raw time series of the Jersey top trend for females in China is divied by the deseasonalized raw time series representing the global Top trend for female in China ($\bar{y}^{c,g,m}$ with $c$=Top, $g$=Female and $m$=China).}
+In this example, the raw and normalized time series of the Jersey top trend for females in China ($y^{c,g,m,j}$ with $c$=Top, $g$=Female, $m$=China and $j$=Jersey top) are presented.
+So as to compute the normalized signal, the raw time series of the Jersey top trend for females in China is divied by the deseasonalized raw time series representing the global Top trend for female in China ($\bar{y}^{c,g,m}$ with $c$=Top, $g$=Female and $m$=China).
 
@@
 \caption{Example of difference between the raw sequence and the normalized one for the Jersey top fashion trend for females in China.
-In this example, \textcolor{orange}{the Jersey top fashion raw time series for females in China is normalized} by the deseasonalized global top raw time series for females in China.
-\textcolor{orange}{The final normalized time series is finally expresssed as a share of the global catagery.} (Top) Time series representing the raw signal of the Jersey top fashion trend for females in China.
+In this example, the Jersey top fashion raw time series for females in China is normalized by the deseasonalized global top raw time series for females in China.
+The final normalized time series is finally expresssed as a share of the global catagery.
+(Top) Time series representing the raw signal of the Jersey top fashion trend for females in China.
 (Bottom) Time series representing the normalized signal of the Jersey top fashion trend for females in China.}
@@
 An overview of the dataset can be found in Table~\ref{tab:fashiondataset}.
-\textcolor{orange}{All the trends names are anonymized and for each trend, only the following macro information are revealed: the geolocalisation, the gender and the cloth type.}
+All the trends names are anonymized and for each trend, only the following macro information are revealed: the geolocalisation, the gender and the cloth type.
 
@@
 In this paper, a more general framework able to deal with any kind of per-time-series models is provided.
-\textcolor{orange}{Thus, the choice of the parametric model can be adjusted depending on the nature of the time series.
+Thus, the choice of the parametric model can be adjusted depending on the nature of the time series.
 The only limitation is the computational time as we aim at forecasting thousands of time series simultaneously.
 For instance, hidden Markov models provide a very interesting framework but inference of such models requires computationally costly iterative procedures such as Expectation Maximization-based algorithms often combined with Monte Carlo estimates of unknown expectations.
-Choosing these approaches as per-time-series predictors would considerably slow the overall training process of the hybrid model.}
-
-\textcolor{orange}{In Section~\ref{sec:exp}, we introduce three declinations of the hybrid framework  using different per-time-series predictors to highlight the adaptability of our approach.
-The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020}, the second one uses Thetam as per-time-series predictor \citep{hyndman2020} and the last one uses a TBATS model \citep{alysha2011}.}
+Choosing these approaches as per-time-series predictors would considerably slow the overall training process of the hybrid model.
+
+In Section~\ref{sec:exp}, we introduce three declinations of the hybrid framework  using different per-time-series predictors to highlight the adaptability of our approach.
+The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020}, the second one uses Thetam as per-time-series predictor \citep{hyndman2020} and the last one uses a TBATS model \citep{alysha2011}.
 
@@
 Let $\rnn(.;\rnnparam)$ be the recurrent neural network model where $\rnnparam$ are  unknown parameters.
-Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\rnnparam$, the \textcolor{orange}{correction terms} $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
+Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\rnnparam$, the correction terms $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
 $$
@@
 
-\textcolor{orange}{In this section, performance of the hybrid model is assessed and compared with several other approaches. The HERMES framework is evaluated on two different use cases.
+In this section, performance of the hybrid model is assessed and compared with several other approaches. The HERMES framework is evaluated on two different use cases.
 \begin{itemize}
@@
 \end{itemize}
-}
-
-\textcolor{orange}{\subsection{Fashion use case}}
-
-\textcolor{orange}{\subsubsection{Training}}
+
+\subsection{Fashion use case}
+
+\subsubsection{Training}
 The fashion dataset is split into three blocks, {\em train}, {\em eval} and {\em test} sets.
@@
 As an illustration, an example of our split is shown in Figure~\ref{fig:train_eval_test_set}.
-\textcolor{orange}{Note that we have just enough historical data to perform the proposed train/eval/test split.
+Note that we have just enough historical data to perform the proposed train/eval/test split.
 Therefore, the common solution of applying a rolling window to increase the different splits cannot be used.
-Only one couple input/output is provided for each split per time series.}
+Only one couple input/output is provided for each split per time series.
 
 For the first parametric per-time-series models, existing Python  libraries named \texttt{statsmodels} and  \texttt{tbats} are used to estimate the different parameters $\statparam^n$.
-\textcolor{orange}{The architecture of the recurrent neural network error-corrector model} is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
+The architecture of the recurrent neural network error-corrector model is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension.
 A classical Adam optimizer is used with a learning rate and a batch size set using a grid search.
@@
 This choice of $\mathrm{L}_1$ loss function is motivated by its robustness to outliers which accounts for some time series in the fashion industry with very specific behaviours.
-The loss and previous parameters are all set with a complete grid search \textcolor{orange}{and have to be adapted regarding the use case}.
+The loss and previous parameters are all set with a complete grid search and have to be adapted regarding the use case.
 See \ref{sec:fashiongridsearch} for additional results concerning the loss function choice and \ref{sec:m4gridsearch} for a complete grid search example.
@@
 
-\textcolor{orange}{\subsubsection{Benchmarks, hybrid models and metrics}}
+\subsubsection{Benchmarks, hybrid models and metrics}
 \label{sec:fashiontraining}
@@
 
-\textcolor{orange}{We also compare our model with recent deep learning architectures for time series.
+We also compare our model with recent deep learning architectures for time series.
 The Prophet model introduced in \citet{Taylor2017} is proposed and implemented with the available package bearing the same name \texttt{prophet}, and three models based on recurrent neural networks called \textit{lstm}, \textit{lstm-ws} and \textit{deepar} are used.
@@
 The last approach is the recent state-of-the-art model called DeepAR and introduced in \citet{salinas2020}.
-The Python package \texttt{GluonTS} \citep{Alexandrov2020} was used to train DeepAR on the fashion dataset with a gridsearch to tune the main hyperparameters.}
-
-\textcolor{orange}{A strength of the proposed HERMES framework is that it can handle any kind of parametric model.
+The Python package \texttt{GluonTS} \citep{Alexandrov2020} was used to train DeepAR on the fashion dataset with a gridsearch to tune the main hyperparameters.
+
+A strength of the proposed HERMES framework is that it can handle any kind of parametric model.
 Thus, three versions of HERMES are proposed on the fashion dataset using different local parametric models.
@@
 Declinations are called respectively \textit{hermes-ets}, \textit{hermes-tbats} and \textit{hermes-thetam} according to the per-time-series model choice.
-For each of them, a variation with the inclusion of the weak signals (\textit{-ws}) is presented.}
+For each of them, a variation with the inclusion of the weak signals (\textit{-ws}) is presented.
 
@@
 
-\textcolor{orange}{\subsubsection{Results}}
+\subsubsection{Results}
 
@@
 It is one of the main motivations why this model is used on the best HERMES candidate as the predictor model.
-\textcolor{orange}{All HERMES versions show consequent improvements regarding their per-time-series predictors in terms of MASE.
+All HERMES versions show consequent improvements regarding their per-time-series predictors in terms of MASE.
 \textit{hermes-tbats} outperforms the two other declinations and all the benchmarks on the fashion dataset.
-This result highlights two important features of the proposed hybrid model: i) the final accuracy of the model is strongly impacted by the choice of the per-time-series predictor and ii) if the per-time-series predictor is well chosen regarding the nature of the time series, the resulting HERMES model seems to outperforms other state-of-the-art approaches.}
-
-\textcolor{orange}{Regarding the impact of the weak signals, Table~\ref{tab:metricresults} highlights an interesting improvement of the accuracy metric when weak signals are included.
-Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} predictions and illustrates some Tbats weaknesses that can be corrected by the hybrid approach.}
+This result highlights two important features of the proposed hybrid model: i) the final accuracy of the model is strongly impacted by the choice of the per-time-series predictor and ii) if the per-time-series predictor is well chosen regarding the nature of the time series, the resulting HERMES model seems to outperforms other state-of-the-art approaches.
+
+Regarding the impact of the weak signals, Table~\ref{tab:metricresults} highlights an interesting improvement of the accuracy metric when weak signals are included.
+Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} predictions and illustrates some Tbats weaknesses that can be corrected by the hybrid approach.
 
@@
 The mean and the standard deviation of the 10 results are displayed.
-\textcolor{orange}{Models with a $^*$ in their name have access to the external signal.}}
+Models with a $^*$ in their name have access to the external signal.}
   \centering
@@
      \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
-     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.845} && \textcolor{orange}{-} &&& \textcolor{orange}{0.463} && \textcolor{orange}{-}\\
+     \textit{thetam} && 0.845 && - &&& 0.463 && -\\
      \textit{arima} && 0.826 && -&&& 0.464 && - & \\
      \textit{ets} && 0.807 && -&&& 0.449 && - & \\
-     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.485} && \textcolor{orange}{-}\\
+     \textit{prophet} && 0.786 && - &&& 0.485 && -\\
      \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
      \textit{hermes-ets-ws*} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
-     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.764} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.497} && \textcolor{orange}{0.005}\\
-     \textcolor{orange}{\textit{hermes-thetam-ws*}} && \textcolor{orange}{0.760} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.520}} && \textcolor{orange}{0.010}\\
+     \textit{hermes-thetam} && 0.764 && 0.003 &&& 0.497 && 0.005\\
+     \textit{hermes-thetam-ws*} && 0.760 && 0.004 &&& \textbf{0.520} && 0.010\\
      \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
-     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.752} && \textcolor{orange}{0.018} &&& \textcolor{orange}{0.459} && \textcolor{orange}{0.015}\\
+     \textit{deepar} && 0.752 && 0.018 &&& 0.459 && 0.015\\
      \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
@@
 We can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases.
-On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms \textcolor{orange}{deep-model-based approaches such as \textit{lstm} of \textit{deepar}}.
+On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms deep-model-based approaches such as \textit{lstm} of \textit{deepar}.
 In fact, providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require large amounts of data to do so.
 By contrast, the HERMES approach can rely on its first statistical part and consequently needs less data to be trained and to obtain interesting performance.
-\textcolor{orange}{We can nevertheless note that the gain brought by the error-corrector recurrent model decreases as the size of the dataset diminishes.}
+We can nevertheless note that the gain brought by the error-corrector recurrent model decreases as the size of the dataset diminishes.
 
@@
 the mean and the standard deviation of the 10 results are displayed.
-\textcolor{orange}{Models with a $^*$ in their name have access to the external signal.}\vspace{0.5cm}}
+Models with a $^*$ in their name have access to the external signal.\vspace{0.5cm}}
  \centering
@@
 	 &&&&&&&&&&\\
-     \textit{snaive} && 0.871 && - &&& \textcolor{orange}{0.383} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.837} && \textcolor{orange}{-} &&& \textcolor{orange}{0.484} && \textcolor{orange}{-} &\\
-     \textit{arima} && 0.821 && - &&& \textcolor{orange}{0.472} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.801} && \textcolor{orange}{-} &&& \textcolor{orange}{0.469} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.788} && \textcolor{orange}{-} &&& \textcolor{orange}{0.476} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.767} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.482} && \textcolor{orange}{0.009} &\\
-     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.476} && \textcolor{orange}{0.009} &\\
-      \textcolor{orange}{\textit{hermes-ets-ws*}} && \textcolor{orange}{0.766} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.507}} && \textcolor{orange}{0.013} &\\
-     \textit{stlm} && 0.765 && - &&& \textcolor{orange}{0.493} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-thetam-ws*}} && \textcolor{orange}{0.763} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.501} && \textcolor{orange}{0.009} &\\
-     \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.740} && \textcolor{orange}{0.007} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
-     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.738} && \textcolor{orange}{0.017} &&& \textcolor{orange}{0.465} && \textcolor{orange}{0.013} &\\
-     \textit{tbats} && 0.734 && - &&& \textcolor{orange}{0.466} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{lstm-ws*}} && \textcolor{orange}{0.731} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.492} && \textcolor{orange}{0.012} &\\
-     \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.721} && \textcolor{orange}{0.002} &&& \textcolor{orange}{0.487} && \textcolor{orange}{0.014} &\\
-     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws*}}} && \textcolor{orange}{0.717} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.500} && \textcolor{orange}{0.010} &\\
+     \textit{snaive} && 0.871 && - &&& 0.383 && - &\\
+     \textit{thetam} && 0.837 && - &&& 0.484 && - &\\
+     \textit{arima} && 0.821 && - &&& 0.472 && - &\\
+     \textit{ets} && 0.801 && - &&& 0.469 && - &\\
+     \textit{prophet} && 0.788 && - &&& 0.476 && - &\\
+     \textit{hermes-ets} && 0.767 && 0.004 &&& 0.482 && 0.009 &\\
+     \textit{hermes-thetam} && 0.766 && 0.002 &&& 0.476 && 0.009 &\\
+      \textit{hermes-ets-ws*} && 0.766 && 0.004 &&& \textbf{0.507} && 0.013 &\\
+     \textit{stlm} && 0.765 && - &&& 0.493 && - &\\
+     \textit{hermes-thetam-ws*} && 0.763 && 0.005 &&& 0.501 && 0.009 &\\
+     \textit{lstm} && 0.740 && 0.007 &&& 0.487 && 0.014 &\\
+     \textit{deepar} && 0.738 && 0.017 &&& 0.465 && 0.013 &\\
+     \textit{tbats} && 0.734 && - &&& 0.466 && - &\\
+     \textit{lstm-ws*} && 0.731 && 0.005 &&& 0.492 && 0.012 &\\
+     \textit{hermes-tbats} && 0.721 && 0.002 &&& 0.487 && 0.014 &\\
+     \textbf{\textit{hermes-tbats-ws*}} && 0.717 && 0.004 &&& 0.500 && 0.010 &\\
 
@@
 	 &&&&&&&&&&\\
-     \textit{snaive} && 0.876 && - &&& \textcolor{orange}{0.330} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.822} && \textcolor{orange}{-} &&& \textcolor{orange}{0.470} && \textcolor{orange}{-} &\\
-     \textit{arima} && 0.814 && - &&& \textcolor{orange}{0.400} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.812} && \textcolor{orange}{0.009} &&& \textcolor{orange}{0.446} && \textcolor{orange}{0.031} &\\
-     \textcolor{orange}{\textit{lstm}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.015} &&& \textcolor{orange}{0.446} && \textcolor{orange}{0.049} &\\
-     \textcolor{orange}{\textit{hermes-thetam-ws*}} && \textcolor{orange}{0.810} && \textcolor{orange}{0.008} &&& \textcolor{orange}{0.479} && \textcolor{orange}{0.024} &\\
-     \textcolor{orange}{\textit{deepar}} && \textcolor{orange}{0.804} && \textcolor{orange}{0.024} &&& \textcolor{orange}{0.393} && \textcolor{orange}{0.029} &\\
-     \textcolor{orange}{\textit{hermes-ets-ws*}} && \textcolor{orange}{0.792} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.386} && \textcolor{orange}{0.010} &\\
-     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.790} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.374} && \textcolor{orange}{0.005} &\\
-     \textcolor{orange}{\textit{lstm-ws*}} && \textcolor{orange}{0.789} && \textcolor{orange}{0.010} &&& \textcolor{orange}{0.485} && \textcolor{orange}{0.036} &\\
-     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.400} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.767} && \textcolor{orange}{-} &&& \textcolor{orange}{\textbf{0.490}} && \textcolor{orange}{-} &\\
-     \textit{tbats} && 0.745 && - &&& \textcolor{orange}{0.440} && \textcolor{orange}{-} &\\
-     \textit{stlm} && 0.742 && - &&& \textcolor{orange}{0.450} && \textcolor{orange}{-} &\\
-     \textcolor{orange}{\textit{hermes-tbats}} && \textcolor{orange}{0.741} && \textcolor{orange}{0.005} &&& \textcolor{orange}{0.462} && \textcolor{orange}{0.021} &\\
-     \textcolor{orange}{\textbf{\textit{hermes-tbats-ws*}}} && \textcolor{orange}{\textbf{0.737}} && \textcolor{orange}{0.004} &&& \textcolor{orange}{0.486} && \textcolor{orange}{0.027} &\\
+     \textit{snaive} && 0.876 && - &&& 0.330 && - &\\
+     \textit{thetam} && 0.822 && - &&& 0.470 && - &\\
+     \textit{arima} && 0.814 && - &&& 0.400 && - &\\
+     \textit{hermes-thetam} && 0.812 && 0.009 &&& 0.446 && 0.031 &\\
+     \textit{lstm} && 0.810 && 0.015 &&& 0.446 && 0.049 &\\
+     \textit{hermes-thetam-ws*} && 0.810 && 0.008 &&& 0.479 && 0.024 &\\
+     \textit{deepar} && 0.804 && 0.024 &&& 0.393 && 0.029 &\\
+     \textit{hermes-ets-ws*} && 0.792 && 0.003 &&& 0.386 && 0.010 &\\
+     \textit{hermes-ets} && 0.790 && 0.004 &&& 0.374 && 0.005 &\\
+     \textit{lstm-ws*} && 0.789 && 0.010 &&& 0.485 && 0.036 &\\
+     \textit{ets} && 0.786 && - &&& 0.400 && - &\\
+     \textit{prophet} && 0.767 && - &&& \textbf{0.490} && - &\\
+     \textit{tbats} && 0.745 && - &&& 0.440 && - &\\
+     \textit{stlm} && 0.742 && - &&& 0.450 && - &\\
+     \textit{hermes-tbats} && 0.741 && 0.005 &&& 0.462 && 0.021 &\\
+     \textbf{\textit{hermes-tbats-ws*}} && \textbf{0.737} && 0.004 &&& 0.486 && 0.027 &\\
   \end{tabular}
@@
 
-\textcolor{orange}{\subsection{M4 competition use case}}
+\subsection{M4 competition use case}
 \label{sec:m4result}
@@
 
-\textcolor{orange}{\subsubsection{Training}}
+\subsubsection{Training}
 The M4 dataset is preprocessed as follows. As some sequences are short (93 time steps), they limit the window size $w$ of the RNN.  
@@
 The Adam optimizer is used and the MASE is directly used as the loss function.
-\textcolor{orange}{As some of the m4 weekly time series have many years of historical data, a rolling window is finally applied on the train set so as to increase the number of examples and improve the training process.} The number of slinding windows, the learning rate, the batch size, the RNN architecture and input size are set using a grid search and detailled in \ref{sec:m4gridsearch}.
+As some of the m4 weekly time series have many years of historical data, a rolling window is finally applied on the train set so as to increase the number of examples and improve the training process.
+The number of slinding windows, the learning rate, the batch size, the RNN architecture and input size are set using a grid search and detailled in \ref{sec:m4gridsearch}.
 
@@
 
-\textcolor{orange}{\subsubsection{Evaluation}}
+\subsubsection{Evaluation}
 The proposed model is evaluated along with a rich collection of benchmarks provided by the M4 competition, encompassing statistical models and neural network approaches.
@@
 
-\textcolor{orange}{\subsubsection{Results}}
+\subsubsection{Results}
 The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}.
@@
 
-\textcolor{orange}{
 \subsection{Discussion}
@@
 A solution to improve this limitation is to propose new  procedures to train jointly both parts of the model with mini batches of observations.
-%, the statistical component of the hybrid model has to be retrained for every new time series.
-For HERMES variations using a complexe statistical predictor like TBATS, this step can be expensive especially on large datasets.
 \item In the Fashion use case, the inclusion and use of the external signals could be improved as the external signals are relevant only in a few fashion time series.
 An ongoing work is to use several neural networks specialized on different uses of the external signals.
-Depending on the past of the time series and the external signals, a hidden state could be used to switch between models.% In addition to bringing more flexibility on the use of the external signals, this promising work could also improve the interpretability of the final prediction depending at which specialized neural network model was chosen in the final prediction.
+Depending on the past of the time series and the external signals, a hidden state could be used to switch between models.
 \end{itemize}
-}
+
 \section{Conclusion}
@@
 In addition, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided.
-\textcolor{orange}{We show that it is possible to represent fashion data with time series and introduce statistical models based on social media data.} By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
+We show that it is possible to represent fashion data with time series and introduce statistical models based on social media data.
+By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
 As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture.
@@
 
-\textcolor{orange}{
 \section{Fashion dataset: a study of sub samples of time series sharing the same behaviour}
-}
-\textcolor{orange}{
+
 A study of 4 subsamples of the fashion dataset is proposed in this section. They are defined as follows.
@@
 Finally, on noisy time series, we can see that neural network models reach the highest accuracy.
-Furthermore, for all the HERMES approaches, we can note that the final hybrid predictions and the per-time-series predictions are the same.}
+Furthermore, for all the HERMES approaches, we can note that the final hybrid predictions and the per-time-series predictions are the same.
 
 \begin{table}
-  \caption{\textcolor{orange}{Results summary on 4 differents subsamples of  Fashion time series: i) disrupting time series, ii) stable time series, iii) seasonal time series and iv) noisy time series.
-Models with a $^*$ in their name have access to the external signal.}}\vspace{0.5cm}
+  \caption{Results summary on 4 differents subsamples of  Fashion time series: i) disrupting time series, ii) stable time series, iii) seasonal time series and iv) noisy time series.
+Models with a $^*$ in their name have access to the external signal.}\vspace{0.5cm}
  \centering
@@
   \includegraphics[width=.49\linewidth]{m4_learning_rate.png}
-  \includegraphics[width=1.\linewidth]{m4_batch_size.png}
+  \includegraphics[width=.49\linewidth]{m4_batch_size.png}
   \includegraphics[width=.49\linewidth]{m4_window_size.png}

### 2023-08-29 tmlr_submission/hermes_paper_revision/hermes_paper.tex
update git repo

@@
       \AND
-      \name Sylvain Le Corff \email sylvain.lecorff@gmail.com\\
+      \name Sylvain Le Corff \email sylvain.le\_corff@sorbonne-universite.fr\\
       \addr LPSM, \\
@@
 Our contribution is  twofold.
-We first provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} a dataset gathering \numberts\ weekly fashion time series.
+We first provide publicly\footnote[1]{\url{https://github.com/etidav/HERMES}} a dataset gathering \numberts\ weekly fashion time series.
 As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviours of influencers.
@@
 
-With this paper, we provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} a sample of $\numberts$ normalized fashion trends for men and women, over 9 different categories and 5 different markets.
+With this paper, we provide publicly\footnote[1]{\url{https://github.com/etidav/HERMES}} a sample of $\numberts$ normalized fashion trends for men and women, over 9 different categories and 5 different markets.
 Each sequence has 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values.
@@
 See \ref{sec:fashiongridsearch} for additional results concerning the loss function choice and \ref{sec:m4gridsearch} for a complete grid search example.
-The code is developed in Python using the Tensorflow library and publicly available\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}}.
+The code is developed in Python using the Tensorflow library and publicly available\footnote[1]{\url{https://github.com/etidav/HERMES}}.
 It allows the use of GPU to speed up the training process.
